### 2020-04-28 Draft_1.Rmd
initial commit with new repo

---
title: "Milestone 7"
author: "Maria Burzillo"
date: "3/28/2020"
output: 
  pdf_document:
    extra_dependencies: ["rotating"]
bibliography: final_proj_bib.bib
#biblio-style: "apalike"
link_citations: true
header_includes:
  usepackage{float}
  usepackage{dcolumn}
  usepackage{rotating}
  restylefloat{table}

---

# Abstract

@trounstine_segregation_2016 suggests that high levels of residential segregation are associated with increased political polarization and decreased public spending. In this analysis, I was able to successfully replicate @trounstine_segregation_2016’s main results. Adding onto her original analysis, I impute a large amount of missing data from the original dataset and re-run the analysis. Finally, I add in income segregation as a predictor in her regressions to assess whether this could be a confounding variable.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center")
knitr::write_bib(c("knitr", "stringr"), "bib.bib", width = 60)
library(haven)
library(gtable)
library(stargazer)
library(tidyverse)
library(gt)
library(gtsummary)
library(knitr)
library(stargazer)
library(lme4)
library(margins)
library(reprex)
library(plm)
library(devtools)
library(lfe)
library(Statamarkdown)
library(readxl)
library(starpolishr)
library(AER)
library(readxl)
library(naniar)
library(mice)
library(gtsummary)
library(VIM)
```

```{r data_imports, include = FALSE}

set.seed(100)

# import both datasets

rp <- read_dta("racial_polarization_winners.dta")
fin_seg<- read_dta("fin_seg.dta")

# add row numbers for fin_seg

fin_seg$row_num <- as.integer(rownames(fin_seg))

```

```{r data_cleaning_rp, include = FALSE}

# create a factor for year for the rp dataset
rp$year.f <- as.factor(rp$year)

# apply the condition that winner == 1 as in the Stata code for the rp regressions

rp_1<- rp %>%
  filter(winner == 1) %>%
  mutate(medincinterp = medincinterp/1000)

```

# Introduction

There is a large degree of variation in public goods spending across local governments. As a result, many scholars have worked to determine what factors may lead to the underprovision of public goods spending. Research in the past has associated racial diversity or changes in levels of diversity with the under-provision of public goods [@baqir_public_1999; @hopkins_diversity_2009].However, @trounstine_segregation_2016 argues that it is racial segregation, not diversity in and of itself, that results in the under-provision of public goods. Trounstine’s analysis consists of two main parts. First, she uses election and demographic data from 25 of America’s largest cities between 1990 and 2010 to run a multilevel mixed-effects linear regression with fixed effects for region and year and with random effects for cities in order to show that polarization increases with segregation. Trounstine measures segregation with Theil's H index, which measures the degree to which the diversity of a neighborhood differs from the diversity of the entire city. The second main part of Trounstine’s analysis looks at the ability of the Theil’s H segregation index to explain a variety of types of public expenditures by city using a sample of 2,637 cities with 13,742 city-year observations. Using linear regressions with fixed effects for cities and robust standard errors clustered by city, Trounstine finds a significant, negative correlation between segregation and public goods spending that is robust to the inclusion of a variety of relevant controls and an alternative specification in which the number of waterways is used as an instrument for segregation.

In this analysis, I first work to replicate the main results of @trounstine_segregation_2016 using R statistical software [@r]. The original data and Stata code made publically available by the author were downloaded via the Harvard Dataverse [@DVN/4LZXTY_2015]. I also make all of my code and analysis available on Github.^[ Link to my [Github repository](https://github.com/mburzillo/new_final_project) for this project.] I was successfully able to replicate the main results of @trounstine_segregation_2016 in R with the exception of some of the marginal analyses, which I was nevertheless able to replicate in Stata.

```{r data_prep_imputations, include = FALSE}

# select the relevant rows from the rp dataset

rp_impute <- rp %>%
  select("winner", "medincinterp",
             "biggestsplit", "H_citytract_multi_i", "diversityinterp",
             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
             "primary", "logpop", "year", "south", "midwest", "west", "geo_id2",
             "H_citytract_NHW_i", "whiteideology_fill2") %>%
  filter(winner == 1) %>%
  mutate(medincinterp = medincinterp/1000,
         year.f = as.factor(year))

# apply the conditions in Stata regression to the fin_seg dataset

fin_imp <- fin_seg %>%
  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0) %>%
  mutate(medinc_cpi = medinc_cpi/1000)

# select the relevant variables to be imputed

fin_imp <- fin_imp %>%
  select(H_citytract_NHW_i, dgepercap_cpi, diversityinterp, pctblkpopinterp, pctasianpopinterp,
         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
         pctcollegegradinterp, logpop, geo_id2, chng5pctblk, chng5pctlatino, chng5pctasian,
         ideology_fill, totaltractsf)

miss_var_summary(fin_imp)
miss_var_summary(rp_impute)

```

```{r obs_count, include = FALSE}

# calculate number of original observations

obs_fin_seg <- nrow(fin_imp)
obs_rp <- nrow(rp_impute)

```

One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data, which substantially constrains the sample size used in the regression analysis. For example, the regression analysis in the main specification using the the original racial polarization dataset exludes %`r round((obs_rp - 91)/obs_rp, 2)` of the observations, and the regression analysis in the main specification using the original financial segregation data excludes %`r round((obs_fin_seg - 13742)/ obs_fin_seg, 2)` of observations from the original dataset. As an extension of @trounstine_segregation_2016, I impute missing values in the original data using the mice package in R, which generates multivariate imputations using chained equations [@mice]. Then, I use the multiply imputed datasets to re-estimate the original models, pooling the results to generate final pooled regression coefficients and parameters.

Comparing the results of the original regressions and those done with the imputed data yields similar big picture results in terms of the direction of the signs on the coefficients on the segregation indices. Like in @trounstine_segregation_2016, I find that segregation is positively associated with political polarization and negatively associated with spending on public goods. However, the magnitude of the effects in most specifications has diminished and most results become statistically insignificant. While these findings do not necessarily challenge the results of @trounstine_segregation_2016, they do call into question the relative importance of segregation in determining public goods spending and political polarization and suggest that the results of @trounstine_segregation_2016 may not be quite as robust as once thought.

# Literature Review

Despite some progress made towards racial equity in the U.S. on other fronts, residential racial segregation continues to be prevasive and deeply entrenched in society [@fischer_distinguishing_2004; @oliver_paradoxes_2010; @massey_american_1993]. Research suggests that this kind of segregation has political consequences, as political cleavages in segregated cities tend to have racial as well as spatial dimensions [@massey_american_1993]. Neighborhoods are often important actors within local politics because local governments provide many functions that are allocational in nature and concern geographical space [@trounstine_segregation_2016]. Thus, when neighborhoods are divided on racial lines as well as spacial lines, it is natural to expect higher degrees of racial polarization as a result.

Studying residential segregation is difficult because its effects tend to differ by geographic level. On the neighborhood level, the kind of geographic racial isolation brought on by residential segregation has been associated with racial intolerance, resentment, and competition between racial groups [@oliver_paradoxes_2010]. Living within segregated neighborhoods has also been associated with holding negative stereotypes and perceptions about out groups [@eric_oliver_intergroup_2003]. As a result, homogeneous neighborhoods have been associated with increased racial tension and political polarization in comparison to integrated, diverse neighborhoods. However, at the city or metropolitan level, the opposite seems to be true: when considering larger geographic areas, diversity and integration are correlated with racial tension, competition, prejudice, lower levels of cooperation, and lower spending on public goods [@oliver_paradoxes_2010; @baqir_public_1999; @hopkins_diversity_2009]. While these differences in the expected effect of segregation on the geographic level may seem confusing at first, they make sense as they suggest that the most severely segregated areas are those that are diverse overall, but have many homogeneous neighborhoods. Thus, while people of different races co-exist within a highly segregated city, they live separately within their own neighborhoods, which creates an environment ripe for racial tension [@trounstine_segregation_2016]. It is thus not simply the level of diversity or integration that matters for racial harmony and cooperation, but their patterns within a larger geographic framework [@trounstine_segregation_2016; @oliver_paradoxes_2010; @bharathi_public_2018].

Political polarization along racial lines may lead to decreased public spending and goods provision because groups may have different preferences, which can make compromise hard, and because groups may preceive a disutility in out-groups receiving public goods expenditure [@baqir_public_1999]. @einstein_divided_2012 found evidence that racial segregation predicts large political divisions at the metropolitan level and that these divisions can create a lack of willingness to compromise and collaborate on local policy problems. @trounstine_segregation_2016 finds similar results at the city level: that residential racial segregation is associated with both increased political division and decreased public spending. Thus, these authors suggest that it is the combination of homogenous neighborhoods within a much larger, diverse geographic area that leads to increased political polarization and reduced public goods spending in local governments.

More recently, some scholars have called this hypothesis and its importance into question. For example, @lee_ethnic_2018 finds evidence that larger inequalities within the political system favoring socially powerful groups, not local diversity patterns leading to decreased cooperation, may be a better explanation of failures in public goods provision in diverse areas. Others suggest that additional factors, such as income segregation, may be important confounding factors in public goods provision. @an_its_2018, for example, suggests that the more closely related income inequality is to racial inequality, the less investment is made in public goods, and that this interaction was a better predictor of public goods spending patterns than measures of diversity. There is, in fact, a variety of evidence suggesting that it is meaningful to consider the effects of income inequaltiy and diversity and segregation jointly [@an_its_2018; @massey_american_1993]. Given the active debate in the literature over the relaitonships between diversity, segregation, public spending, and other factors, it is increasingly important to re-examine previously reported findings as a means of robustness checks.

# Replication

I was able to successfully replicate all of the main results from Trounstine (2016). All regressions and tables were fully replicated in R. As an example, in table X, I replicate Table 1 from page 713 of @trounstine_segregation_2016, which is also included as Figure 1 for comparison. However, I was unable to successfully replicate Trounstine (2016)’s marginal effects analyses and margins plots using R. There does not yet appear to be a built-in R function to calculate marginal or predicted effects or to generate margins plots from the complicated multi-level models employed in the original paper, and creating such a function was outside of the scope of this analysis. Nevertheless, these results were successfully replicated in Stata.

```{r include = FALSE}

## regression 1 Table 1

# fixed effects like a control variable

# lmer(dependent ~ predictors + (random predictors | group level))

# reml v. log likelihood: default in r appears to be log-likelihood. stata defaults to maximum likelihood

# perform a multi-level mixed-effects linear regression of biggest split on the multi-group H index with controls for Herfindahl Diversity Index, % Asian interpolated, % Black interpolated, % Latino interpolated, median household income interpolated, % renters interpolated, percent college grads interpolated, a dummy indicating if there were biracial candidates in the election, a dummy  indicating if the election was nonpartisan, an indicator if the election was a primary, and the log population. The regression also includes fixed effects for year and region and random effects for cities (geo_id2). Diversity is  included because of the claim that more diverse populations will have more heterogeneous political preferences. The other fixed effect control variables are included because they are known to be potentially correlated with segregation. winner == 1 requires that there was a winner in the election.

# regression specification. Apply REML = FALSE. The default for lmer() in R is
# to optimize the restricted (residual) maximum likelihood (REML) whereas in
# xtmixed in Stata the default is to optimize the log likelihood (which you can
# do in lmer() in R by setting REML = FALSE), so this will match the STATA code

m1 <- lmer(biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)

## regression 2 Table 1

# Perform the same regression as for Column 1 above but this time regress on the two-group calculation of Theil's H interpolated. It is unclear where the "diversity" variable is coming from, as the only variable related to diversity in the specificed dataset is diversityinterp. This is a problem that will need to be resolved. Essentially, this regression just tests an alternate specification to the first in which the segregation index in defined in terms of two-groups rather than multiple.

m2 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)

# perform the same regression as for column 2, but now add in a measure of
# average white political ideology. The point of this is to control for ideology
# so that the author can separate any effects of segregation from any potential
# effects of white political ideology. This is important because it is possible
# that segregation is just a proxy for white conservatism and thus failure to
# include this variable could lead to ommitted variable bias.

m3 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)

```

```{r results="asis", echo = FALSE}

# create a stargazer table of the results

t1 <- stargazer(m1, m2, m3, omit = c("year", "south", "midwest", "west"),
                header = FALSE,
                title = "\\textbf{Racial Polarization in Segregated Cities}",
                single.row = TRUE,
                no.space = FALSE,
                add.lines = list(c("Wald Chi Squarred", "a", "b", "c")),
                omit.stat = c("ll","rsq"),
                covariate.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Diversity", "Percent Asian", "Percent Black", "Percent Latino", "Medain HH Income (1000s)", "Percent Renters", "Percent College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology", "Constant"),
                notes = "This table displays...")

# note: "This table displays the results of the replication effort of the analyses conducted in Trounstine (2016) using the racial polarization dataset. The replication code can be found on my personal [Github repository](https://github.com/mburzillo/new_final_project). The original table is displayed for comparison as Figure 1.")

```

![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016. My replication of these results can be found in Table 1 in this paper.](table_1.png)

There was one interesting outcome from my attempt to replicate the original Stata code in R. Due to the differences in R and Stata in dealing with missing values, the results of my first replication of analyses using the financial segregation dataset were slightly different than the results in Stata from the original paper. In order to exclude cities from her analysis with only one census tract, Trounstine conditions her regressions in Stata such that the value for the number of census tracts is greater than one. In Stata, this does not remove missing values, whereas in R, it does. Since this variable is used only as a conditional filter and not as a regression variable (and thus, the observations with missing values for number of census tracts are not dropped), Trounstine’s analysis includes 14 cities and 58 observations with missing values for census tracts in addition to cities with two or more census tracts. This is a potential oversight on the part of the author, and I would suggest also dropping observations with missing census tract data, or else imputing them given that the aim of her condition was to exclude cities without a sufficient number of census tracts. Nevertheless, dropping these values did not have much of an effect on the subsequent results, likely because they represent a small proportion of the overall sample.

# Extension

One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data values in her original datasets. Because both R and Stata drop any observations with missing values for any of the variables used in a regression, this can exlcude a large portion of the data from the analysis and potentially bias the results if the data is not missing completely at random. A large amount of data is missing in both of the main datasets used in the analyses of @trounstine_segregation_2016. The main model specification using the racial polarization dataset exludes `r (obs_rp - 91)` of the original  `r obs_rp` observations, or  %`r round(100*(obs_rp - 91)/obs_rp,2)` of the data. Additionally, the main model specification using the financial segregation data set excludes `r round(obs_fin_seg - 13742,2)` of the original `r obs_fin_seg` observations, or %`r round(100*(obs_fin_seg - 13742)/ obs_fin_seg,2)` of observations from the original dataset.

In an attempt to better deal with the problem of missing data in @trounstine_segregation_2016, I impute missing values in the original data using the mice package in R, which generates multivariate imputations using chained equations [@mice]. While there are a variety of different imputation methods that could have been employed, multiple imputation (such as the multiple multivariate imputations generated by mice) is desireable because instead of inputting a single value such as the mean for missing values, it instead uses the distribution of the available data to estimate multiple potential values for the missing data. As a result, multiple imputation helps to account for the uncertainty inherent in the imputation process and allows for the calculation of standard errors around estimators. As a result, multiple imputation allows the researcher to more accurately assess the of uncertainty in the analysis in general.

Before performing the multiple imputations on the datasets, I first examined the missing data for patterns. To better understand any potential patterns in missing data, I plotted the pattern of missingness and created a histogram showing the frequency of missing values for those variables with missing values in figure X1 for the racial polarization data and figure X2 for the financial segregation data. Looking at figure X1, the histogram shows that the variables for the largest vote split along racial lines and the variable indicating whether or not the election had candidates of more than one race had by far the largest percentages of missing data, missing %`r round(sum(is.na(rp_impute$biggestsplit))/nrow(rp_impute)*100,2)` and  %`r round(sum(is.na(rp_impute$biracial))/nrow(rp_impute)*100,2)`, respectively. It is important to note that the variable for the largest vote split along racial lines is the dependent variable in the regresison analysis, and thus, we are missing a large percentage of this key variable. From the plot on the right, we can see that approximately 42% of observations are complete (have no missing values). There seem to be a correspondence between missing a value for the largest vote split and missing a value for the biracial election indicator. There also seem to be about 2% of values for wich most of the variables are missing. However, most observations are not missing more than 2-3 values.

```{r rp_missing_plot, include = FALSE, warning = FALSE}

# don't show the warning, it's just an irrelevant column missing a name

# plot the missing variables if desired

rp_facet <- rp_impute %>%
   select("medincinterp",
             "biggestsplit", "diversityinterp",
             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
               "south", "midwest", "west", "whiteideology_fill2", "year")

# gg_miss_var(rp_impute, show_pct = TRUE)

```

```{r rp_aggr_plot, echo = FALSE}

# select only the missing values

rp_aggr <- rp_impute %>%
   select("medincinterp",
             "biggestsplit", "diversityinterp",
             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
               "south", "midwest", "west", "whiteideology_fill2")

# create an aggr plot for the missing values

aggr(rp_aggr, bars = TRUE, col=c('navyblue','red'), numbers=TRUE, cex.axis=.5, gap=1, ylab=c("Proporiton of Missing Values","Combinations"))

# caption for this plot when I figure out how to do it... : This plot examines the pattern of missing data in the the original racial polarization dataset from Trounstine (2016). The plot on the left shows the percentage of missing data for each variable with missing data and reveals that the variables that are missing by far the most data are the largest vote split along racial lines (biggestsplit) and the variable indicating whether or not the election had candidates of more than one race (biracial). The plot on the right shows the pattern of missingness among the variables. We can see that approximately 42% of observations are complete (have no missing values). There seems to be a correspondence between missing a value for biggest split and missing biracial. There also seem to be about 2% of values for which most of the variables are missing. However, most observations are not missing more than 2-3 values.

```

In figure X2, we can similarly observe the trends for the financial segregation dataset. In this dataset, there is a very high proportion of missing variables for a number of variables. For example, there are `r sum(is.na(fin_imp$H_citytract_NHW_i))` missing values for the segregation index, which is the main independent variable, or %`r round(sum(is.na(fin_imp$H_citytract_NHW_i))/nrow(fin_imp)*100,2)` of the data. In this dataset, there are also many more observations for which values are missing for multiple variables in comparison to the racial polarization dataset. In total, a mere %`r .0058*100` of observations are complete for all variables included in the main specification for the financial segregaion dataset.

```{r fin_missing_plot, include = FALSE}

miss_var_summary(fin_imp)

gg_miss_var(fin_imp, show_pct = TRUE)

```

```{r fin_aggr_plot, echo = FALSE}

# select all variables with missing values for the aggr plot

fin_imp_aggr <- fin_imp %>%
  select(ideology_fill, H_citytract_NHW_i, chng5pctblk, chng5pctlatino, chng5pctasian, diversityinterp, pctblkpopinterp, pctasianpopinterp,
         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
         pctcollegegradinterp)

new_try <- head(fin_imp_aggr, 20)

aggr(new_try, plot = TRUE, bars = FALSE, col=c('navyblue','red'), numbers=TRUE)

# create the aggr plot

aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.5, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
title(main = "Patterns of Missingness in the Financial Segregation Data",
      sub = "Is this a caption? qiufwnjekfewkfnwein\nwefjwenmf wiufnwqjenf ewfuiwjnef nfijefnwjenfkqwjnf lqwjefnjqwefjwnef winfjqwhf hjwefwiuefief welfiunqlfjnqkjwe qqfniquwenjfjq iqfnjkjeq rfiunfj q")

# this plot tells us that only .58% of the data are complete (not missing anything)

# caption for this plot when I figure out how to do it... : This plot examines the pattern of missing data in the the original financial segregation dataset from Trounstine (2016). The plot on the left shows the percentage of missing data for each variable with missing data and reveals that a large number of variables are missing the vast majority of data. The plot on the right shows the pattern of missingness among the variables. We can see that only .58% of observations are complete (have no missing values), and a large majority of the observations are missing data for many variables.

```

Because neither dataset seems to exhibit any clear patterns in the missing, data, it makes sense to proceed with the imputation. For the racial polarization dataset, I performed multiple imputations with 20 iterations using mice, while for the financial segregation dataset, I performed only 5 iterations due to the large size of the dataset and computing limitaitons. A non-stochastic imputation method, Classification and Regression Trees (CART), was used instead of the default for the imputation for both datasets because of an error with matrix inversion caused by the data that prevented the use of the default method, predictive mean matching. For the racial polarization dataset, I included all of the variables used in the analysis associated with the dataset and was able to impute all missing values. For the financial segregation dataset, however, I only imputed values for the main independent variable, the segregation index, and a few other variables, although all variables used in the analysis were included in the data subset input into the mice function. More of the data could not be imputed from the financial segregation dataset due to computing and time constraints for this project given the dataset's large size and high proportion of missing values.

```{r rp_imputation, include = FALSE}

# Perform multiple imputations using the cart method. Because of the time it
# takes to run this function, I turned the results into a dataset to load in
# instead of re-running everytime.

max_it = 20

imp_1_rp <- mice(rp_impute, method = "cart", maxit = 20)

# can use the line below to check that there are now no missing values

# gg_miss_var(complete(imp_1_rp), show_pct = TRUE)

```

```{r fp_imputations, include = FALSE}

# perform multiple imputations. We have the same issue here with the default method as with the previous dataset so we use CART. Additionally, because of the extremely large size of this dataset, we choose to only impute the variable H_citytract_NHW_i, as it is the most frequently missing variable and also out main independent variable. Just imputing this allows us to include way more observations in the regression than the original data despite the still large number of NAs overall. One concern here would be that if there was some reason that this variable was missing rather than other variables that only imputing this variable could lead to some bias in the results.

# generate a blank run to get the method matrix

ini <- mice(fin_imp, maxit=0, print=F)

# view the current method settings

meth <- ini$method

# change the method variables for all variables except H_citytract_NHW_i to ""
# so that their missing values aren't imputed

meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""

# change the default method to "cart" so that we don't get the error

meth[c("H_citytract_NHW_i", "chng5pctblk", 
       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"

# perform the multiple imputations with 5 iterations

imp_fs <- mice(fin_imp, method = meth, maxit = 5)

# now there are manyb fewer missing variables!!!

miss_var_summary(complete(imp_fs))

head(complete(imp_fs))

miss_var_summary(fin_imp)

```

```{r new_imp}

fin_imp <- fin_imp %>%
  mutate(nas = is.na(H_citytract_NHW_i) + is.na(dgepercap_cpi) + is.na(diversityinterp) + is.na(pctblkpopinterp)  + is.na(pctasianpopinterp) + is.na(pctlatinopopinterp) + is.na(medinc_cpi) + is.na(pctlocalgovworker_100) + is.na(pctrentersinterp) + is.na(pctover65) + is.na(pctcollegegradinterp) + is.na(logpop) + is.na(geo_id2) + is.na(chng5pctblk) + is.na(chng5pctlatino) + is.na(chng5pctasian) + is.na(logpop) + is.na(geo_id2) + is.na(chng5pctblk) + is.na(chng5pctlatino) + is.na(chng5pctasian) + is.na(ideology_fill))

fin_imp %>%
  ggplot(aes(x = nas)) +
  geom_histogram()

fin_imp %>%
  group_by(nas) %>%
  summarise(n())

# exclude all observations with 17 out of 22 nas

fin_imp_sub <- fin_imp %>%
  filter(nas < 17)

nrow(fin_imp_sub)

# generate a blank run to get the method matrix

ini <- mice(fin_imp_sub, maxit=0, print=F)

# view the current method settings

meth <- ini$method

# change the method variables for all variables except H_citytract_NHW_i to ""
# so that their missing values aren't imputed

meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""

# change the default method to "cart" so that we don't get the error

meth[c("H_citytract_NHW_i", "chng5pctblk", 
       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"

# perform the multiple imputations with 5 iterations

new_imp_fs <- mice(fin_imp_sub, method = meth, maxit = 5)

miss_var_summary(complete(new_imp_fs))
```

## make sure to talk about the fact that still a large number of values missing for the imputed variables here

Before examining the results of Trounstine's model using the multiply imputed data, I first ran some diagnostic tests on the imputation results to make sure that everything ran as expected. First, I checked the convergence of the algorithm used within mice() by plotting the trace lines as a function of the number of iterations for each of the variables. Then, I visually inspected the distributions of the imputed data in comparison to the original data with density and strip plots. All of these checks suggested that the imputed values were within a plausible range of the data and that their distribution fit the underlying distribution of the data relatively well. The only cases in which there was some cause for concern were for some of the variables with very few missing values in the racial polarization dataset (such as the indicators for region). However, this is more or less to be expected given the small number of imputations performed in these cases. Thus, and especially because there are so few of these values missing in the actual datasets, this was not a major concern. See figures X and X1 to see the density plots of the imputed values overlayed on the density plots of the original variables. The rest of the plots and results of the diagnostic tests discussed here are presented in the Appendix.

```{r rp_densityplot, echo = FALSE}

densityplot(imp_1_rp)

```

```{r rp_imp_plot, include = FALSE}

# ideally, the fits will intertwine and not exhibit any trends at later iterations. This seems to generally be the case. There are some issues with the results for some of the variables with very few missing values, which makes sense as we would expect the mean to be less reliable due to the law of large numbers and thus convergence is more difficult. However, since these are so few values, it is less important about how robust they are.

plot(imp_1_rp)

```

```{r rp_stripplot, include = FALSE}

# we can also check the imputed values against the original values using stripplot(). Each column in each subplot represents a separate iteration. The magenta points represent the imputed data. The values of the variable in questions are along the y axis. We expect the spread of the data to be similar if the imputations were done well. If the data were missing completely at random, then the imputed data should have the same distribution as the original data. In particular, we want to be sure that the imputations are within a plausible range of the data. This is the case for all of our imputed variables, and there does not seem to be cause for alarm from these results.

# this looks good? All reasonable values...

stripplot(imp_1_rp)

stripplot(imp_1_rp, biggestsplit)

```

```{r fs_densityplot, echo = FALSE}

densityplot(imp_fs)
densityplot(x=imp_fs , data= ~ H_citytract_NHW_i + chng5pctblk + 
       chng5pctlatino + chng5pctasian + ideology_fill)

```

```{r fs_imp_plot, include = FALSE}

# ideally, the fits will intertwine and not exhibit any trends at later iterations. This seems to generally be the case. There are some issues with the results for some of the variables with very few missing values, which makes sense as we would expect the mean to be less reliable due to the law of large numbers and thus convergence is more difficult. However, since these are so few values, it is less important about how robust they are.

plot(imp_fs)

```

```{r fs_stripplot, include = FALSE}

# we can also check the imputed values against the original values using stripplot(). Each column in each subplot represents a separate iteration. The magenta points represent the imputed data. The values of the variable in questions are along the y axis. We expect the spread of the data to be similar if the imputations were done well. If the data were missing completely at random, then the imputed data should have the same distribution as the original data. In particular, we want to be sure that the imputations are within a plausible range of the data. This is the case for all of our imputed variables, and there does not seem to be cause for alarm from these results.

# this looks good? All reasonable values...

stripplot(imp_fs, H_citytract_NHW_i)

stripplot(imp_fs, chng5pctblk)

stripplot(imp_fs, chng5pctlatino)

stripplot(imp_fs, chng5pctasian)

stripplot(imp_fs, ideology_fill)

```

Given the promising results of the diagnostic checks, I next proceeded to re-estimate the original model using the multiply imputed datasets, pooling the results to produce final pooled regression coefficients and parameters. The results for the analyses using the racial polarization dataset are presented in tables 1-3.

```{r rp_imputations, include = FALSE}

# Now that we have imputed the missing data, we can re-run the analyses from the
# original paper to see how and if this changes the analysis. We can use the
# with() function from the mice package to fit each of the imputed datasets to
# the model and then pool the results afterwards.

# regression 1: fit multiple imputed datasets

fit_imp_1_rp <- with(imp_1_rp, lmer(formula = biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))

# pool and summarize the analyses

pool_imp_1_rp <- pool(fit_imp_1_rp)
imp_1_rp_sum <- summary(pool_imp_1_rp)

## regression 2 Table 1: fit multiple imputed datasets

#formula = biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2)

fit_imp_2_rp <- with(imp_1_rp, lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))

# pool and summarize the analyses

pool_imp_2_rp <- pool(fit_imp_2_rp)
imp_2_rp_sum <- summary(pool_imp_2_rp)

## regression 3 Table 1 with new data

#formula = biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2)

fit_imp_3_rp <- with(imp_1_rp, lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))

# pool and summarize the analyses

pool_imp_3_rp <- pool(fit_imp_3_rp)
imp_3_rp_sum <- summary(pool_imp_3_rp)

```

The results of the model with the new dataset are slightly different in comparison to the original results from Trounstine (2016). With the imputed data, we now have a total of `r nrow(complete(rp_impute))` observations in our model as compared to the original model, which had only 91 observations. Interestingly, while the sign of the coefficient on the main variable of interest, the Theil's H segregation index, is the same and the standard error has decreased slightly, the result has become statisically insignificant and the 95% confidence interval contains zero. Thus while these results still suggest that segregation may be associated with increased political polarization, they confer a lesser degree of certainty than Trounstine's original analysis. The coefficients for % Black population, % Latino population, and median household income have also switched signs, and all coefficients except the indicator for a biracial election are also statistically insignificant, as was the case in the original analysis. The coefficient on the indicator for a primary election, has also changed from being significant in the original analysis to insignificant here. In general, the standard errors on the coefficients have decreased slightly.

```{r results_printing_rp_impute_regressions_1, results = "asis", echo=FALSE}

# print results of 1st regression

imp_1_rp_sum_table <- as.data.frame(imp_1_rp_sum %>% 
  select(term, estimate, std.error, p.value)) %>%
  head(13)
print(imp_1_rp_sum_table)

stargazer(imp_1_rp_sum_table,
          header = FALSE,
          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Multigroup Segregation Index}")

```

In the second and third regressions, the results are similar. The main coefficient on segregation index has decreased in magnitude, although in these specifications, it remains statistically significant. The other coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian, Black, and Latino have all switched signs. Standard errors have also reduced slightly in these specifications compared to the original analysis in @trounstine_segregation_2016.

```{r results_printing_rp_impute_regressions_2, results = "asis", echo=FALSE}

# print results of 2nd regression

imp_2_rp_sum_table <- as.data.frame(imp_2_rp_sum %>% 
  select(term, estimate, std.error, p.value)) %>%
  head(13)
print(imp_2_rp_sum_table)

stargazer(imp_2_rp_sum_table,
          header = FALSE,
          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Two-Group Segregation Index}")

```

```{r results_printing_rp_impute_regressions_3, results = "asis", echo=FALSE}

# print results of 3rd regression

imp_3_rp_sum_table <- as.data.frame(imp_3_rp_sum %>% 
  select(term, estimate, std.error, p.value)) %>%
  head(13)
print(imp_3_rp_sum_table)

stargazer(imp_3_rp_sum_table,
          header = FALSE,
          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Ideology Control}")
```

For the financial segregation dataset, we similarly fit each of our 5 imputed datasets to the original models from @trounstine_segregation_2016 using this data and then pool the results for each. The pooled results are presented in tables 4-6.

# FS data results

```{r fs_imputed_pooled_regressions, include = FALSE}
# Main Analysis 2: Imputations

## regression 1 Table 2

# fit multiple imputed datasets

fit_imp_felm1 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm1 <- pool(fit_imp_felm1)
imp_felm1_sum <- summary(pool_imp_felm1)

## regression 2 Table 2

# fit multiple imputed datasets

fit_imp_felm2 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm2 <- pool(fit_imp_felm2)
imp_felm2_sum <- summary(pool_imp_felm2)

## Regression 3 Table 2

fit_imp_felm3 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm3 <- pool(fit_imp_felm3)
imp_felm3_sum <- summary(pool_imp_felm3)

```

```{r fs_imputed_data_included_calc, include = FALSE}
# how many observations were included in those 3 analyses?

# basic filter for table for all regressions

# xtreg dgepercap_cpi H_citytract_NHW_i diversityinterp pctblkpopinterp
# pctasianpopinterp pctlatinopopinterp medinc_cpi pctlocalgovworker_100
# pctrentersinterp pctover65 pctcollegegradinterp logpop if totaltracts>1 &
# dgepercap_cpi~=0,fe vce(cluster geo_id2)

fin <- complete(imp_fs) %>%
  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))

# create dge variable used in regression

fin_dge <-fin %>% filter(dgepercap_cpi != 0)

fin_dge_tab <- tibble(
  Variable = "Direct General Expenditure per Capita",
  Obs = nrow(fin_dge),
  Mean = mean(fin_dge$dgepercap_cpi, na.rm = T),
  SD = sd(fin_dge$dgepercap_cpi, na.rm = T),
  Min = min(fin_dge$dgepercap_cpi, na.rm = T),
  Max = max(fin_dge$dgepercap_cpi, na.rm = T)
)

# now we have 73,119 observations compared to 13,742. Calculation:

nrow(fin_dge)

# number of missing seg indexes before imputation: 282334

# number missing now: 222957 -> Calculation:

new_missing <- sum(is.na(complete(imp_fs)$H_citytract_NHW_i))

# calculate number of observations we added to the sample: 59,377

num_added <- 282334 - new_missing

# INTERPRETATION BEFORE AFTER CHANGED The results of the first regression present a stark difference to the results of @trounstine_segregation_2016. Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant. Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant. The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.

```

The results of the first regression present a stark difference to the results of @trounstine_segregation_2016. Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant. Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant. The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.

The results of the first regression indicate that Trounstine's results are robust to the inclusion of the imputed data, which led to the inclusion of an additional 59,377 observations in the analysis. The coefficients, standard errors, and significance levels are essentially unchanged. The same is largely true for the second and third specifications, but the magnitude of the coefficient on the segregation decreases slightly.

```{r results_printing_fs_impute_regressions_1, results = "asis", echo=FALSE}

# print results of 3rd regression

imp_felm1_sum_table <- as.data.frame(imp_felm1_sum %>% 
  select(term, estimate, std.error, p.value))
print(imp_felm1_sum_table)

stargazer(imp_felm1_sum_table,
          header = FALSE,
          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Expenditure per Capita}")
```

```{r results_printing_fs_impute_regressions_2, results = "asis", echo=FALSE}

# print results of 3rd regression

imp_felm2_sum_table <- as.data.frame(imp_felm2_sum %>% 
  select(term, estimate, std.error, p.value))
print(imp_felm2_sum_table)

stargazer(imp_felm1_sum_table,
          header = FALSE,
          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Changing Demographics}")
```

```{r results_printing_fs_impute_regressions_3, results = "asis", echo=FALSE}

# print results of 3rd regression

imp_felm3_sum_table <- as.data.frame(imp_felm3_sum %>% 
  select(term, estimate, std.error, p.value))
print(imp_felm3_sum_table)

stargazer(imp_felm1_sum_table,
          header = FALSE,
          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Ideology Control}")
```

# FS NEW data results

```{r new_fs_imputation_tries, include = FALSE}
# Main Analysis 2: Imputations

## regression 1 Table 2

# fit multiple imputed datasets

fit_imp_felm1 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm1 <- pool(fit_imp_felm1)
imp_felm1_sum <- summary(pool_imp_felm1)

## regression 2 Table 2

# fit multiple imputed datasets

fit_imp_felm2 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm2 <- pool(fit_imp_felm2)
imp_felm2_sum <- summary(pool_imp_felm2)

## Regression 3 Table 2

fit_imp_felm3 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))

# pool the analyses

pool_imp_felm3 <- pool(fit_imp_felm3)
imp_felm3_sum <- summary(pool_imp_felm3)

# INTERPRETATION BEFORE AFTER CHANGED The results of the first regression present a stark difference to the results of @trounstine_segregation_2016. Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant. Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant. The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.

print(imp_felm1_sum)
print(imp_felm2_sum)
print(imp_felm3_sum)

# large amount of data missing across the board in terms of years

gg_miss_var(fin_dge, facet = year, show_pct = TRUE)

# can't really tell anything about the region facet since a lot of obs missing region data

gg_miss_var(fin_imp_extra, facet = region, show_pct = TRUE)

# not necessarily a significant pattern across states either

gg_miss_var(fin_imp_extra, facet = statecode, show_pct = TRUE)

```

# FS NEW AGAIN

```{r}
cities_to_keep <- c("Austin City", "Baltimore City", "Charlotte City", "Chicago City", "Cleveland City", "Columbus City", "Dallas City", "Denver City", "Detroit City", "Houston City", "Indianapolis", "Jacksonville", "Los Angeles City", "Memphis City", "Milwaukee City", "New York City", "Oklahoma City City", "Philadelphia City", "Phoenix City", "San Antonio City", "San Diego City", "San Francisco City", "San Jose City", "Tucson City", "Washington City")

# apply the conditions in Stata regression to the fin_seg dataset

fin_imp_cities <- fin_seg %>%
  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0, cityname %in% cities_to_keep) %>%
  mutate(medinc_cpi = medinc_cpi/1000)

# select the relevant variables to be imputed

fin_imp <- fin_imp %>%
  select(H_citytract_NHW_i, dgepercap_cpi, diversityinterp, pctblkpopinterp, pctasianpopinterp,
         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
         pctcollegegradinterp, logpop, geo_id2, chng5pctblk, chng5pctlatino, chng5pctasian,
         ideology_fill)
```

```{r looking_at_original_data, include = FALSE}

range(fin_seg$totaltractsf, na.rm = T)

# histogram of tracts in full sample:

fin_seg %>%
  ggplot() +
  geom_histogram(aes(x = totaltractsf))

range(fin_seg$logpop, na.rm = T)

# histogram of tracts in full sample:

fin_seg %>%
  ggplot() +
  geom_histogram(aes(x = logpop))

# add back in year, region, and statecode to be able to look at this

fin_imp_old <- fin_seg %>%
  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0) %>%
  mutate(medinc_cpi = medinc_cpi/1000)

fin_imp_extra <- fin_imp %>%
  mutate(year = fin_imp_old$year,
         region = fin_imp_old$region,
         statecode = fin_imp_old$statecode)

# large amount of data missing across the board in terms of years

gg_miss_var(fin_imp_extra, facet = year, show_pct = TRUE)

# can't really tell anything about the region facet since a lot of obs missing region data

gg_miss_var(fin_imp_extra, facet = region, show_pct = TRUE)

# not necessarily a significant pattern across states either

gg_miss_var(fin_imp_extra, facet = statecode, show_pct = TRUE)

```

```{r looking_at_Trounstine_data, include = FALSE}

# basic filter for table for all regressions

# xtreg dgepercap_cpi H_citytract_NHW_i diversityinterp pctblkpopinterp
# pctasianpopinterp pctlatinopopinterp medinc_cpi pctlocalgovworker_100
# pctrentersinterp pctover65 pctcollegegradinterp logpop if totaltracts>1 &
# dgepercap_cpi~=0,fe vce(cluster geo_id2)

fin_trounstine <-fin_seg %>%
  filter(totaltractsf >1 | is.na(totaltractsf)) %>%
  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))

# create dge variable used in regression

fin_dge_trounstine <-fin_trounstine %>% filter(dgepercap_cpi != 0)

range(fin_dge_trounstine$totaltractsf, na.rm = T)

# histogram of tracts in full sample:

fin_dge_trounstine %>%
  ggplot() +
  geom_histogram(aes(x = totaltractsf))

range(fin_dge_trounstine$logpop, na.rm = T)

# histogram of tracts in full sample:

fin_dge_trounstine %>%
  ggplot() +
  geom_histogram(aes(x = logpop))

```

```{r looking_at_imputed_data}

fin_new_imp <- complete(new_imp_fs) %>%
  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))

range(fin_new_imp$logpop, na.rm = T)

# histogram of tracts in full sample:

fin_new_imp %>%
  ggplot() +
  geom_histogram(aes(x = logpop))

```

# Conclusion

Why cities differ in their amount of spending on public goods is an interesting questions that is frequently debated in the literature. @trounstine_segregation_2016 posits that segregation may be an important underlying cause of the underprovsion of public goods. Finding evidence that residential segregation by race increases political partisanship, @trounstine_segregation_2016 argues that residential segregation can increase division and make cooperation amongst competing groups difficult, which results in decreased spending on public goods. The findings of @trounstine_segregation_2016 are particularly important because they suggest that segregation, as defined by many homogeneous neighborhoods within a larger diverse geographical area, is the key factor in disinvestment in public goods. This contradicts previous research which has suggested that levels of diversity were instead most important (see for example @baqir_public_1999 or @hopkins_diversity_2009). While @trounstine_segregation_2016 still represents relatively new reasearch as of 2020, it has yet to be fully vetted by additional research. Furthermore, some research that has been published on the topic since its publication suggests that other factors such as larger inequities in the political system favoring socially powerful groups [@lee_ethnic_2018] or the interaction of income and racial inequality [@an_its_2018] may be more important in explaining public goods provisions.

I first worked to provide a check on the analysis presented in @trounstine_segregation_2016 by attempting to replicate the work in R. I was able to successfully replicate all of the main results from @trounstine_segregation_2016, with the exception of a few of a few marginal analyses of the complex, multi-level models which, to my knowledge, are currently not supported by available R packages. I was, however, able to successfully replicate these results in Stata.

As an additional robustness check I also tested the models in @trounstine_segregation_2016 by re-running them with additional data that I imputed from missing values in the original datasets. The large number of missing values in both of the datasets used in @trounstine_segregation_2016's main analysis created a concern for potential bias in the original results and a lack of representativeness due to the large amount of data excluded from the regression analysis due to missing values. Thus, I used the mice package in R to create multiply imputed datasets, upon which I re-ran the models and pooled the results to generate the final model coefficients and parameters.

The results of the data imputation exercise differed between the two datasets. For the analyses using the smaller, racial polarization dataset, the results from the imputed data resulted in a smaller magnitude of the coefficient on the main independent variable, and also made it statistically insignificant in the main model specification. This suggests that the segregation index may not have as strong of a positive association with political polarization as @trounstine_segregation_2016 suggests. However, for the analyses using the much larger financial segregation dataset, the results of the models using the multiply imputed data largely mirrored the results of @trounstine_segregation_2016, and the coefficients and significance levels were essentially the same between the two, with the standard errors on the model estimates being generally slightly lower for the analyses using the imputed data. This provides strong support for @trounstine_segregation_2016's finding that residential racial segregation is associated with diminshed spending on public goods.

The replication exercise and robustness check using multiply imputed data here provide strong evidence that residential segregation along racial lines does in fact correlate negatively with spending on a variety of public goods. What my analysis calls more into question, is by what mechanism this happens. Using the multiply imputed data, I still found some evidence that segregation may be associated with increased political polarization which @trounstine_segregation_2016 suggests may lead to diminished public goods spending; however, the effect size is much smaller than that found in @trounstine_segregation_2016, and some of the results have become insignificant. It is possible that other mechanisms may be more important in explaining why segregation might be associated with decreased spending on public goods. For example, it could be that there is an important interaction effect between income and segregation, as others have previously suggested, or there could be some other intervening mechanism or a confounding variable that is leading to the negative association between segregation and lower spending on public goods. @trounstine_segregation_2016 has identified an important relationship between segregation and the provision of public goods. However, my analysis suggests that further research is needed to assess the potential mechanisms by which residential segregation by race or even a confounding variable may result in dimished spending. If this mechanism can be better understood, than it will be possible to more effectively understand and address the underprovision of public goods, which may inhibit social mobility and unfairly disadvantage certain groups.

# Appendix

```{r felm, eval = FALSE}

# Main Analysis 2

## regression 1 Table 2

# The following is a fixed effects model regression with clustering around
# geo_id2. It mandates that total census tracts in the city is greater than 1,
# which we want because our measure of evenness of racial spread is constant for
# cities with only one tract by our definition (which requires comparing tracts
# within cities). It also mandates that Direct General Expenditures (DGE) per
# capita, CPI adjusted is not equal to 0, which would be problematic and
# indicate a potential data error. This regression regresses the DGE per capita
# on the the two-group calculation of  Theil's H interpolated. Controls are
# included for diversity and the % populations of Blacks, Asians, and Latinos to
# help identify whether it is actually diversity that drives down spending.These
# demographic controls also help to account for the fact that whites and
# minorities tend to perfer different levels of government spending in general.
# This will help isolate the effects of segregation v. other forms of diversity
# on public spending. Other controls for Median household income, CPI adjusted,
# percent over 65, percent college grads, percent local government workers, log
# population help control for additional factors related to segregation and
# expenditure. Controls for percent renters interpolated and Median household
# income also help to control for the general wealth of cities, which could be a
# potential driver of public spending. Fixed effects for cities are also
# included  so that the author can examine the effect of segregation in the same
# city over  time, which also helps control for many other factors not otherwise
# taken into account (such as city age)

# apply the conditions in Stata regression

fin_seg_sub <- fin_seg %>%
  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0) %>%
  mutate(medinc_cpi = medinc_cpi/1000)

# felm(y~x | factor(fe1) + factor(fe2) | 0 | clustervar)

felm1 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)

## regression 2 Table 2

# This regression is the same as above except instead of using diversity, a new
# control is added for the five year changes in racial group shares. The goal
# here is to see whether or not changes in diversity are a driving factor
# (rather than absolute levels of diversity).

felm2 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)

## Regression 3 Table 2

# Column 3

# As in column 3 of table 1, this regression simply adds in a control for  mean  ideology of city residents from General Social Survey (GSS) to control for the  possibility that ideology that segregated cities are more ideologically  conservative and that the conservative nature of segregated cities is what actually drives the effect.

felm3 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)

```

```{r main_fp_tables, results = "asis", eval = FALSE}

# create main table for table 3

table2 <- stargazer(felm1, felm2, felm3, omit = c("year", "south", "midwest", "west"), 
                    header = FALSE,
                    title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures}")

```

```{r, eval = FALSE}

# Main Analysis 3

## regression 1 Table 3

# Column 1

# The following is a fixed effects model regression with clustering once again around geo_id2. Again, the if statements at the end mandate that total census tracts in the city is greater than 1, which we want because our measure of evenness of racial spread is constant for cities with only one tract by our definition (which requires comparing tracts within cities). They also mandate that the highways per capita, CPI adjsuted with no cap extend (lagged 5 years) is not equal to 0, which would be problematic and indicate a potential data error. The dependent variable here is highways per capita, CPI adjsuted with no cap extend (lagged 5 years) and it is regressed on the two group calculation of Theil's H, interpolated. Controls are added for diversity, percent population of Blacks, Asians, and Latinos, and median household CPI adjusted income as well as for % local government worker hundreds, percent rentership, percent over 65, percent college graduates, and the log of the population. This essentially examines the effect of segregation on the specific public good of highways. As in the previous table's regressions, fixed effects for cities are also included so that the author can examine the effect of segregation in the same city over time, which also helps control for many other factors not otherwise taken into account (such as city age) *

fin_seg_sub <- fin_seg %>%
  filter(totaltractsf > 1 | is.na(totaltractsf), highwayspercapNC_cpi != 0) %>%
  mutate(medinc_cpi = medinc_cpi/1000)

felm2_1 <- felm(highwayspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)

## regression 2 Table 3

# Column 2

# This is the same regression as column 1, but this time the dependent variable
# is police per capita, CPI adjusted with no cap extend. This essentially
# examines the effect of segregation on the specific public good of police per
# capita.

fin_seg_sub <- fin_seg %>%
  filter(totaltractsf > 1 | is.na(totaltractsf), policepercapNC_cpi != 0) %>%
  mutate(medinc_cpi = medinc_cpi/1000)

felm2_2 <- felm( policepercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)

# Column 3
fin_seg_sub <- fin_seg %>%
  filter(totaltractsf > 1 | is.na(totaltractsf), parkspercapNC_cpi != 0) %>%
  mutate(medinc_cpi = medinc_cpi/1000)

# This is again the same regression, but this time the dependent variable is
# parks per capita, CPI adjusted with no cap extend. This essentially examines
# the effect of segregation on the specific public good of parks.

felm2_3 <- felm(parkspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)

# Column 4

# This is again the same regression, but this time the dependent variable is
# sewers per capita, CPI adjusted with no cap extend. This essentially examines
# the effect of segregation on the specific public good of sewers.

fin_seg_sub <- fin_seg %>%
  filter(totaltractsf > 1 | is.na(totaltractsf), sewerspercapNC_cpi != 0) %>%
  mutate(medinc_cpi = medinc_cpi/1000)

felm2_4 <- felm(sewerspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)

# Column 5

# This is again the same regression, but this time the dependent variable is
# Welfare, Health, Housing per capita, CPI adjusted, no cap expend. This
# essentially examines the effect of segregation on the specific public good of
# welfare and housing.

fin_seg_sub <- fin_seg %>%
  filter(totaltractsf > 1 | is.na(totaltractsf), welfhoushealthNC_cpi != 0) %>%
  mutate(medinc_cpi = medinc_cpi/1000)

felm2_5 <- felm(welfhoushealthNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)

# Column 6

# This is again the same regression, but this time the dependent variable is own
# source of general revenue per capita, CPI adjusted. This essentially examines
# the effect of segregation on the specific public good of own source revenue.

fin_seg_sub <- fin_seg %>%
  filter(totaltractsf > 1 | is.na(totaltractsf), genrevownpercap_cpi != 0) %>%
  mutate(medinc_cpi = medinc_cpi/1000)

felm2_6 <- felm(genrevownpercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)

```

```{r results = "asis", eval = FALSE}
table3a <- stargazer(felm2_1, felm2_2, felm2_3, 
          omit = c("year", "south", "midwest", "west"), 
          header = FALSE,
          title = "\\textbf{Effect of Segregation on Public Goods A}")

table3b <- stargazer(felm2_4, felm2_5, felm2_6, 
          omit = c("year", "south", "midwest", "west"), 
          header = FALSE,
          title = "\\textbf{Effect of Segregation on Public Goods B}")

#star_sidewaystable(table3)
```

```{r iv_regs, eval = FALSE}

## regression 1 Table 5

# Top Row

# Column 1

# This is an instrumental variable regression with DGE per capita, adjusted by the CPI, as the dependent variable and total number of waterways as the instrumental variable for segregation. The instrument includes the log of the population in the first stage because the number of waterways is positively correlated to population and population is positively correlated with segregation. The control variables are the same as those in the regressions for Table 2 except for 2 changes: since the number of waterways does not change, there is no need for city fixed effects. Instead, we include fixed effects for the region and year. A lagged version of the dependent variable (dgepercap_cpilag) is added to the regressions to account for the high correlation between  observations for the same city over time and because changes in local budgets typically are incremental (NOTE: why exactly do we do this/why does it help/why not do it in the non-intstrumental regressions?).

fin_seg_1 <- fin_seg %>%
  filter(dgepercap_cpi != 0) %>%
  mutate(medincinterp = medincinterp/1000)

glimpse(fin_seg_1$medincinterp)

# good explanation: http://eclr.humanities.manchester.ac.uk/index.php/IV_in_R

# iv = ivreg(second stage regression | instrument1 + instrument2 )

ivreg1 <- ivreg(dgepercap_cpi ~ H_citytract_NHW_i + dgepercap_cpilag + diversityinterp +
                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
                  pctcollegegradinterp + northeast + south + midwest + y5 + 
                  y6 + y7 + y8 + y9 | total_rivs_all + 
                  logpop + dgepercap_cpilag + diversityinterp + pctblkpopinterp + 
                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
                  pctcollegegradinterp + northeast + south + 
                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_1)

# Column 2

# this is the same regression as for column 1 but now we use the dependent variable highwayspercapNC_cpi to assess the effect of the instrumental  variable on highways per capita *

fin_seg_2 <- fin_seg %>%
  filter(highwayspercapNC_cpi != 0) %>%
  mutate(medincinterp = medincinterp/1000)

ivreg2 <- ivreg(highwayspercapNC_cpi ~ H_citytract_NHW_i + highwayspercapNC_cpilag + diversityinterp +
                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
                  pctcollegegradinterp + northeast + south + midwest + y5 + 
                  y6 + y7 + y8 + y9 | total_rivs_all + 
                  logpop + highwayspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
                  pctcollegegradinterp + northeast + south + 
                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_2)

# Column 3

# this is the same regression as for column 1 but now we use the dependent variable policepercapNC_cpi to assess the effect of the instrumental variable on police per capita

fin_seg_3 <- fin_seg %>%
  filter(policepercapNC_cpi != 0) %>%
  mutate(medincinterp = medincinterp/1000)

ivreg3 <- ivreg(policepercapNC_cpi ~ H_citytract_NHW_i + policepercapNC_cpilag + diversityinterp +
                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
                  pctcollegegradinterp + northeast + south + midwest + y5 + 
                  y6 + y7 + y8 + y9 | total_rivs_all + 
                  logpop + policepercapNC_cpilag + diversityinterp + pctblkpopinterp + 
                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
                  pctcollegegradinterp + northeast + south + 
                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_3)

# Column 4 this is the same regression as for column 1 but now we use the
# dependent variable parkspercapNC_cpi to assess the effect of the instrumental
# variable on parks per capita

fin_seg_4 <- fin_seg %>%
  filter(parkspercapNC_cpi != 0) %>%
  mutate(medincinterp = medincinterp/1000)

ivreg4 <- ivreg(parkspercapNC_cpi ~ H_citytract_NHW_i + parkspercapNC_cpilag + diversityinterp +
                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
                  pctcollegegradinterp + northeast + south + midwest + y5 + 
                  y6 + y7 + y8 + y9 | total_rivs_all + 
                  logpop + parkspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
                  pctcollegegradinterp + northeast + south + 
                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_4)

# Bottom Row

# Column 1

# this is the same regression as for column 1 but now we use the dependent
# variable sewerspercapNC_cpi to assess the effect of the instrumental variable
# on sewers per capita

fin_seg_5 <- fin_seg %>%
  filter(sewerspercapNC_cpi != 0) %>%
  mutate(medincinterp = medincinterp/1000)

ivreg5 <- ivreg(sewerspercapNC_cpi ~ H_citytract_NHW_i + sewerspercapNC_cpilag + diversityinterp +
                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
                  pctcollegegradinterp + northeast + south + midwest + y5 + 
                  y6 + y7 + y8 + y9 | total_rivs_all + 
                  logpop + sewerspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
                  pctcollegegradinterp + northeast + south + 
                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_5)

# Column 3

# this is the same regression as for column 1 but now we use the dependent variable genrevownpercap_cpi to assess the effect of the instrumental variable on own source revenue per capita

fin_seg_6 <- fin_seg %>%
  filter(genrevownpercap_cpi != 0) %>%
  mutate(medincinterp = medincinterp/1000)

ivreg6 <- ivreg(genrevownpercap_cpi ~ H_citytract_NHW_i + genrevownpercap_cpilag + diversityinterp +
                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
                  pctcollegegradinterp + northeast + south + midwest + y5 + 
                  y6 + y7 + y8 + y9 | total_rivs_all + 
                  logpop + genrevownpercap_cpilag + diversityinterp + pctblkpopinterp + 
                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
                  pctcollegegradinterp + northeast + south + 
                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_6)

# Column 2

# this is the same regression as for column 1 but now we use the dependent
# variable welfhoushealthNC_cpi to assess the effect of the instrumental
# variable on welfare per capita

fin_seg_7 <- fin_seg %>%
  filter(welfhoushealthNC_cpi != 0) %>%
  mutate(medincinterp = medincinterp/1000)

ivreg7 <- ivreg(welfhoushealthNC_cpi ~ H_citytract_NHW_i + welfhoushealthNC_cpilag  + diversityinterp +
                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
                  pctcollegegradinterp + northeast + south + midwest + y5 + 
                  y6 + y7 + y8 + y9 | total_rivs_all + 
                  logpop + welfhoushealthNC_cpilag + diversityinterp + pctblkpopinterp + 
                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
                  pctcollegegradinterp + northeast + south + 
                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_7)

summary(ivreg7)

```

# Table 5

```{r results = "asis", echo = FALSE}

table5a <- stargazer(ivreg1, ivreg2, ivreg3, ivreg4,
          omit = c("y5", "y6", "y7", "y8", "y9", "northeast", "south", "midwest", "west"), 
          header = FALSE,
          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach A}")

table5b <- stargazer(ivreg5, ivreg6, ivreg7,
          omit = c("y5", "y6", "y7", "y8", "y9", "northeast","south", "midwest", "west"), 
          header = FALSE,
          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach B}")
```

```{r import_data, include = FALSE}

# make a list of the cities included in the analysis to filter out from the main
# dataset as specified in the table

cities_to_keep <- c("Austin City", "Baltimore City", "Charlotte City", "Chicago City", "Cleveland City", "Columbus City", "Dallas City", "Denver City", "Detroit City", "Houston City", "Indianapolis", "Jacksonville", "Los Angeles City", "Memphis City", "Milwaukee City", "New York City", "Oklahoma City City", "Philadelphia City", "Phoenix City", "San Antonio City", "San Diego City", "San Francisco City", "San Jose City", "Tucson City", "Washington City")

# based on some investigation, the missing additional filter needed to replicate
# appendix tables 1 and 2 is that biggest split cannot be NA. This was
# discovered in attempting to create table 2. The number of elections with the
# largest divides between each racial group were the same as in the table when
# all results were included and only the summary stats differed in both tables
# using the city and winner subset. So, I tried excluding all entries for which
# biggestsplit was NA, and found that the resulting subset matched the
# statistics in both tables.

# create a subset of the data with the relevant cities where there is a winner
# and the biggestsplit is not NA

rp_sub <- rp %>%
  filter(winner == 1) %>%
  filter(cityname %in% cities_to_keep) %>%
  filter(!(is.na(biggestsplit)))

# select the relevant variables for the table

rp_sub_a1 <- rp_sub %>%
  select(biggestsplit, H_citytract_multi_i, H_citytract_NHW_i, diversityinterp, 
         pctasianpopinterp, pctblkpopinterp, pctlatinopopinterp, medincinterp, 
         pctrentersinterp, pctcollegegradinterp, biracial, nonpartisan, primary, 
         logpop, whiteideology_fill2) %>%
  mutate(medincinterp = medincinterp/1000)

# why are the exact variables H_citytract_NHW and whiteideology_fill not in the
# data? Data variable names author uses and ones in the data don't exactly
# match, but replication results are the same.

```

```{r table_a1, results="asis", echo = FALSE}

# create a stargazer summary table for the relevant statistics of the racial
# polarization data. I couldn't figure out how to change the text of the
# statistic names at the top of the datat table. I also couldn't figure out how
# to only not display additional digits for the income variable. May be
# better to switch to gt for final version?

stargazer(as.data.frame(rp_sub_a1),
          omit.summary.stat = c("p25", "p75"),
          title = "\\textbf{TABLE A1 Summary Statistics: Racial Polarization Data}",
          column.labels = c("\\textbf{Variable}","\\textbf{Obs}", "\\textbf{Mean}", "\\textbf{Std. Dev.}", "\\textbf{Min}", "\\textbf{Max}"),
          covariate.labels = c("Largest Racial Divide","\\emph{H} Index: Multigroup", "\\emph{H} Index: Two-Group", "Diversity", "\\% Asian", "\\% Black", "\\% Latino", "Median HH Income", "\\% Renters", "\\% College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology"),
          no.space = TRUE,
          header = FALSE)

```

```{r table_a2_data_manipulation, include = FALSE}

# initialize variables to indicate if a racial divide had the biggest divide in
# the election

rp_sub$biggest_split_bw <- NA
rp_sub$biggest_split_lw <- NA
rp_sub$biggest_split_bl <- NA

# change the NA value to 1 if the relevant divide was the biggest in the election

rp_sub$biggest_split_bw[rp_sub$biggestsplit_gr == 1] <- 1
rp_sub$biggest_split_lw[rp_sub$biggestsplit_gr == 2] <- 1
rp_sub$biggest_split_bl[rp_sub$biggestsplit_gr == 3] <- 1

# generate the dataset of summary statistics to replicate the second appendix
# table. Group by city name and then summarize the mean H indexes. Sum the
# number of biggest splits by racial divide for each city

rp_sub_2 <- rp_sub %>%
  group_by(cityname) %>%
  summarise(mean_multi_H = mean(H_citytract_multi_i),
            mean_multi_two_group = mean(H_citytract_NHW_i),
            sum_bw = sum(biggest_split_bw, na.rm = T),
            sum_lw = sum(biggest_split_lw, na.rm = T),
            sum_bl = sum(biggest_split_bl, na.rm = T))
```

```{r table_a2, echo = FALSE}

# create appendix table A2 to present the summary statistics for cities included
# in racial polarization data. Efforts to make columns narrower were
# unsuccessful, so some of the labels in the column names were changed to make
# the table fit. I also couldn't get the title to print out without including a
# non-Null subtitle.

city_names <- c("Austin, TX", "Baltimore, MD", "Charlotte, NC", "Chicago, IL", "Cleveland, OH", "Columbus, OH", "Dallas, TX", "Denver, CO", "Detroit, MI", "Houston, TX", "Indianapolis, IN", "Jacksonville, FL", "Los Angeles, CA", "Memphis, TN", "Milwaukee, WI", "New York, NY", "Oklahoma, OK", "Philadelphia, PA", "Phoenix, AZ", "San Antonio, TX","San Diego, CA", "San Francisco, CA", "San Jose, CA", "Tucson, AZ", "Washington, DC")

rp_sub_2$cityname <- city_names

gt(rp_sub_2) %>%
  tab_header(title = md("**TABLE A2 Cities Included in Racial Polarization Data**"),
             subtitle = "Replication") %>%
  tab_spanner(
      label = md("**Segregation: Mean *H* Index**"),
      columns = vars(mean_multi_H, mean_multi_two_group)) %>%
  tab_spanner(
      label = md("**Largest Racial Divide, Number of Elections**"),
      columns = vars(sum_bw, sum_lw, sum_bl)) %>%
  fmt_number(columns = vars(mean_multi_H, mean_multi_two_group),
             decimals = 3) %>%
  cols_label(cityname = "City Name",
             mean_multi_H = md("Multigroup"),
             mean_multi_two_group = md("Two-Group"),
             sum_bw = "Black/White",
             sum_lw = "Latino/White",
             sum_bl = "Black/Latino") %>%
  cols_width(
    vars(cityname) ~ px(10),
    TRUE ~ px(20)
  ) %>%
  cols_align(
    columns = vars(cityname),
    align = "left"
  ) %>%
  tab_options(
    table.margin.left = px(5), 
    table.margin.right = px(5),
    data_row.padding = px(1),
    table.width = pct(90)
  )

```

```{r include = FALSE, include = FALSE}

# basic filter for table for all regressions

# xtreg dgepercap_cpi H_citytract_NHW_i diversityinterp pctblkpopinterp
# pctasianpopinterp pctlatinopopinterp medinc_cpi pctlocalgovworker_100
# pctrentersinterp pctover65 pctcollegegradinterp logpop if totaltracts>1 &
# dgepercap_cpi~=0,fe vce(cluster geo_id2)

fin <-fin_seg %>%
  filter(totaltractsf >1 | is.na(totaltractsf)) %>%
  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))

# create dge variable used in regression

fin_dge <-fin %>% filter(dgepercap_cpi != 0)

fin_dge_tab <- tibble(
  Variable = "Direct General Expenditure per Capita",
  Obs = nrow(fin_dge),
  Mean = mean(fin_dge$dgepercap_cpi, na.rm = T),
  SD = sd(fin_dge$dgepercap_cpi, na.rm = T),
  Min = min(fin_dge$dgepercap_cpi, na.rm = T),
  Max = max(fin_dge$dgepercap_cpi, na.rm = T)
)

print(fin_dge_tab)

# creat summary for highways
fin_hw <-fin %>% filter(highwayspercapNC_cpi != 0)

fin_hw_tab <- tibble(
  Variable = "Highways per Capita",
  Obs = nrow(fin_hw),
  Mean = mean(fin_hw$highwayspercapNC_cpi, na.rm = T),
  SD = sd(fin_hw$highwayspercapNC_cpi, na.rm = T),
  Min = min(fin_hw$highwayspercapNC_cpi, na.rm = T),
  Max = max(fin_hw$highwayspercapNC_cpi, na.rm = T)
)

print(fin_hw_tab)

a3_final <- full_join(fin_dge_tab, fin_hw_tab)

# parks

fin_park <-fin %>% filter(parkspercapNC_cpi != 0)

fin_park_tab <- tibble(
  Variable = "Parks per Capita",
  Obs = nrow(fin_park),
  Mean = mean(fin_park$parkspercapNC_cpi, na.rm = T),
  SD = sd(fin_park$parkspercapNC_cpi, na.rm = T),
  Min = min(fin_park$parkspercapNC_cpi, na.rm = T),
  Max = max(fin_park$parkspercapNC_cpi, na.rm = T)
)

print(fin_park_tab)

a3_final <- full_join(a3_final, fin_park_tab)

# police

fin_police <-fin %>% filter(policepercapNC_cpi != 0)

fin_police_tab <- tibble(
  Variable = "Police per Capita",
  Obs = nrow(fin_police),
  Mean = mean(fin_police$policepercapNC_cpi, na.rm = T),
  SD = sd(fin_police$policepercapNC_cpi, na.rm = T),
  Min = min(fin_police$policepercapNC_cpi, na.rm = T),
  Max = max(fin_police$policepercapNC_cpi, na.rm = T)
)

print(fin_police_tab)

a3_final <- full_join(a3_final, fin_police_tab)

# sewers

fin_sew <-fin %>% filter(sewerspercapNC_cpi != 0)

fin_sew_tab <- tibble(
  Variable = "Sewers per Capita",
  Obs = nrow(fin_sew),
  Mean = mean(fin_sew$sewerspercapNC_cpi, na.rm = T),
  SD = sd(fin_sew$sewerspercapNC_cpi, na.rm = T),
  Min = min(fin_sew$sewerspercapNC_cpi, na.rm = T),
  Max = max(fin_sew$sewerspercapNC_cpi, na.rm = T)
)

print(fin_sew_tab)

a3_final <- full_join(a3_final, fin_sew_tab)

# welfare

fin_welfare <-fin %>% filter(welfhoushealthNC_cpi != 0)

fin_welfare_tab <- tibble(
  Variable = "Welfare, Health, and Housing per Capita",
  Obs = nrow(fin_welfare),
  Mean = mean(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
  SD = sd(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
  Min = min(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
  Max = max(fin_welfare$welfhoushealthNC_cpi, na.rm = T)
)

print(fin_welfare_tab)

a3_final <- full_join(a3_final, fin_welfare_tab)

# own source revenue

fin_own <-fin %>% filter(genrevownpercap_cpi != 0)

fin_own_tab <- tibble(
  Variable = "Own Source Revenue per Capita",
  Obs = nrow(fin_own),
  Mean = mean(fin_own$genrevownpercap_cpi, na.rm = T),
  SD = sd(fin_own$genrevownpercap_cpi, na.rm = T),
  Min = min(fin_own$genrevownpercap_cpi, na.rm = T),
  Max = max(fin_own$genrevownpercap_cpi, na.rm = T)
)

print(fin_own_tab)

a3_final <- full_join(a3_final, fin_own_tab)

# two group H

fin_h <-fin %>% filter(dgepercap_cpi != 0)

fin_h_tab <- tibble(
  Variable = "Two-Group H Index",
  Obs = nrow(fin_h),
  Mean = mean(fin_h$H_citytract_NHW_i, na.rm = T),
  SD = sd(fin_h$H_citytract_NHW_i, na.rm = T),
  Min = min(fin_h$H_citytract_NHW_i, na.rm = T),
  Max = max(fin_h$H_citytract_NHW_i, na.rm = T)
)

print(fin_h_tab)

a3_final <- full_join(a3_final, fin_h_tab)

# Diversity

fin_div <-fin %>% filter(dgepercap_cpi != 0)

fin_div_tab <- tibble(
  Variable = "Diversity",
  Obs = nrow(fin_div),
  Mean = mean(fin_div$diversityinterp, na.rm = T),
  SD = sd(fin_div$diversityinterp, na.rm = T),
  Min = min(fin_div$diversityinterp, na.rm = T),
  Max = max(fin_div$diversityinterp, na.rm = T)
)

print(fin_div_tab)

a3_final <- full_join(a3_final, fin_div_tab)

# % black

fin_pctblk <-fin %>% filter(dgepercap_cpi != 0)

fin_pctblk_tab <- tibble(
  Variable = "%  Black",
  Obs = nrow(fin_pctblk),
  Mean = mean(fin_pctblk$pctblkpopinterp, na.rm = T),
  SD = sd(fin_pctblk$pctblkpopinterp, na.rm = T),
  Min = min(fin_pctblk$pctblkpopinterp, na.rm = T),
  Max = max(fin_pctblk$pctblkpopinterp, na.rm = T)
)

print(fin_pctblk_tab)

a3_final <- full_join(a3_final, fin_pctblk_tab)

# % asian

fin_pcta <-fin %>% filter(dgepercap_cpi != 0)

fin_pcta_tab <- tibble(
  Variable = "%  Asian",
  Obs = nrow(fin_pcta),
  Mean = mean(fin_pcta$pctasianpopinterp, na.rm = T),
  SD = sd(fin_pcta$pctasianpopinterp, na.rm = T),
  Min = min(fin_pcta$pctasianpopinterp, na.rm = T),
  Max = max(fin_pcta$pctasianpopinterp, na.rm = T)
)

print(fin_pcta_tab)

a3_final <- full_join(a3_final, fin_pcta_tab)

# % latino

fin_pctla <-fin %>% filter(dgepercap_cpi != 0)

fin_pctla_tab <- tibble(
  Variable = "%  Latino",
  Obs = nrow(fin_pctla),
  Mean = mean(fin_pctla$pctlatinopopinterp, na.rm = T),
  SD = sd(fin_pctla$pctlatinopopinterp, na.rm = T),
  Min = min(fin_pctla$pctlatinopopinterp, na.rm = T),
  Max = max(fin_pctla$pctlatinopopinterp, na.rm = T)
)

a3_final <- full_join(a3_final, fin_pctla_tab)

# 5y black

fin_chng5pctblk <-fin %>% filter(dgepercap_cpi != 0) %>%
  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))

nrow(fin_chng5pctblk)

fin_chng5pctblk_tab <- tibble(
  Variable = "5Y Change, % Black",
  Obs = nrow(fin_chng5pctblk),
  Mean = mean(fin_chng5pctblk$chng5pctblk, na.rm = T),
  SD = sd(fin_chng5pctblk$chng5pctblk, na.rm = T),
  Min = min(fin_chng5pctblk$chng5pctblk, na.rm = T),
  Max = max(fin_chng5pctblk$chng5pctblk, na.rm = T)
)

print(fin_chng5pctblk_tab)

a3_final <- full_join(a3_final, fin_chng5pctblk_tab)

# 5y latino

fin_chng5pctlatino <-fin %>% filter(dgepercap_cpi != 0) %>%
  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))

fin_chng5pctlatino_tab <- tibble(
  Variable = "5Y Change, % Latino",
  Obs = nrow(fin_chng5pctlatino),
  Mean = mean(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
  SD = sd(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
  Min = min(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
  Max = max(fin_chng5pctlatino$chng5pctlatino, na.rm = T)
)

a3_final <- full_join(a3_final, fin_chng5pctlatino_tab)

# 5y asian

fin_chng5pctasian <-fin %>% filter(dgepercap_cpi != 0) %>%
  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))

fin_chng5pctasian_tab <- tibble(
  Variable = "5Y Change, % Asian",
  Obs = nrow(fin_chng5pctasian),
  Mean = mean(fin_chng5pctasian$chng5pctasian, na.rm = T),
  SD = sd(fin_chng5pctasian$chng5pctasian, na.rm = T),
  Min = min(fin_chng5pctasian$chng5pctasian, na.rm = T),
  Max = max(fin_chng5pctasian$chng5pctasian, na.rm = T)
)

a3_final <- full_join(a3_final, fin_chng5pctasian_tab)

# median income

fin_med <-fin %>% filter(dgepercap_cpi != 0)

fin_med_tab <- tibble(
  Variable = "Median Income",
  Obs = nrow(fin_med),
  Mean = mean(fin_med$medinc_cpi, na.rm = T),
  SD = sd(fin_med$medinc_cpi, na.rm = T),
  Min = min(fin_med$medinc_cpi, na.rm = T),
  Max = max(fin_med$medinc_cpi, na.rm = T)
)

a3_final <- full_join(a3_final, fin_med_tab)

# % local gov. employees

fin_pctlocal <-fin %>% filter(dgepercap_cpi != 0)

fin_pctlocal_tab <- tibble(
  Variable = "% Local Gov. Employees",
  Obs = nrow(fin_pctlocal),
  Mean = mean(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
  SD = sd(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
  Min = min(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
  Max = max(fin_pctlocal$pctlocalgovworker_100, na.rm = T)
)

a3_final <- full_join(a3_final, fin_pctlocal_tab)

# % renters

fin_rent <-fin %>% filter(dgepercap_cpi != 0)

fin_rent_tab <- tibble(
  Variable = "% Renters",
  Obs = nrow(fin_rent),
  Mean = mean(fin_rent$pctrentersinterp, na.rm = T),
  SD = sd(fin_rent$pctrentersinterp, na.rm = T),
  Min = min(fin_rent$pctrentersinterp, na.rm = T),
  Max = max(fin_rent$pctrentersinterp, na.rm = T)
)

a3_final <- full_join(a3_final, fin_rent_tab)

# % over 65

fin_65 <-fin %>% filter(dgepercap_cpi != 0)

fin_65_tab <- tibble(
  Variable = "% Over 65",
  Obs = nrow(fin_65),
  Mean = mean(fin_65$pctover65, na.rm = T),
  SD = sd(fin_65$pctover65, na.rm = T),
  Min = min(fin_65$pctover65, na.rm = T),
  Max = max(fin_65$pctover65, na.rm = T)
)

a3_final <- full_join(a3_final, fin_65_tab)

# % college degree

fin_college <-fin %>% filter(dgepercap_cpi != 0)

fin_college_tab <- tibble(
  Variable = "% College Degree",
  Obs = nrow(fin_college),
  Mean = mean(fin_college$pctcollegegradinterp, na.rm = T),
  SD = sd(fin_college$pctcollegegradinterp, na.rm = T),
  Min = min(fin_college$pctcollegegradinterp, na.rm = T),
  Max = max(fin_college$pctcollegegradinterp, na.rm = T)
)

a3_final <- full_join(a3_final, fin_college_tab)

# pop logged

fin_logpop <-fin %>% filter(dgepercap_cpi != 0)

fin_logpop_tab <- tibble(
  Variable = "Population (logged)",
  Obs = nrow(fin_logpop),
  Mean = mean(fin_logpop$logpop, na.rm = T),
  SD = sd(fin_logpop$logpop, na.rm = T),
  Min = min(fin_logpop$logpop, na.rm = T),
  Max = max(fin_logpop$logpop, na.rm = T)
)

a3_final <- full_join(a3_final, fin_logpop_tab)

# city ideology

fin_ideo <-fin %>% filter(dgepercap_cpi != 0) %>%
  filter(!(is.na(ideology_fill)))

nrow(fin_ideo)

fin_ideo_tab <- tibble(
  Variable = "City Ideology",
  Obs = nrow(fin_ideo),
  Mean = mean(fin_ideo$ideology_fill, na.rm = T),
  SD = sd(fin_ideo$ideology_fill, na.rm = T),
  Min = min(fin_ideo$ideology_fill, na.rm = T),
  Max = max(fin_ideo$ideology_fill, na.rm = T)
)

a3_final <- full_join(a3_final, fin_ideo_tab)

# population
fin_population <-fin %>% filter(dgepercap_cpi != 0)

fin_population_tab <- tibble(
  Variable = "Population",
  Obs = nrow(fin_population),
  Mean = mean(fin_population$population, na.rm = T),
  SD = sd(fin_population$population, na.rm = T),
  Min = min(fin_population$population, na.rm = T),
  Max = max(fin_population$population, na.rm = T)
)

a3_final <- full_join(a3_final, fin_population_tab)

```

```{r, echo = FALSE}
gt(a3_final) %>%
    tab_header(title = md("**TABLE A3 Summary Statistics: Census of Government Finance and Population**"),
             subtitle = "") %>%
    fmt_number(columns = vars(Mean, SD, Min, Max),
             decimals = 3) %>%
    cols_label(Obs = md("**Obs**"),
               Mean = md("**Mean**"),
               SD = md("**SD**"),
               Min = md("**Min**"),
               Max = md("**Max**")
                        ) 
```

# Bibliography

### 2020-04-28 Extension.Rmd
initial commit with new repo

---
title: "Extension"
author: "Maria Burzillo"
date: "4/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center")
knitr::write_bib(c("knitr", "stringr"), "bib.bib", width = 60)
library(haven)
library(gtable)
library(stargazer)
library(tidyverse)
library(gt)
library(gtsummary)
library(knitr)
library(stargazer)
library(lme4)
library(margins)
library(reprex)
library(plm)
library(devtools)
library(lfe)
library(Statamarkdown)
library(readxl)
library(starpolishr)
library(AER)
library(readxl)
library(naniar)
library(mice)
```

```{r data_imports, include = FALSE}

# import both datasets

rp <- read_dta("racial_polarization_winners.dta")
fin_seg<- read_dta("fin_seg.dta")

```

# Main Analysis

```{r include = FALSE}

rp_vars <- c("winner", "medincinterp",
             "biggestsplit", "H_citytract_multi_i", "diversityinterp",
             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
             "primary", "logpop", "year", "south", "midwest", "west", "geo_id2",
             "H_citytract_NHW_i", "whiteideology_fill2"
             )

rp_impute <- rp %>%
  select("winner", "medincinterp",
             "biggestsplit", "H_citytract_multi_i", "diversityinterp",
             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
             "primary", "logpop", "year", "south", "midwest", "west", "geo_id2",
             "H_citytract_NHW_i", "whiteideology_fill2") %>%
  filter(winner == 1)%>%
  mutate(medincinterp = medincinterp/1000,
         year.f = as.factor(year))

nrow(rp_impute)

```

```{r exploring_missing_values, echo = FALSE}

miss_var_summary(rp_impute)

gg_miss_var(rp_impute)

gg_miss_var(rp_impute, show_pct = TRUE)

```

```{r imputation_for_rp_dataset}

imp_1_rp <- mice(rp_impute, maxit = 0)

pred <- imp_1_rp$predictorMatrix

methods_1 <- imp_1_rp$method

methods_1["medincinterp"] <- "cart"
methods_1["biggestsplit"] <- "cart"

imp_1_rp <- mice(rp_impute, maxit = 1, method = methods_1)

# multiple imputations using the cart method

view(rp_impute)

imp_1_rp <- mice(rp_impute, method = "cart", maxit = 3)

write.csv(complete(imp_1_rp), "imp_1_rp.csv")

gg_miss_var(complete(imp_1_rp), show_pct = TRUE)

```

```{r, results="asis", echo = FALSE}
# fit multiple imputed datasets

fit_imp_1_rp <- with(imp_1_rp, lmer(biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))

# pool the analyses

pool_imp_1_rp <- pool(fit_imp_1_rp)
imp_1_rp_sum <- summary(pool_imp_1_rp)

# look at the table
gt(imp_1_rp_sum)

stargazer(imp_1_rp_sum)

imp_1_rp$method

```

```{r}
miss_var_summary(fin_seg)

fin_seg$citypop

gg_miss_var(rp_impute)

gg_miss_var(rp_impute, show_pct = TRUE, facet = year)
```

```{r}

# basic filter for table for all regressions

fin_imp_1 <-fin_seg %>%
  select(totaltractsf,dgepercap_cpi, H_citytract_NHW_i, diversityinterp,
         pctblkpopinterp, pctasianpopinterp, pctlatinopopinterp, medinc_cpi,
         pctlocalgovworker_100, pctrentersinterp, pctover65,
         pctcollegegradinterp, logpop, highwayspercapNC_cpi, parkspercapNC_cpi,
         policepercapNC_cpi, sewerspercapNC_cpi, welfhoushealthNC_cpi,
         genrevownpercap_cpi, H_citytract_multi_i, diversityinterp, pctblkpopinterp, pctasianpopinterp, pctlatinopopinterp, chng5pctblk, chng5pctlatino, chng5pctasian,medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65, pctcollegegradinterp, logpop, ideology_fill, population, geo_id2)

miss_var_summary(fin_imp_1)

#felm1 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)

fin_imp <- fin_imp_1 %>%
  select(H_citytract_NHW_i, dgepercap_cpi, diversityinterp, pctblkpopinterp, pctasianpopinterp,
         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
         pctcollegegradinterp, logpop, geo_id2)

miss_var_summary(fin_imp)

```

```{r}
ini <- mice(fin_imp, maxit=0, print=F)

meth <- ini$method

meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""

meth[c("H_citytract_NHW_i")] = "cart"

imp_1_fs <- mice(fin_imp, method = meth, maxit = 1)

miss_var_summary(complete(imp_1_fs,3))

```

```{r}
fin_seg_sub <- fin_seg %>%
  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0 | is.na(dgepercap_cpi)) %>%
  mutate(medinc_cpi = medinc_cpi/1000)

fin_imp <- fin_seg_sub %>%
  select(H_citytract_NHW_i, dgepercap_cpi, diversityinterp, pctblkpopinterp, pctasianpopinterp, pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp,  pctover65, pctcollegegradinterp, logpop, geo_id2)

#felm1 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)

ini <- mice(fin_imp, maxit=0, print=F)

pred_matrix <- ini$pred

meth <- ini$method

others <- c("medinc_cpi")

meth[c("pctasianpopinterp", "pctlatinopopinterp", "pctblkpopinterp","pctlocalgovworker_100", "pctover65", "pctcollegegradinterp", 
                    "logpop")]=""

meth[c("dgepercap_cpi", "H_citytract_NHW_i", "medinc_cpi", "pctrentersinterp", "diversityinterp")] = "cart"

#meth[c("medinc_cpi")] = "pmm"

#new_pred_matrix <- pred_matrix[,1:2]

try2 <- mice(fin_imp, maxit=1, method = meth)

pred_matrix[,]

view(complete(try2))

nrow(complete(try2))

sum(is.na(complete(try2)$dgepercap_cpi))
sum(is.na(fin_imp$dgepercap_cpi))

miss_var_summary(fin_imp)

miss_var_summary(complete(try2))

felm1_imp <- with(try2, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub))

pool_felm1_imp<- pool(felm1_imp)
felm1_imp_sum <- summary(pool_felm1_imp)

print(felm1_imp_sum, digits = 3)
```

```{r}
ini <- mice(fin_imp, maxit=0, print=F)

pred_matrix <- ini$pred

meth <- ini$method

try3 <- mice(fin_imp, maxit=1, method = "cart")

```

```{r}

ini <- mice(fin_imp, maxit=0, print=F)

pred_matrix <- ini$pred

meth <- ini$method

meth[c("pctlocalgovworker_100", "pctover65", "pctcollegegradinterp", 
                    "logpop")]=""

meth[c("pctasianpopinterp", "pctlatinopopinterp", "pctblkpopinterp","dgepercap_cpi", "H_citytract_NHW_i", "medinc_cpi", "pctrentersinterp", "diversityinterp")] = "cart"

try4 <- mice(fin_imp, maxit=1, method = meth)

```

```{r}

ini <- mice(fin_imp, maxit=0, print=F)

pred_matrix <- ini$pred

meth <- ini$method

meth[c("pctcollegegradinterp", 
                    "logpop")]=""

meth[c("pctasianpopinterp", "pctlatinopopinterp", "pctblkpopinterp","dgepercap_cpi", "H_citytract_NHW_i", "medinc_cpi", "pctrentersinterp", "diversityinterp", "pctlocalgovworker_100", "pctover65")] = "cart"

try5 <- mice(fin_imp, maxit=1, method = meth)

```

```{r}

ini <- mice(fin_imp, maxit=0, print=F)

pred_matrix <- ini$pred

meth <- ini$method

meth[c("logpop")]=""

meth[c("pctasianpopinterp", "pctlatinopopinterp", "pctblkpopinterp","dgepercap_cpi", "H_citytract_NHW_i", "medinc_cpi", "pctrentersinterp", "diversityinterp", "pctlocalgovworker_100", "pctover65", "pctcollegegradinterp")] = "cart"

try5 <- mice(fin_imp, maxit=1)

try7 <- mice(fin_imp, maxit = 1, method = "cart")

write.csv(try6, "try6_1_imp.csv")

try6.2 <- mice(fin_imp, maxit = 3, method = "cart")

write.csv(try6.2, "try6_3_imp.csv")

write.csv(complete(try7), "try7.csv")

```

### 2020-04-28 final_extension.Rmd
initial commit with new repo

--- 2020-04-28 Draft_1.Rmd
@@
 ---
-title: "Milestone 7"
+title: "Final Extension"
 author: "Maria Burzillo"
@@
     extra_dependencies: ["rotating"]
-bibliography: final_proj_bib.bib
+bibliography: trounstine_bib.bib
 #biblio-style: "apalike"
@@
 header_includes:
-  usepackage{float}
-  usepackage{dcolumn}
-  usepackage{rotating}
-  restylefloat{table}
+  - \usepackage{float}
+  - \usepackage{dcolumn}
+  - \usepackage{rotating}
 
@@
 
-# Abstract
-
-@trounstine_segregation_2016 suggests that high levels of residential segregation are associated with increased political polarization and decreased public spending.
-In this analysis, I was able to successfully replicate @trounstine_segregation_2016’s main results.
-Adding onto her original analysis, I impute a large amount of missing data from the original dataset and re-run the analysis.
-Finally, I add in income segregation as a predictor in her regressions to assess whether this could be a confounding variable.
+# Extension
+
+```{r setup, include = FALSE}
+
+# import both datasets
+library(haven)
+rp <- read_dta("racial_polarization_winners.dta")
+fin_seg<- read_dta("fin_seg.dta")
+
+# calculate number of original observations
+obs_fin_seg <- nrow(fin_seg)
+obs_rp <- nrow(rp)
+
+```
+
+One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data values in her original datasets.
+Because both R and Stata drop any observations with missing values for any of the variables used in a regression, this can exlcude a large portion of the data from the analysis and potentially bias the results if the data is not missing completely at random.
+A large amount of data is missing in both of the main datasets used in the analyses of @trounstine_segregation_2016.
+The main model specification using the racial polarization dataset exludes `r (obs_rp - 91)` of the original  `r obs_rp` observations, or  %`r round(100*(obs_rp - 91)/obs_rp,2)` of the data.
+Additionally, the main model specification using the financial segregation data set excludes `r obs_fin_seg - 13742` of the original `r obs_fin_seg` observations, or %`r round(100*(obs_fin_seg - 13742)/ obs_fin_seg,2)` of observations from the original dataset.
+
+In an attempt to better deal with the problem of missing data in @trounstine_segregation_2016, I impute missing values in the original data using the mice package in R, which generates multivariate imputations using chained equations [@mice].
+While there are a variety of different imputation methods that could have been employed, multiple imputation (such as the multiple multivariate imputations generated by mice) is desireable because instead of inputting a single value such as the mean for missing values, it instead uses the distribution of the available data to estimate multiple potential values for the missing data.
+As a result, multiple imputation helps to account for the uncertainty inherent in the imputation process and allows for the calculation of standard errors around estimaotrs.
+As a result, multiple imputation allows the researcher to more accurately assess the of uncertainty in the analysis in general.
+
+Before performing the multiple imputations on the datasets, I first examined the missing data for patterns.
+To better understand any potential patterns in missing data, I plotted the pattern of missingness for only and created a histogram showing the frequency of missing values for those variables with missing values in figure X1 for the racial polarization data and figure X2 for the financial segregation data.
+Looking at figure X1, the histogram shows that the variables for the largest vote split along racial lines and the variable indicating whether or not the election had candidates of more than one race had by far the largest percentages of missing data, missing %`r round(sum(is.na(rp$biggestsplit))/nrow(rp)*100,2)` and  %`r round(sum(is.na(rp$biracial))/nrow(rp)*100,2)`, respectively.
+It is important to note that the variable for the largest vote split along racial lines is the dependent variable in the regresison analysis, and thus, we are missing a large percentage of this key variable.
+From the plot on the right, we can see that approximately 42% of observations are complete (have no missing values).
+There seem to be a correspondence between missing a value for biggest split and missing biracial.
+There also seem to be about 2% of values for wich most of the variables are missing.
+However, most observations are not missing more than 2-3 values.
+
+### need to fix numbers below because this was from the whole fin_seg and not from the one filtered via the regression coefficients
+
+In figure X2, we can similarly observe the trends for the financial segregation dataset.
+In this dataset, there is a very high proportion of missing variables for a number of variables.
+For example, there are a `r sum(is.na(fin_seg$H_citytract_NHW_i))` missing values for the segregation index, which is the main independent variable, or %`r round(sum(is.na(fin_seg$H_citytract_NHW_i))/nrow(fin_seg)*100,2)` of the data.
+
+Then, I use the imputed datasets to re-estimate the original models, pooling the results to final pooled regression coefficients and parameters.
+
+One aspect of Trounstine's paper with room for improvement is that there is a large amount of missing data in her datasets upon which she bases her analyses.
+Using R's mice package (add citation), we can perform multiple imputation.
+By performing imputation multiple times, this helps account for the uncertainty inherent in the individual imputations.
+Before performing the multiple imputations, we will first look at the missing data to see if there are any patterns.
+
+for all of the variables in the racial polarization data used in the analysis and for the main independent variable, the segregation index, used in the analysis with the financial segregation dataset.
+More of the data could not be imputed from the financial segregation dataset due to computing and time constraints for this project.
 
@@
 
-set.seed(100)
-
 # import both datasets
@@
 fin_seg$row_num <- as.integer(rownames(fin_seg))
+
+# import stata geo_id data
+
+regression_ids_edit <- read_excel("regression_ids_edit.xlsx")
+
+nrow(regression_ids_edit %>%
+  filter(in_reg == 1))
+
+# find the ones in the stata regression and run it just on those for a sanity check. then try to see why they were included in one but not the other
 
@@
 
-# Introduction
-
-There is a large degree of variation in public goods spending across local governments.
-As a result, many scholars have worked to determine what factors may lead to the underprovision of public goods spending.
-Research in the past has associated racial diversity or changes in levels of diversity with the under-provision of public goods [@baqir_public_1999; @hopkins_diversity_2009].However, @trounstine_segregation_2016 argues that it is racial segregation, not diversity in and of itself, that results in the under-provision of public goods.
-Trounstine’s analysis consists of two main parts.
-First, she uses election and demographic data from 25 of America’s largest cities between 1990 and 2010 to run a multilevel mixed-effects linear regression with fixed effects for region and year and with random effects for cities in order to show that polarization increases with segregation.
-Trounstine measures segregation with Theil's H index, which measures the degree to which the diversity of a neighborhood differs from the diversity of the entire city.
-The second main part of Trounstine’s analysis looks at the ability of the Theil’s H segregation index to explain a variety of types of public expenditures by city using a sample of 2,637 cities with 13,742 city-year observations.
-Using linear regressions with fixed effects for cities and robust standard errors clustered by city, Trounstine finds a significant, negative correlation between segregation and public goods spending that is robust to the inclusion of a variety of relevant controls and an alternative specification in which the number of waterways is used as an instrument for segregation.
-
-In this analysis, I first work to replicate the main results of @trounstine_segregation_2016 using R statistical software [@r].
-The original data and Stata code made publically available by the author were downloaded via the Harvard Dataverse [@DVN/4LZXTY_2015].
-I also make all of my code and analysis available on Github.^[ Link to my [Github repository](https://github.com/mburzillo/new_final_project) for this project.] I was successfully able to replicate the main results of @trounstine_segregation_2016 in R with the exception of some of the marginal analyses, which I was nevertheless able to replicate in Stata.
-
-```{r data_prep_imputations, include = FALSE}
+# Extension 1
+
+One aspect of Trounstine's paper with room for improvement is that there is a large amount of missing data in her datasets upon which she bases her analyses.
+Using R's mice package (add citation), we can perform multiple imputation.
+By performing imputation multiple times, this helps account for the uncertainty inherent in the individual imputations.
+Before performing the multiple imputations, we will first look at the missing data to see if there are any patterns.
+
+```{r data_prep, include = FALSE}
 
@@
 
-# apply the conditions in Stata regression to the fin_seg dataset
-
-fin_imp <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-# select the relevant variables to be imputed
-
-fin_imp <- fin_imp %>%
-  select(H_citytract_NHW_i, dgepercap_cpi, diversityinterp, pctblkpopinterp, pctasianpopinterp,
-         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
-         pctcollegegradinterp, logpop, geo_id2, chng5pctblk, chng5pctlatino, chng5pctasian,
-         ideology_fill, totaltractsf)
-
-miss_var_summary(fin_imp)
-miss_var_summary(rp_impute)
-
-```
-
-```{r obs_count, include = FALSE}
-
-# calculate number of original observations
-
-obs_fin_seg <- nrow(fin_imp)
-obs_rp <- nrow(rp_impute)
-
-```
-
-One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data, which substantially constrains the sample size used in the regression analysis.
-For example, the regression analysis in the main specification using the the original racial polarization dataset exludes %`r round((obs_rp - 91)/obs_rp, 2)` of the observations, and the regression analysis in the main specification using the original financial segregation data excludes %`r round((obs_fin_seg - 13742)/ obs_fin_seg, 2)` of observations from the original dataset.
-As an extension of @trounstine_segregation_2016, I impute missing values in the original data using the mice package in R, which generates multivariate imputations using chained equations [@mice].
-Then, I use the multiply imputed datasets to re-estimate the original models, pooling the results to generate final pooled regression coefficients and parameters.
-
-Comparing the results of the original regressions and those done with the imputed data yields similar big picture results in terms of the direction of the signs on the coefficients on the segregation indices.
-Like in @trounstine_segregation_2016, I find that segregation is positively associated with political polarization and negatively associated with spending on public goods.
-However, the magnitude of the effects in most specifications has diminished and most results become statistically insignificant.
-While these findings do not necessarily challenge the results of @trounstine_segregation_2016, they do call into question the relative importance of segregation in determining public goods spending and political polarization and suggest that the results of @trounstine_segregation_2016 may not be quite as robust as once thought.
-
-# Literature Review
-
-Despite some progress made towards racial equity in the U.S.
-on other fronts, residential racial segregation continues to be prevasive and deeply entrenched in society [@fischer_distinguishing_2004; @oliver_paradoxes_2010; @massey_american_1993].
-Research suggests that this kind of segregation has political consequences, as political cleavages in segregated cities tend to have racial as well as spatial dimensions [@massey_american_1993].
-Neighborhoods are often important actors within local politics because local governments provide many functions that are allocational in nature and concern geographical space [@trounstine_segregation_2016].
-Thus, when neighborhoods are divided on racial lines as well as spacial lines, it is natural to expect higher degrees of racial polarization as a result.
-
-Studying residential segregation is difficult because its effects tend to differ by geographic level.
-On the neighborhood level, the kind of geographic racial isolation brought on by residential segregation has been associated with racial intolerance, resentment, and competition between racial groups [@oliver_paradoxes_2010].
-Living within segregated neighborhoods has also been associated with holding negative stereotypes and perceptions about out groups [@eric_oliver_intergroup_2003].
-As a result, homogeneous neighborhoods have been associated with increased racial tension and political polarization in comparison to integrated, diverse neighborhoods.
-However, at the city or metropolitan level, the opposite seems to be true: when considering larger geographic areas, diversity and integration are correlated with racial tension, competition, prejudice, lower levels of cooperation, and lower spending on public goods [@oliver_paradoxes_2010; @baqir_public_1999; @hopkins_diversity_2009].
-While these differences in the expected effect of segregation on the geographic level may seem confusing at first, they make sense as they suggest that the most severely segregated areas are those that are diverse overall, but have many homogeneous neighborhoods.
-Thus, while people of different races co-exist within a highly segregated city, they live separately within their own neighborhoods, which creates an environment ripe for racial tension [@trounstine_segregation_2016].
-It is thus not simply the level of diversity or integration that matters for racial harmony and cooperation, but their patterns within a larger geographic framework [@trounstine_segregation_2016; @oliver_paradoxes_2010; @bharathi_public_2018].
-
-Political polarization along racial lines may lead to decreased public spending and goods provision because groups may have different preferences, which can make compromise hard, and because groups may preceive a disutility in out-groups receiving public goods expenditure [@baqir_public_1999].
-@einstein_divided_2012 found evidence that racial segregation predicts large political divisions at the metropolitan level and that these divisions can create a lack of willingness to compromise and collaborate on local policy problems.
-@trounstine_segregation_2016 finds similar results at the city level: that residential racial segregation is associated with both increased political division and decreased public spending.
-Thus, these authors suggest that it is the combination of homogenous neighborhoods within a much larger, diverse geographic area that leads to increased political polarization and reduced public goods spending in local governments.
-
-More recently, some scholars have called this hypothesis and its importance into question.
-For example, @lee_ethnic_2018 finds evidence that larger inequalities within the political system favoring socially powerful groups, not local diversity patterns leading to decreased cooperation, may be a better explanation of failures in public goods provision in diverse areas.
-Others suggest that additional factors, such as income segregation, may be important confounding factors in public goods provision.
-@an_its_2018, for example, suggests that the more closely related income inequality is to racial inequality, the less investment is made in public goods, and that this interaction was a better predictor of public goods spending patterns than measures of diversity.
-There is, in fact, a variety of evidence suggesting that it is meaningful to consider the effects of income inequaltiy and diversity and segregation jointly [@an_its_2018; @massey_american_1993].
-Given the active debate in the literature over the relaitonships between diversity, segregation, public spending, and other factors, it is increasingly important to re-examine previously reported findings as a means of robustness checks.
-
-# Replication
-
-I was able to successfully replicate all of the main results from Trounstine (2016).
-All regressions and tables were fully replicated in R.
-As an example, in table X, I replicate Table 1 from page 713 of @trounstine_segregation_2016, which is also included as Figure 1 for comparison.
-However, I was unable to successfully replicate Trounstine (2016)’s marginal effects analyses and margins plots using R.
-There does not yet appear to be a built-in R function to calculate marginal or predicted effects or to generate margins plots from the complicated multi-level models employed in the original paper, and creating such a function was outside of the scope of this analysis.
-Nevertheless, these results were successfully replicated in Stata.
-
-```{r include = FALSE}
-
-## regression 1 Table 1
-
-# fixed effects like a control variable
-
-# lmer(dependent ~ predictors + (random predictors | group level))
-
-# reml v. log likelihood: default in r appears to be log-likelihood. stata defaults to maximum likelihood
-
-# perform a multi-level mixed-effects linear regression of biggest split on the multi-group H index with controls for Herfindahl Diversity Index, % Asian interpolated, % Black interpolated, % Latino interpolated, median household income interpolated, % renters interpolated, percent college grads interpolated, a dummy indicating if there were biracial candidates in the election, a dummy  indicating if the election was nonpartisan, an indicator if the election was a primary, and the log population.
-The regression also includes fixed effects for year and region and random effects for cities (geo_id2).
-Diversity is  included because of the claim that more diverse populations will have more heterogeneous political preferences.
-The other fixed effect control variables are included because they are known to be potentially correlated with segregation.
-winner == 1 requires that there was a winner in the election.
-
-# regression specification. Apply REML = FALSE. The default for lmer() in R is
-# to optimize the restricted (residual) maximum likelihood (REML) whereas in
-# xtmixed in Stata the default is to optimize the log likelihood (which you can
-# do in lmer() in R by setting REML = FALSE), so this will match the STATA code
-
-m1 <- lmer(biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-## regression 2 Table 1
-
-# Perform the same regression as for Column 1 above but this time regress on the two-group calculation of Theil's H interpolated.
-It is unclear where the "diversity" variable is coming from, as the only variable related to diversity in the specificed dataset is diversityinterp.
-This is a problem that will need to be resolved.
-Essentially, this regression just tests an alternate specification to the first in which the segregation index in defined in terms of two-groups rather than multiple.
-
-m2 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-# perform the same regression as for column 2, but now add in a measure of
-# average white political ideology. The point of this is to control for ideology
-# so that the author can separate any effects of segregation from any potential
-# effects of white political ideology. This is important because it is possible
-# that segregation is just a proxy for white conservatism and thus failure to
-# include this variable could lead to ommitted variable bias.
-
-m3 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-```
-
-```{r results="asis", echo = FALSE}
-
-# create a stargazer table of the results
-
-t1 <- stargazer(m1, m2, m3, omit = c("year", "south", "midwest", "west"),
-                header = FALSE,
-                title = "\\textbf{Racial Polarization in Segregated Cities}",
-                single.row = TRUE,
-                no.space = FALSE,
-                add.lines = list(c("Wald Chi Squarred", "a", "b", "c")),
-                omit.stat = c("ll","rsq"),
-                covariate.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Diversity", "Percent Asian", "Percent Black", "Percent Latino", "Medain HH Income (1000s)", "Percent Renters", "Percent College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology", "Constant"),
-                notes = "This table displays...")
-
-# note: "This table displays the results of the replication effort of the analyses conducted in Trounstine (2016) using the racial polarization dataset.
-The replication code can be found on my personal [Github repository](https://github.com/mburzillo/new_final_project).
-The original table is displayed for comparison as Figure 1.")
-
-```
-
-![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016.
-My replication of these results can be found in Table 1 in this paper.](table_1.png)
-
-There was one interesting outcome from my attempt to replicate the original Stata code in R.
-Due to the differences in R and Stata in dealing with missing values, the results of my first replication of analyses using the financial segregation dataset were slightly different than the results in Stata from the original paper.
-In order to exclude cities from her analysis with only one census tract, Trounstine conditions her regressions in Stata such that the value for the number of census tracts is greater than one.
-In Stata, this does not remove missing values, whereas in R, it does.
-Since this variable is used only as a conditional filter and not as a regression variable (and thus, the observations with missing values for number of census tracts are not dropped), Trounstine’s analysis includes 14 cities and 58 observations with missing values for census tracts in addition to cities with two or more census tracts.
-This is a potential oversight on the part of the author, and I would suggest also dropping observations with missing census tract data, or else imputing them given that the aim of her condition was to exclude cities without a sufficient number of census tracts.
-Nevertheless, dropping these values did not have much of an effect on the subsequent results, likely because they represent a small proportion of the overall sample.
-
-# Extension
-
-One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data values in her original datasets.
-Because both R and Stata drop any observations with missing values for any of the variables used in a regression, this can exlcude a large portion of the data from the analysis and potentially bias the results if the data is not missing completely at random.
-A large amount of data is missing in both of the main datasets used in the analyses of @trounstine_segregation_2016.
-The main model specification using the racial polarization dataset exludes `r (obs_rp - 91)` of the original  `r obs_rp` observations, or  %`r round(100*(obs_rp - 91)/obs_rp,2)` of the data.
-Additionally, the main model specification using the financial segregation data set excludes `r round(obs_fin_seg - 13742,2)` of the original `r obs_fin_seg` observations, or %`r round(100*(obs_fin_seg - 13742)/ obs_fin_seg,2)` of observations from the original dataset.
-
-In an attempt to better deal with the problem of missing data in @trounstine_segregation_2016, I impute missing values in the original data using the mice package in R, which generates multivariate imputations using chained equations [@mice].
-While there are a variety of different imputation methods that could have been employed, multiple imputation (such as the multiple multivariate imputations generated by mice) is desireable because instead of inputting a single value such as the mean for missing values, it instead uses the distribution of the available data to estimate multiple potential values for the missing data.
-As a result, multiple imputation helps to account for the uncertainty inherent in the imputation process and allows for the calculation of standard errors around estimators.
-As a result, multiple imputation allows the researcher to more accurately assess the of uncertainty in the analysis in general.
-
-Before performing the multiple imputations on the datasets, I first examined the missing data for patterns.
-To better understand any potential patterns in missing data, I plotted the pattern of missingness and created a histogram showing the frequency of missing values for those variables with missing values in figure X1 for the racial polarization data and figure X2 for the financial segregation data.
-Looking at figure X1, the histogram shows that the variables for the largest vote split along racial lines and the variable indicating whether or not the election had candidates of more than one race had by far the largest percentages of missing data, missing %`r round(sum(is.na(rp_impute$biggestsplit))/nrow(rp_impute)*100,2)` and  %`r round(sum(is.na(rp_impute$biracial))/nrow(rp_impute)*100,2)`, respectively.
-It is important to note that the variable for the largest vote split along racial lines is the dependent variable in the regresison analysis, and thus, we are missing a large percentage of this key variable.
-From the plot on the right, we can see that approximately 42% of observations are complete (have no missing values).
-There seem to be a correspondence between missing a value for the largest vote split and missing a value for the biracial election indicator.
-There also seem to be about 2% of values for wich most of the variables are missing.
-However, most observations are not missing more than 2-3 values.
-
-```{r rp_missing_plot, include = FALSE, warning = FALSE}
+```
+
+```{r rp_missing_plot, echo = FALSE, warning = FALSE}
 
@@
 
-# gg_miss_var(rp_impute, show_pct = TRUE)
-
-```
-
-```{r rp_aggr_plot, echo = FALSE}
-
-# select only the missing values
+gg_miss_var(rp_impute, show_pct = TRUE)
+
+```
+
+The above plot reveals that biggestsplit and biracial are the two variables with by far the largest percentage of missing values.
+Both of these are missing approximately 50% of their observations.
+Since biggestsplit is the dependent variable in our analysis with this dataset, this is an important fact.
+
+```{r echo = FALSE}
 
@@
 
-# create an aggr plot for the missing values
-
-aggr(rp_aggr, bars = TRUE, col=c('navyblue','red'), numbers=TRUE, cex.axis=.5, gap=1, ylab=c("Proporiton of Missing Values","Combinations"))
-
-# caption for this plot when I figure out how to do it...
-: This plot examines the pattern of missing data in the the original racial polarization dataset from Trounstine (2016).
-The plot on the left shows the percentage of missing data for each variable with missing data and reveals that the variables that are missing by far the most data are the largest vote split along racial lines (biggestsplit) and the variable indicating whether or not the election had candidates of more than one race (biracial).
-The plot on the right shows the pattern of missingness among the variables.
-We can see that approximately 42% of observations are complete (have no missing values).
-There seems to be a correspondence between missing a value for biggest split and missing biracial.
-There also seem to be about 2% of values for which most of the variables are missing.
+aggr_plot <- aggr(rp_aggr, col=c('navyblue','red'), numbers=TRUE, sortVars=TRUE, cex.axis=.5, gap=1, ylab=c("Histogram of missing data","Pattern"))
+
+# this plot tells us that 42% of the data are not missing anything 
+```
+To better understand any potential patterns in missing data, we then plotted the pattern of missingness for only those variables missing values.
+From the plot on the right, we can see that approximately 42% of observations are complete.
+There seem to be a correspondence between missing a value for biggest split and missing biracial.
+There also seem to be about 2% of values for wich most of the variables are missing.
 However, most observations are not missing more than 2-3 values.
 
-```
-
-In figure X2, we can similarly observe the trends for the financial segregation dataset.
-In this dataset, there is a very high proportion of missing variables for a number of variables.
-For example, there are `r sum(is.na(fin_imp$H_citytract_NHW_i))` missing values for the segregation index, which is the main independent variable, or %`r round(sum(is.na(fin_imp$H_citytract_NHW_i))/nrow(fin_imp)*100,2)` of the data.
-In this dataset, there are also many more observations for which values are missing for multiple variables in comparison to the racial polarization dataset.
-In total, a mere %`r .0058*100` of observations are complete for all variables included in the main specification for the financial segregaion dataset.
-
-```{r fin_missing_plot, include = FALSE}
-
-miss_var_summary(fin_imp)
-
-gg_miss_var(fin_imp, show_pct = TRUE)
-
-```
-
-```{r fin_aggr_plot, echo = FALSE}
-
-# select all variables with missing values for the aggr plot
-
-fin_imp_aggr <- fin_imp %>%
-  select(ideology_fill, H_citytract_NHW_i, chng5pctblk, chng5pctlatino, chng5pctasian, diversityinterp, pctblkpopinterp, pctasianpopinterp,
-         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
-         pctcollegegradinterp)
-
-new_try <- head(fin_imp_aggr, 20)
-
-aggr(new_try, plot = TRUE, bars = FALSE, col=c('navyblue','red'), numbers=TRUE)
-
-# create the aggr plot
-
-aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.5, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
-title(main = "Patterns of Missingness in the Financial Segregation Data",
-      sub = "Is this a caption?
-qiufwnjekfewkfnwein\nwefjwenmf wiufnwqjenf ewfuiwjnef nfijefnwjenfkqwjnf lqwjefnjqwefjwnef winfjqwhf hjwefwiuefief welfiunqlfjnqkjwe qqfniquwenjfjq iqfnjkjeq rfiunfj q")
-
-# this plot tells us that only .58% of the data are complete (not missing anything)
-
-# caption for this plot when I figure out how to do it...
-: This plot examines the pattern of missing data in the the original financial segregation dataset from Trounstine (2016).
-The plot on the left shows the percentage of missing data for each variable with missing data and reveals that a large number of variables are missing the vast majority of data.
-The plot on the right shows the pattern of missingness among the variables.
-We can see that only .58% of observations are complete (have no missing values), and a large majority of the observations are missing data for many variables.
-
-```
-
-Because neither dataset seems to exhibit any clear patterns in the missing, data, it makes sense to proceed with the imputation.
-For the racial polarization dataset, I performed multiple imputations with 20 iterations using mice, while for the financial segregation dataset, I performed only 5 iterations due to the large size of the dataset and computing limitaitons.
-A non-stochastic imputation method, Classification and Regression Trees (CART), was used instead of the default for the imputation for both datasets because of an error with matrix inversion caused by the data that prevented the use of the default method, predictive mean matching.
-For the racial polarization dataset, I included all of the variables used in the analysis associated with the dataset and was able to impute all missing values.
-For the financial segregation dataset, however, I only imputed values for the main independent variable, the segregation index, and a few other variables, although all variables used in the analysis were included in the data subset input into the mice function.
-More of the data could not be imputed from the financial segregation dataset due to computing and time constraints for this project given the dataset's large size and high proportion of missing values.
-
-```{r rp_imputation, include = FALSE}
-
+Finding no clear patterns in the missing data, I next performed mutliple imputations (with 10 iterations) on the dataset.
+A non-stochastic imputation method, Classification and Regression Trees (CART), was used instead of the default because of an error with matrix inversion caused by the data.
+Before examining the results of Trounstine's model using the imputed data, I first run some diagnostic tests of the imputation results to make sure that everything is running as expected.
+
+```{r, include = FALSE}
 # Perform multiple imputations using the cart method. Because of the time it
@@
 
-max_it = 20
-
-imp_1_rp <- mice(rp_impute, method = "cart", maxit = 20)
+imp_1_rp <- mice(rp_impute, method = "cart", maxit = 10)
+
+# write.csv(complete(imp_1_rp), "imp_1_rp.csv")
+
+# import new data frame with imputed data
+
+#imp_1_rp <- read_csv("imp_1_rp.csv")
 
@@
 
-```{r fp_imputations, include = FALSE}
-
-# perform multiple imputations.
-We have the same issue here with the default method as with the previous dataset so we use CART.
-Additionally, because of the extremely large size of this dataset, we choose to only impute the variable H_citytract_NHW_i, as it is the most frequently missing variable and also out main independent variable.
-Just imputing this allows us to include way more observations in the regression than the original data despite the still large number of NAs overall.
-One concern here would be that if there was some reason that this variable was missing rather than other variables that only imputing this variable could lead to some bias in the results.
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp, maxit=0, print=F)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs <- mice(fin_imp, method = meth, maxit = 5)
-
-# now there are manyb fewer missing variables!!!
-
-miss_var_summary(complete(imp_fs))
-
-head(complete(imp_fs))
-
-miss_var_summary(fin_imp)
-
-```
-
-```{r new_imp}
-
-fin_imp <- fin_imp %>%
-  mutate(nas = is.na(H_citytract_NHW_i) + is.na(dgepercap_cpi) + is.na(diversityinterp) + is.na(pctblkpopinterp)  + is.na(pctasianpopinterp) + is.na(pctlatinopopinterp) + is.na(medinc_cpi) + is.na(pctlocalgovworker_100) + is.na(pctrentersinterp) + is.na(pctover65) + is.na(pctcollegegradinterp) + is.na(logpop) + is.na(geo_id2) + is.na(chng5pctblk) + is.na(chng5pctlatino) + is.na(chng5pctasian) + is.na(logpop) + is.na(geo_id2) + is.na(chng5pctblk) + is.na(chng5pctlatino) + is.na(chng5pctasian) + is.na(ideology_fill))
-
-fin_imp %>%
-  ggplot(aes(x = nas)) +
-  geom_histogram()
-
-fin_imp %>%
-  group_by(nas) %>%
-  summarise(n())
-
-# exclude all observations with 17 out of 22 nas
-
-fin_imp_sub <- fin_imp %>%
-  filter(nas < 17)
-
-nrow(fin_imp_sub)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_sub, maxit=0, print=F)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-new_imp_fs <- mice(fin_imp_sub, method = meth, maxit = 5)
-
-miss_var_summary(complete(new_imp_fs))
-```
-
-## make sure to talk about the fact that still a large number of values missing for the imputed variables here
-
-Before examining the results of Trounstine's model using the multiply imputed data, I first ran some diagnostic tests on the imputation results to make sure that everything ran as expected.
-First, I checked the convergence of the algorithm used within mice() by plotting the trace lines as a function of the number of iterations for each of the variables.
-Then, I visually inspected the distributions of the imputed data in comparison to the original data with density and strip plots.
-All of these checks suggested that the imputed values were within a plausible range of the data and that their distribution fit the underlying distribution of the data relatively well.
-The only cases in which there was some cause for concern were for some of the variables with very few missing values in the racial polarization dataset (such as the indicators for region).
-However, this is more or less to be expected given the small number of imputations performed in these cases.
-Thus, and especially because there are so few of these values missing in the actual datasets, this was not a major concern.
-See figures X and X1 to see the density plots of the imputed values overlayed on the density plots of the original variables.
-The rest of the plots and results of the diagnostic tests discussed here are presented in the Appendix.
-
-```{r rp_densityplot, echo = FALSE}
-
-densityplot(imp_1_rp)
-
-```
-
-```{r rp_imp_plot, include = FALSE}
+First, I check the convergence of the algorithm used within mice() for each of the variables.
+For the most part, the fits intertwine and do not exhibit any trends at later iterations, as desired.
+There are some issues with the results for some of the variables with very few missing values (such as West and South), which makes sense as we would expect the mean to be less reliable due to the law of large numbers, and convergence is more difficult.
+Nevertheless, since there are so few of these values in the actual dataset, this is not a major concern.
+
+```{r imp_plot, echo = FALSE}
 
@@
 
-```{r rp_stripplot, include = FALSE}
+We can also check the imputed values against the original values using stripplot().
+Each column in each subplot represents a separate iteration.
+The magenta points represent the imputed data.
+The values of the variable in questions are along the y axis.
+We expect the spread of the data to be similar if the imputations were done well.
+If the data were missing completely at random, then the imputed data should have the same distribution as the original data.
+In particular, we want to be sure that the imputations are within a plausible range of the data.
+This is the case for all of our imputed variables, and there does not seem to be cause for alarm from these results.
+
+```{r rp_stripplot, echo = FALSE}
 
@@
 
-```{r fs_densityplot, echo = FALSE}
-
-densityplot(imp_fs)
-densityplot(x=imp_fs , data= ~ H_citytract_NHW_i + chng5pctblk + 
-       chng5pctlatino + chng5pctasian + ideology_fill)
-
-```
-
-```{r fs_imp_plot, include = FALSE}
+Finally, we can also look at the density plots for each variable's actual data and for their imputed data from each of the iterations, which are represented in magenta.
+Overall, the density plots align quite well for the variables with the most missing data, biracial and biggestsplit, and relatively well for most of the other variables with missing data.
+Again, the fit is less good for variables with fewer missing data points.
+
+```{r rp_densityplot, echo = FALSE}
+
+densityplot(imp_1_rp)
+
+```
+
+While the imputations are not perfect, there do not seem to be any major problems so far.
+Thus, we can now proceed with our analysis.
+We fit each of our ten imputed datasets to Trounstine's 3 models using this data and then pool the results for each.
+The results are as follows:
+
+```{r rp_imputations, include = FALSE}
+
+# Now that we have imputed the missing data, we can re-run the analyses from the
+# original paper to see how and if this changes the analysis. We can use the
+# with() function from the mice package to fit each of the imputed datasets to
+# the model and then pool the results afterwards.
+
+# regression 1: fit multiple imputed datasets
+
+fit_imp_1_rp <- with(imp_1_rp, lmer(formula = biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
+
+# pool and summarize the analyses
+
+pool_imp_1_rp <- pool(fit_imp_1_rp)
+imp_1_rp_sum <- summary(pool_imp_1_rp)
+
+## regression 2 Table 1: fit multiple imputed datasets
+
+#formula = biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2)
+
+fit_imp_2_rp <- with(imp_1_rp, lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
+
+# pool and summarize the analyses
+
+pool_imp_2_rp <- pool(fit_imp_2_rp)
+imp_2_rp_sum <- summary(pool_imp_2_rp)
+
+## regression 3 Table 1 with new data
+
+#formula = biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2)
+
+fit_imp_3_rp <- with(imp_1_rp, lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
+
+# pool and summarize the analyses
+
+pool_imp_3_rp <- pool(fit_imp_3_rp)
+imp_3_rp_sum <- summary(pool_imp_3_rp)
+
+```
+
+## Extension 1 Racial Polarization Table
+
+```{r results="asis", echo = FALSE, include = FALSE}
+
+# create a stargazer table of the results
+
+#t1_imp <- stargazer(fit_imp_3_rp, 
+                    #omit = c("year.f", "south", "midwest", "west"),
+#                header = FALSE,
+#                title = "\\textbf{Racial Polarization in Segregated Cities}")
+
+```
+
+```{r echo = FALSE, include = FALSE}
+
+#gt(imp_1_rp_sum_table) %>%
+#  tab_header(title = md("**Extension 1 RP Regression 1**"),
+#             subtitle = "")
+
+#gt(imp_1_rp_sum_table)
+
+#cols_label(term = md("**Term**"), estimate = md("**Estimate**"), std.error = md("**SD**"), p.value = md("**P Value**"))
+
+```
+
+## Regression 1
+
+```{r results_printing_rp_impute_regressions_1, echo=FALSE}
+
+# print results of 1st regression
+
+imp_1_rp_sum_table <- as.data.frame(imp_1_rp_sum %>% 
+  select(term, estimate, std.error, p.value)) %>%
+  head(13)
+print(imp_1_rp_sum_table)
+
+```
+
+The results of the model with the new dataset are slightly different in comparison to the original results from Trounstine (2016).
+With the imputed data, we now have a total of `r nrow(complete(rp_impute))` observations in our model as compared to the original model, which had only 91 observations.
+Interestingly, while the sign of the coefficient on the main variable of interest, the Theil's H segregation index is the same and the standard error has decreased slightly, the result has become statisically insignificant and the 95% confidence interval contains zero.
+Thus while these results still suggest that segregation may be associated with increased political polarization, they confer a lesser degree of certainty than Trounstine's original analysis.
+The coefficients for pctblkpopinterp, pctlatinopopinterp, and medincinterp have also switched signs, and all coefficients except indicators for a biracial and primary election are also statistically insignificant, as was the case in the original analysis.
+In general, the standard error on the coefficients has decreased slightly.
+
+In the second and third regressions, the results are similar in comparison to the unimputed data to the first.
+Standard errors have reduced slightly.
+The main coefficient on segregation index has decreased in magnitude, although in these specifications, it remains statistically significant.
+The other coefficients except for biracial and primary are insignificant, and the coefficients on percent Asian, Black, and Latino have all switched signs.
+
+## Regression 2
+
+```{r results_printing_rp_impute_regressions_2, echo=FALSE}
+
+# print results of 2nd regression
+
+imp_2_rp_sum_table <- as.data.frame(imp_2_rp_sum %>% 
+  select(term, estimate, std.error, p.value)) %>%
+  head(13)
+print(imp_2_rp_sum_table)
+
+```
+
+## Regression 3
+
+```{r results_printing_rp_impute_regressions_3, echo=FALSE}
+
+# print results of 3rd regression
+
+imp_3_rp_sum_table <- as.data.frame(imp_3_rp_sum %>% 
+  select(term, estimate, std.error, p.value)) %>%
+  head(13)
+print(imp_3_rp_sum_table)
+```
+
+# Extension Part 2: Fin Seg Data Set
+
+In the second, and arguably most important dataset in the analysis, the data set on financial segregation, there are a very large number of missing values.
+For example, on the main independent variable of interest, there are a whopping 282,334 missing values, or %`r round(282334/324178*100,2)` of the data.
+
+```{r include = FALSE}
+
+# apply the conditions in Stata regression
+
+fin_imp <- fin_seg %>%
+  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0) %>%
+  mutate(medinc_cpi = medinc_cpi/1000)
+
+# select the relevant variables
+
+fin_imp <- fin_imp %>%
+  select(H_citytract_NHW_i, dgepercap_cpi, diversityinterp, pctblkpopinterp, pctasianpopinterp,
+         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
+         pctcollegegradinterp, logpop, geo_id2, chng5pctblk, chng5pctlatino, chng5pctasian,
+         ideology_fill)
+
+miss_var_summary(fin_imp)
+
+gg_miss_var(fin_imp, show_pct = TRUE)
+
+gg_miss_var(fin_imp)
+
+```
+```{r echo = FALSE}
+
+gg_miss_var(fin_imp, show_pct = TRUE)
+
+```
+
+```{r echo = FALSE}
+
+# select all variables with missing values for the aggr plot
+
+fin_imp_aggr <- fin_imp %>%
+  select(H_citytract_NHW_i, diversityinterp, pctblkpopinterp, pctasianpopinterp,
+         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
+         pctcollegegradinterp, chng5pctblk, chng5pctlatino, chng5pctasian,
+         ideology_fill)
+
+aggr_plot <- aggr(fin_imp_aggr, bars = TRUE, col=c('navyblue','red'), numbers=TRUE, sortVars=TRUE, cex.axis=.5, gap=3, ylab=c("Histogram of missing data","Pattern"))
+
+# this plot tells us that only .066% of the data are complete (not missing anything)
+
+nrow(fin_imp) * .0058
+```
+
+```{r include = FALSE}
+
+# perform multiple imputations.
+We have the same issue here with the default method as with the previous dataset so we use CART.
+Additionally, because of the extremely large size of this dataset, we choose to only impute the variable H_citytract_NHW_i, as it is the most frequently missing variable and also out main independent variable.
+Just imputing this allows us to include way more observations in the regression than the original data despite the still large number of NAs overall.
+One concern here would be that if there was some reason that this variable was missing rather than other variables that only imputing this variable could lead to some bias in the results.
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp, maxit=0, print=F)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# other
+
+other <- c("chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+imp_2_fs <- mice(fin_imp, method = meth, maxit = 5)
+
+# now there are manyb fewer missing variables!!!
+
+# miss_var_summary(complete(imp_2_fs))
+
+```
+
+Finding no clear patterns in the missing data, I next performed mutliple imputations (with 5 iterations) on the dataset.
+A non-stochastic imputation method, Classification and Regression Trees (CART), was used instead of the default because of an error with matrix inversion caused by the data.
+Before examining the results of Trounstine's model using the imputed data, I first run some diagnostic tests of the imputation results to make sure that everything is running as expected.
+
+First, I check the convergence of the algorithm used within mice() for each of the variables. For the most part, the fits intertwine and do not exhibit any trends at later iterations, as desired.
+
+```{r fs_imp_plot, echo = FALSE}
 
@@
 
-plot(imp_fs)
-
-```
-
-```{r fs_stripplot, include = FALSE}
+plot(imp_2_fs)
+
+```
+
+We can also check the imputed values against the original values using stripplot().
+Each column in each subplot represents a separate iteration.
+The magenta points represent the imputed data.
+The values of the variable in questions are along the y axis.
+We expect the spread of the data to be similar if the imputations were done well.
+If the data were missing completely at random, then the imputed data should have the same distribution as the original data.
+In particular, we want to be sure that the imputations are within a plausible range of the data.
+This is the case for all of our imputed variables, and there does not seem to be cause for alarm from these results.
+
+```{r fs_stripplot, echo = FALSE}
 
@@
 
-stripplot(imp_fs, H_citytract_NHW_i)
-
-stripplot(imp_fs, chng5pctblk)
-
-stripplot(imp_fs, chng5pctlatino)
-
-stripplot(imp_fs, chng5pctasian)
-
-stripplot(imp_fs, ideology_fill)
-
-```
-
-Given the promising results of the diagnostic checks, I next proceeded to re-estimate the original model using the multiply imputed datasets, pooling the results to produce final pooled regression coefficients and parameters.
-The results for the analyses using the racial polarization dataset are presented in tables 1-3.
-
-```{r rp_imputations, include = FALSE}
-
-# Now that we have imputed the missing data, we can re-run the analyses from the
-# original paper to see how and if this changes the analysis. We can use the
-# with() function from the mice package to fit each of the imputed datasets to
-# the model and then pool the results afterwards.
-
-# regression 1: fit multiple imputed datasets
-
-fit_imp_1_rp <- with(imp_1_rp, lmer(formula = biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
-
-# pool and summarize the analyses
-
-pool_imp_1_rp <- pool(fit_imp_1_rp)
-imp_1_rp_sum <- summary(pool_imp_1_rp)
-
-## regression 2 Table 1: fit multiple imputed datasets
-
-#formula = biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2)
-
-fit_imp_2_rp <- with(imp_1_rp, lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
-
-# pool and summarize the analyses
-
-pool_imp_2_rp <- pool(fit_imp_2_rp)
-imp_2_rp_sum <- summary(pool_imp_2_rp)
-
-## regression 3 Table 1 with new data
-
-#formula = biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2)
-
-fit_imp_3_rp <- with(imp_1_rp, lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
-
-# pool and summarize the analyses
-
-pool_imp_3_rp <- pool(fit_imp_3_rp)
-imp_3_rp_sum <- summary(pool_imp_3_rp)
-
-```
-
-The results of the model with the new dataset are slightly different in comparison to the original results from Trounstine (2016).
-With the imputed data, we now have a total of `r nrow(complete(rp_impute))` observations in our model as compared to the original model, which had only 91 observations.
-Interestingly, while the sign of the coefficient on the main variable of interest, the Theil's H segregation index, is the same and the standard error has decreased slightly, the result has become statisically insignificant and the 95% confidence interval contains zero.
-Thus while these results still suggest that segregation may be associated with increased political polarization, they confer a lesser degree of certainty than Trounstine's original analysis.
-The coefficients for % Black population, % Latino population, and median household income have also switched signs, and all coefficients except the indicator for a biracial election are also statistically insignificant, as was the case in the original analysis.
-The coefficient on the indicator for a primary election, has also changed from being significant in the original analysis to insignificant here.
-In general, the standard errors on the coefficients have decreased slightly.
-
-```{r results_printing_rp_impute_regressions_1, results = "asis", echo=FALSE}
-
-# print results of 1st regression
-
-imp_1_rp_sum_table <- as.data.frame(imp_1_rp_sum %>% 
-  select(term, estimate, std.error, p.value)) %>%
-  head(13)
-print(imp_1_rp_sum_table)
-
-stargazer(imp_1_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Multigroup Segregation Index}")
-
-```
-
-In the second and third regressions, the results are similar.
-The main coefficient on segregation index has decreased in magnitude, although in these specifications, it remains statistically significant.
-The other coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian, Black, and Latino have all switched signs.
-Standard errors have also reduced slightly in these specifications compared to the original analysis in @trounstine_segregation_2016.
-
-```{r results_printing_rp_impute_regressions_2, results = "asis", echo=FALSE}
-
-# print results of 2nd regression
-
-imp_2_rp_sum_table <- as.data.frame(imp_2_rp_sum %>% 
-  select(term, estimate, std.error, p.value)) %>%
-  head(13)
-print(imp_2_rp_sum_table)
-
-stargazer(imp_2_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Two-Group Segregation Index}")
-
-```
-
-```{r results_printing_rp_impute_regressions_3, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_3_rp_sum_table <- as.data.frame(imp_3_rp_sum %>% 
-  select(term, estimate, std.error, p.value)) %>%
-  head(13)
-print(imp_3_rp_sum_table)
-
-stargazer(imp_3_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Ideology Control}")
-```
-
-For the financial segregation dataset, we similarly fit each of our 5 imputed datasets to the original models from @trounstine_segregation_2016 using this data and then pool the results for each.
-The pooled results are presented in tables 4-6.
-
-# FS data results
-
-```{r fs_imputed_pooled_regressions, include = FALSE}
+stripplot(imp_2_fs, H_citytract_NHW_i)
+
+stripplot(imp_2_fs, chng5pctblk)
+
+stripplot(imp_2_fs, chng5pctlatino)
+
+stripplot(imp_2_fs, ideology_fill)
+
+```
+
+Finally, we can also look at the density plots for each variable's actual data and for their imputed data from each of the iterations, which are represented in magenta.
+Overall, the density plots align quite well for the variables.
+
+```{r fs_densityplot, echo = FALSE}
+
+densityplot(imp_2_fs)
+densityplot( x=imp_2_fs , data= ~ H_citytract_NHW_i + chng5pctblk + 
+       chng5pctlatino + chng5pctasian + ideology_fill)
+```
+
+While the imputations are not perfect, there do not seem to be any major problems so far.
+Thus, we can now proceed with our analysis.
+We fit each of our 5 imputed datasets to Trounstine's 3 models using this data and then pool the results for each.
+The results are as follows:
+
+```{r include = FALSE}
 # Main Analysis 2: Imputations
@@
 
-fit_imp_felm1 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+fit_imp_felm1 <- with(imp_2_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
 
@@
 
-fit_imp_felm2 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+fit_imp_felm2 <- with(imp_2_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
 
@@
 
-fit_imp_felm3 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))
+fit_imp_felm3 <- with(imp_2_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))
 
@@
 
-```{r fs_imputed_data_included_calc, include = FALSE}
+## Regression 1
+
+The results of the first regression indicate that Trounstine's results are robust to the inclusion of the imputed data, which led to the inclusion of an additional 59,377 observaitons in the analysis.
+The coefficients, standard errors, and significance levels are essentially unchanged.
+The same is largely true for the second and third specifications, but the magnitude of the coefficient on the segregation decreases by a marginal amount.
+
+```{r results_printing_fs_impute_regressions_1, echo=FALSE}
+
+# print results of 3rd regression
+
+imp_felm1_sum_table <- as.data.frame(imp_felm1_sum %>% 
+  select(term, estimate, std.error, p.value))
+print(imp_felm1_sum_table)
+```
+
+```{r results_printing_fs_impute_regressions_2, echo=FALSE}
+
+# print results of 3rd regression
+
+imp_felm2_sum_table <- as.data.frame(imp_felm2_sum %>% 
+  select(term, estimate, std.error, p.value))
+print(imp_felm2_sum_table)
+```
+
+```{r results_printing_fs_impute_regressions_3, echo=FALSE}
+
+# print results of 3rd regression
+
+imp_felm3_sum_table <- as.data.frame(imp_felm3_sum %>% 
+  select(term, estimate, std.error, p.value))
+print(imp_felm3_sum_table)
+```
+
+```{r include = FALSE}
 # how many observations were included in those 3 analyses?
@@
 
-fin <- complete(imp_fs) %>%
+sum(is.na(complete(imp_2_fs)$H_citytract_NHW_i))
+sum(is.na(complete(imp_2_fs,1)$H_citytract_NHW_i))
+sum(is.na(complete(imp_2_fs,2)$H_citytract_NHW_i))
+sum(is.na(complete(imp_2_fs,3)$H_citytract_NHW_i))
+sum(is.na(complete(imp_2_fs,4)$H_citytract_NHW_i))
+sum(is.na(complete(imp_2_fs,5)$H_citytract_NHW_i))
+
+fin <- complete(imp_2_fs) %>%
   filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
@@
 
-# now we have 73,119 observations compared to 13,742. Calculation:
-
-nrow(fin_dge)
+print(fin_dge_tab)
+
+# now we have 73,119 observations compared to 13,742
+
+nrow(fin_seg)
 
@@
 
-# number missing now: 222957 -> Calculation:
-
-new_missing <- sum(is.na(complete(imp_fs)$H_citytract_NHW_i))
-
-# calculate number of observations we added to the sample: 59,377
-
-num_added <- 282334 - new_missing
-
-# INTERPRETATION BEFORE AFTER CHANGED The results of the first regression present a stark difference to the results of @trounstine_segregation_2016.
-Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant.
-Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
-The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.
-
-```
-
-The results of the first regression present a stark difference to the results of @trounstine_segregation_2016.
-Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant.
-Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
-The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.
-
-The results of the first regression indicate that Trounstine's results are robust to the inclusion of the imputed data, which led to the inclusion of an additional 59,377 observations in the analysis.
-The coefficients, standard errors, and significance levels are essentially unchanged.
-The same is largely true for the second and third specifications, but the magnitude of the coefficient on the segregation decreases slightly.
-
-```{r results_printing_fs_impute_regressions_1, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_felm1_sum_table <- as.data.frame(imp_felm1_sum %>% 
-  select(term, estimate, std.error, p.value))
-print(imp_felm1_sum_table)
-
-stargazer(imp_felm1_sum_table,
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Expenditure per Capita}")
-```
-
-```{r results_printing_fs_impute_regressions_2, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_felm2_sum_table <- as.data.frame(imp_felm2_sum %>% 
-  select(term, estimate, std.error, p.value))
-print(imp_felm2_sum_table)
-
-stargazer(imp_felm1_sum_table,
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Changing Demographics}")
-```
-
-```{r results_printing_fs_impute_regressions_3, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_felm3_sum_table <- as.data.frame(imp_felm3_sum %>% 
-  select(term, estimate, std.error, p.value))
-print(imp_felm3_sum_table)
-
-stargazer(imp_felm1_sum_table,
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Ideology Control}")
-```
-
-# FS NEW data results
-
-```{r new_fs_imputation_tries, include = FALSE}
-# Main Analysis 2: Imputations
-
-## regression 1 Table 2
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-## regression 2 Table 2
-
-# fit multiple imputed datasets
-
-fit_imp_felm2 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm2 <- pool(fit_imp_felm2)
-imp_felm2_sum <- summary(pool_imp_felm2)
-
-## Regression 3 Table 2
-
-fit_imp_felm3 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm3 <- pool(fit_imp_felm3)
-imp_felm3_sum <- summary(pool_imp_felm3)
-
-# INTERPRETATION BEFORE AFTER CHANGED The results of the first regression present a stark difference to the results of @trounstine_segregation_2016.
-Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant.
-Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
-The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.
-
-print(imp_felm1_sum)
-print(imp_felm2_sum)
-print(imp_felm3_sum)
-
-# large amount of data missing across the board in terms of years
-
-gg_miss_var(fin_dge, facet = year, show_pct = TRUE)
-
-# can't really tell anything about the region facet since a lot of obs missing region data
-
-gg_miss_var(fin_imp_extra, facet = region, show_pct = TRUE)
-
-# not necessarily a significant pattern across states either
-
-gg_miss_var(fin_imp_extra, facet = statecode, show_pct = TRUE)
-
-```
-
-# FS NEW AGAIN
-
-```{r}
-cities_to_keep <- c("Austin City", "Baltimore City", "Charlotte City", "Chicago City", "Cleveland City", "Columbus City", "Dallas City", "Denver City", "Detroit City", "Houston City", "Indianapolis", "Jacksonville", "Los Angeles City", "Memphis City", "Milwaukee City", "New York City", "Oklahoma City City", "Philadelphia City", "Phoenix City", "San Antonio City", "San Diego City", "San Francisco City", "San Jose City", "Tucson City", "Washington City")
-
-# apply the conditions in Stata regression to the fin_seg dataset
-
-fin_imp_cities <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0, cityname %in% cities_to_keep) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-# select the relevant variables to be imputed
-
-fin_imp <- fin_imp %>%
-  select(H_citytract_NHW_i, dgepercap_cpi, diversityinterp, pctblkpopinterp, pctasianpopinterp,
-         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
-         pctcollegegradinterp, logpop, geo_id2, chng5pctblk, chng5pctlatino, chng5pctasian,
-         ideology_fill)
-```
-
-```{r looking_at_original_data, include = FALSE}
-
-range(fin_seg$totaltractsf, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_seg %>%
-  ggplot() +
-  geom_histogram(aes(x = totaltractsf))
-
-range(fin_seg$logpop, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_seg %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-# add back in year, region, and statecode to be able to look at this
-
-fin_imp_old <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-fin_imp_extra <- fin_imp %>%
-  mutate(year = fin_imp_old$year,
-         region = fin_imp_old$region,
-         statecode = fin_imp_old$statecode)
-
-# large amount of data missing across the board in terms of years
-
-gg_miss_var(fin_imp_extra, facet = year, show_pct = TRUE)
-
-# can't really tell anything about the region facet since a lot of obs missing region data
-
-gg_miss_var(fin_imp_extra, facet = region, show_pct = TRUE)
-
-# not necessarily a significant pattern across states either
-
-gg_miss_var(fin_imp_extra, facet = statecode, show_pct = TRUE)
-
-```
-
-```{r looking_at_Trounstine_data, include = FALSE}
-
-# basic filter for table for all regressions
-
-# xtreg dgepercap_cpi H_citytract_NHW_i diversityinterp pctblkpopinterp
-# pctasianpopinterp pctlatinopopinterp medinc_cpi pctlocalgovworker_100
-# pctrentersinterp pctover65 pctcollegegradinterp logpop if totaltracts>1 &
-# dgepercap_cpi~=0,fe vce(cluster geo_id2)
-
-fin_trounstine <-fin_seg %>%
-  filter(totaltractsf >1 | is.na(totaltractsf)) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
-
-# create dge variable used in regression
-
-fin_dge_trounstine <-fin_trounstine %>% filter(dgepercap_cpi != 0)
-
-range(fin_dge_trounstine$totaltractsf, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_dge_trounstine %>%
-  ggplot() +
-  geom_histogram(aes(x = totaltractsf))
-
-range(fin_dge_trounstine$logpop, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_dge_trounstine %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-```
-
-```{r looking_at_imputed_data}
-
-fin_new_imp <- complete(new_imp_fs) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
-
-range(fin_new_imp$logpop, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_new_imp %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-```
-
-# Conclusion
-
-Why cities differ in their amount of spending on public goods is an interesting questions that is frequently debated in the literature.
-@trounstine_segregation_2016 posits that segregation may be an important underlying cause of the underprovsion of public goods.
-Finding evidence that residential segregation by race increases political partisanship, @trounstine_segregation_2016 argues that residential segregation can increase division and make cooperation amongst competing groups difficult, which results in decreased spending on public goods.
-The findings of @trounstine_segregation_2016 are particularly important because they suggest that segregation, as defined by many homogeneous neighborhoods within a larger diverse geographical area, is the key factor in disinvestment in public goods.
-This contradicts previous research which has suggested that levels of diversity were instead most important (see for example @baqir_public_1999 or @hopkins_diversity_2009).
-While @trounstine_segregation_2016 still represents relatively new reasearch as of 2020, it has yet to be fully vetted by additional research.
-Furthermore, some research that has been published on the topic since its publication suggests that other factors such as larger inequities in the political system favoring socially powerful groups [@lee_ethnic_2018] or the interaction of income and racial inequality [@an_its_2018] may be more important in explaining public goods provisions.
-
-I first worked to provide a check on the analysis presented in @trounstine_segregation_2016 by attempting to replicate the work in R.
-I was able to successfully replicate all of the main results from @trounstine_segregation_2016, with the exception of a few of a few marginal analyses of the complex, multi-level models which, to my knowledge, are currently not supported by available R packages.
-I was, however, able to successfully replicate these results in Stata.
-
-As an additional robustness check I also tested the models in @trounstine_segregation_2016 by re-running them with additional data that I imputed from missing values in the original datasets.
-The large number of missing values in both of the datasets used in @trounstine_segregation_2016's main analysis created a concern for potential bias in the original results and a lack of representativeness due to the large amount of data excluded from the regression analysis due to missing values.
-Thus, I used the mice package in R to create multiply imputed datasets, upon which I re-ran the models and pooled the results to generate the final model coefficients and parameters.
-
-The results of the data imputation exercise differed between the two datasets.
-For the analyses using the smaller, racial polarization dataset, the results from the imputed data resulted in a smaller magnitude of the coefficient on the main independent variable, and also made it statistically insignificant in the main model specification.
-This suggests that the segregation index may not have as strong of a positive association with political polarization as @trounstine_segregation_2016 suggests.
-However, for the analyses using the much larger financial segregation dataset, the results of the models using the multiply imputed data largely mirrored the results of @trounstine_segregation_2016, and the coefficients and significance levels were essentially the same between the two, with the standard errors on the model estimates being generally slightly lower for the analyses using the imputed data.
-This provides strong support for @trounstine_segregation_2016's finding that residential racial segregation is associated with diminshed spending on public goods.
-
-The replication exercise and robustness check using multiply imputed data here provide strong evidence that residential segregation along racial lines does in fact correlate negatively with spending on a variety of public goods.
-What my analysis calls more into question, is by what mechanism this happens.
-Using the multiply imputed data, I still found some evidence that segregation may be associated with increased political polarization which @trounstine_segregation_2016 suggests may lead to diminished public goods spending; however, the effect size is much smaller than that found in @trounstine_segregation_2016, and some of the results have become insignificant.
-It is possible that other mechanisms may be more important in explaining why segregation might be associated with decreased spending on public goods.
-For example, it could be that there is an important interaction effect between income and segregation, as others have previously suggested, or there could be some other intervening mechanism or a confounding variable that is leading to the negative association between segregation and lower spending on public goods.
-@trounstine_segregation_2016 has identified an important relationship between segregation and the provision of public goods.
-However, my analysis suggests that further research is needed to assess the potential mechanisms by which residential segregation by race or even a confounding variable may result in dimished spending.
-If this mechanism can be better understood, than it will be possible to more effectively understand and address the underprovision of public goods, which may inhibit social mobility and unfairly disadvantage certain groups.
-
-# Appendix
-
-```{r felm, eval = FALSE}
-
-# Main Analysis 2
-
-## regression 1 Table 2
-
-# The following is a fixed effects model regression with clustering around
-# geo_id2. It mandates that total census tracts in the city is greater than 1,
-# which we want because our measure of evenness of racial spread is constant for
-# cities with only one tract by our definition (which requires comparing tracts
-# within cities). It also mandates that Direct General Expenditures (DGE) per
-# capita, CPI adjusted is not equal to 0, which would be problematic and
-# indicate a potential data error. This regression regresses the DGE per capita
-# on the the two-group calculation of  Theil's H interpolated. Controls are
-# included for diversity and the % populations of Blacks, Asians, and Latinos to
-# help identify whether it is actually diversity that drives down spending.These
-# demographic controls also help to account for the fact that whites and
-# minorities tend to perfer different levels of government spending in general.
-# This will help isolate the effects of segregation v. other forms of diversity
-# on public spending. Other controls for Median household income, CPI adjusted,
-# percent over 65, percent college grads, percent local government workers, log
-# population help control for additional factors related to segregation and
-# expenditure. Controls for percent renters interpolated and Median household
-# income also help to control for the general wealth of cities, which could be a
-# potential driver of public spending. Fixed effects for cities are also
-# included  so that the author can examine the effect of segregation in the same
-# city over  time, which also helps control for many other factors not otherwise
-# taken into account (such as city age)
-
-# apply the conditions in Stata regression
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-# felm(y~x | factor(fe1) + factor(fe2) | 0 | clustervar)
-
-felm1 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-## regression 2 Table 2
-
-# This regression is the same as above except instead of using diversity, a new
-# control is added for the five year changes in racial group shares. The goal
-# here is to see whether or not changes in diversity are a driving factor
-# (rather than absolute levels of diversity).
-
-felm2 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-## Regression 3 Table 2
-
-# Column 3
-
-# As in column 3 of table 1, this regression simply adds in a control for  mean  ideology of city residents from General Social Survey (GSS) to control for the  possibility that ideology that segregated cities are more ideologically  conservative and that the conservative nature of segregated cities is what actually drives the effect.
-
-felm3 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-```
-
-```{r main_fp_tables, results = "asis", eval = FALSE}
-
-# create main table for table 3
-
-table2 <- stargazer(felm1, felm2, felm3, omit = c("year", "south", "midwest", "west"), 
-                    header = FALSE,
-                    title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures}")
-
-```
-
-```{r, eval = FALSE}
-
-# Main Analysis 3
-
-## regression 1 Table 3
-
-# Column 1
-
-# The following is a fixed effects model regression with clustering once again around geo_id2.
-Again, the if statements at the end mandate that total census tracts in the city is greater than 1, which we want because our measure of evenness of racial spread is constant for cities with only one tract by our definition (which requires comparing tracts within cities).
-They also mandate that the highways per capita, CPI adjsuted with no cap extend (lagged 5 years) is not equal to 0, which would be problematic and indicate a potential data error.
-The dependent variable here is highways per capita, CPI adjsuted with no cap extend (lagged 5 years) and it is regressed on the two group calculation of Theil's H, interpolated.
-Controls are added for diversity, percent population of Blacks, Asians, and Latinos, and median household CPI adjusted income as well as for % local government worker hundreds, percent rentership, percent over 65, percent college graduates, and the log of the population.
-This essentially examines the effect of segregation on the specific public good of highways.
-As in the previous table's regressions, fixed effects for cities are also included so that the author can examine the effect of segregation in the same city over time, which also helps control for many other factors not otherwise taken into account (such as city age) *
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), highwayspercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_1 <- felm(highwayspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-## regression 2 Table 3
-
-# Column 2
-
-# This is the same regression as column 1, but this time the dependent variable
-# is police per capita, CPI adjusted with no cap extend. This essentially
-# examines the effect of segregation on the specific public good of police per
-# capita.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), policepercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_2 <- felm( policepercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 3
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), parkspercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-# This is again the same regression, but this time the dependent variable is
-# parks per capita, CPI adjusted with no cap extend. This essentially examines
-# the effect of segregation on the specific public good of parks.
-
-felm2_3 <- felm(parkspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 4
-
-# This is again the same regression, but this time the dependent variable is
-# sewers per capita, CPI adjusted with no cap extend. This essentially examines
-# the effect of segregation on the specific public good of sewers.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), sewerspercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_4 <- felm(sewerspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 5
-
-# This is again the same regression, but this time the dependent variable is
-# Welfare, Health, Housing per capita, CPI adjusted, no cap expend. This
-# essentially examines the effect of segregation on the specific public good of
-# welfare and housing.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), welfhoushealthNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_5 <- felm(welfhoushealthNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 6
-
-# This is again the same regression, but this time the dependent variable is own
-# source of general revenue per capita, CPI adjusted. This essentially examines
-# the effect of segregation on the specific public good of own source revenue.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), genrevownpercap_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_6 <- felm(genrevownpercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-```
-
-```{r results = "asis", eval = FALSE}
-table3a <- stargazer(felm2_1, felm2_2, felm2_3, 
-          omit = c("year", "south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Public Goods A}")
-
-table3b <- stargazer(felm2_4, felm2_5, felm2_6, 
-          omit = c("year", "south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Public Goods B}")
-
-#star_sidewaystable(table3)
-```
-
-```{r iv_regs, eval = FALSE}
-
-## regression 1 Table 5
-
-# Top Row
-
-# Column 1
-
-# This is an instrumental variable regression with DGE per capita, adjusted by the CPI, as the dependent variable and total number of waterways as the instrumental variable for segregation.
-The instrument includes the log of the population in the first stage because the number of waterways is positively correlated to population and population is positively correlated with segregation.
-The control variables are the same as those in the regressions for Table 2 except for 2 changes: since the number of waterways does not change, there is no need for city fixed effects.
-Instead, we include fixed effects for the region and year.
-A lagged version of the dependent variable (dgepercap_cpilag) is added to the regressions to account for the high correlation between  observations for the same city over time and because changes in local budgets typically are incremental (NOTE: why exactly do we do this/why does it help/why not do it in the non-intstrumental regressions?).
-
-fin_seg_1 <- fin_seg %>%
-  filter(dgepercap_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-glimpse(fin_seg_1$medincinterp)
-
-# good explanation: http://eclr.humanities.manchester.ac.uk/index.php/IV_in_R
-
-# iv = ivreg(second stage regression | instrument1 + instrument2 )
-
-ivreg1 <- ivreg(dgepercap_cpi ~ H_citytract_NHW_i + dgepercap_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + dgepercap_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_1)
-
-# Column 2
-
-# this is the same regression as for column 1 but now we use the dependent variable highwayspercapNC_cpi to assess the effect of the instrumental  variable on highways per capita *
-
-fin_seg_2 <- fin_seg %>%
-  filter(highwayspercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg2 <- ivreg(highwayspercapNC_cpi ~ H_citytract_NHW_i + highwayspercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + highwayspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_2)
-
-# Column 3
-
-# this is the same regression as for column 1 but now we use the dependent variable policepercapNC_cpi to assess the effect of the instrumental variable on police per capita
-
-fin_seg_3 <- fin_seg %>%
-  filter(policepercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg3 <- ivreg(policepercapNC_cpi ~ H_citytract_NHW_i + policepercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + policepercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_3)
-
-# Column 4 this is the same regression as for column 1 but now we use the
-# dependent variable parkspercapNC_cpi to assess the effect of the instrumental
-# variable on parks per capita
-
-fin_seg_4 <- fin_seg %>%
-  filter(parkspercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg4 <- ivreg(parkspercapNC_cpi ~ H_citytract_NHW_i + parkspercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + parkspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_4)
-
-# Bottom Row
-
-# Column 1
-
-# this is the same regression as for column 1 but now we use the dependent
-# variable sewerspercapNC_cpi to assess the effect of the instrumental variable
-# on sewers per capita
-
-fin_seg_5 <- fin_seg %>%
-  filter(sewerspercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg5 <- ivreg(sewerspercapNC_cpi ~ H_citytract_NHW_i + sewerspercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + sewerspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_5)
-
-# Column 3
-
-# this is the same regression as for column 1 but now we use the dependent variable genrevownpercap_cpi to assess the effect of the instrumental variable on own source revenue per capita
-
-fin_seg_6 <- fin_seg %>%
-  filter(genrevownpercap_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg6 <- ivreg(genrevownpercap_cpi ~ H_citytract_NHW_i + genrevownpercap_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + genrevownpercap_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_6)
-
-# Column 2
-
-# this is the same regression as for column 1 but now we use the dependent
-# variable welfhoushealthNC_cpi to assess the effect of the instrumental
-# variable on welfare per capita
-
-fin_seg_7 <- fin_seg %>%
-  filter(welfhoushealthNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg7 <- ivreg(welfhoushealthNC_cpi ~ H_citytract_NHW_i + welfhoushealthNC_cpilag  + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + welfhoushealthNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_7)
-
-summary(ivreg7)
-
-```
-
-# Table 5
-
-```{r results = "asis", echo = FALSE}
-
-table5a <- stargazer(ivreg1, ivreg2, ivreg3, ivreg4,
-          omit = c("y5", "y6", "y7", "y8", "y9", "northeast", "south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach A}")
-
-table5b <- stargazer(ivreg5, ivreg6, ivreg7,
-          omit = c("y5", "y6", "y7", "y8", "y9", "northeast","south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach B}")
-```
-
-```{r import_data, include = FALSE}
-
-# make a list of the cities included in the analysis to filter out from the main
-# dataset as specified in the table
-
-cities_to_keep <- c("Austin City", "Baltimore City", "Charlotte City", "Chicago City", "Cleveland City", "Columbus City", "Dallas City", "Denver City", "Detroit City", "Houston City", "Indianapolis", "Jacksonville", "Los Angeles City", "Memphis City", "Milwaukee City", "New York City", "Oklahoma City City", "Philadelphia City", "Phoenix City", "San Antonio City", "San Diego City", "San Francisco City", "San Jose City", "Tucson City", "Washington City")
-
-# based on some investigation, the missing additional filter needed to replicate
-# appendix tables 1 and 2 is that biggest split cannot be NA. This was
-# discovered in attempting to create table 2. The number of elections with the
-# largest divides between each racial group were the same as in the table when
-# all results were included and only the summary stats differed in both tables
-# using the city and winner subset. So, I tried excluding all entries for which
-# biggestsplit was NA, and found that the resulting subset matched the
-# statistics in both tables.
-
-# create a subset of the data with the relevant cities where there is a winner
-# and the biggestsplit is not NA
-
-rp_sub <- rp %>%
-  filter(winner == 1) %>%
-  filter(cityname %in% cities_to_keep) %>%
-  filter(!(is.na(biggestsplit)))
-
-# select the relevant variables for the table
-
-rp_sub_a1 <- rp_sub %>%
-  select(biggestsplit, H_citytract_multi_i, H_citytract_NHW_i, diversityinterp, 
-         pctasianpopinterp, pctblkpopinterp, pctlatinopopinterp, medincinterp, 
-         pctrentersinterp, pctcollegegradinterp, biracial, nonpartisan, primary, 
-         logpop, whiteideology_fill2) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-# why are the exact variables H_citytract_NHW and whiteideology_fill not in the
-# data? Data variable names author uses and ones in the data don't exactly
-# match, but replication results are the same.
-
-```
-
-```{r table_a1, results="asis", echo = FALSE}
-
-# create a stargazer summary table for the relevant statistics of the racial
-# polarization data. I couldn't figure out how to change the text of the
-# statistic names at the top of the datat table. I also couldn't figure out how
-# to only not display additional digits for the income variable. May be
-# better to switch to gt for final version?
-
-stargazer(as.data.frame(rp_sub_a1),
-          omit.summary.stat = c("p25", "p75"),
-          title = "\\textbf{TABLE A1 Summary Statistics: Racial Polarization Data}",
-          column.labels = c("\\textbf{Variable}","\\textbf{Obs}", "\\textbf{Mean}", "\\textbf{Std. Dev.}", "\\textbf{Min}", "\\textbf{Max}"),
-          covariate.labels = c("Largest Racial Divide","\\emph{H} Index: Multigroup", "\\emph{H} Index: Two-Group", "Diversity", "\\% Asian", "\\% Black", "\\% Latino", "Median HH Income", "\\% Renters", "\\% College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology"),
-          no.space = TRUE,
-          header = FALSE)
-
-```
-
-```{r table_a2_data_manipulation, include = FALSE}
-
-# initialize variables to indicate if a racial divide had the biggest divide in
-# the election
-
-rp_sub$biggest_split_bw <- NA
-rp_sub$biggest_split_lw <- NA
-rp_sub$biggest_split_bl <- NA
-
-# change the NA value to 1 if the relevant divide was the biggest in the election
-
-rp_sub$biggest_split_bw[rp_sub$biggestsplit_gr == 1] <- 1
-rp_sub$biggest_split_lw[rp_sub$biggestsplit_gr == 2] <- 1
-rp_sub$biggest_split_bl[rp_sub$biggestsplit_gr == 3] <- 1
-
-# generate the dataset of summary statistics to replicate the second appendix
-# table. Group by city name and then summarize the mean H indexes. Sum the
-# number of biggest splits by racial divide for each city
-
-rp_sub_2 <- rp_sub %>%
-  group_by(cityname) %>%
-  summarise(mean_multi_H = mean(H_citytract_multi_i),
-            mean_multi_two_group = mean(H_citytract_NHW_i),
-            sum_bw = sum(biggest_split_bw, na.rm = T),
-            sum_lw = sum(biggest_split_lw, na.rm = T),
-            sum_bl = sum(biggest_split_bl, na.rm = T))
-```
-
-```{r table_a2, echo = FALSE}
-
-# create appendix table A2 to present the summary statistics for cities included
-# in racial polarization data. Efforts to make columns narrower were
-# unsuccessful, so some of the labels in the column names were changed to make
-# the table fit. I also couldn't get the title to print out without including a
-# non-Null subtitle.
-
-city_names <- c("Austin, TX", "Baltimore, MD", "Charlotte, NC", "Chicago, IL", "Cleveland, OH", "Columbus, OH", "Dallas, TX", "Denver, CO", "Detroit, MI", "Houston, TX", "Indianapolis, IN", "Jacksonville, FL", "Los Angeles, CA", "Memphis, TN", "Milwaukee, WI", "New York, NY", "Oklahoma, OK", "Philadelphia, PA", "Phoenix, AZ", "San Antonio, TX","San Diego, CA", "San Francisco, CA", "San Jose, CA", "Tucson, AZ", "Washington, DC")
-
-rp_sub_2$cityname <- city_names
-
-gt(rp_sub_2) %>%
-  tab_header(title = md("**TABLE A2 Cities Included in Racial Polarization Data**"),
-             subtitle = "Replication") %>%
-  tab_spanner(
-      label = md("**Segregation: Mean *H* Index**"),
-      columns = vars(mean_multi_H, mean_multi_two_group)) %>%
-  tab_spanner(
-      label = md("**Largest Racial Divide, Number of Elections**"),
-      columns = vars(sum_bw, sum_lw, sum_bl)) %>%
-  fmt_number(columns = vars(mean_multi_H, mean_multi_two_group),
-             decimals = 3) %>%
-  cols_label(cityname = "City Name",
-             mean_multi_H = md("Multigroup"),
-             mean_multi_two_group = md("Two-Group"),
-             sum_bw = "Black/White",
-             sum_lw = "Latino/White",
-             sum_bl = "Black/Latino") %>%
-  cols_width(
-    vars(cityname) ~ px(10),
-    TRUE ~ px(20)
-  ) %>%
-  cols_align(
-    columns = vars(cityname),
-    align = "left"
-  ) %>%
-  tab_options(
-    table.margin.left = px(5), 
-    table.margin.right = px(5),
-    data_row.padding = px(1),
-    table.width = pct(90)
-  )
-
-```
-
-```{r include = FALSE, include = FALSE}
-
-# basic filter for table for all regressions
-
-# xtreg dgepercap_cpi H_citytract_NHW_i diversityinterp pctblkpopinterp
-# pctasianpopinterp pctlatinopopinterp medinc_cpi pctlocalgovworker_100
-# pctrentersinterp pctover65 pctcollegegradinterp logpop if totaltracts>1 &
-# dgepercap_cpi~=0,fe vce(cluster geo_id2)
-
-fin <-fin_seg %>%
-  filter(totaltractsf >1 | is.na(totaltractsf)) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
-
-# create dge variable used in regression
-
-fin_dge <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_dge_tab <- tibble(
-  Variable = "Direct General Expenditure per Capita",
-  Obs = nrow(fin_dge),
-  Mean = mean(fin_dge$dgepercap_cpi, na.rm = T),
-  SD = sd(fin_dge$dgepercap_cpi, na.rm = T),
-  Min = min(fin_dge$dgepercap_cpi, na.rm = T),
-  Max = max(fin_dge$dgepercap_cpi, na.rm = T)
-)
-
-print(fin_dge_tab)
-
-# creat summary for highways
-fin_hw <-fin %>% filter(highwayspercapNC_cpi != 0)
-
-fin_hw_tab <- tibble(
-  Variable = "Highways per Capita",
-  Obs = nrow(fin_hw),
-  Mean = mean(fin_hw$highwayspercapNC_cpi, na.rm = T),
-  SD = sd(fin_hw$highwayspercapNC_cpi, na.rm = T),
-  Min = min(fin_hw$highwayspercapNC_cpi, na.rm = T),
-  Max = max(fin_hw$highwayspercapNC_cpi, na.rm = T)
-)
-
-print(fin_hw_tab)
-
-a3_final <- full_join(fin_dge_tab, fin_hw_tab)
-
-# parks
-
-fin_park <-fin %>% filter(parkspercapNC_cpi != 0)
-
-fin_park_tab <- tibble(
-  Variable = "Parks per Capita",
-  Obs = nrow(fin_park),
-  Mean = mean(fin_park$parkspercapNC_cpi, na.rm = T),
-  SD = sd(fin_park$parkspercapNC_cpi, na.rm = T),
-  Min = min(fin_park$parkspercapNC_cpi, na.rm = T),
-  Max = max(fin_park$parkspercapNC_cpi, na.rm = T)
-)
-
-print(fin_park_tab)
-
-a3_final <- full_join(a3_final, fin_park_tab)
-
-# police
-
-fin_police <-fin %>% filter(policepercapNC_cpi != 0)
-
-fin_police_tab <- tibble(
-  Variable = "Police per Capita",
-  Obs = nrow(fin_police),
-  Mean = mean(fin_police$policepercapNC_cpi, na.rm = T),
-  SD = sd(fin_police$policepercapNC_cpi, na.rm = T),
-  Min = min(fin_police$policepercapNC_cpi, na.rm = T),
-  Max = max(fin_police$policepercapNC_cpi, na.rm = T)
-)
-
-print(fin_police_tab)
-
-a3_final <- full_join(a3_final, fin_police_tab)
-
-# sewers
-
-fin_sew <-fin %>% filter(sewerspercapNC_cpi != 0)
-
-fin_sew_tab <- tibble(
-  Variable = "Sewers per Capita",
-  Obs = nrow(fin_sew),
-  Mean = mean(fin_sew$sewerspercapNC_cpi, na.rm = T),
-  SD = sd(fin_sew$sewerspercapNC_cpi, na.rm = T),
-  Min = min(fin_sew$sewerspercapNC_cpi, na.rm = T),
-  Max = max(fin_sew$sewerspercapNC_cpi, na.rm = T)
-)
-
-print(fin_sew_tab)
-
-a3_final <- full_join(a3_final, fin_sew_tab)
-
-# welfare
-
-fin_welfare <-fin %>% filter(welfhoushealthNC_cpi != 0)
-
-fin_welfare_tab <- tibble(
-  Variable = "Welfare, Health, and Housing per Capita",
-  Obs = nrow(fin_welfare),
-  Mean = mean(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
-  SD = sd(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
-  Min = min(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
-  Max = max(fin_welfare$welfhoushealthNC_cpi, na.rm = T)
-)
-
-print(fin_welfare_tab)
-
-a3_final <- full_join(a3_final, fin_welfare_tab)
-
-# own source revenue
-
-fin_own <-fin %>% filter(genrevownpercap_cpi != 0)
-
-fin_own_tab <- tibble(
-  Variable = "Own Source Revenue per Capita",
-  Obs = nrow(fin_own),
-  Mean = mean(fin_own$genrevownpercap_cpi, na.rm = T),
-  SD = sd(fin_own$genrevownpercap_cpi, na.rm = T),
-  Min = min(fin_own$genrevownpercap_cpi, na.rm = T),
-  Max = max(fin_own$genrevownpercap_cpi, na.rm = T)
-)
-
-print(fin_own_tab)
-
-a3_final <- full_join(a3_final, fin_own_tab)
-
-# two group H
-
-fin_h <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_h_tab <- tibble(
-  Variable = "Two-Group H Index",
-  Obs = nrow(fin_h),
-  Mean = mean(fin_h$H_citytract_NHW_i, na.rm = T),
-  SD = sd(fin_h$H_citytract_NHW_i, na.rm = T),
-  Min = min(fin_h$H_citytract_NHW_i, na.rm = T),
-  Max = max(fin_h$H_citytract_NHW_i, na.rm = T)
-)
-
-print(fin_h_tab)
-
-a3_final <- full_join(a3_final, fin_h_tab)
-
-# Diversity
-
-fin_div <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_div_tab <- tibble(
-  Variable = "Diversity",
-  Obs = nrow(fin_div),
-  Mean = mean(fin_div$diversityinterp, na.rm = T),
-  SD = sd(fin_div$diversityinterp, na.rm = T),
-  Min = min(fin_div$diversityinterp, na.rm = T),
-  Max = max(fin_div$diversityinterp, na.rm = T)
-)
-
-print(fin_div_tab)
-
-a3_final <- full_join(a3_final, fin_div_tab)
-
-# % black
-
-fin_pctblk <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pctblk_tab <- tibble(
-  Variable = "%  Black",
-  Obs = nrow(fin_pctblk),
-  Mean = mean(fin_pctblk$pctblkpopinterp, na.rm = T),
-  SD = sd(fin_pctblk$pctblkpopinterp, na.rm = T),
-  Min = min(fin_pctblk$pctblkpopinterp, na.rm = T),
-  Max = max(fin_pctblk$pctblkpopinterp, na.rm = T)
-)
-
-print(fin_pctblk_tab)
-
-a3_final <- full_join(a3_final, fin_pctblk_tab)
-
-# % asian
-
-fin_pcta <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pcta_tab <- tibble(
-  Variable = "%  Asian",
-  Obs = nrow(fin_pcta),
-  Mean = mean(fin_pcta$pctasianpopinterp, na.rm = T),
-  SD = sd(fin_pcta$pctasianpopinterp, na.rm = T),
-  Min = min(fin_pcta$pctasianpopinterp, na.rm = T),
-  Max = max(fin_pcta$pctasianpopinterp, na.rm = T)
-)
-
-print(fin_pcta_tab)
-
-a3_final <- full_join(a3_final, fin_pcta_tab)
-
-# % latino
-
-fin_pctla <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pctla_tab <- tibble(
-  Variable = "%  Latino",
-  Obs = nrow(fin_pctla),
-  Mean = mean(fin_pctla$pctlatinopopinterp, na.rm = T),
-  SD = sd(fin_pctla$pctlatinopopinterp, na.rm = T),
-  Min = min(fin_pctla$pctlatinopopinterp, na.rm = T),
-  Max = max(fin_pctla$pctlatinopopinterp, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_pctla_tab)
-
-# 5y black
-
-fin_chng5pctblk <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))
-
-nrow(fin_chng5pctblk)
-
-fin_chng5pctblk_tab <- tibble(
-  Variable = "5Y Change, % Black",
-  Obs = nrow(fin_chng5pctblk),
-  Mean = mean(fin_chng5pctblk$chng5pctblk, na.rm = T),
-  SD = sd(fin_chng5pctblk$chng5pctblk, na.rm = T),
-  Min = min(fin_chng5pctblk$chng5pctblk, na.rm = T),
-  Max = max(fin_chng5pctblk$chng5pctblk, na.rm = T)
-)
-
-print(fin_chng5pctblk_tab)
-
-a3_final <- full_join(a3_final, fin_chng5pctblk_tab)
-
-# 5y latino
-
-fin_chng5pctlatino <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))
-
-fin_chng5pctlatino_tab <- tibble(
-  Variable = "5Y Change, % Latino",
-  Obs = nrow(fin_chng5pctlatino),
-  Mean = mean(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
-  SD = sd(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
-  Min = min(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
-  Max = max(fin_chng5pctlatino$chng5pctlatino, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_chng5pctlatino_tab)
-
-# 5y asian
-
-fin_chng5pctasian <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))
-
-fin_chng5pctasian_tab <- tibble(
-  Variable = "5Y Change, % Asian",
-  Obs = nrow(fin_chng5pctasian),
-  Mean = mean(fin_chng5pctasian$chng5pctasian, na.rm = T),
-  SD = sd(fin_chng5pctasian$chng5pctasian, na.rm = T),
-  Min = min(fin_chng5pctasian$chng5pctasian, na.rm = T),
-  Max = max(fin_chng5pctasian$chng5pctasian, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_chng5pctasian_tab)
-
-# median income
-
-fin_med <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_med_tab <- tibble(
-  Variable = "Median Income",
-  Obs = nrow(fin_med),
-  Mean = mean(fin_med$medinc_cpi, na.rm = T),
-  SD = sd(fin_med$medinc_cpi, na.rm = T),
-  Min = min(fin_med$medinc_cpi, na.rm = T),
-  Max = max(fin_med$medinc_cpi, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_med_tab)
-
-# % local gov. employees
-
-fin_pctlocal <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pctlocal_tab <- tibble(
-  Variable = "% Local Gov. Employees",
-  Obs = nrow(fin_pctlocal),
-  Mean = mean(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
-  SD = sd(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
-  Min = min(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
-  Max = max(fin_pctlocal$pctlocalgovworker_100, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_pctlocal_tab)
-
-# % renters
-
-fin_rent <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_rent_tab <- tibble(
-  Variable = "% Renters",
-  Obs = nrow(fin_rent),
-  Mean = mean(fin_rent$pctrentersinterp, na.rm = T),
-  SD = sd(fin_rent$pctrentersinterp, na.rm = T),
-  Min = min(fin_rent$pctrentersinterp, na.rm = T),
-  Max = max(fin_rent$pctrentersinterp, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_rent_tab)
-
-# % over 65
-
-fin_65 <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_65_tab <- tibble(
-  Variable = "% Over 65",
-  Obs = nrow(fin_65),
-  Mean = mean(fin_65$pctover65, na.rm = T),
-  SD = sd(fin_65$pctover65, na.rm = T),
-  Min = min(fin_65$pctover65, na.rm = T),
-  Max = max(fin_65$pctover65, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_65_tab)
-
-# % college degree
-
-fin_college <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_college_tab <- tibble(
-  Variable = "% College Degree",
-  Obs = nrow(fin_college),
-  Mean = mean(fin_college$pctcollegegradinterp, na.rm = T),
-  SD = sd(fin_college$pctcollegegradinterp, na.rm = T),
-  Min = min(fin_college$pctcollegegradinterp, na.rm = T),
-  Max = max(fin_college$pctcollegegradinterp, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_college_tab)
-
-# pop logged
-
-fin_logpop <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_logpop_tab <- tibble(
-  Variable = "Population (logged)",
-  Obs = nrow(fin_logpop),
-  Mean = mean(fin_logpop$logpop, na.rm = T),
-  SD = sd(fin_logpop$logpop, na.rm = T),
-  Min = min(fin_logpop$logpop, na.rm = T),
-  Max = max(fin_logpop$logpop, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_logpop_tab)
-
-# city ideology
-
-fin_ideo <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(ideology_fill)))
-
-nrow(fin_ideo)
-
-fin_ideo_tab <- tibble(
-  Variable = "City Ideology",
-  Obs = nrow(fin_ideo),
-  Mean = mean(fin_ideo$ideology_fill, na.rm = T),
-  SD = sd(fin_ideo$ideology_fill, na.rm = T),
-  Min = min(fin_ideo$ideology_fill, na.rm = T),
-  Max = max(fin_ideo$ideology_fill, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_ideo_tab)
-
-# population
-fin_population <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_population_tab <- tibble(
-  Variable = "Population",
-  Obs = nrow(fin_population),
-  Mean = mean(fin_population$population, na.rm = T),
-  SD = sd(fin_population$population, na.rm = T),
-  Min = min(fin_population$population, na.rm = T),
-  Max = max(fin_population$population, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_population_tab)
-
-```
-
-```{r, echo = FALSE}
-gt(a3_final) %>%
-    tab_header(title = md("**TABLE A3 Summary Statistics: Census of Government Finance and Population**"),
-             subtitle = "") %>%
-    fmt_number(columns = vars(Mean, SD, Min, Max),
-             decimals = 3) %>%
-    cols_label(Obs = md("**Obs**"),
-               Mean = md("**Mean**"),
-               SD = md("**SD**"),
-               Min = md("**Min**"),
-               Max = md("**Max**")
-                        ) 
-```
-
-# Bibliography
+# number missing now: 222957
+282334 - 222957
+
+73119-13742
+
+# we were able to increase sample size by 59,377
+
+miss_var_summary(complete(imp_2_fs))
+
+```

### 2020-04-28 m8_turn_in.Rmd
initial commit with new repo

--- 2020-04-28 final_extension.Rmd
@@
 ---
-title: "Final Extension"
+title: "Milestone 8: To Turn In"
 author: "Maria Burzillo"
@@
 
-# Extension
+# Abstract
 
-```{r setup, include = FALSE}
-
-# import both datasets
-library(haven)
-rp <- read_dta("racial_polarization_winners.dta")
-fin_seg<- read_dta("fin_seg.dta")
-
-# calculate number of original observations
-obs_fin_seg <- nrow(fin_seg)
-obs_rp <- nrow(rp)
-
-```
-
-One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data values in her original datasets.
-Because both R and Stata drop any observations with missing values for any of the variables used in a regression, this can exlcude a large portion of the data from the analysis and potentially bias the results if the data is not missing completely at random.
-A large amount of data is missing in both of the main datasets used in the analyses of @trounstine_segregation_2016.
-The main model specification using the racial polarization dataset exludes `r (obs_rp - 91)` of the original  `r obs_rp` observations, or  %`r round(100*(obs_rp - 91)/obs_rp,2)` of the data.
-Additionally, the main model specification using the financial segregation data set excludes `r obs_fin_seg - 13742` of the original `r obs_fin_seg` observations, or %`r round(100*(obs_fin_seg - 13742)/ obs_fin_seg,2)` of observations from the original dataset.
-
-In an attempt to better deal with the problem of missing data in @trounstine_segregation_2016, I impute missing values in the original data using the mice package in R, which generates multivariate imputations using chained equations [@mice].
-While there are a variety of different imputation methods that could have been employed, multiple imputation (such as the multiple multivariate imputations generated by mice) is desireable because instead of inputting a single value such as the mean for missing values, it instead uses the distribution of the available data to estimate multiple potential values for the missing data.
-As a result, multiple imputation helps to account for the uncertainty inherent in the imputation process and allows for the calculation of standard errors around estimaotrs.
-As a result, multiple imputation allows the researcher to more accurately assess the of uncertainty in the analysis in general.
-
-Before performing the multiple imputations on the datasets, I first examined the missing data for patterns.
-To better understand any potential patterns in missing data, I plotted the pattern of missingness for only and created a histogram showing the frequency of missing values for those variables with missing values in figure X1 for the racial polarization data and figure X2 for the financial segregation data.
-Looking at figure X1, the histogram shows that the variables for the largest vote split along racial lines and the variable indicating whether or not the election had candidates of more than one race had by far the largest percentages of missing data, missing %`r round(sum(is.na(rp$biggestsplit))/nrow(rp)*100,2)` and  %`r round(sum(is.na(rp$biracial))/nrow(rp)*100,2)`, respectively.
-It is important to note that the variable for the largest vote split along racial lines is the dependent variable in the regresison analysis, and thus, we are missing a large percentage of this key variable.
-From the plot on the right, we can see that approximately 42% of observations are complete (have no missing values).
-There seem to be a correspondence between missing a value for biggest split and missing biracial.
-There also seem to be about 2% of values for wich most of the variables are missing.
-However, most observations are not missing more than 2-3 values.
-
-### need to fix numbers below because this was from the whole fin_seg and not from the one filtered via the regression coefficients
-
-In figure X2, we can similarly observe the trends for the financial segregation dataset.
-In this dataset, there is a very high proportion of missing variables for a number of variables.
-For example, there are a `r sum(is.na(fin_seg$H_citytract_NHW_i))` missing values for the segregation index, which is the main independent variable, or %`r round(sum(is.na(fin_seg$H_citytract_NHW_i))/nrow(fin_seg)*100,2)` of the data.
-
-Then, I use the imputed datasets to re-estimate the original models, pooling the results to final pooled regression coefficients and parameters.
-
-One aspect of Trounstine's paper with room for improvement is that there is a large amount of missing data in her datasets upon which she bases her analyses.
-Using R's mice package (add citation), we can perform multiple imputation.
-By performing imputation multiple times, this helps account for the uncertainty inherent in the individual imputations.
-Before performing the multiple imputations, we will first look at the missing data to see if there are any patterns.
-
-for all of the variables in the racial polarization data used in the analysis and for the main independent variable, the segregation index, used in the analysis with the financial segregation dataset.
-More of the data could not be imputed from the financial segregation dataset due to computing and time constraints for this project.
+This is an extension of Jessica Trounstine's "Segregation and Inequality in Public Goods" (2016).
+I was able to replicate the main results of Trounstine's paper in R to suggest that racial segregation contributes to political polarization and decreased spending on public goods.
+Additionally, I extend the analysis by imputing missing data and rerunning Trounstine's original model as a robustness check.
 
@@
 print(imp_1_rp_sum_table)
+
+stargazer(imp_1_rp_sum_table,
+          header = "Racial Divide with Multigroup Segregation Index",
+          title = "\\textbf{Racial Polarization in Segregated Cities}")
 

### 2020-04-28 test.Rmd
initial commit with new repo

--- 2020-04-28 Draft_1.Rmd
@@
 header_includes:
-  usepackage{float}
-  usepackage{dcolumn}
-  usepackage{rotating}
-  restylefloat{table}
+  \usepackage{float}
+  \usepackage{dcolumn}
+  \usepackage{rotating}
+  \restylefloat{table}
 
 ---
-
-# Abstract
-
-@trounstine_segregation_2016 suggests that high levels of residential segregation are associated with increased political polarization and decreased public spending.
-In this analysis, I was able to successfully replicate @trounstine_segregation_2016’s main results.
-Adding onto her original analysis, I impute a large amount of missing data from the original dataset and re-run the analysis.
-Finally, I add in income segregation as a predictor in her regressions to assess whether this could be a confounding variable.
 
@@
 
-# Introduction
+# Extension Part 2: Fin Seg Data Set
 
-There is a large degree of variation in public goods spending across local governments.
-As a result, many scholars have worked to determine what factors may lead to the underprovision of public goods spending.
-Research in the past has associated racial diversity or changes in levels of diversity with the under-provision of public goods [@baqir_public_1999; @hopkins_diversity_2009].However, @trounstine_segregation_2016 argues that it is racial segregation, not diversity in and of itself, that results in the under-provision of public goods.
-Trounstine’s analysis consists of two main parts.
-First, she uses election and demographic data from 25 of America’s largest cities between 1990 and 2010 to run a multilevel mixed-effects linear regression with fixed effects for region and year and with random effects for cities in order to show that polarization increases with segregation.
-Trounstine measures segregation with Theil's H index, which measures the degree to which the diversity of a neighborhood differs from the diversity of the entire city.
-The second main part of Trounstine’s analysis looks at the ability of the Theil’s H segregation index to explain a variety of types of public expenditures by city using a sample of 2,637 cities with 13,742 city-year observations.
-Using linear regressions with fixed effects for cities and robust standard errors clustered by city, Trounstine finds a significant, negative correlation between segregation and public goods spending that is robust to the inclusion of a variety of relevant controls and an alternative specification in which the number of waterways is used as an instrument for segregation.
+In the second, and arguably most important dataset in the analysis, the data set on financial segregation, there are a very large number of missing values.
 
-In this analysis, I first work to replicate the main results of @trounstine_segregation_2016 using R statistical software [@r].
-The original data and Stata code made publically available by the author were downloaded via the Harvard Dataverse [@DVN/4LZXTY_2015].
-I also make all of my code and analysis available on Github.^[ Link to my [Github repository](https://github.com/mburzillo/new_final_project) for this project.] I was successfully able to replicate the main results of @trounstine_segregation_2016 in R with the exception of some of the marginal analyses, which I was nevertheless able to replicate in Stata.
+```{r}
 
-```{r data_prep_imputations, include = FALSE}
-
-# select the relevant rows from the rp dataset
-
-rp_impute <- rp %>%
-  select("winner", "medincinterp",
-             "biggestsplit", "H_citytract_multi_i", "diversityinterp",
-             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
-             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
-             "primary", "logpop", "year", "south", "midwest", "west", "geo_id2",
-             "H_citytract_NHW_i", "whiteideology_fill2") %>%
-  filter(winner == 1) %>%
-  mutate(medincinterp = medincinterp/1000,
-         year.f = as.factor(year))
-
-# apply the conditions in Stata regression to the fin_seg dataset
+# apply the conditions in Stata regression
 
@@
 
-# select the relevant variables to be imputed
+# select the relevant variables
 
@@
          pctcollegegradinterp, logpop, geo_id2, chng5pctblk, chng5pctlatino, chng5pctasian,
-         ideology_fill, totaltractsf)
+         ideology_fill)
 
-miss_var_summary(fin_imp)
-miss_var_summary(rp_impute)
+#miss_var_summary(fin_imp)
+
+#gg_miss_var(fin_imp, show_pct = TRUE)
+
+#gg_miss_var(fin_imp)
 
@@
 
-```{r obs_count, include = FALSE}
-
-# calculate number of original observations
-
-obs_fin_seg <- nrow(fin_imp)
-obs_rp <- nrow(rp_impute)
-
-```
-
-One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data, which substantially constrains the sample size used in the regression analysis.
-For example, the regression analysis in the main specification using the the original racial polarization dataset exludes %`r round((obs_rp - 91)/obs_rp, 2)` of the observations, and the regression analysis in the main specification using the original financial segregation data excludes %`r round((obs_fin_seg - 13742)/ obs_fin_seg, 2)` of observations from the original dataset.
-As an extension of @trounstine_segregation_2016, I impute missing values in the original data using the mice package in R, which generates multivariate imputations using chained equations [@mice].
-Then, I use the multiply imputed datasets to re-estimate the original models, pooling the results to generate final pooled regression coefficients and parameters.
-
-Comparing the results of the original regressions and those done with the imputed data yields similar big picture results in terms of the direction of the signs on the coefficients on the segregation indices.
-Like in @trounstine_segregation_2016, I find that segregation is positively associated with political polarization and negatively associated with spending on public goods.
-However, the magnitude of the effects in most specifications has diminished and most results become statistically insignificant.
-While these findings do not necessarily challenge the results of @trounstine_segregation_2016, they do call into question the relative importance of segregation in determining public goods spending and political polarization and suggest that the results of @trounstine_segregation_2016 may not be quite as robust as once thought.
-
-# Literature Review
-
-Despite some progress made towards racial equity in the U.S.
-on other fronts, residential racial segregation continues to be prevasive and deeply entrenched in society [@fischer_distinguishing_2004; @oliver_paradoxes_2010; @massey_american_1993].
-Research suggests that this kind of segregation has political consequences, as political cleavages in segregated cities tend to have racial as well as spatial dimensions [@massey_american_1993].
-Neighborhoods are often important actors within local politics because local governments provide many functions that are allocational in nature and concern geographical space [@trounstine_segregation_2016].
-Thus, when neighborhoods are divided on racial lines as well as spacial lines, it is natural to expect higher degrees of racial polarization as a result.
-
-Studying residential segregation is difficult because its effects tend to differ by geographic level.
-On the neighborhood level, the kind of geographic racial isolation brought on by residential segregation has been associated with racial intolerance, resentment, and competition between racial groups [@oliver_paradoxes_2010].
-Living within segregated neighborhoods has also been associated with holding negative stereotypes and perceptions about out groups [@eric_oliver_intergroup_2003].
-As a result, homogeneous neighborhoods have been associated with increased racial tension and political polarization in comparison to integrated, diverse neighborhoods.
-However, at the city or metropolitan level, the opposite seems to be true: when considering larger geographic areas, diversity and integration are correlated with racial tension, competition, prejudice, lower levels of cooperation, and lower spending on public goods [@oliver_paradoxes_2010; @baqir_public_1999; @hopkins_diversity_2009].
-While these differences in the expected effect of segregation on the geographic level may seem confusing at first, they make sense as they suggest that the most severely segregated areas are those that are diverse overall, but have many homogeneous neighborhoods.
-Thus, while people of different races co-exist within a highly segregated city, they live separately within their own neighborhoods, which creates an environment ripe for racial tension [@trounstine_segregation_2016].
-It is thus not simply the level of diversity or integration that matters for racial harmony and cooperation, but their patterns within a larger geographic framework [@trounstine_segregation_2016; @oliver_paradoxes_2010; @bharathi_public_2018].
-
-Political polarization along racial lines may lead to decreased public spending and goods provision because groups may have different preferences, which can make compromise hard, and because groups may preceive a disutility in out-groups receiving public goods expenditure [@baqir_public_1999].
-@einstein_divided_2012 found evidence that racial segregation predicts large political divisions at the metropolitan level and that these divisions can create a lack of willingness to compromise and collaborate on local policy problems.
-@trounstine_segregation_2016 finds similar results at the city level: that residential racial segregation is associated with both increased political division and decreased public spending.
-Thus, these authors suggest that it is the combination of homogenous neighborhoods within a much larger, diverse geographic area that leads to increased political polarization and reduced public goods spending in local governments.
-
-More recently, some scholars have called this hypothesis and its importance into question.
-For example, @lee_ethnic_2018 finds evidence that larger inequalities within the political system favoring socially powerful groups, not local diversity patterns leading to decreased cooperation, may be a better explanation of failures in public goods provision in diverse areas.
-Others suggest that additional factors, such as income segregation, may be important confounding factors in public goods provision.
-@an_its_2018, for example, suggests that the more closely related income inequality is to racial inequality, the less investment is made in public goods, and that this interaction was a better predictor of public goods spending patterns than measures of diversity.
-There is, in fact, a variety of evidence suggesting that it is meaningful to consider the effects of income inequaltiy and diversity and segregation jointly [@an_its_2018; @massey_american_1993].
-Given the active debate in the literature over the relaitonships between diversity, segregation, public spending, and other factors, it is increasingly important to re-examine previously reported findings as a means of robustness checks.
-
-# Replication
-
-I was able to successfully replicate all of the main results from Trounstine (2016).
-All regressions and tables were fully replicated in R.
-As an example, in table X, I replicate Table 1 from page 713 of @trounstine_segregation_2016, which is also included as Figure 1 for comparison.
-However, I was unable to successfully replicate Trounstine (2016)’s marginal effects analyses and margins plots using R.
-There does not yet appear to be a built-in R function to calculate marginal or predicted effects or to generate margins plots from the complicated multi-level models employed in the original paper, and creating such a function was outside of the scope of this analysis.
-Nevertheless, these results were successfully replicated in Stata.
-
-```{r include = FALSE}
-
-## regression 1 Table 1
-
-# fixed effects like a control variable
-
-# lmer(dependent ~ predictors + (random predictors | group level))
-
-# reml v. log likelihood: default in r appears to be log-likelihood. stata defaults to maximum likelihood
-
-# perform a multi-level mixed-effects linear regression of biggest split on the multi-group H index with controls for Herfindahl Diversity Index, % Asian interpolated, % Black interpolated, % Latino interpolated, median household income interpolated, % renters interpolated, percent college grads interpolated, a dummy indicating if there were biracial candidates in the election, a dummy  indicating if the election was nonpartisan, an indicator if the election was a primary, and the log population.
-The regression also includes fixed effects for year and region and random effects for cities (geo_id2).
-Diversity is  included because of the claim that more diverse populations will have more heterogeneous political preferences.
-The other fixed effect control variables are included because they are known to be potentially correlated with segregation.
-winner == 1 requires that there was a winner in the election.
-
-# regression specification. Apply REML = FALSE. The default for lmer() in R is
-# to optimize the restricted (residual) maximum likelihood (REML) whereas in
-# xtmixed in Stata the default is to optimize the log likelihood (which you can
-# do in lmer() in R by setting REML = FALSE), so this will match the STATA code
-
-m1 <- lmer(biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-## regression 2 Table 1
-
-# Perform the same regression as for Column 1 above but this time regress on the two-group calculation of Theil's H interpolated.
-It is unclear where the "diversity" variable is coming from, as the only variable related to diversity in the specificed dataset is diversityinterp.
-This is a problem that will need to be resolved.
-Essentially, this regression just tests an alternate specification to the first in which the segregation index in defined in terms of two-groups rather than multiple.
-
-m2 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-# perform the same regression as for column 2, but now add in a measure of
-# average white political ideology. The point of this is to control for ideology
-# so that the author can separate any effects of segregation from any potential
-# effects of white political ideology. This is important because it is possible
-# that segregation is just a proxy for white conservatism and thus failure to
-# include this variable could lead to ommitted variable bias.
-
-m3 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-```
-
-```{r results="asis", echo = FALSE}
-
-# create a stargazer table of the results
-
-t1 <- stargazer(m1, m2, m3, omit = c("year", "south", "midwest", "west"),
-                header = FALSE,
-                title = "\\textbf{Racial Polarization in Segregated Cities}",
-                single.row = TRUE,
-                no.space = FALSE,
-                add.lines = list(c("Wald Chi Squarred", "a", "b", "c")),
-                omit.stat = c("ll","rsq"),
-                covariate.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Diversity", "Percent Asian", "Percent Black", "Percent Latino", "Medain HH Income (1000s)", "Percent Renters", "Percent College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology", "Constant"),
-                notes = "This table displays...")
-
-# note: "This table displays the results of the replication effort of the analyses conducted in Trounstine (2016) using the racial polarization dataset.
-The replication code can be found on my personal [Github repository](https://github.com/mburzillo/new_final_project).
-The original table is displayed for comparison as Figure 1.")
-
-```
-
-![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016.
-My replication of these results can be found in Table 1 in this paper.](table_1.png)
-
-There was one interesting outcome from my attempt to replicate the original Stata code in R.
-Due to the differences in R and Stata in dealing with missing values, the results of my first replication of analyses using the financial segregation dataset were slightly different than the results in Stata from the original paper.
-In order to exclude cities from her analysis with only one census tract, Trounstine conditions her regressions in Stata such that the value for the number of census tracts is greater than one.
-In Stata, this does not remove missing values, whereas in R, it does.
-Since this variable is used only as a conditional filter and not as a regression variable (and thus, the observations with missing values for number of census tracts are not dropped), Trounstine’s analysis includes 14 cities and 58 observations with missing values for census tracts in addition to cities with two or more census tracts.
-This is a potential oversight on the part of the author, and I would suggest also dropping observations with missing census tract data, or else imputing them given that the aim of her condition was to exclude cities without a sufficient number of census tracts.
-Nevertheless, dropping these values did not have much of an effect on the subsequent results, likely because they represent a small proportion of the overall sample.
-
-# Extension
-
-One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data values in her original datasets.
-Because both R and Stata drop any observations with missing values for any of the variables used in a regression, this can exlcude a large portion of the data from the analysis and potentially bias the results if the data is not missing completely at random.
-A large amount of data is missing in both of the main datasets used in the analyses of @trounstine_segregation_2016.
-The main model specification using the racial polarization dataset exludes `r (obs_rp - 91)` of the original  `r obs_rp` observations, or  %`r round(100*(obs_rp - 91)/obs_rp,2)` of the data.
-Additionally, the main model specification using the financial segregation data set excludes `r round(obs_fin_seg - 13742,2)` of the original `r obs_fin_seg` observations, or %`r round(100*(obs_fin_seg - 13742)/ obs_fin_seg,2)` of observations from the original dataset.
-
-In an attempt to better deal with the problem of missing data in @trounstine_segregation_2016, I impute missing values in the original data using the mice package in R, which generates multivariate imputations using chained equations [@mice].
-While there are a variety of different imputation methods that could have been employed, multiple imputation (such as the multiple multivariate imputations generated by mice) is desireable because instead of inputting a single value such as the mean for missing values, it instead uses the distribution of the available data to estimate multiple potential values for the missing data.
-As a result, multiple imputation helps to account for the uncertainty inherent in the imputation process and allows for the calculation of standard errors around estimators.
-As a result, multiple imputation allows the researcher to more accurately assess the of uncertainty in the analysis in general.
-
-Before performing the multiple imputations on the datasets, I first examined the missing data for patterns.
-To better understand any potential patterns in missing data, I plotted the pattern of missingness and created a histogram showing the frequency of missing values for those variables with missing values in figure X1 for the racial polarization data and figure X2 for the financial segregation data.
-Looking at figure X1, the histogram shows that the variables for the largest vote split along racial lines and the variable indicating whether or not the election had candidates of more than one race had by far the largest percentages of missing data, missing %`r round(sum(is.na(rp_impute$biggestsplit))/nrow(rp_impute)*100,2)` and  %`r round(sum(is.na(rp_impute$biracial))/nrow(rp_impute)*100,2)`, respectively.
-It is important to note that the variable for the largest vote split along racial lines is the dependent variable in the regresison analysis, and thus, we are missing a large percentage of this key variable.
-From the plot on the right, we can see that approximately 42% of observations are complete (have no missing values).
-There seem to be a correspondence between missing a value for the largest vote split and missing a value for the biracial election indicator.
-There also seem to be about 2% of values for wich most of the variables are missing.
-However, most observations are not missing more than 2-3 values.
-
-```{r rp_missing_plot, include = FALSE, warning = FALSE}
-
-# don't show the warning, it's just an irrelevant column missing a name
-
-# plot the missing variables if desired
-
-rp_facet <- rp_impute %>%
-   select("medincinterp",
-             "biggestsplit", "diversityinterp",
-             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
-             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
-               "south", "midwest", "west", "whiteideology_fill2", "year")
-
-# gg_miss_var(rp_impute, show_pct = TRUE)
-
-```
-
-```{r rp_aggr_plot, echo = FALSE}
-
-# select only the missing values
-
-rp_aggr <- rp_impute %>%
-   select("medincinterp",
-             "biggestsplit", "diversityinterp",
-             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
-             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
-               "south", "midwest", "west", "whiteideology_fill2")
-
-# create an aggr plot for the missing values
-
-aggr(rp_aggr, bars = TRUE, col=c('navyblue','red'), numbers=TRUE, cex.axis=.5, gap=1, ylab=c("Proporiton of Missing Values","Combinations"))
-
-# caption for this plot when I figure out how to do it...
-: This plot examines the pattern of missing data in the the original racial polarization dataset from Trounstine (2016).
-The plot on the left shows the percentage of missing data for each variable with missing data and reveals that the variables that are missing by far the most data are the largest vote split along racial lines (biggestsplit) and the variable indicating whether or not the election had candidates of more than one race (biracial).
-The plot on the right shows the pattern of missingness among the variables.
-We can see that approximately 42% of observations are complete (have no missing values).
-There seems to be a correspondence between missing a value for biggest split and missing biracial.
-There also seem to be about 2% of values for which most of the variables are missing.
-However, most observations are not missing more than 2-3 values.
-
-```
-
-In figure X2, we can similarly observe the trends for the financial segregation dataset.
-In this dataset, there is a very high proportion of missing variables for a number of variables.
-For example, there are `r sum(is.na(fin_imp$H_citytract_NHW_i))` missing values for the segregation index, which is the main independent variable, or %`r round(sum(is.na(fin_imp$H_citytract_NHW_i))/nrow(fin_imp)*100,2)` of the data.
-In this dataset, there are also many more observations for which values are missing for multiple variables in comparison to the racial polarization dataset.
-In total, a mere %`r .0058*100` of observations are complete for all variables included in the main specification for the financial segregaion dataset.
-
-```{r fin_missing_plot, include = FALSE}
-
-miss_var_summary(fin_imp)
-
-gg_miss_var(fin_imp, show_pct = TRUE)
-
-```
-
-```{r fin_aggr_plot, echo = FALSE}
+```{r eval=FALSE}
 
@@
 fin_imp_aggr <- fin_imp %>%
-  select(ideology_fill, H_citytract_NHW_i, chng5pctblk, chng5pctlatino, chng5pctasian, diversityinterp, pctblkpopinterp, pctasianpopinterp,
+  select(H_citytract_NHW_i, diversityinterp, pctblkpopinterp, pctasianpopinterp,
          pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
-         pctcollegegradinterp)
+         pctcollegegradinterp, chng5pctblk, chng5pctlatino, chng5pctasian,
+         ideology_fill)
 
-new_try <- head(fin_imp_aggr, 20)
+#aggr_plot <- aggr(fin_imp_aggr, bars = TRUE, col=c('navyblue','red'), numbers=TRUE, sortVars=TRUE, cex.axis=.5, gap=3, ylab=c("Histogram of missing data","Pattern"))
 
-aggr(new_try, plot = TRUE, bars = FALSE, col=c('navyblue','red'), numbers=TRUE)
+# this plot tells us that only .066% of the data are complete (not missing anything)
 
-# create the aggr plot
-
-aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.5, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
-title(main = "Patterns of Missingness in the Financial Segregation Data",
-      sub = "Is this a caption?
-qiufwnjekfewkfnwein\nwefjwenmf wiufnwqjenf ewfuiwjnef nfijefnwjenfkqwjnf lqwjefnjqwefjwnef winfjqwhf hjwefwiuefief welfiunqlfjnqkjwe qqfniquwenjfjq iqfnjkjeq rfiunfj q")
-
-# this plot tells us that only .58% of the data are complete (not missing anything)
-
-# caption for this plot when I figure out how to do it...
-: This plot examines the pattern of missing data in the the original financial segregation dataset from Trounstine (2016).
-The plot on the left shows the percentage of missing data for each variable with missing data and reveals that a large number of variables are missing the vast majority of data.
-The plot on the right shows the pattern of missingness among the variables.
-We can see that only .58% of observations are complete (have no missing values), and a large majority of the observations are missing data for many variables.
-
+nrow(fin_imp) * .0058
 ```
 
-Because neither dataset seems to exhibit any clear patterns in the missing, data, it makes sense to proceed with the imputation.
-For the racial polarization dataset, I performed multiple imputations with 20 iterations using mice, while for the financial segregation dataset, I performed only 5 iterations due to the large size of the dataset and computing limitaitons.
-A non-stochastic imputation method, Classification and Regression Trees (CART), was used instead of the default for the imputation for both datasets because of an error with matrix inversion caused by the data that prevented the use of the default method, predictive mean matching.
-For the racial polarization dataset, I included all of the variables used in the analysis associated with the dataset and was able to impute all missing values.
-For the financial segregation dataset, however, I only imputed values for the main independent variable, the segregation index, and a few other variables, although all variables used in the analysis were included in the data subset input into the mice function.
-More of the data could not be imputed from the financial segregation dataset due to computing and time constraints for this project given the dataset's large size and high proportion of missing values.
-
-```{r rp_imputation, include = FALSE}
-
-# Perform multiple imputations using the cart method. Because of the time it
-# takes to run this function, I turned the results into a dataset to load in
-# instead of re-running everytime.
-
-max_it = 20
-
-imp_1_rp <- mice(rp_impute, method = "cart", maxit = 20)
-
-# can use the line below to check that there are now no missing values
-
-# gg_miss_var(complete(imp_1_rp), show_pct = TRUE)
-
-```
-
-```{r fp_imputations, include = FALSE}
+```{r}
 
@@
          "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")]=""
 
@@
 
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+meth[c("H_citytract_NHW_i")] = "cart"
 
-# perform the multiple imputations with 5 iterations
+# perform 5 imputations of the data
 
-imp_fs <- mice(fin_imp, method = meth, maxit = 5)
+imp_1_fs <- mice(fin_imp, method = meth, maxit = 5)
 
-# now there are manyb fewer missing variables!!!
+gg_miss_var(complete(imp_1_fs), show_pct = T)
 
-miss_var_summary(complete(imp_fs))
-
-head(complete(imp_fs))
-
+miss_var_summary(complete(imp_1_fs))
 miss_var_summary(fin_imp)
 
-```
-
-```{r new_imp}
-
-fin_imp <- fin_imp %>%
-  mutate(nas = is.na(H_citytract_NHW_i) + is.na(dgepercap_cpi) + is.na(diversityinterp) + is.na(pctblkpopinterp)  + is.na(pctasianpopinterp) + is.na(pctlatinopopinterp) + is.na(medinc_cpi) + is.na(pctlocalgovworker_100) + is.na(pctrentersinterp) + is.na(pctover65) + is.na(pctcollegegradinterp) + is.na(logpop) + is.na(geo_id2) + is.na(chng5pctblk) + is.na(chng5pctlatino) + is.na(chng5pctasian) + is.na(logpop) + is.na(geo_id2) + is.na(chng5pctblk) + is.na(chng5pctlatino) + is.na(chng5pctasian) + is.na(ideology_fill))
-
-fin_imp %>%
-  ggplot(aes(x = nas)) +
-  geom_histogram()
-
-fin_imp %>%
-  group_by(nas) %>%
-  summarise(n())
-
-# exclude all observations with 17 out of 22 nas
-
-fin_imp_sub <- fin_imp %>%
-  filter(nas < 17)
-
-nrow(fin_imp_sub)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_sub, maxit=0, print=F)
-
-# view the current method settings
+# another try
 
@@
 
+# other
+
+other <- c("chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")
+
 # change the default method to "cart" so that we don't get the error
@@
 
-# perform the multiple imputations with 5 iterations
+#imp_2_fs <- mice(fin_imp, method = meth, maxit = 5)
 
-new_imp_fs <- mice(fin_imp_sub, method = meth, maxit = 5)
+# now there are manyb fewer missing variables!!!
 
-miss_var_summary(complete(new_imp_fs))
-```
+#miss_var_summary(complete(imp_2_fs))
 
-## make sure to talk about the fact that still a large number of values missing for the imputed variables here
-
-Before examining the results of Trounstine's model using the multiply imputed data, I first ran some diagnostic tests on the imputation results to make sure that everything ran as expected.
-First, I checked the convergence of the algorithm used within mice() by plotting the trace lines as a function of the number of iterations for each of the variables.
-Then, I visually inspected the distributions of the imputed data in comparison to the original data with density and strip plots.
-All of these checks suggested that the imputed values were within a plausible range of the data and that their distribution fit the underlying distribution of the data relatively well.
-The only cases in which there was some cause for concern were for some of the variables with very few missing values in the racial polarization dataset (such as the indicators for region).
-However, this is more or less to be expected given the small number of imputations performed in these cases.
-Thus, and especially because there are so few of these values missing in the actual datasets, this was not a major concern.
-See figures X and X1 to see the density plots of the imputed values overlayed on the density plots of the original variables.
-The rest of the plots and results of the diagnostic tests discussed here are presented in the Appendix.
-
-```{r rp_densityplot, echo = FALSE}
-
-densityplot(imp_1_rp)
+#head(complete(imp_2_fs))
 
@@
 
-```{r rp_imp_plot, include = FALSE}
+Finding no clear patterns in the missing data, I next performed mutliple imputations (with 5 iterations) on the dataset.
+A non-stochastic imputation method, Classification and Regression Trees (CART), was used instead of the default because of an error with matrix inversion caused by the data.
+Before examining the results of Trounstine's model using the imputed data, I first run some diagnostic tests of the imputation results to make sure that everything is running as expected.
+
+First, I check the convergence of the algorithm used within mice() for each of the variables. For the most part, the fits intertwine and do not exhibit any trends at later iterations, as desired.
+
+```{r imp_plot, echo = FALSE}
 
@@
 
-plot(imp_1_rp)
+#plot(imp_1_fs)
 
@@
 
-stripplot(imp_1_rp)
-
-stripplot(imp_1_rp, biggestsplit)
+#stripplot(x = imp_1_fs, data = ~H_citytract_NHW_i)
 
@@
 
-```{r fs_densityplot, echo = FALSE}
+Finally, we can also look at the density plots for each variable's actual data and for their imputed data from each of the iterations, which are represented in magenta.
+Overall, the density plots align quite well for the variables with the most missing data, biracial and biggestsplit, and relatively well for most of the other variables with missing data.
+Again, the fit is less good for variables with fewer missing data points.
 
-densityplot(imp_fs)
-densityplot(x=imp_fs , data= ~ H_citytract_NHW_i + chng5pctblk + 
-       chng5pctlatino + chng5pctasian + ideology_fill)
+```{r rp_densityplot, echo = FALSE}
 
+#densityplot(x=imp_1_fs, data= ~ H_citytract_NHW_i)
 ```
 
-```{r fs_imp_plot, include = FALSE}
+While the imputations are not perfect, there do not seem to be any major problems so far.
+Thus, we can now proceed with our analysis.
+We fit each of our ten imputed datasets to Trounstine's 3 models using this data and then pool the results for each.
+The results are as follows:
 
-# ideally, the fits will intertwine and not exhibit any trends at later iterations.
-This seems to generally be the case.
-There are some issues with the results for some of the variables with very few missing values, which makes sense as we would expect the mean to be less reliable due to the law of large numbers and thus convergence is more difficult.
-However, since these are so few values, it is less important about how robust they are.
-
-plot(imp_fs)
-
-```
-
-```{r fs_stripplot, include = FALSE}
-
-# we can also check the imputed values against the original values using stripplot().
-Each column in each subplot represents a separate iteration.
-The magenta points represent the imputed data.
-The values of the variable in questions are along the y axis.
-We expect the spread of the data to be similar if the imputations were done well.
-If the data were missing completely at random, then the imputed data should have the same distribution as the original data.
-In particular, we want to be sure that the imputations are within a plausible range of the data.
-This is the case for all of our imputed variables, and there does not seem to be cause for alarm from these results.
-
-# this looks good? All reasonable values...
-
-stripplot(imp_fs, H_citytract_NHW_i)
-
-stripplot(imp_fs, chng5pctblk)
-
-stripplot(imp_fs, chng5pctlatino)
-
-stripplot(imp_fs, chng5pctasian)
-
-stripplot(imp_fs, ideology_fill)
-
-```
-
-Given the promising results of the diagnostic checks, I next proceeded to re-estimate the original model using the multiply imputed datasets, pooling the results to produce final pooled regression coefficients and parameters.
-The results for the analyses using the racial polarization dataset are presented in tables 1-3.
-
-```{r rp_imputations, include = FALSE}
-
-# Now that we have imputed the missing data, we can re-run the analyses from the
-# original paper to see how and if this changes the analysis. We can use the
-# with() function from the mice package to fit each of the imputed datasets to
-# the model and then pool the results afterwards.
-
-# regression 1: fit multiple imputed datasets
-
-fit_imp_1_rp <- with(imp_1_rp, lmer(formula = biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
-
-# pool and summarize the analyses
-
-pool_imp_1_rp <- pool(fit_imp_1_rp)
-imp_1_rp_sum <- summary(pool_imp_1_rp)
-
-## regression 2 Table 1: fit multiple imputed datasets
-
-#formula = biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2)
-
-fit_imp_2_rp <- with(imp_1_rp, lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
-
-# pool and summarize the analyses
-
-pool_imp_2_rp <- pool(fit_imp_2_rp)
-imp_2_rp_sum <- summary(pool_imp_2_rp)
-
-## regression 3 Table 1 with new data
-
-#formula = biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2)
-
-fit_imp_3_rp <- with(imp_1_rp, lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
-
-# pool and summarize the analyses
-
-pool_imp_3_rp <- pool(fit_imp_3_rp)
-imp_3_rp_sum <- summary(pool_imp_3_rp)
-
-```
-
-The results of the model with the new dataset are slightly different in comparison to the original results from Trounstine (2016).
-With the imputed data, we now have a total of `r nrow(complete(rp_impute))` observations in our model as compared to the original model, which had only 91 observations.
-Interestingly, while the sign of the coefficient on the main variable of interest, the Theil's H segregation index, is the same and the standard error has decreased slightly, the result has become statisically insignificant and the 95% confidence interval contains zero.
-Thus while these results still suggest that segregation may be associated with increased political polarization, they confer a lesser degree of certainty than Trounstine's original analysis.
-The coefficients for % Black population, % Latino population, and median household income have also switched signs, and all coefficients except the indicator for a biracial election are also statistically insignificant, as was the case in the original analysis.
-The coefficient on the indicator for a primary election, has also changed from being significant in the original analysis to insignificant here.
-In general, the standard errors on the coefficients have decreased slightly.
-
-```{r results_printing_rp_impute_regressions_1, results = "asis", echo=FALSE}
-
-# print results of 1st regression
-
-imp_1_rp_sum_table <- as.data.frame(imp_1_rp_sum %>% 
-  select(term, estimate, std.error, p.value)) %>%
-  head(13)
-print(imp_1_rp_sum_table)
-
-stargazer(imp_1_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Multigroup Segregation Index}")
-
-```
-
-In the second and third regressions, the results are similar.
-The main coefficient on segregation index has decreased in magnitude, although in these specifications, it remains statistically significant.
-The other coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian, Black, and Latino have all switched signs.
-Standard errors have also reduced slightly in these specifications compared to the original analysis in @trounstine_segregation_2016.
-
-```{r results_printing_rp_impute_regressions_2, results = "asis", echo=FALSE}
-
-# print results of 2nd regression
-
-imp_2_rp_sum_table <- as.data.frame(imp_2_rp_sum %>% 
-  select(term, estimate, std.error, p.value)) %>%
-  head(13)
-print(imp_2_rp_sum_table)
-
-stargazer(imp_2_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Two-Group Segregation Index}")
-
-```
-
-```{r results_printing_rp_impute_regressions_3, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_3_rp_sum_table <- as.data.frame(imp_3_rp_sum %>% 
-  select(term, estimate, std.error, p.value)) %>%
-  head(13)
-print(imp_3_rp_sum_table)
-
-stargazer(imp_3_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Ideology Control}")
-```
-
-For the financial segregation dataset, we similarly fit each of our 5 imputed datasets to the original models from @trounstine_segregation_2016 using this data and then pool the results for each.
-The pooled results are presented in tables 4-6.
-
-# FS data results
-
-```{r fs_imputed_pooled_regressions, include = FALSE}
+```{r}
 # Main Analysis 2: Imputations
@@
 
-fit_imp_felm1 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+fit_imp_felm1 <- with(imp_1_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
 
@@
 
-fit_imp_felm2 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+fit_imp_felm2 <- with(imp_1_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
 
@@
 
-fit_imp_felm3 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))
+fit_imp_felm3 <- with(imp_1_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))
 
@@
 
-```{r fs_imputed_data_included_calc, include = FALSE}
+## Regression 1
+
+The results of the first regression indicate that Trounstine's results are robust to the inclusion of the imputed data.
+The coefficients, standard errors, and significance levels are essentially unchanged.
+The same is largely true for the second and third specifications, but the magnitude of the coefficient on the segregation decreases by a marginal amount.
+
+```{r results_printing_fs_impute_regressions_1, echo=FALSE}
+
+# print results of 3rd regression
+
+imp_felm1_sum_table <- as.data.frame(imp_felm1_sum %>% 
+  select(term, estimate, std.error, p.value))
+print(imp_felm1_sum_table)
+```
+
+Despite some progress made towards racial equity in the U.S.
+on other fronts, residential racial segregation continues to be prevasive and deeply entrenched in society [@fischer_distinguishing_2004; @oliver_paradoxes_2010; @massey_american_1993].
+Research suggests that this kind of segregation has political consequences, as political cleavages in segregated cities tend to have racial as well as spatial dimensions [@massey_american_1993].
+Neighborhoods are often important actors within local politics because local governments provide many functions that are allocational in nature and concern geographical space [@trounstine_segregation_2016].
+Thus, when neighborhoods are divided on racial lines as well as spacial lines, it is natural to expect higher degrees of racial polarization as a result.
+
+Studying residential segregation is difficult because its effects tend to differ by geographic level.
+On the neighborhood level, the kind of geographic racial isolation brought on by residential segregation has been associated with racial intolerance, resentment, and competition between racial groups [@oliver_paradoxes_2010].
+Living within segregated neighborhoods has also been associated with holding negative stereotypes and perceptions about out groups [@eric_oliver_intergroup_2003].
+As a result, homogeneous neighborhoods have been associated with increased racial tension and political polarization in comparison to integrated, diverse neighborhoods.
+However, at the city or metropolitan level, the opposite seems to be true: when considering larger geographic areas, diversity and integration are correlated with racial tension, competition, prejudice, lower levels of cooperation, and lower spending on public goods [@oliver_paradoxes_2010; @baqir_public_1999; @hopkins_diversity_2009].
+While these differences in the expected effect of segregation on the geographic level may seem confusing at first, they make sense as they suggest that the most severely segregated areas are those that are diverse overall, but have many homogeneous neighborhoods.
+Thus, while people of different races co-exist within a highly segregated city, they live separately within their own neighborhoods, which creates an environment ripe for racial tension [@trounstine_segregation_2016].
+It is thus not simply the level of diversity or integration that matters for racial harmony and cooperation, but their patterns within a larger geographic framework [@trounstine_segregation_2016; @oliver_paradoxes_2010; @bharathi_public_2018].
+
+# TABLE SHOULD BE RIGHT HERE
+
+```{r results_printing_rp_impute_regressions_1, echo=FALSE, results="asis"}
+
+# print results of 1st regression
+
+imp_1_rp_sum_table <- as.data.frame(imp_felm1_sum_table %>% 
+  select(term, estimate, std.error, p.value)) %>%
+  head(13)
+
+stargazer(imp_1_rp_sum_table,
+          header = FALSE,
+          title = "\\textbf{Racial Polarization in Segregated Cities: A}",
+          float = FALSE,
+          table.placement = "H")
+
+```
+
+Political polarization along racial lines may lead to decreased public spending and goods provision because groups may have different preferences, which can make compromise hard, and because groups may preceive a disutility in out-groups receiving public goods expenditure @baqir_public_1999.
+@einstein_divided_2012 found evidence that racial segregation predicts large political divisions at the metropolitan level and that these divisions can create a lack of willingness to compromise and collaborate on local policy problems.
+@trounstine_segregation_2016 finds similar results at the city level: that residential racial segregation is associated with both increased political division and decreased public spending.
+Thus, these authors suggest that it is the combination of homogenous neighborhoods within a much larger, diverse geographic area that leads to increased political polarization and reduced public goods spending in local governments.
+
+More recently, some scholars have called this hypothesis and its importance into question.
+For example, @lee_ethnic_2018 finds evidence that larger inequalities within the political system favoring socially powerful groups, not local diversity patterns leading to decreased cooperation, may be a better explanation of failures in public goods provision in diverse areas.
+Others suggest that additional factors, such as income segregation, may be important confounding factors in public goods provision.
+@an_its_2018, for example, suggests that the more closely related income inequality is to racial inequality, the less investment is made in public goods, and that this interaciton was a better predictor of public goods spending patterns than measures of diversity.
+There is, in fact, a variety of evidence suggesting that it is meaningful to consider the effects of income inequaltiy and diversity and segregation jointly [@an_its_2018; @massey_american_1993].
+Given the active debate in the literature over the relaitonships between diversity, segregation, public spending, and other factors, it is increasingly important to re-examine previously reported findings as a means of robustness checks.
+
+# Replication
+
+I was able to successfully replicate all of the main results from Trounstine (2016).
+All regressions and tables were fully replicated in R.
+As an example, in table X, I replicate Table 1 from page 713 of @trounstine_segregation_2016, which is also included as Figure 1 for comparison.
+However, I was unable to successfully replicate Trounstine (2016)’s marginal effects analyses and margins plots using R.
+There does not yet appear to be a built-in R function to calculate marginal or predicted effects or to generate margins plots from the complicated multi-level models employed in the original paper, and creating such a function was outside of the scope of this analysis.
+Nevertheless, these results were successfully replicated in Stata.
+
+```{r results_printing_fs_impute_regressions_2, echo=FALSE}
+
+# print results of 3rd regression
+
+imp_felm2_sum_table <- as.data.frame(imp_felm2_sum %>% 
+  select(term, estimate, std.error, p.value))
+print(imp_felm2_sum_table)
+```
+
+```{r results_printing_fs_impute_regressions_3, echo=FALSE}
+
+# print results of 3rd regression
+
+imp_felm3_sum_table <- as.data.frame(imp_felm3_sum %>% 
+  select(term, estimate, std.error, p.value))
+print(imp_felm3_sum_table)
+```
+
+```{r}
+
+# practice tables
+
+```
+
+```{r}
 # how many observations were included in those 3 analyses?
@@
 
-fin <- complete(imp_fs) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
+sum(is.na(complete(imp_1_fs)$H_citytract_NHW_i))
+sum(is.na(complete(imp_1_fs,1)$H_citytract_NHW_i))
+sum(is.na(complete(imp_1_fs,2)$H_citytract_NHW_i))
+sum(is.na(complete(imp_1_fs,3)$H_citytract_NHW_i))
+sum(is.na(complete(imp_1_fs,4)$H_citytract_NHW_i))
+sum(is.na(complete(imp_1_fs,5)$H_citytract_NHW_i))
 
-# create dge variable used in regression
-
-fin_dge <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_dge_tab <- tibble(
-  Variable = "Direct General Expenditure per Capita",
-  Obs = nrow(fin_dge),
-  Mean = mean(fin_dge$dgepercap_cpi, na.rm = T),
-  SD = sd(fin_dge$dgepercap_cpi, na.rm = T),
-  Min = min(fin_dge$dgepercap_cpi, na.rm = T),
-  Max = max(fin_dge$dgepercap_cpi, na.rm = T)
-)
-
-# now we have 73,119 observations compared to 13,742. Calculation:
-
-nrow(fin_dge)
-
-# number of missing seg indexes before imputation: 282334
-
-# number missing now: 222957 -> Calculation:
-
-new_missing <- sum(is.na(complete(imp_fs)$H_citytract_NHW_i))
-
-# calculate number of observations we added to the sample: 59,377
-
-num_added <- 282334 - new_missing
-
-# INTERPRETATION BEFORE AFTER CHANGED The results of the first regression present a stark difference to the results of @trounstine_segregation_2016.
-Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant.
-Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
-The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.
-
-```
-
-The results of the first regression present a stark difference to the results of @trounstine_segregation_2016.
-Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant.
-Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
-The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.
-
-The results of the first regression indicate that Trounstine's results are robust to the inclusion of the imputed data, which led to the inclusion of an additional 59,377 observations in the analysis.
-The coefficients, standard errors, and significance levels are essentially unchanged.
-The same is largely true for the second and third specifications, but the magnitude of the coefficient on the segregation decreases slightly.
-
-```{r results_printing_fs_impute_regressions_1, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_felm1_sum_table <- as.data.frame(imp_felm1_sum %>% 
-  select(term, estimate, std.error, p.value))
-print(imp_felm1_sum_table)
-
-stargazer(imp_felm1_sum_table,
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Expenditure per Capita}")
-```
-
-```{r results_printing_fs_impute_regressions_2, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_felm2_sum_table <- as.data.frame(imp_felm2_sum %>% 
-  select(term, estimate, std.error, p.value))
-print(imp_felm2_sum_table)
-
-stargazer(imp_felm1_sum_table,
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Changing Demographics}")
-```
-
-```{r results_printing_fs_impute_regressions_3, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_felm3_sum_table <- as.data.frame(imp_felm3_sum %>% 
-  select(term, estimate, std.error, p.value))
-print(imp_felm3_sum_table)
-
-stargazer(imp_felm1_sum_table,
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Ideology Control}")
-```
-
-# FS NEW data results
-
-```{r new_fs_imputation_tries, include = FALSE}
-# Main Analysis 2: Imputations
-
-## regression 1 Table 2
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-## regression 2 Table 2
-
-# fit multiple imputed datasets
-
-fit_imp_felm2 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm2 <- pool(fit_imp_felm2)
-imp_felm2_sum <- summary(pool_imp_felm2)
-
-## Regression 3 Table 2
-
-fit_imp_felm3 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm3 <- pool(fit_imp_felm3)
-imp_felm3_sum <- summary(pool_imp_felm3)
-
-# INTERPRETATION BEFORE AFTER CHANGED The results of the first regression present a stark difference to the results of @trounstine_segregation_2016.
-Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant.
-Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
-The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.
-
-print(imp_felm1_sum)
-print(imp_felm2_sum)
-print(imp_felm3_sum)
-
-# large amount of data missing across the board in terms of years
-
-gg_miss_var(fin_dge, facet = year, show_pct = TRUE)
-
-# can't really tell anything about the region facet since a lot of obs missing region data
-
-gg_miss_var(fin_imp_extra, facet = region, show_pct = TRUE)
-
-# not necessarily a significant pattern across states either
-
-gg_miss_var(fin_imp_extra, facet = statecode, show_pct = TRUE)
-
-```
-
-# FS NEW AGAIN
-
-```{r}
-cities_to_keep <- c("Austin City", "Baltimore City", "Charlotte City", "Chicago City", "Cleveland City", "Columbus City", "Dallas City", "Denver City", "Detroit City", "Houston City", "Indianapolis", "Jacksonville", "Los Angeles City", "Memphis City", "Milwaukee City", "New York City", "Oklahoma City City", "Philadelphia City", "Phoenix City", "San Antonio City", "San Diego City", "San Francisco City", "San Jose City", "Tucson City", "Washington City")
-
-# apply the conditions in Stata regression to the fin_seg dataset
-
-fin_imp_cities <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0, cityname %in% cities_to_keep) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-# select the relevant variables to be imputed
-
-fin_imp <- fin_imp %>%
-  select(H_citytract_NHW_i, dgepercap_cpi, diversityinterp, pctblkpopinterp, pctasianpopinterp,
-         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
-         pctcollegegradinterp, logpop, geo_id2, chng5pctblk, chng5pctlatino, chng5pctasian,
-         ideology_fill)
-```
-
-```{r looking_at_original_data, include = FALSE}
-
-range(fin_seg$totaltractsf, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_seg %>%
-  ggplot() +
-  geom_histogram(aes(x = totaltractsf))
-
-range(fin_seg$logpop, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_seg %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-# add back in year, region, and statecode to be able to look at this
-
-fin_imp_old <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-fin_imp_extra <- fin_imp %>%
-  mutate(year = fin_imp_old$year,
-         region = fin_imp_old$region,
-         statecode = fin_imp_old$statecode)
-
-# large amount of data missing across the board in terms of years
-
-gg_miss_var(fin_imp_extra, facet = year, show_pct = TRUE)
-
-# can't really tell anything about the region facet since a lot of obs missing region data
-
-gg_miss_var(fin_imp_extra, facet = region, show_pct = TRUE)
-
-# not necessarily a significant pattern across states either
-
-gg_miss_var(fin_imp_extra, facet = statecode, show_pct = TRUE)
-
-```
-
-```{r looking_at_Trounstine_data, include = FALSE}
-
-# basic filter for table for all regressions
-
-# xtreg dgepercap_cpi H_citytract_NHW_i diversityinterp pctblkpopinterp
-# pctasianpopinterp pctlatinopopinterp medinc_cpi pctlocalgovworker_100
-# pctrentersinterp pctover65 pctcollegegradinterp logpop if totaltracts>1 &
-# dgepercap_cpi~=0,fe vce(cluster geo_id2)
-
-fin_trounstine <-fin_seg %>%
-  filter(totaltractsf >1 | is.na(totaltractsf)) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
-
-# create dge variable used in regression
-
-fin_dge_trounstine <-fin_trounstine %>% filter(dgepercap_cpi != 0)
-
-range(fin_dge_trounstine$totaltractsf, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_dge_trounstine %>%
-  ggplot() +
-  geom_histogram(aes(x = totaltractsf))
-
-range(fin_dge_trounstine$logpop, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_dge_trounstine %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-```
-
-```{r looking_at_imputed_data}
-
-fin_new_imp <- complete(new_imp_fs) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
-
-range(fin_new_imp$logpop, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_new_imp %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-```
-
-# Conclusion
-
-Why cities differ in their amount of spending on public goods is an interesting questions that is frequently debated in the literature.
-@trounstine_segregation_2016 posits that segregation may be an important underlying cause of the underprovsion of public goods.
-Finding evidence that residential segregation by race increases political partisanship, @trounstine_segregation_2016 argues that residential segregation can increase division and make cooperation amongst competing groups difficult, which results in decreased spending on public goods.
-The findings of @trounstine_segregation_2016 are particularly important because they suggest that segregation, as defined by many homogeneous neighborhoods within a larger diverse geographical area, is the key factor in disinvestment in public goods.
-This contradicts previous research which has suggested that levels of diversity were instead most important (see for example @baqir_public_1999 or @hopkins_diversity_2009).
-While @trounstine_segregation_2016 still represents relatively new reasearch as of 2020, it has yet to be fully vetted by additional research.
-Furthermore, some research that has been published on the topic since its publication suggests that other factors such as larger inequities in the political system favoring socially powerful groups [@lee_ethnic_2018] or the interaction of income and racial inequality [@an_its_2018] may be more important in explaining public goods provisions.
-
-I first worked to provide a check on the analysis presented in @trounstine_segregation_2016 by attempting to replicate the work in R.
-I was able to successfully replicate all of the main results from @trounstine_segregation_2016, with the exception of a few of a few marginal analyses of the complex, multi-level models which, to my knowledge, are currently not supported by available R packages.
-I was, however, able to successfully replicate these results in Stata.
-
-As an additional robustness check I also tested the models in @trounstine_segregation_2016 by re-running them with additional data that I imputed from missing values in the original datasets.
-The large number of missing values in both of the datasets used in @trounstine_segregation_2016's main analysis created a concern for potential bias in the original results and a lack of representativeness due to the large amount of data excluded from the regression analysis due to missing values.
-Thus, I used the mice package in R to create multiply imputed datasets, upon which I re-ran the models and pooled the results to generate the final model coefficients and parameters.
-
-The results of the data imputation exercise differed between the two datasets.
-For the analyses using the smaller, racial polarization dataset, the results from the imputed data resulted in a smaller magnitude of the coefficient on the main independent variable, and also made it statistically insignificant in the main model specification.
-This suggests that the segregation index may not have as strong of a positive association with political polarization as @trounstine_segregation_2016 suggests.
-However, for the analyses using the much larger financial segregation dataset, the results of the models using the multiply imputed data largely mirrored the results of @trounstine_segregation_2016, and the coefficients and significance levels were essentially the same between the two, with the standard errors on the model estimates being generally slightly lower for the analyses using the imputed data.
-This provides strong support for @trounstine_segregation_2016's finding that residential racial segregation is associated with diminshed spending on public goods.
-
-The replication exercise and robustness check using multiply imputed data here provide strong evidence that residential segregation along racial lines does in fact correlate negatively with spending on a variety of public goods.
-What my analysis calls more into question, is by what mechanism this happens.
-Using the multiply imputed data, I still found some evidence that segregation may be associated with increased political polarization which @trounstine_segregation_2016 suggests may lead to diminished public goods spending; however, the effect size is much smaller than that found in @trounstine_segregation_2016, and some of the results have become insignificant.
-It is possible that other mechanisms may be more important in explaining why segregation might be associated with decreased spending on public goods.
-For example, it could be that there is an important interaction effect between income and segregation, as others have previously suggested, or there could be some other intervening mechanism or a confounding variable that is leading to the negative association between segregation and lower spending on public goods.
-@trounstine_segregation_2016 has identified an important relationship between segregation and the provision of public goods.
-However, my analysis suggests that further research is needed to assess the potential mechanisms by which residential segregation by race or even a confounding variable may result in dimished spending.
-If this mechanism can be better understood, than it will be possible to more effectively understand and address the underprovision of public goods, which may inhibit social mobility and unfairly disadvantage certain groups.
-
-# Appendix
-
-```{r felm, eval = FALSE}
-
-# Main Analysis 2
-
-## regression 1 Table 2
-
-# The following is a fixed effects model regression with clustering around
-# geo_id2. It mandates that total census tracts in the city is greater than 1,
-# which we want because our measure of evenness of racial spread is constant for
-# cities with only one tract by our definition (which requires comparing tracts
-# within cities). It also mandates that Direct General Expenditures (DGE) per
-# capita, CPI adjusted is not equal to 0, which would be problematic and
-# indicate a potential data error. This regression regresses the DGE per capita
-# on the the two-group calculation of  Theil's H interpolated. Controls are
-# included for diversity and the % populations of Blacks, Asians, and Latinos to
-# help identify whether it is actually diversity that drives down spending.These
-# demographic controls also help to account for the fact that whites and
-# minorities tend to perfer different levels of government spending in general.
-# This will help isolate the effects of segregation v. other forms of diversity
-# on public spending. Other controls for Median household income, CPI adjusted,
-# percent over 65, percent college grads, percent local government workers, log
-# population help control for additional factors related to segregation and
-# expenditure. Controls for percent renters interpolated and Median household
-# income also help to control for the general wealth of cities, which could be a
-# potential driver of public spending. Fixed effects for cities are also
-# included  so that the author can examine the effect of segregation in the same
-# city over  time, which also helps control for many other factors not otherwise
-# taken into account (such as city age)
-
-# apply the conditions in Stata regression
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-# felm(y~x | factor(fe1) + factor(fe2) | 0 | clustervar)
-
-felm1 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-## regression 2 Table 2
-
-# This regression is the same as above except instead of using diversity, a new
-# control is added for the five year changes in racial group shares. The goal
-# here is to see whether or not changes in diversity are a driving factor
-# (rather than absolute levels of diversity).
-
-felm2 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-## Regression 3 Table 2
-
-# Column 3
-
-# As in column 3 of table 1, this regression simply adds in a control for  mean  ideology of city residents from General Social Survey (GSS) to control for the  possibility that ideology that segregated cities are more ideologically  conservative and that the conservative nature of segregated cities is what actually drives the effect.
-
-felm3 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-```
-
-```{r main_fp_tables, results = "asis", eval = FALSE}
-
-# create main table for table 3
-
-table2 <- stargazer(felm1, felm2, felm3, omit = c("year", "south", "midwest", "west"), 
-                    header = FALSE,
-                    title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures}")
-
-```
-
-```{r, eval = FALSE}
-
-# Main Analysis 3
-
-## regression 1 Table 3
-
-# Column 1
-
-# The following is a fixed effects model regression with clustering once again around geo_id2.
-Again, the if statements at the end mandate that total census tracts in the city is greater than 1, which we want because our measure of evenness of racial spread is constant for cities with only one tract by our definition (which requires comparing tracts within cities).
-They also mandate that the highways per capita, CPI adjsuted with no cap extend (lagged 5 years) is not equal to 0, which would be problematic and indicate a potential data error.
-The dependent variable here is highways per capita, CPI adjsuted with no cap extend (lagged 5 years) and it is regressed on the two group calculation of Theil's H, interpolated.
-Controls are added for diversity, percent population of Blacks, Asians, and Latinos, and median household CPI adjusted income as well as for % local government worker hundreds, percent rentership, percent over 65, percent college graduates, and the log of the population.
-This essentially examines the effect of segregation on the specific public good of highways.
-As in the previous table's regressions, fixed effects for cities are also included so that the author can examine the effect of segregation in the same city over time, which also helps control for many other factors not otherwise taken into account (such as city age) *
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), highwayspercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_1 <- felm(highwayspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-## regression 2 Table 3
-
-# Column 2
-
-# This is the same regression as column 1, but this time the dependent variable
-# is police per capita, CPI adjusted with no cap extend. This essentially
-# examines the effect of segregation on the specific public good of police per
-# capita.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), policepercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_2 <- felm( policepercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 3
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), parkspercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-# This is again the same regression, but this time the dependent variable is
-# parks per capita, CPI adjusted with no cap extend. This essentially examines
-# the effect of segregation on the specific public good of parks.
-
-felm2_3 <- felm(parkspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 4
-
-# This is again the same regression, but this time the dependent variable is
-# sewers per capita, CPI adjusted with no cap extend. This essentially examines
-# the effect of segregation on the specific public good of sewers.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), sewerspercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_4 <- felm(sewerspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 5
-
-# This is again the same regression, but this time the dependent variable is
-# Welfare, Health, Housing per capita, CPI adjusted, no cap expend. This
-# essentially examines the effect of segregation on the specific public good of
-# welfare and housing.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), welfhoushealthNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_5 <- felm(welfhoushealthNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 6
-
-# This is again the same regression, but this time the dependent variable is own
-# source of general revenue per capita, CPI adjusted. This essentially examines
-# the effect of segregation on the specific public good of own source revenue.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), genrevownpercap_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_6 <- felm(genrevownpercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-```
-
-```{r results = "asis", eval = FALSE}
-table3a <- stargazer(felm2_1, felm2_2, felm2_3, 
-          omit = c("year", "south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Public Goods A}")
-
-table3b <- stargazer(felm2_4, felm2_5, felm2_6, 
-          omit = c("year", "south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Public Goods B}")
-
-#star_sidewaystable(table3)
-```
-
-```{r iv_regs, eval = FALSE}
-
-## regression 1 Table 5
-
-# Top Row
-
-# Column 1
-
-# This is an instrumental variable regression with DGE per capita, adjusted by the CPI, as the dependent variable and total number of waterways as the instrumental variable for segregation.
-The instrument includes the log of the population in the first stage because the number of waterways is positively correlated to population and population is positively correlated with segregation.
-The control variables are the same as those in the regressions for Table 2 except for 2 changes: since the number of waterways does not change, there is no need for city fixed effects.
-Instead, we include fixed effects for the region and year.
-A lagged version of the dependent variable (dgepercap_cpilag) is added to the regressions to account for the high correlation between  observations for the same city over time and because changes in local budgets typically are incremental (NOTE: why exactly do we do this/why does it help/why not do it in the non-intstrumental regressions?).
-
-fin_seg_1 <- fin_seg %>%
-  filter(dgepercap_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-glimpse(fin_seg_1$medincinterp)
-
-# good explanation: http://eclr.humanities.manchester.ac.uk/index.php/IV_in_R
-
-# iv = ivreg(second stage regression | instrument1 + instrument2 )
-
-ivreg1 <- ivreg(dgepercap_cpi ~ H_citytract_NHW_i + dgepercap_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + dgepercap_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_1)
-
-# Column 2
-
-# this is the same regression as for column 1 but now we use the dependent variable highwayspercapNC_cpi to assess the effect of the instrumental  variable on highways per capita *
-
-fin_seg_2 <- fin_seg %>%
-  filter(highwayspercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg2 <- ivreg(highwayspercapNC_cpi ~ H_citytract_NHW_i + highwayspercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + highwayspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_2)
-
-# Column 3
-
-# this is the same regression as for column 1 but now we use the dependent variable policepercapNC_cpi to assess the effect of the instrumental variable on police per capita
-
-fin_seg_3 <- fin_seg %>%
-  filter(policepercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg3 <- ivreg(policepercapNC_cpi ~ H_citytract_NHW_i + policepercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + policepercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_3)
-
-# Column 4 this is the same regression as for column 1 but now we use the
-# dependent variable parkspercapNC_cpi to assess the effect of the instrumental
-# variable on parks per capita
-
-fin_seg_4 <- fin_seg %>%
-  filter(parkspercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg4 <- ivreg(parkspercapNC_cpi ~ H_citytract_NHW_i + parkspercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + parkspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_4)
-
-# Bottom Row
-
-# Column 1
-
-# this is the same regression as for column 1 but now we use the dependent
-# variable sewerspercapNC_cpi to assess the effect of the instrumental variable
-# on sewers per capita
-
-fin_seg_5 <- fin_seg %>%
-  filter(sewerspercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg5 <- ivreg(sewerspercapNC_cpi ~ H_citytract_NHW_i + sewerspercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + sewerspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_5)
-
-# Column 3
-
-# this is the same regression as for column 1 but now we use the dependent variable genrevownpercap_cpi to assess the effect of the instrumental variable on own source revenue per capita
-
-fin_seg_6 <- fin_seg %>%
-  filter(genrevownpercap_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg6 <- ivreg(genrevownpercap_cpi ~ H_citytract_NHW_i + genrevownpercap_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + genrevownpercap_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_6)
-
-# Column 2
-
-# this is the same regression as for column 1 but now we use the dependent
-# variable welfhoushealthNC_cpi to assess the effect of the instrumental
-# variable on welfare per capita
-
-fin_seg_7 <- fin_seg %>%
-  filter(welfhoushealthNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg7 <- ivreg(welfhoushealthNC_cpi ~ H_citytract_NHW_i + welfhoushealthNC_cpilag  + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + welfhoushealthNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_7)
-
-summary(ivreg7)
-
-```
-
-# Table 5
-
-```{r results = "asis", echo = FALSE}
-
-table5a <- stargazer(ivreg1, ivreg2, ivreg3, ivreg4,
-          omit = c("y5", "y6", "y7", "y8", "y9", "northeast", "south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach A}")
-
-table5b <- stargazer(ivreg5, ivreg6, ivreg7,
-          omit = c("y5", "y6", "y7", "y8", "y9", "northeast","south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach B}")
-```
-
-```{r import_data, include = FALSE}
-
-# make a list of the cities included in the analysis to filter out from the main
-# dataset as specified in the table
-
-cities_to_keep <- c("Austin City", "Baltimore City", "Charlotte City", "Chicago City", "Cleveland City", "Columbus City", "Dallas City", "Denver City", "Detroit City", "Houston City", "Indianapolis", "Jacksonville", "Los Angeles City", "Memphis City", "Milwaukee City", "New York City", "Oklahoma City City", "Philadelphia City", "Phoenix City", "San Antonio City", "San Diego City", "San Francisco City", "San Jose City", "Tucson City", "Washington City")
-
-# based on some investigation, the missing additional filter needed to replicate
-# appendix tables 1 and 2 is that biggest split cannot be NA. This was
-# discovered in attempting to create table 2. The number of elections with the
-# largest divides between each racial group were the same as in the table when
-# all results were included and only the summary stats differed in both tables
-# using the city and winner subset. So, I tried excluding all entries for which
-# biggestsplit was NA, and found that the resulting subset matched the
-# statistics in both tables.
-
-# create a subset of the data with the relevant cities where there is a winner
-# and the biggestsplit is not NA
-
-rp_sub <- rp %>%
-  filter(winner == 1) %>%
-  filter(cityname %in% cities_to_keep) %>%
-  filter(!(is.na(biggestsplit)))
-
-# select the relevant variables for the table
-
-rp_sub_a1 <- rp_sub %>%
-  select(biggestsplit, H_citytract_multi_i, H_citytract_NHW_i, diversityinterp, 
-         pctasianpopinterp, pctblkpopinterp, pctlatinopopinterp, medincinterp, 
-         pctrentersinterp, pctcollegegradinterp, biracial, nonpartisan, primary, 
-         logpop, whiteideology_fill2) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-# why are the exact variables H_citytract_NHW and whiteideology_fill not in the
-# data? Data variable names author uses and ones in the data don't exactly
-# match, but replication results are the same.
-
-```
-
-```{r table_a1, results="asis", echo = FALSE}
-
-# create a stargazer summary table for the relevant statistics of the racial
-# polarization data. I couldn't figure out how to change the text of the
-# statistic names at the top of the datat table. I also couldn't figure out how
-# to only not display additional digits for the income variable. May be
-# better to switch to gt for final version?
-
-stargazer(as.data.frame(rp_sub_a1),
-          omit.summary.stat = c("p25", "p75"),
-          title = "\\textbf{TABLE A1 Summary Statistics: Racial Polarization Data}",
-          column.labels = c("\\textbf{Variable}","\\textbf{Obs}", "\\textbf{Mean}", "\\textbf{Std. Dev.}", "\\textbf{Min}", "\\textbf{Max}"),
-          covariate.labels = c("Largest Racial Divide","\\emph{H} Index: Multigroup", "\\emph{H} Index: Two-Group", "Diversity", "\\% Asian", "\\% Black", "\\% Latino", "Median HH Income", "\\% Renters", "\\% College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology"),
-          no.space = TRUE,
-          header = FALSE)
-
-```
-
-```{r table_a2_data_manipulation, include = FALSE}
-
-# initialize variables to indicate if a racial divide had the biggest divide in
-# the election
-
-rp_sub$biggest_split_bw <- NA
-rp_sub$biggest_split_lw <- NA
-rp_sub$biggest_split_bl <- NA
-
-# change the NA value to 1 if the relevant divide was the biggest in the election
-
-rp_sub$biggest_split_bw[rp_sub$biggestsplit_gr == 1] <- 1
-rp_sub$biggest_split_lw[rp_sub$biggestsplit_gr == 2] <- 1
-rp_sub$biggest_split_bl[rp_sub$biggestsplit_gr == 3] <- 1
-
-# generate the dataset of summary statistics to replicate the second appendix
-# table. Group by city name and then summarize the mean H indexes. Sum the
-# number of biggest splits by racial divide for each city
-
-rp_sub_2 <- rp_sub %>%
-  group_by(cityname) %>%
-  summarise(mean_multi_H = mean(H_citytract_multi_i),
-            mean_multi_two_group = mean(H_citytract_NHW_i),
-            sum_bw = sum(biggest_split_bw, na.rm = T),
-            sum_lw = sum(biggest_split_lw, na.rm = T),
-            sum_bl = sum(biggest_split_bl, na.rm = T))
-```
-
-```{r table_a2, echo = FALSE}
-
-# create appendix table A2 to present the summary statistics for cities included
-# in racial polarization data. Efforts to make columns narrower were
-# unsuccessful, so some of the labels in the column names were changed to make
-# the table fit. I also couldn't get the title to print out without including a
-# non-Null subtitle.
-
-city_names <- c("Austin, TX", "Baltimore, MD", "Charlotte, NC", "Chicago, IL", "Cleveland, OH", "Columbus, OH", "Dallas, TX", "Denver, CO", "Detroit, MI", "Houston, TX", "Indianapolis, IN", "Jacksonville, FL", "Los Angeles, CA", "Memphis, TN", "Milwaukee, WI", "New York, NY", "Oklahoma, OK", "Philadelphia, PA", "Phoenix, AZ", "San Antonio, TX","San Diego, CA", "San Francisco, CA", "San Jose, CA", "Tucson, AZ", "Washington, DC")
-
-rp_sub_2$cityname <- city_names
-
-gt(rp_sub_2) %>%
-  tab_header(title = md("**TABLE A2 Cities Included in Racial Polarization Data**"),
-             subtitle = "Replication") %>%
-  tab_spanner(
-      label = md("**Segregation: Mean *H* Index**"),
-      columns = vars(mean_multi_H, mean_multi_two_group)) %>%
-  tab_spanner(
-      label = md("**Largest Racial Divide, Number of Elections**"),
-      columns = vars(sum_bw, sum_lw, sum_bl)) %>%
-  fmt_number(columns = vars(mean_multi_H, mean_multi_two_group),
-             decimals = 3) %>%
-  cols_label(cityname = "City Name",
-             mean_multi_H = md("Multigroup"),
-             mean_multi_two_group = md("Two-Group"),
-             sum_bw = "Black/White",
-             sum_lw = "Latino/White",
-             sum_bl = "Black/Latino") %>%
-  cols_width(
-    vars(cityname) ~ px(10),
-    TRUE ~ px(20)
-  ) %>%
-  cols_align(
-    columns = vars(cityname),
-    align = "left"
-  ) %>%
-  tab_options(
-    table.margin.left = px(5), 
-    table.margin.right = px(5),
-    data_row.padding = px(1),
-    table.width = pct(90)
-  )
-
-```
-
-```{r include = FALSE, include = FALSE}
-
-# basic filter for table for all regressions
-
-# xtreg dgepercap_cpi H_citytract_NHW_i diversityinterp pctblkpopinterp
-# pctasianpopinterp pctlatinopopinterp medinc_cpi pctlocalgovworker_100
-# pctrentersinterp pctover65 pctcollegegradinterp logpop if totaltracts>1 &
-# dgepercap_cpi~=0,fe vce(cluster geo_id2)
-
-fin <-fin_seg %>%
-  filter(totaltractsf >1 | is.na(totaltractsf)) %>%
+fin <- complete(imp_1_fs) %>%
   filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
@@
 
-# creat summary for highways
-fin_hw <-fin %>% filter(highwayspercapNC_cpi != 0)
+# now we have 73,119 observations compared to 13,742 --> this only included an extra 200 obs!!
 
-fin_hw_tab <- tibble(
-  Variable = "Highways per Capita",
-  Obs = nrow(fin_hw),
-  Mean = mean(fin_hw$highwayspercapNC_cpi, na.rm = T),
-  SD = sd(fin_hw$highwayspercapNC_cpi, na.rm = T),
-  Min = min(fin_hw$highwayspercapNC_cpi, na.rm = T),
-  Max = max(fin_hw$highwayspercapNC_cpi, na.rm = T)
-)
+nrow(fin_seg)
 
-print(fin_hw_tab)
+# number of missing seg indexes before imputation: 282334
 
-a3_final <- full_join(fin_dge_tab, fin_hw_tab)
+# number missing now: 222957
+282334 - 222957
 
-# parks
+73119-13742
 
-fin_park <-fin %>% filter(parkspercapNC_cpi != 0)
+# we were able to increase sample size by 59,377
 
-fin_park_tab <- tibble(
-  Variable = "Parks per Capita",
-  Obs = nrow(fin_park),
-  Mean = mean(fin_park$parkspercapNC_cpi, na.rm = T),
-  SD = sd(fin_park$parkspercapNC_cpi, na.rm = T),
-  Min = min(fin_park$parkspercapNC_cpi, na.rm = T),
-  Max = max(fin_park$parkspercapNC_cpi, na.rm = T)
-)
-
-print(fin_park_tab)
-
-a3_final <- full_join(a3_final, fin_park_tab)
-
-# police
-
-fin_police <-fin %>% filter(policepercapNC_cpi != 0)
-
-fin_police_tab <- tibble(
-  Variable = "Police per Capita",
-  Obs = nrow(fin_police),
-  Mean = mean(fin_police$policepercapNC_cpi, na.rm = T),
-  SD = sd(fin_police$policepercapNC_cpi, na.rm = T),
-  Min = min(fin_police$policepercapNC_cpi, na.rm = T),
-  Max = max(fin_police$policepercapNC_cpi, na.rm = T)
-)
-
-print(fin_police_tab)
-
-a3_final <- full_join(a3_final, fin_police_tab)
-
-# sewers
-
-fin_sew <-fin %>% filter(sewerspercapNC_cpi != 0)
-
-fin_sew_tab <- tibble(
-  Variable = "Sewers per Capita",
-  Obs = nrow(fin_sew),
-  Mean = mean(fin_sew$sewerspercapNC_cpi, na.rm = T),
-  SD = sd(fin_sew$sewerspercapNC_cpi, na.rm = T),
-  Min = min(fin_sew$sewerspercapNC_cpi, na.rm = T),
-  Max = max(fin_sew$sewerspercapNC_cpi, na.rm = T)
-)
-
-print(fin_sew_tab)
-
-a3_final <- full_join(a3_final, fin_sew_tab)
-
-# welfare
-
-fin_welfare <-fin %>% filter(welfhoushealthNC_cpi != 0)
-
-fin_welfare_tab <- tibble(
-  Variable = "Welfare, Health, and Housing per Capita",
-  Obs = nrow(fin_welfare),
-  Mean = mean(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
-  SD = sd(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
-  Min = min(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
-  Max = max(fin_welfare$welfhoushealthNC_cpi, na.rm = T)
-)
-
-print(fin_welfare_tab)
-
-a3_final <- full_join(a3_final, fin_welfare_tab)
-
-# own source revenue
-
-fin_own <-fin %>% filter(genrevownpercap_cpi != 0)
-
-fin_own_tab <- tibble(
-  Variable = "Own Source Revenue per Capita",
-  Obs = nrow(fin_own),
-  Mean = mean(fin_own$genrevownpercap_cpi, na.rm = T),
-  SD = sd(fin_own$genrevownpercap_cpi, na.rm = T),
-  Min = min(fin_own$genrevownpercap_cpi, na.rm = T),
-  Max = max(fin_own$genrevownpercap_cpi, na.rm = T)
-)
-
-print(fin_own_tab)
-
-a3_final <- full_join(a3_final, fin_own_tab)
-
-# two group H
-
-fin_h <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_h_tab <- tibble(
-  Variable = "Two-Group H Index",
-  Obs = nrow(fin_h),
-  Mean = mean(fin_h$H_citytract_NHW_i, na.rm = T),
-  SD = sd(fin_h$H_citytract_NHW_i, na.rm = T),
-  Min = min(fin_h$H_citytract_NHW_i, na.rm = T),
-  Max = max(fin_h$H_citytract_NHW_i, na.rm = T)
-)
-
-print(fin_h_tab)
-
-a3_final <- full_join(a3_final, fin_h_tab)
-
-# Diversity
-
-fin_div <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_div_tab <- tibble(
-  Variable = "Diversity",
-  Obs = nrow(fin_div),
-  Mean = mean(fin_div$diversityinterp, na.rm = T),
-  SD = sd(fin_div$diversityinterp, na.rm = T),
-  Min = min(fin_div$diversityinterp, na.rm = T),
-  Max = max(fin_div$diversityinterp, na.rm = T)
-)
-
-print(fin_div_tab)
-
-a3_final <- full_join(a3_final, fin_div_tab)
-
-# % black
-
-fin_pctblk <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pctblk_tab <- tibble(
-  Variable = "%  Black",
-  Obs = nrow(fin_pctblk),
-  Mean = mean(fin_pctblk$pctblkpopinterp, na.rm = T),
-  SD = sd(fin_pctblk$pctblkpopinterp, na.rm = T),
-  Min = min(fin_pctblk$pctblkpopinterp, na.rm = T),
-  Max = max(fin_pctblk$pctblkpopinterp, na.rm = T)
-)
-
-print(fin_pctblk_tab)
-
-a3_final <- full_join(a3_final, fin_pctblk_tab)
-
-# % asian
-
-fin_pcta <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pcta_tab <- tibble(
-  Variable = "%  Asian",
-  Obs = nrow(fin_pcta),
-  Mean = mean(fin_pcta$pctasianpopinterp, na.rm = T),
-  SD = sd(fin_pcta$pctasianpopinterp, na.rm = T),
-  Min = min(fin_pcta$pctasianpopinterp, na.rm = T),
-  Max = max(fin_pcta$pctasianpopinterp, na.rm = T)
-)
-
-print(fin_pcta_tab)
-
-a3_final <- full_join(a3_final, fin_pcta_tab)
-
-# % latino
-
-fin_pctla <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pctla_tab <- tibble(
-  Variable = "%  Latino",
-  Obs = nrow(fin_pctla),
-  Mean = mean(fin_pctla$pctlatinopopinterp, na.rm = T),
-  SD = sd(fin_pctla$pctlatinopopinterp, na.rm = T),
-  Min = min(fin_pctla$pctlatinopopinterp, na.rm = T),
-  Max = max(fin_pctla$pctlatinopopinterp, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_pctla_tab)
-
-# 5y black
-
-fin_chng5pctblk <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))
-
-nrow(fin_chng5pctblk)
-
-fin_chng5pctblk_tab <- tibble(
-  Variable = "5Y Change, % Black",
-  Obs = nrow(fin_chng5pctblk),
-  Mean = mean(fin_chng5pctblk$chng5pctblk, na.rm = T),
-  SD = sd(fin_chng5pctblk$chng5pctblk, na.rm = T),
-  Min = min(fin_chng5pctblk$chng5pctblk, na.rm = T),
-  Max = max(fin_chng5pctblk$chng5pctblk, na.rm = T)
-)
-
-print(fin_chng5pctblk_tab)
-
-a3_final <- full_join(a3_final, fin_chng5pctblk_tab)
-
-# 5y latino
-
-fin_chng5pctlatino <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))
-
-fin_chng5pctlatino_tab <- tibble(
-  Variable = "5Y Change, % Latino",
-  Obs = nrow(fin_chng5pctlatino),
-  Mean = mean(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
-  SD = sd(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
-  Min = min(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
-  Max = max(fin_chng5pctlatino$chng5pctlatino, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_chng5pctlatino_tab)
-
-# 5y asian
-
-fin_chng5pctasian <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))
-
-fin_chng5pctasian_tab <- tibble(
-  Variable = "5Y Change, % Asian",
-  Obs = nrow(fin_chng5pctasian),
-  Mean = mean(fin_chng5pctasian$chng5pctasian, na.rm = T),
-  SD = sd(fin_chng5pctasian$chng5pctasian, na.rm = T),
-  Min = min(fin_chng5pctasian$chng5pctasian, na.rm = T),
-  Max = max(fin_chng5pctasian$chng5pctasian, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_chng5pctasian_tab)
-
-# median income
-
-fin_med <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_med_tab <- tibble(
-  Variable = "Median Income",
-  Obs = nrow(fin_med),
-  Mean = mean(fin_med$medinc_cpi, na.rm = T),
-  SD = sd(fin_med$medinc_cpi, na.rm = T),
-  Min = min(fin_med$medinc_cpi, na.rm = T),
-  Max = max(fin_med$medinc_cpi, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_med_tab)
-
-# % local gov. employees
-
-fin_pctlocal <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pctlocal_tab <- tibble(
-  Variable = "% Local Gov. Employees",
-  Obs = nrow(fin_pctlocal),
-  Mean = mean(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
-  SD = sd(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
-  Min = min(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
-  Max = max(fin_pctlocal$pctlocalgovworker_100, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_pctlocal_tab)
-
-# % renters
-
-fin_rent <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_rent_tab <- tibble(
-  Variable = "% Renters",
-  Obs = nrow(fin_rent),
-  Mean = mean(fin_rent$pctrentersinterp, na.rm = T),
-  SD = sd(fin_rent$pctrentersinterp, na.rm = T),
-  Min = min(fin_rent$pctrentersinterp, na.rm = T),
-  Max = max(fin_rent$pctrentersinterp, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_rent_tab)
-
-# % over 65
-
-fin_65 <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_65_tab <- tibble(
-  Variable = "% Over 65",
-  Obs = nrow(fin_65),
-  Mean = mean(fin_65$pctover65, na.rm = T),
-  SD = sd(fin_65$pctover65, na.rm = T),
-  Min = min(fin_65$pctover65, na.rm = T),
-  Max = max(fin_65$pctover65, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_65_tab)
-
-# % college degree
-
-fin_college <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_college_tab <- tibble(
-  Variable = "% College Degree",
-  Obs = nrow(fin_college),
-  Mean = mean(fin_college$pctcollegegradinterp, na.rm = T),
-  SD = sd(fin_college$pctcollegegradinterp, na.rm = T),
-  Min = min(fin_college$pctcollegegradinterp, na.rm = T),
-  Max = max(fin_college$pctcollegegradinterp, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_college_tab)
-
-# pop logged
-
-fin_logpop <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_logpop_tab <- tibble(
-  Variable = "Population (logged)",
-  Obs = nrow(fin_logpop),
-  Mean = mean(fin_logpop$logpop, na.rm = T),
-  SD = sd(fin_logpop$logpop, na.rm = T),
-  Min = min(fin_logpop$logpop, na.rm = T),
-  Max = max(fin_logpop$logpop, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_logpop_tab)
-
-# city ideology
-
-fin_ideo <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(ideology_fill)))
-
-nrow(fin_ideo)
-
-fin_ideo_tab <- tibble(
-  Variable = "City Ideology",
-  Obs = nrow(fin_ideo),
-  Mean = mean(fin_ideo$ideology_fill, na.rm = T),
-  SD = sd(fin_ideo$ideology_fill, na.rm = T),
-  Min = min(fin_ideo$ideology_fill, na.rm = T),
-  Max = max(fin_ideo$ideology_fill, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_ideo_tab)
-
-# population
-fin_population <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_population_tab <- tibble(
-  Variable = "Population",
-  Obs = nrow(fin_population),
-  Mean = mean(fin_population$population, na.rm = T),
-  SD = sd(fin_population$population, na.rm = T),
-  Min = min(fin_population$population, na.rm = T),
-  Max = max(fin_population$population, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_population_tab)
+miss_var_summary(complete(imp_2_fs))
 
 ```
-
-```{r, echo = FALSE}
-gt(a3_final) %>%
-    tab_header(title = md("**TABLE A3 Summary Statistics: Census of Government Finance and Population**"),
-             subtitle = "") %>%
-    fmt_number(columns = vars(Mean, SD, Min, Max),
-             decimals = 3) %>%
-    cols_label(Obs = md("**Obs**"),
-               Mean = md("**Mean**"),
-               SD = md("**SD**"),
-               Min = md("**Min**"),
-               Max = md("**Max**")
-                        ) 
-```
-
-# Bibliography

### 2020-04-28 writing.Rmd
initial commit with new repo

--- 2020-04-28 Draft_1.Rmd
@@
 ---
-title: "Milestone 7"
+title: "Writing Draft"
 author: "Maria Burzillo"
@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, fig.align = "center")
-knitr::write_bib(c("knitr", "stringr"), "bib.bib", width = 60)
-library(haven)
-library(gtable)
-library(stargazer)
-library(tidyverse)
-library(gt)
-library(gtsummary)
-library(knitr)
-library(stargazer)
-library(lme4)
-library(margins)
-library(reprex)
-library(plm)
-library(devtools)
-library(lfe)
-library(Statamarkdown)
-library(readxl)
-library(starpolishr)
-library(AER)
-library(readxl)
-library(naniar)
-library(mice)
-library(gtsummary)
-library(VIM)
-```
-
-```{r data_imports, include = FALSE}
-
-set.seed(100)
-
-# import both datasets
-
-rp <- read_dta("racial_polarization_winners.dta")
-fin_seg<- read_dta("fin_seg.dta")
-
-# add row numbers for fin_seg
-
-fin_seg$row_num <- as.integer(rownames(fin_seg))
-
-```
-
-```{r data_cleaning_rp, include = FALSE}
-
-# create a factor for year for the rp dataset
-rp$year.f <- as.factor(rp$year)
-
-# apply the condition that winner == 1 as in the Stata code for the rp regressions
-
-rp_1<- rp %>%
-  filter(winner == 1) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-```
-
 # Introduction
@@
 As a result, many scholars have worked to determine what factors may lead to the underprovision of public goods spending.
-Research in the past has associated racial diversity or changes in levels of diversity with the under-provision of public goods [@baqir_public_1999; @hopkins_diversity_2009].However, @trounstine_segregation_2016 argues that it is racial segregation, not diversity in and of itself, that results in the under-provision of public goods.
+Some scholars in the past have associated racial diversity or changes in levels of diversity with the under-provision of public goods [@baqir_public_1999; @hopkins_diversity_2009].
+However, @trounstine_segregation_2016 argues that it is racial segregation, not diversity in and of itself, that results in the under-provision of public goods.
 Trounstine’s analysis consists of two main parts.
@@
 
-```{r data_prep_imputations, include = FALSE}
+```{r setup, include = FALSE}
 
-# select the relevant rows from the rp dataset
-
-rp_impute <- rp %>%
-  select("winner", "medincinterp",
-             "biggestsplit", "H_citytract_multi_i", "diversityinterp",
-             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
-             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
-             "primary", "logpop", "year", "south", "midwest", "west", "geo_id2",
-             "H_citytract_NHW_i", "whiteideology_fill2") %>%
-  filter(winner == 1) %>%
-  mutate(medincinterp = medincinterp/1000,
-         year.f = as.factor(year))
-
-# apply the conditions in Stata regression to the fin_seg dataset
-
-fin_imp <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-# select the relevant variables to be imputed
-
-fin_imp <- fin_imp %>%
-  select(H_citytract_NHW_i, dgepercap_cpi, diversityinterp, pctblkpopinterp, pctasianpopinterp,
-         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
-         pctcollegegradinterp, logpop, geo_id2, chng5pctblk, chng5pctlatino, chng5pctasian,
-         ideology_fill, totaltractsf)
-
-miss_var_summary(fin_imp)
-miss_var_summary(rp_impute)
-
-```
-
-```{r obs_count, include = FALSE}
+# import both datasets
+library(haven)
+rp <- read_dta("racial_polarization_winners.dta")
+fin_seg<- read_dta("fin_seg.dta")
 
 # calculate number of original observations
-
-obs_fin_seg <- nrow(fin_imp)
-obs_rp <- nrow(rp_impute)
+obs_fin_seg <- nrow(fin_seg)
+obs_rp <- nrow(rp)
 
@@
 One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data, which substantially constrains the sample size used in the regression analysis.
-For example, the regression analysis in the main specification using the the original racial polarization dataset exludes %`r round((obs_rp - 91)/obs_rp, 2)` of the observations, and the regression analysis in the main specification using the original financial segregation data excludes %`r round((obs_fin_seg - 13742)/ obs_fin_seg, 2)` of observations from the original dataset.
+For example, the regression analysis in the main specification using the the original racial polarization exludes %`r (obs_rp - 91)/obs_rp` of the observations in the original dataset, and the regression analysis in the main specification using the original financial segregation data excludes %`r (obs_fin_seg - 13742)/ obs_fin_seg` of observations from the original dataset.
 As an extension of @trounstine_segregation_2016, I impute missing values in the original data using the mice package in R, which generates multivariate imputations using chained equations [@mice].
-Then, I use the multiply imputed datasets to re-estimate the original models, pooling the results to generate final pooled regression coefficients and parameters.
+Then, I use the imputed datasets to re-estimate the original models, pooling the results to final pooled regression coefficients and parameters.
 
@@
 Like in @trounstine_segregation_2016, I find that segregation is positively associated with political polarization and negatively associated with spending on public goods.
-However, the magnitude of the effects in most specifications has diminished and most results become statistically insignificant.
+However, the magnitude of the effects in most specifications has dminished and most results become statistically insignificant.
 While these findings do not necessarily challenge the results of @trounstine_segregation_2016, they do call into question the relative importance of segregation in determining public goods spending and political polarization and suggest that the results of @trounstine_segregation_2016 may not be quite as robust as once thought.
@@
 Despite some progress made towards racial equity in the U.S.
-on other fronts, residential racial segregation continues to be prevasive and deeply entrenched in society [@fischer_distinguishing_2004; @oliver_paradoxes_2010; @massey_american_1993].
+on other fronts, residential racial segregation in U.S.
+neighborhoods continues to be prevasive and deeply entrenched in society [@fischer_distinguishing_2004; @oliver_paradoxes_2010; @massey_american_1993].
 Research suggests that this kind of segregation has political consequences, as political cleavages in segregated cities tend to have racial as well as spatial dimensions [@massey_american_1993].
@@
 However, at the city or metropolitan level, the opposite seems to be true: when considering larger geographic areas, diversity and integration are correlated with racial tension, competition, prejudice, lower levels of cooperation, and lower spending on public goods [@oliver_paradoxes_2010; @baqir_public_1999; @hopkins_diversity_2009].
-While these differences in the expected effect of segregation on the geographic level may seem confusing at first, they make sense as they suggest that the most severely segregated areas are those that are diverse overall, but have many homogeneous neighborhoods.
-Thus, while people of different races co-exist within a highly segregated city, they live separately within their own neighborhoods, which creates an environment ripe for racial tension [@trounstine_segregation_2016].
+While these differences in the expected effect of segregation on the geographic level may seem confusing at first, they make sense as they suggest that the most severely segregated area is one that is diverse overall, but has many homogeneous neighborhoods.
+Thus, while people of different races co-exist within a highly segregated city, they live separately within their own neighborhoods, which creates an environment ripe for racial antagonism [@trounstine_segregation_2016].
 It is thus not simply the level of diversity or integration that matters for racial harmony and cooperation, but their patterns within a larger geographic framework [@trounstine_segregation_2016; @oliver_paradoxes_2010; @bharathi_public_2018].
 
-Political polarization along racial lines may lead to decreased public spending and goods provision because groups may have different preferences, which can make compromise hard, and because groups may preceive a disutility in out-groups receiving public goods expenditure [@baqir_public_1999].
+Political polarization along racial lines may lead to decreased public spending and goods provision because groups may have different preferences, which can make compromise hard, and because groups may preceive a disutility in out-groups receiving public goods expenditure @baqir_public_1999.
 @einstein_divided_2012 found evidence that racial segregation predicts large political divisions at the metropolitan level and that these divisions can create a lack of willingness to compromise and collaborate on local policy problems.
@@
 For example, @lee_ethnic_2018 finds evidence that larger inequalities within the political system favoring socially powerful groups, not local diversity patterns leading to decreased cooperation, may be a better explanation of failures in public goods provision in diverse areas.
-Others suggest that additional factors, such as income segregation, may be important confounding factors in public goods provision.
-@an_its_2018, for example, suggests that the more closely related income inequality is to racial inequality, the less investment is made in public goods, and that this interaction was a better predictor of public goods spending patterns than measures of diversity.
-There is, in fact, a variety of evidence suggesting that it is meaningful to consider the effects of income inequaltiy and diversity and segregation jointly [@an_its_2018; @massey_american_1993].
+Other suggests that additional factors, such as income segregation, may be important confounding factors in public goods provision.
+@an_its_2018, for example, suggests that the more closely related income inequality is to racial inequality, the less investment is made in public goods, and that this interaciton was a better predictor of public goods spending patterns than measures of diversity.
+inequality and diversity jointly.
+A variety of evidence suggests that it is meaningful to consider the effects of income inequaltiy and diversity and segregation jointly [@an_its_2018; @massey_american_1993].
 Given the active debate in the literature over the relaitonships between diversity, segregation, public spending, and other factors, it is increasingly important to re-examine previously reported findings as a means of robustness checks.
@@
 
-I was able to successfully replicate all of the main results from Trounstine (2016).
+For the most part, results from Trounstine (2016) were successfully replicated.
 All regressions and tables were fully replicated in R.
-As an example, in table X, I replicate Table 1 from page 713 of @trounstine_segregation_2016, which is also included as Figure 1 for comparison.
 However, I was unable to successfully replicate Trounstine (2016)’s marginal effects analyses and margins plots using R.
@@
 
-```{r include = FALSE}
-
-## regression 1 Table 1
-
-# fixed effects like a control variable
-
-# lmer(dependent ~ predictors + (random predictors | group level))
-
-# reml v. log likelihood: default in r appears to be log-likelihood. stata defaults to maximum likelihood
-
-# perform a multi-level mixed-effects linear regression of biggest split on the multi-group H index with controls for Herfindahl Diversity Index, % Asian interpolated, % Black interpolated, % Latino interpolated, median household income interpolated, % renters interpolated, percent college grads interpolated, a dummy indicating if there were biracial candidates in the election, a dummy  indicating if the election was nonpartisan, an indicator if the election was a primary, and the log population.
-The regression also includes fixed effects for year and region and random effects for cities (geo_id2).
-Diversity is  included because of the claim that more diverse populations will have more heterogeneous political preferences.
-The other fixed effect control variables are included because they are known to be potentially correlated with segregation.
-winner == 1 requires that there was a winner in the election.
-
-# regression specification. Apply REML = FALSE. The default for lmer() in R is
-# to optimize the restricted (residual) maximum likelihood (REML) whereas in
-# xtmixed in Stata the default is to optimize the log likelihood (which you can
-# do in lmer() in R by setting REML = FALSE), so this will match the STATA code
-
-m1 <- lmer(biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-## regression 2 Table 1
-
-# Perform the same regression as for Column 1 above but this time regress on the two-group calculation of Theil's H interpolated.
-It is unclear where the "diversity" variable is coming from, as the only variable related to diversity in the specificed dataset is diversityinterp.
-This is a problem that will need to be resolved.
-Essentially, this regression just tests an alternate specification to the first in which the segregation index in defined in terms of two-groups rather than multiple.
-
-m2 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-# perform the same regression as for column 2, but now add in a measure of
-# average white political ideology. The point of this is to control for ideology
-# so that the author can separate any effects of segregation from any potential
-# effects of white political ideology. This is important because it is possible
-# that segregation is just a proxy for white conservatism and thus failure to
-# include this variable could lead to ommitted variable bias.
-
-m3 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-```
-
-```{r results="asis", echo = FALSE}
-
-# create a stargazer table of the results
-
-t1 <- stargazer(m1, m2, m3, omit = c("year", "south", "midwest", "west"),
-                header = FALSE,
-                title = "\\textbf{Racial Polarization in Segregated Cities}",
-                single.row = TRUE,
-                no.space = FALSE,
-                add.lines = list(c("Wald Chi Squarred", "a", "b", "c")),
-                omit.stat = c("ll","rsq"),
-                covariate.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Diversity", "Percent Asian", "Percent Black", "Percent Latino", "Medain HH Income (1000s)", "Percent Renters", "Percent College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology", "Constant"),
-                notes = "This table displays...")
-
-# note: "This table displays the results of the replication effort of the analyses conducted in Trounstine (2016) using the racial polarization dataset.
-The replication code can be found on my personal [Github repository](https://github.com/mburzillo/new_final_project).
-The original table is displayed for comparison as Figure 1.")
-
-```
-
-![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016.
-My replication of these results can be found in Table 1 in this paper.](table_1.png)
-
 There was one interesting outcome from my attempt to replicate the original Stata code in R.
-Due to the differences in R and Stata in dealing with missing values, the results of my first replication of analyses using the financial segregation dataset were slightly different than the results in Stata from the original paper.
+Due to the differences in R and Stata in dealing with missing values, my first replication of analyses using the financial segregation dataset were slightly different than the results in Stata from the original paper.
 In order to exclude cities from her analysis with only one census tract, Trounstine conditions her regressions in Stata such that the value for the number of census tracts is greater than one.
@@
 Since this variable is used only as a conditional filter and not as a regression variable (and thus, the observations with missing values for number of census tracts are not dropped), Trounstine’s analysis includes 14 cities and 58 observations with missing values for census tracts in addition to cities with two or more census tracts.
-This is a potential oversight on the part of the author, and I would suggest also dropping observations with missing census tract data, or else imputing them given that the aim of her condition was to exclude cities without a sufficient number of census tracts.
-Nevertheless, dropping these values did not have much of an effect on the subsequent results, likely because they represent a small proportion of the overall sample.
+This is a potential oversight on the part of the author, and I would suggest also dropping observations with missing census tract data, or else imputing them.
+Nevertheless, dropping these values did not have much of an effect on the subsequent results.
 
@@
 The main model specification using the racial polarization dataset exludes `r (obs_rp - 91)` of the original  `r obs_rp` observations, or  %`r round(100*(obs_rp - 91)/obs_rp,2)` of the data.
-Additionally, the main model specification using the financial segregation data set excludes `r round(obs_fin_seg - 13742,2)` of the original `r obs_fin_seg` observations, or %`r round(100*(obs_fin_seg - 13742)/ obs_fin_seg,2)` of observations from the original dataset.
+Additionally, the main model specification using the financial segregation data set excludes `r obs_fin_seg - 13742` of the original `r obs_fin_seg` observations, or %`r round(100*(obs_fin_seg - 13742)/ obs_fin_seg,2)` of observations from the original dataset.
 
@@
 While there are a variety of different imputation methods that could have been employed, multiple imputation (such as the multiple multivariate imputations generated by mice) is desireable because instead of inputting a single value such as the mean for missing values, it instead uses the distribution of the available data to estimate multiple potential values for the missing data.
-As a result, multiple imputation helps to account for the uncertainty inherent in the imputation process and allows for the calculation of standard errors around estimators.
+As a result, multiple imputation helps to account for the uncertainty inherent in the imputation process and allows for the calculation of standard errors around estimaotrs.
 As a result, multiple imputation allows the researcher to more accurately assess the of uncertainty in the analysis in general.
@@
 Before performing the multiple imputations on the datasets, I first examined the missing data for patterns.
-To better understand any potential patterns in missing data, I plotted the pattern of missingness and created a histogram showing the frequency of missing values for those variables with missing values in figure X1 for the racial polarization data and figure X2 for the financial segregation data.
-Looking at figure X1, the histogram shows that the variables for the largest vote split along racial lines and the variable indicating whether or not the election had candidates of more than one race had by far the largest percentages of missing data, missing %`r round(sum(is.na(rp_impute$biggestsplit))/nrow(rp_impute)*100,2)` and  %`r round(sum(is.na(rp_impute$biracial))/nrow(rp_impute)*100,2)`, respectively.
+To better understand any potential patterns in missing data, I plotted the pattern of missingness for only and created a histogram showing the frequency of missing values for those variables with missing values in figure X1 for the racial polarization data and figure X2 for the financial segregation data.
+Looking at figure X1, the histogram shows that the variables for the largest vote split along racial lines and the variable indicating whether or not the election had candidates of more than one race had by far the largest percentages of missing data, missing %`r round(sum(is.na(rp$biggestsplit))/nrow(rp)*100,2)` and  %`r round(sum(is.na(rp$biracial))/nrow(rp)*100,2)`, respectively.
 It is important to note that the variable for the largest vote split along racial lines is the dependent variable in the regresison analysis, and thus, we are missing a large percentage of this key variable.
 From the plot on the right, we can see that approximately 42% of observations are complete (have no missing values).
-There seem to be a correspondence between missing a value for the largest vote split and missing a value for the biracial election indicator.
+There seem to be a correspondence between missing a value for biggest split and missing biracial.
 There also seem to be about 2% of values for wich most of the variables are missing.
@@
 
-```{r rp_missing_plot, include = FALSE, warning = FALSE}
-
-# don't show the warning, it's just an irrelevant column missing a name
-
-# plot the missing variables if desired
-
-rp_facet <- rp_impute %>%
-   select("medincinterp",
-             "biggestsplit", "diversityinterp",
-             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
-             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
-               "south", "midwest", "west", "whiteideology_fill2", "year")
-
-# gg_miss_var(rp_impute, show_pct = TRUE)
-
-```
-
-```{r rp_aggr_plot, echo = FALSE}
-
-# select only the missing values
-
-rp_aggr <- rp_impute %>%
-   select("medincinterp",
-             "biggestsplit", "diversityinterp",
-             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
-             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
-               "south", "midwest", "west", "whiteideology_fill2")
-
-# create an aggr plot for the missing values
-
-aggr(rp_aggr, bars = TRUE, col=c('navyblue','red'), numbers=TRUE, cex.axis=.5, gap=1, ylab=c("Proporiton of Missing Values","Combinations"))
-
-# caption for this plot when I figure out how to do it...
-: This plot examines the pattern of missing data in the the original racial polarization dataset from Trounstine (2016).
-The plot on the left shows the percentage of missing data for each variable with missing data and reveals that the variables that are missing by far the most data are the largest vote split along racial lines (biggestsplit) and the variable indicating whether or not the election had candidates of more than one race (biracial).
-The plot on the right shows the pattern of missingness among the variables.
-We can see that approximately 42% of observations are complete (have no missing values).
-There seems to be a correspondence between missing a value for biggest split and missing biracial.
-There also seem to be about 2% of values for which most of the variables are missing.
-However, most observations are not missing more than 2-3 values.
-
-```
+### need to fix numbers below because this was from the whole fin_seg and not from the one filtered via the regression coefficients
 
@@
 In this dataset, there is a very high proportion of missing variables for a number of variables.
-For example, there are `r sum(is.na(fin_imp$H_citytract_NHW_i))` missing values for the segregation index, which is the main independent variable, or %`r round(sum(is.na(fin_imp$H_citytract_NHW_i))/nrow(fin_imp)*100,2)` of the data.
+For example, there are a `r sum(is.na(fin_seg$H_citytract_NHW_i))` missing values for the segregation index, which is the main independent variable, or %`r round(sum(is.na(fin_seg$H_citytract_NHW_i))/nrow(fin_seg)*100,2)` of the data.
 In this dataset, there are also many more observations for which values are missing for multiple variables in comparison to the racial polarization dataset.
-In total, a mere %`r .0058*100` of observations are complete for all variables included in the main specification for the financial segregaion dataset.
-
-```{r fin_missing_plot, include = FALSE}
-
-miss_var_summary(fin_imp)
-
-gg_miss_var(fin_imp, show_pct = TRUE)
-
-```
-
-```{r fin_aggr_plot, echo = FALSE}
-
-# select all variables with missing values for the aggr plot
-
-fin_imp_aggr <- fin_imp %>%
-  select(ideology_fill, H_citytract_NHW_i, chng5pctblk, chng5pctlatino, chng5pctasian, diversityinterp, pctblkpopinterp, pctasianpopinterp,
-         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
-         pctcollegegradinterp)
-
-new_try <- head(fin_imp_aggr, 20)
-
-aggr(new_try, plot = TRUE, bars = FALSE, col=c('navyblue','red'), numbers=TRUE)
-
-# create the aggr plot
-
-aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.5, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
-title(main = "Patterns of Missingness in the Financial Segregation Data",
-      sub = "Is this a caption?
-qiufwnjekfewkfnwein\nwefjwenmf wiufnwqjenf ewfuiwjnef nfijefnwjenfkqwjnf lqwjefnjqwefjwnef winfjqwhf hjwefwiuefief welfiunqlfjnqkjwe qqfniquwenjfjq iqfnjkjeq rfiunfj q")
-
-# this plot tells us that only .58% of the data are complete (not missing anything)
-
-# caption for this plot when I figure out how to do it...
-: This plot examines the pattern of missing data in the the original financial segregation dataset from Trounstine (2016).
-The plot on the left shows the percentage of missing data for each variable with missing data and reveals that a large number of variables are missing the vast majority of data.
-The plot on the right shows the pattern of missingness among the variables.
-We can see that only .58% of observations are complete (have no missing values), and a large majority of the observations are missing data for many variables.
-
-```
+In total, a mere XX% of observations are complete for all variables included in the main specification for the financial segregaion dataset.
 
@@
 For the financial segregation dataset, however, I only imputed values for the main independent variable, the segregation index, and a few other variables, although all variables used in the analysis were included in the data subset input into the mice function.
-More of the data could not be imputed from the financial segregation dataset due to computing and time constraints for this project given the dataset's large size and high proportion of missing values.
-
-```{r rp_imputation, include = FALSE}
-
-# Perform multiple imputations using the cart method. Because of the time it
-# takes to run this function, I turned the results into a dataset to load in
-# instead of re-running everytime.
-
-max_it = 20
-
-imp_1_rp <- mice(rp_impute, method = "cart", maxit = 20)
-
-# can use the line below to check that there are now no missing values
-
-# gg_miss_var(complete(imp_1_rp), show_pct = TRUE)
-
-```
-
-```{r fp_imputations, include = FALSE}
-
-# perform multiple imputations.
-We have the same issue here with the default method as with the previous dataset so we use CART.
-Additionally, because of the extremely large size of this dataset, we choose to only impute the variable H_citytract_NHW_i, as it is the most frequently missing variable and also out main independent variable.
-Just imputing this allows us to include way more observations in the regression than the original data despite the still large number of NAs overall.
-One concern here would be that if there was some reason that this variable was missing rather than other variables that only imputing this variable could lead to some bias in the results.
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp, maxit=0, print=F)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs <- mice(fin_imp, method = meth, maxit = 5)
-
-# now there are manyb fewer missing variables!!!
-
-miss_var_summary(complete(imp_fs))
-
-head(complete(imp_fs))
-
-miss_var_summary(fin_imp)
-
-```
-
-```{r new_imp}
-
-fin_imp <- fin_imp %>%
-  mutate(nas = is.na(H_citytract_NHW_i) + is.na(dgepercap_cpi) + is.na(diversityinterp) + is.na(pctblkpopinterp)  + is.na(pctasianpopinterp) + is.na(pctlatinopopinterp) + is.na(medinc_cpi) + is.na(pctlocalgovworker_100) + is.na(pctrentersinterp) + is.na(pctover65) + is.na(pctcollegegradinterp) + is.na(logpop) + is.na(geo_id2) + is.na(chng5pctblk) + is.na(chng5pctlatino) + is.na(chng5pctasian) + is.na(logpop) + is.na(geo_id2) + is.na(chng5pctblk) + is.na(chng5pctlatino) + is.na(chng5pctasian) + is.na(ideology_fill))
-
-fin_imp %>%
-  ggplot(aes(x = nas)) +
-  geom_histogram()
-
-fin_imp %>%
-  group_by(nas) %>%
-  summarise(n())
-
-# exclude all observations with 17 out of 22 nas
-
-fin_imp_sub <- fin_imp %>%
-  filter(nas < 17)
-
-nrow(fin_imp_sub)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_sub, maxit=0, print=F)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-new_imp_fs <- mice(fin_imp_sub, method = meth, maxit = 5)
-
-miss_var_summary(complete(new_imp_fs))
-```
+More of the data could not be imputed from the financial segregation dataset due to computing and time constraints for this project given the dataset's large size and proportion of missing values.
 
@@
 However, this is more or less to be expected given the small number of imputations performed in these cases.
-Thus, and especially because there are so few of these values missing in the actual datasets, this was not a major concern.
+Thus, and especially because there are so few of these values in the actual imputed datasets, this was not a major concern.
 See figures X and X1 to see the density plots of the imputed values overlayed on the density plots of the original variables.
-The rest of the plots and results of the diagnostic tests discussed here are presented in the Appendix.
+The rest of the plots and results of the diagnostic tests discussed ehre are presented in the Appendix.
 
-```{r rp_densityplot, echo = FALSE}
-
-densityplot(imp_1_rp)
-
-```
-
-```{r rp_imp_plot, include = FALSE}
-
-# ideally, the fits will intertwine and not exhibit any trends at later iterations.
-This seems to generally be the case.
-There are some issues with the results for some of the variables with very few missing values, which makes sense as we would expect the mean to be less reliable due to the law of large numbers and thus convergence is more difficult.
-However, since these are so few values, it is less important about how robust they are.
-
-plot(imp_1_rp)
-
-```
-
-```{r rp_stripplot, include = FALSE}
-
-# we can also check the imputed values against the original values using stripplot().
-Each column in each subplot represents a separate iteration.
-The magenta points represent the imputed data.
-The values of the variable in questions are along the y axis.
-We expect the spread of the data to be similar if the imputations were done well.
-If the data were missing completely at random, then the imputed data should have the same distribution as the original data.
-In particular, we want to be sure that the imputations are within a plausible range of the data.
-This is the case for all of our imputed variables, and there does not seem to be cause for alarm from these results.
-
-# this looks good? All reasonable values...
-
-stripplot(imp_1_rp)
-
-stripplot(imp_1_rp, biggestsplit)
-
-```
-
-```{r fs_densityplot, echo = FALSE}
-
-densityplot(imp_fs)
-densityplot(x=imp_fs , data= ~ H_citytract_NHW_i + chng5pctblk + 
-       chng5pctlatino + chng5pctasian + ideology_fill)
-
-```
-
-```{r fs_imp_plot, include = FALSE}
-
-# ideally, the fits will intertwine and not exhibit any trends at later iterations.
-This seems to generally be the case.
-There are some issues with the results for some of the variables with very few missing values, which makes sense as we would expect the mean to be less reliable due to the law of large numbers and thus convergence is more difficult.
-However, since these are so few values, it is less important about how robust they are.
-
-plot(imp_fs)
-
-```
-
-```{r fs_stripplot, include = FALSE}
-
-# we can also check the imputed values against the original values using stripplot().
-Each column in each subplot represents a separate iteration.
-The magenta points represent the imputed data.
-The values of the variable in questions are along the y axis.
-We expect the spread of the data to be similar if the imputations were done well.
-If the data were missing completely at random, then the imputed data should have the same distribution as the original data.
-In particular, we want to be sure that the imputations are within a plausible range of the data.
-This is the case for all of our imputed variables, and there does not seem to be cause for alarm from these results.
-
-# this looks good? All reasonable values...
-
-stripplot(imp_fs, H_citytract_NHW_i)
-
-stripplot(imp_fs, chng5pctblk)
-
-stripplot(imp_fs, chng5pctlatino)
-
-stripplot(imp_fs, chng5pctasian)
-
-stripplot(imp_fs, ideology_fill)
-
-```
-
-Given the promising results of the diagnostic checks, I next proceeded to re-estimate the original model using the multiply imputed datasets, pooling the results to produce final pooled regression coefficients and parameters.
-The results for the analyses using the racial polarization dataset are presented in tables 1-3.
-
-```{r rp_imputations, include = FALSE}
-
-# Now that we have imputed the missing data, we can re-run the analyses from the
-# original paper to see how and if this changes the analysis. We can use the
-# with() function from the mice package to fit each of the imputed datasets to
-# the model and then pool the results afterwards.
-
-# regression 1: fit multiple imputed datasets
-
-fit_imp_1_rp <- with(imp_1_rp, lmer(formula = biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
-
-# pool and summarize the analyses
-
-pool_imp_1_rp <- pool(fit_imp_1_rp)
-imp_1_rp_sum <- summary(pool_imp_1_rp)
-
-## regression 2 Table 1: fit multiple imputed datasets
-
-#formula = biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2)
-
-fit_imp_2_rp <- with(imp_1_rp, lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
-
-# pool and summarize the analyses
-
-pool_imp_2_rp <- pool(fit_imp_2_rp)
-imp_2_rp_sum <- summary(pool_imp_2_rp)
-
-## regression 3 Table 1 with new data
-
-#formula = biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2)
-
-fit_imp_3_rp <- with(imp_1_rp, lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
-
-# pool and summarize the analyses
-
-pool_imp_3_rp <- pool(fit_imp_3_rp)
-imp_3_rp_sum <- summary(pool_imp_3_rp)
-
-```
-
-The results of the model with the new dataset are slightly different in comparison to the original results from Trounstine (2016).
-With the imputed data, we now have a total of `r nrow(complete(rp_impute))` observations in our model as compared to the original model, which had only 91 observations.
-Interestingly, while the sign of the coefficient on the main variable of interest, the Theil's H segregation index, is the same and the standard error has decreased slightly, the result has become statisically insignificant and the 95% confidence interval contains zero.
-Thus while these results still suggest that segregation may be associated with increased political polarization, they confer a lesser degree of certainty than Trounstine's original analysis.
-The coefficients for % Black population, % Latino population, and median household income have also switched signs, and all coefficients except the indicator for a biracial election are also statistically insignificant, as was the case in the original analysis.
-The coefficient on the indicator for a primary election, has also changed from being significant in the original analysis to insignificant here.
-In general, the standard errors on the coefficients have decreased slightly.
-
-```{r results_printing_rp_impute_regressions_1, results = "asis", echo=FALSE}
-
-# print results of 1st regression
-
-imp_1_rp_sum_table <- as.data.frame(imp_1_rp_sum %>% 
-  select(term, estimate, std.error, p.value)) %>%
-  head(13)
-print(imp_1_rp_sum_table)
-
-stargazer(imp_1_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Multigroup Segregation Index}")
-
-```
-
-In the second and third regressions, the results are similar.
-The main coefficient on segregation index has decreased in magnitude, although in these specifications, it remains statistically significant.
-The other coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian, Black, and Latino have all switched signs.
-Standard errors have also reduced slightly in these specifications compared to the original analysis in @trounstine_segregation_2016.
-
-```{r results_printing_rp_impute_regressions_2, results = "asis", echo=FALSE}
-
-# print results of 2nd regression
-
-imp_2_rp_sum_table <- as.data.frame(imp_2_rp_sum %>% 
-  select(term, estimate, std.error, p.value)) %>%
-  head(13)
-print(imp_2_rp_sum_table)
-
-stargazer(imp_2_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Two-Group Segregation Index}")
-
-```
-
-```{r results_printing_rp_impute_regressions_3, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_3_rp_sum_table <- as.data.frame(imp_3_rp_sum %>% 
-  select(term, estimate, std.error, p.value)) %>%
-  head(13)
-print(imp_3_rp_sum_table)
-
-stargazer(imp_3_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Ideology Control}")
-```
-
-For the financial segregation dataset, we similarly fit each of our 5 imputed datasets to the original models from @trounstine_segregation_2016 using this data and then pool the results for each.
-The pooled results are presented in tables 4-6.
-
-# FS data results
-
-```{r fs_imputed_pooled_regressions, include = FALSE}
-# Main Analysis 2: Imputations
-
-## regression 1 Table 2
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-## regression 2 Table 2
-
-# fit multiple imputed datasets
-
-fit_imp_felm2 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm2 <- pool(fit_imp_felm2)
-imp_felm2_sum <- summary(pool_imp_felm2)
-
-## Regression 3 Table 2
-
-fit_imp_felm3 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm3 <- pool(fit_imp_felm3)
-imp_felm3_sum <- summary(pool_imp_felm3)
-
-```
-
-```{r fs_imputed_data_included_calc, include = FALSE}
-# how many observations were included in those 3 analyses?
-
-# basic filter for table for all regressions
-
-# xtreg dgepercap_cpi H_citytract_NHW_i diversityinterp pctblkpopinterp
-# pctasianpopinterp pctlatinopopinterp medinc_cpi pctlocalgovworker_100
-# pctrentersinterp pctover65 pctcollegegradinterp logpop if totaltracts>1 &
-# dgepercap_cpi~=0,fe vce(cluster geo_id2)
-
-fin <- complete(imp_fs) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
-
-# create dge variable used in regression
-
-fin_dge <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_dge_tab <- tibble(
-  Variable = "Direct General Expenditure per Capita",
-  Obs = nrow(fin_dge),
-  Mean = mean(fin_dge$dgepercap_cpi, na.rm = T),
-  SD = sd(fin_dge$dgepercap_cpi, na.rm = T),
-  Min = min(fin_dge$dgepercap_cpi, na.rm = T),
-  Max = max(fin_dge$dgepercap_cpi, na.rm = T)
-)
-
-# now we have 73,119 observations compared to 13,742. Calculation:
-
-nrow(fin_dge)
-
-# number of missing seg indexes before imputation: 282334
-
-# number missing now: 222957 -> Calculation:
-
-new_missing <- sum(is.na(complete(imp_fs)$H_citytract_NHW_i))
-
-# calculate number of observations we added to the sample: 59,377
-
-num_added <- 282334 - new_missing
-
-# INTERPRETATION BEFORE AFTER CHANGED The results of the first regression present a stark difference to the results of @trounstine_segregation_2016.
-Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant.
-Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
-The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.
-
-```
-
-The results of the first regression present a stark difference to the results of @trounstine_segregation_2016.
-Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant.
-Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
-The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.
-
-The results of the first regression indicate that Trounstine's results are robust to the inclusion of the imputed data, which led to the inclusion of an additional 59,377 observations in the analysis.
-The coefficients, standard errors, and significance levels are essentially unchanged.
-The same is largely true for the second and third specifications, but the magnitude of the coefficient on the segregation decreases slightly.
-
-```{r results_printing_fs_impute_regressions_1, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_felm1_sum_table <- as.data.frame(imp_felm1_sum %>% 
-  select(term, estimate, std.error, p.value))
-print(imp_felm1_sum_table)
-
-stargazer(imp_felm1_sum_table,
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Expenditure per Capita}")
-```
-
-```{r results_printing_fs_impute_regressions_2, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_felm2_sum_table <- as.data.frame(imp_felm2_sum %>% 
-  select(term, estimate, std.error, p.value))
-print(imp_felm2_sum_table)
-
-stargazer(imp_felm1_sum_table,
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Changing Demographics}")
-```
-
-```{r results_printing_fs_impute_regressions_3, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_felm3_sum_table <- as.data.frame(imp_felm3_sum %>% 
-  select(term, estimate, std.error, p.value))
-print(imp_felm3_sum_table)
-
-stargazer(imp_felm1_sum_table,
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Ideology Control}")
-```
-
-# FS NEW data results
-
-```{r new_fs_imputation_tries, include = FALSE}
-# Main Analysis 2: Imputations
-
-## regression 1 Table 2
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-## regression 2 Table 2
-
-# fit multiple imputed datasets
-
-fit_imp_felm2 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm2 <- pool(fit_imp_felm2)
-imp_felm2_sum <- summary(pool_imp_felm2)
-
-## Regression 3 Table 2
-
-fit_imp_felm3 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm3 <- pool(fit_imp_felm3)
-imp_felm3_sum <- summary(pool_imp_felm3)
-
-# INTERPRETATION BEFORE AFTER CHANGED The results of the first regression present a stark difference to the results of @trounstine_segregation_2016.
-Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant.
-Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
-The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.
-
-print(imp_felm1_sum)
-print(imp_felm2_sum)
-print(imp_felm3_sum)
-
-# large amount of data missing across the board in terms of years
-
-gg_miss_var(fin_dge, facet = year, show_pct = TRUE)
-
-# can't really tell anything about the region facet since a lot of obs missing region data
-
-gg_miss_var(fin_imp_extra, facet = region, show_pct = TRUE)
-
-# not necessarily a significant pattern across states either
-
-gg_miss_var(fin_imp_extra, facet = statecode, show_pct = TRUE)
-
-```
-
-# FS NEW AGAIN
-
-```{r}
-cities_to_keep <- c("Austin City", "Baltimore City", "Charlotte City", "Chicago City", "Cleveland City", "Columbus City", "Dallas City", "Denver City", "Detroit City", "Houston City", "Indianapolis", "Jacksonville", "Los Angeles City", "Memphis City", "Milwaukee City", "New York City", "Oklahoma City City", "Philadelphia City", "Phoenix City", "San Antonio City", "San Diego City", "San Francisco City", "San Jose City", "Tucson City", "Washington City")
-
-# apply the conditions in Stata regression to the fin_seg dataset
-
-fin_imp_cities <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0, cityname %in% cities_to_keep) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-# select the relevant variables to be imputed
-
-fin_imp <- fin_imp %>%
-  select(H_citytract_NHW_i, dgepercap_cpi, diversityinterp, pctblkpopinterp, pctasianpopinterp,
-         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
-         pctcollegegradinterp, logpop, geo_id2, chng5pctblk, chng5pctlatino, chng5pctasian,
-         ideology_fill)
-```
-
-```{r looking_at_original_data, include = FALSE}
-
-range(fin_seg$totaltractsf, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_seg %>%
-  ggplot() +
-  geom_histogram(aes(x = totaltractsf))
-
-range(fin_seg$logpop, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_seg %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-# add back in year, region, and statecode to be able to look at this
-
-fin_imp_old <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-fin_imp_extra <- fin_imp %>%
-  mutate(year = fin_imp_old$year,
-         region = fin_imp_old$region,
-         statecode = fin_imp_old$statecode)
-
-# large amount of data missing across the board in terms of years
-
-gg_miss_var(fin_imp_extra, facet = year, show_pct = TRUE)
-
-# can't really tell anything about the region facet since a lot of obs missing region data
-
-gg_miss_var(fin_imp_extra, facet = region, show_pct = TRUE)
-
-# not necessarily a significant pattern across states either
-
-gg_miss_var(fin_imp_extra, facet = statecode, show_pct = TRUE)
-
-```
-
-```{r looking_at_Trounstine_data, include = FALSE}
-
-# basic filter for table for all regressions
-
-# xtreg dgepercap_cpi H_citytract_NHW_i diversityinterp pctblkpopinterp
-# pctasianpopinterp pctlatinopopinterp medinc_cpi pctlocalgovworker_100
-# pctrentersinterp pctover65 pctcollegegradinterp logpop if totaltracts>1 &
-# dgepercap_cpi~=0,fe vce(cluster geo_id2)
-
-fin_trounstine <-fin_seg %>%
-  filter(totaltractsf >1 | is.na(totaltractsf)) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
-
-# create dge variable used in regression
-
-fin_dge_trounstine <-fin_trounstine %>% filter(dgepercap_cpi != 0)
-
-range(fin_dge_trounstine$totaltractsf, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_dge_trounstine %>%
-  ggplot() +
-  geom_histogram(aes(x = totaltractsf))
-
-range(fin_dge_trounstine$logpop, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_dge_trounstine %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-```
-
-```{r looking_at_imputed_data}
-
-fin_new_imp <- complete(new_imp_fs) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
-
-range(fin_new_imp$logpop, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_new_imp %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-```
-
-# Conclusion
-
-Why cities differ in their amount of spending on public goods is an interesting questions that is frequently debated in the literature.
-@trounstine_segregation_2016 posits that segregation may be an important underlying cause of the underprovsion of public goods.
-Finding evidence that residential segregation by race increases political partisanship, @trounstine_segregation_2016 argues that residential segregation can increase division and make cooperation amongst competing groups difficult, which results in decreased spending on public goods.
-The findings of @trounstine_segregation_2016 are particularly important because they suggest that segregation, as defined by many homogeneous neighborhoods within a larger diverse geographical area, is the key factor in disinvestment in public goods.
-This contradicts previous research which has suggested that levels of diversity were instead most important (see for example @baqir_public_1999 or @hopkins_diversity_2009).
-While @trounstine_segregation_2016 still represents relatively new reasearch as of 2020, it has yet to be fully vetted by additional research.
-Furthermore, some research that has been published on the topic since its publication suggests that other factors such as larger inequities in the political system favoring socially powerful groups [@lee_ethnic_2018] or the interaction of income and racial inequality [@an_its_2018] may be more important in explaining public goods provisions.
-
-I first worked to provide a check on the analysis presented in @trounstine_segregation_2016 by attempting to replicate the work in R.
-I was able to successfully replicate all of the main results from @trounstine_segregation_2016, with the exception of a few of a few marginal analyses of the complex, multi-level models which, to my knowledge, are currently not supported by available R packages.
-I was, however, able to successfully replicate these results in Stata.
-
-As an additional robustness check I also tested the models in @trounstine_segregation_2016 by re-running them with additional data that I imputed from missing values in the original datasets.
-The large number of missing values in both of the datasets used in @trounstine_segregation_2016's main analysis created a concern for potential bias in the original results and a lack of representativeness due to the large amount of data excluded from the regression analysis due to missing values.
-Thus, I used the mice package in R to create multiply imputed datasets, upon which I re-ran the models and pooled the results to generate the final model coefficients and parameters.
-
-The results of the data imputation exercise differed between the two datasets.
-For the analyses using the smaller, racial polarization dataset, the results from the imputed data resulted in a smaller magnitude of the coefficient on the main independent variable, and also made it statistically insignificant in the main model specification.
-This suggests that the segregation index may not have as strong of a positive association with political polarization as @trounstine_segregation_2016 suggests.
-However, for the analyses using the much larger financial segregation dataset, the results of the models using the multiply imputed data largely mirrored the results of @trounstine_segregation_2016, and the coefficients and significance levels were essentially the same between the two, with the standard errors on the model estimates being generally slightly lower for the analyses using the imputed data.
-This provides strong support for @trounstine_segregation_2016's finding that residential racial segregation is associated with diminshed spending on public goods.
-
-The replication exercise and robustness check using multiply imputed data here provide strong evidence that residential segregation along racial lines does in fact correlate negatively with spending on a variety of public goods.
-What my analysis calls more into question, is by what mechanism this happens.
-Using the multiply imputed data, I still found some evidence that segregation may be associated with increased political polarization which @trounstine_segregation_2016 suggests may lead to diminished public goods spending; however, the effect size is much smaller than that found in @trounstine_segregation_2016, and some of the results have become insignificant.
-It is possible that other mechanisms may be more important in explaining why segregation might be associated with decreased spending on public goods.
-For example, it could be that there is an important interaction effect between income and segregation, as others have previously suggested, or there could be some other intervening mechanism or a confounding variable that is leading to the negative association between segregation and lower spending on public goods.
-@trounstine_segregation_2016 has identified an important relationship between segregation and the provision of public goods.
-However, my analysis suggests that further research is needed to assess the potential mechanisms by which residential segregation by race or even a confounding variable may result in dimished spending.
-If this mechanism can be better understood, than it will be possible to more effectively understand and address the underprovision of public goods, which may inhibit social mobility and unfairly disadvantage certain groups.
-
-# Appendix
-
-```{r felm, eval = FALSE}
-
-# Main Analysis 2
-
-## regression 1 Table 2
-
-# The following is a fixed effects model regression with clustering around
-# geo_id2. It mandates that total census tracts in the city is greater than 1,
-# which we want because our measure of evenness of racial spread is constant for
-# cities with only one tract by our definition (which requires comparing tracts
-# within cities). It also mandates that Direct General Expenditures (DGE) per
-# capita, CPI adjusted is not equal to 0, which would be problematic and
-# indicate a potential data error. This regression regresses the DGE per capita
-# on the the two-group calculation of  Theil's H interpolated. Controls are
-# included for diversity and the % populations of Blacks, Asians, and Latinos to
-# help identify whether it is actually diversity that drives down spending.These
-# demographic controls also help to account for the fact that whites and
-# minorities tend to perfer different levels of government spending in general.
-# This will help isolate the effects of segregation v. other forms of diversity
-# on public spending. Other controls for Median household income, CPI adjusted,
-# percent over 65, percent college grads, percent local government workers, log
-# population help control for additional factors related to segregation and
-# expenditure. Controls for percent renters interpolated and Median household
-# income also help to control for the general wealth of cities, which could be a
-# potential driver of public spending. Fixed effects for cities are also
-# included  so that the author can examine the effect of segregation in the same
-# city over  time, which also helps control for many other factors not otherwise
-# taken into account (such as city age)
-
-# apply the conditions in Stata regression
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-# felm(y~x | factor(fe1) + factor(fe2) | 0 | clustervar)
-
-felm1 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-## regression 2 Table 2
-
-# This regression is the same as above except instead of using diversity, a new
-# control is added for the five year changes in racial group shares. The goal
-# here is to see whether or not changes in diversity are a driving factor
-# (rather than absolute levels of diversity).
-
-felm2 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-## Regression 3 Table 2
-
-# Column 3
-
-# As in column 3 of table 1, this regression simply adds in a control for  mean  ideology of city residents from General Social Survey (GSS) to control for the  possibility that ideology that segregated cities are more ideologically  conservative and that the conservative nature of segregated cities is what actually drives the effect.
-
-felm3 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-```
-
-```{r main_fp_tables, results = "asis", eval = FALSE}
-
-# create main table for table 3
-
-table2 <- stargazer(felm1, felm2, felm3, omit = c("year", "south", "midwest", "west"), 
-                    header = FALSE,
-                    title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures}")
-
-```
-
-```{r, eval = FALSE}
-
-# Main Analysis 3
-
-## regression 1 Table 3
-
-# Column 1
-
-# The following is a fixed effects model regression with clustering once again around geo_id2.
-Again, the if statements at the end mandate that total census tracts in the city is greater than 1, which we want because our measure of evenness of racial spread is constant for cities with only one tract by our definition (which requires comparing tracts within cities).
-They also mandate that the highways per capita, CPI adjsuted with no cap extend (lagged 5 years) is not equal to 0, which would be problematic and indicate a potential data error.
-The dependent variable here is highways per capita, CPI adjsuted with no cap extend (lagged 5 years) and it is regressed on the two group calculation of Theil's H, interpolated.
-Controls are added for diversity, percent population of Blacks, Asians, and Latinos, and median household CPI adjusted income as well as for % local government worker hundreds, percent rentership, percent over 65, percent college graduates, and the log of the population.
-This essentially examines the effect of segregation on the specific public good of highways.
-As in the previous table's regressions, fixed effects for cities are also included so that the author can examine the effect of segregation in the same city over time, which also helps control for many other factors not otherwise taken into account (such as city age) *
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), highwayspercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_1 <- felm(highwayspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-## regression 2 Table 3
-
-# Column 2
-
-# This is the same regression as column 1, but this time the dependent variable
-# is police per capita, CPI adjusted with no cap extend. This essentially
-# examines the effect of segregation on the specific public good of police per
-# capita.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), policepercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_2 <- felm( policepercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 3
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), parkspercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-# This is again the same regression, but this time the dependent variable is
-# parks per capita, CPI adjusted with no cap extend. This essentially examines
-# the effect of segregation on the specific public good of parks.
-
-felm2_3 <- felm(parkspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 4
-
-# This is again the same regression, but this time the dependent variable is
-# sewers per capita, CPI adjusted with no cap extend. This essentially examines
-# the effect of segregation on the specific public good of sewers.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), sewerspercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_4 <- felm(sewerspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 5
-
-# This is again the same regression, but this time the dependent variable is
-# Welfare, Health, Housing per capita, CPI adjusted, no cap expend. This
-# essentially examines the effect of segregation on the specific public good of
-# welfare and housing.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), welfhoushealthNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_5 <- felm(welfhoushealthNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 6
-
-# This is again the same regression, but this time the dependent variable is own
-# source of general revenue per capita, CPI adjusted. This essentially examines
-# the effect of segregation on the specific public good of own source revenue.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), genrevownpercap_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_6 <- felm(genrevownpercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-```
-
-```{r results = "asis", eval = FALSE}
-table3a <- stargazer(felm2_1, felm2_2, felm2_3, 
-          omit = c("year", "south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Public Goods A}")
-
-table3b <- stargazer(felm2_4, felm2_5, felm2_6, 
-          omit = c("year", "south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Public Goods B}")
-
-#star_sidewaystable(table3)
-```
-
-```{r iv_regs, eval = FALSE}
-
-## regression 1 Table 5
-
-# Top Row
-
-# Column 1
-
-# This is an instrumental variable regression with DGE per capita, adjusted by the CPI, as the dependent variable and total number of waterways as the instrumental variable for segregation.
-The instrument includes the log of the population in the first stage because the number of waterways is positively correlated to population and population is positively correlated with segregation.
-The control variables are the same as those in the regressions for Table 2 except for 2 changes: since the number of waterways does not change, there is no need for city fixed effects.
-Instead, we include fixed effects for the region and year.
-A lagged version of the dependent variable (dgepercap_cpilag) is added to the regressions to account for the high correlation between  observations for the same city over time and because changes in local budgets typically are incremental (NOTE: why exactly do we do this/why does it help/why not do it in the non-intstrumental regressions?).
-
-fin_seg_1 <- fin_seg %>%
-  filter(dgepercap_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-glimpse(fin_seg_1$medincinterp)
-
-# good explanation: http://eclr.humanities.manchester.ac.uk/index.php/IV_in_R
-
-# iv = ivreg(second stage regression | instrument1 + instrument2 )
-
-ivreg1 <- ivreg(dgepercap_cpi ~ H_citytract_NHW_i + dgepercap_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + dgepercap_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_1)
-
-# Column 2
-
-# this is the same regression as for column 1 but now we use the dependent variable highwayspercapNC_cpi to assess the effect of the instrumental  variable on highways per capita *
-
-fin_seg_2 <- fin_seg %>%
-  filter(highwayspercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg2 <- ivreg(highwayspercapNC_cpi ~ H_citytract_NHW_i + highwayspercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + highwayspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_2)
-
-# Column 3
-
-# this is the same regression as for column 1 but now we use the dependent variable policepercapNC_cpi to assess the effect of the instrumental variable on police per capita
-
-fin_seg_3 <- fin_seg %>%
-  filter(policepercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg3 <- ivreg(policepercapNC_cpi ~ H_citytract_NHW_i + policepercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + policepercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_3)
-
-# Column 4 this is the same regression as for column 1 but now we use the
-# dependent variable parkspercapNC_cpi to assess the effect of the instrumental
-# variable on parks per capita
-
-fin_seg_4 <- fin_seg %>%
-  filter(parkspercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg4 <- ivreg(parkspercapNC_cpi ~ H_citytract_NHW_i + parkspercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + parkspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_4)
-
-# Bottom Row
-
-# Column 1
-
-# this is the same regression as for column 1 but now we use the dependent
-# variable sewerspercapNC_cpi to assess the effect of the instrumental variable
-# on sewers per capita
-
-fin_seg_5 <- fin_seg %>%
-  filter(sewerspercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg5 <- ivreg(sewerspercapNC_cpi ~ H_citytract_NHW_i + sewerspercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + sewerspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_5)
-
-# Column 3
-
-# this is the same regression as for column 1 but now we use the dependent variable genrevownpercap_cpi to assess the effect of the instrumental variable on own source revenue per capita
-
-fin_seg_6 <- fin_seg %>%
-  filter(genrevownpercap_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg6 <- ivreg(genrevownpercap_cpi ~ H_citytract_NHW_i + genrevownpercap_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + genrevownpercap_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_6)
-
-# Column 2
-
-# this is the same regression as for column 1 but now we use the dependent
-# variable welfhoushealthNC_cpi to assess the effect of the instrumental
-# variable on welfare per capita
-
-fin_seg_7 <- fin_seg %>%
-  filter(welfhoushealthNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg7 <- ivreg(welfhoushealthNC_cpi ~ H_citytract_NHW_i + welfhoushealthNC_cpilag  + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + welfhoushealthNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_7)
-
-summary(ivreg7)
-
-```
-
-# Table 5
-
-```{r results = "asis", echo = FALSE}
-
-table5a <- stargazer(ivreg1, ivreg2, ivreg3, ivreg4,
-          omit = c("y5", "y6", "y7", "y8", "y9", "northeast", "south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach A}")
-
-table5b <- stargazer(ivreg5, ivreg6, ivreg7,
-          omit = c("y5", "y6", "y7", "y8", "y9", "northeast","south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach B}")
-```
-
-```{r import_data, include = FALSE}
-
-# make a list of the cities included in the analysis to filter out from the main
-# dataset as specified in the table
-
-cities_to_keep <- c("Austin City", "Baltimore City", "Charlotte City", "Chicago City", "Cleveland City", "Columbus City", "Dallas City", "Denver City", "Detroit City", "Houston City", "Indianapolis", "Jacksonville", "Los Angeles City", "Memphis City", "Milwaukee City", "New York City", "Oklahoma City City", "Philadelphia City", "Phoenix City", "San Antonio City", "San Diego City", "San Francisco City", "San Jose City", "Tucson City", "Washington City")
-
-# based on some investigation, the missing additional filter needed to replicate
-# appendix tables 1 and 2 is that biggest split cannot be NA. This was
-# discovered in attempting to create table 2. The number of elections with the
-# largest divides between each racial group were the same as in the table when
-# all results were included and only the summary stats differed in both tables
-# using the city and winner subset. So, I tried excluding all entries for which
-# biggestsplit was NA, and found that the resulting subset matched the
-# statistics in both tables.
-
-# create a subset of the data with the relevant cities where there is a winner
-# and the biggestsplit is not NA
-
-rp_sub <- rp %>%
-  filter(winner == 1) %>%
-  filter(cityname %in% cities_to_keep) %>%
-  filter(!(is.na(biggestsplit)))
-
-# select the relevant variables for the table
-
-rp_sub_a1 <- rp_sub %>%
-  select(biggestsplit, H_citytract_multi_i, H_citytract_NHW_i, diversityinterp, 
-         pctasianpopinterp, pctblkpopinterp, pctlatinopopinterp, medincinterp, 
-         pctrentersinterp, pctcollegegradinterp, biracial, nonpartisan, primary, 
-         logpop, whiteideology_fill2) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-# why are the exact variables H_citytract_NHW and whiteideology_fill not in the
-# data? Data variable names author uses and ones in the data don't exactly
-# match, but replication results are the same.
-
-```
-
-```{r table_a1, results="asis", echo = FALSE}
-
-# create a stargazer summary table for the relevant statistics of the racial
-# polarization data. I couldn't figure out how to change the text of the
-# statistic names at the top of the datat table. I also couldn't figure out how
-# to only not display additional digits for the income variable. May be
-# better to switch to gt for final version?
-
-stargazer(as.data.frame(rp_sub_a1),
-          omit.summary.stat = c("p25", "p75"),
-          title = "\\textbf{TABLE A1 Summary Statistics: Racial Polarization Data}",
-          column.labels = c("\\textbf{Variable}","\\textbf{Obs}", "\\textbf{Mean}", "\\textbf{Std. Dev.}", "\\textbf{Min}", "\\textbf{Max}"),
-          covariate.labels = c("Largest Racial Divide","\\emph{H} Index: Multigroup", "\\emph{H} Index: Two-Group", "Diversity", "\\% Asian", "\\% Black", "\\% Latino", "Median HH Income", "\\% Renters", "\\% College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology"),
-          no.space = TRUE,
-          header = FALSE)
-
-```
-
-```{r table_a2_data_manipulation, include = FALSE}
-
-# initialize variables to indicate if a racial divide had the biggest divide in
-# the election
-
-rp_sub$biggest_split_bw <- NA
-rp_sub$biggest_split_lw <- NA
-rp_sub$biggest_split_bl <- NA
-
-# change the NA value to 1 if the relevant divide was the biggest in the election
-
-rp_sub$biggest_split_bw[rp_sub$biggestsplit_gr == 1] <- 1
-rp_sub$biggest_split_lw[rp_sub$biggestsplit_gr == 2] <- 1
-rp_sub$biggest_split_bl[rp_sub$biggestsplit_gr == 3] <- 1
-
-# generate the dataset of summary statistics to replicate the second appendix
-# table. Group by city name and then summarize the mean H indexes. Sum the
-# number of biggest splits by racial divide for each city
-
-rp_sub_2 <- rp_sub %>%
-  group_by(cityname) %>%
-  summarise(mean_multi_H = mean(H_citytract_multi_i),
-            mean_multi_two_group = mean(H_citytract_NHW_i),
-            sum_bw = sum(biggest_split_bw, na.rm = T),
-            sum_lw = sum(biggest_split_lw, na.rm = T),
-            sum_bl = sum(biggest_split_bl, na.rm = T))
-```
-
-```{r table_a2, echo = FALSE}
-
-# create appendix table A2 to present the summary statistics for cities included
-# in racial polarization data. Efforts to make columns narrower were
-# unsuccessful, so some of the labels in the column names were changed to make
-# the table fit. I also couldn't get the title to print out without including a
-# non-Null subtitle.
-
-city_names <- c("Austin, TX", "Baltimore, MD", "Charlotte, NC", "Chicago, IL", "Cleveland, OH", "Columbus, OH", "Dallas, TX", "Denver, CO", "Detroit, MI", "Houston, TX", "Indianapolis, IN", "Jacksonville, FL", "Los Angeles, CA", "Memphis, TN", "Milwaukee, WI", "New York, NY", "Oklahoma, OK", "Philadelphia, PA", "Phoenix, AZ", "San Antonio, TX","San Diego, CA", "San Francisco, CA", "San Jose, CA", "Tucson, AZ", "Washington, DC")
-
-rp_sub_2$cityname <- city_names
-
-gt(rp_sub_2) %>%
-  tab_header(title = md("**TABLE A2 Cities Included in Racial Polarization Data**"),
-             subtitle = "Replication") %>%
-  tab_spanner(
-      label = md("**Segregation: Mean *H* Index**"),
-      columns = vars(mean_multi_H, mean_multi_two_group)) %>%
-  tab_spanner(
-      label = md("**Largest Racial Divide, Number of Elections**"),
-      columns = vars(sum_bw, sum_lw, sum_bl)) %>%
-  fmt_number(columns = vars(mean_multi_H, mean_multi_two_group),
-             decimals = 3) %>%
-  cols_label(cityname = "City Name",
-             mean_multi_H = md("Multigroup"),
-             mean_multi_two_group = md("Two-Group"),
-             sum_bw = "Black/White",
-             sum_lw = "Latino/White",
-             sum_bl = "Black/Latino") %>%
-  cols_width(
-    vars(cityname) ~ px(10),
-    TRUE ~ px(20)
-  ) %>%
-  cols_align(
-    columns = vars(cityname),
-    align = "left"
-  ) %>%
-  tab_options(
-    table.margin.left = px(5), 
-    table.margin.right = px(5),
-    data_row.padding = px(1),
-    table.width = pct(90)
-  )
-
-```
-
-```{r include = FALSE, include = FALSE}
-
-# basic filter for table for all regressions
-
-# xtreg dgepercap_cpi H_citytract_NHW_i diversityinterp pctblkpopinterp
-# pctasianpopinterp pctlatinopopinterp medinc_cpi pctlocalgovworker_100
-# pctrentersinterp pctover65 pctcollegegradinterp logpop if totaltracts>1 &
-# dgepercap_cpi~=0,fe vce(cluster geo_id2)
-
-fin <-fin_seg %>%
-  filter(totaltractsf >1 | is.na(totaltractsf)) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
-
-# create dge variable used in regression
-
-fin_dge <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_dge_tab <- tibble(
-  Variable = "Direct General Expenditure per Capita",
-  Obs = nrow(fin_dge),
-  Mean = mean(fin_dge$dgepercap_cpi, na.rm = T),
-  SD = sd(fin_dge$dgepercap_cpi, na.rm = T),
-  Min = min(fin_dge$dgepercap_cpi, na.rm = T),
-  Max = max(fin_dge$dgepercap_cpi, na.rm = T)
-)
-
-print(fin_dge_tab)
-
-# creat summary for highways
-fin_hw <-fin %>% filter(highwayspercapNC_cpi != 0)
-
-fin_hw_tab <- tibble(
-  Variable = "Highways per Capita",
-  Obs = nrow(fin_hw),
-  Mean = mean(fin_hw$highwayspercapNC_cpi, na.rm = T),
-  SD = sd(fin_hw$highwayspercapNC_cpi, na.rm = T),
-  Min = min(fin_hw$highwayspercapNC_cpi, na.rm = T),
-  Max = max(fin_hw$highwayspercapNC_cpi, na.rm = T)
-)
-
-print(fin_hw_tab)
-
-a3_final <- full_join(fin_dge_tab, fin_hw_tab)
-
-# parks
-
-fin_park <-fin %>% filter(parkspercapNC_cpi != 0)
-
-fin_park_tab <- tibble(
-  Variable = "Parks per Capita",
-  Obs = nrow(fin_park),
-  Mean = mean(fin_park$parkspercapNC_cpi, na.rm = T),
-  SD = sd(fin_park$parkspercapNC_cpi, na.rm = T),
-  Min = min(fin_park$parkspercapNC_cpi, na.rm = T),
-  Max = max(fin_park$parkspercapNC_cpi, na.rm = T)
-)
-
-print(fin_park_tab)
-
-a3_final <- full_join(a3_final, fin_park_tab)
-
-# police
-
-fin_police <-fin %>% filter(policepercapNC_cpi != 0)
-
-fin_police_tab <- tibble(
-  Variable = "Police per Capita",
-  Obs = nrow(fin_police),
-  Mean = mean(fin_police$policepercapNC_cpi, na.rm = T),
-  SD = sd(fin_police$policepercapNC_cpi, na.rm = T),
-  Min = min(fin_police$policepercapNC_cpi, na.rm = T),
-  Max = max(fin_police$policepercapNC_cpi, na.rm = T)
-)
-
-print(fin_police_tab)
-
-a3_final <- full_join(a3_final, fin_police_tab)
-
-# sewers
-
-fin_sew <-fin %>% filter(sewerspercapNC_cpi != 0)
-
-fin_sew_tab <- tibble(
-  Variable = "Sewers per Capita",
-  Obs = nrow(fin_sew),
-  Mean = mean(fin_sew$sewerspercapNC_cpi, na.rm = T),
-  SD = sd(fin_sew$sewerspercapNC_cpi, na.rm = T),
-  Min = min(fin_sew$sewerspercapNC_cpi, na.rm = T),
-  Max = max(fin_sew$sewerspercapNC_cpi, na.rm = T)
-)
-
-print(fin_sew_tab)
-
-a3_final <- full_join(a3_final, fin_sew_tab)
-
-# welfare
-
-fin_welfare <-fin %>% filter(welfhoushealthNC_cpi != 0)
-
-fin_welfare_tab <- tibble(
-  Variable = "Welfare, Health, and Housing per Capita",
-  Obs = nrow(fin_welfare),
-  Mean = mean(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
-  SD = sd(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
-  Min = min(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
-  Max = max(fin_welfare$welfhoushealthNC_cpi, na.rm = T)
-)
-
-print(fin_welfare_tab)
-
-a3_final <- full_join(a3_final, fin_welfare_tab)
-
-# own source revenue
-
-fin_own <-fin %>% filter(genrevownpercap_cpi != 0)
-
-fin_own_tab <- tibble(
-  Variable = "Own Source Revenue per Capita",
-  Obs = nrow(fin_own),
-  Mean = mean(fin_own$genrevownpercap_cpi, na.rm = T),
-  SD = sd(fin_own$genrevownpercap_cpi, na.rm = T),
-  Min = min(fin_own$genrevownpercap_cpi, na.rm = T),
-  Max = max(fin_own$genrevownpercap_cpi, na.rm = T)
-)
-
-print(fin_own_tab)
-
-a3_final <- full_join(a3_final, fin_own_tab)
-
-# two group H
-
-fin_h <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_h_tab <- tibble(
-  Variable = "Two-Group H Index",
-  Obs = nrow(fin_h),
-  Mean = mean(fin_h$H_citytract_NHW_i, na.rm = T),
-  SD = sd(fin_h$H_citytract_NHW_i, na.rm = T),
-  Min = min(fin_h$H_citytract_NHW_i, na.rm = T),
-  Max = max(fin_h$H_citytract_NHW_i, na.rm = T)
-)
-
-print(fin_h_tab)
-
-a3_final <- full_join(a3_final, fin_h_tab)
-
-# Diversity
-
-fin_div <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_div_tab <- tibble(
-  Variable = "Diversity",
-  Obs = nrow(fin_div),
-  Mean = mean(fin_div$diversityinterp, na.rm = T),
-  SD = sd(fin_div$diversityinterp, na.rm = T),
-  Min = min(fin_div$diversityinterp, na.rm = T),
-  Max = max(fin_div$diversityinterp, na.rm = T)
-)
-
-print(fin_div_tab)
-
-a3_final <- full_join(a3_final, fin_div_tab)
-
-# % black
-
-fin_pctblk <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pctblk_tab <- tibble(
-  Variable = "%  Black",
-  Obs = nrow(fin_pctblk),
-  Mean = mean(fin_pctblk$pctblkpopinterp, na.rm = T),
-  SD = sd(fin_pctblk$pctblkpopinterp, na.rm = T),
-  Min = min(fin_pctblk$pctblkpopinterp, na.rm = T),
-  Max = max(fin_pctblk$pctblkpopinterp, na.rm = T)
-)
-
-print(fin_pctblk_tab)
-
-a3_final <- full_join(a3_final, fin_pctblk_tab)
-
-# % asian
-
-fin_pcta <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pcta_tab <- tibble(
-  Variable = "%  Asian",
-  Obs = nrow(fin_pcta),
-  Mean = mean(fin_pcta$pctasianpopinterp, na.rm = T),
-  SD = sd(fin_pcta$pctasianpopinterp, na.rm = T),
-  Min = min(fin_pcta$pctasianpopinterp, na.rm = T),
-  Max = max(fin_pcta$pctasianpopinterp, na.rm = T)
-)
-
-print(fin_pcta_tab)
-
-a3_final <- full_join(a3_final, fin_pcta_tab)
-
-# % latino
-
-fin_pctla <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pctla_tab <- tibble(
-  Variable = "%  Latino",
-  Obs = nrow(fin_pctla),
-  Mean = mean(fin_pctla$pctlatinopopinterp, na.rm = T),
-  SD = sd(fin_pctla$pctlatinopopinterp, na.rm = T),
-  Min = min(fin_pctla$pctlatinopopinterp, na.rm = T),
-  Max = max(fin_pctla$pctlatinopopinterp, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_pctla_tab)
-
-# 5y black
-
-fin_chng5pctblk <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))
-
-nrow(fin_chng5pctblk)
-
-fin_chng5pctblk_tab <- tibble(
-  Variable = "5Y Change, % Black",
-  Obs = nrow(fin_chng5pctblk),
-  Mean = mean(fin_chng5pctblk$chng5pctblk, na.rm = T),
-  SD = sd(fin_chng5pctblk$chng5pctblk, na.rm = T),
-  Min = min(fin_chng5pctblk$chng5pctblk, na.rm = T),
-  Max = max(fin_chng5pctblk$chng5pctblk, na.rm = T)
-)
-
-print(fin_chng5pctblk_tab)
-
-a3_final <- full_join(a3_final, fin_chng5pctblk_tab)
-
-# 5y latino
-
-fin_chng5pctlatino <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))
-
-fin_chng5pctlatino_tab <- tibble(
-  Variable = "5Y Change, % Latino",
-  Obs = nrow(fin_chng5pctlatino),
-  Mean = mean(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
-  SD = sd(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
-  Min = min(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
-  Max = max(fin_chng5pctlatino$chng5pctlatino, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_chng5pctlatino_tab)
-
-# 5y asian
-
-fin_chng5pctasian <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))
-
-fin_chng5pctasian_tab <- tibble(
-  Variable = "5Y Change, % Asian",
-  Obs = nrow(fin_chng5pctasian),
-  Mean = mean(fin_chng5pctasian$chng5pctasian, na.rm = T),
-  SD = sd(fin_chng5pctasian$chng5pctasian, na.rm = T),
-  Min = min(fin_chng5pctasian$chng5pctasian, na.rm = T),
-  Max = max(fin_chng5pctasian$chng5pctasian, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_chng5pctasian_tab)
-
-# median income
-
-fin_med <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_med_tab <- tibble(
-  Variable = "Median Income",
-  Obs = nrow(fin_med),
-  Mean = mean(fin_med$medinc_cpi, na.rm = T),
-  SD = sd(fin_med$medinc_cpi, na.rm = T),
-  Min = min(fin_med$medinc_cpi, na.rm = T),
-  Max = max(fin_med$medinc_cpi, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_med_tab)
-
-# % local gov. employees
-
-fin_pctlocal <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pctlocal_tab <- tibble(
-  Variable = "% Local Gov. Employees",
-  Obs = nrow(fin_pctlocal),
-  Mean = mean(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
-  SD = sd(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
-  Min = min(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
-  Max = max(fin_pctlocal$pctlocalgovworker_100, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_pctlocal_tab)
-
-# % renters
-
-fin_rent <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_rent_tab <- tibble(
-  Variable = "% Renters",
-  Obs = nrow(fin_rent),
-  Mean = mean(fin_rent$pctrentersinterp, na.rm = T),
-  SD = sd(fin_rent$pctrentersinterp, na.rm = T),
-  Min = min(fin_rent$pctrentersinterp, na.rm = T),
-  Max = max(fin_rent$pctrentersinterp, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_rent_tab)
-
-# % over 65
-
-fin_65 <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_65_tab <- tibble(
-  Variable = "% Over 65",
-  Obs = nrow(fin_65),
-  Mean = mean(fin_65$pctover65, na.rm = T),
-  SD = sd(fin_65$pctover65, na.rm = T),
-  Min = min(fin_65$pctover65, na.rm = T),
-  Max = max(fin_65$pctover65, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_65_tab)
-
-# % college degree
-
-fin_college <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_college_tab <- tibble(
-  Variable = "% College Degree",
-  Obs = nrow(fin_college),
-  Mean = mean(fin_college$pctcollegegradinterp, na.rm = T),
-  SD = sd(fin_college$pctcollegegradinterp, na.rm = T),
-  Min = min(fin_college$pctcollegegradinterp, na.rm = T),
-  Max = max(fin_college$pctcollegegradinterp, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_college_tab)
-
-# pop logged
-
-fin_logpop <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_logpop_tab <- tibble(
-  Variable = "Population (logged)",
-  Obs = nrow(fin_logpop),
-  Mean = mean(fin_logpop$logpop, na.rm = T),
-  SD = sd(fin_logpop$logpop, na.rm = T),
-  Min = min(fin_logpop$logpop, na.rm = T),
-  Max = max(fin_logpop$logpop, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_logpop_tab)
-
-# city ideology
-
-fin_ideo <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(ideology_fill)))
-
-nrow(fin_ideo)
-
-fin_ideo_tab <- tibble(
-  Variable = "City Ideology",
-  Obs = nrow(fin_ideo),
-  Mean = mean(fin_ideo$ideology_fill, na.rm = T),
-  SD = sd(fin_ideo$ideology_fill, na.rm = T),
-  Min = min(fin_ideo$ideology_fill, na.rm = T),
-  Max = max(fin_ideo$ideology_fill, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_ideo_tab)
-
-# population
-fin_population <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_population_tab <- tibble(
-  Variable = "Population",
-  Obs = nrow(fin_population),
-  Mean = mean(fin_population$population, na.rm = T),
-  SD = sd(fin_population$population, na.rm = T),
-  Min = min(fin_population$population, na.rm = T),
-  Max = max(fin_population$population, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_population_tab)
-
-```
-
-```{r, echo = FALSE}
-gt(a3_final) %>%
-    tab_header(title = md("**TABLE A3 Summary Statistics: Census of Government Finance and Population**"),
-             subtitle = "") %>%
-    fmt_number(columns = vars(Mean, SD, Min, Max),
-             decimals = 3) %>%
-    cols_label(Obs = md("**Obs**"),
-               Mean = md("**Mean**"),
-               SD = md("**SD**"),
-               Min = md("**Min**"),
-               Max = md("**Max**")
-                        ) 
-```
+Then, I use the imputed datasets to re-estimate the original models, pooling the results to final pooled regression coefficients and parameters.
 

### 2020-04-29 Draft_1.Rmd
filtering by population cutoffs

@@
 Adding onto her original analysis, I impute a large amount of missing data from the original dataset and re-run the analysis.
-Finally, I add in income segregation as a predictor in her regressions to assess whether this could be a confounding variable.
 
@@
 fin_imp <- fin_imp %>%
-  select(H_citytract_NHW_i, dgepercap_cpi, diversityinterp, pctblkpopinterp, pctasianpopinterp,
-         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
-         pctcollegegradinterp, logpop, geo_id2, chng5pctblk, chng5pctlatino, chng5pctasian,
-         ideology_fill, totaltractsf)
+  select(H_citytract_NHW_i, dgepercap_cpi, diversityinterp, pctblkpopinterp,
+         pctasianpopinterp,pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100,
+         pctrentersinterp, pctover65, pctcollegegradinterp, logpop, geo_id2,
+         chng5pctblk, chng5pctlatino, chng5pctasian, ideology_fill)
+
+# When we subset for only the cities in the original analysis, this about doubles the sample size still...
+
+fin_imp_cities <- fin_imp %>%
+  filter(geo_id2 %in% cities_trounstine_fp)
 
@@
 fin_imp_aggr <- fin_imp %>%
-  select(ideology_fill, H_citytract_NHW_i, chng5pctblk, chng5pctlatino, chng5pctasian, diversityinterp, pctblkpopinterp, pctasianpopinterp,
+  select(ideology_fill, H_citytract_NHW_i, chng5pctblk, chng5pctlatino, chng5pctasian,
+         diversityinterp, pctblkpopinterp, pctasianpopinterp,
          pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
@@
 
-```{r fp_imputations, include = FALSE}
+```{r fp_imputations_original, include = FALSE}
 
@@
 
-ini <- mice(fin_imp, maxit=0, print=F)
+ini <- mice(fin_imp, maxit = 0, print = FALSE)
 
@@
 
-imp_fs <- mice(fin_imp, method = meth, maxit = 5)
+imp_fs <- mice(fin_imp, method = meth, maxit = 1)
+
+imp_fs_all <- mice(fin_imp, method = "cart", maxit = 5)
 
@@
 
-head(complete(imp_fs))
-
 miss_var_summary(fin_imp)
 
-```
-
-```{r new_imp}
+282334 - 222957
+
+```
+
+```{r}
+#now missing 282261
+
+#before impute:
+```
+
+```{r new_imp_less_than_17_nas}
 
@@
 miss_var_summary(complete(new_imp_fs))
+
+```
+
+```{r fp_imputations_cities, include = FALSE}
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_cities, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_fs_cities <- mice(fin_imp_cities, method = meth, maxit = 1)
+
+# fit multiple imputed datasets
+
+fit_imp_felm1 <- with(imp_fs_cities, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_imp_felm1 <- pool(fit_imp_felm1)
+imp_felm1_sum <- summary(pool_imp_felm1)
+
+# RESULTS ARE ESSENTIALLY THE SAME!
+print(imp_felm1_sum)
+
+# doesn't add very much to the sample though, still, robust to additional 73 entries
+
+miss_var_summary(complete(imp_fs_cities))
+
+miss_var_summary(fin_imp_cities)
+
+5039 - 4966
+
+```
+
+```{r fp_population_full_range}
+
+# what if we condition on population size?
+
+fin_imp_pop_size <- fin_imp %>%
+  filter(logpop > 6 & logpop < 16)
+
+nrow(fin_imp_pop_size)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_pop_size, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_fs_pop_size <- mice(fin_imp_pop_size, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_felm1 <- with(imp_fs_pop_size, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_imp_felm1 <- pool(fit_imp_felm1)
+imp_felm1_sum <- summary(pool_imp_felm1)
+
+# RESULTS ARE ESSENTIALLY THE SAME!
+print(imp_felm1_sum)
+
+# doesn't add very much to the sample though, still, robust to additional 73 entries
+
+miss_var_summary(complete(imp_fs_cities))
+
+miss_var_summary(fin_imp_cities)
+
+5039 - 4966
+
+```
+
+```{r 95_pop}
+fin_imp_pop_trounstine_95 <- fin_imp %>%
+  filter(logpop < 11.93437 & logpop > 8.7754)
+
+nrow(fin_imp_pop_trounstine_95)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_pop_trounstine_95, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_fs_pop_size_trounstine_95 <- mice(fin_imp_pop_trounstine_95, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_felm1 <- with(imp_fs_pop_size_trounstine_95, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_imp_felm1 <- pool(fit_imp_felm1)
+imp_felm1_sum <- summary(pool_imp_felm1)
+
+# RESULTS ARE ESSENTIALLY THE SAME!
+print(imp_felm1_sum)
+
+# doesn't add very much to the sample though, still, robust to additional 73 entries
+
+miss_var_summary(complete(imp_fs_cities))
+
+miss_var_summary(fin_imp_cities)
+
+5039 - 4966
+
+```
+
+```{r fp_population_full_range}
+
+# what if we condition on population size?
+
+fin_imp_pop_size <- fin_imp %>%
+  filter(logpop > 6 & logpop < 16)
+
+nrow(fin_imp_pop_size)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_pop_size, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_fs_pop_size <- mice(fin_imp_pop_size, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_felm1 <- with(imp_fs_pop_size, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_imp_felm1 <- pool(fit_imp_felm1)
+imp_felm1_sum <- summary(pool_imp_felm1)
+
+# RESULTS ARE ESSENTIALLY THE SAME!
+print(imp_felm1_sum)
+
+# doesn't add very much to the sample though, still, robust to additional 73 entries
+
+miss_var_summary(complete(imp_fs_cities))
+
+miss_var_summary(fin_imp_cities)
+
+5039 - 4966
+
+```
+
+```{r population_first_quartile}
+
+quantile(fin_dge$logpop, c(.25))
+
+quantile(fin_seg$logpop, c(.25), na.rm = T)
+
+fin_imp_pop_trounstine_first_quart <- fin_imp %>%
+  filter(logpop < 9.388152)
+
+nrow(fin_imp_pop_trounstine_first_quart)
+
+gg_miss_var(fin_imp_pop_trounstine_first_quart, show_pct = T)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_pop_trounstine_first_quart, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_fs_pop_size_bottom_25 <- mice(fin_imp_pop_trounstine_first_quart, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_felm1 <- with(imp_fs_pop_size_bottom_25, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_imp_felm1 <- pool(fit_imp_felm1)
+imp_felm1_sum <- summary(pool_imp_felm1)
+
+# RESULTS ARE ESSENTIALLY THE SAME!
+print(imp_felm1_sum)
+
+# doesn't add very much to the sample though, still, robust to additional 73 entries
+
+miss_var_summary(complete(imp_fs_cities))
+
+miss_var_summary(fin_imp_cities)
+
+5039 - 4966
+
+```
+
+```{r population_top_90_trounstine}
+
+quantile(fin_dge$logpop, c(.90))
+
+quantile(fin_seg$logpop, c(.90), na.rm = T)
+
+fin_imp_pop_top_90_trounstine <- fin_imp %>%
+  filter(logpop > 11.43575)
+
+fin_seg %>%
+  ggplot() +
+  geom_histogram(aes(x = logpop))
+
+nrow(fin_imp_pop_top_90_trounstine)
+
+gg_miss_var(fin_imp_pop_top_90_trounstine, show_pct = T)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_pop_top_90_trounstine, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_fs_pop_size_top_90_trounstine <- mice(fin_imp_pop_top_90_trounstine, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_felm1 <- with(imp_fs_pop_size_top_90_trounstine, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_imp_felm1 <- pool(fit_imp_felm1)
+imp_felm1_sum <- summary(pool_imp_felm1)
+
+# RESULTS ARE ESSENTIALLY THE SAME!
+print(imp_felm1_sum)
+
+# doesn't add very much to the sample though, still, robust to additional 73 entries
+
+miss_var_summary(complete(imp_fs_cities))
+
+miss_var_summary(fin_imp_cities)
+
+5039 - 4966
+
+```
+
+```{r population_bottom_5_trounstine}
+
+quantile(fin_dge$logpop, c(.05))
+
+quantile(fin_seg$logpop, c(.05), na.rm = T)
+
+fin_imp_pop_bottom_5_trounstine <- fin_imp %>%
+  filter(logpop < 8.775581)
+
+fin_seg %>%
+  ggplot() +
+  geom_histogram(aes(x = logpop))
+
+nrow(fin_imp_pop_bottom_5_trounstine)
+
+gg_miss_var(fin_imp_pop_bottom_5_trounstine, show_pct = T)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_pop_bottom_5_trounstine, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_fs_pop_size_bottom_5_trounstine <- mice(fin_imp_pop_bottom_5_trounstine, method = meth, maxit = 1)
+
+# fit multiple imputed datasets
+
+fit_imp_felm1 <- with(imp_fs_pop_size_bottom_5_trounstine, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_imp_felm1 <- pool(fit_imp_felm1)
+imp_felm1_sum <- summary(pool_imp_felm1)
+
+# RESULTS ARE ESSENTIALLY THE SAME!
+print(imp_felm1_sum)
+
+# doesn't add very much to the sample though, still, robust to additional 73 entries
+
+miss_var_summary(complete(imp_fs_pop_size_bottom_5_trounstine))
+
+miss_var_summary(fin_imp_cities)
+
+nrow(complete(imp_fs_pop_size_bottom_5_trounstine))
+
+5039 - 4966
+
+```
+
+```{r population_bottom_1}
+
+quantile(fin_dge$logpop, c(.01))
+
+quantile(fin_seg$logpop, c(.20), na.rm = T)
+
+fin_imp_pop_bottom_1_trounstine <- fin_imp %>%
+  filter(logpop < 8.364976 )
+
+fin_seg %>%
+  ggplot() +
+  geom_histogram(aes(x = logpop))
+
+nrow(fin_imp_pop_bottom_1_trounstine)
+
+gg_miss_var(fin_imp_pop_bottom_1_trounstine, show_pct = T)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_pop_bottom_1_trounstine, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_fs_pop_size_bottom_1_trounstine <- mice(fin_imp_pop_bottom_1_trounstine, method = meth, maxit = 1)
+
+# fit multiple imputed datasets
+
+fit_imp_felm1 <- with(imp_fs_pop_size_bottom_1_trounstine, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_imp_felm1 <- pool(fit_imp_felm1)
+imp_felm1_sum <- summary(pool_imp_felm1)
+
+# RESULTS ARE ESSENTIALLY THE SAME!
+print(imp_felm1_sum)
+
+# doesn't add very much to the sample though, still, robust to additional 73 entries
+
+miss_var_summary(complete(imp_fs_cities))
+
+miss_var_summary(fin_imp_cities)
+
+5039 - 4966
+
+```
+
+```{r population_over_Baqir}
+
+# Baqir et al uses city as population above 25,000
+
+baqir <- log(25000)
+
+fin_imp_pop_over_baqir <- fin_imp %>%
+  filter(logpop > baqir )
+
+nrow(fin_imp_pop_over_baqir)
+
+gg_miss_var(fin_imp_pop_over_baqir, show_pct = T)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_pop_over_baqir, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_fs_pop_overbaqir <- mice(fin_imp_pop_over_baqir, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_felm1 <- with(imp_fs_pop_overbaqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_imp_felm1 <- pool(fit_imp_felm1)
+imp_felm1_sum <- summary(pool_imp_felm1)
+
+# RESULTS ARE ESSENTIALLY THE SAME!
+print(imp_felm1_sum)
+
+# doesn't add very much to the sample though, still, robust to additional 73 entries
+
+miss_var_summary(complete(imp_fs_cities))
+
+miss_var_summary(fin_imp_cities)
+
+5039 - 4966
+
+```
+
+```{r population_under_Baqir}
+
+# Baqir et al uses city as population above 25,000
+
+baqir <- log(25000)
+
+fin_imp_pop_under_baqir <- fin_imp %>%
+  filter(logpop < baqir )
+
+nrow(fin_imp_pop_under_baqir)
+
+gg_miss_var(fin_imp_pop_under_baqir, show_pct = T)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_pop_under_baqir, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_fs_pop_under_baqir <- mice(fin_imp_pop_under_baqir, method = meth, maxit = 1)
+
+# fit multiple imputed datasets
+
+fit_imp_felm1 <- with(imp_fs_pop_under_baqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_imp_felm1 <- pool(fit_imp_felm1)
+imp_felm1_sum <- summary(pool_imp_felm1)
+
+# RESULTS ARE ESSENTIALLY THE SAME!
+print(imp_felm1_sum)
+
+# doesn't add very much to the sample though, still, robust to additional 73 entries
+
+miss_var_summary(complete(imp_fs_cities))
+
+miss_var_summary(fin_imp_cities)
+
+5039 - 4966
+
+```
+
+```{r population_mid_50}
+
+# essentially the same - let's do full population
+(quantile(fin_seg$logpop, c(.25, .75), na.rm = T))
+(quantile(fin_imp$logpop, c(.25, .75), na.rm = T))
+
+baqir <- log(25000)
+
+fin_imp_pop_mid_50 <- fin_imp %>%
+  filter(logpop > 5.777652 & logpop < 7.936303)
+
+nrow(fin_imp_pop_mid_50)
+
+gg_miss_var(fin_imp_pop_mid_50, show_pct = T)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_pop_mid_50, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_fs_pop_mid_50 <- mice(fin_imp_pop_mid_50, method = meth, maxit = 1)
+
+# fit multiple imputed datasets
+
+fit_imp_felm1 <- with(imp_fs_pop_mid_50, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_imp_felm1 <- pool(fit_imp_felm1)
+imp_felm1_sum <- summary(pool_imp_felm1)
+
+# RESULTS ARE ESSENTIALLY THE SAME!
+print(imp_felm1_sum)
+
+# doesn't add very much to the sample though, still, robust to additional 73 entries
+
+miss_var_summary(complete(imp_fs_cities))
+
+miss_var_summary(fin_imp_cities)
+
+5039 - 4966
+
+```
+
+```{r population_top_1_trounstine}
+
+(quantile(fin_seg$logpop, c(.99), na.rm = T))
+(quantile(fin_dge$logpop, c(.99), na.rm = T))
+
+fin_imp_top_1_trounstine <- fin_imp %>%
+  filter(logpop > 13.1907 )
+
+nrow(fin_imp_top_1_trounstine)
+
+gg_miss_var(fin_imp_top_1_trounstine, show_pct = T)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_top_1_trounstine, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_fs_pop_top_1_trounstine <- mice(fin_imp_top_1_trounstine, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_felm1 <- with(imp_fs_pop_top_1_trounstine, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_imp_felm1 <- pool(fit_imp_felm1)
+imp_felm1_sum <- summary(pool_imp_felm1)
+
+# RESULTS ARE ESSENTIALLY THE SAME!
+print(imp_felm1_sum)
+
+nrow(complete(imp_fs_pop_top_1_trounstine))
+
+# doesn't add very much to the sample though, still, robust to additional 73 entries
+
+miss_var_summary(complete(imp_fs_cities))
+
+miss_var_summary(fin_imp_cities)
+
+5039 - 4966
+
+```
+
+```{r population_top_1}
+
+(quantile(fin_seg$logpop, c(.99), na.rm = T))
+(quantile(fin_dge$logpop, c(.99), na.rm = T))
+
+fin_imp_top_1 <- fin_imp %>%
+  filter(logpop > 11.28648)
+
+nrow(fin_imp_top_1)
+
+gg_miss_var(fin_imp_top_1, show_pct = T)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_top_1, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_fs_pop_top_1 <- mice(fin_imp_top_1_trounstine, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_felm1 <- with(imp_fs_pop_top_1, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_imp_felm1 <- pool(fit_imp_felm1)
+imp_felm1_sum <- summary(pool_imp_felm1)
+
+# RESULTS ARE ESSENTIALLY THE SAME!
+print(imp_felm1_sum)
+
+nrow(complete(imp_fs_pop_top_1))
+
+# doesn't add very much to the sample though, still, robust to additional 73 entries
+
+miss_var_summary(complete(imp_fs_cities))
+
+miss_var_summary(fin_imp_cities)
+
+5039 - 4966
+
 ```
@@
 
+print(imp_felm1_sum)
+
 ```
@@
 fin_dge <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_dge_tab <- tibble(
-  Variable = "Direct General Expenditure per Capita",
-  Obs = nrow(fin_dge),
-  Mean = mean(fin_dge$dgepercap_cpi, na.rm = T),
-  SD = sd(fin_dge$dgepercap_cpi, na.rm = T),
-  Min = min(fin_dge$dgepercap_cpi, na.rm = T),
-  Max = max(fin_dge$dgepercap_cpi, na.rm = T)
-)
 
@@
 
+# cities in original Trounstine
+
+cities_trounstine_fp <- fin_dge %>%
+  select(geo_id2) %>%
+  unique() %>%
+  pull()
+
+# pop quantiles original Trounstine
+
+quantile(fin_dge$logpop, c(.10, .25, .5, .75, .90))
+
+quantile(fin_dge$logpop, c(.05, .95))
+
+nrow(fin_imp)
+
+fin_imp_pop_trounstine_95 <- fin_imp %>%
+  filter(logpop < 11.93437 & logpop > 8.7754)
+
 # creat summary for highways

### 2020-04-29 Draft_1.Rmd
edits to draft

@@
 
-# gg_miss_var(rp_impute, show_pct = TRUE)
+gg_miss_var(rp_impute, show_pct = TRUE) +
+  ggtitle("% Missing Values in Trounstine (2016)'s Racial Polarization Dataset")
+
+nrow(rp_impute)
 
@@
 title(main = "Patterns of Missingness in the Financial Segregation Data",
-      sub = "Is this a caption?
-qiufwnjekfewkfnwein\nwefjwenmf wiufnwqjenf ewfuiwjnef nfijefnwjenfkqwjnf lqwjefnjqwefjwnef winfjqwhf hjwefwiuefief welfiunqlfjnqkjwe qqfniquwenjfjq iqfnjkjeq rfiunfj q")
+      sub = "")
 

### 2020-04-29 Draft_1.Rmd
edits to abstract

@@
 In this analysis, I was able to successfully replicate @trounstine_segregation_2016’s main results.
-Adding onto her original analysis, I impute a large amount of missing data from the original dataset and re-run the analysis.
+I then attempted to better deal with the large amounts of missing data in the datasets used in the original analysis by multiply imputing missing values using the mice() package and then by re-running the original models using the multiply imputed datasets.
+My results suggest that segregation is associated with increased racial political polarization, although maybe not as strongly as Trounstine (2016) originally suggested.
+Furthermore, I find that Trounstine (2016)'s conclusion that increases in segregation are associated with decreases in public spending holds for large cities, but that diversity is a better explanatory factor for small cities.
 

### 2020-04-29 Draft_1.Rmd
deleting unnecessary files

@@
 ---
-title: "Milestone 7"
+title: "Investigating the Underprovision of Public Goods: Does Segregation Matter?"
 author: "Maria Burzillo"
-date: "3/28/2020"
+date: "5/8/2020"
 output: 

### 2020-04-29 Draft_1.Rmd
table lable changes

@@
 
-# fixed effects like a control variable
-
-# lmer(dependent ~ predictors + (random predictors | group level))
-
-# reml v. log likelihood: default in r appears to be log-likelihood. stata defaults to maximum likelihood
-
 # perform a multi-level mixed-effects linear regression of biggest split on the multi-group H index with controls for Herfindahl Diversity Index, % Asian interpolated, % Black interpolated, % Latino interpolated, median household income interpolated, % renters interpolated, percent college grads interpolated, a dummy indicating if there were biracial candidates in the election, a dummy  indicating if the election was nonpartisan, an indicator if the election was a primary, and the log population.
@@
 
-```{r felm, eval = FALSE}
+```{r felm, include = FALSE}
 
@@
 
-```{r main_fp_tables, results = "asis", eval = FALSE}
+```{r main_fp_tables, results = "asis", echo = FALSE}
 
@@
                     header = FALSE,
-                    title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures}")
-
-```
-
-```{r, eval = FALSE}
+                    title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures}",
+                covariate.labels = c("White/Nonwhite H Index", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Change Percent Black", "Change Percent Latino", "Change Percent Asian", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Population (logged)", "White Ideology", "Constant"))
+
+```
+
+```{r, include = FALSE}
 
@@
 
-```{r results = "asis", eval = FALSE}
+```{r results = "asis", echo = FALSE}
 table3a <- stargazer(felm2_1, felm2_2, felm2_3, 
@@
           header = FALSE,
-          title = "\\textbf{Effect of Segregation on Public Goods A}")
+          title = "\\textbf{Effect of Segregation on Public Goods A}",
+          covariate.labels = c("White/Nonwhite H Index", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Population (logged)", "Constant"))
 
@@
 
-```{r iv_regs, eval = FALSE}
+```{r iv_regs, include = FALSE}
 
@@
 
-# Table 5
-
-```{r results = "asis", echo = FALSE}
+```{r results = "asis", echo = FALSE, eval = FALSE}
 
@@
           header = FALSE,
-          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach A}")
+          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach A}",
+          covariate.labels = c("White/Nonwhite H Index", "Lagged Direct Gen.
+Exp.", "Lagged Highway Exp.", "Lagged Police Exp.", "Lagged Parks Exp.", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Constant"))
 
@@
           header = FALSE,
-          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach B}")
+          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach B}",
+          covariate.labels = c("White/Nonwhite H Index", "Lagged Sewers Exp.", "Lagged Gen.
+Rev.
+Own Sources", "Lagged Police Exp.", "Lagged Welfare", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Constant"))
 ```
@@
 
-```{r include = FALSE, include = FALSE}
+```{r fp_summary_table, include = FALSE}
 
@@
 
-```{r, echo = FALSE}
+```{r fp_summary_table_stargazer, echo = FALSE}
 gt(a3_final) %>%

### 2020-04-30 Draft_1.Rmd
changes to table formatting

@@
 
+miss_var_summary(fin_imp)
+miss_var_summary(rp_impute)
+
+```
+
+```{r obs_in_original_fin_and_cities, include = FALSE}
+# basic filter for table for all regressions
+
+# xtreg dgepercap_cpi H_citytract_NHW_i diversityinterp pctblkpopinterp
+# pctasianpopinterp pctlatinopopinterp medinc_cpi pctlocalgovworker_100
+# pctrentersinterp pctover65 pctcollegegradinterp logpop if totaltracts>1 &
+# dgepercap_cpi~=0,fe vce(cluster geo_id2)
+
+fin <-fin_seg %>%
+  filter(totaltractsf >1 | is.na(totaltractsf)) %>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
+
+# create dge variable used in regression
+
+fin_dge <-fin %>% filter(dgepercap_cpi != 0)
+
+# cities in original Trounstine
+
+cities_trounstine_fp <- fin_dge %>%
+  select(geo_id2) %>%
+  unique() %>%
+  pull()
+
 # When we subset for only the cities in the original analysis, this about doubles the sample size still...
@@
   filter(geo_id2 %in% cities_trounstine_fp)
-
-miss_var_summary(fin_imp)
-miss_var_summary(rp_impute)
 
@@
 In an attempt to better deal with the problem of missing data in @trounstine_segregation_2016, I impute missing values in the original data using the mice package in R, which generates multivariate imputations using chained equations [@mice].
-While there are a variety of different imputation methods that could have been employed, multiple imputation (such as the multiple multivariate imputations generated by mice) is desireable because instead of inputting a single value such as the mean for missing values, it instead uses the distribution of the available data to estimate multiple potential values for the missing data.
+While there are a variety of different imputation methods that could have been employed, multiple imputation (such as the multiple multivariate imputations generated by mice) is desirable because instead of inputting a single value such as the mean for missing values, it instead uses the distribution of the available data to estimate multiple potential values for the missing data.
 As a result, multiple imputation helps to account for the uncertainty inherent in the imputation process and allows for the calculation of standard errors around estimators.
-As a result, multiple imputation allows the researcher to more accurately assess the of uncertainty in the analysis in general.
+Thus, multiple imputation allows the researcher to more accurately assess the of uncertainty in the analysis in general.
 
@@
 fit_imp_felm1 <- with(imp_fs_pop_size_trounstine_95, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r fp_population_full_range}
-
-# what if we condition on population size?
-
-fin_imp_pop_size <- fin_imp %>%
-  filter(logpop > 6 & logpop < 16)
-
-nrow(fin_imp_pop_size)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_size, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_size <- mice(fin_imp_pop_size, method = meth, maxit = 5)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_size, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
 

### 2020-04-30 Final_Draft.Rmd
initial commit final draft

--- 2020-04-29 Draft_1.Rmd
@@
 Nevertheless, these results were successfully replicated in Stata.
-
-```{r include = FALSE}
-
-## regression 1 Table 1
-
-# fixed effects like a control variable
-
-# lmer(dependent ~ predictors + (random predictors | group level))
-
-# reml v. log likelihood: default in r appears to be log-likelihood. stata defaults to maximum likelihood
-
-# perform a multi-level mixed-effects linear regression of biggest split on the multi-group H index with controls for Herfindahl Diversity Index, % Asian interpolated, % Black interpolated, % Latino interpolated, median household income interpolated, % renters interpolated, percent college grads interpolated, a dummy indicating if there were biracial candidates in the election, a dummy  indicating if the election was nonpartisan, an indicator if the election was a primary, and the log population.
-The regression also includes fixed effects for year and region and random effects for cities (geo_id2).
-Diversity is  included because of the claim that more diverse populations will have more heterogeneous political preferences.
-The other fixed effect control variables are included because they are known to be potentially correlated with segregation.
-winner == 1 requires that there was a winner in the election.
-
-# regression specification. Apply REML = FALSE. The default for lmer() in R is
-# to optimize the restricted (residual) maximum likelihood (REML) whereas in
-# xtmixed in Stata the default is to optimize the log likelihood (which you can
-# do in lmer() in R by setting REML = FALSE), so this will match the STATA code
-
-m1 <- lmer(biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-## regression 2 Table 1
-
-# Perform the same regression as for Column 1 above but this time regress on the two-group calculation of Theil's H interpolated.
-It is unclear where the "diversity" variable is coming from, as the only variable related to diversity in the specificed dataset is diversityinterp.
-This is a problem that will need to be resolved.
-Essentially, this regression just tests an alternate specification to the first in which the segregation index in defined in terms of two-groups rather than multiple.
-
-m2 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-# perform the same regression as for column 2, but now add in a measure of
-# average white political ideology. The point of this is to control for ideology
-# so that the author can separate any effects of segregation from any potential
-# effects of white political ideology. This is important because it is possible
-# that segregation is just a proxy for white conservatism and thus failure to
-# include this variable could lead to ommitted variable bias.
-
-m3 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-```
-
-```{r results="asis", echo = FALSE}
-
-# create a stargazer table of the results
-
-t1 <- stargazer(m1, m2, m3, omit = c("year", "south", "midwest", "west"),
-                header = FALSE,
-                title = "\\textbf{Racial Polarization in Segregated Cities}",
-                single.row = TRUE,
-                no.space = FALSE,
-                add.lines = list(c("Wald Chi Squarred", "a", "b", "c")),
-                omit.stat = c("ll","rsq"),
-                covariate.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Diversity", "Percent Asian", "Percent Black", "Percent Latino", "Medain HH Income (1000s)", "Percent Renters", "Percent College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology", "Constant"),
-                notes = "This table displays...")
-
-# note: "This table displays the results of the replication effort of the analyses conducted in Trounstine (2016) using the racial polarization dataset.
-The replication code can be found on my personal [Github repository](https://github.com/mburzillo/new_final_project).
-The original table is displayed for comparison as Figure 1.")
-
-```
-
-![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016.
-My replication of these results can be found in Table 1 in this paper.](table_1.png)
-
-There was one interesting outcome from my attempt to replicate the original Stata code in R.
-Due to the differences in R and Stata in dealing with missing values, the results of my first replication of analyses using the financial segregation dataset were slightly different than the results in Stata from the original paper.
-In order to exclude cities from her analysis with only one census tract, Trounstine conditions her regressions in Stata such that the value for the number of census tracts is greater than one.
-In Stata, this does not remove missing values, whereas in R, it does.
-Since this variable is used only as a conditional filter and not as a regression variable (and thus, the observations with missing values for number of census tracts are not dropped), Trounstine’s analysis includes 14 cities and 58 observations with missing values for census tracts in addition to cities with two or more census tracts.
-This is a potential oversight on the part of the author, and I would suggest also dropping observations with missing census tract data, or else imputing them given that the aim of her condition was to exclude cities without a sufficient number of census tracts.
-Nevertheless, dropping these values did not have much of an effect on the subsequent results, likely because they represent a small proportion of the overall sample.
-
-# Extension
-
-One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data values in her original datasets.
-Because both R and Stata drop any observations with missing values for any of the variables used in a regression, this can exlcude a large portion of the data from the analysis and potentially bias the results if the data is not missing completely at random.
-A large amount of data is missing in both of the main datasets used in the analyses of @trounstine_segregation_2016.
-The main model specification using the racial polarization dataset exludes `r (obs_rp - 91)` of the original  `r obs_rp` observations, or  %`r round(100*(obs_rp - 91)/obs_rp,2)` of the data.
-Additionally, the main model specification using the financial segregation data set excludes `r round(obs_fin_seg - 13742,2)` of the original `r obs_fin_seg` observations, or %`r round(100*(obs_fin_seg - 13742)/ obs_fin_seg,2)` of observations from the original dataset.
-
-In an attempt to better deal with the problem of missing data in @trounstine_segregation_2016, I impute missing values in the original data using the mice package in R, which generates multivariate imputations using chained equations [@mice].
-While there are a variety of different imputation methods that could have been employed, multiple imputation (such as the multiple multivariate imputations generated by mice) is desireable because instead of inputting a single value such as the mean for missing values, it instead uses the distribution of the available data to estimate multiple potential values for the missing data.
-As a result, multiple imputation helps to account for the uncertainty inherent in the imputation process and allows for the calculation of standard errors around estimators.
-As a result, multiple imputation allows the researcher to more accurately assess the of uncertainty in the analysis in general.
-
-Before performing the multiple imputations on the datasets, I first examined the missing data for patterns.
-To better understand any potential patterns in missing data, I plotted the pattern of missingness and created a histogram showing the frequency of missing values for those variables with missing values in figure X1 for the racial polarization data and figure X2 for the financial segregation data.
-Looking at figure X1, the histogram shows that the variables for the largest vote split along racial lines and the variable indicating whether or not the election had candidates of more than one race had by far the largest percentages of missing data, missing %`r round(sum(is.na(rp_impute$biggestsplit))/nrow(rp_impute)*100,2)` and  %`r round(sum(is.na(rp_impute$biracial))/nrow(rp_impute)*100,2)`, respectively.
-It is important to note that the variable for the largest vote split along racial lines is the dependent variable in the regresison analysis, and thus, we are missing a large percentage of this key variable.
-From the plot on the right, we can see that approximately 42% of observations are complete (have no missing values).
-There seem to be a correspondence between missing a value for the largest vote split and missing a value for the biracial election indicator.
-There also seem to be about 2% of values for wich most of the variables are missing.
-However, most observations are not missing more than 2-3 values.
-
-```{r rp_missing_plot, include = FALSE, warning = FALSE}
-
-# don't show the warning, it's just an irrelevant column missing a name
-
-# plot the missing variables if desired
-
-rp_facet <- rp_impute %>%
-   select("medincinterp",
-             "biggestsplit", "diversityinterp",
-             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
-             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
-               "south", "midwest", "west", "whiteideology_fill2", "year")
-
-gg_miss_var(rp_impute, show_pct = TRUE) +
-  ggtitle("% Missing Values in Trounstine (2016)'s Racial Polarization Dataset")
-
-nrow(rp_impute)
-
-```
-
-```{r rp_aggr_plot, echo = FALSE}
-
-# select only the missing values
-
-rp_aggr <- rp_impute %>%
-   select("medincinterp",
-             "biggestsplit", "diversityinterp",
-             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
-             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
-               "south", "midwest", "west", "whiteideology_fill2")
-
-# create an aggr plot for the missing values
-
-aggr(rp_aggr, bars = TRUE, col=c('navyblue','red'), numbers=TRUE, cex.axis=.5, gap=1, ylab=c("Proporiton of Missing Values","Combinations"))
-
-# caption for this plot when I figure out how to do it...
-: This plot examines the pattern of missing data in the the original racial polarization dataset from Trounstine (2016).
-The plot on the left shows the percentage of missing data for each variable with missing data and reveals that the variables that are missing by far the most data are the largest vote split along racial lines (biggestsplit) and the variable indicating whether or not the election had candidates of more than one race (biracial).
-The plot on the right shows the pattern of missingness among the variables.
-We can see that approximately 42% of observations are complete (have no missing values).
-There seems to be a correspondence between missing a value for biggest split and missing biracial.
-There also seem to be about 2% of values for which most of the variables are missing.
-However, most observations are not missing more than 2-3 values.
-
-```
-
-In figure X2, we can similarly observe the trends for the financial segregation dataset.
-In this dataset, there is a very high proportion of missing variables for a number of variables.
-For example, there are `r sum(is.na(fin_imp$H_citytract_NHW_i))` missing values for the segregation index, which is the main independent variable, or %`r round(sum(is.na(fin_imp$H_citytract_NHW_i))/nrow(fin_imp)*100,2)` of the data.
-In this dataset, there are also many more observations for which values are missing for multiple variables in comparison to the racial polarization dataset.
-In total, a mere %`r .0058*100` of observations are complete for all variables included in the main specification for the financial segregaion dataset.
-
-```{r fin_missing_plot, include = FALSE}
-
-miss_var_summary(fin_imp)
-
-gg_miss_var(fin_imp, show_pct = TRUE)
-
-```
-
-```{r fin_aggr_plot, echo = FALSE}
-
-# select all variables with missing values for the aggr plot
-
-fin_imp_aggr <- fin_imp %>%
-  select(ideology_fill, H_citytract_NHW_i, chng5pctblk, chng5pctlatino, chng5pctasian,
-         diversityinterp, pctblkpopinterp, pctasianpopinterp,
-         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
-         pctcollegegradinterp)
-
-new_try <- head(fin_imp_aggr, 20)
-
-aggr(new_try, plot = TRUE, bars = FALSE, col=c('navyblue','red'), numbers=TRUE)
-
-# create the aggr plot
-
-aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.5, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
-title(main = "Patterns of Missingness in the Financial Segregation Data",
-      sub = "")
-
-# this plot tells us that only .58% of the data are complete (not missing anything)
-
-# caption for this plot when I figure out how to do it...
-: This plot examines the pattern of missing data in the the original financial segregation dataset from Trounstine (2016).
-The plot on the left shows the percentage of missing data for each variable with missing data and reveals that a large number of variables are missing the vast majority of data.
-The plot on the right shows the pattern of missingness among the variables.
-We can see that only .58% of observations are complete (have no missing values), and a large majority of the observations are missing data for many variables.
-
-```
-
-Because neither dataset seems to exhibit any clear patterns in the missing, data, it makes sense to proceed with the imputation.
-For the racial polarization dataset, I performed multiple imputations with 20 iterations using mice, while for the financial segregation dataset, I performed only 5 iterations due to the large size of the dataset and computing limitaitons.
-A non-stochastic imputation method, Classification and Regression Trees (CART), was used instead of the default for the imputation for both datasets because of an error with matrix inversion caused by the data that prevented the use of the default method, predictive mean matching.
-For the racial polarization dataset, I included all of the variables used in the analysis associated with the dataset and was able to impute all missing values.
-For the financial segregation dataset, however, I only imputed values for the main independent variable, the segregation index, and a few other variables, although all variables used in the analysis were included in the data subset input into the mice function.
-More of the data could not be imputed from the financial segregation dataset due to computing and time constraints for this project given the dataset's large size and high proportion of missing values.
-
-```{r rp_imputation, include = FALSE}
-
-# Perform multiple imputations using the cart method. Because of the time it
-# takes to run this function, I turned the results into a dataset to load in
-# instead of re-running everytime.
-
-max_it = 20
-
-imp_1_rp <- mice(rp_impute, method = "cart", maxit = 20)
-
-# can use the line below to check that there are now no missing values
-
-# gg_miss_var(complete(imp_1_rp), show_pct = TRUE)
-
-```
-
-```{r fp_imputations_original, include = FALSE}
-
-# perform multiple imputations.
-We have the same issue here with the default method as with the previous dataset so we use CART.
-Additionally, because of the extremely large size of this dataset, we choose to only impute the variable H_citytract_NHW_i, as it is the most frequently missing variable and also out main independent variable.
-Just imputing this allows us to include way more observations in the regression than the original data despite the still large number of NAs overall.
-One concern here would be that if there was some reason that this variable was missing rather than other variables that only imputing this variable could lead to some bias in the results.
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs <- mice(fin_imp, method = meth, maxit = 1)
-
-imp_fs_all <- mice(fin_imp, method = "cart", maxit = 5)
-
-# now there are manyb fewer missing variables!!!
-
-miss_var_summary(complete(imp_fs))
-
-miss_var_summary(fin_imp)
-
-282334 - 222957
-
-```
-
-```{r}
-#now missing 282261
-
-#before impute:
-```
-
-```{r new_imp_less_than_17_nas}
-
-fin_imp <- fin_imp %>%
-  mutate(nas = is.na(H_citytract_NHW_i) + is.na(dgepercap_cpi) + is.na(diversityinterp) + is.na(pctblkpopinterp)  + is.na(pctasianpopinterp) + is.na(pctlatinopopinterp) + is.na(medinc_cpi) + is.na(pctlocalgovworker_100) + is.na(pctrentersinterp) + is.na(pctover65) + is.na(pctcollegegradinterp) + is.na(logpop) + is.na(geo_id2) + is.na(chng5pctblk) + is.na(chng5pctlatino) + is.na(chng5pctasian) + is.na(logpop) + is.na(geo_id2) + is.na(chng5pctblk) + is.na(chng5pctlatino) + is.na(chng5pctasian) + is.na(ideology_fill))
-
-fin_imp %>%
-  ggplot(aes(x = nas)) +
-  geom_histogram()
-
-fin_imp %>%
-  group_by(nas) %>%
-  summarise(n())
-
-# exclude all observations with 17 out of 22 nas
-
-fin_imp_sub <- fin_imp %>%
-  filter(nas < 17)
-
-nrow(fin_imp_sub)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_sub, maxit=0, print=F)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-new_imp_fs <- mice(fin_imp_sub, method = meth, maxit = 5)
-
-miss_var_summary(complete(new_imp_fs))
-
-```
-
-```{r fp_imputations_cities, include = FALSE}
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_cities, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_cities <- mice(fin_imp_cities, method = meth, maxit = 1)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_cities, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r fp_population_full_range}
-
-# what if we condition on population size?
-
-fin_imp_pop_size <- fin_imp %>%
-  filter(logpop > 6 & logpop < 16)
-
-nrow(fin_imp_pop_size)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_size, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_size <- mice(fin_imp_pop_size, method = meth, maxit = 5)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_size, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r 95_pop}
-fin_imp_pop_trounstine_95 <- fin_imp %>%
-  filter(logpop < 11.93437 & logpop > 8.7754)
-
-nrow(fin_imp_pop_trounstine_95)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_trounstine_95, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_size_trounstine_95 <- mice(fin_imp_pop_trounstine_95, method = meth, maxit = 5)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_size_trounstine_95, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r fp_population_full_range}
-
-# what if we condition on population size?
-
-fin_imp_pop_size <- fin_imp %>%
-  filter(logpop > 6 & logpop < 16)
-
-nrow(fin_imp_pop_size)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_size, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_size <- mice(fin_imp_pop_size, method = meth, maxit = 5)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_size, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r population_first_quartile}
-
-quantile(fin_dge$logpop, c(.25))
-
-quantile(fin_seg$logpop, c(.25), na.rm = T)
-
-fin_imp_pop_trounstine_first_quart <- fin_imp %>%
-  filter(logpop < 9.388152)
-
-nrow(fin_imp_pop_trounstine_first_quart)
-
-gg_miss_var(fin_imp_pop_trounstine_first_quart, show_pct = T)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_trounstine_first_quart, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_size_bottom_25 <- mice(fin_imp_pop_trounstine_first_quart, method = meth, maxit = 5)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_size_bottom_25, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r population_top_90_trounstine}
-
-quantile(fin_dge$logpop, c(.90))
-
-quantile(fin_seg$logpop, c(.90), na.rm = T)
-
-fin_imp_pop_top_90_trounstine <- fin_imp %>%
-  filter(logpop > 11.43575)
-
-fin_seg %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-nrow(fin_imp_pop_top_90_trounstine)
-
-gg_miss_var(fin_imp_pop_top_90_trounstine, show_pct = T)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_top_90_trounstine, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_size_top_90_trounstine <- mice(fin_imp_pop_top_90_trounstine, method = meth, maxit = 5)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_size_top_90_trounstine, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r population_bottom_5_trounstine}
-
-quantile(fin_dge$logpop, c(.05))
-
-quantile(fin_seg$logpop, c(.05), na.rm = T)
-
-fin_imp_pop_bottom_5_trounstine <- fin_imp %>%
-  filter(logpop < 8.775581)
-
-fin_seg %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-nrow(fin_imp_pop_bottom_5_trounstine)
-
-gg_miss_var(fin_imp_pop_bottom_5_trounstine, show_pct = T)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_bottom_5_trounstine, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_size_bottom_5_trounstine <- mice(fin_imp_pop_bottom_5_trounstine, method = meth, maxit = 1)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_size_bottom_5_trounstine, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_pop_size_bottom_5_trounstine))
-
-miss_var_summary(fin_imp_cities)
-
-nrow(complete(imp_fs_pop_size_bottom_5_trounstine))
-
-5039 - 4966
-
-```
-
-```{r population_bottom_1}
-
-quantile(fin_dge$logpop, c(.01))
-
-quantile(fin_seg$logpop, c(.20), na.rm = T)
-
-fin_imp_pop_bottom_1_trounstine <- fin_imp %>%
-  filter(logpop < 8.364976 )
-
-fin_seg %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-nrow(fin_imp_pop_bottom_1_trounstine)
-
-gg_miss_var(fin_imp_pop_bottom_1_trounstine, show_pct = T)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_bottom_1_trounstine, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_size_bottom_1_trounstine <- mice(fin_imp_pop_bottom_1_trounstine, method = meth, maxit = 1)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_size_bottom_1_trounstine, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r population_over_Baqir}
-
-# Baqir et al uses city as population above 25,000
-
-baqir <- log(25000)
-
-fin_imp_pop_over_baqir <- fin_imp %>%
-  filter(logpop > baqir )
-
-nrow(fin_imp_pop_over_baqir)
-
-gg_miss_var(fin_imp_pop_over_baqir, show_pct = T)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_over_baqir, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_overbaqir <- mice(fin_imp_pop_over_baqir, method = meth, maxit = 5)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_overbaqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r population_under_Baqir}
-
-# Baqir et al uses city as population above 25,000
-
-baqir <- log(25000)
-
-fin_imp_pop_under_baqir <- fin_imp %>%
-  filter(logpop < baqir )
-
-nrow(fin_imp_pop_under_baqir)
-
-gg_miss_var(fin_imp_pop_under_baqir, show_pct = T)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_under_baqir, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_under_baqir <- mice(fin_imp_pop_under_baqir, method = meth, maxit = 1)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_under_baqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r population_mid_50}
-
-# essentially the same - let's do full population
-(quantile(fin_seg$logpop, c(.25, .75), na.rm = T))
-(quantile(fin_imp$logpop, c(.25, .75), na.rm = T))
-
-baqir <- log(25000)
-
-fin_imp_pop_mid_50 <- fin_imp %>%
-  filter(logpop > 5.777652 & logpop < 7.936303)
-
-nrow(fin_imp_pop_mid_50)
-
-gg_miss_var(fin_imp_pop_mid_50, show_pct = T)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_mid_50, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_mid_50 <- mice(fin_imp_pop_mid_50, method = meth, maxit = 1)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_mid_50, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r population_top_1_trounstine}
-
-(quantile(fin_seg$logpop, c(.99), na.rm = T))
-(quantile(fin_dge$logpop, c(.99), na.rm = T))
-
-fin_imp_top_1_trounstine <- fin_imp %>%
-  filter(logpop > 13.1907 )
-
-nrow(fin_imp_top_1_trounstine)
-
-gg_miss_var(fin_imp_top_1_trounstine, show_pct = T)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_top_1_trounstine, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_top_1_trounstine <- mice(fin_imp_top_1_trounstine, method = meth, maxit = 5)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_top_1_trounstine, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-nrow(complete(imp_fs_pop_top_1_trounstine))
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r population_top_1}
-
-(quantile(fin_seg$logpop, c(.99), na.rm = T))
-(quantile(fin_dge$logpop, c(.99), na.rm = T))
-
-fin_imp_top_1 <- fin_imp %>%
-  filter(logpop > 11.28648)
-
-nrow(fin_imp_top_1)
-
-gg_miss_var(fin_imp_top_1, show_pct = T)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_top_1, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_top_1 <- mice(fin_imp_top_1_trounstine, method = meth, maxit = 5)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_top_1, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-nrow(complete(imp_fs_pop_top_1))
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-## make sure to talk about the fact that still a large number of values missing for the imputed variables here
-
-Before examining the results of Trounstine's model using the multiply imputed data, I first ran some diagnostic tests on the imputation results to make sure that everything ran as expected.
-First, I checked the convergence of the algorithm used within mice() by plotting the trace lines as a function of the number of iterations for each of the variables.
-Then, I visually inspected the distributions of the imputed data in comparison to the original data with density and strip plots.
-All of these checks suggested that the imputed values were within a plausible range of the data and that their distribution fit the underlying distribution of the data relatively well.
-The only cases in which there was some cause for concern were for some of the variables with very few missing values in the racial polarization dataset (such as the indicators for region).
-However, this is more or less to be expected given the small number of imputations performed in these cases.
-Thus, and especially because there are so few of these values missing in the actual datasets, this was not a major concern.
-See figures X and X1 to see the density plots of the imputed values overlayed on the density plots of the original variables.
-The rest of the plots and results of the diagnostic tests discussed here are presented in the Appendix.
-
-```{r rp_densityplot, echo = FALSE}
-
-densityplot(imp_1_rp)
-
-```
-
-```{r rp_imp_plot, include = FALSE}
-
-# ideally, the fits will intertwine and not exhibit any trends at later iterations.
-This seems to generally be the case.
-There are some issues with the results for some of the variables with very few missing values, which makes sense as we would expect the mean to be less reliable due to the law of large numbers and thus convergence is more difficult.
-However, since these are so few values, it is less important about how robust they are.
-
-plot(imp_1_rp)
-
-```
-
-```{r rp_stripplot, include = FALSE}
-
-# we can also check the imputed values against the original values using stripplot().
-Each column in each subplot represents a separate iteration.
-The magenta points represent the imputed data.
-The values of the variable in questions are along the y axis.
-We expect the spread of the data to be similar if the imputations were done well.
-If the data were missing completely at random, then the imputed data should have the same distribution as the original data.
-In particular, we want to be sure that the imputations are within a plausible range of the data.
-This is the case for all of our imputed variables, and there does not seem to be cause for alarm from these results.
-
-# this looks good? All reasonable values...
-
-stripplot(imp_1_rp)
-
-stripplot(imp_1_rp, biggestsplit)
-
-```
-
-```{r fs_densityplot, echo = FALSE}
-
-densityplot(imp_fs)
-densityplot(x=imp_fs , data= ~ H_citytract_NHW_i + chng5pctblk + 
-       chng5pctlatino + chng5pctasian + ideology_fill)
-
-```
-
-```{r fs_imp_plot, include = FALSE}
-
-# ideally, the fits will intertwine and not exhibit any trends at later iterations.
-This seems to generally be the case.
-There are some issues with the results for some of the variables with very few missing values, which makes sense as we would expect the mean to be less reliable due to the law of large numbers and thus convergence is more difficult.
-However, since these are so few values, it is less important about how robust they are.
-
-plot(imp_fs)
-
-```
-
-```{r fs_stripplot, include = FALSE}
-
-# we can also check the imputed values against the original values using stripplot().
-Each column in each subplot represents a separate iteration.
-The magenta points represent the imputed data.
-The values of the variable in questions are along the y axis.
-We expect the spread of the data to be similar if the imputations were done well.
-If the data were missing completely at random, then the imputed data should have the same distribution as the original data.
-In particular, we want to be sure that the imputations are within a plausible range of the data.
-This is the case for all of our imputed variables, and there does not seem to be cause for alarm from these results.
-
-# this looks good? All reasonable values...
-
-stripplot(imp_fs, H_citytract_NHW_i)
-
-stripplot(imp_fs, chng5pctblk)
-
-stripplot(imp_fs, chng5pctlatino)
-
-stripplot(imp_fs, chng5pctasian)
-
-stripplot(imp_fs, ideology_fill)
-
-```
-
-Given the promising results of the diagnostic checks, I next proceeded to re-estimate the original model using the multiply imputed datasets, pooling the results to produce final pooled regression coefficients and parameters.
-The results for the analyses using the racial polarization dataset are presented in tables 1-3.
-
-```{r rp_imputations, include = FALSE}
-
-# Now that we have imputed the missing data, we can re-run the analyses from the
-# original paper to see how and if this changes the analysis. We can use the
-# with() function from the mice package to fit each of the imputed datasets to
-# the model and then pool the results afterwards.
-
-# regression 1: fit multiple imputed datasets
-
-fit_imp_1_rp <- with(imp_1_rp, lmer(formula = biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
-
-# pool and summarize the analyses
-
-pool_imp_1_rp <- pool(fit_imp_1_rp)
-imp_1_rp_sum <- summary(pool_imp_1_rp)
-
-## regression 2 Table 1: fit multiple imputed datasets
-
-#formula = biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2)
-
-fit_imp_2_rp <- with(imp_1_rp, lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
-
-# pool and summarize the analyses
-
-pool_imp_2_rp <- pool(fit_imp_2_rp)
-imp_2_rp_sum <- summary(pool_imp_2_rp)
-
-## regression 3 Table 1 with new data
-
-#formula = biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2)
-
-fit_imp_3_rp <- with(imp_1_rp, lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
-
-# pool and summarize the analyses
-
-pool_imp_3_rp <- pool(fit_imp_3_rp)
-imp_3_rp_sum <- summary(pool_imp_3_rp)
-
-```
-
-The results of the model with the new dataset are slightly different in comparison to the original results from Trounstine (2016).
-With the imputed data, we now have a total of `r nrow(complete(rp_impute))` observations in our model as compared to the original model, which had only 91 observations.
-Interestingly, while the sign of the coefficient on the main variable of interest, the Theil's H segregation index, is the same and the standard error has decreased slightly, the result has become statisically insignificant and the 95% confidence interval contains zero.
-Thus while these results still suggest that segregation may be associated with increased political polarization, they confer a lesser degree of certainty than Trounstine's original analysis.
-The coefficients for % Black population, % Latino population, and median household income have also switched signs, and all coefficients except the indicator for a biracial election are also statistically insignificant, as was the case in the original analysis.
-The coefficient on the indicator for a primary election, has also changed from being significant in the original analysis to insignificant here.
-In general, the standard errors on the coefficients have decreased slightly.
-
-```{r results_printing_rp_impute_regressions_1, results = "asis", echo=FALSE}
-
-# print results of 1st regression
-
-imp_1_rp_sum_table <- as.data.frame(imp_1_rp_sum %>% 
-  select(term, estimate, std.error, p.value)) %>%
-  head(13)
-print(imp_1_rp_sum_table)
-
-stargazer(imp_1_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Multigroup Segregation Index}")
-
-```
-
-In the second and third regressions, the results are similar.
-The main coefficient on segregation index has decreased in magnitude, although in these specifications, it remains statistically significant.
-The other coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian, Black, and Latino have all switched signs.
-Standard errors have also reduced slightly in these specifications compared to the original analysis in @trounstine_segregation_2016.
-
-```{r results_printing_rp_impute_regressions_2, results = "asis", echo=FALSE}
-
-# print results of 2nd regression
-
-imp_2_rp_sum_table <- as.data.frame(imp_2_rp_sum %>% 
-  select(term, estimate, std.error, p.value)) %>%
-  head(13)
-print(imp_2_rp_sum_table)
-
-stargazer(imp_2_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Two-Group Segregation Index}")
-
-```
-
-```{r results_printing_rp_impute_regressions_3, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_3_rp_sum_table <- as.data.frame(imp_3_rp_sum %>% 
-  select(term, estimate, std.error, p.value)) %>%
-  head(13)
-print(imp_3_rp_sum_table)
-
-stargazer(imp_3_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Ideology Control}")
-```
-
-For the financial segregation dataset, we similarly fit each of our 5 imputed datasets to the original models from @trounstine_segregation_2016 using this data and then pool the results for each.
-The pooled results are presented in tables 4-6.
-
-# FS data results
-
-```{r fs_imputed_pooled_regressions, include = FALSE}
-# Main Analysis 2: Imputations
-
-## regression 1 Table 2
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-## regression 2 Table 2
-
-# fit multiple imputed datasets
-
-fit_imp_felm2 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm2 <- pool(fit_imp_felm2)
-imp_felm2_sum <- summary(pool_imp_felm2)
-
-## Regression 3 Table 2
-
-fit_imp_felm3 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm3 <- pool(fit_imp_felm3)
-imp_felm3_sum <- summary(pool_imp_felm3)
-
-print(imp_felm1_sum)
-
-```
-
-```{r fs_imputed_data_included_calc, include = FALSE}
-# how many observations were included in those 3 analyses?
-
-# basic filter for table for all regressions
-
-# xtreg dgepercap_cpi H_citytract_NHW_i diversityinterp pctblkpopinterp
-# pctasianpopinterp pctlatinopopinterp medinc_cpi pctlocalgovworker_100
-# pctrentersinterp pctover65 pctcollegegradinterp logpop if totaltracts>1 &
-# dgepercap_cpi~=0,fe vce(cluster geo_id2)
-
-fin <- complete(imp_fs) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
-
-# create dge variable used in regression
-
-fin_dge <-fin %>% filter(dgepercap_cpi != 0)
-
-# now we have 73,119 observations compared to 13,742. Calculation:
-
-nrow(fin_dge)
-
-# number of missing seg indexes before imputation: 282334
-
-# number missing now: 222957 -> Calculation:
-
-new_missing <- sum(is.na(complete(imp_fs)$H_citytract_NHW_i))
-
-# calculate number of observations we added to the sample: 59,377
-
-num_added <- 282334 - new_missing
-
-# INTERPRETATION BEFORE AFTER CHANGED The results of the first regression present a stark difference to the results of @trounstine_segregation_2016.
-Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant.
-Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
-The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.
-
-```
-
-The results of the first regression present a stark difference to the results of @trounstine_segregation_2016.
-Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant.
-Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
-The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.
-
-The results of the first regression indicate that Trounstine's results are robust to the inclusion of the imputed data, which led to the inclusion of an additional 59,377 observations in the analysis.
-The coefficients, standard errors, and significance levels are essentially unchanged.
-The same is largely true for the second and third specifications, but the magnitude of the coefficient on the segregation decreases slightly.
-
-```{r results_printing_fs_impute_regressions_1, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_felm1_sum_table <- as.data.frame(imp_felm1_sum %>% 
-  select(term, estimate, std.error, p.value))
-print(imp_felm1_sum_table)
-
-stargazer(imp_felm1_sum_table,
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Expenditure per Capita}")
-```
-
-```{r results_printing_fs_impute_regressions_2, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_felm2_sum_table <- as.data.frame(imp_felm2_sum %>% 
-  select(term, estimate, std.error, p.value))
-print(imp_felm2_sum_table)
-
-stargazer(imp_felm1_sum_table,
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Changing Demographics}")
-```
-
-```{r results_printing_fs_impute_regressions_3, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_felm3_sum_table <- as.data.frame(imp_felm3_sum %>% 
-  select(term, estimate, std.error, p.value))
-print(imp_felm3_sum_table)
-
-stargazer(imp_felm1_sum_table,
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Ideology Control}")
-```
-
-# FS NEW data results
-
-```{r new_fs_imputation_tries, include = FALSE}
-# Main Analysis 2: Imputations
-
-## regression 1 Table 2
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-## regression 2 Table 2
-
-# fit multiple imputed datasets
-
-fit_imp_felm2 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm2 <- pool(fit_imp_felm2)
-imp_felm2_sum <- summary(pool_imp_felm2)
-
-## Regression 3 Table 2
-
-fit_imp_felm3 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm3 <- pool(fit_imp_felm3)
-imp_felm3_sum <- summary(pool_imp_felm3)
-
-# INTERPRETATION BEFORE AFTER CHANGED The results of the first regression present a stark difference to the results of @trounstine_segregation_2016.
-Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant.
-Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
-The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.
-
-print(imp_felm1_sum)
-print(imp_felm2_sum)
-print(imp_felm3_sum)
-
-# large amount of data missing across the board in terms of years
-
-gg_miss_var(fin_dge, facet = year, show_pct = TRUE)
-
-# can't really tell anything about the region facet since a lot of obs missing region data
-
-gg_miss_var(fin_imp_extra, facet = region, show_pct = TRUE)
-
-# not necessarily a significant pattern across states either
-
-gg_miss_var(fin_imp_extra, facet = statecode, show_pct = TRUE)
-
-```
-
-# FS NEW AGAIN
-
-```{r}
-cities_to_keep <- c("Austin City", "Baltimore City", "Charlotte City", "Chicago City", "Cleveland City", "Columbus City", "Dallas City", "Denver City", "Detroit City", "Houston City", "Indianapolis", "Jacksonville", "Los Angeles City", "Memphis City", "Milwaukee City", "New York City", "Oklahoma City City", "Philadelphia City", "Phoenix City", "San Antonio City", "San Diego City", "San Francisco City", "San Jose City", "Tucson City", "Washington City")
-
-# apply the conditions in Stata regression to the fin_seg dataset
-
-fin_imp_cities <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0, cityname %in% cities_to_keep) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-# select the relevant variables to be imputed
-
-fin_imp <- fin_imp %>%
-  select(H_citytract_NHW_i, dgepercap_cpi, diversityinterp, pctblkpopinterp, pctasianpopinterp,
-         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
-         pctcollegegradinterp, logpop, geo_id2, chng5pctblk, chng5pctlatino, chng5pctasian,
-         ideology_fill)
-```
-
-```{r looking_at_original_data, include = FALSE}
-
-range(fin_seg$totaltractsf, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_seg %>%
-  ggplot() +
-  geom_histogram(aes(x = totaltractsf))
-
-range(fin_seg$logpop, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_seg %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-# add back in year, region, and statecode to be able to look at this
-
-fin_imp_old <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-fin_imp_extra <- fin_imp %>%
-  mutate(year = fin_imp_old$year,
-         region = fin_imp_old$region,
-         statecode = fin_imp_old$statecode)
-
-# large amount of data missing across the board in terms of years
-
-gg_miss_var(fin_imp_extra, facet = year, show_pct = TRUE)
-
-# can't really tell anything about the region facet since a lot of obs missing region data
-
-gg_miss_var(fin_imp_extra, facet = region, show_pct = TRUE)
-
-# not necessarily a significant pattern across states either
-
-gg_miss_var(fin_imp_extra, facet = statecode, show_pct = TRUE)
-
-```
-
-```{r looking_at_Trounstine_data, include = FALSE}
-
-# basic filter for table for all regressions
-
-# xtreg dgepercap_cpi H_citytract_NHW_i diversityinterp pctblkpopinterp
-# pctasianpopinterp pctlatinopopinterp medinc_cpi pctlocalgovworker_100
-# pctrentersinterp pctover65 pctcollegegradinterp logpop if totaltracts>1 &
-# dgepercap_cpi~=0,fe vce(cluster geo_id2)
-
-fin_trounstine <-fin_seg %>%
-  filter(totaltractsf >1 | is.na(totaltractsf)) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
-
-# create dge variable used in regression
-
-fin_dge_trounstine <-fin_trounstine %>% filter(dgepercap_cpi != 0)
-
-range(fin_dge_trounstine$totaltractsf, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_dge_trounstine %>%
-  ggplot() +
-  geom_histogram(aes(x = totaltractsf))
-
-range(fin_dge_trounstine$logpop, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_dge_trounstine %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-```
-
-```{r looking_at_imputed_data}
-
-fin_new_imp <- complete(new_imp_fs) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
-
-range(fin_new_imp$logpop, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_new_imp %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-```
-
-# Conclusion
-
-Why cities differ in their amount of spending on public goods is an interesting questions that is frequently debated in the literature.
-@trounstine_segregation_2016 posits that segregation may be an important underlying cause of the underprovsion of public goods.
-Finding evidence that residential segregation by race increases political partisanship, @trounstine_segregation_2016 argues that residential segregation can increase division and make cooperation amongst competing groups difficult, which results in decreased spending on public goods.
-The findings of @trounstine_segregation_2016 are particularly important because they suggest that segregation, as defined by many homogeneous neighborhoods within a larger diverse geographical area, is the key factor in disinvestment in public goods.
-This contradicts previous research which has suggested that levels of diversity were instead most important (see for example @baqir_public_1999 or @hopkins_diversity_2009).
-While @trounstine_segregation_2016 still represents relatively new reasearch as of 2020, it has yet to be fully vetted by additional research.
-Furthermore, some research that has been published on the topic since its publication suggests that other factors such as larger inequities in the political system favoring socially powerful groups [@lee_ethnic_2018] or the interaction of income and racial inequality [@an_its_2018] may be more important in explaining public goods provisions.
-
-I first worked to provide a check on the analysis presented in @trounstine_segregation_2016 by attempting to replicate the work in R.
-I was able to successfully replicate all of the main results from @trounstine_segregation_2016, with the exception of a few of a few marginal analyses of the complex, multi-level models which, to my knowledge, are currently not supported by available R packages.
-I was, however, able to successfully replicate these results in Stata.
-
-As an additional robustness check I also tested the models in @trounstine_segregation_2016 by re-running them with additional data that I imputed from missing values in the original datasets.
-The large number of missing values in both of the datasets used in @trounstine_segregation_2016's main analysis created a concern for potential bias in the original results and a lack of representativeness due to the large amount of data excluded from the regression analysis due to missing values.
-Thus, I used the mice package in R to create multiply imputed datasets, upon which I re-ran the models and pooled the results to generate the final model coefficients and parameters.
-
-The results of the data imputation exercise differed between the two datasets.
-For the analyses using the smaller, racial polarization dataset, the results from the imputed data resulted in a smaller magnitude of the coefficient on the main independent variable, and also made it statistically insignificant in the main model specification.
-This suggests that the segregation index may not have as strong of a positive association with political polarization as @trounstine_segregation_2016 suggests.
-However, for the analyses using the much larger financial segregation dataset, the results of the models using the multiply imputed data largely mirrored the results of @trounstine_segregation_2016, and the coefficients and significance levels were essentially the same between the two, with the standard errors on the model estimates being generally slightly lower for the analyses using the imputed data.
-This provides strong support for @trounstine_segregation_2016's finding that residential racial segregation is associated with diminshed spending on public goods.
-
-The replication exercise and robustness check using multiply imputed data here provide strong evidence that residential segregation along racial lines does in fact correlate negatively with spending on a variety of public goods.
-What my analysis calls more into question, is by what mechanism this happens.
-Using the multiply imputed data, I still found some evidence that segregation may be associated with increased political polarization which @trounstine_segregation_2016 suggests may lead to diminished public goods spending; however, the effect size is much smaller than that found in @trounstine_segregation_2016, and some of the results have become insignificant.
-It is possible that other mechanisms may be more important in explaining why segregation might be associated with decreased spending on public goods.
-For example, it could be that there is an important interaction effect between income and segregation, as others have previously suggested, or there could be some other intervening mechanism or a confounding variable that is leading to the negative association between segregation and lower spending on public goods.
-@trounstine_segregation_2016 has identified an important relationship between segregation and the provision of public goods.
-However, my analysis suggests that further research is needed to assess the potential mechanisms by which residential segregation by race or even a confounding variable may result in dimished spending.
-If this mechanism can be better understood, than it will be possible to more effectively understand and address the underprovision of public goods, which may inhibit social mobility and unfairly disadvantage certain groups.
-
-# Appendix
-
-```{r felm, eval = FALSE}
-
-# Main Analysis 2
-
-## regression 1 Table 2
-
-# The following is a fixed effects model regression with clustering around
-# geo_id2. It mandates that total census tracts in the city is greater than 1,
-# which we want because our measure of evenness of racial spread is constant for
-# cities with only one tract by our definition (which requires comparing tracts
-# within cities). It also mandates that Direct General Expenditures (DGE) per
-# capita, CPI adjusted is not equal to 0, which would be problematic and
-# indicate a potential data error. This regression regresses the DGE per capita
-# on the the two-group calculation of  Theil's H interpolated. Controls are
-# included for diversity and the % populations of Blacks, Asians, and Latinos to
-# help identify whether it is actually diversity that drives down spending.These
-# demographic controls also help to account for the fact that whites and
-# minorities tend to perfer different levels of government spending in general.
-# This will help isolate the effects of segregation v. other forms of diversity
-# on public spending. Other controls for Median household income, CPI adjusted,
-# percent over 65, percent college grads, percent local government workers, log
-# population help control for additional factors related to segregation and
-# expenditure. Controls for percent renters interpolated and Median household
-# income also help to control for the general wealth of cities, which could be a
-# potential driver of public spending. Fixed effects for cities are also
-# included  so that the author can examine the effect of segregation in the same
-# city over  time, which also helps control for many other factors not otherwise
-# taken into account (such as city age)
-
-# apply the conditions in Stata regression
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-# felm(y~x | factor(fe1) + factor(fe2) | 0 | clustervar)
-
-felm1 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-## regression 2 Table 2
-
-# This regression is the same as above except instead of using diversity, a new
-# control is added for the five year changes in racial group shares. The goal
-# here is to see whether or not changes in diversity are a driving factor
-# (rather than absolute levels of diversity).
-
-felm2 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-## Regression 3 Table 2
-
-# Column 3
-
-# As in column 3 of table 1, this regression simply adds in a control for  mean  ideology of city residents from General Social Survey (GSS) to control for the  possibility that ideology that segregated cities are more ideologically  conservative and that the conservative nature of segregated cities is what actually drives the effect.
-
-felm3 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-```
-
-```{r main_fp_tables, results = "asis", eval = FALSE}
-
-# create main table for table 3
-
-table2 <- stargazer(felm1, felm2, felm3, omit = c("year", "south", "midwest", "west"), 
-                    header = FALSE,
-                    title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures}")
-
-```
-
-```{r, eval = FALSE}
-
-# Main Analysis 3
-
-## regression 1 Table 3
-
-# Column 1
-
-# The following is a fixed effects model regression with clustering once again around geo_id2.
-Again, the if statements at the end mandate that total census tracts in the city is greater than 1, which we want because our measure of evenness of racial spread is constant for cities with only one tract by our definition (which requires comparing tracts within cities).
-They also mandate that the highways per capita, CPI adjsuted with no cap extend (lagged 5 years) is not equal to 0, which would be problematic and indicate a potential data error.
-The dependent variable here is highways per capita, CPI adjsuted with no cap extend (lagged 5 years) and it is regressed on the two group calculation of Theil's H, interpolated.
-Controls are added for diversity, percent population of Blacks, Asians, and Latinos, and median household CPI adjusted income as well as for % local government worker hundreds, percent rentership, percent over 65, percent college graduates, and the log of the population.
-This essentially examines the effect of segregation on the specific public good of highways.
-As in the previous table's regressions, fixed effects for cities are also included so that the author can examine the effect of segregation in the same city over time, which also helps control for many other factors not otherwise taken into account (such as city age) *
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), highwayspercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_1 <- felm(highwayspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-## regression 2 Table 3
-
-# Column 2
-
-# This is the same regression as column 1, but this time the dependent variable
-# is police per capita, CPI adjusted with no cap extend. This essentially
-# examines the effect of segregation on the specific public good of police per
-# capita.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), policepercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_2 <- felm( policepercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 3
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), parkspercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-# This is again the same regression, but this time the dependent variable is
-# parks per capita, CPI adjusted with no cap extend. This essentially examines
-# the effect of segregation on the specific public good of parks.
-
-felm2_3 <- felm(parkspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 4
-
-# This is again the same regression, but this time the dependent variable is
-# sewers per capita, CPI adjusted with no cap extend. This essentially examines
-# the effect of segregation on the specific public good of sewers.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), sewerspercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_4 <- felm(sewerspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 5
-
-# This is again the same regression, but this time the dependent variable is
-# Welfare, Health, Housing per capita, CPI adjusted, no cap expend. This
-# essentially examines the effect of segregation on the specific public good of
-# welfare and housing.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), welfhoushealthNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_5 <- felm(welfhoushealthNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 6
-
-# This is again the same regression, but this time the dependent variable is own
-# source of general revenue per capita, CPI adjusted. This essentially examines
-# the effect of segregation on the specific public good of own source revenue.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), genrevownpercap_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_6 <- felm(genrevownpercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-```
-
-```{r results = "asis", eval = FALSE}
-table3a <- stargazer(felm2_1, felm2_2, felm2_3, 
-          omit = c("year", "south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Public Goods A}")
-
-table3b <- stargazer(felm2_4, felm2_5, felm2_6, 
-          omit = c("year", "south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Public Goods B}")
-
-#star_sidewaystable(table3)
-```
-
-```{r iv_regs, eval = FALSE}
-
-## regression 1 Table 5
-
-# Top Row
-
-# Column 1
-
-# This is an instrumental variable regression with DGE per capita, adjusted by the CPI, as the dependent variable and total number of waterways as the instrumental variable for segregation.
-The instrument includes the log of the population in the first stage because the number of waterways is positively correlated to population and population is positively correlated with segregation.
-The control variables are the same as those in the regressions for Table 2 except for 2 changes: since the number of waterways does not change, there is no need for city fixed effects.
-Instead, we include fixed effects for the region and year.
-A lagged version of the dependent variable (dgepercap_cpilag) is added to the regressions to account for the high correlation between  observations for the same city over time and because changes in local budgets typically are incremental (NOTE: why exactly do we do this/why does it help/why not do it in the non-intstrumental regressions?).
-
-fin_seg_1 <- fin_seg %>%
-  filter(dgepercap_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-glimpse(fin_seg_1$medincinterp)
-
-# good explanation: http://eclr.humanities.manchester.ac.uk/index.php/IV_in_R
-
-# iv = ivreg(second stage regression | instrument1 + instrument2 )
-
-ivreg1 <- ivreg(dgepercap_cpi ~ H_citytract_NHW_i + dgepercap_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + dgepercap_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_1)
-
-# Column 2
-
-# this is the same regression as for column 1 but now we use the dependent variable highwayspercapNC_cpi to assess the effect of the instrumental  variable on highways per capita *
-
-fin_seg_2 <- fin_seg %>%
-  filter(highwayspercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg2 <- ivreg(highwayspercapNC_cpi ~ H_citytract_NHW_i + highwayspercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + highwayspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_2)
-
-# Column 3
-
-# this is the same regression as for column 1 but now we use the dependent variable policepercapNC_cpi to assess the effect of the instrumental variable on police per capita
-
-fin_seg_3 <- fin_seg %>%
-  filter(policepercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg3 <- ivreg(policepercapNC_cpi ~ H_citytract_NHW_i + policepercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + policepercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_3)
-
-# Column 4 this is the same regression as for column 1 but now we use the
-# dependent variable parkspercapNC_cpi to assess the effect of the instrumental
-# variable on parks per capita
-
-fin_seg_4 <- fin_seg %>%
-  filter(parkspercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg4 <- ivreg(parkspercapNC_cpi ~ H_citytract_NHW_i + parkspercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + parkspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_4)
-
-# Bottom Row
-
-# Column 1
-
-# this is the same regression as for column 1 but now we use the dependent
-# variable sewerspercapNC_cpi to assess the effect of the instrumental variable
-# on sewers per capita
-
-fin_seg_5 <- fin_seg %>%
-  filter(sewerspercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg5 <- ivreg(sewerspercapNC_cpi ~ H_citytract_NHW_i + sewerspercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + sewerspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_5)
-
-# Column 3
-
-# this is the same regression as for column 1 but now we use the dependent variable genrevownpercap_cpi to assess the effect of the instrumental variable on own source revenue per capita
-
-fin_seg_6 <- fin_seg %>%
-  filter(genrevownpercap_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg6 <- ivreg(genrevownpercap_cpi ~ H_citytract_NHW_i + genrevownpercap_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + genrevownpercap_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_6)
-
-# Column 2
-
-# this is the same regression as for column 1 but now we use the dependent
-# variable welfhoushealthNC_cpi to assess the effect of the instrumental
-# variable on welfare per capita
-
-fin_seg_7 <- fin_seg %>%
-  filter(welfhoushealthNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg7 <- ivreg(welfhoushealthNC_cpi ~ H_citytract_NHW_i + welfhoushealthNC_cpilag  + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + welfhoushealthNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_7)
-
-summary(ivreg7)
-
-```
-
-# Table 5
-
-```{r results = "asis", echo = FALSE}
-
-table5a <- stargazer(ivreg1, ivreg2, ivreg3, ivreg4,
-          omit = c("y5", "y6", "y7", "y8", "y9", "northeast", "south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach A}")
-
-table5b <- stargazer(ivreg5, ivreg6, ivreg7,
-          omit = c("y5", "y6", "y7", "y8", "y9", "northeast","south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach B}")
-```
-
-```{r import_data, include = FALSE}
-
-# make a list of the cities included in the analysis to filter out from the main
-# dataset as specified in the table
-
-cities_to_keep <- c("Austin City", "Baltimore City", "Charlotte City", "Chicago City", "Cleveland City", "Columbus City", "Dallas City", "Denver City", "Detroit City", "Houston City", "Indianapolis", "Jacksonville", "Los Angeles City", "Memphis City", "Milwaukee City", "New York City", "Oklahoma City City", "Philadelphia City", "Phoenix City", "San Antonio City", "San Diego City", "San Francisco City", "San Jose City", "Tucson City", "Washington City")
-
-# based on some investigation, the missing additional filter needed to replicate
-# appendix tables 1 and 2 is that biggest split cannot be NA. This was
-# discovered in attempting to create table 2. The number of elections with the
-# largest divides between each racial group were the same as in the table when
-# all results were included and only the summary stats differed in both tables
-# using the city and winner subset. So, I tried excluding all entries for which
-# biggestsplit was NA, and found that the resulting subset matched the
-# statistics in both tables.
-
-# create a subset of the data with the relevant cities where there is a winner
-# and the biggestsplit is not NA
-
-rp_sub <- rp %>%
-  filter(winner == 1) %>%
-  filter(cityname %in% cities_to_keep) %>%
-  filter(!(is.na(biggestsplit)))
-
-# select the relevant variables for the table
-
-rp_sub_a1 <- rp_sub %>%
-  select(biggestsplit, H_citytract_multi_i, H_citytract_NHW_i, diversityinterp, 
-         pctasianpopinterp, pctblkpopinterp, pctlatinopopinterp, medincinterp, 
-         pctrentersinterp, pctcollegegradinterp, biracial, nonpartisan, primary, 
-         logpop, whiteideology_fill2) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-# why are the exact variables H_citytract_NHW and whiteideology_fill not in the
-# data? Data variable names author uses and ones in the data don't exactly
-# match, but replication results are the same.
-
-```
-
-```{r table_a1, results="asis", echo = FALSE}
-
-# create a stargazer summary table for the relevant statistics of the racial
-# polarization data. I couldn't figure out how to change the text of the
-# statistic names at the top of the datat table. I also couldn't figure out how
-# to only not display additional digits for the income variable. May be
-# better to switch to gt for final version?
-
-stargazer(as.data.frame(rp_sub_a1),
-          omit.summary.stat = c("p25", "p75"),
-          title = "\\textbf{TABLE A1 Summary Statistics: Racial Polarization Data}",
-          column.labels = c("\\textbf{Variable}","\\textbf{Obs}", "\\textbf{Mean}", "\\textbf{Std. Dev.}", "\\textbf{Min}", "\\textbf{Max}"),
-          covariate.labels = c("Largest Racial Divide","\\emph{H} Index: Multigroup", "\\emph{H} Index: Two-Group", "Diversity", "\\% Asian", "\\% Black", "\\% Latino", "Median HH Income", "\\% Renters", "\\% College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology"),
-          no.space = TRUE,
-          header = FALSE)
-
-```
-
-```{r table_a2_data_manipulation, include = FALSE}
-
-# initialize variables to indicate if a racial divide had the biggest divide in
-# the election
-
-rp_sub$biggest_split_bw <- NA
-rp_sub$biggest_split_lw <- NA
-rp_sub$biggest_split_bl <- NA
-
-# change the NA value to 1 if the relevant divide was the biggest in the election
-
-rp_sub$biggest_split_bw[rp_sub$biggestsplit_gr == 1] <- 1
-rp_sub$biggest_split_lw[rp_sub$biggestsplit_gr == 2] <- 1
-rp_sub$biggest_split_bl[rp_sub$biggestsplit_gr == 3] <- 1
-
-# generate the dataset of summary statistics to replicate the second appendix
-# table. Group by city name and then summarize the mean H indexes. Sum the
-# number of biggest splits by racial divide for each city
-
-rp_sub_2 <- rp_sub %>%
-  group_by(cityname) %>%
-  summarise(mean_multi_H = mean(H_citytract_multi_i),
-            mean_multi_two_group = mean(H_citytract_NHW_i),
-            sum_bw = sum(biggest_split_bw, na.rm = T),
-            sum_lw = sum(biggest_split_lw, na.rm = T),
-            sum_bl = sum(biggest_split_bl, na.rm = T))
-```
-
-```{r table_a2, echo = FALSE}
-
-# create appendix table A2 to present the summary statistics for cities included
-# in racial polarization data. Efforts to make columns narrower were
-# unsuccessful, so some of the labels in the column names were changed to make
-# the table fit. I also couldn't get the title to print out without including a
-# non-Null subtitle.
-
-city_names <- c("Austin, TX", "Baltimore, MD", "Charlotte, NC", "Chicago, IL", "Cleveland, OH", "Columbus, OH", "Dallas, TX", "Denver, CO", "Detroit, MI", "Houston, TX", "Indianapolis, IN", "Jacksonville, FL", "Los Angeles, CA", "Memphis, TN", "Milwaukee, WI", "New York, NY", "Oklahoma, OK", "Philadelphia, PA", "Phoenix, AZ", "San Antonio, TX","San Diego, CA", "San Francisco, CA", "San Jose, CA", "Tucson, AZ", "Washington, DC")
-
-rp_sub_2$cityname <- city_names
-
-gt(rp_sub_2) %>%
-  tab_header(title = md("**TABLE A2 Cities Included in Racial Polarization Data**"),
-             subtitle = "Replication") %>%
-  tab_spanner(
-      label = md("**Segregation: Mean *H* Index**"),
-      columns = vars(mean_multi_H, mean_multi_two_group)) %>%
-  tab_spanner(
-      label = md("**Largest Racial Divide, Number of Elections**"),
-      columns = vars(sum_bw, sum_lw, sum_bl)) %>%
-  fmt_number(columns = vars(mean_multi_H, mean_multi_two_group),
-             decimals = 3) %>%
-  cols_label(cityname = "City Name",
-             mean_multi_H = md("Multigroup"),
-             mean_multi_two_group = md("Two-Group"),
-             sum_bw = "Black/White",
-             sum_lw = "Latino/White",
-             sum_bl = "Black/Latino") %>%
-  cols_width(
-    vars(cityname) ~ px(10),
-    TRUE ~ px(20)
-  ) %>%
-  cols_align(
-    columns = vars(cityname),
-    align = "left"
-  ) %>%
-  tab_options(
-    table.margin.left = px(5), 
-    table.margin.right = px(5),
-    data_row.padding = px(1),
-    table.width = pct(90)
-  )
-
-```
-
-```{r include = FALSE, include = FALSE}
-
-# basic filter for table for all regressions
-
-# xtreg dgepercap_cpi H_citytract_NHW_i diversityinterp pctblkpopinterp
-# pctasianpopinterp pctlatinopopinterp medinc_cpi pctlocalgovworker_100
-# pctrentersinterp pctover65 pctcollegegradinterp logpop if totaltracts>1 &
-# dgepercap_cpi~=0,fe vce(cluster geo_id2)
-
-fin <-fin_seg %>%
-  filter(totaltractsf >1 | is.na(totaltractsf)) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
-
-# create dge variable used in regression
-
-fin_dge <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_dge_tab <- tibble(
-  Variable = "Direct General Expenditure per Capita",
-  Obs = nrow(fin_dge),
-  Mean = mean(fin_dge$dgepercap_cpi, na.rm = T),
-  SD = sd(fin_dge$dgepercap_cpi, na.rm = T),
-  Min = min(fin_dge$dgepercap_cpi, na.rm = T),
-  Max = max(fin_dge$dgepercap_cpi, na.rm = T)
-)
-
-print(fin_dge_tab)
-
-# cities in original Trounstine
-
-cities_trounstine_fp <- fin_dge %>%
-  select(geo_id2) %>%
-  unique() %>%
-  pull()
-
-# pop quantiles original Trounstine
-
-quantile(fin_dge$logpop, c(.10, .25, .5, .75, .90))
-
-quantile(fin_dge$logpop, c(.05, .95))
-
-nrow(fin_imp)
-
-fin_imp_pop_trounstine_95 <- fin_imp %>%
-  filter(logpop < 11.93437 & logpop > 8.7754)
-
-# creat summary for highways
-fin_hw <-fin %>% filter(highwayspercapNC_cpi != 0)
-
-fin_hw_tab <- tibble(
-  Variable = "Highways per Capita",
-  Obs = nrow(fin_hw),
-  Mean = mean(fin_hw$highwayspercapNC_cpi, na.rm = T),
-  SD = sd(fin_hw$highwayspercapNC_cpi, na.rm = T),
-  Min = min(fin_hw$highwayspercapNC_cpi, na.rm = T),
-  Max = max(fin_hw$highwayspercapNC_cpi, na.rm = T)
-)
-
-print(fin_hw_tab)
-
-a3_final <- full_join(fin_dge_tab, fin_hw_tab)
-
-# parks
-
-fin_park <-fin %>% filter(parkspercapNC_cpi != 0)
-
-fin_park_tab <- tibble(
-  Variable = "Parks per Capita",
-  Obs = nrow(fin_park),
-  Mean = mean(fin_park$parkspercapNC_cpi, na.rm = T),
-  SD = sd(fin_park$parkspercapNC_cpi, na.rm = T),
-  Min = min(fin_park$parkspercapNC_cpi, na.rm = T),
-  Max = max(fin_park$parkspercapNC_cpi, na.rm = T)
-)
-
-print(fin_park_tab)
-
-a3_final <- full_join(a3_final, fin_park_tab)
-
-# police
-
-fin_police <-fin %>% filter(policepercapNC_cpi != 0)
-
-fin_police_tab <- tibble(
-  Variable = "Police per Capita",
-  Obs = nrow(fin_police),
-  Mean = mean(fin_police$policepercapNC_cpi, na.rm = T),
-  SD = sd(fin_police$policepercapNC_cpi, na.rm = T),
-  Min = min(fin_police$policepercapNC_cpi, na.rm = T),
-  Max = max(fin_police$policepercapNC_cpi, na.rm = T)
-)
-
-print(fin_police_tab)
-
-a3_final <- full_join(a3_final, fin_police_tab)
-
-# sewers
-
-fin_sew <-fin %>% filter(sewerspercapNC_cpi != 0)
-
-fin_sew_tab <- tibble(
-  Variable = "Sewers per Capita",
-  Obs = nrow(fin_sew),
-  Mean = mean(fin_sew$sewerspercapNC_cpi, na.rm = T),
-  SD = sd(fin_sew$sewerspercapNC_cpi, na.rm = T),
-  Min = min(fin_sew$sewerspercapNC_cpi, na.rm = T),
-  Max = max(fin_sew$sewerspercapNC_cpi, na.rm = T)
-)
-
-print(fin_sew_tab)
-
-a3_final <- full_join(a3_final, fin_sew_tab)
-
-# welfare
-
-fin_welfare <-fin %>% filter(welfhoushealthNC_cpi != 0)
-
-fin_welfare_tab <- tibble(
-  Variable = "Welfare, Health, and Housing per Capita",
-  Obs = nrow(fin_welfare),
-  Mean = mean(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
-  SD = sd(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
-  Min = min(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
-  Max = max(fin_welfare$welfhoushealthNC_cpi, na.rm = T)
-)
-
-print(fin_welfare_tab)
-
-a3_final <- full_join(a3_final, fin_welfare_tab)
-
-# own source revenue
-
-fin_own <-fin %>% filter(genrevownpercap_cpi != 0)
-
-fin_own_tab <- tibble(
-  Variable = "Own Source Revenue per Capita",
-  Obs = nrow(fin_own),
-  Mean = mean(fin_own$genrevownpercap_cpi, na.rm = T),
-  SD = sd(fin_own$genrevownpercap_cpi, na.rm = T),
-  Min = min(fin_own$genrevownpercap_cpi, na.rm = T),
-  Max = max(fin_own$genrevownpercap_cpi, na.rm = T)
-)
-
-print(fin_own_tab)
-
-a3_final <- full_join(a3_final, fin_own_tab)
-
-# two group H
-
-fin_h <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_h_tab <- tibble(
-  Variable = "Two-Group H Index",
-  Obs = nrow(fin_h),
-  Mean = mean(fin_h$H_citytract_NHW_i, na.rm = T),
-  SD = sd(fin_h$H_citytract_NHW_i, na.rm = T),
-  Min = min(fin_h$H_citytract_NHW_i, na.rm = T),
-  Max = max(fin_h$H_citytract_NHW_i, na.rm = T)
-)
-
-print(fin_h_tab)
-
-a3_final <- full_join(a3_final, fin_h_tab)
-
-# Diversity
-
-fin_div <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_div_tab <- tibble(
-  Variable = "Diversity",
-  Obs = nrow(fin_div),
-  Mean = mean(fin_div$diversityinterp, na.rm = T),
-  SD = sd(fin_div$diversityinterp, na.rm = T),
-  Min = min(fin_div$diversityinterp, na.rm = T),
-  Max = max(fin_div$diversityinterp, na.rm = T)
-)
-
-print(fin_div_tab)
-
-a3_final <- full_join(a3_final, fin_div_tab)
-
-# % black
-
-fin_pctblk <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pctblk_tab <- tibble(
-  Variable = "%  Black",
-  Obs = nrow(fin_pctblk),
-  Mean = mean(fin_pctblk$pctblkpopinterp, na.rm = T),
-  SD = sd(fin_pctblk$pctblkpopinterp, na.rm = T),
-  Min = min(fin_pctblk$pctblkpopinterp, na.rm = T),
-  Max = max(fin_pctblk$pctblkpopinterp, na.rm = T)
-)
-
-print(fin_pctblk_tab)
-
-a3_final <- full_join(a3_final, fin_pctblk_tab)
-
-# % asian
-
-fin_pcta <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pcta_tab <- tibble(
-  Variable = "%  Asian",
-  Obs = nrow(fin_pcta),
-  Mean = mean(fin_pcta$pctasianpopinterp, na.rm = T),
-  SD = sd(fin_pcta$pctasianpopinterp, na.rm = T),
-  Min = min(fin_pcta$pctasianpopinterp, na.rm = T),
-  Max = max(fin_pcta$pctasianpopinterp, na.rm = T)
-)
-
-print(fin_pcta_tab)
-
-a3_final <- full_join(a3_final, fin_pcta_tab)
-
-# % latino
-
-fin_pctla <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pctla_tab <- tibble(
-  Variable = "%  Latino",
-  Obs = nrow(fin_pctla),
-  Mean = mean(fin_pctla$pctlatinopopinterp, na.rm = T),
-  SD = sd(fin_pctla$pctlatinopopinterp, na.rm = T),
-  Min = min(fin_pctla$pctlatinopopinterp, na.rm = T),
-  Max = max(fin_pctla$pctlatinopopinterp, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_pctla_tab)
-
-# 5y black
-
-fin_chng5pctblk <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))
-
-nrow(fin_chng5pctblk)
-
-fin_chng5pctblk_tab <- tibble(
-  Variable = "5Y Change, % Black",
-  Obs = nrow(fin_chng5pctblk),
-  Mean = mean(fin_chng5pctblk$chng5pctblk, na.rm = T),
-  SD = sd(fin_chng5pctblk$chng5pctblk, na.rm = T),
-  Min = min(fin_chng5pctblk$chng5pctblk, na.rm = T),
-  Max = max(fin_chng5pctblk$chng5pctblk, na.rm = T)
-)
-
-print(fin_chng5pctblk_tab)
-
-a3_final <- full_join(a3_final, fin_chng5pctblk_tab)
-
-# 5y latino
-
-fin_chng5pctlatino <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))
-
-fin_chng5pctlatino_tab <- tibble(
-  Variable = "5Y Change, % Latino",
-  Obs = nrow(fin_chng5pctlatino),
-  Mean = mean(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
-  SD = sd(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
-  Min = min(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
-  Max = max(fin_chng5pctlatino$chng5pctlatino, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_chng5pctlatino_tab)
-
-# 5y asian
-
-fin_chng5pctasian <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))
-
-fin_chng5pctasian_tab <- tibble(
-  Variable = "5Y Change, % Asian",
-  Obs = nrow(fin_chng5pctasian),
-  Mean = mean(fin_chng5pctasian$chng5pctasian, na.rm = T),
-  SD = sd(fin_chng5pctasian$chng5pctasian, na.rm = T),
-  Min = min(fin_chng5pctasian$chng5pctasian, na.rm = T),
-  Max = max(fin_chng5pctasian$chng5pctasian, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_chng5pctasian_tab)
-
-# median income
-
-fin_med <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_med_tab <- tibble(
-  Variable = "Median Income",
-  Obs = nrow(fin_med),
-  Mean = mean(fin_med$medinc_cpi, na.rm = T),
-  SD = sd(fin_med$medinc_cpi, na.rm = T),
-  Min = min(fin_med$medinc_cpi, na.rm = T),
-  Max = max(fin_med$medinc_cpi, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_med_tab)
-
-# % local gov. employees
-
-fin_pctlocal <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pctlocal_tab <- tibble(
-  Variable = "% Local Gov. Employees",
-  Obs = nrow(fin_pctlocal),
-  Mean = mean(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
-  SD = sd(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
-  Min = min(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
-  Max = max(fin_pctlocal$pctlocalgovworker_100, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_pctlocal_tab)
-
-# % renters
-
-fin_rent <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_rent_tab <- tibble(
-  Variable = "% Renters",
-  Obs = nrow(fin_rent),
-  Mean = mean(fin_rent$pctrentersinterp, na.rm = T),
-  SD = sd(fin_rent$pctrentersinterp, na.rm = T),
-  Min = min(fin_rent$pctrentersinterp, na.rm = T),
-  Max = max(fin_rent$pctrentersinterp, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_rent_tab)
-
-# % over 65
-
-fin_65 <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_65_tab <- tibble(
-  Variable = "% Over 65",
-  Obs = nrow(fin_65),
-  Mean = mean(fin_65$pctover65, na.rm = T),
-  SD = sd(fin_65$pctover65, na.rm = T),
-  Min = min(fin_65$pctover65, na.rm = T),
-  Max = max(fin_65$pctover65, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_65_tab)
-
-# % college degree
-
-fin_college <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_college_tab <- tibble(
-  Variable = "% College Degree",
-  Obs = nrow(fin_college),
-  Mean = mean(fin_college$pctcollegegradinterp, na.rm = T),
-  SD = sd(fin_college$pctcollegegradinterp, na.rm = T),
-  Min = min(fin_college$pctcollegegradinterp, na.rm = T),
-  Max = max(fin_college$pctcollegegradinterp, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_college_tab)
-
-# pop logged
-
-fin_logpop <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_logpop_tab <- tibble(
-  Variable = "Population (logged)",
-  Obs = nrow(fin_logpop),
-  Mean = mean(fin_logpop$logpop, na.rm = T),
-  SD = sd(fin_logpop$logpop, na.rm = T),
-  Min = min(fin_logpop$logpop, na.rm = T),
-  Max = max(fin_logpop$logpop, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_logpop_tab)
-
-# city ideology
-
-fin_ideo <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(ideology_fill)))
-
-nrow(fin_ideo)
-
-fin_ideo_tab <- tibble(
-  Variable = "City Ideology",
-  Obs = nrow(fin_ideo),
-  Mean = mean(fin_ideo$ideology_fill, na.rm = T),
-  SD = sd(fin_ideo$ideology_fill, na.rm = T),
-  Min = min(fin_ideo$ideology_fill, na.rm = T),
-  Max = max(fin_ideo$ideology_fill, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_ideo_tab)
-
-# population
-fin_population <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_population_tab <- tibble(
-  Variable = "Population",
-  Obs = nrow(fin_population),
-  Mean = mean(fin_population$population, na.rm = T),
-  SD = sd(fin_population$population, na.rm = T),
-  Min = min(fin_population$population, na.rm = T),
-  Max = max(fin_population$population, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_population_tab)
-
-```
-
-```{r, echo = FALSE}
-gt(a3_final) %>%
-    tab_header(title = md("**TABLE A3 Summary Statistics: Census of Government Finance and Population**"),
-             subtitle = "") %>%
-    fmt_number(columns = vars(Mean, SD, Min, Max),
-             decimals = 3) %>%
-    cols_label(Obs = md("**Obs**"),
-               Mean = md("**Mean**"),
-               SD = md("**SD**"),
-               Min = md("**Min**"),
-               Max = md("**Max**")
-                        ) 
-```
-
-# Bibliography

### 2020-04-30 Final_Draft.Rmd
changes to appendix replication table

@@
   pdf_document:
+    fig_caption: yes
     extra_dependencies: ["rotating"]
@@
 fin_seg<- read_dta("fin_seg.dta")
-
-# add row numbers for fin_seg
-
-fin_seg$row_num <- as.integer(rownames(fin_seg))
 
@@
          chng5pctblk, chng5pctlatino, chng5pctasian, ideology_fill)
-
-miss_var_summary(fin_imp)
-miss_var_summary(rp_impute)
 
@@
 Nevertheless, these results were successfully replicated in Stata.
+
+There was one interesting outcome from my attempt to replicate the original Stata code in R.
+Due to the differences in R and Stata in dealing with missing values, the results of my first replication of analyses using the financial segregation dataset were slightly different than the results in Stata from the original paper.
+In order to exclude cities from her analysis with only one census tract, Trounstine conditions her regressions in Stata such that the value for the number of census tracts is greater than one.
+In Stata, this does not remove missing values, whereas in R, it does.
+Since this variable is used only as a conditional filter and not as a regression variable (and thus, the observations with missing values for number of census tracts are not dropped), Trounstine’s analysis includes 14 cities and 58 observations with missing values for census tracts in addition to cities with two or more census tracts.
+This is a potential oversight on the part of the author, and I would suggest also dropping observations with missing census tract data, or else imputing them given that the aim of her condition was to exclude cities without a sufficient number of census tracts.
+Nevertheless, dropping these values did not have much of an effect on the subsequent results, likely because they represent a small proportion of the overall sample.
+
+# Extension
+
+One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data values in her original datasets.
+Because both R and Stata drop any observations with missing values for any of the variables used in a regression, this can exlcude a large portion of the data from the analysis and potentially bias the results if the data is not missing completely at random.
+A large amount of data is missing in both of the main datasets used in the analyses of @trounstine_segregation_2016.
+The main model specification using the racial polarization dataset exludes `r (obs_rp - 91)` of the original  `r obs_rp` observations, or  %`r round(100*(obs_rp - 91)/obs_rp,2)` of the data.
+Additionally, the main model specification using the financial segregation data set excludes `r round(obs_fin_seg - 13742,2)` of the original `r obs_fin_seg` observations, or %`r round(100*(obs_fin_seg - 13742)/ obs_fin_seg,2)` of observations from the original dataset.
+
+In an attempt to better deal with the problem of missing data in @trounstine_segregation_2016, I impute missing values in the original data using the mice package in R, which generates multivariate imputations using chained equations [@mice].
+While there are a variety of different imputation methods that could have been employed, multiple imputation (such as the multiple multivariate imputations generated by mice) is desirable because instead of inputting a single value such as the mean for missing values, it instead uses the distribution of the available data to estimate multiple potential values for the missing data.
+As a result, multiple imputation helps to account for the uncertainty inherent in the imputation process and allows for the calculation of standard errors around estimators.
+Thus, multiple imputation allows the researcher to more accurately assess the of uncertainty in the analysis in general.
+
+Before performing the multiple imputations on the datasets, I first examined the missing data for patterns.
+To better understand any potential patterns in missing data, I plotted the pattern of missingness and created a histogram showing the frequency of missing values for those variables with missing values in figure X1 for the racial polarization data and figure X2 for the financial segregation data.
+Looking at figure X1, the histogram shows that the variables for the largest vote split along racial lines and the variable indicating whether or not the election had candidates of more than one race had by far the largest percentages of missing data, missing %`r round(sum(is.na(rp_impute$biggestsplit))/nrow(rp_impute)*100,2)` and  %`r round(sum(is.na(rp_impute$biracial))/nrow(rp_impute)*100,2)`, respectively.
+It is important to note that the variable for the largest vote split along racial lines is the dependent variable in the regresison analysis, and thus, we are missing a large percentage of this key variable.
+From the plot on the right, we can see that approximately 42% of observations are complete (have no missing values).
+There seem to be a correspondence between missing a value for the largest vote split and missing a value for the biracial election indicator.
+There also seem to be about 2% of values for wich most of the variables are missing.
+However, most observations are not missing more than 2-3 values.
+
+# Appendix
+
+```{r include = FALSE}
+
+## regression 1 Table 1
+
+# perform a multi-level mixed-effects linear regression of biggest split on the multi-group H index with controls for Herfindahl Diversity Index, % Asian interpolated, % Black interpolated, % Latino interpolated, median household income interpolated, % renters interpolated, percent college grads interpolated, a dummy indicating if there were biracial candidates in the election, a dummy  indicating if the election was nonpartisan, an indicator if the election was a primary, and the log population.
+The regression also includes fixed effects for year and region and random effects for cities (geo_id2).
+Diversity is  included because of the claim that more diverse populations will have more heterogeneous political preferences.
+The other fixed effect control variables are included because they are known to be potentially correlated with segregation.
+winner == 1 requires that there was a winner in the election.
+
+# regression specification. Apply REML = FALSE. The default for lmer() in R is
+# to optimize the restricted (residual) maximum likelihood (REML) whereas in
+# xtmixed in Stata the default is to optimize the log likelihood (which you can
+# do in lmer() in R by setting REML = FALSE), so this will match the STATA code
+
+m1 <- lmer(biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
+
+## regression 2 Table 1
+
+# Perform the same regression as for Column 1 above but this time regress on the two-group calculation of Theil's H interpolated.
+It is unclear where the "diversity" variable is coming from, as the only variable related to diversity in the specificed dataset is diversityinterp.
+This is a problem that will need to be resolved.
+Essentially, this regression just tests an alternate specification to the first in which the segregation index in defined in terms of two-groups rather than multiple.
+
+m2 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
+
+# perform the same regression as for column 2, but now add in a measure of
+# average white political ideology. The point of this is to control for ideology
+# so that the author can separate any effects of segregation from any potential
+# effects of white political ideology. This is important because it is possible
+# that segregation is just a proxy for white conservatism and thus failure to
+# include this variable could lead to ommitted variable bias.
+
+m3 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
+
+```
+
+```{r results="asis", echo = FALSE, fig.cap= "THIS IS A CAPTION IS IT WORKING WHAT IS GOING ON!"}
+
+# create a stargazer table of the results
+
+t1 <- stargazer(m1, m2, m3, omit = c("year", "south", "midwest", "west"),
+                header = FALSE,
+                title = "\\textbf{Racial Polarization in Segregated Cities}",
+                single.row = TRUE,
+                no.space = FALSE,
+                keep.stat = c("n"),
+                covariate.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Diversity", "Percent Asian", "Percent Black", "Percent Latino", "Medain HH Income (1000s)", "Percent Renters", "Percent College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology", "Constant"),
+                dep.var.labels = c("Racial Divide"),
+                column.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Ideology Controls"),
+                notes = "This table displays the results of the replication effort of the analyses conducted in Trounstine (2016) using the racial polarization dataset.
+The replication code can be found on my personal Github repository, which is linked in the introduction.
+The original table is displayed for comparison as Figure 1.)")
+
+# note: "This table displays the results of the replication effort of the analyses conducted in Trounstine (2016) using the racial polarization dataset.
+The replication code can be found on my personal [Github repository](https://github.com/mburzillo/new_final_project).
+The original table is displayed for comparison as Figure 1.")
+
+```
+
+![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016.
+My replication of these results can be found in Table 1 in this paper.](table_1.png)

### 2020-04-30 Draft_1.Rmd
changes to appendix and tables

@@
 header_includes:
-  usepackage{float}
-  usepackage{dcolumn}
-  usepackage{rotating}
-  restylefloat{table}
+  \usepackage{float}
+  \usepackage{dcolumn}
+  \usepackage{rotating}
+  \restylefloat{table}
 

### 2020-04-30 Final_Draft.Rmd
changes to appendix and tables

@@
     fig_caption: yes
-    extra_dependencies: ["rotating"]
 bibliography: final_proj_bib.bib
@@
 link_citations: true
-header_includes:
-  usepackage{float}
-  usepackage{dcolumn}
-  usepackage{rotating}
-  restylefloat{table}
+keep_tex: yes
+header_includes: \usepackage{float}
 
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, fig.align = "center")
+knitr::opts_chunk$set(echo = TRUE, fig.align = "center", fig.pos = "!H")
 knitr::write_bib(c("knitr", "stringr"), "bib.bib", width = 60)
@@
 library(knitr)
-library(stargazer)
 library(lme4)
@@
                 column.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Ideology Controls"),
-                notes = "This table displays the results of the replication effort of the analyses conducted in Trounstine (2016) using the racial polarization dataset.
-The replication code can be found on my personal Github repository, which is linked in the introduction.
-The original table is displayed for comparison as Figure 1.)")
+                notes = "This table displays the results of the replication\neffort of the analyses conducted in Trounstine (2016) using the racial polarization dataset.\nThe replication code can be found on my personal Github repository, which is linked in the introduction.
+The original table is displayed for comparison as Figure 1.)",
+                notes.align = "l")
 
@@
 My replication of these results can be found in Table 1 in this paper.](table_1.png)
+
+```{r felm, include = FALSE}
+
+# Main Analysis 2
+
+## regression 1 Table 2
+
+# The following is a fixed effects model regression with clustering around
+# geo_id2. It mandates that total census tracts in the city is greater than 1,
+# which we want because our measure of evenness of racial spread is constant for
+# cities with only one tract by our definition (which requires comparing tracts
+# within cities). It also mandates that Direct General Expenditures (DGE) per
+# capita, CPI adjusted is not equal to 0, which would be problematic and
+# indicate a potential data error. This regression regresses the DGE per capita
+# on the the two-group calculation of  Theil's H interpolated. Controls are
+# included for diversity and the % populations of Blacks, Asians, and Latinos to
+# help identify whether it is actually diversity that drives down spending.These
+# demographic controls also help to account for the fact that whites and
+# minorities tend to perfer different levels of government spending in general.
+# This will help isolate the effects of segregation v. other forms of diversity
+# on public spending. Other controls for Median household income, CPI adjusted,
+# percent over 65, percent college grads, percent local government workers, log
+# population help control for additional factors related to segregation and
+# expenditure. Controls for percent renters interpolated and Median household
+# income also help to control for the general wealth of cities, which could be a
+# potential driver of public spending. Fixed effects for cities are also
+# included  so that the author can examine the effect of segregation in the same
+# city over  time, which also helps control for many other factors not otherwise
+# taken into account (such as city age)
+
+# apply the conditions in Stata regression
+
+fin_seg_sub <- fin_seg %>%
+  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0) %>%
+  mutate(medinc_cpi = medinc_cpi/1000)
+
+# felm(y~x | factor(fe1) + factor(fe2) | 0 | clustervar)
+
+felm1 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
+
+## regression 2 Table 2
+
+# This regression is the same as above except instead of using diversity, a new
+# control is added for the five year changes in racial group shares. The goal
+# here is to see whether or not changes in diversity are a driving factor
+# (rather than absolute levels of diversity).
+
+felm2 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
+
+## Regression 3 Table 2
+
+# Column 3
+
+# As in column 3 of table 1, this regression simply adds in a control for  mean  ideology of city residents from General Social Survey (GSS) to control for the  possibility that ideology that segregated cities are more ideologically  conservative and that the conservative nature of segregated cities is what actually drives the effect.
+
+felm3 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
+
+```
+
+```{r main_fp_tables, results = "asis", echo = FALSE}
+
+# create main table for table 3
+
+table2 <- stargazer(felm1, felm2, felm3, omit = c("year", "south", "midwest", "west"), 
+                    header = FALSE,
+                    title = "\textbf{Effect of Segregation on Overall per Capita City Expenditures}",
+                    covariate.labels = c("White/Nonwhite H Index", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Change Percent Black", "Change Percent Latino", "Change Percent Asian", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Population (logged)", "White Ideology", "Constant"))
+
+```
+
+```{r, include = FALSE}
+
+# Main Analysis 3
+
+## regression 1 Table 3
+
+# Column 1
+
+# The following is a fixed effects model regression with clustering once again around geo_id2.
+Again, the if statements at the end mandate that total census tracts in the city is greater than 1, which we want because our measure of evenness of racial spread is constant for cities with only one tract by our definition (which requires comparing tracts within cities).
+They also mandate that the highways per capita, CPI adjsuted with no cap extend (lagged 5 years) is not equal to 0, which would be problematic and indicate a potential data error.
+The dependent variable here is highways per capita, CPI adjsuted with no cap extend (lagged 5 years) and it is regressed on the two group calculation of Theil's H, interpolated.
+Controls are added for diversity, percent population of Blacks, Asians, and Latinos, and median household CPI adjusted income as well as for % local government worker hundreds, percent rentership, percent over 65, percent college graduates, and the log of the population.
+This essentially examines the effect of segregation on the specific public good of highways.
+As in the previous table's regressions, fixed effects for cities are also included so that the author can examine the effect of segregation in the same city over time, which also helps control for many other factors not otherwise taken into account (such as city age) *
+
+fin_seg_sub <- fin_seg %>%
+  filter(totaltractsf > 1 | is.na(totaltractsf), highwayspercapNC_cpi != 0) %>%
+  mutate(medinc_cpi = medinc_cpi/1000)
+
+felm2_1 <- felm(highwayspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
+
+## regression 2 Table 3
+
+# Column 2
+
+# This is the same regression as column 1, but this time the dependent variable
+# is police per capita, CPI adjusted with no cap extend. This essentially
+# examines the effect of segregation on the specific public good of police per
+# capita.
+
+fin_seg_sub <- fin_seg %>%
+  filter(totaltractsf > 1 | is.na(totaltractsf), policepercapNC_cpi != 0) %>%
+  mutate(medinc_cpi = medinc_cpi/1000)
+
+felm2_2 <- felm( policepercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
+
+# Column 3
+fin_seg_sub <- fin_seg %>%
+  filter(totaltractsf > 1 | is.na(totaltractsf), parkspercapNC_cpi != 0) %>%
+  mutate(medinc_cpi = medinc_cpi/1000)
+
+# This is again the same regression, but this time the dependent variable is
+# parks per capita, CPI adjusted with no cap extend. This essentially examines
+# the effect of segregation on the specific public good of parks.
+
+felm2_3 <- felm(parkspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
+
+# Column 4
+
+# This is again the same regression, but this time the dependent variable is
+# sewers per capita, CPI adjusted with no cap extend. This essentially examines
+# the effect of segregation on the specific public good of sewers.
+
+fin_seg_sub <- fin_seg %>%
+  filter(totaltractsf > 1 | is.na(totaltractsf), sewerspercapNC_cpi != 0) %>%
+  mutate(medinc_cpi = medinc_cpi/1000)
+
+felm2_4 <- felm(sewerspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
+
+# Column 5
+
+# This is again the same regression, but this time the dependent variable is
+# Welfare, Health, Housing per capita, CPI adjusted, no cap expend. This
+# essentially examines the effect of segregation on the specific public good of
+# welfare and housing.
+
+fin_seg_sub <- fin_seg %>%
+  filter(totaltractsf > 1 | is.na(totaltractsf), welfhoushealthNC_cpi != 0) %>%
+  mutate(medinc_cpi = medinc_cpi/1000)
+
+felm2_5 <- felm(welfhoushealthNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
+
+# Column 6
+
+# This is again the same regression, but this time the dependent variable is own
+# source of general revenue per capita, CPI adjusted. This essentially examines
+# the effect of segregation on the specific public good of own source revenue.
+
+fin_seg_sub <- fin_seg %>%
+  filter(totaltractsf > 1 | is.na(totaltractsf), genrevownpercap_cpi != 0) %>%
+  mutate(medinc_cpi = medinc_cpi/1000)
+
+felm2_6 <- felm(genrevownpercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
+
+```
+
+```{r iv_regs, include = FALSE}
+
+## regression 1 Table 5
+
+# Top Row
+
+# Column 1
+
+# This is an instrumental variable regression with DGE per capita, adjusted by the CPI, as the dependent variable and total number of waterways as the instrumental variable for segregation.
+The instrument includes the log of the population in the first stage because the number of waterways is positively correlated to population and population is positively correlated with segregation.
+The control variables are the same as those in the regressions for Table 2 except for 2 changes: since the number of waterways does not change, there is no need for city fixed effects.
+Instead, we include fixed effects for the region and year.
+A lagged version of the dependent variable (dgepercap_cpilag) is added to the regressions to account for the high correlation between  observations for the same city over time and because changes in local budgets typically are incremental (NOTE: why exactly do we do this/why does it help/why not do it in the non-intstrumental regressions?).
+
+fin_seg_1 <- fin_seg %>%
+  filter(dgepercap_cpi != 0) %>%
+  mutate(medincinterp = medincinterp/1000)
+
+glimpse(fin_seg_1$medincinterp)
+
+# good explanation: http://eclr.humanities.manchester.ac.uk/index.php/IV_in_R
+
+# iv = ivreg(second stage regression | instrument1 + instrument2 )
+
+ivreg1 <- ivreg(dgepercap_cpi ~ H_citytract_NHW_i + dgepercap_cpilag + diversityinterp +
+                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
+                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
+                  pctcollegegradinterp + northeast + south + midwest + y5 + 
+                  y6 + y7 + y8 + y9 | total_rivs_all + 
+                  logpop + dgepercap_cpilag + diversityinterp + pctblkpopinterp + 
+                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
+                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
+                  pctcollegegradinterp + northeast + south + 
+                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_1)
+
+# Column 2
+
+# this is the same regression as for column 1 but now we use the dependent variable highwayspercapNC_cpi to assess the effect of the instrumental  variable on highways per capita *
+
+fin_seg_2 <- fin_seg %>%
+  filter(highwayspercapNC_cpi != 0) %>%
+  mutate(medincinterp = medincinterp/1000)
+
+ivreg2 <- ivreg(highwayspercapNC_cpi ~ H_citytract_NHW_i + highwayspercapNC_cpilag + diversityinterp +
+                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
+                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
+                  pctcollegegradinterp + northeast + south + midwest + y5 + 
+                  y6 + y7 + y8 + y9 | total_rivs_all + 
+                  logpop + highwayspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
+                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
+                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
+                  pctcollegegradinterp + northeast + south + 
+                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_2)
+
+# Column 3
+
+# this is the same regression as for column 1 but now we use the dependent variable policepercapNC_cpi to assess the effect of the instrumental variable on police per capita
+
+fin_seg_3 <- fin_seg %>%
+  filter(policepercapNC_cpi != 0) %>%
+  mutate(medincinterp = medincinterp/1000)
+
+ivreg3 <- ivreg(policepercapNC_cpi ~ H_citytract_NHW_i + policepercapNC_cpilag + diversityinterp +
+                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
+                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
+                  pctcollegegradinterp + northeast + south + midwest + y5 + 
+                  y6 + y7 + y8 + y9 | total_rivs_all + 
+                  logpop + policepercapNC_cpilag + diversityinterp + pctblkpopinterp + 
+                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
+                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
+                  pctcollegegradinterp + northeast + south + 
+                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_3)
+
+# Column 4 this is the same regression as for column 1 but now we use the
+# dependent variable parkspercapNC_cpi to assess the effect of the instrumental
+# variable on parks per capita
+
+fin_seg_4 <- fin_seg %>%
+  filter(parkspercapNC_cpi != 0) %>%
+  mutate(medincinterp = medincinterp/1000)
+
+ivreg4 <- ivreg(parkspercapNC_cpi ~ H_citytract_NHW_i + parkspercapNC_cpilag + diversityinterp +
+                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
+                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
+                  pctcollegegradinterp + northeast + south + midwest + y5 + 
+                  y6 + y7 + y8 + y9 | total_rivs_all + 
+                  logpop + parkspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
+                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
+                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
+                  pctcollegegradinterp + northeast + south + 
+                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_4)
+
+# Bottom Row
+
+# Column 1
+
+# this is the same regression as for column 1 but now we use the dependent
+# variable sewerspercapNC_cpi to assess the effect of the instrumental variable
+# on sewers per capita
+
+fin_seg_5 <- fin_seg %>%
+  filter(sewerspercapNC_cpi != 0) %>%
+  mutate(medincinterp = medincinterp/1000)
+
+ivreg5 <- ivreg(sewerspercapNC_cpi ~ H_citytract_NHW_i + sewerspercapNC_cpilag + diversityinterp +
+                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
+                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
+                  pctcollegegradinterp + northeast + south + midwest + y5 + 
+                  y6 + y7 + y8 + y9 | total_rivs_all + 
+                  logpop + sewerspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
+                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
+                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
+                  pctcollegegradinterp + northeast + south + 
+                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_5)
+
+# Column 3
+
+# this is the same regression as for column 1 but now we use the dependent variable genrevownpercap_cpi to assess the effect of the instrumental variable on own source revenue per capita
+
+fin_seg_6 <- fin_seg %>%
+  filter(genrevownpercap_cpi != 0) %>%
+  mutate(medincinterp = medincinterp/1000)
+
+ivreg6 <- ivreg(genrevownpercap_cpi ~ H_citytract_NHW_i + genrevownpercap_cpilag + diversityinterp +
+                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
+                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
+                  pctcollegegradinterp + northeast + south + midwest + y5 + 
+                  y6 + y7 + y8 + y9 | total_rivs_all + 
+                  logpop + genrevownpercap_cpilag + diversityinterp + pctblkpopinterp + 
+                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
+                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
+                  pctcollegegradinterp + northeast + south + 
+                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_6)
+
+# Column 2
+
+# this is the same regression as for column 1 but now we use the dependent
+# variable welfhoushealthNC_cpi to assess the effect of the instrumental
+# variable on welfare per capita
+
+fin_seg_7 <- fin_seg %>%
+  filter(welfhoushealthNC_cpi != 0) %>%
+  mutate(medincinterp = medincinterp/1000)
+
+ivreg7 <- ivreg(welfhoushealthNC_cpi ~ H_citytract_NHW_i + welfhoushealthNC_cpilag  + diversityinterp +
+                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
+                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
+                  pctcollegegradinterp + northeast + south + midwest + y5 + 
+                  y6 + y7 + y8 + y9 | total_rivs_all + 
+                  logpop + welfhoushealthNC_cpilag + diversityinterp + pctblkpopinterp + 
+                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
+                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
+                  pctcollegegradinterp + northeast + south + 
+                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_7)
+
+summary(ivreg7)
+
+```
+
+# Bibliography

### 2020-04-30 stargazer_reprex.Rmd
changes to appendix and tables

---
title: "Title"
author: "Author"
output: 
  pdf_document:
    fig_caption: yes
    extra_dependencies: ["rotating"]
header_includes:
  \usepackage{float}
  \usepackage{dcolumn}
  \usepackage{rotating}
  \restylefloat{table}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center", fig.position = "!H")
library(tidyverse)
library(stargazer)
library(reprex)
```

```{r results = "asis", echo = FALSE}

library(tidyverse)
library(stargazer)

output <- lm(mpg ~ cyl + disp + wt, data = mtcars)
output2 <- lm(mpg ~ cyl + disp + wt + drat, data = mtcars)

t1 <- stargazer(output, output2, 
                header = FALSE,
                title = "\\textbf{Practice Table}",
                notes = "Notes Could Go Here???????????? This is an example. Notes Could Go Here???????????? This is an example. Notes Could Go Here???????????? This is an example. Notes Could Go Here???????????? This is an example. ",
                notes.align = "l",
                float = FALSE,
                table.placement = "H")

```

### 2020-04-30 Final_Draft.Rmd
figuring out table placement

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, fig.align = "center", fig.pos = "!H")
+knitr::opts_chunk$set(echo = TRUE, fig.align = "center")
 knitr::write_bib(c("knitr", "stringr"), "bib.bib", width = 60)
@@
 library(VIM)
+library(kableExtra)
 ```
@@
 
+```{r rp_missing_plot, echo = FALSE, warning = FALSE}
+
+# don't show the warning, it's just an irrelevant column missing a name
+
+# plot the missing variables if desired
+
+rp_facet <- rp_impute %>%
+   select("medincinterp",
+             "biggestsplit", "diversityinterp",
+             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
+             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
+               "south", "midwest", "west", "whiteideology_fill2", "year")
+
+gg_miss_var(rp_impute, show_pct = TRUE) +
+  ggtitle("% Missing Values in Trounstine (2016)'s Racial\nPolarization Dataset") +
+  labs(caption = ",jweh,rbguywaflkwanejkfhbwa,keifjlqwibfkjqwhbsfjkhwbsdwhqefhgwef") +
+  theme(plot.caption = element_text(hjust = 0))
+
+nrow(rp_impute)
+
+```
+
+```{r rp_aggr_plot, echo = FALSE, fig.cap = "This plot examines the pattern of missing data in the the original racial polarization dataset from Trounstine (2016).
+The plot on the left shows the percentage of missing data for each variable with missing data and reveals that the variables that are missing by far the most data are the largest vote split along racial lines (biggestsplit) and the variable indicating whether or not the election had candidates of more than one race (biracial).
+The plot on the right shows the pattern of missingness among the variables.
+We can see that approximately 42% of observations are complete (have no missing values).
+There seems to be a correspondence between missing a value for biggest split and missing biracial.
+There also seem to be about 2% of values for which most of the variables are missing.
+However, most observations are not missing more than 2-3 values."}
+
+# select only the missing values
+
+rp_aggr <- rp_impute %>%
+   select("biggestsplit", "biracial", "whiteideology_fill2", "medincinterp",
+            "diversityinterp",
+             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
+             "pctrentersinterp", "pctcollegegradinterp", "nonpartisan",
+               "south", "midwest", "west")
+
+# create an aggr plot for the missing values
+par(oma=c(0,0,3,0))
+par(omi=c(1,1,1,1))
+aggr(rp_aggr, bars = TRUE, combined = T, col=c('navyblue','red'), numbers=TRUE, cex.axis=.5, gap=1, ylab=c("Proporiton of Missing Values","Combinations"))
+title(main = "Patterns of Missingness in the Financial Segregation Data",
+      sub = "", line = 2)
+
+# caption for this plot when I figure out how to do it...
+: This plot examines the pattern of missing data in the the original racial polarization dataset from Trounstine (2016).
+The plot on the left shows the percentage of missing data for each variable with missing data and reveals that the variables that are missing by far the most data are the largest vote split along racial lines (biggestsplit) and the variable indicating whether or not the election had candidates of more than one race (biracial).
+The plot on the right shows the pattern of missingness among the variables.
+We can see that approximately 42% of observations are complete (have no missing values).
+There seems to be a correspondence between missing a value for biggest split and missing biracial.
+There also seem to be about 2% of values for which most of the variables are missing.
+However, most observations are not missing more than 2-3 values.
+
+```
+
+```{r eval = FALSE}
+row.plot <- rp_impute %>%
+  select(-year.f) %>%
+  mutate(id = row_number()) %>%
+  gather(-id, key = "key", value = "val") %>%
+  mutate(isna = is.na(val)) %>%
+  ggplot(aes(key, id, fill = isna)) +
+    geom_raster(alpha=0.8) +
+    scale_fill_manual(name = "",
+        values = c('blue', 'red'),
+        labels = c("Present", "Missing")) +
+    #scale_x_discrete(limits = levels) +
+    labs(x = "Variable",
+           y = "Observation Number", 
+         title = "Missing values in rows") +
+    coord_flip() +
+  theme_bw()
+
+row.plot
+
+glimpse(rp_impute)
+```
+
+```{r eval = FALSE}
+
+# select all variables with missing values for the aggr plot
+
+row.plot <- fin_imp %>%
+  mutate(id = row_number()) %>%
+  gather(-id, key = "key", value = "val") %>%
+  mutate(isna = is.na(val)) %>%
+  ggplot(aes(key, id, fill = isna)) +
+    geom_raster(alpha=0.8) +
+    scale_fill_manual(name = "",
+        values = c('blue', 'red'),
+        labels = c("Present", "Missing")) +
+    #scale_x_discrete(limits = levels) +
+    labs(x = "Variable",
+           y = "Observation Number", 
+         title = "Missing values in rows") +
+    coord_flip() +
+  theme_bw()
+
+row.plot
+
+```
+
 # Appendix
@@
 The original table is displayed for comparison as Figure 1.)",
+                table.placement = "H",
                 notes.align = "l")
@@
                     header = FALSE,
-                    title = "\textbf{Effect of Segregation on Overall per Capita City Expenditures}",
-                    covariate.labels = c("White/Nonwhite H Index", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Change Percent Black", "Change Percent Latino", "Change Percent Asian", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Population (logged)", "White Ideology", "Constant"))
+                    title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures}",
+                    covariate.labels = c("White/Nonwhite H Index", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Change Percent Black", "Change Percent Latino", "Change Percent Asian", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Population (logged)", "White Ideology", "Constant"),
+                    table.placement = "H")
 

### 2020-05-01 Final_Draft.Rmd
changes to aggr plot format

@@
 There also seem to be about 2% of values for which most of the variables are missing.
-However, most observations are not missing more than 2-3 values."}
+However, most observations are not missing more than 2-3 values.", fig.width= 6, fig.height = 5}
 
@@
 # create an aggr plot for the missing values
-par(oma=c(0,0,3,0))
-par(omi=c(1,1,1,1))
 aggr(rp_aggr, bars = TRUE, combined = T, col=c('navyblue','red'), numbers=TRUE, cex.axis=.5, gap=1, ylab=c("Proporiton of Missing Values","Combinations"))
 title(main = "Patterns of Missingness in the Financial Segregation Data",
-      sub = "", line = 2)
+      sub = "", line = 3, oma = c(1,3,5,1))
 

### 2020-05-01 Draft_1.Rmd
formatting to aggr plots

@@
 aggr(rp_aggr, bars = TRUE, col=c('navyblue','red'), numbers=TRUE, cex.axis=.5, gap=1, ylab=c("Proporiton of Missing Values","Combinations"))
+title(main = "Patterns of Missingness in the Racial Polarization Data",
+      sub = "", font.main = 1, font.axis = 1, cex.main = .75)
 
@@
 
+```{r eval = FALSE}
+row.plot <- rp_impute %>%
+  select(-year.f) %>%
+  mutate(id = row_number()) %>%
+  gather(-id, key = "key", value = "val") %>%
+  mutate(isna = is.na(val)) %>%
+  ggplot(aes(key, id, fill = isna)) +
+    geom_raster(alpha=0.8) +
+    scale_fill_manual(name = "",
+        values = c('blue', 'red'),
+        labels = c("Present", "Missing")) +
+    #scale_x_discrete(limits = levels) +
+    labs(x = "Variable",
+           y = "Observation Number", 
+         title = "Missing values in rows") +
+    coord_flip() +
+  theme_bw()
+
+row.plot
+
+glimpse(rp_impute)
+```
+
+```{r eval = FALSE}
+
+# select all variables with missing values for the aggr plot
+
+row.plot <- fin_imp %>%
+  mutate(id = row_number()) %>%
+  gather(-id, key = "key", value = "val") %>%
+  mutate(isna = is.na(val)) %>%
+  ggplot(aes(key, id, fill = isna)) +
+    geom_raster(alpha=0.8) +
+    scale_fill_manual(name = "",
+        values = c('blue', 'red'),
+        labels = c("Present", "Missing")) +
+    #scale_x_discrete(limits = levels) +
+    labs(x = "Variable",
+           y = "Observation Number", 
+         title = "Missing values in rows") +
+    coord_flip() +
+  theme_bw()
+
+row.plot
+
+```
+
 In figure X2, we can similarly observe the trends for the financial segregation dataset.
@@
 
-```{r fin_missing_plot, include = FALSE}
-
-miss_var_summary(fin_imp)
-
-gg_miss_var(fin_imp, show_pct = TRUE)
-
-```
-
 ```{r fin_aggr_plot, echo = FALSE}
@@
 title(main = "Patterns of Missingness in the Financial Segregation Data",
-      sub = "")
+      sub = "", font.main = 1, font.axis = 1, cex.main = .75)
 

### 2020-05-01 Final_Draft.Rmd
formatting to aggr plots

--- 2020-04-30 Final_Draft.Rmd
@@
   pdf_document:
-    fig_caption: yes
+    fig_caption: true
 bibliography: final_proj_bib.bib
@@
 link_citations: true
-keep_tex: yes
 header_includes: \usepackage{float}
@@
 
-```{r rp_missing_plot, echo = FALSE, warning = FALSE}
-
-# don't show the warning, it's just an irrelevant column missing a name
-
-# plot the missing variables if desired
-
-rp_facet <- rp_impute %>%
-   select("medincinterp",
-             "biggestsplit", "diversityinterp",
-             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
-             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
-               "south", "midwest", "west", "whiteideology_fill2", "year")
-
-gg_miss_var(rp_impute, show_pct = TRUE) +
-  ggtitle("% Missing Values in Trounstine (2016)'s Racial\nPolarization Dataset") +
-  labs(caption = ",jweh,rbguywaflkwanejkfhbwa,keifjlqwibfkjqwhbsfjkhwbsdwhqefhgwef") +
-  theme(plot.caption = element_text(hjust = 0))
-
-nrow(rp_impute)
-
-```
-
 ```{r rp_aggr_plot, echo = FALSE, fig.cap = "This plot examines the pattern of missing data in the the original racial polarization dataset from Trounstine (2016).
@@
 The plot on the right shows the pattern of missingness among the variables.
-We can see that approximately 42% of observations are complete (have no missing values).
+We can see that approximately 42\\% of observations are complete (have no missing values).
 There seems to be a correspondence between missing a value for biggest split and missing biracial.
-There also seem to be about 2% of values for which most of the variables are missing.
-However, most observations are not missing more than 2-3 values."}
+There also seem to be about 2\\% of values for which most of the variables are missing.
+However, most observations are not missing more than 2-3 values.", fig.width= 6, fig.height = 5, warning = F, fig.pos="H"}
 
@@
 # create an aggr plot for the missing values
-par(oma=c(0,0,3,0))
-par(omi=c(1,1,1,1))
-aggr(rp_aggr, bars = TRUE, combined = T, col=c('navyblue','red'), numbers=TRUE, cex.axis=.5, gap=1, ylab=c("Proporiton of Missing Values","Combinations"))
+par(font = 1)
+aggr(rp_aggr, bars = TRUE,  col=c('navyblue','red'), numbers=TRUE, cex.axis=.5, gap=1, ylab=c("Proporiton of Missing Values","Combinations"))
 title(main = "Patterns of Missingness in the Financial Segregation Data",
-      sub = "", line = 2)
-
-# caption for this plot when I figure out how to do it...
-: This plot examines the pattern of missing data in the the original racial polarization dataset from Trounstine (2016).
-The plot on the left shows the percentage of missing data for each variable with missing data and reveals that the variables that are missing by far the most data are the largest vote split along racial lines (biggestsplit) and the variable indicating whether or not the election had candidates of more than one race (biracial).
-The plot on the right shows the pattern of missingness among the variables.
-We can see that approximately 42% of observations are complete (have no missing values).
-There seems to be a correspondence between missing a value for biggest split and missing biracial.
-There also seem to be about 2% of values for which most of the variables are missing.
-However, most observations are not missing more than 2-3 values.
+      sub = "", line = 3, oma = c(1,3,5,1), cex.axis = .5, font.main = 1, font.axis = 1, cex.main = 1, cex.lab = .75)
 
@@
 
-```{r eval = FALSE}
-row.plot <- rp_impute %>%
-  select(-year.f) %>%
-  mutate(id = row_number()) %>%
-  gather(-id, key = "key", value = "val") %>%
-  mutate(isna = is.na(val)) %>%
-  ggplot(aes(key, id, fill = isna)) +
-    geom_raster(alpha=0.8) +
-    scale_fill_manual(name = "",
-        values = c('blue', 'red'),
-        labels = c("Present", "Missing")) +
-    #scale_x_discrete(limits = levels) +
-    labs(x = "Variable",
-           y = "Observation Number", 
-         title = "Missing values in rows") +
-    coord_flip() +
-  theme_bw()
+In figure X2, we can similarly observe the trends for the financial segregation dataset.
+In this dataset, there is a very high proportion of missing variables for a number of variables.
+For example, there are `r sum(is.na(fin_imp$H_citytract_NHW_i))` missing values for the segregation index, which is the main independent variable, or %`r round(sum(is.na(fin_imp$H_citytract_NHW_i))/nrow(fin_imp)*100,2)` of the data.
+In this dataset, there are also many more observations for which values are missing for multiple variables in comparison to the racial polarization dataset.
+In total, a mere %`r .0058*100` of observations are complete for all variables included in the main specification for the financial segregaion dataset.
 
-row.plot
-
-glimpse(rp_impute)
-```
-
-```{r eval = FALSE}
+```{r fin_aggr_plot, echo = FALSE, fig.cap = "This plot examines the pattern of missing data in the the original financial segregation dataset from Trounstine (2016).
+The plot on the left shows the percentage of missing data for each variable with missing data and reveals that a large number of variables are missing the vast majority of data.
+The plot on the right shows the pattern of missingness among the variables.
+We can see that only .58\\% of observations are complete (have no missing values), and a large majority of the observations are missing data for many variables.", fig.width= 6, fig.height = 5, fig.pos="H"}
 
@@
 
-row.plot <- fin_imp %>%
-  mutate(id = row_number()) %>%
-  gather(-id, key = "key", value = "val") %>%
-  mutate(isna = is.na(val)) %>%
-  ggplot(aes(key, id, fill = isna)) +
-    geom_raster(alpha=0.8) +
-    scale_fill_manual(name = "",
-        values = c('blue', 'red'),
-        labels = c("Present", "Missing")) +
-    #scale_x_discrete(limits = levels) +
-    labs(x = "Variable",
-           y = "Observation Number", 
-         title = "Missing values in rows") +
-    coord_flip() +
-  theme_bw()
+fin_imp_aggr <- fin_imp %>%
+  select(ideology_fill, H_citytract_NHW_i, chng5pctblk, chng5pctlatino, 
+         chng5pctasian, diversityinterp, pctblkpopinterp, pctasianpopinterp,
+         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp,
+         pctover65, pctcollegegradinterp)
 
-row.plot
+new_try <- head(fin_imp_aggr, 20)
+
+# create the aggr plot
+
+aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.5, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
+title(main = "Patterns of Missingness in the Financial Segregation Data",
+      sub = "", font.main = 1, font.axis = 1, cex.main = 1, line = 3,  oma = c(1,3,5,1), font.main = 1, font.axis = 1)
+
+# this plot tells us that only .58% of the data are complete (not missing anything)
 
 ```
+
+Because neither dataset seems to exhibit any clear patterns in the missing, data, it makes sense to proceed with the imputation.
+For the racial polarization dataset, I performed multiple imputations with 20 iterations using mice, while for the financial segregation dataset, I performed only 5 iterations due to the large size of the dataset and computing limitaitons.
+A non-stochastic imputation method, Classification and Regression Trees (CART), was used instead of the default for the imputation for both datasets because of an error with matrix inversion caused by the data that prevented the use of the default method, predictive mean matching.
+For the racial polarization dataset, I included all of the variables used in the analysis associated with the dataset and was able to impute all missing values.
+For the financial segregation dataset, however, I only imputed values for the main independent variable, the segregation index, and a few other variables, although all variables used in the analysis were included in the data subset input into the mice function.
+More of the data could not be imputed from the financial segregation dataset due to computing and time constraints for this project given the dataset's large size and high proportion of missing values.
 

### 2020-05-01 draft_v_4_30.Rmd
finalization of aggr plots

--- 2020-05-01 Final_Draft.Rmd
@@
              "pctrentersinterp", "pctcollegegradinterp", "nonpartisan",
-               "south", "midwest", "west")
+               "south", "midwest", "west") %>%
+  rename("Racial Divide" = biggestsplit, "Biracial Contest" = biracial, 
+         "White Ideology" = whiteideology_fill2, "Median HH Income" = medincinterp,
+         "Diversity" = diversityinterp, "% Asian" = pctasianpopinterp, 
+         "% Black" = pctblkpopinterp, "% Latino" = pctlatinopopinterp,
+         "% Renters" = pctrentersinterp, "% College Grads" = pctcollegegradinterp,
+         "Nonpartisan Elect." = nonpartisan, "South" = south, "Midwest" = midwest,
+         "West" = "west")
 
@@
 The plot on the right shows the pattern of missingness among the variables.
-We can see that only .58\\% of observations are complete (have no missing values), and a large majority of the observations are missing data for many variables.", fig.width= 6, fig.height = 5, fig.pos="H"}
+We can see that only .58\\% of observations are complete (have no missing values), and a large majority of the observations are missing data for many variables.", fig.width= 7, fig.height = 5, fig.pos="H"}
 
@@
          pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp,
-         pctover65, pctcollegegradinterp)
+         pctover65, pctcollegegradinterp) %>%
+    rename("White Ideology" = ideology_fill, "White/Non-White H Index" = H_citytract_NHW_i,
+           "5Y Change % Black" = chng5pctblk, "5Y Change % Latino" = chng5pctlatino, 
+           "5Y Change % Asian" = chng5pctasian, "Diversity" = diversityinterp, 
+           "% Asian" = pctasianpopinterp, "% Black" = pctblkpopinterp, 
+           "% Latino" = pctlatinopopinterp, "Median HH Income" = medinc_cpi,
+           "% Local Gov. Worker" = pctlocalgovworker_100, "% Renters" = pctrentersinterp, 
+           "% College Grads" = pctcollegegradinterp, "% 65+" = pctover65)
 
@@
 
-aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.5, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
+aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.4, gap=2, ylab=c("Proporiton of Missing Values","Combinations"), srt = 45)
 title(main = "Patterns of Missingness in the Financial Segregation Data",
-      sub = "", font.main = 1, font.axis = 1, cex.main = 1, line = 3,  oma = c(1,3,5,1), font.main = 1, font.axis = 1)
-
+      sub = "", font.main = 1, font.axis = 1, cex.main = 1, line = 3,  oma = c(1,3,5,1), font.main = 1, font.axis = 1, srt = 45)
 # this plot tells us that only .58% of the data are complete (not missing anything)

### 2020-05-02 Final Draft.Rmd
table 1 formatting

--- 2020-05-01 draft_v_4_30.Rmd
@@
 link_citations: true
-header_includes: \usepackage{float}
+header_includes: 
+  \usepackage{float}
+  \usepackage{multirow}
 
@@
 
+\newpage
+
 ```{r setup, include=FALSE}
@@
 library(haven)
-library(gtable)
 library(stargazer)
 library(tidyverse)
-library(gt)
 library(gtsummary)
 library(knitr)
+library(AER)
 library(lme4)
 library(margins)
-library(reprex)
-library(plm)
-library(devtools)
 library(lfe)
-library(Statamarkdown)
 library(readxl)
-library(starpolishr)
-library(AER)
-library(readxl)
-library(naniar)
 library(mice)
-library(gtsummary)
 library(VIM)
@@
 
-aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.4, gap=2, ylab=c("Proporiton of Missing Values","Combinations"), srt = 45)
+aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.4, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
 title(main = "Patterns of Missingness in the Financial Segregation Data",
-      sub = "", font.main = 1, font.axis = 1, cex.main = 1, line = 3,  oma = c(1,3,5,1), font.main = 1, font.axis = 1, srt = 45)
+      sub = "", font.main = 1, font.axis = 1, cex.main = 1, line = 3,  oma = c(1,3,5,1), font.main = 1, font.axis = 1)
 # this plot tells us that only .58% of the data are complete (not missing anything)
@@
 
-```{r results="asis", echo = FALSE, fig.cap= "THIS IS A CAPTION IS IT WORKING WHAT IS GOING ON!"}
+```{r results="asis", echo = FALSE}
 
@@
                 header = FALSE,
+                style = "apsr",
                 title = "\\textbf{Racial Polarization in Segregated Cities}",
-                single.row = TRUE,
-                no.space = FALSE,
+                single.row = FALSE,
+                no.space = F,
                 keep.stat = c("n"),
                 covariate.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Diversity", "Percent Asian", "Percent Black", "Percent Latino", "Medain HH Income (1000s)", "Percent Renters", "Percent College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology", "Constant"),
-                dep.var.labels = c("Racial Divide"),
+                dep.var.labels = c("\\textbf{\\underline{Racial Divide with:    }}"),
                 column.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Ideology Controls"),
-                notes = "This table displays the results of the replication\neffort of the analyses conducted in Trounstine (2016) using the racial polarization dataset.\nThe replication code can be found on my personal Github repository, which is linked in the introduction.
-The original table is displayed for comparison as Figure 1.)",
+                notes = c("Table 1: This table displays the results of the replication effort of the analyses conducted in Trounstine (2016)", 
+                          "using the racial polarization dataset. The replication code can be found on my personal Github repository, which is",
+                          " linked in the introduction. The original table is displayed for comparison as Figure 3."),
                 table.placement = "H",
-                notes.align = "l")
+                notes.align = "l",
+                #column.sep.width = "-10pt",
+                font.size = "small")
 
-# note: "This table displays the results of the replication effort of the analyses conducted in Trounstine (2016) using the racial polarization dataset.
-The replication code can be found on my personal [Github repository](https://github.com/mburzillo/new_final_project).
-The original table is displayed for comparison as Figure 1.")
+#c("\\textbf{Table 1:} This table displays the results of the replication effort",
+#                          "of the analyses conducted in Trounstine (2016) using the racial",
+#                          "polarization dataset. The replication code can be found on my
+#                          personal", "Github repository, which is linked in the introduction.",
+#                          "The original table is displayed for comparison as Figure 3.")
 

### 2020-05-02 stargazer_reprex.Rmd
table 1 formatting

@@
 output: 
-  pdf_document:
+  bookdown::pdf_document2:
     fig_caption: yes
@@
 library(reprex)
+library(kableExtra)
+library(huxtable)
 ```
 
-```{r results = "asis", echo = FALSE}
+# Simple Plot
+
+```{r fig.cap= "this is a caption", echo = FALSE}
+mtcars %>%
+  ggplot(aes(x = disp, y = mpg )) +
+  geom_point()
+
+```
+
+# Stargazer
+
+```{r results = "asis", echo = FALSE, fig.cap= "this is my captions"}
 
@@
                 title = "\\textbf{Practice Table}",
-                notes = "Notes Could Go Here????????????
+                notes = c("Notes Could Go Here????????????", "This is an example.
+Notes Could Go Here????????????
+This is an example.", "Notes Could Go Here????????????
+This is an example.", "Notes Could Go Here????????????
 This is an example.
-Notes Could Go Here????????????
-This is an example.
-Notes Could Go Here????????????
-This is an example.
-Notes Could Go Here????????????
-This is an example.
-",
+"),
                 notes.align = "l",
+                notes.append = F,
                 float = FALSE,
+                style = "apsr",
                 table.placement = "H")
@@
 ```
+
+```{r fig.cap="this is my caption", echo = FALSE, warning=FALSE}
+huxreg(output, output2)
+```

### 2020-05-02 Final-Draft.Rmd
edits to tables

--- 2020-04-30 Draft_1.Rmd
@@
   pdf_document:
-    extra_dependencies: ["rotating"]
+    fig_caption: true
 bibliography: final_proj_bib.bib
@@
   \usepackage{float}
-  \usepackage{dcolumn}
-  \usepackage{rotating}
-  \restylefloat{table}
+  \usepackage{multirow}
 
@@
 library(haven)
-library(gtable)
 library(stargazer)
 library(tidyverse)
-library(gt)
 library(gtsummary)
 library(knitr)
-library(stargazer)
+library(AER)
 library(lme4)
 library(margins)
-library(reprex)
-library(plm)
-library(devtools)
 library(lfe)
-library(Statamarkdown)
 library(readxl)
-library(starpolishr)
-library(AER)
-library(readxl)
-library(naniar)
 library(mice)
-library(gtsummary)
 library(VIM)
+library(kableExtra)
 ```
@@
 
-miss_var_summary(fin_imp)
-miss_var_summary(rp_impute)
-
 ```
@@
 
-```{r include = FALSE}
-
-## regression 1 Table 1
-
-# perform a multi-level mixed-effects linear regression of biggest split on the multi-group H index with controls for Herfindahl Diversity Index, % Asian interpolated, % Black interpolated, % Latino interpolated, median household income interpolated, % renters interpolated, percent college grads interpolated, a dummy indicating if there were biracial candidates in the election, a dummy  indicating if the election was nonpartisan, an indicator if the election was a primary, and the log population.
-The regression also includes fixed effects for year and region and random effects for cities (geo_id2).
-Diversity is  included because of the claim that more diverse populations will have more heterogeneous political preferences.
-The other fixed effect control variables are included because they are known to be potentially correlated with segregation.
-winner == 1 requires that there was a winner in the election.
-
-# regression specification. Apply REML = FALSE. The default for lmer() in R is
-# to optimize the restricted (residual) maximum likelihood (REML) whereas in
-# xtmixed in Stata the default is to optimize the log likelihood (which you can
-# do in lmer() in R by setting REML = FALSE), so this will match the STATA code
-
-m1 <- lmer(biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-## regression 2 Table 1
-
-# Perform the same regression as for Column 1 above but this time regress on the two-group calculation of Theil's H interpolated.
-It is unclear where the "diversity" variable is coming from, as the only variable related to diversity in the specificed dataset is diversityinterp.
-This is a problem that will need to be resolved.
-Essentially, this regression just tests an alternate specification to the first in which the segregation index in defined in terms of two-groups rather than multiple.
-
-m2 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-# perform the same regression as for column 2, but now add in a measure of
-# average white political ideology. The point of this is to control for ideology
-# so that the author can separate any effects of segregation from any potential
-# effects of white political ideology. This is important because it is possible
-# that segregation is just a proxy for white conservatism and thus failure to
-# include this variable could lead to ommitted variable bias.
-
-m3 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-```
-
-```{r results="asis", echo = FALSE}
-
-# create a stargazer table of the results
-
-t1 <- stargazer(m1, m2, m3, omit = c("year", "south", "midwest", "west"),
-                header = FALSE,
-                title = "\\textbf{Racial Polarization in Segregated Cities}",
-                single.row = TRUE,
-                no.space = FALSE,
-                add.lines = list(c("Wald Chi Squarred", "a", "b", "c")),
-                omit.stat = c("ll","rsq"),
-                covariate.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Diversity", "Percent Asian", "Percent Black", "Percent Latino", "Medain HH Income (1000s)", "Percent Renters", "Percent College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology", "Constant"),
-                notes = "This table displays...")
-
-# note: "This table displays the results of the replication effort of the analyses conducted in Trounstine (2016) using the racial polarization dataset.
-The replication code can be found on my personal [Github repository](https://github.com/mburzillo/new_final_project).
-The original table is displayed for comparison as Figure 1.")
-
-```
-
-![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016.
-My replication of these results can be found in Table 1 in this paper.](table_1.png)
-
 There was one interesting outcome from my attempt to replicate the original Stata code in R.
@@
 
-```{r rp_missing_plot, include = FALSE, warning = FALSE}
-
-# don't show the warning, it's just an irrelevant column missing a name
-
-# plot the missing variables if desired
-
-rp_facet <- rp_impute %>%
-   select("medincinterp",
-             "biggestsplit", "diversityinterp",
-             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
-             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
-               "south", "midwest", "west", "whiteideology_fill2", "year")
-
-gg_miss_var(rp_impute, show_pct = TRUE) +
-  ggtitle("% Missing Values in Trounstine (2016)'s Racial Polarization Dataset")
-
-nrow(rp_impute)
-
-```
-
-```{r rp_aggr_plot, echo = FALSE}
-
-# select only the missing values
-
-rp_aggr <- rp_impute %>%
-   select("medincinterp",
-             "biggestsplit", "diversityinterp",
-             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
-             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
-               "south", "midwest", "west", "whiteideology_fill2")
-
-# create an aggr plot for the missing values
-
-aggr(rp_aggr, bars = TRUE, col=c('navyblue','red'), numbers=TRUE, cex.axis=.5, gap=1, ylab=c("Proporiton of Missing Values","Combinations"))
-
-# caption for this plot when I figure out how to do it...
-: This plot examines the pattern of missing data in the the original racial polarization dataset from Trounstine (2016).
+```{r rp_aggr_plot, echo = FALSE, fig.cap = "This plot examines the pattern of missing data in the the original racial polarization dataset from Trounstine (2016).
 The plot on the left shows the percentage of missing data for each variable with missing data and reveals that the variables that are missing by far the most data are the largest vote split along racial lines (biggestsplit) and the variable indicating whether or not the election had candidates of more than one race (biracial).
 The plot on the right shows the pattern of missingness among the variables.
-We can see that approximately 42% of observations are complete (have no missing values).
+We can see that approximately 42\\% of observations are complete (have no missing values).
 There seems to be a correspondence between missing a value for biggest split and missing biracial.
-There also seem to be about 2% of values for which most of the variables are missing.
-However, most observations are not missing more than 2-3 values.
+There also seem to be about 2\\% of values for which most of the variables are missing.
+However, most observations are not missing more than 2-3 values.", fig.width= 6, fig.height = 5, warning = F, fig.pos="H"}
+
+# select only the missing values
+
+rp_aggr <- rp_impute %>%
+   select("biggestsplit", "biracial", "whiteideology_fill2", "medincinterp",
+            "diversityinterp",
+             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
+             "pctrentersinterp", "pctcollegegradinterp", "nonpartisan",
+               "south", "midwest", "west") %>%
+  rename("Racial Divide" = biggestsplit, "Biracial Contest" = biracial, 
+         "White Ideology" = whiteideology_fill2, "Median HH Income" = medincinterp,
+         "Diversity" = diversityinterp, "% Asian" = pctasianpopinterp, 
+         "% Black" = pctblkpopinterp, "% Latino" = pctlatinopopinterp,
+         "% Renters" = pctrentersinterp, "% College Grads" = pctcollegegradinterp,
+         "Nonpartisan Elect." = nonpartisan, "South" = south, "Midwest" = midwest,
+         "West" = "west")
+
+# create an aggr plot for the missing values
+par(font = 1)
+aggr(rp_aggr, bars = TRUE,  col=c('navyblue','red'), numbers=TRUE, cex.axis=.5, gap=1, ylab=c("Proporiton of Missing Values","Combinations"))
+title(main = "Patterns of Missingness in the Financial Segregation Data",
+      sub = "", line = 3, oma = c(1,3,5,1), cex.axis = .5, font.main = 1, font.axis = 1, cex.main = 1, cex.lab = .75)
 
@@
 
-```{r fin_missing_plot, include = FALSE}
-
-miss_var_summary(fin_imp)
-
-gg_miss_var(fin_imp, show_pct = TRUE)
-
-```
-
-```{r fin_aggr_plot, echo = FALSE}
-
-# select all variables with missing values for the aggr plot
-
-fin_imp_aggr <- fin_imp %>%
-  select(ideology_fill, H_citytract_NHW_i, chng5pctblk, chng5pctlatino, chng5pctasian,
-         diversityinterp, pctblkpopinterp, pctasianpopinterp,
-         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
-         pctcollegegradinterp)
-
-new_try <- head(fin_imp_aggr, 20)
-
-aggr(new_try, plot = TRUE, bars = FALSE, col=c('navyblue','red'), numbers=TRUE)
-
-# create the aggr plot
-
-aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.5, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
-title(main = "Patterns of Missingness in the Financial Segregation Data",
-      sub = "")
-
-# this plot tells us that only .58% of the data are complete (not missing anything)
-
-# caption for this plot when I figure out how to do it...
-: This plot examines the pattern of missing data in the the original financial segregation dataset from Trounstine (2016).
+```{r fin_aggr_plot, echo = FALSE, fig.cap = "This plot examines the pattern of missing data in the the original financial segregation dataset from Trounstine (2016).
 The plot on the left shows the percentage of missing data for each variable with missing data and reveals that a large number of variables are missing the vast majority of data.
 The plot on the right shows the pattern of missingness among the variables.
-We can see that only .58% of observations are complete (have no missing values), and a large majority of the observations are missing data for many variables.
+We can see that only .58\\% of observations are complete (have no missing values), and a large majority of the observations are missing data for many variables.", fig.width= 7, fig.height = 5, fig.pos="H"}
+
+# select all variables with missing values for the aggr plot
+
+fin_imp_aggr <- fin_imp %>%
+  select(ideology_fill, H_citytract_NHW_i, chng5pctblk, chng5pctlatino, 
+         chng5pctasian, diversityinterp, pctblkpopinterp, pctasianpopinterp,
+         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp,
+         pctover65, pctcollegegradinterp) %>%
+    rename("White Ideology" = ideology_fill, "White/Non-White H Index" = H_citytract_NHW_i,
+           "5Y Change % Black" = chng5pctblk, "5Y Change % Latino" = chng5pctlatino, 
+           "5Y Change % Asian" = chng5pctasian, "Diversity" = diversityinterp, 
+           "% Asian" = pctasianpopinterp, "% Black" = pctblkpopinterp, 
+           "% Latino" = pctlatinopopinterp, "Median HH Income" = medinc_cpi,
+           "% Local Gov. Worker" = pctlocalgovworker_100, "% Renters" = pctrentersinterp, 
+           "% College Grads" = pctcollegegradinterp, "% 65+" = pctover65)
+
+new_try <- head(fin_imp_aggr, 20)
+
+# create the aggr plot
+
+aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.4, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
+title(main = "Patterns of Missingness in the Financial Segregation Data",
+      sub = "", font.main = 1, font.axis = 1, cex.main = 1, line = 3,  oma = c(1,3,5,1), font.main = 1, font.axis = 1)
+# this plot tells us that only .58% of the data are complete (not missing anything)
 
@@
 
+rp_impute_labels <- rp_impute
+
+rp_impute_labels$biggestsplit <- "Racial Divide"
+rp_impute_labels$medincinterp <- "Median HH Income"
+
+#c("Racial Divide" = biggestsplit, "Biracial Contest" = biracial, "White Ideology" = whiteideology_fill2, "Median HH Income" = medincinterp, "Diversity" = diversityinterp, "% Asian" = pctasianpopinterp,  "% Black" = pctblkpopinterp, "% Latino" = pctlatinopopinterp,"% Renters" = pctrentersinterp, "% College Grads" = pctcollegegradinterp, "Nonpartisan Elect." = nonpartisan, "South" = south, "Midwest" = midwest,"West" = "west")
+
 max_it = 20
@@
 
-# can use the line below to check that there are now no missing values
-
-# gg_miss_var(complete(imp_1_rp), show_pct = TRUE)
-
-```
-
-```{r fp_imputations_original, include = FALSE}
+```
+
+```{r fp_imputations_original, eval = FALSE, include = FALSE}
 
@@
 
-imp_fs_all <- mice(fin_imp, method = "cart", maxit = 5)
-
-# now there are manyb fewer missing variables!!!
+# now there are many fewer missing variables!!!
 
@@
 282334 - 222957
-
-```
-
-```{r}
-#now missing 282261
-
-#before impute:
-```
-
-```{r new_imp_less_than_17_nas}
-
-fin_imp <- fin_imp %>%
-  mutate(nas = is.na(H_citytract_NHW_i) + is.na(dgepercap_cpi) + is.na(diversityinterp) + is.na(pctblkpopinterp)  + is.na(pctasianpopinterp) + is.na(pctlatinopopinterp) + is.na(medinc_cpi) + is.na(pctlocalgovworker_100) + is.na(pctrentersinterp) + is.na(pctover65) + is.na(pctcollegegradinterp) + is.na(logpop) + is.na(geo_id2) + is.na(chng5pctblk) + is.na(chng5pctlatino) + is.na(chng5pctasian) + is.na(logpop) + is.na(geo_id2) + is.na(chng5pctblk) + is.na(chng5pctlatino) + is.na(chng5pctasian) + is.na(ideology_fill))
-
-fin_imp %>%
-  ggplot(aes(x = nas)) +
-  geom_histogram()
-
-fin_imp %>%
-  group_by(nas) %>%
-  summarise(n())
-
-# exclude all observations with 17 out of 22 nas
-
-fin_imp_sub <- fin_imp %>%
-  filter(nas < 17)
-
-nrow(fin_imp_sub)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_sub, maxit=0, print=F)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-new_imp_fs <- mice(fin_imp_sub, method = meth, maxit = 5)
-
-miss_var_summary(complete(new_imp_fs))
-
-```
-
-```{r fp_imputations_cities, include = FALSE}
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_cities, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_cities <- mice(fin_imp_cities, method = meth, maxit = 1)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_cities, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r fp_population_full_range}
-
-# what if we condition on population size?
-
-fin_imp_pop_size <- fin_imp %>%
-  filter(logpop > 6 & logpop < 16)
-
-nrow(fin_imp_pop_size)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_size, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_size <- mice(fin_imp_pop_size, method = meth, maxit = 5)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_size, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r 95_pop}
-fin_imp_pop_trounstine_95 <- fin_imp %>%
-  filter(logpop < 11.93437 & logpop > 8.7754)
-
-nrow(fin_imp_pop_trounstine_95)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_trounstine_95, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_size_trounstine_95 <- mice(fin_imp_pop_trounstine_95, method = meth, maxit = 5)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_size_trounstine_95, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r population_first_quartile}
-
-quantile(fin_dge$logpop, c(.25))
-
-quantile(fin_seg$logpop, c(.25), na.rm = T)
-
-fin_imp_pop_trounstine_first_quart <- fin_imp %>%
-  filter(logpop < 9.388152)
-
-nrow(fin_imp_pop_trounstine_first_quart)
-
-gg_miss_var(fin_imp_pop_trounstine_first_quart, show_pct = T)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_trounstine_first_quart, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_size_bottom_25 <- mice(fin_imp_pop_trounstine_first_quart, method = meth, maxit = 5)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_size_bottom_25, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r population_top_90_trounstine}
-
-quantile(fin_dge$logpop, c(.90))
-
-quantile(fin_seg$logpop, c(.90), na.rm = T)
-
-fin_imp_pop_top_90_trounstine <- fin_imp %>%
-  filter(logpop > 11.43575)
-
-fin_seg %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-nrow(fin_imp_pop_top_90_trounstine)
-
-gg_miss_var(fin_imp_pop_top_90_trounstine, show_pct = T)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_top_90_trounstine, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_size_top_90_trounstine <- mice(fin_imp_pop_top_90_trounstine, method = meth, maxit = 5)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_size_top_90_trounstine, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r population_bottom_5_trounstine}
-
-quantile(fin_dge$logpop, c(.05))
-
-quantile(fin_seg$logpop, c(.05), na.rm = T)
-
-fin_imp_pop_bottom_5_trounstine <- fin_imp %>%
-  filter(logpop < 8.775581)
-
-fin_seg %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-nrow(fin_imp_pop_bottom_5_trounstine)
-
-gg_miss_var(fin_imp_pop_bottom_5_trounstine, show_pct = T)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_bottom_5_trounstine, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_size_bottom_5_trounstine <- mice(fin_imp_pop_bottom_5_trounstine, method = meth, maxit = 1)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_size_bottom_5_trounstine, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_pop_size_bottom_5_trounstine))
-
-miss_var_summary(fin_imp_cities)
-
-nrow(complete(imp_fs_pop_size_bottom_5_trounstine))
-
-5039 - 4966
-
-```
-
-```{r population_bottom_1}
-
-quantile(fin_dge$logpop, c(.01))
-
-quantile(fin_seg$logpop, c(.20), na.rm = T)
-
-fin_imp_pop_bottom_1_trounstine <- fin_imp %>%
-  filter(logpop < 8.364976 )
-
-fin_seg %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-nrow(fin_imp_pop_bottom_1_trounstine)
-
-gg_miss_var(fin_imp_pop_bottom_1_trounstine, show_pct = T)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_bottom_1_trounstine, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_size_bottom_1_trounstine <- mice(fin_imp_pop_bottom_1_trounstine, method = meth, maxit = 1)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_size_bottom_1_trounstine, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r population_over_Baqir}
-
-# Baqir et al uses city as population above 25,000
-
-baqir <- log(25000)
-
-fin_imp_pop_over_baqir <- fin_imp %>%
-  filter(logpop > baqir )
-
-nrow(fin_imp_pop_over_baqir)
-
-gg_miss_var(fin_imp_pop_over_baqir, show_pct = T)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_over_baqir, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_overbaqir <- mice(fin_imp_pop_over_baqir, method = meth, maxit = 5)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_overbaqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r population_under_Baqir}
-
-# Baqir et al uses city as population above 25,000
-
-baqir <- log(25000)
-
-fin_imp_pop_under_baqir <- fin_imp %>%
-  filter(logpop < baqir )
-
-nrow(fin_imp_pop_under_baqir)
-
-gg_miss_var(fin_imp_pop_under_baqir, show_pct = T)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_under_baqir, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_under_baqir <- mice(fin_imp_pop_under_baqir, method = meth, maxit = 1)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_under_baqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r population_mid_50}
-
-# essentially the same - let's do full population
-(quantile(fin_seg$logpop, c(.25, .75), na.rm = T))
-(quantile(fin_imp$logpop, c(.25, .75), na.rm = T))
-
-baqir <- log(25000)
-
-fin_imp_pop_mid_50 <- fin_imp %>%
-  filter(logpop > 5.777652 & logpop < 7.936303)
-
-nrow(fin_imp_pop_mid_50)
-
-gg_miss_var(fin_imp_pop_mid_50, show_pct = T)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_mid_50, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_mid_50 <- mice(fin_imp_pop_mid_50, method = meth, maxit = 1)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_mid_50, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r population_top_1_trounstine}
-
-(quantile(fin_seg$logpop, c(.99), na.rm = T))
-(quantile(fin_dge$logpop, c(.99), na.rm = T))
-
-fin_imp_top_1_trounstine <- fin_imp %>%
-  filter(logpop > 13.1907 )
-
-nrow(fin_imp_top_1_trounstine)
-
-gg_miss_var(fin_imp_top_1_trounstine, show_pct = T)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_top_1_trounstine, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_top_1_trounstine <- mice(fin_imp_top_1_trounstine, method = meth, maxit = 5)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_top_1_trounstine, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-nrow(complete(imp_fs_pop_top_1_trounstine))
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
-
-```
-
-```{r population_top_1}
-
-(quantile(fin_seg$logpop, c(.99), na.rm = T))
-(quantile(fin_dge$logpop, c(.99), na.rm = T))
-
-fin_imp_top_1 <- fin_imp %>%
-  filter(logpop > 11.28648)
-
-nrow(fin_imp_top_1)
-
-gg_miss_var(fin_imp_top_1, show_pct = T)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_top_1, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_top_1 <- mice(fin_imp_top_1_trounstine, method = meth, maxit = 5)
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs_pop_top_1, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-# RESULTS ARE ESSENTIALLY THE SAME!
-print(imp_felm1_sum)
-
-nrow(complete(imp_fs_pop_top_1))
-
-# doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_cities))
-
-miss_var_summary(fin_imp_cities)
-
-5039 - 4966
 
@@
 See figures X and X1 to see the density plots of the imputed values overlayed on the density plots of the original variables.
-The rest of the plots and results of the diagnostic tests discussed here are presented in the Appendix.
+The code to generate the rest of the plots and results of the diagnostic tests discussed here are presented in the Appendix.
 
@@
 
-densityplot(imp_1_rp)
-
-```
-
-```{r rp_imp_plot, include = FALSE}
-
-# ideally, the fits will intertwine and not exhibit any trends at later iterations.
-This seems to generally be the case.
-There are some issues with the results for some of the variables with very few missing values, which makes sense as we would expect the mean to be less reliable due to the law of large numbers and thus convergence is more difficult.
-However, since these are so few values, it is less important about how robust they are.
-
-plot(imp_1_rp)
-
-```
-
-```{r rp_stripplot, include = FALSE}
-
-# we can also check the imputed values against the original values using stripplot().
-Each column in each subplot represents a separate iteration.
-The magenta points represent the imputed data.
-The values of the variable in questions are along the y axis.
-We expect the spread of the data to be similar if the imputations were done well.
-If the data were missing completely at random, then the imputed data should have the same distribution as the original data.
-In particular, we want to be sure that the imputations are within a plausible range of the data.
-This is the case for all of our imputed variables, and there does not seem to be cause for alarm from these results.
-
-# this looks good? All reasonable values...
-
-stripplot(imp_1_rp)
-
-stripplot(imp_1_rp, biggestsplit)
-
-```
-
-```{r fs_densityplot, echo = FALSE}
+my.settings <- list(
+  par.main.text = list(font = 1)
+)
+
+densityplot(imp_1_rp, main = "Density Plots of Imputed and Original Data by Variable\nin the Racial Polarization Dataset",
+      par.settings = my.settings,
+      par.strip.text = list(cex = .7))
+
+```
+
+```{r fs_densityplot, echo = FALSE, eval = FALSE}
 
 densityplot(imp_fs)
-densityplot(x=imp_fs , data= ~ H_citytract_NHW_i + chng5pctblk + 
+densityplot(x = imp_fs , data = ~ H_citytract_NHW_i + chng5pctblk + 
        chng5pctlatino + chng5pctasian + ideology_fill)
@@
 
-```{r fs_imp_plot, include = FALSE}
-
-# ideally, the fits will intertwine and not exhibit any trends at later iterations.
-This seems to generally be the case.
-There are some issues with the results for some of the variables with very few missing values, which makes sense as we would expect the mean to be less reliable due to the law of large numbers and thus convergence is more difficult.
-However, since these are so few values, it is less important about how robust they are.
-
-plot(imp_fs)
-
-```
-
-```{r fs_stripplot, include = FALSE}
-
-# we can also check the imputed values against the original values using stripplot().
-Each column in each subplot represents a separate iteration.
-The magenta points represent the imputed data.
-The values of the variable in questions are along the y axis.
-We expect the spread of the data to be similar if the imputations were done well.
-If the data were missing completely at random, then the imputed data should have the same distribution as the original data.
-In particular, we want to be sure that the imputations are within a plausible range of the data.
-This is the case for all of our imputed variables, and there does not seem to be cause for alarm from these results.
-
-# this looks good? All reasonable values...
-
-stripplot(imp_fs, H_citytract_NHW_i)
-
-stripplot(imp_fs, chng5pctblk)
-
-stripplot(imp_fs, chng5pctlatino)
-
-stripplot(imp_fs, chng5pctasian)
-
-stripplot(imp_fs, ideology_fill)
-
-```
-
 Given the promising results of the diagnostic checks, I next proceeded to re-estimate the original model using the multiply imputed datasets, pooling the results to produce final pooled regression coefficients and parameters.
-The results for the analyses using the racial polarization dataset are presented in tables 1-3.
+The results for the analyses using the racial polarization dataset are presented in tables X1-X3.
 
@@
 
-imp_1_rp_sum_table <- as.data.frame(imp_1_rp_sum %>% 
+imp_1_rp_sum_table <- as.data.frame(imp_1_rp_sum) %>% 
   select(term, estimate, std.error, p.value)) %>%
@@
 
-imp_2_rp_sum_table <- as.data.frame(imp_2_rp_sum %>% 
+imp_2_rp_sum_table <- as.data.frame(imp_2_rp_sum) %>% 
   select(term, estimate, std.error, p.value)) %>%
@@
 
-imp_3_rp_sum_table <- as.data.frame(imp_3_rp_sum %>% 
+imp_3_rp_sum_table <- as.data.frame(imp_3_rp_sum) %>% 
   select(term, estimate, std.error, p.value)) %>%
@@
 
-For the financial segregation dataset, we similarly fit each of our 5 imputed datasets to the original models from @trounstine_segregation_2016 using this data and then pool the results for each.
-The pooled results are presented in tables 4-6.
-
-# FS data results
-
-```{r fs_imputed_pooled_regressions, include = FALSE}
-# Main Analysis 2: Imputations
-
-## regression 1 Table 2
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-## regression 2 Table 2
-
-# fit multiple imputed datasets
-
-fit_imp_felm2 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm2 <- pool(fit_imp_felm2)
-imp_felm2_sum <- summary(pool_imp_felm2)
-
-## Regression 3 Table 2
-
-fit_imp_felm3 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm3 <- pool(fit_imp_felm3)
-imp_felm3_sum <- summary(pool_imp_felm3)
-
-print(imp_felm1_sum)
-
-```
-
-```{r fs_imputed_data_included_calc, include = FALSE}
-# how many observations were included in those 3 analyses?
-
-# basic filter for table for all regressions
-
-# xtreg dgepercap_cpi H_citytract_NHW_i diversityinterp pctblkpopinterp
-# pctasianpopinterp pctlatinopopinterp medinc_cpi pctlocalgovworker_100
-# pctrentersinterp pctover65 pctcollegegradinterp logpop if totaltracts>1 &
-# dgepercap_cpi~=0,fe vce(cluster geo_id2)
-
-fin <- complete(imp_fs) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
-
-# create dge variable used in regression
-
-fin_dge <-fin %>% filter(dgepercap_cpi != 0)
-
-# now we have 73,119 observations compared to 13,742. Calculation:
-
-nrow(fin_dge)
-
-# number of missing seg indexes before imputation: 282334
-
-# number missing now: 222957 -> Calculation:
-
-new_missing <- sum(is.na(complete(imp_fs)$H_citytract_NHW_i))
-
-# calculate number of observations we added to the sample: 59,377
-
-num_added <- 282334 - new_missing
-
-# INTERPRETATION BEFORE AFTER CHANGED The results of the first regression present a stark difference to the results of @trounstine_segregation_2016.
-Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant.
-Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
-The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.
-
-```
-
-The results of the first regression present a stark difference to the results of @trounstine_segregation_2016.
-Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant.
-Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
-The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.
-
-The results of the first regression indicate that Trounstine's results are robust to the inclusion of the imputed data, which led to the inclusion of an additional 59,377 observations in the analysis.
-The coefficients, standard errors, and significance levels are essentially unchanged.
-The same is largely true for the second and third specifications, but the magnitude of the coefficient on the segregation decreases slightly.
-
-```{r results_printing_fs_impute_regressions_1, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_felm1_sum_table <- as.data.frame(imp_felm1_sum %>% 
-  select(term, estimate, std.error, p.value))
-print(imp_felm1_sum_table)
-
-stargazer(imp_felm1_sum_table,
+\newpage
+
+# Appendix
+
+```{r  include = FALSE}
+
+## regression 1 Table 1
+
+# perform a multi-level mixed-effects linear regression of biggest split on the multi-group H index with controls for Herfindahl Diversity Index, % Asian interpolated, % Black interpolated, % Latino interpolated, median household income interpolated, % renters interpolated, percent college grads interpolated, a dummy indicating if there were biracial candidates in the election, a dummy  indicating if the election was nonpartisan, an indicator if the election was a primary, and the log population.
+The regression also includes fixed effects for year and region and random effects for cities (geo_id2).
+Diversity is  included because of the claim that more diverse populations will have more heterogeneous political preferences.
+The other fixed effect control variables are included because they are known to be potentially correlated with segregation.
+winner == 1 requires that there was a winner in the election.
+
+# regression specification. Apply REML = FALSE. The default for lmer() in R is
+# to optimize the restricted (residual) maximum likelihood (REML) whereas in
+# xtmixed in Stata the default is to optimize the log likelihood (which you can
+# do in lmer() in R by setting REML = FALSE), so this will match the STATA code
+
+m1 <- lmer(biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
+
+## regression 2 Table 1
+
+# Perform the same regression as for Column 1 above but this time regress on the two-group calculation of Theil's H interpolated.
+It is unclear where the "diversity" variable is coming from, as the only variable related to diversity in the specificed dataset is diversityinterp.
+This is a problem that will need to be resolved.
+Essentially, this regression just tests an alternate specification to the first in which the segregation index in defined in terms of two-groups rather than multiple.
+
+m2 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
+
+# perform the same regression as for column 2, but now add in a measure of
+# average white political ideology. The point of this is to control for ideology
+# so that the author can separate any effects of segregation from any potential
+# effects of white political ideology. This is important because it is possible
+# that segregation is just a proxy for white conservatism and thus failure to
+# include this variable could lead to ommitted variable bias.
+
+m3 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
+
+```
+
+```{r results="asis", echo = FALSE}
+
+# create a stargazer table of the results
+
+t1 <- stargazer(m1, m2, m3, omit = c("year", "south", "midwest", "west"),
                 header = FALSE,
-          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Expenditure per Capita}")
-```
-
-```{r results_printing_fs_impute_regressions_2, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_felm2_sum_table <- as.data.frame(imp_felm2_sum %>% 
-  select(term, estimate, std.error, p.value))
-print(imp_felm2_sum_table)
-
-stargazer(imp_felm1_sum_table,
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Changing Demographics}")
-```
-
-```{r results_printing_fs_impute_regressions_3, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_felm3_sum_table <- as.data.frame(imp_felm3_sum %>% 
-  select(term, estimate, std.error, p.value))
-print(imp_felm3_sum_table)
-
-stargazer(imp_felm1_sum_table,
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Ideology Control}")
-```
-
-# FS NEW data results
-
-```{r new_fs_imputation_tries, include = FALSE}
-# Main Analysis 2: Imputations
-
-## regression 1 Table 2
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-## regression 2 Table 2
-
-# fit multiple imputed datasets
-
-fit_imp_felm2 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm2 <- pool(fit_imp_felm2)
-imp_felm2_sum <- summary(pool_imp_felm2)
-
-## Regression 3 Table 2
-
-fit_imp_felm3 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm3 <- pool(fit_imp_felm3)
-imp_felm3_sum <- summary(pool_imp_felm3)
-
-# INTERPRETATION BEFORE AFTER CHANGED The results of the first regression present a stark difference to the results of @trounstine_segregation_2016.
-Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant.
-Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
-The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.
-
-print(imp_felm1_sum)
-print(imp_felm2_sum)
-print(imp_felm3_sum)
-
-# large amount of data missing across the board in terms of years
-
-gg_miss_var(fin_dge, facet = year, show_pct = TRUE)
-
-# can't really tell anything about the region facet since a lot of obs missing region data
-
-gg_miss_var(fin_imp_extra, facet = region, show_pct = TRUE)
-
-# not necessarily a significant pattern across states either
-
-gg_miss_var(fin_imp_extra, facet = statecode, show_pct = TRUE)
-
-```
-
-# FS NEW AGAIN
-
-```{r}
-cities_to_keep <- c("Austin City", "Baltimore City", "Charlotte City", "Chicago City", "Cleveland City", "Columbus City", "Dallas City", "Denver City", "Detroit City", "Houston City", "Indianapolis", "Jacksonville", "Los Angeles City", "Memphis City", "Milwaukee City", "New York City", "Oklahoma City City", "Philadelphia City", "Phoenix City", "San Antonio City", "San Diego City", "San Francisco City", "San Jose City", "Tucson City", "Washington City")
-
-# apply the conditions in Stata regression to the fin_seg dataset
-
-fin_imp_cities <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0, cityname %in% cities_to_keep) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-# select the relevant variables to be imputed
-
-fin_imp <- fin_imp %>%
-  select(H_citytract_NHW_i, dgepercap_cpi, diversityinterp, pctblkpopinterp, pctasianpopinterp,
-         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
-         pctcollegegradinterp, logpop, geo_id2, chng5pctblk, chng5pctlatino, chng5pctasian,
-         ideology_fill)
-```
-
-```{r looking_at_original_data, include = FALSE}
-
-range(fin_seg$totaltractsf, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_seg %>%
-  ggplot() +
-  geom_histogram(aes(x = totaltractsf))
-
-range(fin_seg$logpop, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_seg %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-# add back in year, region, and statecode to be able to look at this
-
-fin_imp_old <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-fin_imp_extra <- fin_imp %>%
-  mutate(year = fin_imp_old$year,
-         region = fin_imp_old$region,
-         statecode = fin_imp_old$statecode)
-
-# large amount of data missing across the board in terms of years
-
-gg_miss_var(fin_imp_extra, facet = year, show_pct = TRUE)
-
-# can't really tell anything about the region facet since a lot of obs missing region data
-
-gg_miss_var(fin_imp_extra, facet = region, show_pct = TRUE)
-
-# not necessarily a significant pattern across states either
-
-gg_miss_var(fin_imp_extra, facet = statecode, show_pct = TRUE)
-
-```
-
-```{r looking_at_Trounstine_data, include = FALSE}
-
-# basic filter for table for all regressions
-
-# xtreg dgepercap_cpi H_citytract_NHW_i diversityinterp pctblkpopinterp
-# pctasianpopinterp pctlatinopopinterp medinc_cpi pctlocalgovworker_100
-# pctrentersinterp pctover65 pctcollegegradinterp logpop if totaltracts>1 &
-# dgepercap_cpi~=0,fe vce(cluster geo_id2)
-
-fin_trounstine <-fin_seg %>%
-  filter(totaltractsf >1 | is.na(totaltractsf)) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
-
-# create dge variable used in regression
-
-fin_dge_trounstine <-fin_trounstine %>% filter(dgepercap_cpi != 0)
-
-range(fin_dge_trounstine$totaltractsf, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_dge_trounstine %>%
-  ggplot() +
-  geom_histogram(aes(x = totaltractsf))
-
-range(fin_dge_trounstine$logpop, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_dge_trounstine %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-```
-
-```{r looking_at_imputed_data}
-
-fin_new_imp <- complete(new_imp_fs) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
-
-range(fin_new_imp$logpop, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_new_imp %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-```
-
-# Conclusion
-
-Why cities differ in their amount of spending on public goods is an interesting questions that is frequently debated in the literature.
-@trounstine_segregation_2016 posits that segregation may be an important underlying cause of the underprovsion of public goods.
-Finding evidence that residential segregation by race increases political partisanship, @trounstine_segregation_2016 argues that residential segregation can increase division and make cooperation amongst competing groups difficult, which results in decreased spending on public goods.
-The findings of @trounstine_segregation_2016 are particularly important because they suggest that segregation, as defined by many homogeneous neighborhoods within a larger diverse geographical area, is the key factor in disinvestment in public goods.
-This contradicts previous research which has suggested that levels of diversity were instead most important (see for example @baqir_public_1999 or @hopkins_diversity_2009).
-While @trounstine_segregation_2016 still represents relatively new reasearch as of 2020, it has yet to be fully vetted by additional research.
-Furthermore, some research that has been published on the topic since its publication suggests that other factors such as larger inequities in the political system favoring socially powerful groups [@lee_ethnic_2018] or the interaction of income and racial inequality [@an_its_2018] may be more important in explaining public goods provisions.
-
-I first worked to provide a check on the analysis presented in @trounstine_segregation_2016 by attempting to replicate the work in R.
-I was able to successfully replicate all of the main results from @trounstine_segregation_2016, with the exception of a few of a few marginal analyses of the complex, multi-level models which, to my knowledge, are currently not supported by available R packages.
-I was, however, able to successfully replicate these results in Stata.
-
-As an additional robustness check I also tested the models in @trounstine_segregation_2016 by re-running them with additional data that I imputed from missing values in the original datasets.
-The large number of missing values in both of the datasets used in @trounstine_segregation_2016's main analysis created a concern for potential bias in the original results and a lack of representativeness due to the large amount of data excluded from the regression analysis due to missing values.
-Thus, I used the mice package in R to create multiply imputed datasets, upon which I re-ran the models and pooled the results to generate the final model coefficients and parameters.
-
-The results of the data imputation exercise differed between the two datasets.
-For the analyses using the smaller, racial polarization dataset, the results from the imputed data resulted in a smaller magnitude of the coefficient on the main independent variable, and also made it statistically insignificant in the main model specification.
-This suggests that the segregation index may not have as strong of a positive association with political polarization as @trounstine_segregation_2016 suggests.
-However, for the analyses using the much larger financial segregation dataset, the results of the models using the multiply imputed data largely mirrored the results of @trounstine_segregation_2016, and the coefficients and significance levels were essentially the same between the two, with the standard errors on the model estimates being generally slightly lower for the analyses using the imputed data.
-This provides strong support for @trounstine_segregation_2016's finding that residential racial segregation is associated with diminshed spending on public goods.
-
-The replication exercise and robustness check using multiply imputed data here provide strong evidence that residential segregation along racial lines does in fact correlate negatively with spending on a variety of public goods.
-What my analysis calls more into question, is by what mechanism this happens.
-Using the multiply imputed data, I still found some evidence that segregation may be associated with increased political polarization which @trounstine_segregation_2016 suggests may lead to diminished public goods spending; however, the effect size is much smaller than that found in @trounstine_segregation_2016, and some of the results have become insignificant.
-It is possible that other mechanisms may be more important in explaining why segregation might be associated with decreased spending on public goods.
-For example, it could be that there is an important interaction effect between income and segregation, as others have previously suggested, or there could be some other intervening mechanism or a confounding variable that is leading to the negative association between segregation and lower spending on public goods.
-@trounstine_segregation_2016 has identified an important relationship between segregation and the provision of public goods.
-However, my analysis suggests that further research is needed to assess the potential mechanisms by which residential segregation by race or even a confounding variable may result in dimished spending.
-If this mechanism can be better understood, than it will be possible to more effectively understand and address the underprovision of public goods, which may inhibit social mobility and unfairly disadvantage certain groups.
-
-# Appendix
+                style = "apsr",
+                title = "\\textbf{Racial Polarization in Segregated Cities}",
+                single.row = FALSE,
+                no.space = F,
+                covariate.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Diversity", "Percent Asian", "Percent Black", "Percent Latino", "Medain HH Income (1000s)", "Percent Renters", "Percent College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology", "Constant"),
+                dep.var.labels = c("\\textbf{\\underline{Racial Divide with:    }}"),
+                column.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Ideology Controls"),
+                notes = c("Table A1: This table displays the results of the replication effort of the analyses conducted in Trounstine (2016)", 
+                          "using the racial polarization dataset. The replication code can be found on my personal Github repository, which is",
+                          " linked in the introduction. The original table is displayed for comparison as Figure 3."),
+                table.placement = "H",
+                notes.align = "l",
+                #column.sep.width = "-10pt",
+                font.size = "small")
+
+```
+
+![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016.
+My replication of these results can be found in Table A1 in this paper.](table_1.png)
 
@@
                     header = FALSE,
+                    style = "apsr",
                     title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures}",
-                covariate.labels = c("White/Nonwhite H Index", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Change Percent Black", "Change Percent Latino", "Change Percent Asian", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Population (logged)", "White Ideology", "Constant"))
+                    covariate.labels = c("White/Nonwhite H Index", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Change Percent Black", "Change Percent Latino", "Change Percent Asian", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Population (logged)", "White Ideology", "Constant"),
+                    dep.var.labels = c("\\textbf{\\underline{Direct General Expenditure Per Capita}}"),
+                    column.labels = c("Main Specification", "Changing Demographics", "Ideology Controls"),
+                    notes = c("Table A2: This table displays the results of the replication effort of the analyses conducted in Trounstine (2016)", "
+                              assessing the effect of segregation in direct per capita public expenditures using the financial segregation",
+                              "dataset. The replication code can be found on my personal Github repository, which islinked in the introduction."),
+                    table.placement = "H",
+                    notes.align = "l",
+                    font.size = "small")
 
@@
 
-```{r results = "asis", echo = FALSE}
-table3a <- stargazer(felm2_1, felm2_2, felm2_3, 
-          omit = c("year", "south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Public Goods A}",
-          covariate.labels = c("White/Nonwhite H Index", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Population (logged)", "Constant"))
-
-table3b <- stargazer(felm2_4, felm2_5, felm2_6, 
-          omit = c("year", "south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Public Goods B}")
-
-#star_sidewaystable(table3)
-```
-
 ```{r iv_regs, include = FALSE}
@@
 
-```{r results = "asis", echo = FALSE, eval = FALSE}
-
-table5a <- stargazer(ivreg1, ivreg2, ivreg3, ivreg4,
-          omit = c("y5", "y6", "y7", "y8", "y9", "northeast", "south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach A}",
-          covariate.labels = c("White/Nonwhite H Index", "Lagged Direct Gen.
-Exp.", "Lagged Highway Exp.", "Lagged Police Exp.", "Lagged Parks Exp.", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Constant"))
-
-table5b <- stargazer(ivreg5, ivreg6, ivreg7,
-          omit = c("y5", "y6", "y7", "y8", "y9", "northeast","south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach B}",
-          covariate.labels = c("White/Nonwhite H Index", "Lagged Sewers Exp.", "Lagged Gen.
-Rev.
-Own Sources", "Lagged Police Exp.", "Lagged Welfare", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Constant"))
-```
-
-```{r import_data, include = FALSE}
-
-# make a list of the cities included in the analysis to filter out from the main
-# dataset as specified in the table
-
-cities_to_keep <- c("Austin City", "Baltimore City", "Charlotte City", "Chicago City", "Cleveland City", "Columbus City", "Dallas City", "Denver City", "Detroit City", "Houston City", "Indianapolis", "Jacksonville", "Los Angeles City", "Memphis City", "Milwaukee City", "New York City", "Oklahoma City City", "Philadelphia City", "Phoenix City", "San Antonio City", "San Diego City", "San Francisco City", "San Jose City", "Tucson City", "Washington City")
-
-# based on some investigation, the missing additional filter needed to replicate
-# appendix tables 1 and 2 is that biggest split cannot be NA. This was
-# discovered in attempting to create table 2. The number of elections with the
-# largest divides between each racial group were the same as in the table when
-# all results were included and only the summary stats differed in both tables
-# using the city and winner subset. So, I tried excluding all entries for which
-# biggestsplit was NA, and found that the resulting subset matched the
-# statistics in both tables.
-
-# create a subset of the data with the relevant cities where there is a winner
-# and the biggestsplit is not NA
-
-rp_sub <- rp %>%
-  filter(winner == 1) %>%
-  filter(cityname %in% cities_to_keep) %>%
-  filter(!(is.na(biggestsplit)))
-
-# select the relevant variables for the table
-
-rp_sub_a1 <- rp_sub %>%
-  select(biggestsplit, H_citytract_multi_i, H_citytract_NHW_i, diversityinterp, 
-         pctasianpopinterp, pctblkpopinterp, pctlatinopopinterp, medincinterp, 
-         pctrentersinterp, pctcollegegradinterp, biracial, nonpartisan, primary, 
-         logpop, whiteideology_fill2) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-# why are the exact variables H_citytract_NHW and whiteideology_fill not in the
-# data? Data variable names author uses and ones in the data don't exactly
-# match, but replication results are the same.
-
-```
-
-```{r table_a1, results="asis", echo = FALSE}
-
-# create a stargazer summary table for the relevant statistics of the racial
-# polarization data. I couldn't figure out how to change the text of the
-# statistic names at the top of the datat table. I also couldn't figure out how
-# to only not display additional digits for the income variable. May be
-# better to switch to gt for final version?
-
-stargazer(as.data.frame(rp_sub_a1),
-          omit.summary.stat = c("p25", "p75"),
-          title = "\\textbf{TABLE A1 Summary Statistics: Racial Polarization Data}",
-          column.labels = c("\\textbf{Variable}","\\textbf{Obs}", "\\textbf{Mean}", "\\textbf{Std. Dev.}", "\\textbf{Min}", "\\textbf{Max}"),
-          covariate.labels = c("Largest Racial Divide","\\emph{H} Index: Multigroup", "\\emph{H} Index: Two-Group", "Diversity", "\\% Asian", "\\% Black", "\\% Latino", "Median HH Income", "\\% Renters", "\\% College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology"),
-          no.space = TRUE,
-          header = FALSE)
-
-```
-
-```{r table_a2_data_manipulation, include = FALSE}
-
-# initialize variables to indicate if a racial divide had the biggest divide in
-# the election
-
-rp_sub$biggest_split_bw <- NA
-rp_sub$biggest_split_lw <- NA
-rp_sub$biggest_split_bl <- NA
-
-# change the NA value to 1 if the relevant divide was the biggest in the election
-
-rp_sub$biggest_split_bw[rp_sub$biggestsplit_gr == 1] <- 1
-rp_sub$biggest_split_lw[rp_sub$biggestsplit_gr == 2] <- 1
-rp_sub$biggest_split_bl[rp_sub$biggestsplit_gr == 3] <- 1
-
-# generate the dataset of summary statistics to replicate the second appendix
-# table. Group by city name and then summarize the mean H indexes. Sum the
-# number of biggest splits by racial divide for each city
-
-rp_sub_2 <- rp_sub %>%
-  group_by(cityname) %>%
-  summarise(mean_multi_H = mean(H_citytract_multi_i),
-            mean_multi_two_group = mean(H_citytract_NHW_i),
-            sum_bw = sum(biggest_split_bw, na.rm = T),
-            sum_lw = sum(biggest_split_lw, na.rm = T),
-            sum_bl = sum(biggest_split_bl, na.rm = T))
-```
-
-```{r table_a2, echo = FALSE}
-
-# create appendix table A2 to present the summary statistics for cities included
-# in racial polarization data. Efforts to make columns narrower were
-# unsuccessful, so some of the labels in the column names were changed to make
-# the table fit. I also couldn't get the title to print out without including a
-# non-Null subtitle.
-
-city_names <- c("Austin, TX", "Baltimore, MD", "Charlotte, NC", "Chicago, IL", "Cleveland, OH", "Columbus, OH", "Dallas, TX", "Denver, CO", "Detroit, MI", "Houston, TX", "Indianapolis, IN", "Jacksonville, FL", "Los Angeles, CA", "Memphis, TN", "Milwaukee, WI", "New York, NY", "Oklahoma, OK", "Philadelphia, PA", "Phoenix, AZ", "San Antonio, TX","San Diego, CA", "San Francisco, CA", "San Jose, CA", "Tucson, AZ", "Washington, DC")
-
-rp_sub_2$cityname <- city_names
-
-gt(rp_sub_2) %>%
-  tab_header(title = md("**TABLE A2 Cities Included in Racial Polarization Data**"),
-             subtitle = "Replication") %>%
-  tab_spanner(
-      label = md("**Segregation: Mean *H* Index**"),
-      columns = vars(mean_multi_H, mean_multi_two_group)) %>%
-  tab_spanner(
-      label = md("**Largest Racial Divide, Number of Elections**"),
-      columns = vars(sum_bw, sum_lw, sum_bl)) %>%
-  fmt_number(columns = vars(mean_multi_H, mean_multi_two_group),
-             decimals = 3) %>%
-  cols_label(cityname = "City Name",
-             mean_multi_H = md("Multigroup"),
-             mean_multi_two_group = md("Two-Group"),
-             sum_bw = "Black/White",
-             sum_lw = "Latino/White",
-             sum_bl = "Black/Latino") %>%
-  cols_width(
-    vars(cityname) ~ px(10),
-    TRUE ~ px(20)
-  ) %>%
-  cols_align(
-    columns = vars(cityname),
-    align = "left"
-  ) %>%
-  tab_options(
-    table.margin.left = px(5), 
-    table.margin.right = px(5),
-    data_row.padding = px(1),
-    table.width = pct(90)
-  )
-
-```
-
-```{r fp_summary_table, include = FALSE}
-
-# basic filter for table for all regressions
-
-# xtreg dgepercap_cpi H_citytract_NHW_i diversityinterp pctblkpopinterp
-# pctasianpopinterp pctlatinopopinterp medinc_cpi pctlocalgovworker_100
-# pctrentersinterp pctover65 pctcollegegradinterp logpop if totaltracts>1 &
-# dgepercap_cpi~=0,fe vce(cluster geo_id2)
-
-fin <-fin_seg %>%
-  filter(totaltractsf >1 | is.na(totaltractsf)) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
-
-# create dge variable used in regression
-
-fin_dge <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_dge_tab <- tibble(
-  Variable = "Direct General Expenditure per Capita",
-  Obs = nrow(fin_dge),
-  Mean = mean(fin_dge$dgepercap_cpi, na.rm = T),
-  SD = sd(fin_dge$dgepercap_cpi, na.rm = T),
-  Min = min(fin_dge$dgepercap_cpi, na.rm = T),
-  Max = max(fin_dge$dgepercap_cpi, na.rm = T)
-)
-
-print(fin_dge_tab)
-
-# cities in original Trounstine
-
-cities_trounstine_fp <- fin_dge %>%
-  select(geo_id2) %>%
-  unique() %>%
-  pull()
-
-# pop quantiles original Trounstine
-
-quantile(fin_dge$logpop, c(.10, .25, .5, .75, .90))
-
-quantile(fin_dge$logpop, c(.05, .95))
-
-nrow(fin_imp)
-
-fin_imp_pop_trounstine_95 <- fin_imp %>%
-  filter(logpop < 11.93437 & logpop > 8.7754)
-
-# creat summary for highways
-fin_hw <-fin %>% filter(highwayspercapNC_cpi != 0)
-
-fin_hw_tab <- tibble(
-  Variable = "Highways per Capita",
-  Obs = nrow(fin_hw),
-  Mean = mean(fin_hw$highwayspercapNC_cpi, na.rm = T),
-  SD = sd(fin_hw$highwayspercapNC_cpi, na.rm = T),
-  Min = min(fin_hw$highwayspercapNC_cpi, na.rm = T),
-  Max = max(fin_hw$highwayspercapNC_cpi, na.rm = T)
-)
-
-print(fin_hw_tab)
-
-a3_final <- full_join(fin_dge_tab, fin_hw_tab)
-
-# parks
-
-fin_park <-fin %>% filter(parkspercapNC_cpi != 0)
-
-fin_park_tab <- tibble(
-  Variable = "Parks per Capita",
-  Obs = nrow(fin_park),
-  Mean = mean(fin_park$parkspercapNC_cpi, na.rm = T),
-  SD = sd(fin_park$parkspercapNC_cpi, na.rm = T),
-  Min = min(fin_park$parkspercapNC_cpi, na.rm = T),
-  Max = max(fin_park$parkspercapNC_cpi, na.rm = T)
-)
-
-print(fin_park_tab)
-
-a3_final <- full_join(a3_final, fin_park_tab)
-
-# police
-
-fin_police <-fin %>% filter(policepercapNC_cpi != 0)
-
-fin_police_tab <- tibble(
-  Variable = "Police per Capita",
-  Obs = nrow(fin_police),
-  Mean = mean(fin_police$policepercapNC_cpi, na.rm = T),
-  SD = sd(fin_police$policepercapNC_cpi, na.rm = T),
-  Min = min(fin_police$policepercapNC_cpi, na.rm = T),
-  Max = max(fin_police$policepercapNC_cpi, na.rm = T)
-)
-
-print(fin_police_tab)
-
-a3_final <- full_join(a3_final, fin_police_tab)
-
-# sewers
-
-fin_sew <-fin %>% filter(sewerspercapNC_cpi != 0)
-
-fin_sew_tab <- tibble(
-  Variable = "Sewers per Capita",
-  Obs = nrow(fin_sew),
-  Mean = mean(fin_sew$sewerspercapNC_cpi, na.rm = T),
-  SD = sd(fin_sew$sewerspercapNC_cpi, na.rm = T),
-  Min = min(fin_sew$sewerspercapNC_cpi, na.rm = T),
-  Max = max(fin_sew$sewerspercapNC_cpi, na.rm = T)
-)
-
-print(fin_sew_tab)
-
-a3_final <- full_join(a3_final, fin_sew_tab)
-
-# welfare
-
-fin_welfare <-fin %>% filter(welfhoushealthNC_cpi != 0)
-
-fin_welfare_tab <- tibble(
-  Variable = "Welfare, Health, and Housing per Capita",
-  Obs = nrow(fin_welfare),
-  Mean = mean(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
-  SD = sd(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
-  Min = min(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
-  Max = max(fin_welfare$welfhoushealthNC_cpi, na.rm = T)
-)
-
-print(fin_welfare_tab)
-
-a3_final <- full_join(a3_final, fin_welfare_tab)
-
-# own source revenue
-
-fin_own <-fin %>% filter(genrevownpercap_cpi != 0)
-
-fin_own_tab <- tibble(
-  Variable = "Own Source Revenue per Capita",
-  Obs = nrow(fin_own),
-  Mean = mean(fin_own$genrevownpercap_cpi, na.rm = T),
-  SD = sd(fin_own$genrevownpercap_cpi, na.rm = T),
-  Min = min(fin_own$genrevownpercap_cpi, na.rm = T),
-  Max = max(fin_own$genrevownpercap_cpi, na.rm = T)
-)
-
-print(fin_own_tab)
-
-a3_final <- full_join(a3_final, fin_own_tab)
-
-# two group H
-
-fin_h <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_h_tab <- tibble(
-  Variable = "Two-Group H Index",
-  Obs = nrow(fin_h),
-  Mean = mean(fin_h$H_citytract_NHW_i, na.rm = T),
-  SD = sd(fin_h$H_citytract_NHW_i, na.rm = T),
-  Min = min(fin_h$H_citytract_NHW_i, na.rm = T),
-  Max = max(fin_h$H_citytract_NHW_i, na.rm = T)
-)
-
-print(fin_h_tab)
-
-a3_final <- full_join(a3_final, fin_h_tab)
-
-# Diversity
-
-fin_div <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_div_tab <- tibble(
-  Variable = "Diversity",
-  Obs = nrow(fin_div),
-  Mean = mean(fin_div$diversityinterp, na.rm = T),
-  SD = sd(fin_div$diversityinterp, na.rm = T),
-  Min = min(fin_div$diversityinterp, na.rm = T),
-  Max = max(fin_div$diversityinterp, na.rm = T)
-)
-
-print(fin_div_tab)
-
-a3_final <- full_join(a3_final, fin_div_tab)
-
-# % black
-
-fin_pctblk <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pctblk_tab <- tibble(
-  Variable = "%  Black",
-  Obs = nrow(fin_pctblk),
-  Mean = mean(fin_pctblk$pctblkpopinterp, na.rm = T),
-  SD = sd(fin_pctblk$pctblkpopinterp, na.rm = T),
-  Min = min(fin_pctblk$pctblkpopinterp, na.rm = T),
-  Max = max(fin_pctblk$pctblkpopinterp, na.rm = T)
-)
-
-print(fin_pctblk_tab)
-
-a3_final <- full_join(a3_final, fin_pctblk_tab)
-
-# % asian
-
-fin_pcta <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pcta_tab <- tibble(
-  Variable = "%  Asian",
-  Obs = nrow(fin_pcta),
-  Mean = mean(fin_pcta$pctasianpopinterp, na.rm = T),
-  SD = sd(fin_pcta$pctasianpopinterp, na.rm = T),
-  Min = min(fin_pcta$pctasianpopinterp, na.rm = T),
-  Max = max(fin_pcta$pctasianpopinterp, na.rm = T)
-)
-
-print(fin_pcta_tab)
-
-a3_final <- full_join(a3_final, fin_pcta_tab)
-
-# % latino
-
-fin_pctla <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pctla_tab <- tibble(
-  Variable = "%  Latino",
-  Obs = nrow(fin_pctla),
-  Mean = mean(fin_pctla$pctlatinopopinterp, na.rm = T),
-  SD = sd(fin_pctla$pctlatinopopinterp, na.rm = T),
-  Min = min(fin_pctla$pctlatinopopinterp, na.rm = T),
-  Max = max(fin_pctla$pctlatinopopinterp, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_pctla_tab)
-
-# 5y black
-
-fin_chng5pctblk <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))
-
-nrow(fin_chng5pctblk)
-
-fin_chng5pctblk_tab <- tibble(
-  Variable = "5Y Change, % Black",
-  Obs = nrow(fin_chng5pctblk),
-  Mean = mean(fin_chng5pctblk$chng5pctblk, na.rm = T),
-  SD = sd(fin_chng5pctblk$chng5pctblk, na.rm = T),
-  Min = min(fin_chng5pctblk$chng5pctblk, na.rm = T),
-  Max = max(fin_chng5pctblk$chng5pctblk, na.rm = T)
-)
-
-print(fin_chng5pctblk_tab)
-
-a3_final <- full_join(a3_final, fin_chng5pctblk_tab)
-
-# 5y latino
-
-fin_chng5pctlatino <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))
-
-fin_chng5pctlatino_tab <- tibble(
-  Variable = "5Y Change, % Latino",
-  Obs = nrow(fin_chng5pctlatino),
-  Mean = mean(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
-  SD = sd(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
-  Min = min(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
-  Max = max(fin_chng5pctlatino$chng5pctlatino, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_chng5pctlatino_tab)
-
-# 5y asian
-
-fin_chng5pctasian <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))
-
-fin_chng5pctasian_tab <- tibble(
-  Variable = "5Y Change, % Asian",
-  Obs = nrow(fin_chng5pctasian),
-  Mean = mean(fin_chng5pctasian$chng5pctasian, na.rm = T),
-  SD = sd(fin_chng5pctasian$chng5pctasian, na.rm = T),
-  Min = min(fin_chng5pctasian$chng5pctasian, na.rm = T),
-  Max = max(fin_chng5pctasian$chng5pctasian, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_chng5pctasian_tab)
-
-# median income
-
-fin_med <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_med_tab <- tibble(
-  Variable = "Median Income",
-  Obs = nrow(fin_med),
-  Mean = mean(fin_med$medinc_cpi, na.rm = T),
-  SD = sd(fin_med$medinc_cpi, na.rm = T),
-  Min = min(fin_med$medinc_cpi, na.rm = T),
-  Max = max(fin_med$medinc_cpi, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_med_tab)
-
-# % local gov. employees
-
-fin_pctlocal <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pctlocal_tab <- tibble(
-  Variable = "% Local Gov. Employees",
-  Obs = nrow(fin_pctlocal),
-  Mean = mean(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
-  SD = sd(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
-  Min = min(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
-  Max = max(fin_pctlocal$pctlocalgovworker_100, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_pctlocal_tab)
-
-# % renters
-
-fin_rent <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_rent_tab <- tibble(
-  Variable = "% Renters",
-  Obs = nrow(fin_rent),
-  Mean = mean(fin_rent$pctrentersinterp, na.rm = T),
-  SD = sd(fin_rent$pctrentersinterp, na.rm = T),
-  Min = min(fin_rent$pctrentersinterp, na.rm = T),
-  Max = max(fin_rent$pctrentersinterp, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_rent_tab)
-
-# % over 65
-
-fin_65 <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_65_tab <- tibble(
-  Variable = "% Over 65",
-  Obs = nrow(fin_65),
-  Mean = mean(fin_65$pctover65, na.rm = T),
-  SD = sd(fin_65$pctover65, na.rm = T),
-  Min = min(fin_65$pctover65, na.rm = T),
-  Max = max(fin_65$pctover65, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_65_tab)
-
-# % college degree
-
-fin_college <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_college_tab <- tibble(
-  Variable = "% College Degree",
-  Obs = nrow(fin_college),
-  Mean = mean(fin_college$pctcollegegradinterp, na.rm = T),
-  SD = sd(fin_college$pctcollegegradinterp, na.rm = T),
-  Min = min(fin_college$pctcollegegradinterp, na.rm = T),
-  Max = max(fin_college$pctcollegegradinterp, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_college_tab)
-
-# pop logged
-
-fin_logpop <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_logpop_tab <- tibble(
-  Variable = "Population (logged)",
-  Obs = nrow(fin_logpop),
-  Mean = mean(fin_logpop$logpop, na.rm = T),
-  SD = sd(fin_logpop$logpop, na.rm = T),
-  Min = min(fin_logpop$logpop, na.rm = T),
-  Max = max(fin_logpop$logpop, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_logpop_tab)
-
-# city ideology
-
-fin_ideo <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(ideology_fill)))
-
-nrow(fin_ideo)
-
-fin_ideo_tab <- tibble(
-  Variable = "City Ideology",
-  Obs = nrow(fin_ideo),
-  Mean = mean(fin_ideo$ideology_fill, na.rm = T),
-  SD = sd(fin_ideo$ideology_fill, na.rm = T),
-  Min = min(fin_ideo$ideology_fill, na.rm = T),
-  Max = max(fin_ideo$ideology_fill, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_ideo_tab)
-
-# population
-fin_population <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_population_tab <- tibble(
-  Variable = "Population",
-  Obs = nrow(fin_population),
-  Mean = mean(fin_population$population, na.rm = T),
-  SD = sd(fin_population$population, na.rm = T),
-  Min = min(fin_population$population, na.rm = T),
-  Max = max(fin_population$population, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_population_tab)
-
-```
-
-```{r fp_summary_table_stargazer, echo = FALSE}
-gt(a3_final) %>%
-    tab_header(title = md("**TABLE A3 Summary Statistics: Census of Government Finance and Population**"),
-             subtitle = "") %>%
-    fmt_number(columns = vars(Mean, SD, Min, Max),
-             decimals = 3) %>%
-    cols_label(Obs = md("**Obs**"),
-               Mean = md("**Mean**"),
-               SD = md("**SD**"),
-               Min = md("**Min**"),
-               Max = md("**Max**")
-                        ) 
-```
-
+```{r additional_robustness_checks_imp_rp, eval = FALSE, include = FALSE}
+
+# ideally, the fits will intertwine and not exhibit any trends at later iterations.
+This seems to generally be the case.
+There are some issues with the results for some of the variables with very few missing values, which makes sense as we would expect the mean to be less reliable due to the law of large numbers and thus convergence is more difficult.
+However, since these are so few values, it is less important about how robust they are.
+
+plot(imp_1_rp)
+
+# we can also check the imputed values against the original values using stripplot().
+Each column in each subplot represents a separate iteration.
+The magenta points represent the imputed data.
+The values of the variable in questions are along the y axis.
+We expect the spread of the data to be similar if the imputations were done well.
+If the data were missing completely at random, then the imputed data should have the same distribution as the original data.
+In particular, we want to be sure that the imputations are within a plausible range of the data.
+This is the case for all of our imputed variables, and there does not seem to be cause for alarm from these results.
+
+stripplot(imp_1_rp)
+
+```
+
+```{r additional_robustness_checks_imp_fs_v1, eval = FALSE, include = FALSE}
+
+# ideally, the fits will intertwine and not exhibit any trends at later iterations.
+This seems to generally be the case.
+There are some issues with the results for some of the variables with very few missing values, which makes sense as we would expect the mean to be less reliable due to the law of large numbers and thus convergence is more difficult.
+However, since these are so few values, it is less important about how robust they are.
+
+plot(imp_fs)
+
+# we can also check the imputed values against the original values using stripplot().
+Each column in each subplot represents a separate iteration.
+The magenta points represent the imputed data.
+The values of the variable in questions are along the y axis.
+We expect the spread of the data to be similar if the imputations were done well.
+If the data were missing completely at random, then the imputed data should have the same distribution as the original data.
+In particular, we want to be sure that the imputations are within a plausible range of the data.
+This is the case for all of our imputed variables, and there does not seem to be cause for alarm from these results.
+
+stripplot(imp_fs, H_citytract_NHW_i)
+
+stripplot(imp_fs, chng5pctblk)
+
+stripplot(imp_fs, chng5pctlatino)
+
+stripplot(imp_fs, chng5pctasian)
+
+stripplot(imp_fs, ideology_fill)
+
+```
+
+\newpage
 # Bibliography

### 2020-05-02 Final_Draft.Rmd
edits to tables

@@
 library(haven)
-library(gtable)
 library(stargazer)
 library(tidyverse)
-library(gt)
 library(gtsummary)
 library(knitr)
+library(AER)
 library(lme4)
 library(margins)
-library(reprex)
-library(plm)
-library(devtools)
 library(lfe)
-library(Statamarkdown)
 library(readxl)
-library(starpolishr)
-library(AER)
-library(readxl)
-library(naniar)
 library(mice)
-library(gtsummary)
 library(VIM)
 library(kableExtra)
+library(huxtable)
 ```
@@
 
-aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.5, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
+aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.4, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
 title(main = "Patterns of Missingness in the Financial Segregation Data",
       sub = "", font.main = 1, font.axis = 1, cex.main = 1, line = 3,  oma = c(1,3,5,1), font.main = 1, font.axis = 1)
-
 # this plot tells us that only .58% of the data are complete (not missing anything)
@@
 More of the data could not be imputed from the financial segregation dataset due to computing and time constraints for this project given the dataset's large size and high proportion of missing values.
+
+```{r rp_imputation, include = FALSE}
+
+# Perform multiple imputations using the cart method. Because of the time it
+# takes to run this function, I turned the results into a dataset to load in
+# instead of re-running everytime.
+
+rp_impute_labels <- rp_impute
+
+rp_impute_labels$biggestsplit <- "Racial Divide"
+rp_impute_labels$medincinterp <- "Median HH Income"
+
+#c("Racial Divide" = biggestsplit, "Biracial Contest" = biracial, "White Ideology" = whiteideology_fill2, "Median HH Income" = medincinterp, "Diversity" = diversityinterp, "% Asian" = pctasianpopinterp,  "% Black" = pctblkpopinterp, "% Latino" = pctlatinopopinterp,"% Renters" = pctrentersinterp, "% College Grads" = pctcollegegradinterp, "Nonpartisan Elect." = nonpartisan, "South" = south, "Midwest" = midwest,"West" = "west")
+
+max_it = 20
+
+imp_1_rp <- mice(rp_impute, method = "cart", maxit = 20)
+
+```
+
+```{r fp_imputations_original, eval = FALSE, include = FALSE}
+
+# perform multiple imputations.
+We have the same issue here with the default method as with the previous dataset so we use CART.
+Additionally, because of the extremely large size of this dataset, we choose to only impute the variable H_citytract_NHW_i, as it is the most frequently missing variable and also out main independent variable.
+Just imputing this allows us to include way more observations in the regression than the original data despite the still large number of NAs overall.
+One concern here would be that if there was some reason that this variable was missing rather than other variables that only imputing this variable could lead to some bias in the results.
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_fs <- mice(fin_imp, method = meth, maxit = 1)
+
+# now there are many fewer missing variables!!!
+
+miss_var_summary(complete(imp_fs))
+
+miss_var_summary(fin_imp)
+
+282334 - 222957
+
+```
+
+## make sure to talk about the fact that still a large number of values missing for the imputed variables here
+
+Before examining the results of Trounstine's model using the multiply imputed data, I first ran some diagnostic tests on the imputation results to make sure that everything ran as expected.
+First, I checked the convergence of the algorithm used within mice() by plotting the trace lines as a function of the number of iterations for each of the variables.
+Then, I visually inspected the distributions of the imputed data in comparison to the original data with density and strip plots.
+All of these checks suggested that the imputed values were within a plausible range of the data and that their distribution fit the underlying distribution of the data relatively well.
+The only cases in which there was some cause for concern were for some of the variables with very few missing values in the racial polarization dataset (such as the indicators for region).
+However, this is more or less to be expected given the small number of imputations performed in these cases.
+Thus, and especially because there are so few of these values missing in the actual datasets, this was not a major concern.
+See figures X and X1 to see the density plots of the imputed values overlayed on the density plots of the original variables.
+The code to generate the rest of the plots and results of the diagnostic tests discussed here are presented in the Appendix.
+
+```{r rp_densityplot, echo = FALSE}
+
+my.settings <- list(
+  par.main.text = list(font = 1, cex = 1)
+)
+
+densityplot(imp_1_rp, main = "Density Plots of Imputed and Original Data by Variable\nin the Racial Polarization Dataset",
+      par.settings = my.settings,
+      par.strip.text = list(cex = .7))
+
+```
+
+```{r fs_densityplot, echo = FALSE, eval = FALSE}
+
+densityplot(imp_fs)
+densityplot(x = imp_fs , data = ~ H_citytract_NHW_i + chng5pctblk + 
+       chng5pctlatino + chng5pctasian + ideology_fill)
+
+```
+
+Given the promising results of the diagnostic checks, I next proceeded to re-estimate the original model using the multiply imputed datasets, pooling the results to produce final pooled regression coefficients and parameters.
+The results for the analyses using the racial polarization dataset are presented in tables X1-X3.
+
+```{r rp_imputations, include = FALSE}
+
+# Now that we have imputed the missing data, we can re-run the analyses from the
+# original paper to see how and if this changes the analysis. We can use the
+# with() function from the mice package to fit each of the imputed datasets to
+# the model and then pool the results afterwards.
+
+# regression 1: fit multiple imputed datasets
+
+fit_imp_1_rp <- with(imp_1_rp, lmer(formula = biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
+
+# pool and summarize the analyses
+
+pool_imp_1_rp <- pool(fit_imp_1_rp)
+imp_1_rp_sum <- summary(pool_imp_1_rp)
+
+## regression 2 Table 1: fit multiple imputed datasets
+
+#formula = biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2)
+
+fit_imp_2_rp <- with(imp_1_rp, lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
+
+# pool and summarize the analyses
+
+pool_imp_2_rp <- pool(fit_imp_2_rp)
+imp_2_rp_sum <- summary(pool_imp_2_rp)
+
+## regression 3 Table 1 with new data
+
+#formula = biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2)
+
+fit_imp_3_rp <- with(imp_1_rp, lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
+
+# pool and summarize the analyses
+
+pool_imp_3_rp <- pool(fit_imp_3_rp)
+imp_3_rp_sum <- summary(pool_imp_3_rp)
+
+```
+
+The results of the model with the new dataset are slightly different in comparison to the original results from Trounstine (2016).
+With the imputed data, we now have a total of `r nrow(complete(rp_impute))` observations in our model as compared to the original model, which had only 91 observations.
+Interestingly, while the sign of the coefficient on the main variable of interest, the Theil's H segregation index, is the same and the standard error has decreased slightly, the result has become statisically insignificant and the 95% confidence interval contains zero.
+Thus while these results still suggest that segregation may be associated with increased political polarization, they confer a lesser degree of certainty than Trounstine's original analysis.
+The coefficients for % Black population, % Latino population, and median household income have also switched signs, and all coefficients except the indicator for a biracial election are also statistically insignificant, as was the case in the original analysis.
+The coefficient on the indicator for a primary election, has also changed from being significant in the original analysis to insignificant here.
+In general, the standard errors on the coefficients have decreased slightly.
+
+```{r results_printing_rp_impute_regressions_1, results = "asis", echo=FALSE}
+
+# print results of 1st regression
+
+imp_1_rp_sum_table <- as.data.frame(imp_1_rp_sum) %>% 
+  select(term, estimate, std.error, p.value) %>%
+  head(13) %>%
+  mutate()
+
+imp_1_rp_sum_table_vars <- tibble(
+  Variable = c("Intercept", "Multigroup Seg. Index", "Diversity", "% Asian", "% Black", "% Latino",
+               "Median Income (1000s)", "% Renters", "% College Grads", "Biracial Elec.", "Nonpartisan Elec.", "Primary Elec.", "Pop (logged)"),
+  Estimate = round(imp_1_rp_sum_table$estimate, 3),
+  `Std. Error` = round(imp_1_rp_sum_table$std.error,3),
+  `P-Value` = round(imp_1_rp_sum_table$p.value, 3)
+  )
+
+stargazer(imp_1_rp_sum_table,
+          header = FALSE,
+          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Multigroup Segregation Index}")
+
+kable(imp_1_rp_sum_table_vars, "latex", caption = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Multigroup Segregation Index}", booktabs = T) %>%
+  row_spec(0, bold = TRUE) %>%
+  footnote(general = "this is my second caption to see if this works and how i will need to deal with newjhfhfjhbcjhwbrjfnwmfnirfjnwmfwkfnj wfjwjenfkwejwefhwefb",
+           general_title = "Table 1:")
+
+```
+
+In the second and third regressions, the results are similar.
+The main coefficient on segregation index has decreased in magnitude, although in these specifications, it remains statistically significant.
+The other coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian, Black, and Latino have all switched signs.
+Standard errors have also reduced slightly in these specifications compared to the original analysis in @trounstine_segregation_2016.
+
+```{r results_printing_rp_impute_regressions_2, results = "asis", echo=FALSE}
+
+# print results of 2nd regression
+
+imp_2_rp_sum_table <- as.data.frame(imp_2_rp_sum) %>% 
+  select(term, estimate, std.error, p.value) %>%
+  head(13)
+
+stargazer(imp_2_rp_sum_table,
+          header = FALSE,
+          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Two-Group Segregation Index}")
+
+```
+
+```{r results_printing_rp_impute_regressions_3, results = "asis", echo=FALSE}
+
+# print results of 3rd regression
+
+imp_3_rp_sum_table <- as.data.frame(imp_3_rp_sum) %>% 
+  select(term, estimate, std.error, p.value) %>%
+  head(13)
+
+stargazer(imp_3_rp_sum_table,
+          header = FALSE,
+          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Ideology Control}")
+```
+
+\newpage
 
@@
                 header = FALSE,
+                style = "apsr",
                 title = "\\textbf{Racial Polarization in Segregated Cities}",
-                single.row = TRUE,
-                no.space = FALSE,
-                keep.stat = c("n"),
+                single.row = FALSE,
+                no.space = F,
                 covariate.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Diversity", "Percent Asian", "Percent Black", "Percent Latino", "Medain HH Income (1000s)", "Percent Renters", "Percent College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology", "Constant"),
-                dep.var.labels = c("Racial Divide"),
+                dep.var.labels = c("\\textbf{\\underline{Racial Divide with:    }}"),
                 column.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Ideology Controls"),
-                notes = "This table displays the results of the replication\neffort of the analyses conducted in Trounstine (2016) using the racial polarization dataset.\nThe replication code can be found on my personal Github repository, which is linked in the introduction.
-The original table is displayed for comparison as Figure 1.)",
+                notes = c("Table A1: This table displays the results of the replication effort of the analyses conducted in Trounstine (2016)", 
+                          "using the racial polarization dataset. The replication code can be found on my personal Github repository, which is",
+                          " linked in the introduction. The original table is displayed for comparison as Figure 3."),
                 table.placement = "H",
-                notes.align = "l")
-
-# note: "This table displays the results of the replication effort of the analyses conducted in Trounstine (2016) using the racial polarization dataset.
-The replication code can be found on my personal [Github repository](https://github.com/mburzillo/new_final_project).
-The original table is displayed for comparison as Figure 1.")
+                notes.align = "l",
+                #column.sep.width = "-10pt",
+                font.size = "small")
 
@@
 ![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016.
-My replication of these results can be found in Table 1 in this paper.](table_1.png)
+My replication of these results can be found in Table A1 in this paper.](table_1.png)
 
@@
                     header = FALSE,
+                    style = "apsr",
                     title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures}",
                     covariate.labels = c("White/Nonwhite H Index", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Change Percent Black", "Change Percent Latino", "Change Percent Asian", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Population (logged)", "White Ideology", "Constant"),
-                    table.placement = "H")
+                    dep.var.labels = c("\\textbf{\\underline{Direct General Expenditure Per Capita}}"),
+                    column.labels = c("Main Specification", "Changing Demographics", "Ideology Controls"),
+                    notes = c("Table A2: This table displays the results of the replication effort of the analyses conducted in Trounstine (2016)", "
+                              assessing the effect of segregation in direct per capita public expenditures using the financial segregation",
+                              "dataset. The replication code can be found on my personal Github repository, which islinked in the introduction."),
+                    table.placement = "H",
+                    notes.align = "l",
+                    font.size = "small")
 
@@
 
+```{r additional_robustness_checks_imp_rp, eval = FALSE, include = FALSE}
+
+# ideally, the fits will intertwine and not exhibit any trends at later iterations.
+This seems to generally be the case.
+There are some issues with the results for some of the variables with very few missing values, which makes sense as we would expect the mean to be less reliable due to the law of large numbers and thus convergence is more difficult.
+However, since these are so few values, it is less important about how robust they are.
+
+plot(imp_1_rp)
+
+# we can also check the imputed values against the original values using stripplot().
+Each column in each subplot represents a separate iteration.
+The magenta points represent the imputed data.
+The values of the variable in questions are along the y axis.
+We expect the spread of the data to be similar if the imputations were done well.
+If the data were missing completely at random, then the imputed data should have the same distribution as the original data.
+In particular, we want to be sure that the imputations are within a plausible range of the data.
+This is the case for all of our imputed variables, and there does not seem to be cause for alarm from these results.
+
+stripplot(imp_1_rp)
+
+```
+
+```{r additional_robustness_checks_imp_fs_v1, eval = FALSE, include = FALSE}
+
+# ideally, the fits will intertwine and not exhibit any trends at later iterations.
+This seems to generally be the case.
+There are some issues with the results for some of the variables with very few missing values, which makes sense as we would expect the mean to be less reliable due to the law of large numbers and thus convergence is more difficult.
+However, since these are so few values, it is less important about how robust they are.
+
+plot(imp_fs)
+
+# we can also check the imputed values against the original values using stripplot().
+Each column in each subplot represents a separate iteration.
+The magenta points represent the imputed data.
+The values of the variable in questions are along the y axis.
+We expect the spread of the data to be similar if the imputations were done well.
+If the data were missing completely at random, then the imputed data should have the same distribution as the original data.
+In particular, we want to be sure that the imputations are within a plausible range of the data.
+This is the case for all of our imputed variables, and there does not seem to be cause for alarm from these results.
+
+stripplot(imp_fs, H_citytract_NHW_i)
+
+stripplot(imp_fs, chng5pctblk)
+
+stripplot(imp_fs, chng5pctlatino)
+
+stripplot(imp_fs, chng5pctasian)
+
+stripplot(imp_fs, ideology_fill)
+
+```
+
+\newpage
 # Bibliography

### 2020-05-02 Final_Draft.Rmd
changes to rp imputation tables

@@
 
-```{r fp_imputations_original, eval = FALSE, include = FALSE}
+```{r fp_imputations_original, include = FALSE, eval = FALSE}
 
@@
 
-stargazer(imp_1_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Multigroup Segregation Index}")
-
 kable(imp_1_rp_sum_table_vars, "latex", caption = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Multigroup Segregation Index}", booktabs = T) %>%
   row_spec(0, bold = TRUE) %>%
-  footnote(general = "this is my second caption to see if this works and how i will need to deal with newjhfhfjhbcjhwbrjfnwmfnirfjnwmfwkfnj wfjwjenfkwejwefhwefb",
-           general_title = "Table 1:")
+  footnote(general = c("This table shows the results of Trounstine's first model for the effect of segregation on political polarization (racial vote divide) using the multi-group Theil's H segregation Index using the new, multiply imputed datasets.
+The sign of the coefficient on the main variable of interest, the segregation index, is the same, but the result has become statisically insignificant with the 95% confidence interval containing zero.
+Thus while these results still suggest that segregation may be associated with increased political polarization, they confer a lesser degree of certainty than Trounstine's original analysis.
+The coefficients for % Black population, % Latino population, and median household income have also switched signs.
+The coefficient on the indicator for a primary election, has also changed from being significant in the original analysis to insignificant here.
+In general, the standard errors on the coefficients have decreased slightly."),
+           general_title = "Table 1:")%>%
+  kable_styling(full_width = TRUE)
 
@@
 
-stargazer(imp_2_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Two-Group Segregation Index}")
+imp_2_rp_sum_table_vars <- tibble(
+  Variable = c("Intercept", "White/Nonwhite Seg. Index", "Diversity", "% Asian", "% Black", "% Latino",
+               "Median Income (1000s)", "% Renters", "% College Grads", "Biracial Elec.", "Nonpartisan Elec.", "Primary Elec.", "Pop (logged)"),
+  Estimate = round(imp_2_rp_sum_table$estimate, 3),
+  `Std. Error` = round(imp_2_rp_sum_table$std.error,3),
+  `P-Value` = round(imp_2_rp_sum_table$p.value, 3)
+  )
+
+kable(imp_2_rp_sum_table_vars, "latex", caption = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Two-Group Segregation Index}", booktabs = T) %>%
+  row_spec(0, bold = TRUE) %>%
+  footnote(general = c("This table shows the results of Trounstine's second model for the effect of segregation on political polarization (racial vote divide) using the two-group Theil's H segregation Index using the new, multiply imputed datasets.
+Compared to Trounstine's original results, the main coefficient on segregation index has decreased in magnitude, although, it remains statistically significant.
+The other coefficients except for the biracial indicator are insignificant, and the coefficients on percent Black, percent Latino, and Median Income have switched signs.
+Standard errors have also reduced slightly in these specifications compared to the original analysis in Trounstine (2016)."),
+           general_title = "Table 2:") %>%
+  kable_styling(full_width = TRUE)
 
@@
 
-stargazer(imp_3_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Ideology Control}")
+imp_3_rp_sum_table_vars <- tibble(
+  Variable = c("Intercept", "White/Nonwhite Seg. Index", "Diversity", "% Asian", "% Black", "% Latino",
+               "Median Income (1000s)", "% Renters", "% College Grads", "Biracial Elec.", "Nonpartisan Elec.", "Primary Elec.", "Pop (logged)"),
+  Estimate = round(imp_3_rp_sum_table$estimate, 3),
+  `Std. Error` = round(imp_3_rp_sum_table$std.error,3),
+  `P-Value` = round(imp_3_rp_sum_table$p.value, 3)
+  )
+
+kable(imp_3_rp_sum_table_vars, "latex", caption = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Ideology Control}", booktabs = T) %>%
+  row_spec(0, bold = TRUE) %>%
+  footnote(general = c("This table shows the results of Trounstine's third model for the effect of segregation on political polarization (racial vote divide) using the two-group Theil's H segregation Index and including controls for ideology using the new, multiply imputed datasets.
+Compared to Trounstine's original results, the main coefficient on segregation index has decreased in magnitude, although, it remains statistically significant.
+The other coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian and Black have switched signs.
+Standard errors have also reduced slightly in these specifications compared to the original analysis in Trounstine (2016).""),
+           general_title = "Table 3:") %>%
+  kable_styling(full_width = TRUE)
+
 ```

### 2020-05-03 Final_Draft.Rmd
changes to rp imputation table captions

--- 2020-05-02 Final_Draft.Rmd
@@
 
-stargazer(imp_1_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Multigroup Segregation Index}")
-
 kable(imp_1_rp_sum_table_vars, "latex", caption = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Multigroup Segregation Index}", booktabs = T) %>%
   row_spec(0, bold = TRUE) %>%
-  footnote(general = "this is my second caption to see if this works and how i will need to deal with newjhfhfjhbcjhwbrjfnwmfnirfjnwmfwkfnj wfjwjenfkwejwefhwefb",
-           general_title = "Table 1:")
+  footnote(general = c("This table shows the results of Trounstine's first model for the effect of segregation on political polarization",
+  "(racial vote divide) using the multi-group Theil's H segregation Index using the new, multiply imputed datasets.",
+  "The sign of the coefficient on the main variable of interest, the segregation index, is the same, but the",
+  "result has become statisically insignificant with the 95% confidence interval containing zero. Thus",
+  "while these results still suggest that segregation may be associated with increased political polarization,",
+  "they confer a lesser degree of certainty than Trounstine's original analysis. The coefficients for %",
+  "Black population, % Latino population, and median household income have also switched signs. The coefficient",
+  "on the indicator for a primary election, has also changed from being significant in the original analysis",
+  "to insignificant here. In general, the standard errors on the coefficients have decreased slightly."),
+           general_title = "Table 1:")%>%
+  kable_styling(full_width = TRUE)
 
@@
 
-In the second and third regressions, the results are similar.
+In the second regression, the results are similar.
 The main coefficient on segregation index has decreased in magnitude, although in these specifications, it remains statistically significant.
-The other coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian, Black, and Latino have all switched signs.
-Standard errors have also reduced slightly in these specifications compared to the original analysis in @trounstine_segregation_2016.
+The other coefficients except for the biracial indicator are insignificant, and the coefficients on percent Black, percent Latino, and median household income have all switched signs.
 
@@
 
-stargazer(imp_2_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Two-Group Segregation Index}")
+imp_2_rp_sum_table_vars <- tibble(
+  Variable = c("Intercept", "White/Nonwhite Seg. Index", "Diversity", "% Asian", "% Black", "% Latino",
+               "Median Income (1000s)", "% Renters", "% College Grads", "Biracial Elec.", "Nonpartisan Elec.", "Primary Elec.", "Pop (logged)"),
+  Estimate = round(imp_2_rp_sum_table$estimate, 3),
+  `Std. Error` = round(imp_2_rp_sum_table$std.error,3),
+  `P-Value` = round(imp_2_rp_sum_table$p.value, 3)
+  )
+
+kable(imp_2_rp_sum_table_vars, "latex", caption = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Two-Group Segregation Index}", booktabs = T) %>%
+  row_spec(0, bold = TRUE) %>%
+  footnote(general = c("This table shows the results of Trounstine's second model for the effect of segregation on political polarization",
+  "(racial vote divide) using the two-group Theil's H segregation Index using the new, multiply imputed datasets.", 
+  "Compared to Trounstine's original results, the main coefficient on segregation index has decreased in magnitude",
+  "although, it remains statistically significant. The other coefficients except for the biracial indicator are",
+  "insignificant, and the coefficients on percent Black, percent Latino, and Median Income have switched signs.",
+  "Standard errors have also reduced slightly in these specifications compared to the original analysis in",
+  "Trounstine (2016)."),
+           general_title = "Table 2:") %>%
+  kable_styling(full_width = TRUE)
 
 ```
+
+In the third regression, like in the second, the main coefficient on segregation index has decreased in magnitude but remains significant.
+The other coefficients except for the biracial indicator are insignificant, and the coefficients on percent Black, percent Asian, median income, and logged population have switched signs.
+In all three of the specifications, tandard errors reduced slightly using the larger, multiply imputed datasets compared to the original analysis with the original data in @trounstine_segregation_2016.
 
@@
   select(term, estimate, std.error, p.value) %>%
-  head(13)
+  head(14)
 
-stargazer(imp_3_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Ideology Control}")
+imp_3_rp_sum_table_vars <- tibble(
+  Variable = c("Intercept", "White/Nonwhite Seg. Index", "Diversity", "% Asian", "% Black", "% Latino",
+               "Median Income (1000s)", "% Renters", "% College Grads", "Biracial Elec.", "Nonpartisan Elec.", "Primary Elec.", "Pop (logged)", "White Ideology"),
+  Estimate = round(imp_3_rp_sum_table$estimate, 3),
+  `Std. Error` = round(imp_3_rp_sum_table$std.error,3),
+  `P-Value` = round(imp_3_rp_sum_table$p.value, 3)
+  )
+
+kable(imp_3_rp_sum_table_vars, "latex", caption = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Ideology Control}", booktabs = T) %>%
+  row_spec(0, bold = TRUE) %>%
+  footnote(general = c("This table shows the results of Trounstine's third model for the effect of segregation on political polarization",
+  "(racial vote divide) using the two-group Theil's H segregation Index and including controls for ideology",
+  "using the new, multiply imputed datasets. Compared to Trounstine's original results, the main coefficient on segregation index has decreased in",
+  "magnitude although, it remains statistically significant. The other coefficients except for the biracial",
+  "indicator are insignificant, and the coefficients on percent Asian and Black have switched signs.",
+  "Standard errors have also reduced slightly in these specifications compared to the original analysis",
+  "in Trounstine (2016)."),
+           general_title = "Table 3:") %>%
+  kable_styling(full_width = TRUE)
+
 ```
@@
                 notes.align = "l",
-                #column.sep.width = "-10pt",
                 font.size = "small")

### 2020-05-03 Final_Draft.Rmd
changes to city size threshold analysis

@@
   footnote(general = c("This table shows the results of Trounstine's first model for the effect of segregation on political polarization",
-  "(racial vote divide) using the multi-group Theil's H segregation Index using the new, multiply imputed datasets.",
-  "The sign of the coefficient on the main variable of interest, the segregation index, is the same, but the",
-  "result has become statisically insignificant with the 95% confidence interval containing zero. Thus",
+  "(racial vote divide) using the multi-group Theil's H segregation Index using the new, multiply imputed",
+  "datasets. The sign of the coefficient on the main variable of interest, the segregation index, is the same, but",
+  "the result has become statisically insignificant with the 95% confidence interval containing zero. Thus",
   "while these results still suggest that segregation may be associated with increased political polarization,",
-  "they confer a lesser degree of certainty than Trounstine's original analysis. The coefficients for %",
-  "Black population, % Latino population, and median household income have also switched signs. The coefficient",
+  "they confer a lesser degree of certainty than Trounstine's original analysis. The coefficients for % Black",
+  "population, % Latino population, and median household income have also switched signs. The coefficient",
   "on the indicator for a primary election, has also changed from being significant in the original analysis",
@@
   "(racial vote divide) using the two-group Theil's H segregation Index and including controls for ideology",
-  "using the new, multiply imputed datasets. Compared to Trounstine's original results, the main coefficient on segregation index has decreased in",
-  "magnitude although, it remains statistically significant. The other coefficients except for the biracial",
-  "indicator are insignificant, and the coefficients on percent Asian and Black have switched signs.",
-  "Standard errors have also reduced slightly in these specifications compared to the original analysis",
-  "in Trounstine (2016)."),
+  "using the new, multiply imputed datasets. Compared to Trounstine's original results, the main coefficient on",
+  "segregation index has decreased in magnitude although, it remains statistically significant. The other",
+  "coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian and",
+  "Black have switched signs. Standard errors have also reduced slightly in these specifications compared to",
+  "the original analysis in Trounstine (2016)."),
            general_title = "Table 3:") %>%

### 2020-05-03 final_draft_extension_fs.Rmd
changes to city size threshold analysis

--- 2020-04-30 Draft_1.Rmd
@@
 library(haven)
-library(gtable)
 library(stargazer)
 library(tidyverse)
-library(gt)
 library(gtsummary)
 library(knitr)
-library(stargazer)
+library(AER)
 library(lme4)
 library(margins)
-library(reprex)
-library(plm)
-library(devtools)
 library(lfe)
-library(Statamarkdown)
 library(readxl)
-library(starpolishr)
-library(AER)
-library(readxl)
-library(naniar)
 library(mice)
-library(gtsummary)
 library(VIM)
+library(kableExtra)
+library(huxtable)
 ```
@@
 
-rp <- read_dta("racial_polarization_winners.dta")
+#rp <- read_dta("racial_polarization_winners.dta")
 fin_seg<- read_dta("fin_seg.dta")
-
-# add row numbers for fin_seg
-
-fin_seg$row_num <- as.integer(rownames(fin_seg))
-
-```
-
-```{r data_cleaning_rp, include = FALSE}
-
-# create a factor for year for the rp dataset
-rp$year.f <- as.factor(rp$year)
-
-# apply the condition that winner == 1 as in the Stata code for the rp regressions
-
-rp_1<- rp %>%
-  filter(winner == 1) %>%
-  mutate(medincinterp = medincinterp/1000)
 
@@
 
-```{r rp_missing_plot, include = FALSE, warning = FALSE}
-
-# don't show the warning, it's just an irrelevant column missing a name
-
-# plot the missing variables if desired
-
-rp_facet <- rp_impute %>%
-   select("medincinterp",
-             "biggestsplit", "diversityinterp",
-             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
-             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
-               "south", "midwest", "west", "whiteideology_fill2", "year")
-
-gg_miss_var(rp_impute, show_pct = TRUE) +
-  ggtitle("% Missing Values in Trounstine (2016)'s Racial Polarization Dataset")
-
-nrow(rp_impute)
-
-```
-
-```{r rp_aggr_plot, echo = FALSE}
-
-# select only the missing values
-
-rp_aggr <- rp_impute %>%
-   select("medincinterp",
-             "biggestsplit", "diversityinterp",
-             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
-             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
-               "south", "midwest", "west", "whiteideology_fill2")
-
-# create an aggr plot for the missing values
-
-aggr(rp_aggr, bars = TRUE, col=c('navyblue','red'), numbers=TRUE, cex.axis=.5, gap=1, ylab=c("Proporiton of Missing Values","Combinations"))
-
-# caption for this plot when I figure out how to do it...
-: This plot examines the pattern of missing data in the the original racial polarization dataset from Trounstine (2016).
-The plot on the left shows the percentage of missing data for each variable with missing data and reveals that the variables that are missing by far the most data are the largest vote split along racial lines (biggestsplit) and the variable indicating whether or not the election had candidates of more than one race (biracial).
-The plot on the right shows the pattern of missingness among the variables.
-We can see that approximately 42% of observations are complete (have no missing values).
-There seems to be a correspondence between missing a value for biggest split and missing biracial.
-There also seem to be about 2% of values for which most of the variables are missing.
-However, most observations are not missing more than 2-3 values.
-
-```
-
 In figure X2, we can similarly observe the trends for the financial segregation dataset.
@@
 
-```{r fin_missing_plot, include = FALSE}
-
-miss_var_summary(fin_imp)
-
-gg_miss_var(fin_imp, show_pct = TRUE)
-
-```
-
-```{r fin_aggr_plot, echo = FALSE}
-
-# select all variables with missing values for the aggr plot
-
-fin_imp_aggr <- fin_imp %>%
-  select(ideology_fill, H_citytract_NHW_i, chng5pctblk, chng5pctlatino, chng5pctasian,
-         diversityinterp, pctblkpopinterp, pctasianpopinterp,
-         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
-         pctcollegegradinterp)
-
-new_try <- head(fin_imp_aggr, 20)
-
-aggr(new_try, plot = TRUE, bars = FALSE, col=c('navyblue','red'), numbers=TRUE)
-
-# create the aggr plot
-
-aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.5, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
-title(main = "Patterns of Missingness in the Financial Segregation Data",
-      sub = "")
-
-# this plot tells us that only .58% of the data are complete (not missing anything)
-
-# caption for this plot when I figure out how to do it...
-: This plot examines the pattern of missing data in the the original financial segregation dataset from Trounstine (2016).
+```{r fin_aggr_plot, echo = FALSE, fig.cap = "This plot examines the pattern of missing data in the the original financial segregation dataset from Trounstine (2016).
 The plot on the left shows the percentage of missing data for each variable with missing data and reveals that a large number of variables are missing the vast majority of data.
 The plot on the right shows the pattern of missingness among the variables.
-We can see that only .58% of observations are complete (have no missing values), and a large majority of the observations are missing data for many variables.
+We can see that only .58\\% of observations are complete (have no missing values), and a large majority of the observations are missing data for many variables.", fig.width= 7, fig.height = 5, fig.pos="H", eval = FALSE}
+
+# select all variables with missing values for the aggr plot
+
+fin_imp_aggr <- fin_imp %>%
+  select(ideology_fill, H_citytract_NHW_i, chng5pctblk, chng5pctlatino, 
+         chng5pctasian, diversityinterp, pctblkpopinterp, pctasianpopinterp,
+         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp,
+         pctover65, pctcollegegradinterp) %>%
+    rename("White Ideology" = ideology_fill, "White/Non-White H Index" = H_citytract_NHW_i,
+           "5Y Change % Black" = chng5pctblk, "5Y Change % Latino" = chng5pctlatino, 
+           "5Y Change % Asian" = chng5pctasian, "Diversity" = diversityinterp, 
+           "% Asian" = pctasianpopinterp, "% Black" = pctblkpopinterp, 
+           "% Latino" = pctlatinopopinterp, "Median HH Income" = medinc_cpi,
+           "% Local Gov. Worker" = pctlocalgovworker_100, "% Renters" = pctrentersinterp, 
+           "% College Grads" = pctcollegegradinterp, "% 65+" = pctover65)
+
+new_try <- head(fin_imp_aggr, 20)
+
+# create the aggr plot
+
+aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.4, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
+title(main = "Patterns of Missingness in the Financial Segregation Data",
+      sub = "", font.main = 1, font.axis = 1, cex.main = 1, line = 3,  oma = c(1,3,5,1), font.main = 1, font.axis = 1)
+# this plot tells us that only .58% of the data are complete (not missing anything)
 
@@
 
-```{r rp_imputation, include = FALSE}
-
-# Perform multiple imputations using the cart method. Because of the time it
-# takes to run this function, I turned the results into a dataset to load in
-# instead of re-running everytime.
-
-max_it = 20
-
-imp_1_rp <- mice(rp_impute, method = "cart", maxit = 20)
-
-# can use the line below to check that there are now no missing values
-
-# gg_miss_var(complete(imp_1_rp), show_pct = TRUE)
-
-```
-
 ```{r fp_imputations_original, include = FALSE}
@@
 See figures X and X1 to see the density plots of the imputed values overlayed on the density plots of the original variables.
-The rest of the plots and results of the diagnostic tests discussed here are presented in the Appendix.
-
-```{r rp_densityplot, echo = FALSE}
-
-densityplot(imp_1_rp)
-
-```
-
-```{r rp_imp_plot, include = FALSE}
-
-# ideally, the fits will intertwine and not exhibit any trends at later iterations.
-This seems to generally be the case.
-There are some issues with the results for some of the variables with very few missing values, which makes sense as we would expect the mean to be less reliable due to the law of large numbers and thus convergence is more difficult.
-However, since these are so few values, it is less important about how robust they are.
-
-plot(imp_1_rp)
-
-```
-
-```{r rp_stripplot, include = FALSE}
-
-# we can also check the imputed values against the original values using stripplot().
-Each column in each subplot represents a separate iteration.
-The magenta points represent the imputed data.
-The values of the variable in questions are along the y axis.
-We expect the spread of the data to be similar if the imputations were done well.
-If the data were missing completely at random, then the imputed data should have the same distribution as the original data.
-In particular, we want to be sure that the imputations are within a plausible range of the data.
-This is the case for all of our imputed variables, and there does not seem to be cause for alarm from these results.
-
-# this looks good? All reasonable values...
-
-stripplot(imp_1_rp)
-
-stripplot(imp_1_rp, biggestsplit)
-
-```
-
-```{r fs_densityplot, echo = FALSE}
-
-densityplot(imp_fs)
-densityplot(x=imp_fs , data= ~ H_citytract_NHW_i + chng5pctblk + 
-       chng5pctlatino + chng5pctasian + ideology_fill)
-
-```
-
-```{r fs_imp_plot, include = FALSE}
-
-# ideally, the fits will intertwine and not exhibit any trends at later iterations.
-This seems to generally be the case.
-There are some issues with the results for some of the variables with very few missing values, which makes sense as we would expect the mean to be less reliable due to the law of large numbers and thus convergence is more difficult.
-However, since these are so few values, it is less important about how robust they are.
-
-plot(imp_fs)
-
-```
-
-```{r fs_stripplot, include = FALSE}
-
-# we can also check the imputed values against the original values using stripplot().
-Each column in each subplot represents a separate iteration.
-The magenta points represent the imputed data.
-The values of the variable in questions are along the y axis.
-We expect the spread of the data to be similar if the imputations were done well.
-If the data were missing completely at random, then the imputed data should have the same distribution as the original data.
-In particular, we want to be sure that the imputations are within a plausible range of the data.
-This is the case for all of our imputed variables, and there does not seem to be cause for alarm from these results.
-
-# this looks good? All reasonable values...
-
-stripplot(imp_fs, H_citytract_NHW_i)
-
-stripplot(imp_fs, chng5pctblk)
-
-stripplot(imp_fs, chng5pctlatino)
-
-stripplot(imp_fs, chng5pctasian)
-
-stripplot(imp_fs, ideology_fill)
+The code to generate the rest of the plots and results of the diagnostic tests discussed here are presented in the Appendix.
+
+```{r fs_densityplot, echo = FALSE, eval = FALSE}
+
+my.settings <- list(
+  par.main.text = list(font = 1, cex = 1)
+)
+
+#densityplot(imp_fs)
+densityplot(x = imp_fs , 
+            data = ~ H_citytract_NHW_i + chng5pctblk + chng5pctlatino + chng5pctasian + ideology_fill,
+            main = "Density Plots of Imputed and Original Data by Variable\nin the Financial Segregation Dataset",
+            par.settings = my.settings,
+            par.strip.text = list(cex = 1))
 
@@
 Given the promising results of the diagnostic checks, I next proceeded to re-estimate the original model using the multiply imputed datasets, pooling the results to produce final pooled regression coefficients and parameters.
-The results for the analyses using the racial polarization dataset are presented in tables 1-3.
-
-```{r rp_imputations, include = FALSE}
-
-# Now that we have imputed the missing data, we can re-run the analyses from the
-# original paper to see how and if this changes the analysis. We can use the
-# with() function from the mice package to fit each of the imputed datasets to
-# the model and then pool the results afterwards.
-
-# regression 1: fit multiple imputed datasets
-
-fit_imp_1_rp <- with(imp_1_rp, lmer(formula = biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
-
-# pool and summarize the analyses
-
-pool_imp_1_rp <- pool(fit_imp_1_rp)
-imp_1_rp_sum <- summary(pool_imp_1_rp)
-
-## regression 2 Table 1: fit multiple imputed datasets
-
-#formula = biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2)
-
-fit_imp_2_rp <- with(imp_1_rp, lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
-
-# pool and summarize the analyses
-
-pool_imp_2_rp <- pool(fit_imp_2_rp)
-imp_2_rp_sum <- summary(pool_imp_2_rp)
-
-## regression 3 Table 1 with new data
-
-#formula = biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2)
-
-fit_imp_3_rp <- with(imp_1_rp, lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
-
-# pool and summarize the analyses
-
-pool_imp_3_rp <- pool(fit_imp_3_rp)
-imp_3_rp_sum <- summary(pool_imp_3_rp)
-
-```
+The results for the analyses using the racial polarization dataset are presented in tables X1-X3.
 
@@
 
-```{r results_printing_rp_impute_regressions_1, results = "asis", echo=FALSE}
-
-# print results of 1st regression
-
-imp_1_rp_sum_table <- as.data.frame(imp_1_rp_sum %>% 
-  select(term, estimate, std.error, p.value)) %>%
-  head(13)
-print(imp_1_rp_sum_table)
-
-stargazer(imp_1_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Multigroup Segregation Index}")
-
-```
-
-In the second and third regressions, the results are similar.
+In the second regression, the results are similar.
 The main coefficient on segregation index has decreased in magnitude, although in these specifications, it remains statistically significant.
-The other coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian, Black, and Latino have all switched signs.
-Standard errors have also reduced slightly in these specifications compared to the original analysis in @trounstine_segregation_2016.
-
-```{r results_printing_rp_impute_regressions_2, results = "asis", echo=FALSE}
-
-# print results of 2nd regression
-
-imp_2_rp_sum_table <- as.data.frame(imp_2_rp_sum %>% 
-  select(term, estimate, std.error, p.value)) %>%
-  head(13)
-print(imp_2_rp_sum_table)
-
-stargazer(imp_2_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Two-Group Segregation Index}")
-
-```
-
-```{r results_printing_rp_impute_regressions_3, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_3_rp_sum_table <- as.data.frame(imp_3_rp_sum %>% 
-  select(term, estimate, std.error, p.value)) %>%
-  head(13)
-print(imp_3_rp_sum_table)
-
-stargazer(imp_3_rp_sum_table,
-          header = FALSE,
-          title = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Ideology Control}")
-```
-
-For the financial segregation dataset, we similarly fit each of our 5 imputed datasets to the original models from @trounstine_segregation_2016 using this data and then pool the results for each.
-The pooled results are presented in tables 4-6.
-
-# FS data results
+The other coefficients except for the biracial indicator are insignificant, and the coefficients on percent Black, percent Latino, and median household income have all switched signs.
+
+In the third regression, like in the second, the main coefficient on segregation index has decreased in magnitude but remains significant.
+The other coefficients except for the biracial indicator are insignificant, and the coefficients on percent Black, percent Asian, median income, and logged population have switched signs.
+In all three of the specifications, tandard errors reduced slightly using the larger, multiply imputed datasets compared to the original analysis with the original data in @trounstine_segregation_2016.
 
@@
 
-# print results of 3rd regression
+# print results of 1st regression
 
@@
   select(term, estimate, std.error, p.value))
-print(imp_felm1_sum_table)
-
-stargazer(imp_felm1_sum_table,
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Expenditure per Capita}")
+
+imp_felm1_sum_table_vars <- tibble(
+  Variable = c("White/Nonwhite Seg. Index", "Diversity", "% Black", "% Asian", "% Latino", "Median Income (1000s)", "% Local Gov. Worker", "% Renters", "% 65+", "% College Grads", "Pop (logged)"),
+  Estimate = round(imp_felm1_sum_table$estimate, 3),
+  `Std. Error` = round(imp_felm1_sum_table$std.error,3),
+  `P-Value` = round(imp_felm1_sum_table$p.value, 3)
+)
+
+kable(imp_felm1_sum_table_vars, "latex",
+      caption = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Expenditure per Capita}",
+      booktabs = T) %>%
+    row_spec(0, bold = TRUE) %>%
+  footnote(general = c("This table shows the results of Trounstine's first model for the effect of segregation on per capita",
+  "direct public expenditure using the two-group Theil's H Segregation Index using the new, multiply imputed datasets.",
+  "The results present a stark contrast to Trounstine's original results: the main coefficient on segregation index",
+  "has decreased to essentially zero and has become statistically insignificant. The very large P-Value may indicate there is",
+  "a larger difference between the two models. The coefficient on diversity has increased in magnitude and become",
+  "statistically significant."),
+           general_title = "Table 4:") %>%
+  kable_styling(full_width = TRUE)
+
 ```
@@
 
-# print results of 3rd regression
+# print results of 2nd regression
 
@@
   select(term, estimate, std.error, p.value))
-print(imp_felm2_sum_table)
-
-stargazer(imp_felm1_sum_table,
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Changing Demographics}")
+
+imp_felm2_sum_table_vars <- tibble(
+  Variable = c("White/Nonwhite Seg.
+Index", "% Black", "% Asian", "% Latino", "5Y Change % Black", "5Y Change % Latino", "5Y Change % Asian", "Median Income (1000s)", "% Local Gov.
+Worker", "% Renters", "% 65+", "% College Grads", "Pop (logged)"),
+  Estimate = round(imp_felm2_sum_table$estimate, 3),
+  `Std. Error` = round(imp_felm2_sum_table$std.error,3),
+  `P-Value` = round(imp_felm2_sum_table$p.value, 3)
+)
+
+kable(imp_felm2_sum_table_vars, "latex",
+      caption = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Changing Demographics}",
+      booktabs = T) %>%
+    row_spec(0, bold = TRUE) %>%
+  footnote(general = c("This table shows the results of Trounstine's second model for the effect of segregation on per capita",
+  "direct public expenditure using the two-group Theil's H Segregation Index using the new, multiply imputed datasets.",
+  "Again, in contrast to Trounstine's original results, the main coefficient on segregation index has decreased to",
+  "essentially zero and has become statistically insignificant with a very large P-Value."),
+           general_title = "Table 5:") %>%
+  kable_styling(full_width = TRUE)
+
 ```
@@
   select(term, estimate, std.error, p.value))
-print(imp_felm3_sum_table)
-
-stargazer(imp_felm1_sum_table,
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Ideology Control}")
-```
-
-# FS NEW data results
-
-```{r new_fs_imputation_tries, include = FALSE}
-# Main Analysis 2: Imputations
-
-## regression 1 Table 2
-
+
+imp_felm3_sum_table_vars <- tibble(
+  Variable = c("White/Nonwhite Seg.
+Index", "Diversity", "% Black", "% Asian", "% Latino", "Median Income (1000s)", "% Local Gov.
+Worker", "% Renters", "% 65+", "% College Grads", "Pop (logged)", "Ideology"),
+  Estimate = round(imp_felm3_sum_table$estimate, 3),
+  `Std. Error` = round(imp_felm3_sum_table$std.error,3),
+  `P-Value` = round(imp_felm3_sum_table$p.value, 3)
+)
+
+kable(imp_felm3_sum_table_vars, "latex",
+      caption = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Ideology Control}",
+      booktabs = T) %>%
+    row_spec(0, bold = TRUE) %>%
+  footnote(general = c("This table shows the results of Trounstine's third model for the effect of segregation on political polarization",
+  "(racial vote divide) using the two-group Theil's H segregation Index and including controls for ideology",
+  "using the new, multiply imputed datasets. Compared to Trounstine's original results, the main coefficient on",
+  "segregation index has decreased in magnitude although, it remains statistically significant. The other",
+  "coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian and",
+  "Black have switched signs. Standard errors have also reduced slightly in these specifications compared to",
+  "the original analysis in Trounstine (2016)."),
+           general_title = "Table 6:") %>%
+  kable_styling(full_width = TRUE)
+
+```
+
+```{r population_over_Baqir, include = FALSE}
+
+# Baqir et al uses city as population above 25,000
+
+baqir <- log(25000)
+
+fin_imp_pop_over_baqir <- fin_imp %>%
+  filter(logpop > baqir )
+
+nrow(fin_imp_pop_over_baqir)
+
+gg_miss_var(fin_imp_pop_over_baqir, show_pct = T)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_pop_over_baqir, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_fs_pop_overbaqir <- mice(fin_imp_pop_over_baqir, method = meth, maxit = 5)
+
+```
+
+```{r over_baqir_fit, include = FALSE}
 # fit multiple imputed datasets
 
-fit_imp_felm1 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+fit_over_baqir_1 <- with(imp_fs_pop_overbaqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
 
@@
 
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
+pool_fit_over_baqir_1 <- pool(fit_over_baqir_1)
+imp_over_baqir_1_sum <- summary(pool_fit_over_baqir_1)
 
@@
 
-fit_imp_felm2 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+fit_over_baqir_2 <- with(imp_fs_pop_overbaqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
 
@@
 
-pool_imp_felm2 <- pool(fit_imp_felm2)
-imp_felm2_sum <- summary(pool_imp_felm2)
+pool_fit_over_baqir_2 <- pool(fit_over_baqir_2)
+imp_over_baqir_2_sum <- summary(pool_fit_over_baqir_2)
 
@@
 
-fit_imp_felm3 <- with(new_imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))
+fit_over_baqir_3 <- with(imp_fs_pop_overbaqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))
 
@@
 
-pool_imp_felm3 <- pool(fit_imp_felm3)
-imp_felm3_sum <- summary(pool_imp_felm3)
-
-# INTERPRETATION BEFORE AFTER CHANGED The results of the first regression present a stark difference to the results of @trounstine_segregation_2016.
-Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant.
-Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
-The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.
-
-print(imp_felm1_sum)
-print(imp_felm2_sum)
-print(imp_felm3_sum)
-
-# large amount of data missing across the board in terms of years
-
-gg_miss_var(fin_dge, facet = year, show_pct = TRUE)
-
-# can't really tell anything about the region facet since a lot of obs missing region data
-
-gg_miss_var(fin_imp_extra, facet = region, show_pct = TRUE)
-
-# not necessarily a significant pattern across states either
-
-gg_miss_var(fin_imp_extra, facet = statecode, show_pct = TRUE)
-
-```
-
-# FS NEW AGAIN
-
-```{r}
-cities_to_keep <- c("Austin City", "Baltimore City", "Charlotte City", "Chicago City", "Cleveland City", "Columbus City", "Dallas City", "Denver City", "Detroit City", "Houston City", "Indianapolis", "Jacksonville", "Los Angeles City", "Memphis City", "Milwaukee City", "New York City", "Oklahoma City City", "Philadelphia City", "Phoenix City", "San Antonio City", "San Diego City", "San Francisco City", "San Jose City", "Tucson City", "Washington City")
-
-# apply the conditions in Stata regression to the fin_seg dataset
-
-fin_imp_cities <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0, cityname %in% cities_to_keep) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-# select the relevant variables to be imputed
-
-fin_imp <- fin_imp %>%
-  select(H_citytract_NHW_i, dgepercap_cpi, diversityinterp, pctblkpopinterp, pctasianpopinterp,
-         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
-         pctcollegegradinterp, logpop, geo_id2, chng5pctblk, chng5pctlatino, chng5pctasian,
-         ideology_fill)
-```
-
-```{r looking_at_original_data, include = FALSE}
-
-range(fin_seg$totaltractsf, na.rm = T)
-
-# histogram of tracts in full sample:
+pool_fit_over_baqir_3 <- pool(fit_over_baqir_3)
+imp_over_baqir_3_sum <- summary(pool_fit_over_baqir_3)
+# doesn't add very much to the sample though, still, robust to additional 73 entries
+
+miss_var_summary(complete(imp_fs_pop_overbaqir))
+
+5039 - 4966
+
+```
+
+```{r population_under_Baqir, include = FALSE}
+
+# Baqir et al uses city as population above 25,000
+
+baqir <- log(25000)
+
+fin_imp_pop_under_baqir <- fin_imp %>%
+  filter(logpop < baqir )
+
+nrow(fin_imp_pop_under_baqir)
+
+gg_miss_var(fin_imp_pop_under_baqir, show_pct = T)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_pop_under_baqir, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_fs_pop_under_baqir <- mice(fin_imp_pop_under_baqir, method = meth, maxit = 1)
+
+```
+
+```{r population_under_Baqir_fitting, include = FALSE}
+
+# fit multiple imputed datasets
+
+fit_under_baqir_1 <- with(imp_fs_pop_under_baqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fit_under_baqir_1 <- pool(fit_under_baqir_1)
+imp_under_baqir_1_sum <- summary(pool_fit_under_baqir_1)
+
+## regression 2 Table 2
+
+# fit multiple imputed datasets
+
+fit_under_baqir_2 <- with(imp_fs_pop_under_baqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fit_under_baqir_2 <- pool(fit_under_baqir_2)
+imp_under_baqir_2_sum <- summary(pool_fit_under_baqir_2)
+
+## Regression 3 Table 2
+
+fit_under_baqir_3 <- with(imp_fs_pop_under_baqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fit_under_baqir_3 <- pool(fit_under_baqir_3)
+imp_under_baqir_3_sum <- summary(pool_fit_under_baqir_3)
+# doesn't add very much to the sample though, still, robust to additional 73 entries
+
+miss_var_summary(complete(imp_fs_pop_overbaqir))
+
+5039 - 4966
+
+```
+
+```{r over_baqir_t1, echo = FALSE}
+
+# print results of 1st regression
+
+imp_over_baqir_1_sum_table <- as.data.frame(imp_over_baqir_1_sum %>% 
+  select(term, estimate, std.error, p.value))
+
+imp_over_baqir_1_sum_table_vars <- tibble(
+  Variable = c("White/Nonwhite Seg. Index", "Diversity", "% Black", "% Asian", "% Latino", "Median Income (1000s)", "% Local Gov. Worker", "% Renters", "% 65+", "% College Grads", "Pop (logged)"),
+  Estimate = round(imp_over_baqir_1_sum_table$estimate, 3),
+  `Std. Error` = round(imp_over_baqir_1_sum_table$std.error,3),
+  `P-Value` = round(imp_over_baqir_1_sum_table$p.value, 3)
+)
+
+kable(imp_over_baqir_1_sum_table_vars, "latex",
+      caption = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Expenditure per Capita}",
+      booktabs = T) %>%
+    row_spec(0, bold = TRUE) %>%
+  footnote(general = c("This table shows the results of Trounstine's third model for the effect of segregation on political polarization",
+  "(racial vote divide) using the two-group Theil's H segregation Index and including controls for ideology",
+  "using the new, multiply imputed datasets. Compared to Trounstine's original results, the main coefficient on",
+  "segregation index has decreased in magnitude although, it remains statistically significant. The other",
+  "coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian and",
+  "Black have switched signs. Standard errors have also reduced slightly in these specifications compared to",
+  "the original analysis in Trounstine (2016)."),
+           general_title = "Table 6:") %>%
+  kable_styling(full_width = TRUE)
+
+```
+
+```{r histograms_city_pop_in_specifications}
+
+pop_data_over_baqir <- tibble(
+  log_pop = complete(imp_fs_pop_overbaqir,1)$logpop,
+  id = "over_baqir"
+)
+
+pop_data_under_baqir <- tibble(
+  log_pop = complete(imp_fs_pop_under_baqir, 1)$logpop,
+  id = "under_baqir"
+)
+
+pop_data_imp_fs <- tibble(
+  log_pop = complete(imp_fs, 1)$logpop,
+  id = "imp_fs"
+)
+
+pop_data_fin_dge <- tibble(
+  log_pop = fin_dge$logpop,
+  id = "fin_dge"
+)
+
+pop_data_fin_seg <- tibble(
+  log_pop = fin_seg$logpop,
+  id = "fin_seg"
+)
+
+pop_hist_data <- rbind(pop_data_over_baqir, pop_data_imp_fs)
+pop_hist_data <- rbind(pop_hist_data, pop_data_under_baqir)
+pop_hist_data <- rbind(pop_hist_data, pop_data_fin_dge)
+pop_hist_data <- rbind(pop_hist_data, pop_data_fin_seg)
+
+pop_hist_data %>%
+  ggplot(aes(x = log_pop)) +
+  geom_histogram(aes(color = id)) +
+  facet_wrap(~id)
+
+pop_hist_data %>%
+  ggplot(aes(x = log_pop)) +
+  geom_density(aes(color = id)) +
+  facet_wrap(~id)
+
+range(fin_seg$population)
 
 fin_seg %>%
-  ggplot() +
-  geom_histogram(aes(x = totaltractsf))
-
-range(fin_seg$logpop, na.rm = T)
-
-# histogram of tracts in full sample:
+  filter(fin_seg$logpop == 0)
 
 fin_seg %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-# add back in year, region, and statecode to be able to look at this
-
-fin_imp_old <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-fin_imp_extra <- fin_imp %>%
-  mutate(year = fin_imp_old$year,
-         region = fin_imp_old$region,
-         statecode = fin_imp_old$statecode)
-
-# large amount of data missing across the board in terms of years
-
-gg_miss_var(fin_imp_extra, facet = year, show_pct = TRUE)
-
-# can't really tell anything about the region facet since a lot of obs missing region data
-
-gg_miss_var(fin_imp_extra, facet = region, show_pct = TRUE)
-
-# not necessarily a significant pattern across states either
-
-gg_miss_var(fin_imp_extra, facet = statecode, show_pct = TRUE)
-
-```
-
-```{r looking_at_Trounstine_data, include = FALSE}
-
-# basic filter for table for all regressions
-
-# xtreg dgepercap_cpi H_citytract_NHW_i diversityinterp pctblkpopinterp
-# pctasianpopinterp pctlatinopopinterp medinc_cpi pctlocalgovworker_100
-# pctrentersinterp pctover65 pctcollegegradinterp logpop if totaltracts>1 &
-# dgepercap_cpi~=0,fe vce(cluster geo_id2)
-
-fin_trounstine <-fin_seg %>%
-  filter(totaltractsf >1 | is.na(totaltractsf)) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
-
-# create dge variable used in regression
-
-fin_dge_trounstine <-fin_trounstine %>% filter(dgepercap_cpi != 0)
-
-range(fin_dge_trounstine$totaltractsf, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_dge_trounstine %>%
-  ggplot() +
-  geom_histogram(aes(x = totaltractsf))
-
-range(fin_dge_trounstine$logpop, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_dge_trounstine %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
-
-```
-
-```{r looking_at_imputed_data}
-
-fin_new_imp <- complete(new_imp_fs) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
-
-range(fin_new_imp$logpop, na.rm = T)
-
-# histogram of tracts in full sample:
-
-fin_new_imp %>%
-  ggplot() +
-  geom_histogram(aes(x = logpop))
+  filter(populationinterp < 25000)
 
@@
 
-```{r felm, include = FALSE}
-
-# Main Analysis 2
-
-## regression 1 Table 2
-
-# The following is a fixed effects model regression with clustering around
-# geo_id2. It mandates that total census tracts in the city is greater than 1,
-# which we want because our measure of evenness of racial spread is constant for
-# cities with only one tract by our definition (which requires comparing tracts
-# within cities). It also mandates that Direct General Expenditures (DGE) per
-# capita, CPI adjusted is not equal to 0, which would be problematic and
-# indicate a potential data error. This regression regresses the DGE per capita
-# on the the two-group calculation of  Theil's H interpolated. Controls are
-# included for diversity and the % populations of Blacks, Asians, and Latinos to
-# help identify whether it is actually diversity that drives down spending.These
-# demographic controls also help to account for the fact that whites and
-# minorities tend to perfer different levels of government spending in general.
-# This will help isolate the effects of segregation v. other forms of diversity
-# on public spending. Other controls for Median household income, CPI adjusted,
-# percent over 65, percent college grads, percent local government workers, log
-# population help control for additional factors related to segregation and
-# expenditure. Controls for percent renters interpolated and Median household
-# income also help to control for the general wealth of cities, which could be a
-# potential driver of public spending. Fixed effects for cities are also
-# included  so that the author can examine the effect of segregation in the same
-# city over  time, which also helps control for many other factors not otherwise
-# taken into account (such as city age)
-
-# apply the conditions in Stata regression
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-# felm(y~x | factor(fe1) + factor(fe2) | 0 | clustervar)
-
-felm1 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-## regression 2 Table 2
-
-# This regression is the same as above except instead of using diversity, a new
-# control is added for the five year changes in racial group shares. The goal
-# here is to see whether or not changes in diversity are a driving factor
-# (rather than absolute levels of diversity).
-
-felm2 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-## Regression 3 Table 2
-
-# Column 3
-
-# As in column 3 of table 1, this regression simply adds in a control for  mean  ideology of city residents from General Social Survey (GSS) to control for the  possibility that ideology that segregated cities are more ideologically  conservative and that the conservative nature of segregated cities is what actually drives the effect.
-
-felm3 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-```
-
-```{r main_fp_tables, results = "asis", echo = FALSE}
-
-# create main table for table 3
-
-table2 <- stargazer(felm1, felm2, felm3, omit = c("year", "south", "midwest", "west"), 
-                    header = FALSE,
-                    title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures}",
-                covariate.labels = c("White/Nonwhite H Index", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Change Percent Black", "Change Percent Latino", "Change Percent Asian", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Population (logged)", "White Ideology", "Constant"))
-
-```
-
-```{r, include = FALSE}
-
-# Main Analysis 3
-
-## regression 1 Table 3
-
-# Column 1
-
-# The following is a fixed effects model regression with clustering once again around geo_id2.
-Again, the if statements at the end mandate that total census tracts in the city is greater than 1, which we want because our measure of evenness of racial spread is constant for cities with only one tract by our definition (which requires comparing tracts within cities).
-They also mandate that the highways per capita, CPI adjsuted with no cap extend (lagged 5 years) is not equal to 0, which would be problematic and indicate a potential data error.
-The dependent variable here is highways per capita, CPI adjsuted with no cap extend (lagged 5 years) and it is regressed on the two group calculation of Theil's H, interpolated.
-Controls are added for diversity, percent population of Blacks, Asians, and Latinos, and median household CPI adjusted income as well as for % local government worker hundreds, percent rentership, percent over 65, percent college graduates, and the log of the population.
-This essentially examines the effect of segregation on the specific public good of highways.
-As in the previous table's regressions, fixed effects for cities are also included so that the author can examine the effect of segregation in the same city over time, which also helps control for many other factors not otherwise taken into account (such as city age) *
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), highwayspercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_1 <- felm(highwayspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-## regression 2 Table 3
-
-# Column 2
-
-# This is the same regression as column 1, but this time the dependent variable
-# is police per capita, CPI adjusted with no cap extend. This essentially
-# examines the effect of segregation on the specific public good of police per
-# capita.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), policepercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_2 <- felm( policepercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 3
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), parkspercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-# This is again the same regression, but this time the dependent variable is
-# parks per capita, CPI adjusted with no cap extend. This essentially examines
-# the effect of segregation on the specific public good of parks.
-
-felm2_3 <- felm(parkspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 4
-
-# This is again the same regression, but this time the dependent variable is
-# sewers per capita, CPI adjusted with no cap extend. This essentially examines
-# the effect of segregation on the specific public good of sewers.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), sewerspercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_4 <- felm(sewerspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 5
-
-# This is again the same regression, but this time the dependent variable is
-# Welfare, Health, Housing per capita, CPI adjusted, no cap expend. This
-# essentially examines the effect of segregation on the specific public good of
-# welfare and housing.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), welfhoushealthNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_5 <- felm(welfhoushealthNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 6
-
-# This is again the same regression, but this time the dependent variable is own
-# source of general revenue per capita, CPI adjusted. This essentially examines
-# the effect of segregation on the specific public good of own source revenue.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), genrevownpercap_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_6 <- felm(genrevownpercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-```
-
-```{r results = "asis", echo = FALSE}
-table3a <- stargazer(felm2_1, felm2_2, felm2_3, 
-          omit = c("year", "south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Public Goods A}",
-          covariate.labels = c("White/Nonwhite H Index", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Population (logged)", "Constant"))
-
-table3b <- stargazer(felm2_4, felm2_5, felm2_6, 
-          omit = c("year", "south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on Public Goods B}")
-
-#star_sidewaystable(table3)
-```
-
-```{r iv_regs, include = FALSE}
-
-## regression 1 Table 5
-
-# Top Row
-
-# Column 1
-
-# This is an instrumental variable regression with DGE per capita, adjusted by the CPI, as the dependent variable and total number of waterways as the instrumental variable for segregation.
-The instrument includes the log of the population in the first stage because the number of waterways is positively correlated to population and population is positively correlated with segregation.
-The control variables are the same as those in the regressions for Table 2 except for 2 changes: since the number of waterways does not change, there is no need for city fixed effects.
-Instead, we include fixed effects for the region and year.
-A lagged version of the dependent variable (dgepercap_cpilag) is added to the regressions to account for the high correlation between  observations for the same city over time and because changes in local budgets typically are incremental (NOTE: why exactly do we do this/why does it help/why not do it in the non-intstrumental regressions?).
-
-fin_seg_1 <- fin_seg %>%
-  filter(dgepercap_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-glimpse(fin_seg_1$medincinterp)
-
-# good explanation: http://eclr.humanities.manchester.ac.uk/index.php/IV_in_R
-
-# iv = ivreg(second stage regression | instrument1 + instrument2 )
-
-ivreg1 <- ivreg(dgepercap_cpi ~ H_citytract_NHW_i + dgepercap_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + dgepercap_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_1)
-
-# Column 2
-
-# this is the same regression as for column 1 but now we use the dependent variable highwayspercapNC_cpi to assess the effect of the instrumental  variable on highways per capita *
-
-fin_seg_2 <- fin_seg %>%
-  filter(highwayspercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg2 <- ivreg(highwayspercapNC_cpi ~ H_citytract_NHW_i + highwayspercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + highwayspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_2)
-
-# Column 3
-
-# this is the same regression as for column 1 but now we use the dependent variable policepercapNC_cpi to assess the effect of the instrumental variable on police per capita
-
-fin_seg_3 <- fin_seg %>%
-  filter(policepercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg3 <- ivreg(policepercapNC_cpi ~ H_citytract_NHW_i + policepercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + policepercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_3)
-
-# Column 4 this is the same regression as for column 1 but now we use the
-# dependent variable parkspercapNC_cpi to assess the effect of the instrumental
-# variable on parks per capita
-
-fin_seg_4 <- fin_seg %>%
-  filter(parkspercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg4 <- ivreg(parkspercapNC_cpi ~ H_citytract_NHW_i + parkspercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + parkspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_4)
-
-# Bottom Row
-
-# Column 1
-
-# this is the same regression as for column 1 but now we use the dependent
-# variable sewerspercapNC_cpi to assess the effect of the instrumental variable
-# on sewers per capita
-
-fin_seg_5 <- fin_seg %>%
-  filter(sewerspercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg5 <- ivreg(sewerspercapNC_cpi ~ H_citytract_NHW_i + sewerspercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + sewerspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_5)
-
-# Column 3
-
-# this is the same regression as for column 1 but now we use the dependent variable genrevownpercap_cpi to assess the effect of the instrumental variable on own source revenue per capita
-
-fin_seg_6 <- fin_seg %>%
-  filter(genrevownpercap_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg6 <- ivreg(genrevownpercap_cpi ~ H_citytract_NHW_i + genrevownpercap_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + genrevownpercap_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_6)
-
-# Column 2
-
-# this is the same regression as for column 1 but now we use the dependent
-# variable welfhoushealthNC_cpi to assess the effect of the instrumental
-# variable on welfare per capita
-
-fin_seg_7 <- fin_seg %>%
-  filter(welfhoushealthNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg7 <- ivreg(welfhoushealthNC_cpi ~ H_citytract_NHW_i + welfhoushealthNC_cpilag  + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + welfhoushealthNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_7)
-
-summary(ivreg7)
-
-```
-
-```{r results = "asis", echo = FALSE, eval = FALSE}
-
-table5a <- stargazer(ivreg1, ivreg2, ivreg3, ivreg4,
-          omit = c("y5", "y6", "y7", "y8", "y9", "northeast", "south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach A}",
-          covariate.labels = c("White/Nonwhite H Index", "Lagged Direct Gen.
-Exp.", "Lagged Highway Exp.", "Lagged Police Exp.", "Lagged Parks Exp.", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Constant"))
-
-table5b <- stargazer(ivreg5, ivreg6, ivreg7,
-          omit = c("y5", "y6", "y7", "y8", "y9", "northeast","south", "midwest", "west"), 
-          header = FALSE,
-          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach B}",
-          covariate.labels = c("White/Nonwhite H Index", "Lagged Sewers Exp.", "Lagged Gen.
-Rev.
-Own Sources", "Lagged Police Exp.", "Lagged Welfare", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Constant"))
-```
-
-```{r import_data, include = FALSE}
-
-# make a list of the cities included in the analysis to filter out from the main
-# dataset as specified in the table
-
-cities_to_keep <- c("Austin City", "Baltimore City", "Charlotte City", "Chicago City", "Cleveland City", "Columbus City", "Dallas City", "Denver City", "Detroit City", "Houston City", "Indianapolis", "Jacksonville", "Los Angeles City", "Memphis City", "Milwaukee City", "New York City", "Oklahoma City City", "Philadelphia City", "Phoenix City", "San Antonio City", "San Diego City", "San Francisco City", "San Jose City", "Tucson City", "Washington City")
-
-# based on some investigation, the missing additional filter needed to replicate
-# appendix tables 1 and 2 is that biggest split cannot be NA. This was
-# discovered in attempting to create table 2. The number of elections with the
-# largest divides between each racial group were the same as in the table when
-# all results were included and only the summary stats differed in both tables
-# using the city and winner subset. So, I tried excluding all entries for which
-# biggestsplit was NA, and found that the resulting subset matched the
-# statistics in both tables.
-
-# create a subset of the data with the relevant cities where there is a winner
-# and the biggestsplit is not NA
-
-rp_sub <- rp %>%
-  filter(winner == 1) %>%
-  filter(cityname %in% cities_to_keep) %>%
-  filter(!(is.na(biggestsplit)))
-
-# select the relevant variables for the table
-
-rp_sub_a1 <- rp_sub %>%
-  select(biggestsplit, H_citytract_multi_i, H_citytract_NHW_i, diversityinterp, 
-         pctasianpopinterp, pctblkpopinterp, pctlatinopopinterp, medincinterp, 
-         pctrentersinterp, pctcollegegradinterp, biracial, nonpartisan, primary, 
-         logpop, whiteideology_fill2) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-# why are the exact variables H_citytract_NHW and whiteideology_fill not in the
-# data? Data variable names author uses and ones in the data don't exactly
-# match, but replication results are the same.
-
-```
-
-```{r table_a1, results="asis", echo = FALSE}
-
-# create a stargazer summary table for the relevant statistics of the racial
-# polarization data. I couldn't figure out how to change the text of the
-# statistic names at the top of the datat table. I also couldn't figure out how
-# to only not display additional digits for the income variable. May be
-# better to switch to gt for final version?
-
-stargazer(as.data.frame(rp_sub_a1),
-          omit.summary.stat = c("p25", "p75"),
-          title = "\\textbf{TABLE A1 Summary Statistics: Racial Polarization Data}",
-          column.labels = c("\\textbf{Variable}","\\textbf{Obs}", "\\textbf{Mean}", "\\textbf{Std. Dev.}", "\\textbf{Min}", "\\textbf{Max}"),
-          covariate.labels = c("Largest Racial Divide","\\emph{H} Index: Multigroup", "\\emph{H} Index: Two-Group", "Diversity", "\\% Asian", "\\% Black", "\\% Latino", "Median HH Income", "\\% Renters", "\\% College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology"),
-          no.space = TRUE,
-          header = FALSE)
-
-```
-
-```{r table_a2_data_manipulation, include = FALSE}
-
-# initialize variables to indicate if a racial divide had the biggest divide in
-# the election
-
-rp_sub$biggest_split_bw <- NA
-rp_sub$biggest_split_lw <- NA
-rp_sub$biggest_split_bl <- NA
-
-# change the NA value to 1 if the relevant divide was the biggest in the election
-
-rp_sub$biggest_split_bw[rp_sub$biggestsplit_gr == 1] <- 1
-rp_sub$biggest_split_lw[rp_sub$biggestsplit_gr == 2] <- 1
-rp_sub$biggest_split_bl[rp_sub$biggestsplit_gr == 3] <- 1
-
-# generate the dataset of summary statistics to replicate the second appendix
-# table. Group by city name and then summarize the mean H indexes. Sum the
-# number of biggest splits by racial divide for each city
-
-rp_sub_2 <- rp_sub %>%
-  group_by(cityname) %>%
-  summarise(mean_multi_H = mean(H_citytract_multi_i),
-            mean_multi_two_group = mean(H_citytract_NHW_i),
-            sum_bw = sum(biggest_split_bw, na.rm = T),
-            sum_lw = sum(biggest_split_lw, na.rm = T),
-            sum_bl = sum(biggest_split_bl, na.rm = T))
-```
-
-```{r table_a2, echo = FALSE}
-
-# create appendix table A2 to present the summary statistics for cities included
-# in racial polarization data. Efforts to make columns narrower were
-# unsuccessful, so some of the labels in the column names were changed to make
-# the table fit. I also couldn't get the title to print out without including a
-# non-Null subtitle.
-
-city_names <- c("Austin, TX", "Baltimore, MD", "Charlotte, NC", "Chicago, IL", "Cleveland, OH", "Columbus, OH", "Dallas, TX", "Denver, CO", "Detroit, MI", "Houston, TX", "Indianapolis, IN", "Jacksonville, FL", "Los Angeles, CA", "Memphis, TN", "Milwaukee, WI", "New York, NY", "Oklahoma, OK", "Philadelphia, PA", "Phoenix, AZ", "San Antonio, TX","San Diego, CA", "San Francisco, CA", "San Jose, CA", "Tucson, AZ", "Washington, DC")
-
-rp_sub_2$cityname <- city_names
-
-gt(rp_sub_2) %>%
-  tab_header(title = md("**TABLE A2 Cities Included in Racial Polarization Data**"),
-             subtitle = "Replication") %>%
-  tab_spanner(
-      label = md("**Segregation: Mean *H* Index**"),
-      columns = vars(mean_multi_H, mean_multi_two_group)) %>%
-  tab_spanner(
-      label = md("**Largest Racial Divide, Number of Elections**"),
-      columns = vars(sum_bw, sum_lw, sum_bl)) %>%
-  fmt_number(columns = vars(mean_multi_H, mean_multi_two_group),
-             decimals = 3) %>%
-  cols_label(cityname = "City Name",
-             mean_multi_H = md("Multigroup"),
-             mean_multi_two_group = md("Two-Group"),
-             sum_bw = "Black/White",
-             sum_lw = "Latino/White",
-             sum_bl = "Black/Latino") %>%
-  cols_width(
-    vars(cityname) ~ px(10),
-    TRUE ~ px(20)
-  ) %>%
-  cols_align(
-    columns = vars(cityname),
-    align = "left"
-  ) %>%
-  tab_options(
-    table.margin.left = px(5), 
-    table.margin.right = px(5),
-    data_row.padding = px(1),
-    table.width = pct(90)
-  )
-
-```
-
-```{r fp_summary_table, include = FALSE}
-
-# basic filter for table for all regressions
-
-# xtreg dgepercap_cpi H_citytract_NHW_i diversityinterp pctblkpopinterp
-# pctasianpopinterp pctlatinopopinterp medinc_cpi pctlocalgovworker_100
-# pctrentersinterp pctover65 pctcollegegradinterp logpop if totaltracts>1 &
-# dgepercap_cpi~=0,fe vce(cluster geo_id2)
-
-fin <-fin_seg %>%
-  filter(totaltractsf >1 | is.na(totaltractsf)) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)), !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)), !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)), !(is.na(logpop)))
-
-# create dge variable used in regression
-
-fin_dge <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_dge_tab <- tibble(
-  Variable = "Direct General Expenditure per Capita",
-  Obs = nrow(fin_dge),
-  Mean = mean(fin_dge$dgepercap_cpi, na.rm = T),
-  SD = sd(fin_dge$dgepercap_cpi, na.rm = T),
-  Min = min(fin_dge$dgepercap_cpi, na.rm = T),
-  Max = max(fin_dge$dgepercap_cpi, na.rm = T)
-)
-
-print(fin_dge_tab)
-
-# cities in original Trounstine
-
-cities_trounstine_fp <- fin_dge %>%
-  select(geo_id2) %>%
-  unique() %>%
-  pull()
-
-# pop quantiles original Trounstine
-
-quantile(fin_dge$logpop, c(.10, .25, .5, .75, .90))
-
-quantile(fin_dge$logpop, c(.05, .95))
-
-nrow(fin_imp)
-
-fin_imp_pop_trounstine_95 <- fin_imp %>%
-  filter(logpop < 11.93437 & logpop > 8.7754)
-
-# creat summary for highways
-fin_hw <-fin %>% filter(highwayspercapNC_cpi != 0)
-
-fin_hw_tab <- tibble(
-  Variable = "Highways per Capita",
-  Obs = nrow(fin_hw),
-  Mean = mean(fin_hw$highwayspercapNC_cpi, na.rm = T),
-  SD = sd(fin_hw$highwayspercapNC_cpi, na.rm = T),
-  Min = min(fin_hw$highwayspercapNC_cpi, na.rm = T),
-  Max = max(fin_hw$highwayspercapNC_cpi, na.rm = T)
-)
-
-print(fin_hw_tab)
-
-a3_final <- full_join(fin_dge_tab, fin_hw_tab)
-
-# parks
-
-fin_park <-fin %>% filter(parkspercapNC_cpi != 0)
-
-fin_park_tab <- tibble(
-  Variable = "Parks per Capita",
-  Obs = nrow(fin_park),
-  Mean = mean(fin_park$parkspercapNC_cpi, na.rm = T),
-  SD = sd(fin_park$parkspercapNC_cpi, na.rm = T),
-  Min = min(fin_park$parkspercapNC_cpi, na.rm = T),
-  Max = max(fin_park$parkspercapNC_cpi, na.rm = T)
-)
-
-print(fin_park_tab)
-
-a3_final <- full_join(a3_final, fin_park_tab)
-
-# police
-
-fin_police <-fin %>% filter(policepercapNC_cpi != 0)
-
-fin_police_tab <- tibble(
-  Variable = "Police per Capita",
-  Obs = nrow(fin_police),
-  Mean = mean(fin_police$policepercapNC_cpi, na.rm = T),
-  SD = sd(fin_police$policepercapNC_cpi, na.rm = T),
-  Min = min(fin_police$policepercapNC_cpi, na.rm = T),
-  Max = max(fin_police$policepercapNC_cpi, na.rm = T)
-)
-
-print(fin_police_tab)
-
-a3_final <- full_join(a3_final, fin_police_tab)
-
-# sewers
-
-fin_sew <-fin %>% filter(sewerspercapNC_cpi != 0)
-
-fin_sew_tab <- tibble(
-  Variable = "Sewers per Capita",
-  Obs = nrow(fin_sew),
-  Mean = mean(fin_sew$sewerspercapNC_cpi, na.rm = T),
-  SD = sd(fin_sew$sewerspercapNC_cpi, na.rm = T),
-  Min = min(fin_sew$sewerspercapNC_cpi, na.rm = T),
-  Max = max(fin_sew$sewerspercapNC_cpi, na.rm = T)
-)
-
-print(fin_sew_tab)
-
-a3_final <- full_join(a3_final, fin_sew_tab)
-
-# welfare
-
-fin_welfare <-fin %>% filter(welfhoushealthNC_cpi != 0)
-
-fin_welfare_tab <- tibble(
-  Variable = "Welfare, Health, and Housing per Capita",
-  Obs = nrow(fin_welfare),
-  Mean = mean(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
-  SD = sd(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
-  Min = min(fin_welfare$welfhoushealthNC_cpi, na.rm = T),
-  Max = max(fin_welfare$welfhoushealthNC_cpi, na.rm = T)
-)
-
-print(fin_welfare_tab)
-
-a3_final <- full_join(a3_final, fin_welfare_tab)
-
-# own source revenue
-
-fin_own <-fin %>% filter(genrevownpercap_cpi != 0)
-
-fin_own_tab <- tibble(
-  Variable = "Own Source Revenue per Capita",
-  Obs = nrow(fin_own),
-  Mean = mean(fin_own$genrevownpercap_cpi, na.rm = T),
-  SD = sd(fin_own$genrevownpercap_cpi, na.rm = T),
-  Min = min(fin_own$genrevownpercap_cpi, na.rm = T),
-  Max = max(fin_own$genrevownpercap_cpi, na.rm = T)
-)
-
-print(fin_own_tab)
-
-a3_final <- full_join(a3_final, fin_own_tab)
-
-# two group H
-
-fin_h <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_h_tab <- tibble(
-  Variable = "Two-Group H Index",
-  Obs = nrow(fin_h),
-  Mean = mean(fin_h$H_citytract_NHW_i, na.rm = T),
-  SD = sd(fin_h$H_citytract_NHW_i, na.rm = T),
-  Min = min(fin_h$H_citytract_NHW_i, na.rm = T),
-  Max = max(fin_h$H_citytract_NHW_i, na.rm = T)
-)
-
-print(fin_h_tab)
-
-a3_final <- full_join(a3_final, fin_h_tab)
-
-# Diversity
-
-fin_div <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_div_tab <- tibble(
-  Variable = "Diversity",
-  Obs = nrow(fin_div),
-  Mean = mean(fin_div$diversityinterp, na.rm = T),
-  SD = sd(fin_div$diversityinterp, na.rm = T),
-  Min = min(fin_div$diversityinterp, na.rm = T),
-  Max = max(fin_div$diversityinterp, na.rm = T)
-)
-
-print(fin_div_tab)
-
-a3_final <- full_join(a3_final, fin_div_tab)
-
-# % black
-
-fin_pctblk <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pctblk_tab <- tibble(
-  Variable = "%  Black",
-  Obs = nrow(fin_pctblk),
-  Mean = mean(fin_pctblk$pctblkpopinterp, na.rm = T),
-  SD = sd(fin_pctblk$pctblkpopinterp, na.rm = T),
-  Min = min(fin_pctblk$pctblkpopinterp, na.rm = T),
-  Max = max(fin_pctblk$pctblkpopinterp, na.rm = T)
-)
-
-print(fin_pctblk_tab)
-
-a3_final <- full_join(a3_final, fin_pctblk_tab)
-
-# % asian
-
-fin_pcta <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pcta_tab <- tibble(
-  Variable = "%  Asian",
-  Obs = nrow(fin_pcta),
-  Mean = mean(fin_pcta$pctasianpopinterp, na.rm = T),
-  SD = sd(fin_pcta$pctasianpopinterp, na.rm = T),
-  Min = min(fin_pcta$pctasianpopinterp, na.rm = T),
-  Max = max(fin_pcta$pctasianpopinterp, na.rm = T)
-)
-
-print(fin_pcta_tab)
-
-a3_final <- full_join(a3_final, fin_pcta_tab)
-
-# % latino
-
-fin_pctla <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pctla_tab <- tibble(
-  Variable = "%  Latino",
-  Obs = nrow(fin_pctla),
-  Mean = mean(fin_pctla$pctlatinopopinterp, na.rm = T),
-  SD = sd(fin_pctla$pctlatinopopinterp, na.rm = T),
-  Min = min(fin_pctla$pctlatinopopinterp, na.rm = T),
-  Max = max(fin_pctla$pctlatinopopinterp, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_pctla_tab)
-
-# 5y black
-
-fin_chng5pctblk <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))
-
-nrow(fin_chng5pctblk)
-
-fin_chng5pctblk_tab <- tibble(
-  Variable = "5Y Change, % Black",
-  Obs = nrow(fin_chng5pctblk),
-  Mean = mean(fin_chng5pctblk$chng5pctblk, na.rm = T),
-  SD = sd(fin_chng5pctblk$chng5pctblk, na.rm = T),
-  Min = min(fin_chng5pctblk$chng5pctblk, na.rm = T),
-  Max = max(fin_chng5pctblk$chng5pctblk, na.rm = T)
-)
-
-print(fin_chng5pctblk_tab)
-
-a3_final <- full_join(a3_final, fin_chng5pctblk_tab)
-
-# 5y latino
-
-fin_chng5pctlatino <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))
-
-fin_chng5pctlatino_tab <- tibble(
-  Variable = "5Y Change, % Latino",
-  Obs = nrow(fin_chng5pctlatino),
-  Mean = mean(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
-  SD = sd(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
-  Min = min(fin_chng5pctlatino$chng5pctlatino, na.rm = T),
-  Max = max(fin_chng5pctlatino$chng5pctlatino, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_chng5pctlatino_tab)
-
-# 5y asian
-
-fin_chng5pctasian <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(chng5pctblk)), !(is.na(chng5pctasian)), !(is.na(chng5pctlatino)))
-
-fin_chng5pctasian_tab <- tibble(
-  Variable = "5Y Change, % Asian",
-  Obs = nrow(fin_chng5pctasian),
-  Mean = mean(fin_chng5pctasian$chng5pctasian, na.rm = T),
-  SD = sd(fin_chng5pctasian$chng5pctasian, na.rm = T),
-  Min = min(fin_chng5pctasian$chng5pctasian, na.rm = T),
-  Max = max(fin_chng5pctasian$chng5pctasian, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_chng5pctasian_tab)
-
-# median income
-
-fin_med <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_med_tab <- tibble(
-  Variable = "Median Income",
-  Obs = nrow(fin_med),
-  Mean = mean(fin_med$medinc_cpi, na.rm = T),
-  SD = sd(fin_med$medinc_cpi, na.rm = T),
-  Min = min(fin_med$medinc_cpi, na.rm = T),
-  Max = max(fin_med$medinc_cpi, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_med_tab)
-
-# % local gov. employees
-
-fin_pctlocal <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_pctlocal_tab <- tibble(
-  Variable = "% Local Gov. Employees",
-  Obs = nrow(fin_pctlocal),
-  Mean = mean(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
-  SD = sd(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
-  Min = min(fin_pctlocal$pctlocalgovworker_100, na.rm = T),
-  Max = max(fin_pctlocal$pctlocalgovworker_100, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_pctlocal_tab)
-
-# % renters
-
-fin_rent <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_rent_tab <- tibble(
-  Variable = "% Renters",
-  Obs = nrow(fin_rent),
-  Mean = mean(fin_rent$pctrentersinterp, na.rm = T),
-  SD = sd(fin_rent$pctrentersinterp, na.rm = T),
-  Min = min(fin_rent$pctrentersinterp, na.rm = T),
-  Max = max(fin_rent$pctrentersinterp, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_rent_tab)
-
-# % over 65
-
-fin_65 <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_65_tab <- tibble(
-  Variable = "% Over 65",
-  Obs = nrow(fin_65),
-  Mean = mean(fin_65$pctover65, na.rm = T),
-  SD = sd(fin_65$pctover65, na.rm = T),
-  Min = min(fin_65$pctover65, na.rm = T),
-  Max = max(fin_65$pctover65, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_65_tab)
-
-# % college degree
-
-fin_college <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_college_tab <- tibble(
-  Variable = "% College Degree",
-  Obs = nrow(fin_college),
-  Mean = mean(fin_college$pctcollegegradinterp, na.rm = T),
-  SD = sd(fin_college$pctcollegegradinterp, na.rm = T),
-  Min = min(fin_college$pctcollegegradinterp, na.rm = T),
-  Max = max(fin_college$pctcollegegradinterp, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_college_tab)
-
-# pop logged
-
-fin_logpop <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_logpop_tab <- tibble(
-  Variable = "Population (logged)",
-  Obs = nrow(fin_logpop),
-  Mean = mean(fin_logpop$logpop, na.rm = T),
-  SD = sd(fin_logpop$logpop, na.rm = T),
-  Min = min(fin_logpop$logpop, na.rm = T),
-  Max = max(fin_logpop$logpop, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_logpop_tab)
-
-# city ideology
-
-fin_ideo <-fin %>% filter(dgepercap_cpi != 0) %>%
-  filter(!(is.na(ideology_fill)))
-
-nrow(fin_ideo)
-
-fin_ideo_tab <- tibble(
-  Variable = "City Ideology",
-  Obs = nrow(fin_ideo),
-  Mean = mean(fin_ideo$ideology_fill, na.rm = T),
-  SD = sd(fin_ideo$ideology_fill, na.rm = T),
-  Min = min(fin_ideo$ideology_fill, na.rm = T),
-  Max = max(fin_ideo$ideology_fill, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_ideo_tab)
-
-# population
-fin_population <-fin %>% filter(dgepercap_cpi != 0)
-
-fin_population_tab <- tibble(
-  Variable = "Population",
-  Obs = nrow(fin_population),
-  Mean = mean(fin_population$population, na.rm = T),
-  SD = sd(fin_population$population, na.rm = T),
-  Min = min(fin_population$population, na.rm = T),
-  Max = max(fin_population$population, na.rm = T)
-)
-
-a3_final <- full_join(a3_final, fin_population_tab)
-
-```
-
-```{r fp_summary_table_stargazer, echo = FALSE}
-gt(a3_final) %>%
-    tab_header(title = md("**TABLE A3 Summary Statistics: Census of Government Finance and Population**"),
-             subtitle = "") %>%
-    fmt_number(columns = vars(Mean, SD, Min, Max),
-             decimals = 3) %>%
-    cols_label(Obs = md("**Obs**"),
-               Mean = md("**Mean**"),
-               SD = md("**SD**"),
-               Min = md("**Min**"),
-               Max = md("**Max**")
-                        ) 
-```
-
-# Bibliography
+\newpage
+
+# Appendix

### 2020-05-04 Final_Draft.Rmd
histogram plot edits

@@
 library(huxtable)
+library(naniar)
 ```

### 2020-05-04 final_draft_extension_fs.Rmd
histogram plot edits

@@
 ```{r data_prep_imputations, include = FALSE}
-
-# select the relevant rows from the rp dataset
-
-rp_impute <- rp %>%
-  select("winner", "medincinterp",
-             "biggestsplit", "H_citytract_multi_i", "diversityinterp",
-             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
-             "pctrentersinterp", "pctcollegegradinterp", "biracial", "nonpartisan",
-             "primary", "logpop", "year", "south", "midwest", "west", "geo_id2",
-             "H_citytract_NHW_i", "whiteideology_fill2") %>%
-  filter(winner == 1) %>%
-  mutate(medincinterp = medincinterp/1000,
-         year.f = as.factor(year))
 
@@
 
+nrow(fin_dge)
+
 # cities in original Trounstine
@@
 obs_fin_seg <- nrow(fin_imp)
-obs_rp <- nrow(rp_impute)
 
 ```
-
-One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data, which substantially constrains the sample size used in the regression analysis.
-For example, the regression analysis in the main specification using the the original racial polarization dataset exludes %`r round((obs_rp - 91)/obs_rp, 2)` of the observations, and the regression analysis in the main specification using the original financial segregation data excludes %`r round((obs_fin_seg - 13742)/ obs_fin_seg, 2)` of observations from the original dataset.
-As an extension of @trounstine_segregation_2016, I impute missing values in the original data using the mice package in R, which generates multivariate imputations using chained equations [@mice].
-Then, I use the multiply imputed datasets to re-estimate the original models, pooling the results to generate final pooled regression coefficients and parameters.
 
@@
 
-One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data values in her original datasets.
-Because both R and Stata drop any observations with missing values for any of the variables used in a regression, this can exlcude a large portion of the data from the analysis and potentially bias the results if the data is not missing completely at random.
-A large amount of data is missing in both of the main datasets used in the analyses of @trounstine_segregation_2016.
-The main model specification using the racial polarization dataset exludes `r (obs_rp - 91)` of the original  `r obs_rp` observations, or  %`r round(100*(obs_rp - 91)/obs_rp,2)` of the data.
-Additionally, the main model specification using the financial segregation data set excludes `r round(obs_fin_seg - 13742,2)` of the original `r obs_fin_seg` observations, or %`r round(100*(obs_fin_seg - 13742)/ obs_fin_seg,2)` of observations from the original dataset.
-
 In an attempt to better deal with the problem of missing data in @trounstine_segregation_2016, I impute missing values in the original data using the mice package in R, which generates multivariate imputations using chained equations [@mice].
@@
 To better understand any potential patterns in missing data, I plotted the pattern of missingness and created a histogram showing the frequency of missing values for those variables with missing values in figure X1 for the racial polarization data and figure X2 for the financial segregation data.
-Looking at figure X1, the histogram shows that the variables for the largest vote split along racial lines and the variable indicating whether or not the election had candidates of more than one race had by far the largest percentages of missing data, missing %`r round(sum(is.na(rp_impute$biggestsplit))/nrow(rp_impute)*100,2)` and  %`r round(sum(is.na(rp_impute$biracial))/nrow(rp_impute)*100,2)`, respectively.
-It is important to note that the variable for the largest vote split along racial lines is the dependent variable in the regresison analysis, and thus, we are missing a large percentage of this key variable.
-From the plot on the right, we can see that approximately 42% of observations are complete (have no missing values).
-There seem to be a correspondence between missing a value for the largest vote split and missing a value for the biracial election indicator.
-There also seem to be about 2% of values for wich most of the variables are missing.
-However, most observations are not missing more than 2-3 values.
+Looking at figure X1, the histogram shows that the variables for the largest vote split along racial lines and the variable indicating whether or not the
 
@@
 
-```{r fp_imputations_original, include = FALSE}
+```{r fp_imputations_original, include = FALSE, eval = FALSE}
 
@@
 # now there are many fewer missing variables!!!
-
-miss_var_summary(complete(imp_fs))
-
-miss_var_summary(fin_imp)
 
@@
 
-The results of the model with the new dataset are slightly different in comparison to the original results from Trounstine (2016).
-With the imputed data, we now have a total of `r nrow(complete(rp_impute))` observations in our model as compared to the original model, which had only 91 observations.
-Interestingly, while the sign of the coefficient on the main variable of interest, the Theil's H segregation index, is the same and the standard error has decreased slightly, the result has become statisically insignificant and the 95% confidence interval contains zero.
-Thus while these results still suggest that segregation may be associated with increased political polarization, they confer a lesser degree of certainty than Trounstine's original analysis.
-The coefficients for % Black population, % Latino population, and median household income have also switched signs, and all coefficients except the indicator for a biracial election are also statistically insignificant, as was the case in the original analysis.
-The coefficient on the indicator for a primary election, has also changed from being significant in the original analysis to insignificant here.
-In general, the standard errors on the coefficients have decreased slightly.
-
 In the second regression, the results are similar.
@@
 
-```{r fs_imputed_pooled_regressions, include = FALSE}
+```{r fs_imputed_main_1st_specification, include = FALSE}
+
 # Main Analysis 2: Imputations
@@
 imp_felm1_sum <- summary(pool_imp_felm1)
+
+```
+
+```{r fs_imputed_pooled_regressions, include = FALSE, eval = FALSE}
 
@@
 
-```{r results_printing_fs_impute_regressions_2, results = "asis", echo=FALSE}
+```{r results_printing_fs_impute_regressions_2, results = "asis", echo=FALSE, eval = FALSE, invlude = FALSE}
 
@@
 
-```{r results_printing_fs_impute_regressions_3, results = "asis", echo=FALSE}
+```{r results_printing_fs_impute_regressions_3, results = "asis", echo=FALSE, eval = FALSE, invlude = FALSE}
 
@@
 
-```{r over_baqir_fit, include = FALSE}
+```{r over_baqir_1st_specification, include = FALSE}
+
 # fit multiple imputed datasets
@@
 imp_over_baqir_1_sum <- summary(pool_fit_over_baqir_1)
+
+```
+
+```{r over_baqir_fit_2_and_3, include = FALSE, eval = FALSE}
 
@@
 # doesn't add very much to the sample though, still, robust to additional 73 entries
-
-miss_var_summary(complete(imp_fs_pop_overbaqir))
-
-5039 - 4966
 
@@
 
-```{r population_under_Baqir_fitting, include = FALSE}
+```{r population_under_Baqir_1st_specification, include = FALSE}
 
@@
 imp_under_baqir_1_sum <- summary(pool_fit_under_baqir_1)
+
+```
+
+```{r population_under_Baqir_fitting_specification_2_and_3, include = FALSE}
 
@@
 
-```{r histograms_city_pop_in_specifications}
+```{r histograms_city_pop_in_specifications_prep, include = FALSE}
 
@@
   log_pop = complete(imp_fs_pop_overbaqir,1)$logpop,
-  id = "over_baqir"
+  Analysis = "Imputed, pop. > 25k"
 )
@@
   log_pop = complete(imp_fs_pop_under_baqir, 1)$logpop,
-  id = "under_baqir"
+  Analysis = "Imputed, pop. < 25k"
 )
@@
   log_pop = complete(imp_fs, 1)$logpop,
-  id = "imp_fs"
+  Analysis = "Imputed, Whole Sample"
 )
@@
   log_pop = fin_dge$logpop,
-  id = "fin_dge"
+  Analysis = "Trounstine (2016)"
 )
@@
   log_pop = fin_seg$logpop,
-  id = "fin_seg"
+  Analysis = "Original Sample"
 )
@@
 
-pop_hist_data %>%
-  ggplot(aes(x = log_pop)) +
-  geom_histogram(aes(color = id)) +
-  facet_wrap(~id)
+median_pops <- tibble(
+  Analysis = c("Imputed, pop. > 25k", "Imputed, pop. < 25k", "Imputed, Whole Sample", "Trounstine (2016)", "Original Sample"),
+  median_log_pop = c(median(complete(imp_fs_pop_overbaqir,1)$logpop),
+                     median(complete(imp_fs_pop_under_baqir, 1)$logpop),
+                     median(complete(imp_fs, 1)$logpop),
+                     median(fin_dge$logpop),
+                     median(fin_seg$logpop, na.rm = T))
+)
+
+pop_hist_data <- left_join(pop_hist_data, median_pops)
+
+```
+
+```{r city_pops_histogram, echo = FALSE}
 
 pop_hist_data %>%
-  ggplot(aes(x = log_pop)) +
-  geom_density(aes(color = id)) +
-  facet_wrap(~id)
+  ggplot() +
+  geom_histogram(aes(x = log_pop, fill = Analysis)) +
+  geom_vline(aes(xintercept = median_log_pop), color = "red") +
+  facet_wrap(~Analysis) +
+  coord_cartesian(xlim = c(0,15)) +
+  ggtitle("Histograms of Log Populaiton of City Observations Included in the Various\nRegression Analyses") +
+  labs(caption = "This figure makes clear the differences in city size (in terms of population) among the different analyses.
+It is\nclear that the listwise deletion of observations with missing values resulted in a sample that almost entirely\nconsisted of larger cities in Trounstine (2016).
+The distribution of city population in Trounstine (2016) more\nclosely resembles the distribution of the original sample with a greater than 25,000 population cutoff imposed\nthan the original sample.
+The red lines indicate the median log population in each sample.") +
+  ylab("Count") +
+  xlab("Log Population") +
+  theme_bw() +
+  theme(plot.caption = element_text(hjust = 0))
 
-range(fin_seg$population)
+```
 
-fin_seg %>%
-  filter(fin_seg$logpop == 0)
+```{r calc_coeff_sds_original_fs_impute, include = FALSE, eval = FALSE}
 
-fin_seg %>%
-  filter(populationinterp < 25000)
+imp_felm1_sum[1,2]
+imp_under_baqir_1_sum
+imp_over_baqir_1_sum
+coef(felm1)[1]
+
+summary(felm1)$coeff[2,2]
+
+model_coeff <- tibble(
+  variable = c("H_citytract_NHW_i", "diversityinterp", 
+               "H_citytract_NHW_i", "diversityinterp", 
+               "H_citytract_NHW_i", "diversityinterp",
+               "H_citytract_NHW_i", "diversityinterp"),
+  estimate = c(imp_felm1_sum[1,2], imp_felm1_sum[2,2],
+               imp_under_baqir_1_sum[1,2], imp_under_baqir_1_sum[2,2],
+               imp_over_baqir_1_sum[1,2], imp_over_baqir_1_sum[2,2],
+               coef(felm1)[1], coef(felm1)[2]),
+  std_error = c(imp_under_baqir_1_sum[1,3], imp_under_baqir_1_sum[2,3],
+                imp_felm2_sum[1,3], imp_felm2_sum[2,3],
+                imp_over_baqir_1_sum[1,3], imp_over_baqir_1_sum[2,3],
+                summary(felm1)$coeff[1,2], summary(felm1)$coeff[2,2]),
+  model = c(1, 1,
+            2, 2,
+            3, 3,
+            4, 4)
+)
+
+model_coeff <- model_coeff %>%
+  mutate(variable = as.factor(variable))
+
+model_coeff %>%
+  ggplot(aes(x = model, y = estimate)) +
+  geom_point()+
+  geom_errorbar(aes(ymin = estimate - std_error, ymax = estimate + std_error, width = .2)) +
+  geom_hline(yintercept = 0, color = "red") +
+  facet_wrap(~variable)
 

### 2020-05-05 final_draft_extension_fs.Rmd
cutoff analysis

@@
 
-```{r fp_imputations_original, include = FALSE, eval = FALSE}
+```{r fp_imputations_original, include = FALSE}
 
@@
 
+# basic filter for table for all regressions
+
 # xtreg dgepercap_cpi H_citytract_NHW_i diversityinterp pctblkpopinterp
@@
 
-fin <- complete(imp_fs) %>%
+fin <-fin_seg %>%
+  filter(totaltractsf >1 | is.na(totaltractsf)) %>%
   filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
@@
 kable(imp_felm1_sum_table_vars, "latex",
-      caption = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Expenditure per Capita}",
+      caption = "\\textbf{Effect of Segregation on Overall per Capita Direct General City Expenditures: Imputed Data for all Cities}",
       booktabs = T) %>%
     row_spec(0, bold = TRUE) %>%
-  footnote(general = c("This table shows the results of Trounstine's first model for the effect of segregation on per capita",
-  "direct public expenditure using the two-group Theil's H Segregation Index using the new, multiply imputed datasets.",
+  footnote(general = c("This table shows the results of Trounstine's first model for the effect of segregation on per capita direct",
+  "public expenditure using the two-group Theil's H Segregation Index using the new, multiply imputed datasets.",
   "The results present a stark contrast to Trounstine's original results: the main coefficient on segregation index",
-  "has decreased to essentially zero and has become statistically insignificant. The very large P-Value may indicate there is",
-  "a larger difference between the two models. The coefficient on diversity has increased in magnitude and become",
-  "statistically significant."),
+  "has decreased to essentially zero and has become statistically insignificant. The very large P-Value may indicate",
+  "there is a larger difference between the two models. The coefficient on diversity has increased in magnitude and",
+  "become statistically significant."),
            general_title = "Table 4:") %>%
@@
 
-```{r results_printing_fs_impute_regressions_3, results = "asis", echo=FALSE, eval = FALSE, invlude = FALSE}
+```{r results_printing_fs_impute_regressions_3, results = "asis", echo=FALSE, eval = FALSE, include = FALSE}
 
@@
 kable(imp_over_baqir_1_sum_table_vars, "latex",
-      caption = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Expenditure per Capita}",
+      caption = "\\textbf{Effect of Segregation on Overall per Capita Direct General City Expenditures: Imputed Data for Cities with Populations of 25,000+}",
       booktabs = T) %>%
@@
 
-```{r city_pops_histogram, echo = FALSE}
+```{r city_pops_histogram, echo = FALSE, warning = FALSE}
 
@@
   coord_cartesian(xlim = c(0,15)) +
-  ggtitle("Histograms of Log Populaiton of City Observations Included in the Various\nRegression Analyses") +
-  labs(caption = "This figure makes clear the differences in city size (in terms of population) among the different analyses.
-It is\nclear that the listwise deletion of observations with missing values resulted in a sample that almost entirely\nconsisted of larger cities in Trounstine (2016).
-The distribution of city population in Trounstine (2016) more\nclosely resembles the distribution of the original sample with a greater than 25,000 population cutoff imposed\nthan the original sample.
+  ggtitle("Histograms of Log Populaiton of City Observations Included in the\nVarious Regression Analyses") +
+  labs(caption = "This figure makes clear the differences in city size (in terms of population) among the different analyses.\n It is clear that the listwise deletion of observations with missing values resulted in a sample that almost entirely\nconsisted of larger cities in Trounstine (2016).
+The distribution of city population in Trounstine (2016)\nmore closely resembles the distribution of the original sample with a greater than 25,000 population\ncutoff imposed than the original sample.
 The red lines indicate the median log population in each sample.") +
@@
   theme_bw() +
-  theme(plot.caption = element_text(hjust = 0))
+  theme(plot.caption = element_text(hjust = 0),
+        strip.text.x = element_text(size = 8))
 
@@
 
-```{r calc_coeff_sds_original_fs_impute, include = FALSE, eval = FALSE}
+```{r top_1_%_pop}
+
+fin_imp_top_1 <- fin_imp %>%
+  filter(logpop > quantile(fin_seg$logpop, c(.95), na.rm = T))
+
+nrow(fin_imp_top_1)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_top_1, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_fs_pop_top_1 <- mice(fin_imp_top_1, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_fs_pop_top_1 <- with(imp_fs_pop_top_1, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fs_pop_top_1 <- pool(fit_fs_pop_top_1)
+imp_fs_pop_top_1_sum <- summary(pool_fs_pop_top_1)
+
+```
+
+```{r}
+fin_seg %>%
+  ggplot(aes(x = logpop)) +
+  geom_histogram() +
+  geom_vline(aes(xintercept = log(25000)))
+
+log(25000)
+```
+
+```{r bottom_60_%_pop}
+
+quantile(fin_seg$logpop, c(.60), na.rm = T)
+
+fin_imp_bottom_60 <- fin_imp %>%
+  filter(logpop < quantile(fin_seg$logpop, c(.60), na.rm = T))
+
+nrow(fin_imp_bottom_60)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_bottom_60, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_bottom_60 <- mice(fin_imp_bottom_60, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_bottom_60 <- with(imp_bottom_60, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fs_bottom_60 <- pool(fit_imp_bottom_60)
+imp_fs_pop_bottom_60<- summary(pool_fs_bottom_60)
+
+```
+
+```{r 50k}
+
+fin_imp_50k <- fin_imp %>%
+  filter(logpop < log(50000))
+
+nrow(fin_imp_50k)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_50k, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_50k <- mice(fin_imp_50k, method = meth, maxit = 1)
+
+# fit multiple imputed datasets
+
+fit_imp_50k <- with(imp_50k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses: insignificant for both
+
+pool_fs_50k<- pool(fit_imp_50k)
+imp_fs_pop_50k<- summary(pool_fs_50k)
+
+```
+
+```{r 250k}
+
+fin_imp_250k <- fin_imp %>%
+  filter(logpop < log(250000))
+
+nrow(fin_imp_250k)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_250k, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_250k <- mice(fin_imp_250k, method = meth, maxit = 1)
+
+# fit multiple imputed datasets
+
+fit_imp_250k <- with(imp_250k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fs_250k<- pool(fit_imp_250k)
+imp_fs_pop_250k<- summary(pool_fs_250k)
+
+```
+
+```{r 500k}
+
+fin_imp_250_500k <- fin_imp %>%
+  filter(logpop > log(250000) & logpop < log(500000))
+
+nrow(fin_imp_250k)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_250k, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_250k <- mice(fin_imp_250k, method = meth, maxit = 1)
+
+# fit multiple imputed datasets
+
+fit_imp_250k <- with(imp_250k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fs_250k<- pool(fit_imp_250k)
+imp_fs_pop_250k<- summary(pool_fs_250k)
+
+```
+
+```{r calc_coeff_sds_original_fs_impute, include = FALSE}
 
@@
 imp_over_baqir_1_sum
-coef(felm1)[1]
+#coef(felm1)[1]
+imp_fs_pop_top_1_sum
 
-summary(felm1)$coeff[2,2]
+#summary(felm1)$coeff[2,2]
+
+# lets put the models in order of increasing median population size in the sample.
+
+pop_hist_data %>%
+  select(Analysis, median_log_pop) %>%
+  arrange(median_log_pop) %>%
+  unique()
 
 model_coeff <- tibble(
-  variable = c("H_citytract_NHW_i", "diversityinterp", 
-               "H_citytract_NHW_i", "diversityinterp", 
-               "H_citytract_NHW_i", "diversityinterp",
-               "H_citytract_NHW_i", "diversityinterp"),
-  estimate = c(imp_felm1_sum[1,2], imp_felm1_sum[2,2],
-               imp_under_baqir_1_sum[1,2], imp_under_baqir_1_sum[2,2],
+  variable = c("White/Non-White Seg. Index", "Diversity", 
+               "White/Non-White Seg. Index", "Diversity", 
+               #"White/Non-White Seg. Index", "Diversity",
+               "White/Non-White Seg. Index", "Diversity",
+               "White/Non-White Seg. Index", "Diversity"),
+  estimate = c(imp_under_baqir_1_sum[1,2], imp_under_baqir_1_sum[2,2],
+               imp_felm1_sum[1,2], imp_felm1_sum[2,2],
+               #coef(felm1)[1], coef(felm1)[2],
                imp_over_baqir_1_sum[1,2], imp_over_baqir_1_sum[2,2],
-               coef(felm1)[1], coef(felm1)[2]),
+               imp_fs_pop_top_1_sum[1,2], imp_fs_pop_top_1_sum[2,2]),
   std_error = c(imp_under_baqir_1_sum[1,3], imp_under_baqir_1_sum[2,3],
-                imp_felm2_sum[1,3], imp_felm2_sum[2,3],
+                imp_felm1_sum[1,3], imp_felm1_sum[2,3],
+                #summary(felm1)$coeff[1,2], summary(felm1)$coeff[2,2],
                 imp_over_baqir_1_sum[1,3], imp_over_baqir_1_sum[2,3],
-                summary(felm1)$coeff[1,2], summary(felm1)$coeff[2,2]),
+                imp_fs_pop_top_1_sum[1,3], imp_fs_pop_top_1_sum[2,3]),
   model = c(1, 1, 
             2, 2,
+            #3, 3,
             3, 3,
-            4, 4)
+            5, 5)
 )
@@
 
+```
+
+```{r coef_plot, echo = FALSE}
+
+coef.labels <- c("Diversity", "White/Non-White Seg. Index")
+names(coef.labels) <- c("Diversity", "White/Non-White Seg. Index")
+
 model_coeff %>%
@@
   geom_point()+
-  geom_errorbar(aes(ymin = estimate - std_error, ymax = estimate + std_error, width = .2)) +
+  geom_errorbar(aes(ymin = estimate - 2 * std_error, ymax = estimate + 2 * std_error, width = .2)) +
   geom_hline(yintercept = 0, color = "red") +
-  facet_wrap(~variable)
+  facet_wrap(~variable, labeller = labeller(variable = coef.labels)) +
+  ggtitle("Coefficient Plots for Diversity and White/Non-White Segregation Indices Across\nthe Models")+
+  xlab("Models Ordered by Increasing Median Population Size of the Sample") +
+  ylab("Estimate and 95% Confidence Interval") +
+  labs(caption = "This plot demonstrates how the significance of diversity and segregation in predicting public\ngoods spending varies with city size.
+As city populaiton size increases, diversity tends to have\nless explanatory power for public goods spending while segregation has more.
+The opposite\nis true when considering city population size decreasing: segregation becomes less important\nas diversity becomes increasingly important.") +
+  theme_bw()+
+  theme(plot.caption = element_text(hjust = 0))
 

### 2020-05-07 Final_Draft.Rmd
edits to text

@@
 imp_fs <- mice(fin_imp, method = meth, maxit = 1)
-
-# now there are many fewer missing variables!!!
-
-miss_var_summary(complete(imp_fs))
-
-miss_var_summary(fin_imp)
-
-282334 - 222957
 
@@
 
-```{r fs_densityplot, echo = FALSE, eval = FALSE}
-
-densityplot(imp_fs)
-densityplot(x = imp_fs , data = ~ H_citytract_NHW_i + chng5pctblk + 
-       chng5pctlatino + chng5pctasian + ideology_fill)
-
-```
-
-Given the promising results of the diagnostic checks, I next proceeded to re-estimate the original model using the multiply imputed datasets, pooling the results to produce final pooled regression coefficients and parameters.
+```{r fs_densityplot, echo = FALSE}
+
+my.settings <- list(
+  par.main.text = list(font = 1, cex = 1)
+)
+
+#densityplot(imp_fs)
+densityplot(x = imp_fs, 
+            data = ~ H_citytract_NHW_i + chng5pctblk + chng5pctlatino + chng5pctasian + ideology_fill,
+            main = "Density Plots of Imputed and Original Data by Variable\nin the Financial Segregation Dataset",
+            par.settings = my.settings,
+            par.strip.text = list(cex = 1))
+
+```
+
+Since the results of the diagnostic checks were promising, I next proceeded to re-estimate the original model using the multiply imputed datasets, pooling the results to produce final pooled regression coefficients and parameters.
 The results for the analyses using the racial polarization dataset are presented in tables X1-X3.
@@
 ```
+
+For the financial segregation dataset, we similarly fit each of our 5 imputed datasets to the original models from @trounstine_segregation_2016 using this data and then pool the results for each.
+The pooled results are presented in tables 4-6.
+
+```{r fs_imputed_main_1st_specification, include = FALSE}
+
+# Main Analysis 2: Imputations
+
+## regression 1 Table 2
+
+# fit multiple imputed datasets
+
+fit_imp_felm1 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_imp_felm1 <- pool(fit_imp_felm1)
+imp_felm1_sum <- summary(pool_imp_felm1)
+
+```
+
+As a result of the imputation process, I was able to include an additional XXXXXX observations in the analysis.
+
+The results of the first regression present a stark difference to the results of @trounstine_segregation_2016.
+Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant.
+Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
+The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.
+
+```{r fs_imputed_pooled_regressions, include = FALSE, eval = FALSE}
+
+## regression 2 Table 2
+
+# fit multiple imputed datasets
+
+fit_imp_felm2 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_imp_felm2 <- pool(fit_imp_felm2)
+imp_felm2_sum <- summary(pool_imp_felm2)
+
+## Regression 3 Table 2
+
+fit_imp_felm3 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_imp_felm3 <- pool(fit_imp_felm3)
+imp_felm3_sum <- summary(pool_imp_felm3)
+
+print(imp_felm1_sum)
+
+```
+
+```{r results_printing_fs_impute_regressions_1, results = "asis", echo=FALSE}
+
+# print results of 1st regression
+
+imp_felm1_sum_table <- as.data.frame(imp_felm1_sum %>% 
+  select(term, estimate, std.error, p.value))
+
+imp_felm1_sum_table_vars <- tibble(
+  Variable = c("White/Nonwhite Seg. Index", "Diversity", "% Black", "% Asian", "% Latino", "Median Income (1000s)", "% Local Gov. Worker", "% Renters", "% 65+", "% College Grads", "Pop (logged)"),
+  Estimate = round(imp_felm1_sum_table$estimate, 3),
+  `Std. Error` = round(imp_felm1_sum_table$std.error,3),
+  `P-Value` = round(imp_felm1_sum_table$p.value, 3)
+)
+
+kable(imp_felm1_sum_table_vars, "latex",
+      caption = "\\textbf{Effect of Segregation on Overall per Capita Direct General City Expenditures: Imputed Data for all Cities}",
+      booktabs = T) %>%
+    row_spec(0, bold = TRUE) %>%
+  footnote(general = c("This table shows the results of Trounstine's first model for the effect of segregation on per capita direct",
+  "public expenditure using the two-group Theil's H Segregation Index using the new, multiply imputed datasets.",
+  "The results present a stark contrast to Trounstine's original results: the main coefficient on segregation index",
+  "has decreased to essentially zero and has become statistically insignificant. The very large P-Value may indicate",
+  "there is a larger difference between the two models. The coefficient on diversity has increased in magnitude and",
+  "become statistically significant."),
+           general_title = "Table 4:") %>%
+  kable_styling(full_width = TRUE)
+
+```
+
+```{r results_printing_fs_impute_regressions_2, results = "asis", echo=FALSE, eval = FALSE, invlude = FALSE}
+
+# print results of 2nd regression
+
+imp_felm2_sum_table <- as.data.frame(imp_felm2_sum %>% 
+  select(term, estimate, std.error, p.value))
+
+imp_felm2_sum_table_vars <- tibble(
+  Variable = c("White/Nonwhite Seg.
+Index", "% Black", "% Asian", "% Latino", "5Y Change % Black", "5Y Change % Latino", "5Y Change % Asian", "Median Income (1000s)", "% Local Gov.
+Worker", "% Renters", "% 65+", "% College Grads", "Pop (logged)"),
+  Estimate = round(imp_felm2_sum_table$estimate, 3),
+  `Std. Error` = round(imp_felm2_sum_table$std.error,3),
+  `P-Value` = round(imp_felm2_sum_table$p.value, 3)
+)
+
+kable(imp_felm2_sum_table_vars, "latex",
+      caption = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Changing Demographics}",
+      booktabs = T) %>%
+    row_spec(0, bold = TRUE) %>%
+  footnote(general = c("This table shows the results of Trounstine's second model for the effect of segregation on per capita",
+  "direct public expenditure using the two-group Theil's H Segregation Index using the new, multiply imputed datasets.",
+  "Again, in contrast to Trounstine's original results, the main coefficient on segregation index has decreased to",
+  "essentially zero and has become statistically insignificant with a very large P-Value."),
+           general_title = "Table 5:") %>%
+  kable_styling(full_width = TRUE)
+
+```
+
+```{r results_printing_fs_impute_regressions_3, results = "asis", echo=FALSE, eval = FALSE, include = FALSE}
+
+# print results of 3rd regression
+
+imp_felm3_sum_table <- as.data.frame(imp_felm3_sum %>% 
+  select(term, estimate, std.error, p.value))
+
+imp_felm3_sum_table_vars <- tibble(
+  Variable = c("White/Nonwhite Seg.
+Index", "Diversity", "% Black", "% Asian", "% Latino", "Median Income (1000s)", "% Local Gov.
+Worker", "% Renters", "% 65+", "% College Grads", "Pop (logged)", "Ideology"),
+  Estimate = round(imp_felm3_sum_table$estimate, 3),
+  `Std. Error` = round(imp_felm3_sum_table$std.error,3),
+  `P-Value` = round(imp_felm3_sum_table$p.value, 3)
+)
+
+kable(imp_felm3_sum_table_vars, "latex",
+      caption = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Ideology Control}",
+      booktabs = T) %>%
+    row_spec(0, bold = TRUE) %>%
+  footnote(general = c("This table shows the results of Trounstine's third model for the effect of segregation on political polarization",
+  "(racial vote divide) using the two-group Theil's H segregation Index and including controls for ideology",
+  "using the new, multiply imputed datasets. Compared to Trounstine's original results, the main coefficient on",
+  "segregation index has decreased in magnitude although, it remains statistically significant. The other",
+  "coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian and",
+  "Black have switched signs. Standard errors have also reduced slightly in these specifications compared to",
+  "the original analysis in Trounstine (2016)."),
+           general_title = "Table 6:") %>%
+  kable_styling(full_width = TRUE)
+
+```
+
+Because these results differed to such a degree from @trounstine_segregation_2016's original findings, I performed some checks on the data included in each analysis.
+I discovered that @trounstine_segregation_2016 excluded most cities below a certain population size because of the nature of the paper's listwise deletion.
+It may be that small cities are more likely to be missing data, and thus they were more likely to be dropped in @trounstine_segregation_2016's analysis.
+Referring back to @baqir_public_1999, I decided to divide the orginal sample based upon the populaiton cutoff for cities used in that paper, which determined that the populaiton must be above 25,000 people for an area to be considered a city.
+Splitting the financial segregation dataset into two datasets, one above and one below the 25,000 population cutoff, I then imputed missing values and used the multiply imputed datasets in Trounstine's original models.
+
+Figure XXX displays the populaiton distributions used in each of these analyses.
+The figure makes it clear that the observations included in @trounstine_segregation_2016's original analysis were not representative of the original datasample with the missing values, as most of the cities with lower populations were excluded as a result of the list-wise data deletion.
+While the dataset generated from the data imputation on the whole sample also has a different distribution for city populaiton, the range of the data seems to be much more representative of the overall data range in comparison to the @trounstine_segregation_2016 sample.
+For comparison, I also include the distributions of the multiply imputed datasets above and below the 25,000 populaiton cutoff.
+For cities above the cutoff, the city population distribution is similar to the distribution in @trounstine_segregation_2016.
+
+```{r population_over_Baqir, include = FALSE}
+
+# Baqir et al uses city as population above 25,000
+
+baqir <- log(25000)
+
+fin_imp_pop_over_baqir <- fin_imp %>%
+  filter(logpop > baqir )
+
+nrow(fin_imp_pop_over_baqir)
+median(fin_imp_pop_over_baqir$logpop)
+
+gg_miss_var(fin_imp_pop_over_baqir, show_pct = T)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_pop_over_baqir, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_fs_pop_overbaqir <- mice(fin_imp_pop_over_baqir, method = meth, maxit = 5)
+
+```
+
+```{r over_baqir_1st_specification, include = FALSE}
+
+# fit multiple imputed datasets
+
+fit_over_baqir_1 <- with(imp_fs_pop_overbaqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp  + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fit_over_baqir_1 <- pool(fit_over_baqir_1)
+imp_over_baqir_1_sum <- summary(pool_fit_over_baqir_1)
+
+```
+
+```{r population_under_Baqir, include = FALSE}
+
+# Baqir et al uses city as population above 25,000
+
+baqir <- log(25000)
+
+fin_imp_pop_under_baqir <- fin_imp %>%
+  filter(logpop < baqir )
+
+nrow(fin_imp_pop_under_baqir)
+median(fin_imp_pop_under_baqir$logpop)
+
+gg_miss_var(fin_imp_pop_under_baqir, show_pct = T)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_pop_under_baqir, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_fs_pop_under_baqir <- mice(fin_imp_pop_under_baqir, method = meth, maxit = 1)
+
+```
+
+```{r population_under_Baqir_1st_specification, include = FALSE}
+
+# fit multiple imputed datasets
+
+fit_under_baqir_1 <- with(imp_fs_pop_under_baqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp +  logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fit_under_baqir_1 <- pool(fit_under_baqir_1)
+imp_under_baqir_1_sum <- summary(pool_fit_under_baqir_1)
+
+```
+
+```{r calc_coeff_sds_original_fs_impute, include = FALSE}
+
+model_coeff <- tibble(
+  variable = c("White/Non-White Seg. Index", "Diversity", 
+               "White/Non-White Seg. Index", "Diversity",
+               "White/Non-White Seg. Index", "Diversity", 
+               "White/Non-White Seg. Index", "Diversity"),
+  estimate = c(imp_under_baqir_1_sum[1,2], imp_under_baqir_1_sum[2,2],
+               imp_felm1_sum[1,2], imp_felm1_sum[2,2],
+               coef(felm1)[1], coef(felm1)[2],
+               imp_over_baqir_1_sum[1,2], imp_over_baqir_1_sum[2,2]),
+  std_error = c(imp_under_baqir_1_sum[1,3], imp_under_baqir_1_sum[2,3],
+                imp_felm1_sum[1,3], imp_felm1_sum[2,3],
+                summary(felm1)$coeff[1,2], summary(felm1)$coeff[2,2],
+                imp_over_baqir_1_sum[1,3], imp_over_baqir_1_sum[2,3]),
+  model = c( "fin_imp_pop_under_baqir", "fin_imp_pop_under_baqir",
+             "fin_imp", "fin_imp",
+            "fin_dge", "fin_dge",
+            "fin_imp_pop_over_baqir", "fin_imp_pop_over_baqir")
+)
+
+model_coeff <- model_coeff %>%
+  mutate(variable = as.factor(variable))
+
+```
+
+```{r dataset_rows_in_analysis}
+
+complete_fs <- complete(imp_fs,1) %>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+complete_over_baqir <- complete(imp_fs_pop_overbaqir, 1)%>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+complete_under_baqir <- complete(imp_fs_pop_under_baqir, 1)%>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+```
+
+```{r dataset_medians}
+
+data_info <- tibble(
+  dataset = c("fin_imp", "fin_imp_pop_over_baqir", "fin_imp_pop_under_baqir",
+               "fin_dge"),
+  median = c(median(fin_imp$logpop), median(fin_imp_pop_over_baqir$logpop),
+              median(fin_imp_pop_under_baqir$logpop), median(fin_dge$logpop)),
+  rows = c(nrow(complete_fs), nrow(complete_over_baqir), nrow(complete_under_baqir),
+          nrow(fin_dge))
+)
+
+model_summaries <- left_join(model_coeff, data_info, by = c("model" = "dataset"))
+
+```
+
+```{r histograms_city_pop_in_specifications_prep, include = FALSE}
+
+pop_data_over_baqir <- tibble(
+  log_pop = complete_over_baqir$logpop,
+  Analysis = "Imputed, pop. > 25k"
+)
+
+pop_data_under_baqir <- tibble(
+  log_pop = complete_under_baqir$logpop,
+  Analysis = "Imputed, pop. < 25k"
+)
+
+pop_data_imp_fs <- tibble(
+  log_pop = complete_fs$logpop,
+  Analysis = "Imputed, Whole Sample"
+)
+
+pop_data_fin_dge <- tibble(
+  log_pop = fin_dge$logpop,
+  Analysis = "Trounstine (2016)"
+)
+
+pop_data_fin_seg <- tibble(
+  log_pop = fin_seg$logpop,
+  Analysis = "Original Sample"
+)
+
+pop_hist_data <- rbind(pop_data_over_baqir, pop_data_imp_fs)
+pop_hist_data <- rbind(pop_hist_data, pop_data_under_baqir)
+pop_hist_data <- rbind(pop_hist_data, pop_data_fin_dge)
+pop_hist_data <- rbind(pop_hist_data, pop_data_fin_seg)
+
+median_pops <- tibble(
+  Analysis = c("Imputed, pop. > 25k", "Imputed, pop. < 25k", "Imputed, Whole Sample", "Trounstine (2016)", "Original Sample"),
+  median_log_pop = c(median(complete(imp_fs_pop_overbaqir,1)$logpop),
+                     median(complete(imp_fs_pop_under_baqir, 1)$logpop),
+                     median(complete(imp_fs, 1)$logpop),
+                     median(fin_dge$logpop),
+                     median(fin_seg$logpop, na.rm = T))
+)
+
+pop_hist_data <- left_join(pop_hist_data, median_pops)
+
+```
+
+```{r city_pops_histogram, echo = FALSE, warning = FALSE}
+
+pop_hist_data %>%
+  ggplot() +
+  geom_histogram(aes(x = log_pop, fill = Analysis)) +
+  geom_vline(aes(xintercept = median_log_pop), color = "red") +
+  facet_wrap(~Analysis) +
+  coord_cartesian(xlim = c(0,15)) +
+  ggtitle("Histograms of Log Population of City Observations Included in the\nVarious Regression Analyses") +
+  labs(caption = "This figure makes clear the differences in city size (in terms of population) among the different analyses.\n It is clear that the listwise deletion of observations with missing values resulted in a sample that almost entirely\nconsisted of larger cities in Trounstine (2016).
+The distribution of city population in Trounstine (2016)\nmore closely resembles the distribution of the original sample with a greater than 25,000 population\ncutoff imposed than the original sample.
+The red lines indicate the median log population in each sample.") +
+  ylab("Count") +
+  xlab("Log Population") +
+  theme_bw() +
+  theme(plot.caption = element_text(hjust = 0),
+        strip.text.x = element_text(size = 8))
+
+```
+
+The results of the models run with the multiply imputed datasets above and below the cutoff are presented in the following two tables.
+
+```{r over_baqir_t1, echo = FALSE}
+
+# print results of 1st regression
+
+imp_over_baqir_1_sum_table <- as.data.frame(imp_over_baqir_1_sum %>% 
+  select(term, estimate, std.error, p.value))
+
+imp_over_baqir_1_sum_table_vars <- tibble(
+  Variable = c("White/Nonwhite Seg. Index", "Diversity", "% Black", "% Asian", "% Latino", "Median Income (1000s)", "% Local Gov. Worker", "% Renters", "% 65+", "% College Grads", "Pop (logged)"),
+  Estimate = round(imp_over_baqir_1_sum_table$estimate, 3),
+  `Std. Error` = round(imp_over_baqir_1_sum_table$std.error,3),
+  `P-Value` = round(imp_over_baqir_1_sum_table$p.value, 3)
+)
+
+kable(imp_over_baqir_1_sum_table_vars, "latex",
+      caption = "\\textbf{Effect of Segregation on Overall per Capita Direct General City Expenditures: Imputed Data for Cities with Populations of 25,000+}",
+      booktabs = T) %>%
+    row_spec(0, bold = TRUE) %>%
+  footnote(general = c("This table shows the results of Trounstine's third model for the effect of segregation on political polarization",
+  "(racial vote divide) using the two-group Theil's H segregation Index and including controls for ideology",
+  "using the new, multiply imputed datasets. Compared to Trounstine's original results, the main coefficient on",
+  "segregation index has decreased in magnitude although, it remains statistically significant. The other",
+  "coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian and",
+  "Black have switched signs. Standard errors have also reduced slightly in these specifications compared to",
+  "the original analysis in Trounstine (2016)."),
+           general_title = "Table 6:") %>%
+  kable_styling(full_width = TRUE)
+
+```
+
+As a summary of all of the model results for the two main coefficients of interest, segregation index and diversity, a coefficient plot is presented in Figure XXX, with the models ordered by increasing median log population size of the sample on the x-axis.
+Looking first at the coefficients for diversity, the two models with low median city populaiton size have significant, positive coefficients, while the models with the larger median city populations have insignificant coefficients.
+This suggestst that diversity is an important estimator of public goods spending for small, but not necessarily for large, cities.
+Next, looking at the plot for the segregation index, we see the oppposite effect.
+For the models where the median city population sizes were small, the coefficient on segregaiton is insignificant.
+However, for the two models with larger median city populations, the coefficients were significant and negative.
+This suggests that for small cities, segregation is not a very good estimator of public goods spending, but when cities are larger, increases in a city's segregation index are associated with decreases in public goods spending.
+
+```{r coef_plot_originals_over_under, echo = FALSE}
+
+model_summaries %>%
+  ggplot(aes(x = median, y = estimate)) +
+  geom_point()+
+  geom_errorbar(aes(ymin = estimate - 2 * std_error, ymax = estimate + 2 * std_error, width = .2)) +
+  geom_hline(yintercept = 0, color = "red") +
+  facet_wrap(~variable, labeller = labeller(variable = coef.labels)) +
+  ggtitle("Coefficient Plots for Diversity and White/Non-White Segregation Indices Across\nthe Models")+
+  xlab("Models Ordered by Increasing Median Population Size of the Sample") +
+  ylab("Estimate and 95% Confidence Interval") +
+  labs(caption = "This plot demonstrates how the significance of diversity and segregation in predicting public\ngoods spending varies with city size.
+As city populaiton size increases, diversity tends to have\nless explanatory power for public goods spending while segregation has more.
+The opposite\nis true when considering city population size decreasing: segregation becomes less important\nas diversity becomes increasingly important.") +
+  theme_bw()+
+  theme(plot.caption = element_text(hjust = 0))
+
+```
+
+# Conclusion
+
+Why cities differ in their amount of spending on public goods is an interesting questions that is frequently debated in the literature.
+@trounstine_segregation_2016 posits that segregation may be an important underlying cause of the underprovsion of public goods.
+Finding evidence that residential segregation by race increases political partisanship, @trounstine_segregation_2016 argues that residential segregation can increase division and make cooperation amongst competing groups difficult, which results in decreased spending on public goods.
+The findings of @trounstine_segregation_2016 are particularly important because they suggest that segregation, as defined by many homogeneous neighborhoods within a larger diverse geographical area, is the key factor in disinvestment in public goods.
+This contradicts previous research which has suggested that levels of diversity were instead most important (see for example @baqir_public_1999 or @hopkins_diversity_2009).
+While @trounstine_segregation_2016 still represents relatively new reasearch as of 2020, it has yet to be fully vetted by additional research.
+Furthermore, some research that has been published on the topic since its publication suggests that other factors such as larger inequities in the political system favoring socially powerful groups [@lee_ethnic_2018] or the interaction of income and racial inequality [@an_its_2018] may be more important in explaining public goods provisions.
+
+I first worked to provide a check on the analysis presented in @trounstine_segregation_2016 by attempting to replicate the work in R.
+I was able to successfully replicate all of the main results from @trounstine_segregation_2016, with the exception of a few of a few marginal analyses of the complex, multi-level models which, to my knowledge, are currently not supported by available R packages.
+I was, however, able to successfully replicate these results in Stata.
+
+As an additional robustness check I also tested the models in @trounstine_segregation_2016 by re-running them with additional data that I imputed from missing values in the original datasets.
+The large number of missing values in both of the datasets used in @trounstine_segregation_2016's main analysis created a concern for potential bias in the original results and a lack of representativeness due to the large amount of data excluded from the regression analysis due to missing values.
+Thus, I used the mice package in R to create multiply imputed datasets, upon which I re-ran the models and pooled the results to generate the final model coefficients and parameters.
+
+The results of the data imputation exercise differed between the two datasets.
+For the analyses using the smaller, racial polarization dataset, the results from the imputed data resulted in a smaller magnitude of the coefficient on the main independent variable, and also made it statistically insignificant in the main model specification.
+This suggests that the segregation index may not have as strong of a positive association with political polarization as @trounstine_segregation_2016 suggests.
+Nevertheless, the imputation exercise generally supports the main ideas in this part of Trounstine's analysis.
+
+On the other hand, for the analyses using the much larger financial segregation dataset, the results of the models using the multiply imputed data sharply contrasted the results of @trounstine_segregation_2016, suggesting that diversity, and not segregation, was the best explanatory variable for public goods spending across cities.
+While these results originally seemed quite contradictory, I was able reconcile this finding by discovering that the results of @trounstine_segregation_2016 seem to be only really representative of larger cities.
+By dropping all observations in the original data with missing values for key variables, it seems that @trounstine_segregation_2016 inadvertently restricted their sample to almost entirely larger cities (above 25,000 residents) whereas the full sample consisted of cities that had smaller populaitons.
+To test the hypothesis that diversity is more important for predicting public goods spending for small cities while segregation is more important for predicting public goods spending for larger cities, I divided the original dataset into two subsets based on the city classificaiton criteria used in @baqir_public_1999 that cities must have a population of at least 25,000 people.
+I then multiply imputed the missing values for each data subset and re-ran the models.
+I found that the results presented initial evidence in support of my hypothesis.
+for the cities below the 25,000 person populaiton cutoff, the coefficient for diversity was positive and significant while the coefficient for the segregation index was insignificant.
+For cities above the 25,000 person cutoff, the results were very similar to the results found in @trounstine_segregation_2016: the coefficient for diversity was insignificant, but the coefficient for the segregation index was significant and negative.
+
+The replication exercise and the robustness check of @trounstine_segregation_2016's model using multiply imputed data provide additional evidence that residential racial segregation is associated with political polarization.
+Furthermore, I find evidence that supports the finding of @trounstine_segregation_2016 that increases in segregation are associated with decreases in public goods spending; however, I find that this is only the case for larger cities.
+In contrast to the argument made by @trounstine_segregation_2016, I find that, for small cities, diversity, not segregation, seems to be the most important explanatory variable for public goods spending.
+One potential explanation for this result could be that when cities become too small, the sort of segregation by neighborhood described in @trounstine_segregation_2016 as a diverse city broken down into homogenous, segregated neighborhoods becomes hard to maintain.
+When populaiton sizes are small, segregation may become difficult and inter-racial interactions may become more common, leading diversity to be more indicative of a degree of integration.
+This provides a possible explanation as to why the coefficient on diversity was positive for very small cities, as these "cities" may function more closely as neighborhoods (many of them with populaitons ranging from X-X thousand); as discussed in the literature review, diversity at the neighborhood level is associated with lower levels of political polarization (Oliver 2010) and thus we would expect these areas to have higher levels of public goods spending according to the ideas of @trounstine_segregation_2016.
+As cities become larger and larger, however, comprehensive segregation becomes more attainable.
+Thus, as cities become larger, segregation, not diversity, becomes a better indicator of inter-racial harmony and cooperation and thus the best explanatory variable for public goods spending.
+
+It is possible that other mechanisms may be more important in explaining why segregation might be associated with decreased spending on public goods.
+For example, it could be that there is an important interaction effect between income and segregation, as others have previously suggested, or there could be some other intervening mechanism or a confounding variable that is leading to the negative association between segregation and lower spending on public goods.
+@trounstine_segregation_2016 has identified an important relationship between segregation and the provision of public goods.
+However, my analysis suggests that further research is needed to assess the potential mechanisms by which residential segregation by race or even a confounding variable may result in dimished spending.
+If this mechanism can be better understood, than it will be possible to more effectively understand and address the underprovision of public goods, which may inhibit social mobility and unfairly disadvantage certain groups.
 

### 2020-05-07 final_draft_extension_fs.Rmd
edits to text

@@
 nrow(fin_imp_pop_over_baqir)
+median(fin_imp_pop_over_baqir$logpop)
 
@@
 
-fit_over_baqir_1 <- with(imp_fs_pop_overbaqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+fit_over_baqir_1 <- with(imp_fs_pop_overbaqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
 
@@
 nrow(fin_imp_pop_under_baqir)
+median(fin_imp_pop_under_baqir$logpop)
 
@@
 
-fit_under_baqir_1 <- with(imp_fs_pop_under_baqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+fit_under_baqir_1 <- with(imp_fs_pop_under_baqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
 
@@
 
-```{r histograms_city_pop_in_specifications_prep, include = FALSE}
-
-pop_data_over_baqir <- tibble(
-  log_pop = complete(imp_fs_pop_overbaqir,1)$logpop,
-  Analysis = "Imputed, pop. > 25k"
-)
-
-pop_data_under_baqir <- tibble(
-  log_pop = complete(imp_fs_pop_under_baqir, 1)$logpop,
-  Analysis = "Imputed, pop. < 25k"
-)
-
-pop_data_imp_fs <- tibble(
-  log_pop = complete(imp_fs, 1)$logpop,
-  Analysis = "Imputed, Whole Sample"
-)
-
-pop_data_fin_dge <- tibble(
-  log_pop = fin_dge$logpop,
-  Analysis = "Trounstine (2016)"
-)
-
-pop_data_fin_seg <- tibble(
-  log_pop = fin_seg$logpop,
-  Analysis = "Original Sample"
-)
-
-pop_hist_data <- rbind(pop_data_over_baqir, pop_data_imp_fs)
-pop_hist_data <- rbind(pop_hist_data, pop_data_under_baqir)
-pop_hist_data <- rbind(pop_hist_data, pop_data_fin_dge)
-pop_hist_data <- rbind(pop_hist_data, pop_data_fin_seg)
-
-median_pops <- tibble(
-  Analysis = c("Imputed, pop. > 25k", "Imputed, pop. < 25k", "Imputed, Whole Sample", "Trounstine (2016)", "Original Sample"),
-  median_log_pop = c(median(complete(imp_fs_pop_overbaqir,1)$logpop),
-                     median(complete(imp_fs_pop_under_baqir, 1)$logpop),
-                     median(complete(imp_fs, 1)$logpop),
-                     median(fin_dge$logpop),
-                     median(fin_seg$logpop, na.rm = T))
-)
-
-pop_hist_data <- left_join(pop_hist_data, median_pops)
-
-```
-
-```{r city_pops_histogram, echo = FALSE, warning = FALSE}
-
-pop_hist_data %>%
-  ggplot() +
-  geom_histogram(aes(x = log_pop, fill = Analysis)) +
-  geom_vline(aes(xintercept = median_log_pop), color = "red") +
-  facet_wrap(~Analysis) +
-  coord_cartesian(xlim = c(0,15)) +
-  ggtitle("Histograms of Log Populaiton of City Observations Included in the\nVarious Regression Analyses") +
-  labs(caption = "This figure makes clear the differences in city size (in terms of population) among the different analyses.\n It is clear that the listwise deletion of observations with missing values resulted in a sample that almost entirely\nconsisted of larger cities in Trounstine (2016).
-The distribution of city population in Trounstine (2016)\nmore closely resembles the distribution of the original sample with a greater than 25,000 population\ncutoff imposed than the original sample.
-The red lines indicate the median log population in each sample.") +
-  ylab("Count") +
-  xlab("Log Population") +
-  theme_bw() +
-  theme(plot.caption = element_text(hjust = 0),
-        strip.text.x = element_text(size = 8))
-
-```
-
 ```{r top_1_%_pop}
@@
 nrow(fin_imp_top_1)
-
+median(fin_imp_top_1$logpop)
 # generate a blank run to get the method matrix
@@
 
-fit_fs_pop_top_1 <- with(imp_fs_pop_top_1, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+fit_fs_pop_top_1 <- with(imp_fs_pop_top_1, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
 
@@
 
-```{r}
-fin_seg %>%
-  ggplot(aes(x = logpop)) +
-  geom_histogram() +
-  geom_vline(aes(xintercept = log(25000)))
-
-log(25000)
-```
-
 ```{r bottom_60_%_pop}
@@
 nrow(fin_imp_bottom_60)
+median(fin_imp_bottom_60$logpop)
 
@@
 
-fit_imp_bottom_60 <- with(imp_bottom_60, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+fit_imp_bottom_60 <- with(imp_bottom_60, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
 
@@
 
+```{r 60-80}
+
+quantile(fin_seg$logpop, c(.60, .8), na.rm = T)
+
+fin_imp_60_80 <- fin_imp %>%
+  filter(logpop > quantile(fin_seg$logpop, c(.60), na.rm = T) & logpop < quantile(fin_seg$logpop, c(.80), na.rm = T))
+
+nrow(fin_imp_60_80)
+median(fin_imp_60_80$logpop)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_60_80, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_60_80 <- mice(fin_imp_60_80, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_60_80 <- with(imp_60_80, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fs_60_80 <- pool(fit_imp_60_80)
+imp_fs_60_80 <- summary(pool_fs_60_80)
+
+```
+
+```{r 80-100}
+
+quantile(fin_seg$logpop, c(.60, .8), na.rm = T)
+
+fin_imp_80_100 <- fin_imp %>%
+  filter(logpop > quantile(fin_seg$logpop, c(.80), na.rm = T) & logpop < quantile(fin_seg$logpop, c(1), na.rm = T))
+
+nrow(fin_imp_80_100)
+median(fin_imp_80_100$logpop)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_80_100, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_80_100 <- mice(fin_imp_80_100, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_80_100 <- with(imp_80_100, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fs_80_100 <- pool(fit_imp_80_100)
+imp_fs_80_100 <- summary(pool_fs_80_100)
+
+```
+
+```{r 80-90}
+
+quantile(fin_seg$logpop, c(.60, .8), na.rm = T)
+
+fin_imp_80_90 <- fin_imp %>%
+  filter(logpop > quantile(fin_seg$logpop, c(.80), na.rm = T) & logpop < quantile(fin_seg$logpop, c(.9), na.rm = T))
+
+nrow(fin_imp_80_90)
+median(fin_imp_80_90$logpop)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_80_90, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_80_90 <- mice(fin_imp_80_90, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_80_90 <- with(imp_80_90, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fs_80_90 <- pool(fit_imp_80_90)
+imp_fs_80_90 <- summary(pool_fs_80_90)
+
+```
+
+```{r 90-100}
+
+fin_imp_90_100 <- fin_imp %>%
+  filter(logpop > quantile(fin_seg$logpop, c(.90), na.rm = T) & logpop < quantile(fin_seg$logpop, c(1), na.rm = T))
+
+nrow(fin_imp_90_100)
+median(fin_imp_90_100$logpop)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_90_100, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_90_100 <- mice(fin_imp_90_100, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_90_100 <- with(imp_90_100, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fs_90_100 <- pool(fit_imp_90_100)
+imp_fs_90_100 <- summary(pool_fs_90_100)
+
+quantile(fin_seg$logpop, c(.90), na.rm = T) & logpop < quantile(fin_seg$logpop, c(1), na.rm = T)
+
+exp(quantile(fin_seg$logpop, c(.90), na.rm = T))
+exp(quantile(fin_seg$logpop, c(.95), na.rm = T))
+exp(quantile(fin_seg$logpop, c(1), na.rm = T))
+
+```
+
+```{r 25_100k}
+
+fin_imp_25_100k <- fin_imp %>%
+  filter(logpop < log(100000) & logpop > log(25000))
+
+nrow(fin_imp_25_100k)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_25_100k, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_25_100k <- mice(fin_imp_25_100k, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_25_100k <- with(imp_25_100k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses: insignificant for both
+
+pool_fs_25_100k<- pool(fit_imp_25_100k)
+imp_fs_pop_25_100k<- summary(pool_fs_25_100k)
+
+```
+
+```{r 100-250k}
+
+fin_imp_100_250k <- fin_imp %>%
+  filter(logpop > log(100000) & logpop < log(250000))
+
+nrow(fin_imp_100_250k)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_100_250k, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_100_250k <- mice(fin_imp_100_250k, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_100_250k <- with(imp_100_250k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses: insignificant for both
+
+pool_fs_100_250k<- pool(fit_imp_100_250k)
+imp_fs_pop_100_250k <- summary(pool_fs_100_250k)
+
+```
+
+```{r 250_500k}
+
+fin_imp_250_500k <- fin_imp %>%
+  filter(logpop < log(500000) & logpop > log(250000))
+
+nrow(fin_imp_250_500k)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_250_500k, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_250_500k <- mice(fin_imp_250_500k, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_250_500k <- with(imp_250_500k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses: insignificant for both
+
+pool_fs_250_500k <- pool(fit_imp_250_500k)
+imp_fs_pop_250_500k <- summary(pool_fs_250_500k)
+
+```
+
 ```{r 50k}
@@
 
-fit_imp_50k <- with(imp_50k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+fit_imp_50k <- with(imp_50k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
 
@@
 
-fit_imp_250k <- with(imp_250k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+fit_imp_250k <- with(imp_250k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
 
@@
 
-```{r 500k}
+```{r 25_50k}
+
+fin_imp_25_50k <- fin_imp %>%
+  filter(logpop > log(25000) & logpop < log(50000))
+
+nrow(fin_imp_25_50k)
+median(fin_imp_25_50k$logpop)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_25_50k, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_25_50k <- mice(fin_imp_25_50k, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_25_50k <- with(imp_25_50k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fs_25_50k<- pool(fit_imp_25_50k)
+imp_fs_pop_25_50k<- summary(pool_fs_25_50k)
+
+```
+
+```{r 50_100k}
+
+fin_imp_50_100k <- fin_imp %>%
+  filter(logpop > log(50000) & logpop < log(100000))
+
+nrow(fin_imp_50_100k)
+median(fin_imp_50_100k$logpop)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_50_100k, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_50_100k <- mice(fin_imp_50_100k, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_50_100k<- with(imp_50_100k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fs_50_100k <- pool(fit_imp_50_100k)
+imp_fs_pop_50_100k <- summary(pool_fs_50_100k)
+
+```
+
+```{r 100_250k}
+
+fin_imp_100_250k <- fin_imp %>%
+  filter(logpop > log(100000) & logpop < log(250000))
+
+nrow(fin_imp_100_250k)
+median(fin_imp_100_250k$logpop)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_100_250k, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_100_250k <- mice(fin_imp_100_250k, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_100_250k<- with(imp_100_250k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fs_100_250k <- pool(fit_imp_100_250k)
+imp_fs_pop_100_250k <- summary(pool_fs_100_250k)
+
+```
+
+```{r 250_500K}
 
@@
 
+nrow(fin_imp_250_500k)
+median(fin_imp_250_500k$logpop)
+
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_250_500k, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_250_500k <- mice(fin_imp_250_500k, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_250_500k<- with(imp_250_500k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fs_250_500k <- pool(fit_imp_250_500k)
+imp_fs_pop_250_500k <- summary(pool_fs_250_500k)
+
+```
+
+```{r 500_1m}
+
+fin_imp_500_1m <- fin_imp %>%
+  filter(logpop > log(500000) & logpop < log(1000000))
+
+nrow(fin_imp_500_1m)
+median(fin_imp_500_1m$logpop)
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_500_1m, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_500_1m <- mice(fin_imp_500_1m, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_500_1m<- with(imp_500_1m, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fs_500_1m <- pool(fit_imp_500_1m)
+imp_fs_pop_500_1m <- summary(pool_fs_500_1m)
+
+```
+
+```{r 1m+}
+
+fin_imp_1m <- fin_imp %>%
+  filter(logpop > log(1000000))
+
+nrow(fin_imp_1m)
+median(fin_imp_1m$logpop)
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_1m, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_1m <- mice(fin_imp_1m, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_1m<- with(imp_1m, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fs_1m <- pool(fit_imp_1m)
+imp_fs_pop_1m <- summary(pool_fs_1m)
+
+```
+
+```{r 500,000+}
+
+fin_imp_500k <- fin_imp %>%
+  filter(logpop > log(500000))
+
+nrow(fin_imp_500k)
+median(fin_imp_500k$logpop)
+# generate a blank run to get the method matrix
+
+ini <- mice(fin_imp_500k, maxit = 0, print = FALSE)
+
+# view the current method settings
+
+meth <- ini$method
+
+# change the method variables for all variables except H_citytract_NHW_i to ""
+# so that their missing values aren't imputed
+
+meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
+         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
+         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
+
+# change the default method to "cart" so that we don't get the error
+
+meth[c("H_citytract_NHW_i", "chng5pctblk", 
+       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
+
+# perform the multiple imputations with 5 iterations
+
+imp_500k <- mice(fin_imp_500k, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_500k <- with(imp_500k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fs_500k <- pool(fit_imp_500k)
+imp_fs_pop_500k <- summary(pool_fs_500k)
+
+```
+
+```{r 250,000+}
+
+fin_imp_250k <- fin_imp %>%
+  filter(logpop > log(250000))
+
 nrow(fin_imp_250k)
-
+median(fin_imp_250k$logpop)
 # generate a blank run to get the method matrix
@@
 
-imp_250k <- mice(fin_imp_250k, method = meth, maxit = 1)
-
-# fit multiple imputed datasets
-
-fit_imp_250k <- with(imp_250k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_fs_250k<- pool(fit_imp_250k)
-imp_fs_pop_250k<- summary(pool_fs_250k)
+imp_250k <- mice(fin_imp_250k, method = meth, maxit = 5)
+
+# fit multiple imputed datasets
+
+fit_imp_250k <- with(imp_250k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_fs_250k <- pool(fit_imp_250k)
+imp_fs_pop_250k <- summary(pool_fs_250k)
 
@@
 imp_over_baqir_1_sum
-#coef(felm1)[1]
+coef(felm1)[1]
 imp_fs_pop_top_1_sum
@@
                "White/Non-White Seg. Index", "Diversity",
-               #"White/Non-White Seg. Index", "Diversity",
+               "White/Non-White Seg. Index", "Diversity", 
+               "White/Non-White Seg. Index", "Diversity",
+               "White/Non-White Seg. Index", "Diversity",
+               "White/Non-White Seg. Index", "Diversity",
+               "White/Non-White Seg. Index", "Diversity", 
+               "White/Non-White Seg. Index", "Diversity", 
+               "White/Non-White Seg. Index", "Diversity",
+               "White/Non-White Seg. Index", "Diversity",
+               "White/Non-White Seg. Index", "Diversity", 
+               "White/Non-White Seg. Index", "Diversity",
+               "White/Non-White Seg. Index", "Diversity",
+               "White/Non-White Seg. Index", "Diversity",
+                "White/Non-White Seg. Index", "Diversity",
+               "White/Non-White Seg. Index", "Diversity",
+               "White/Non-White Seg. Index", "Diversity",
                 "White/Non-White Seg. Index", "Diversity",
@@
                imp_felm1_sum[1,2], imp_felm1_sum[2,2],
-               #coef(felm1)[1], coef(felm1)[2],
+                imp_fs_pop_bottom_60[1,2], imp_fs_pop_bottom_60[2,2],
+               imp_fs_60_80[1,2], imp_fs_60_80[2,2],
+                imp_fs_80_90[1,2], imp_fs_80_90[2,2],
+                imp_fs_80_100[1,2], imp_fs_80_100[2,2],
+               coef(felm1)[1], coef(felm1)[2],
+               imp_fs_90_100[1,2], imp_fs_90_100[2,2],
+               imp_fs_pop_25_50k[1,2], imp_fs_pop_25_50k[2,2],
+               imp_fs_pop_top_1_sum[1,2], imp_fs_pop_top_1_sum[2,2],
                imp_over_baqir_1_sum[1,2], imp_over_baqir_1_sum[2,2],
-               imp_fs_pop_top_1_sum[1,2], imp_fs_pop_top_1_sum[2,2]),
+               imp_fs_pop_50_100k[1,2], imp_fs_pop_50_100k[2,2],
+               imp_fs_pop_100_250k[1,2], imp_fs_pop_100_250k[2,2],
+               imp_fs_pop_250_500k[1,2], imp_fs_pop_250_500k[2,2],
+               imp_fs_pop_500_1m[1,2], imp_fs_pop_500_1m[2,2],
+               imp_fs_pop_1m[1,2], imp_fs_pop_1m[2,2],
+                imp_fs_pop_25_100k[1,2], imp_fs_pop_25_100k[2,2],
+               imp_fs_pop_100_250k[1,2], imp_fs_pop_100_250k[2,2],
+               imp_fs_pop_250_500k[1,2], imp_fs_pop_250_500k[2,2]),
   std_error = c(imp_under_baqir_1_sum[1,3], imp_under_baqir_1_sum[2,3],
                 imp_felm1_sum[1,3], imp_felm1_sum[2,3],
-                #summary(felm1)$coeff[1,2], summary(felm1)$coeff[2,2],
+                imp_fs_pop_bottom_60[1,3], imp_fs_pop_bottom_60[2,3],
+                imp_fs_60_80[1,3], imp_fs_60_80[2,3],
+                imp_fs_80_90[1,3], imp_fs_80_90[2,3],
+                imp_fs_80_100[1,3], imp_fs_80_100[2,3],
+                summary(felm1)$coeff[1,2], summary(felm1)$coeff[2,2],
+                imp_fs_90_100[1,3], imp_fs_90_100[2,3],
+                imp_fs_pop_25_50k[1,3], imp_fs_pop_25_50k[2,3],
+                imp_fs_pop_top_1_sum[1,3], imp_fs_pop_top_1_sum[2,3],
                 imp_over_baqir_1_sum[1,3], imp_over_baqir_1_sum[2,3],
-                imp_fs_pop_top_1_sum[1,3], imp_fs_pop_top_1_sum[2,3]),
-  model = c(1, 1, 
-            2, 2,
-            #3, 3,
-            3, 3,
-            5, 5)
+                imp_fs_pop_50_100k[1,3], imp_fs_pop_50_100k[2,3],
+                imp_fs_pop_100_250k[1,3], imp_fs_pop_100_250k[2,3],
+                imp_fs_pop_250_500k[1,3], imp_fs_pop_250_500k[2,3],
+                imp_fs_pop_500_1m[1,3], imp_fs_pop_500_1m[2,3],
+                imp_fs_pop_1m[1,3], imp_fs_pop_1m[2,3],
+                imp_fs_pop_25_100k[1,3], imp_fs_pop_25_100k[2,3],
+               imp_fs_pop_100_250k[1,3], imp_fs_pop_100_250k[2,3],
+               imp_fs_pop_250_500k[1,3], imp_fs_pop_250_500k[2,3]),
+  model = c( "fin_imp_pop_under_baqir", "fin_imp_pop_under_baqir",
+             "fin_imp", "fin_imp",
+             "fin_imp_bottom_60",  "fin_imp_bottom_60", 
+             "fin_imp_60_80", "fin_imp_60_80", 
+             "fin_imp_80_90", "fin_imp_80_90",
+             "fin_imp_80_100", "fin_imp_80_100",
+            "fin_dge", "fin_dge",
+            "fin_imp_90_100", "fin_imp_90_100",
+            "fin_imp_25_50k", "fin_imp_25_50k",
+            "fin_imp_top_1", "fin_imp_top_1",
+            "fin_imp_pop_over_baqir", "fin_imp_pop_over_baqir",
+            "fin_imp_50_100k", "fin_imp_50_100k",
+            "fin_imp_100_250k", "fin_imp_100_250k",
+            "fin_imp_250_500k", "fin_imp_250_500k",
+            "fin_imp_500_1m", "fin_imp_500_1m",
+            "fin_imp_1m", "fin_imp_1m",
+            "fin_imp_25_100", "fin_imp_25_100",
+            "fin_imp_100_250", "fin_imp_100_250",
+            "fin_imp_250_500", "fin_imp_250_500")
 )
@@
 
+```{r dataset_rows_in_analysis}
+
+complete_fs <- complete(imp_fs,1) %>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+complete_over_baqir <- complete(imp_fs_pop_overbaqir, 1)%>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+complete_under_baqir <- complete(imp_fs_pop_under_baqir, 1)%>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+complete_top_1 <- complete(imp_fs_pop_top_1, 1)%>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+complete_bottom_60 <- complete(imp_bottom_60, 1)%>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+complete_1m <- complete(imp_1m, 1)%>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+complete_25_50k <- complete(imp_25_50k, 1)%>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+complete_50_100k <- complete(imp_50_100k, 1)%>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+complete_100_250k <- complete(imp_100_250k , 1)%>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+complete_250_500k <- complete(imp_250_500k , 1)%>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+complete_500_1m <- complete(imp_500_1m , 1)%>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+complete_60_80 <- complete(imp_60_80, 1) %>%
+    filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)),
+           !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+complete_80_100 <- complete(imp_80_100, 1) %>%
+    filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)),
+           !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+complete_80_90 <- complete(imp_80_90, 1) %>%
+    filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)),
+           !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+complete_90_100 <- complete(imp_90_100, 1) %>%
+    filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)),
+           !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+```
+
+```{r dataset_medians}
+
+data_info <- tibble(
+  dataset = c("fin_imp", "fin_imp_pop_over_baqir", "fin_imp_pop_under_baqir",
+               "fin_imp_top_1", "fin_imp_bottom_60", "fin_imp_1m", "fin_imp_25_50k", "fin_imp_50_100k", "fin_imp_100_250k", "fin_imp_250_500k", "fin_imp_500_1m", "fin_dge", "fin_imp_60_80", "fin_imp_80_100", "fin_imp_80_90", "fin_imp_90_100", "fin_imp_25_100", "fin_imp_100_250", "fin_imp_250_500"),
+  median = c(median(fin_imp$logpop), median(fin_imp_pop_over_baqir$logpop),
+              median(fin_imp_pop_under_baqir$logpop), median(fin_imp_top_1$logpop),
+              median(fin_imp_bottom_60$logpop), median(fin_imp_1m$logpop),
+             median(fin_imp_25_50k$logpop), median(fin_imp_50_100k$logpop),
+             median(fin_imp_100_250k$logpop), median(fin_imp_250_500k$logpop),
+             median(fin_imp_500_1m$logpop), median(fin_dge$logpop), 
+             median(fin_imp_60_80$logpop), median(fin_imp_80_100$logpop),
+             median(fin_imp_80_90$logpop), median(fin_imp_90_100$logpop),
+             median(fin_imp_25_100k$logpop), median(fin_imp_100_250k$logpop),
+             median(fin_imp_250_500k$logpop)),
+  rows = c(nrow(complete_fs), nrow(complete_over_baqir), nrow(complete_under_baqir),
+           nrow(complete_top_1), nrow(complete_bottom_60), nrow(complete_1m),
+           nrow(complete_25_50k), nrow(complete_50_100k), nrow(complete_100_250k), 
+           nrow(complete_250_500k), nrow(complete_500_1m), nrow(fin_dge),
+           nrow(complete_60_80), nrow(complete_80_100), nrow(complete_80_90),
+           nrow(complete_90_100), NA, NA, NA )
+)
+
+data_info %>%
+  arrange(median)
+
+data_info %>%
+  mutate(full_pop = exp(median)) %>%
+  arrange(median)
+
+model_summaries <- left_join(model_coeff, data_info, by = c("model" = "dataset"))
+
+fin_imp_pop_under_baqir %>%
+  ggplot(aes(x = exp(logpop))) +
+  geom_histogram()
+
+fin_imp_pop_under_baqir %>%
+  filter(logpop < log(1000))
+
+nrow(fin_imp_pop_under_baqir)
+
+```
+
 ```{r coef_plot, echo = FALSE}
 
-coef.labels <- c("Diversity", "White/Non-White Seg. Index")
-names(coef.labels) <- c("Diversity", "White/Non-White Seg. Index")
-
-model_coeff %>%
-  ggplot(aes(x = model, y = estimate)) +
+model_summaries %>%
+  ggplot(aes(x = median, y = estimate)) +
   geom_point()+
@@
 
+```{r coef_plot_originals_over_under, echo = FALSE}
+
+originals_over_under <- c("fin_imp_pop_under_baqir", 
+             "fin_imp", 
+            "fin_dge", 
+            "fin_imp_pop_over_baqir")
+
+model_summaries %>%
+  filter(model %in% originals_over_under) %>%
+  ggplot(aes(x = median, y = estimate)) +
+  geom_point()+
+  geom_errorbar(aes(ymin = estimate - 2 * std_error, ymax = estimate + 2 * std_error, width = .2)) +
+  geom_hline(yintercept = 0, color = "red") +
+  facet_wrap(~variable, labeller = labeller(variable = coef.labels)) +
+  ggtitle("Coefficient Plots for Diversity and White/Non-White Segregation Indices Across\nthe Models")+
+  xlab("Models Ordered by Increasing Median Population Size of the Sample") +
+  ylab("Estimate and 95% Confidence Interval") +
+  labs(caption = "This plot demonstrates how the significance of diversity and segregation in predicting public\ngoods spending varies with city size.
+As city populaiton size increases, diversity tends to have\nless explanatory power for public goods spending while segregation has more.
+The opposite\nis true when considering city population size decreasing: segregation becomes less important\nas diversity becomes increasingly important.") +
+  theme_bw()+
+  theme(plot.caption = element_text(hjust = 0))
+
+```
+
+```{r coef_plot_percentiles, echo = FALSE}
+
+originals_percentiles <- c("fin_imp", "fin_dge", 
+                           "fin_imp_bottom_60",  
+                            "fin_imp_60_80", 
+                            "fin_imp_80_90",
+                           "fin_imp_90_100",
+                           "fin_imp_500_1m",
+                            "fin_imp_1m")
+
+model_summaries %>%
+  filter(model %in% originals_percentiles) %>%
+  ggplot(aes(x = median, y = estimate)) +
+  geom_point()+
+  geom_errorbar(aes(ymin = estimate - 2 * std_error, ymax = estimate + 2 * std_error, width = .2)) +
+  geom_hline(yintercept = 0, color = "red") +
+  facet_wrap(~variable, labeller = labeller(variable = coef.labels)) +
+  ggtitle("Coefficient Plots for Diversity and White/Non-White Segregation Indices Across\nthe Models")+
+  xlab("Models Ordered by Increasing Median Population Size of the Sample") +
+  ylab("Estimate and 95% Confidence Interval") +
+  labs(caption = "This plot demonstrates how the significance of diversity and segregation in predicting public\ngoods spending varies with city size.
+As city populaiton size increases, diversity tends to have\nless explanatory power for public goods spending while segregation has more.
+The opposite\nis true when considering city population size decreasing: segregation becomes less important\nas diversity becomes increasingly important.") +
+  theme_bw()+
+  theme(plot.caption = element_text(hjust = 0))
+
+```
+
+```{r new_ranges}
+
+new_ranges <- c("fin_imp_pop_under_baqir",
+                           "fin_imp_25_100",  
+                            "fin_imp_100_250", 
+                            "fin_imp_250_500",
+                           "fin_imp_500_1m",
+                            "fin_imp_1m")
+
+model_summaries %>%
+  filter(model %in% new_ranges) %>%
+  ggplot(aes(x = median, y = estimate)) +
+  geom_point()+
+  geom_errorbar(aes(ymin = estimate - 2 * std_error, ymax = estimate + 2 * std_error, width = .2)) +
+  geom_hline(yintercept = 0, color = "red") +
+  facet_wrap(~variable, labeller = labeller(variable = coef.labels)) +
+  ggtitle("Coefficient Plots for Diversity and White/Non-White Segregation Indices Across\nthe Models")+
+  xlab("Models Ordered by Increasing Median Population Size of the Sample") +
+  ylab("Estimate and 95% Confidence Interval") +
+  labs(caption = "This plot demonstrates how the significance of diversity and segregation in predicting public\ngoods spending varies with city size.
+As city populaiton size increases, diversity tends to have\nless explanatory power for public goods spending while segregation has more.
+The opposite\nis true when considering city population size decreasing: segregation becomes less important\nas diversity becomes increasingly important.") +
+  theme_bw()+
+  theme(plot.caption = element_text(hjust = 0))
+
+```
+
+```{r}
+first_two <- c("fin_imp", "fin_dge", "fin_imp_pop_under_baqir", "fin_imp_pop_over_baqir")
+
+model_summaries %>%
+  filter(model %in% first_two) %>%
+  ggplot(aes(x = median, y = estimate)) +
+  geom_point()+
+  geom_errorbar(aes(ymin = estimate - 2 * std_error, ymax = estimate + 2 * std_error, width = .2)) +
+  geom_hline(yintercept = 0, color = "red") +
+  facet_wrap(~variable, labeller = labeller(variable = coef.labels)) +
+  ggtitle("Coefficient Plots for Diversity and White/Non-White Segregation Indices Across\nthe Models")+
+  xlab("Models Ordered by Increasing Median Population Size of the Sample") +
+  ylab("Estimate and 95% Confidence Interval") +
+  labs(caption = "This plot demonstrates how the significance of diversity and segregation in predicting public\ngoods spending varies with city size.
+As city populaiton size increases, diversity tends to have\nless explanatory power for public goods spending while segregation has more.
+The opposite\nis true when considering city population size decreasing: segregation becomes less important\nas diversity becomes increasingly important.") +
+  theme_bw()+
+  theme(plot.caption = element_text(hjust = 0))
+```
+
+```{r histograms_city_pop_in_specifications_prep, include = FALSE}
+
+pop_data_over_baqir <- tibble(
+  log_pop = complete_over_baqir$logpop,
+  Analysis = "Imputed, pop. > 25k"
+)
+
+pop_data_under_baqir <- tibble(
+  log_pop = complete_under_baqir$logpop,
+  Analysis = "Imputed, pop. < 25k"
+)
+
+pop_data_imp_fs <- tibble(
+  log_pop = complete_fs$logpop,
+  Analysis = "Imputed, Whole Sample"
+)
+
+pop_data_fin_dge <- tibble(
+  log_pop = fin_dge$logpop,
+  Analysis = "Trounstine (2016)"
+)
+
+pop_data_fin_seg <- tibble(
+  log_pop = fin_seg$logpop,
+  Analysis = "Original Sample"
+)
+
+pop_hist_data <- rbind(pop_data_over_baqir, pop_data_imp_fs)
+pop_hist_data <- rbind(pop_hist_data, pop_data_under_baqir)
+pop_hist_data <- rbind(pop_hist_data, pop_data_fin_dge)
+pop_hist_data <- rbind(pop_hist_data, pop_data_fin_seg)
+
+median_pops <- tibble(
+  Analysis = c("Imputed, pop. > 25k", "Imputed, pop. < 25k", "Imputed, Whole Sample", "Trounstine (2016)", "Original Sample"),
+  median_log_pop = c(median(complete(imp_fs_pop_overbaqir,1)$logpop),
+                     median(complete(imp_fs_pop_under_baqir, 1)$logpop),
+                     median(complete(imp_fs, 1)$logpop),
+                     median(fin_dge$logpop),
+                     median(fin_seg$logpop, na.rm = T))
+)
+
+pop_hist_data <- left_join(pop_hist_data, median_pops)
+
+```
+
+```{r city_pops_histogram, echo = FALSE, warning = FALSE}
+
+pop_hist_data %>%
+  ggplot() +
+  geom_histogram(aes(x = log_pop, fill = Analysis)) +
+  geom_vline(aes(xintercept = median_log_pop), color = "red") +
+  facet_wrap(~Analysis) +
+  coord_cartesian(xlim = c(0,15)) +
+  ggtitle("Histograms of Log Population of City Observations Included in the\nVarious Regression Analyses") +
+  labs(caption = "This figure makes clear the differences in city size (in terms of population) among the different analyses.\n It is clear that the listwise deletion of observations with missing values resulted in a sample that almost entirely\nconsisted of larger cities in Trounstine (2016).
+The distribution of city population in Trounstine (2016)\nmore closely resembles the distribution of the original sample with a greater than 25,000 population\ncutoff imposed than the original sample.
+The red lines indicate the median log population in each sample.") +
+  ylab("Count") +
+  xlab("Log Population") +
+  theme_bw() +
+  theme(plot.caption = element_text(hjust = 0),
+        strip.text.x = element_text(size = 8))
+
+```
+
 # Conclusion

### 2020-05-07 test_extension.Rmd
edits to text

--- 2020-05-07 Final_Draft.Rmd
@@
 
-```{r rp_aggr_plot, echo = FALSE, fig.cap = "This plot examines the pattern of missing data in the the original racial polarization dataset from Trounstine (2016).
-The plot on the left shows the percentage of missing data for each variable with missing data and reveals that the variables that are missing by far the most data are the largest vote split along racial lines (biggestsplit) and the variable indicating whether or not the election had candidates of more than one race (biracial).
-The plot on the right shows the pattern of missingness among the variables.
-We can see that approximately 42\\% of observations are complete (have no missing values).
-There seems to be a correspondence between missing a value for biggest split and missing biracial.
-There also seem to be about 2\\% of values for which most of the variables are missing.
-However, most observations are not missing more than 2-3 values.", fig.width= 6, fig.height = 5, warning = F, fig.pos="H"}
-
-# select only the missing values
-
-rp_aggr <- rp_impute %>%
-   select("biggestsplit", "biracial", "whiteideology_fill2", "medincinterp",
-            "diversityinterp",
-             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
-             "pctrentersinterp", "pctcollegegradinterp", "nonpartisan",
-               "south", "midwest", "west") %>%
-  rename("Racial Divide" = biggestsplit, "Biracial Contest" = biracial, 
-         "White Ideology" = whiteideology_fill2, "Median HH Income" = medincinterp,
-         "Diversity" = diversityinterp, "% Asian" = pctasianpopinterp, 
-         "% Black" = pctblkpopinterp, "% Latino" = pctlatinopopinterp,
-         "% Renters" = pctrentersinterp, "% College Grads" = pctcollegegradinterp,
-         "Nonpartisan Elect." = nonpartisan, "South" = south, "Midwest" = midwest,
-         "West" = "west")
-
-# create an aggr plot for the missing values
-par(font = 1)
-aggr(rp_aggr, bars = TRUE,  col=c('navyblue','red'), numbers=TRUE, cex.axis=.5, gap=1, ylab=c("Proporiton of Missing Values","Combinations"))
-title(main = "Patterns of Missingness in the Financial Segregation Data",
-      sub = "", line = 3, oma = c(1,3,5,1), cex.axis = .5, font.main = 1, font.axis = 1, cex.main = 1, cex.lab = .75)
-
-```
-
 In figure X2, we can similarly observe the trends for the financial segregation dataset.
@@
 
-```{r rp_densityplot, echo = FALSE}
-
-my.settings <- list(
-  par.main.text = list(font = 1, cex = 1)
-)
-
-densityplot(imp_1_rp, main = "Density Plots of Imputed and Original Data by Variable\nin the Racial Polarization Dataset",
-      par.settings = my.settings,
-      par.strip.text = list(cex = .7))
-
-```
-
 ```{r fs_densityplot, echo = FALSE}
@@
 
-Since the results of the diagnostic checks were promising, I next proceeded to re-estimate the original model using the multiply imputed datasets, pooling the results to produce final pooled regression coefficients and parameters.
+Given the promising results of the diagnostic checks, I next proceeded to re-estimate the original model using the multiply imputed datasets, pooling the results to produce final pooled regression coefficients and parameters.
 The results for the analyses using the racial polarization dataset are presented in tables X1-X3.
-
-```{r rp_imputations, include = FALSE}
-
-# Now that we have imputed the missing data, we can re-run the analyses from the
-# original paper to see how and if this changes the analysis. We can use the
-# with() function from the mice package to fit each of the imputed datasets to
-# the model and then pool the results afterwards.
-
-# regression 1: fit multiple imputed datasets
-
-fit_imp_1_rp <- with(imp_1_rp, lmer(formula = biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
-
-# pool and summarize the analyses
-
-pool_imp_1_rp <- pool(fit_imp_1_rp)
-imp_1_rp_sum <- summary(pool_imp_1_rp)
-
-## regression 2 Table 1: fit multiple imputed datasets
-
-#formula = biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2)
-
-fit_imp_2_rp <- with(imp_1_rp, lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
-
-# pool and summarize the analyses
-
-pool_imp_2_rp <- pool(fit_imp_2_rp)
-imp_2_rp_sum <- summary(pool_imp_2_rp)
-
-## regression 3 Table 1 with new data
-
-#formula = biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2)
-
-fit_imp_3_rp <- with(imp_1_rp, lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
-
-# pool and summarize the analyses
-
-pool_imp_3_rp <- pool(fit_imp_3_rp)
-imp_3_rp_sum <- summary(pool_imp_3_rp)
-
-```
 
@@
 
-```{r results_printing_rp_impute_regressions_1, results = "asis", echo=FALSE}
-
-# print results of 1st regression
-
-imp_1_rp_sum_table <- as.data.frame(imp_1_rp_sum) %>% 
-  select(term, estimate, std.error, p.value) %>%
-  head(13) %>%
-  mutate()
-
-imp_1_rp_sum_table_vars <- tibble(
-  Variable = c("Intercept", "Multigroup Seg. Index", "Diversity", "% Asian", "% Black", "% Latino",
-               "Median Income (1000s)", "% Renters", "% College Grads", "Biracial Elec.", "Nonpartisan Elec.", "Primary Elec.", "Pop (logged)"),
-  Estimate = round(imp_1_rp_sum_table$estimate, 3),
-  `Std. Error` = round(imp_1_rp_sum_table$std.error,3),
-  `P-Value` = round(imp_1_rp_sum_table$p.value, 3)
-  )
-
-kable(imp_1_rp_sum_table_vars, "latex", caption = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Multigroup Segregation Index}", booktabs = T) %>%
-  row_spec(0, bold = TRUE) %>%
-  footnote(general = c("This table shows the results of Trounstine's first model for the effect of segregation on political polarization",
-  "(racial vote divide) using the multi-group Theil's H segregation Index using the new, multiply imputed",
-  "datasets. The sign of the coefficient on the main variable of interest, the segregation index, is the same, but",
-  "the result has become statisically insignificant with the 95% confidence interval containing zero. Thus",
-  "while these results still suggest that segregation may be associated with increased political polarization,",
-  "they confer a lesser degree of certainty than Trounstine's original analysis. The coefficients for % Black",
-  "population, % Latino population, and median household income have also switched signs. The coefficient",
-  "on the indicator for a primary election, has also changed from being significant in the original analysis",
-  "to insignificant here. In general, the standard errors on the coefficients have decreased slightly."),
-           general_title = "Table 1:")%>%
-  kable_styling(full_width = TRUE)
-
-```
-
 In the second regression, the results are similar.
@@
 
-```{r results_printing_rp_impute_regressions_2, results = "asis", echo=FALSE}
-
-# print results of 2nd regression
-
-imp_2_rp_sum_table <- as.data.frame(imp_2_rp_sum) %>% 
-  select(term, estimate, std.error, p.value) %>%
-  head(13)
-
-imp_2_rp_sum_table_vars <- tibble(
-  Variable = c("Intercept", "White/Nonwhite Seg. Index", "Diversity", "% Asian", "% Black", "% Latino",
-               "Median Income (1000s)", "% Renters", "% College Grads", "Biracial Elec.", "Nonpartisan Elec.", "Primary Elec.", "Pop (logged)"),
-  Estimate = round(imp_2_rp_sum_table$estimate, 3),
-  `Std. Error` = round(imp_2_rp_sum_table$std.error,3),
-  `P-Value` = round(imp_2_rp_sum_table$p.value, 3)
-  )
-
-kable(imp_2_rp_sum_table_vars, "latex", caption = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Two-Group Segregation Index}", booktabs = T) %>%
-  row_spec(0, bold = TRUE) %>%
-  footnote(general = c("This table shows the results of Trounstine's second model for the effect of segregation on political polarization",
-  "(racial vote divide) using the two-group Theil's H segregation Index using the new, multiply imputed datasets.", 
-  "Compared to Trounstine's original results, the main coefficient on segregation index has decreased in magnitude",
-  "although, it remains statistically significant. The other coefficients except for the biracial indicator are",
-  "insignificant, and the coefficients on percent Black, percent Latino, and Median Income have switched signs.",
-  "Standard errors have also reduced slightly in these specifications compared to the original analysis in",
-  "Trounstine (2016)."),
-           general_title = "Table 2:") %>%
-  kable_styling(full_width = TRUE)
-
-```
-
 In the third regression, like in the second, the main coefficient on segregation index has decreased in magnitude but remains significant.
@@
 
-```{r results_printing_rp_impute_regressions_3, results = "asis", echo=FALSE}
-
-# print results of 3rd regression
-
-imp_3_rp_sum_table <- as.data.frame(imp_3_rp_sum) %>% 
-  select(term, estimate, std.error, p.value) %>%
-  head(14)
-
-imp_3_rp_sum_table_vars <- tibble(
-  Variable = c("Intercept", "White/Nonwhite Seg. Index", "Diversity", "% Asian", "% Black", "% Latino",
-               "Median Income (1000s)", "% Renters", "% College Grads", "Biracial Elec.", "Nonpartisan Elec.", "Primary Elec.", "Pop (logged)", "White Ideology"),
-  Estimate = round(imp_3_rp_sum_table$estimate, 3),
-  `Std. Error` = round(imp_3_rp_sum_table$std.error,3),
-  `P-Value` = round(imp_3_rp_sum_table$p.value, 3)
-  )
-
-kable(imp_3_rp_sum_table_vars, "latex", caption = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Ideology Control}", booktabs = T) %>%
-  row_spec(0, bold = TRUE) %>%
-  footnote(general = c("This table shows the results of Trounstine's third model for the effect of segregation on political polarization",
-  "(racial vote divide) using the two-group Theil's H segregation Index and including controls for ideology",
-  "using the new, multiply imputed datasets. Compared to Trounstine's original results, the main coefficient on",
-  "segregation index has decreased in magnitude although, it remains statistically significant. The other",
-  "coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian and",
-  "Black have switched signs. Standard errors have also reduced slightly in these specifications compared to",
-  "the original analysis in Trounstine (2016)."),
-           general_title = "Table 3:") %>%
-  kable_styling(full_width = TRUE)
-
-```
-
 For the financial segregation dataset, we similarly fit each of our 5 imputed datasets to the original models from @trounstine_segregation_2016 using this data and then pool the results for each.
@@
 ```
-
-As a result of the imputation process, I was able to include an additional XXXXXX observations in the analysis.
 
@@
 The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.
+
+The results of the first regression indicate that Trounstine's results are robust to the inclusion of the imputed data, which led to the inclusion of an additional 59,377 observations in the analysis.
+The coefficients, standard errors, and significance levels are essentially unchanged.
+The same is largely true for the second and third specifications, but the magnitude of the coefficient on the segregation decreases slightly.
 
@@
 
-Because these results differed to such a degree from @trounstine_segregation_2016's original findings, I performed some checks on the data included in each analysis.
-I discovered that @trounstine_segregation_2016 excluded most cities below a certain population size because of the nature of the paper's listwise deletion.
-It may be that small cities are more likely to be missing data, and thus they were more likely to be dropped in @trounstine_segregation_2016's analysis.
-Referring back to @baqir_public_1999, I decided to divide the orginal sample based upon the populaiton cutoff for cities used in that paper, which determined that the populaiton must be above 25,000 people for an area to be considered a city.
-Splitting the financial segregation dataset into two datasets, one above and one below the 25,000 population cutoff, I then imputed missing values and used the multiply imputed datasets in Trounstine's original models.
-
-Figure XXX displays the populaiton distributions used in each of these analyses.
-The figure makes it clear that the observations included in @trounstine_segregation_2016's original analysis were not representative of the original datasample with the missing values, as most of the cities with lower populations were excluded as a result of the list-wise data deletion.
-While the dataset generated from the data imputation on the whole sample also has a different distribution for city populaiton, the range of the data seems to be much more representative of the overall data range in comparison to the @trounstine_segregation_2016 sample.
-For comparison, I also include the distributions of the multiply imputed datasets above and below the 25,000 populaiton cutoff.
-For cities above the cutoff, the city population distribution is similar to the distribution in @trounstine_segregation_2016.
-
 ```{r population_over_Baqir, include = FALSE}
@@
 
-fit_over_baqir_1 <- with(imp_fs_pop_overbaqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp  + logpop | factor(geo_id2) |0| geo_id2))
+fit_over_baqir_1 <- with(imp_fs_pop_overbaqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
 
@@
 imp_over_baqir_1_sum <- summary(pool_fit_over_baqir_1)
+
+```
+
+```{r over_baqir_t1, echo = FALSE}
+
+# print results of 1st regression
+
+imp_over_baqir_1_sum_table <- as.data.frame(imp_over_baqir_1_sum %>% 
+  select(term, estimate, std.error, p.value))
+
+imp_over_baqir_1_sum_table_vars <- tibble(
+  Variable = c("White/Nonwhite Seg. Index", "Diversity", "% Black", "% Asian", "% Latino", "Median Income (1000s)", "% Local Gov. Worker", "% Renters", "% 65+", "% College Grads"),
+  Estimate = round(imp_over_baqir_1_sum_table$estimate, 3),
+  `Std. Error` = round(imp_over_baqir_1_sum_table$std.error,3),
+  `P-Value` = round(imp_over_baqir_1_sum_table$p.value, 3)
+)
+
+kable(imp_over_baqir_1_sum_table_vars, "latex",
+      caption = "\\textbf{Effect of Segregation on Overall per Capita Direct General City Expenditures: Imputed Data for Cities with Populations of 25,000+}",
+      booktabs = T) %>%
+    row_spec(0, bold = TRUE) %>%
+  footnote(general = c("This table shows the results of Trounstine's third model for the effect of segregation on political polarization",
+  "(racial vote divide) using the two-group Theil's H segregation Index and including controls for ideology",
+  "using the new, multiply imputed datasets. Compared to Trounstine's original results, the main coefficient on",
+  "segregation index has decreased in magnitude although, it remains statistically significant. The other",
+  "coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian and",
+  "Black have switched signs. Standard errors have also reduced slightly in these specifications compared to",
+  "the original analysis in Trounstine (2016)."),
+           general_title = "Table 6:") %>%
+  kable_styling(full_width = TRUE)
 
@@
 
-fit_under_baqir_1 <- with(imp_fs_pop_under_baqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp +  logpop | factor(geo_id2) |0| geo_id2))
+fit_under_baqir_1 <- with(imp_fs_pop_under_baqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
 
@@
 
+```{r coef_plot_originals_over_under, echo = FALSE}
+
+model_summaries %>%
+  ggplot(aes(x = median, y = estimate)) +
+  geom_point()+
+  geom_errorbar(aes(ymin = estimate - 2 * std_error, ymax = estimate + 2 * std_error, width = .2)) +
+  geom_hline(yintercept = 0, color = "red") +
+  facet_wrap(~variable, labeller = labeller(variable = coef.labels)) +
+  ggtitle("Coefficient Plots for Diversity and White/Non-White Segregation Indices Across\nthe Models")+
+  xlab("Models Ordered by Increasing Median Population Size of the Sample") +
+  ylab("Estimate and 95% Confidence Interval") +
+  labs(caption = "This plot demonstrates how the significance of diversity and segregation in predicting public\ngoods spending varies with city size.
+As city populaiton size increases, diversity tends to have\nless explanatory power for public goods spending while segregation has more.
+The opposite\nis true when considering city population size decreasing: segregation becomes less important\nas diversity becomes increasingly important.") +
+  theme_bw()+
+  theme(plot.caption = element_text(hjust = 0))
+
+```
+
 ```{r histograms_city_pop_in_specifications_prep, include = FALSE}
@@
 
-The results of the models run with the multiply imputed datasets above and below the cutoff are presented in the following two tables.
-
-```{r over_baqir_t1, echo = FALSE}
-
-# print results of 1st regression
-
-imp_over_baqir_1_sum_table <- as.data.frame(imp_over_baqir_1_sum %>% 
-  select(term, estimate, std.error, p.value))
-
-imp_over_baqir_1_sum_table_vars <- tibble(
-  Variable = c("White/Nonwhite Seg. Index", "Diversity", "% Black", "% Asian", "% Latino", "Median Income (1000s)", "% Local Gov. Worker", "% Renters", "% 65+", "% College Grads", "Pop (logged)"),
-  Estimate = round(imp_over_baqir_1_sum_table$estimate, 3),
-  `Std. Error` = round(imp_over_baqir_1_sum_table$std.error,3),
-  `P-Value` = round(imp_over_baqir_1_sum_table$p.value, 3)
-)
-
-kable(imp_over_baqir_1_sum_table_vars, "latex",
-      caption = "\\textbf{Effect of Segregation on Overall per Capita Direct General City Expenditures: Imputed Data for Cities with Populations of 25,000+}",
-      booktabs = T) %>%
-    row_spec(0, bold = TRUE) %>%
-  footnote(general = c("This table shows the results of Trounstine's third model for the effect of segregation on political polarization",
-  "(racial vote divide) using the two-group Theil's H segregation Index and including controls for ideology",
-  "using the new, multiply imputed datasets. Compared to Trounstine's original results, the main coefficient on",
-  "segregation index has decreased in magnitude although, it remains statistically significant. The other",
-  "coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian and",
-  "Black have switched signs. Standard errors have also reduced slightly in these specifications compared to",
-  "the original analysis in Trounstine (2016)."),
-           general_title = "Table 6:") %>%
-  kable_styling(full_width = TRUE)
-
-```
-
-As a summary of all of the model results for the two main coefficients of interest, segregation index and diversity, a coefficient plot is presented in Figure XXX, with the models ordered by increasing median log population size of the sample on the x-axis.
-Looking first at the coefficients for diversity, the two models with low median city populaiton size have significant, positive coefficients, while the models with the larger median city populations have insignificant coefficients.
-This suggestst that diversity is an important estimator of public goods spending for small, but not necessarily for large, cities.
-Next, looking at the plot for the segregation index, we see the oppposite effect.
-For the models where the median city population sizes were small, the coefficient on segregaiton is insignificant.
-However, for the two models with larger median city populations, the coefficients were significant and negative.
-This suggests that for small cities, segregation is not a very good estimator of public goods spending, but when cities are larger, increases in a city's segregation index are associated with decreases in public goods spending.
-
-```{r coef_plot_originals_over_under, echo = FALSE}
-
-model_summaries %>%
-  ggplot(aes(x = median, y = estimate)) +
-  geom_point()+
-  geom_errorbar(aes(ymin = estimate - 2 * std_error, ymax = estimate + 2 * std_error, width = .2)) +
-  geom_hline(yintercept = 0, color = "red") +
-  facet_wrap(~variable, labeller = labeller(variable = coef.labels)) +
-  ggtitle("Coefficient Plots for Diversity and White/Non-White Segregation Indices Across\nthe Models")+
-  xlab("Models Ordered by Increasing Median Population Size of the Sample") +
-  ylab("Estimate and 95% Confidence Interval") +
-  labs(caption = "This plot demonstrates how the significance of diversity and segregation in predicting public\ngoods spending varies with city size.
-As city populaiton size increases, diversity tends to have\nless explanatory power for public goods spending while segregation has more.
-The opposite\nis true when considering city population size decreasing: segregation becomes less important\nas diversity becomes increasingly important.") +
-  theme_bw()+
-  theme(plot.caption = element_text(hjust = 0))
-
-```
-
 # Conclusion
@@
 This suggests that the segregation index may not have as strong of a positive association with political polarization as @trounstine_segregation_2016 suggests.
-Nevertheless, the imputation exercise generally supports the main ideas in this part of Trounstine's analysis.
-
-On the other hand, for the analyses using the much larger financial segregation dataset, the results of the models using the multiply imputed data sharply contrasted the results of @trounstine_segregation_2016, suggesting that diversity, and not segregation, was the best explanatory variable for public goods spending across cities.
-While these results originally seemed quite contradictory, I was able reconcile this finding by discovering that the results of @trounstine_segregation_2016 seem to be only really representative of larger cities.
-By dropping all observations in the original data with missing values for key variables, it seems that @trounstine_segregation_2016 inadvertently restricted their sample to almost entirely larger cities (above 25,000 residents) whereas the full sample consisted of cities that had smaller populaitons.
-To test the hypothesis that diversity is more important for predicting public goods spending for small cities while segregation is more important for predicting public goods spending for larger cities, I divided the original dataset into two subsets based on the city classificaiton criteria used in @baqir_public_1999 that cities must have a population of at least 25,000 people.
-I then multiply imputed the missing values for each data subset and re-ran the models.
-I found that the results presented initial evidence in support of my hypothesis.
-for the cities below the 25,000 person populaiton cutoff, the coefficient for diversity was positive and significant while the coefficient for the segregation index was insignificant.
-For cities above the 25,000 person cutoff, the results were very similar to the results found in @trounstine_segregation_2016: the coefficient for diversity was insignificant, but the coefficient for the segregation index was significant and negative.
-
-The replication exercise and the robustness check of @trounstine_segregation_2016's model using multiply imputed data provide additional evidence that residential racial segregation is associated with political polarization.
-Furthermore, I find evidence that supports the finding of @trounstine_segregation_2016 that increases in segregation are associated with decreases in public goods spending; however, I find that this is only the case for larger cities.
-In contrast to the argument made by @trounstine_segregation_2016, I find that, for small cities, diversity, not segregation, seems to be the most important explanatory variable for public goods spending.
-One potential explanation for this result could be that when cities become too small, the sort of segregation by neighborhood described in @trounstine_segregation_2016 as a diverse city broken down into homogenous, segregated neighborhoods becomes hard to maintain.
-When populaiton sizes are small, segregation may become difficult and inter-racial interactions may become more common, leading diversity to be more indicative of a degree of integration.
-This provides a possible explanation as to why the coefficient on diversity was positive for very small cities, as these "cities" may function more closely as neighborhoods (many of them with populaitons ranging from X-X thousand); as discussed in the literature review, diversity at the neighborhood level is associated with lower levels of political polarization (Oliver 2010) and thus we would expect these areas to have higher levels of public goods spending according to the ideas of @trounstine_segregation_2016.
-As cities become larger and larger, however, comprehensive segregation becomes more attainable.
-Thus, as cities become larger, segregation, not diversity, becomes a better indicator of inter-racial harmony and cooperation and thus the best explanatory variable for public goods spending.
-
+However, for the analyses using the much larger financial segregation dataset, the results of the models using the multiply imputed data largely mirrored the results of @trounstine_segregation_2016, and the coefficients and significance levels were essentially the same between the two, with the standard errors on the model estimates being generally slightly lower for the analyses using the imputed data.
+This provides strong support for @trounstine_segregation_2016's finding that residential racial segregation is associated with diminshed spending on public goods.
+
+The replication exercise and robustness check using multiply imputed data here provide strong evidence that residential segregation along racial lines does in fact correlate negatively with spending on a variety of public goods.
+What my analysis calls more into question, is by what mechanism this happens.
+Using the multiply imputed data, I still found some evidence that segregation may be associated with increased political polarization which @trounstine_segregation_2016 suggests may lead to diminished public goods spending; however, the effect size is much smaller than that found in @trounstine_segregation_2016, and some of the results have become insignificant.
 It is possible that other mechanisms may be more important in explaining why segregation might be associated with decreased spending on public goods.
@@
 \newpage
-
-# Appendix
-
-```{r  include = FALSE}
-
-## regression 1 Table 1
-
-# perform a multi-level mixed-effects linear regression of biggest split on the multi-group H index with controls for Herfindahl Diversity Index, % Asian interpolated, % Black interpolated, % Latino interpolated, median household income interpolated, % renters interpolated, percent college grads interpolated, a dummy indicating if there were biracial candidates in the election, a dummy  indicating if the election was nonpartisan, an indicator if the election was a primary, and the log population.
-The regression also includes fixed effects for year and region and random effects for cities (geo_id2).
-Diversity is  included because of the claim that more diverse populations will have more heterogeneous political preferences.
-The other fixed effect control variables are included because they are known to be potentially correlated with segregation.
-winner == 1 requires that there was a winner in the election.
-
-# regression specification. Apply REML = FALSE. The default for lmer() in R is
-# to optimize the restricted (residual) maximum likelihood (REML) whereas in
-# xtmixed in Stata the default is to optimize the log likelihood (which you can
-# do in lmer() in R by setting REML = FALSE), so this will match the STATA code
-
-m1 <- lmer(biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-## regression 2 Table 1
-
-# Perform the same regression as for Column 1 above but this time regress on the two-group calculation of Theil's H interpolated.
-It is unclear where the "diversity" variable is coming from, as the only variable related to diversity in the specificed dataset is diversityinterp.
-This is a problem that will need to be resolved.
-Essentially, this regression just tests an alternate specification to the first in which the segregation index in defined in terms of two-groups rather than multiple.
-
-m2 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-# perform the same regression as for column 2, but now add in a measure of
-# average white political ideology. The point of this is to control for ideology
-# so that the author can separate any effects of segregation from any potential
-# effects of white political ideology. This is important because it is possible
-# that segregation is just a proxy for white conservatism and thus failure to
-# include this variable could lead to ommitted variable bias.
-
-m3 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-```
-
-```{r results="asis", echo = FALSE}
-
-# create a stargazer table of the results
-
-t1 <- stargazer(m1, m2, m3, omit = c("year", "south", "midwest", "west"),
-                header = FALSE,
-                style = "apsr",
-                title = "\\textbf{Racial Polarization in Segregated Cities}",
-                single.row = FALSE,
-                no.space = F,
-                covariate.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Diversity", "Percent Asian", "Percent Black", "Percent Latino", "Medain HH Income (1000s)", "Percent Renters", "Percent College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology", "Constant"),
-                dep.var.labels = c("\\textbf{\\underline{Racial Divide with:    }}"),
-                column.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Ideology Controls"),
-                notes = c("Table A1: This table displays the results of the replication effort of the analyses conducted in Trounstine (2016)", 
-                          "using the racial polarization dataset. The replication code can be found on my personal Github repository, which is",
-                          " linked in the introduction. The original table is displayed for comparison as Figure 3."),
-                table.placement = "H",
-                notes.align = "l",
-                font.size = "small")
-
-```
-
-![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016.
-My replication of these results can be found in Table A1 in this paper.](table_1.png)
-
-```{r felm, include = FALSE}
-
-# Main Analysis 2
-
-## regression 1 Table 2
-
-# The following is a fixed effects model regression with clustering around
-# geo_id2. It mandates that total census tracts in the city is greater than 1,
-# which we want because our measure of evenness of racial spread is constant for
-# cities with only one tract by our definition (which requires comparing tracts
-# within cities). It also mandates that Direct General Expenditures (DGE) per
-# capita, CPI adjusted is not equal to 0, which would be problematic and
-# indicate a potential data error. This regression regresses the DGE per capita
-# on the the two-group calculation of  Theil's H interpolated. Controls are
-# included for diversity and the % populations of Blacks, Asians, and Latinos to
-# help identify whether it is actually diversity that drives down spending.These
-# demographic controls also help to account for the fact that whites and
-# minorities tend to perfer different levels of government spending in general.
-# This will help isolate the effects of segregation v. other forms of diversity
-# on public spending. Other controls for Median household income, CPI adjusted,
-# percent over 65, percent college grads, percent local government workers, log
-# population help control for additional factors related to segregation and
-# expenditure. Controls for percent renters interpolated and Median household
-# income also help to control for the general wealth of cities, which could be a
-# potential driver of public spending. Fixed effects for cities are also
-# included  so that the author can examine the effect of segregation in the same
-# city over  time, which also helps control for many other factors not otherwise
-# taken into account (such as city age)
-
-# apply the conditions in Stata regression
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-# felm(y~x | factor(fe1) + factor(fe2) | 0 | clustervar)
-
-felm1 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-## regression 2 Table 2
-
-# This regression is the same as above except instead of using diversity, a new
-# control is added for the five year changes in racial group shares. The goal
-# here is to see whether or not changes in diversity are a driving factor
-# (rather than absolute levels of diversity).
-
-felm2 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-## Regression 3 Table 2
-
-# Column 3
-
-# As in column 3 of table 1, this regression simply adds in a control for  mean  ideology of city residents from General Social Survey (GSS) to control for the  possibility that ideology that segregated cities are more ideologically  conservative and that the conservative nature of segregated cities is what actually drives the effect.
-
-felm3 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-```
-
-```{r main_fp_tables, results = "asis", echo = FALSE}
-
-# create main table for table 3
-
-table2 <- stargazer(felm1, felm2, felm3, omit = c("year", "south", "midwest", "west"), 
-                    header = FALSE,
-                    style = "apsr",
-                    title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures}",
-                    covariate.labels = c("White/Nonwhite H Index", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Change Percent Black", "Change Percent Latino", "Change Percent Asian", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Population (logged)", "White Ideology", "Constant"),
-                    dep.var.labels = c("\\textbf{\\underline{Direct General Expenditure Per Capita}}"),
-                    column.labels = c("Main Specification", "Changing Demographics", "Ideology Controls"),
-                    notes = c("Table A2: This table displays the results of the replication effort of the analyses conducted in Trounstine (2016)", "
-                              assessing the effect of segregation in direct per capita public expenditures using the financial segregation",
-                              "dataset. The replication code can be found on my personal Github repository, which islinked in the introduction."),
-                    table.placement = "H",
-                    notes.align = "l",
-                    font.size = "small")
-
-```
-
-```{r, include = FALSE}
-
-# Main Analysis 3
-
-## regression 1 Table 3
-
-# Column 1
-
-# The following is a fixed effects model regression with clustering once again around geo_id2.
-Again, the if statements at the end mandate that total census tracts in the city is greater than 1, which we want because our measure of evenness of racial spread is constant for cities with only one tract by our definition (which requires comparing tracts within cities).
-They also mandate that the highways per capita, CPI adjsuted with no cap extend (lagged 5 years) is not equal to 0, which would be problematic and indicate a potential data error.
-The dependent variable here is highways per capita, CPI adjsuted with no cap extend (lagged 5 years) and it is regressed on the two group calculation of Theil's H, interpolated.
-Controls are added for diversity, percent population of Blacks, Asians, and Latinos, and median household CPI adjusted income as well as for % local government worker hundreds, percent rentership, percent over 65, percent college graduates, and the log of the population.
-This essentially examines the effect of segregation on the specific public good of highways.
-As in the previous table's regressions, fixed effects for cities are also included so that the author can examine the effect of segregation in the same city over time, which also helps control for many other factors not otherwise taken into account (such as city age) *
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), highwayspercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_1 <- felm(highwayspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-## regression 2 Table 3
-
-# Column 2
-
-# This is the same regression as column 1, but this time the dependent variable
-# is police per capita, CPI adjusted with no cap extend. This essentially
-# examines the effect of segregation on the specific public good of police per
-# capita.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), policepercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_2 <- felm( policepercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 3
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), parkspercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-# This is again the same regression, but this time the dependent variable is
-# parks per capita, CPI adjusted with no cap extend. This essentially examines
-# the effect of segregation on the specific public good of parks.
-
-felm2_3 <- felm(parkspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 4
-
-# This is again the same regression, but this time the dependent variable is
-# sewers per capita, CPI adjusted with no cap extend. This essentially examines
-# the effect of segregation on the specific public good of sewers.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), sewerspercapNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_4 <- felm(sewerspercapNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 5
-
-# This is again the same regression, but this time the dependent variable is
-# Welfare, Health, Housing per capita, CPI adjusted, no cap expend. This
-# essentially examines the effect of segregation on the specific public good of
-# welfare and housing.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), welfhoushealthNC_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_5 <- felm(welfhoushealthNC_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-# Column 6
-
-# This is again the same regression, but this time the dependent variable is own
-# source of general revenue per capita, CPI adjusted. This essentially examines
-# the effect of segregation on the specific public good of own source revenue.
-
-fin_seg_sub <- fin_seg %>%
-  filter(totaltractsf > 1 | is.na(totaltractsf), genrevownpercap_cpi != 0) %>%
-  mutate(medinc_cpi = medinc_cpi/1000)
-
-felm2_6 <- felm(genrevownpercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
-
-```
-
-```{r iv_regs, include = FALSE}
-
-## regression 1 Table 5
-
-# Top Row
-
-# Column 1
-
-# This is an instrumental variable regression with DGE per capita, adjusted by the CPI, as the dependent variable and total number of waterways as the instrumental variable for segregation.
-The instrument includes the log of the population in the first stage because the number of waterways is positively correlated to population and population is positively correlated with segregation.
-The control variables are the same as those in the regressions for Table 2 except for 2 changes: since the number of waterways does not change, there is no need for city fixed effects.
-Instead, we include fixed effects for the region and year.
-A lagged version of the dependent variable (dgepercap_cpilag) is added to the regressions to account for the high correlation between  observations for the same city over time and because changes in local budgets typically are incremental (NOTE: why exactly do we do this/why does it help/why not do it in the non-intstrumental regressions?).
-
-fin_seg_1 <- fin_seg %>%
-  filter(dgepercap_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-glimpse(fin_seg_1$medincinterp)
-
-# good explanation: http://eclr.humanities.manchester.ac.uk/index.php/IV_in_R
-
-# iv = ivreg(second stage regression | instrument1 + instrument2 )
-
-ivreg1 <- ivreg(dgepercap_cpi ~ H_citytract_NHW_i + dgepercap_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + dgepercap_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_1)
-
-# Column 2
-
-# this is the same regression as for column 1 but now we use the dependent variable highwayspercapNC_cpi to assess the effect of the instrumental  variable on highways per capita *
-
-fin_seg_2 <- fin_seg %>%
-  filter(highwayspercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg2 <- ivreg(highwayspercapNC_cpi ~ H_citytract_NHW_i + highwayspercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + highwayspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_2)
-
-# Column 3
-
-# this is the same regression as for column 1 but now we use the dependent variable policepercapNC_cpi to assess the effect of the instrumental variable on police per capita
-
-fin_seg_3 <- fin_seg %>%
-  filter(policepercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg3 <- ivreg(policepercapNC_cpi ~ H_citytract_NHW_i + policepercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + policepercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_3)
-
-# Column 4 this is the same regression as for column 1 but now we use the
-# dependent variable parkspercapNC_cpi to assess the effect of the instrumental
-# variable on parks per capita
-
-fin_seg_4 <- fin_seg %>%
-  filter(parkspercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg4 <- ivreg(parkspercapNC_cpi ~ H_citytract_NHW_i + parkspercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + parkspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_4)
-
-# Bottom Row
-
-# Column 1
-
-# this is the same regression as for column 1 but now we use the dependent
-# variable sewerspercapNC_cpi to assess the effect of the instrumental variable
-# on sewers per capita
-
-fin_seg_5 <- fin_seg %>%
-  filter(sewerspercapNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg5 <- ivreg(sewerspercapNC_cpi ~ H_citytract_NHW_i + sewerspercapNC_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + sewerspercapNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_5)
-
-# Column 3
-
-# this is the same regression as for column 1 but now we use the dependent variable genrevownpercap_cpi to assess the effect of the instrumental variable on own source revenue per capita
-
-fin_seg_6 <- fin_seg %>%
-  filter(genrevownpercap_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg6 <- ivreg(genrevownpercap_cpi ~ H_citytract_NHW_i + genrevownpercap_cpilag + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + genrevownpercap_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_6)
-
-# Column 2
-
-# this is the same regression as for column 1 but now we use the dependent
-# variable welfhoushealthNC_cpi to assess the effect of the instrumental
-# variable on welfare per capita
-
-fin_seg_7 <- fin_seg %>%
-  filter(welfhoushealthNC_cpi != 0) %>%
-  mutate(medincinterp = medincinterp/1000)
-
-ivreg7 <- ivreg(welfhoushealthNC_cpi ~ H_citytract_NHW_i + welfhoushealthNC_cpilag  + diversityinterp +
-                  pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +
-                  pctcollegegradinterp + northeast + south + midwest + y5 + 
-                  y6 + y7 + y8 + y9 | total_rivs_all + 
-                  logpop + welfhoushealthNC_cpilag + diversityinterp + pctblkpopinterp + 
-                  pctasianpopinterp + pctlatinopopinterp + medincinterp +
-                  pctlocalgovworker_100 + pctrentersinterp + pctover65 +   
-                  pctcollegegradinterp + northeast + south + 
-                  midwest + y5 + y6 + y7 + y8 + y9, data = fin_seg_7)
-
-summary(ivreg7)
-
-```
-
-```{r additional_robustness_checks_imp_rp, eval = FALSE, include = FALSE}
-
-# ideally, the fits will intertwine and not exhibit any trends at later iterations.
-This seems to generally be the case.
-There are some issues with the results for some of the variables with very few missing values, which makes sense as we would expect the mean to be less reliable due to the law of large numbers and thus convergence is more difficult.
-However, since these are so few values, it is less important about how robust they are.
-
-plot(imp_1_rp)
-
-# we can also check the imputed values against the original values using stripplot().
-Each column in each subplot represents a separate iteration.
-The magenta points represent the imputed data.
-The values of the variable in questions are along the y axis.
-We expect the spread of the data to be similar if the imputations were done well.
-If the data were missing completely at random, then the imputed data should have the same distribution as the original data.
-In particular, we want to be sure that the imputations are within a plausible range of the data.
-This is the case for all of our imputed variables, and there does not seem to be cause for alarm from these results.
-
-stripplot(imp_1_rp)
-
-```
-
-```{r additional_robustness_checks_imp_fs_v1, eval = FALSE, include = FALSE}
-
-# ideally, the fits will intertwine and not exhibit any trends at later iterations.
-This seems to generally be the case.
-There are some issues with the results for some of the variables with very few missing values, which makes sense as we would expect the mean to be less reliable due to the law of large numbers and thus convergence is more difficult.
-However, since these are so few values, it is less important about how robust they are.
-
-plot(imp_fs)
-
-# we can also check the imputed values against the original values using stripplot().
-Each column in each subplot represents a separate iteration.
-The magenta points represent the imputed data.
-The values of the variable in questions are along the y axis.
-We expect the spread of the data to be similar if the imputations were done well.
-If the data were missing completely at random, then the imputed data should have the same distribution as the original data.
-In particular, we want to be sure that the imputations are within a plausible range of the data.
-This is the case for all of our imputed variables, and there does not seem to be cause for alarm from these results.
-
-stripplot(imp_fs, H_citytract_NHW_i)
-
-stripplot(imp_fs, chng5pctblk)
-
-stripplot(imp_fs, chng5pctlatino)
-
-stripplot(imp_fs, chng5pctasian)
-
-stripplot(imp_fs, ideology_fill)
-
-```
-
-\newpage
 # Bibliography

### 2020-05-07 Final_Draft.Rmd
edits to text

@@
 As cities become larger and larger, however, comprehensive segregation becomes more attainable.
-Thus, as cities become larger, segregation, not diversity, becomes a better indicator of inter-racial harmony and cooperation and thus the best explanatory variable for public goods spending.
-
-It is possible that other mechanisms may be more important in explaining why segregation might be associated with decreased spending on public goods.
+Thus, segregation, not diversity, becomes a better indicator of inter-racial harmony and cooperation and thus the best explanatory variable for public goods spending.
+
+It is possible that other mechanisms may be more important in explaining differences in spending across cities on public goods.
 For example, it could be that there is an important interaction effect between income and segregation, as others have previously suggested, or there could be some other intervening mechanism or a confounding variable that is leading to the negative association between segregation and lower spending on public goods.
 @trounstine_segregation_2016 has identified an important relationship between segregation and the provision of public goods.
-However, my analysis suggests that further research is needed to assess the potential mechanisms by which residential segregation by race or even a confounding variable may result in dimished spending.
-If this mechanism can be better understood, than it will be possible to more effectively understand and address the underprovision of public goods, which may inhibit social mobility and unfairly disadvantage certain groups.
+However, my analysis suggests that further research is needed to assess for which cities this relationship holds.
+At what city size or population density does segregaiton become more relevant than diversity?
+And what implications does this have for how public policy should be designed and implemented to address these issues?
+These are important questions that merit further investigation, because by improving our ability to identify, understand, and address its root causes, we may be able to better address the underprovision of public goods, which may inhibit social mobility and unfairly disadvantage certain groups.
 

### 2020-05-07 Final_Draft.Rmd
rp coefficient plot work and formatting

@@
 
-```{r fs_densityplot, echo = FALSE}
-
-my.settings <- list(
-  par.main.text = list(font = 1, cex = 1)
-)
-
-#densityplot(imp_fs)
-densityplot(x = imp_fs, 
-            data = ~ H_citytract_NHW_i + chng5pctblk + chng5pctlatino + chng5pctasian + ideology_fill,
-            main = "Density Plots of Imputed and Original Data by Variable\nin the Financial Segregation Dataset",
-            par.settings = my.settings,
-            par.strip.text = list(cex = 1))
-
-```
-
 Since the results of the diagnostic checks were promising, I next proceeded to re-estimate the original model using the multiply imputed datasets, pooling the results to produce final pooled regression coefficients and parameters.
@@
 In the second regression, the results are similar.
-The main coefficient on segregation index has decreased in magnitude, although in these specifications, it remains statistically significant.
+The main coefficient on segregation index has decreased in magnitude, it remains statistically significant.
 The other coefficients except for the biracial indicator are insignificant, and the coefficients on percent Black, percent Latino, and median household income have all switched signs.
 
-```{r results_printing_rp_impute_regressions_2, results = "asis", echo=FALSE}
+```{r results_printing_rp_impute_regressions_2, results = "asis", include = FALSE, eval = FALSE}
 
@@
 The other coefficients except for the biracial indicator are insignificant, and the coefficients on percent Black, percent Asian, median income, and logged population have switched signs.
-In all three of the specifications, tandard errors reduced slightly using the larger, multiply imputed datasets compared to the original analysis with the original data in @trounstine_segregation_2016.
-
-```{r results_printing_rp_impute_regressions_3, results = "asis", echo=FALSE}
+In all three of the specifications, standard errors reduced slightly using the larger, multiply imputed datasets compared to the original analysis with the original data in @trounstine_segregation_2016.
+
+```{r results_printing_rp_impute_regressions_3, results = "asis", include = FALSE, eval = FALSE}
 
@@
 
+```{r Trounstine_rp_models_for_coeff_plot, include = FALSE}
+
+## regression 1 Table 1
+
+# perform a multi-level mixed-effects linear regression of biggest split on the multi-group H index with controls for Herfindahl Diversity Index, % Asian interpolated, % Black interpolated, % Latino interpolated, median household income interpolated, % renters interpolated, percent college grads interpolated, a dummy indicating if there were biracial candidates in the election, a dummy  indicating if the election was nonpartisan, an indicator if the election was a primary, and the log population.
+The regression also includes fixed effects for year and region and random effects for cities (geo_id2).
+Diversity is  included because of the claim that more diverse populations will have more heterogeneous political preferences.
+The other fixed effect control variables are included because they are known to be potentially correlated with segregation.
+winner == 1 requires that there was a winner in the election.
+
+# regression specification. Apply REML = FALSE. The default for lmer() in R is
+# to optimize the restricted (residual) maximum likelihood (REML) whereas in
+# xtmixed in Stata the default is to optimize the log likelihood (which you can
+# do in lmer() in R by setting REML = FALSE), so this will match the STATA code
+
+m1 <- lmer(biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
+
+## regression 2 Table 1
+
+# Perform the same regression as for Column 1 above but this time regress on the two-group calculation of Theil's H interpolated.
+It is unclear where the "diversity" variable is coming from, as the only variable related to diversity in the specificed dataset is diversityinterp.
+This is a problem that will need to be resolved.
+Essentially, this regression just tests an alternate specification to the first in which the segregation index in defined in terms of two-groups rather than multiple.
+
+m2 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
+
+# perform the same regression as for column 2, but now add in a measure of
+# average white political ideology. The point of this is to control for ideology
+# so that the author can separate any effects of segregation from any potential
+# effects of white political ideology. This is important because it is possible
+# that segregation is just a proxy for white conservatism and thus failure to
+# include this variable could lead to ommitted variable bias.
+
+m3 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
+
+m1_estimate_seg <- 0.931958
+m1_se_seg <- 0.394180
+m1_estimate_d <- 0.384535
+m1_se_d <-0.361625
+
+m2_estimate_seg <- 0.755719
+m2_se_seg <- 0.296916 
+m2_est_d <- 0.518369
+m2_se_d <- 0.323161
+
+m3_estimate_seg <- 0.835441
+m3_se_seg <- 0.295759
+m3_est_d <- 0.583684
+m3_se_d <- 0.323488
+
+```
+
+```{r calc_coeff_sds_original_rp_impute, include = FALSE}
+
+model_coeff_rp <- tibble(
+  variable = c("Segregation Index", "Diversity", 
+               "Segregation Index", "Diversity",
+               "Segregation Index", "Diversity", 
+               "Segregation Index", "Diversity",
+                "Segregation Index", "Diversity", 
+               "Segregation Index", "Diversity"),
+  estimate = c(imp_1_rp_sum[2,2], imp_1_rp_sum[3,2],
+               imp_2_rp_sum[2,2], imp_2_rp_sum[3,2],
+               imp_3_rp_sum[2,2], imp_3_rp_sum[3,2],
+               m1_estimate_seg, m1_estimate_d,
+               m2_estimate_seg, m2_est_d,
+               m3_estimate_seg, m3_est_d),
+  std_error = c(imp_1_rp_sum[2,3], imp_1_rp_sum[3,3],
+                imp_2_rp_sum[2,3], imp_2_rp_sum[3,3],
+                imp_3_rp_sum[2,2], imp_3_rp_sum[3,2],
+                m1_se_seg, m1_se_d,
+                m2_se_seg, m2_se_d,
+                m3_se_seg, m3_se_d),
+  model = c( "Imputation 1", "Imputation 1",
+             "Imputation 2","Imputation 2",
+             "Imputation 3", "Imputation 3",
+             "Trounstine 1", "Trounstine 1",
+            "Trounstine 2", "Trounstine 2",
+            "Trounstine 3",  "Trounstine 3"),
+  order = c (2,2,
+             5,5,
+             8,8,
+             1,1,
+             4,4,
+             7,7),
+  color = c("Imputations", "Imputations", "Imputations", 
+            "Imputations", "Imputations", "Imputations", 
+            "Trounstine", "Trounstine", "Trounstine",
+            "Trounstine","Trounstine","Trounstine"),
+  model_num = c("1","1","2","2","3","3","1","1","2","2","3","3")
+)
+
+model_coeff_rp <- model_coeff_rp  %>%
+  mutate(order = as.factor(order))
+
+```
+
+```{r coef_plot_originals_over_under, echo = FALSE}
+
+model_coeff_rp %>%
+  ggplot(aes(x = order, y = estimate, color = color, shape = model_num)) +
+  geom_point()+
+  geom_errorbar(aes(ymin = estimate - 2 * std_error, ymax = estimate + 2 * std_error, width = .2)) +
+  geom_hline(yintercept = 0, color = "red") +
+  facet_wrap(~variable) +
+  ggtitle("Coefficient Plots for Diversity and Segregation Indices Across\nthe Racial Polarization Models")+
+  xlab("Model Specifications") +
+  ylab("Estimate and 95% Confidence Interval") +
+  labs(caption = "This plot demonstrates how the significance of diversity and segregation in predicting public goods spending varies\n with city size.
+As city populaiton size increases, diversity tends to have less explanatory power for public goods\nspending while segregation has more.
+The opposite is true when considering city population size decreasing:\nsegregation becomes less important as diversity becomes increasingly important.") +
+  theme_bw()+
+  theme(plot.caption = element_text(hjust = 0),
+        axis.ticks.x = element_blank()) +
+  scale_x_discrete(labels = c("            1", "", "            2", "", "           3", "")) +
+  labs(color = "Model Category", shape = "Specification") +
+  scale_color_manual(values= c("orange", "blue"))
+
+```
+
 For the financial segregation dataset, we similarly fit each of our 5 imputed datasets to the original models from @trounstine_segregation_2016 using this data and then pool the results for each.
@@
 Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
-The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.
+The results of the second and third specifications were similar, with the coefficient on segregation going almost to zero and becoming insignificant on both.
+For brevity, these results are not presented.
 
@@
 
-```{r results_printing_fs_impute_regressions_2, results = "asis", echo=FALSE, eval = FALSE, invlude = FALSE}
+```{r results_printing_fs_impute_regressions_2, results = "asis", echo=FALSE, eval = FALSE, include = FALSE}
 
@@
 
-```{r results_printing_fs_impute_regressions_3, results = "asis", echo=FALSE, eval = FALSE, include = FALSE}
+```{r results_printing_fs_impute_regressions_3, results = "asis", echo = FALSE, eval = FALSE, include = FALSE}
 
@@
 
-```{r calc_coeff_sds_original_fs_impute, include = FALSE}
-
-model_coeff <- tibble(
-  variable = c("White/Non-White Seg. Index", "Diversity", 
-               "White/Non-White Seg. Index", "Diversity",
-               "White/Non-White Seg. Index", "Diversity", 
-               "White/Non-White Seg. Index", "Diversity"),
-  estimate = c(imp_under_baqir_1_sum[1,2], imp_under_baqir_1_sum[2,2],
-               imp_felm1_sum[1,2], imp_felm1_sum[2,2],
-               coef(felm1)[1], coef(felm1)[2],
-               imp_over_baqir_1_sum[1,2], imp_over_baqir_1_sum[2,2]),
-  std_error = c(imp_under_baqir_1_sum[1,3], imp_under_baqir_1_sum[2,3],
-                imp_felm1_sum[1,3], imp_felm1_sum[2,3],
-                summary(felm1)$coeff[1,2], summary(felm1)$coeff[2,2],
-                imp_over_baqir_1_sum[1,3], imp_over_baqir_1_sum[2,3]),
-  model = c( "fin_imp_pop_under_baqir", "fin_imp_pop_under_baqir",
-             "fin_imp", "fin_imp",
-            "fin_dge", "fin_dge",
-            "fin_imp_pop_over_baqir", "fin_imp_pop_over_baqir")
-)
-
-model_coeff <- model_coeff %>%
-  mutate(variable = as.factor(variable))
-
-```
-
-```{r dataset_rows_in_analysis}
-
-complete_fs <- complete(imp_fs,1) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
-         !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
-         !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
-         !(is.na(logpop)), dgepercap_cpi != 0)
-
-complete_over_baqir <- complete(imp_fs_pop_overbaqir, 1)%>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
-         !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
-         !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
-         !(is.na(logpop)), dgepercap_cpi != 0)
-
-complete_under_baqir <- complete(imp_fs_pop_under_baqir, 1)%>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
-         !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
-         !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
-         !(is.na(logpop)), dgepercap_cpi != 0)
-
-```
-
-```{r dataset_medians}
-
-data_info <- tibble(
-  dataset = c("fin_imp", "fin_imp_pop_over_baqir", "fin_imp_pop_under_baqir",
-               "fin_dge"),
-  median = c(median(fin_imp$logpop), median(fin_imp_pop_over_baqir$logpop),
-              median(fin_imp_pop_under_baqir$logpop), median(fin_dge$logpop)),
-  rows = c(nrow(complete_fs), nrow(complete_over_baqir), nrow(complete_under_baqir),
-          nrow(fin_dge))
-)
-
-model_summaries <- left_join(model_coeff, data_info, by = c("model" = "dataset"))
-
-```
-
-```{r histograms_city_pop_in_specifications_prep, include = FALSE}
-
-pop_data_over_baqir <- tibble(
-  log_pop = complete_over_baqir$logpop,
-  Analysis = "Imputed, pop. > 25k"
-)
-
-pop_data_under_baqir <- tibble(
-  log_pop = complete_under_baqir$logpop,
-  Analysis = "Imputed, pop. < 25k"
-)
-
-pop_data_imp_fs <- tibble(
-  log_pop = complete_fs$logpop,
-  Analysis = "Imputed, Whole Sample"
-)
-
-pop_data_fin_dge <- tibble(
-  log_pop = fin_dge$logpop,
-  Analysis = "Trounstine (2016)"
-)
-
-pop_data_fin_seg <- tibble(
-  log_pop = fin_seg$logpop,
-  Analysis = "Original Sample"
-)
-
-pop_hist_data <- rbind(pop_data_over_baqir, pop_data_imp_fs)
-pop_hist_data <- rbind(pop_hist_data, pop_data_under_baqir)
-pop_hist_data <- rbind(pop_hist_data, pop_data_fin_dge)
-pop_hist_data <- rbind(pop_hist_data, pop_data_fin_seg)
-
-median_pops <- tibble(
-  Analysis = c("Imputed, pop. > 25k", "Imputed, pop. < 25k", "Imputed, Whole Sample", "Trounstine (2016)", "Original Sample"),
-  median_log_pop = c(median(complete(imp_fs_pop_overbaqir,1)$logpop),
-                     median(complete(imp_fs_pop_under_baqir, 1)$logpop),
-                     median(complete(imp_fs, 1)$logpop),
-                     median(fin_dge$logpop),
-                     median(fin_seg$logpop, na.rm = T))
-)
-
-pop_hist_data <- left_join(pop_hist_data, median_pops)
-
-```
-
-```{r city_pops_histogram, echo = FALSE, warning = FALSE}
-
-pop_hist_data %>%
-  ggplot() +
-  geom_histogram(aes(x = log_pop, fill = Analysis)) +
-  geom_vline(aes(xintercept = median_log_pop), color = "red") +
-  facet_wrap(~Analysis) +
-  coord_cartesian(xlim = c(0,15)) +
-  ggtitle("Histograms of Log Population of City Observations Included in the\nVarious Regression Analyses") +
-  labs(caption = "This figure makes clear the differences in city size (in terms of population) among the different analyses.\n It is clear that the listwise deletion of observations with missing values resulted in a sample that almost entirely\nconsisted of larger cities in Trounstine (2016).
-The distribution of city population in Trounstine (2016)\nmore closely resembles the distribution of the original sample with a greater than 25,000 population\ncutoff imposed than the original sample.
-The red lines indicate the median log population in each sample.") +
-  ylab("Count") +
-  xlab("Log Population") +
-  theme_bw() +
-  theme(plot.caption = element_text(hjust = 0),
-        strip.text.x = element_text(size = 8))
-
-```
-
-The results of the models run with the multiply imputed datasets above and below the cutoff are presented in the following two tables.
-
-```{r over_baqir_t1, echo = FALSE}
-
-# print results of 1st regression
-
-imp_over_baqir_1_sum_table <- as.data.frame(imp_over_baqir_1_sum %>% 
-  select(term, estimate, std.error, p.value))
-
-imp_over_baqir_1_sum_table_vars <- tibble(
-  Variable = c("White/Nonwhite Seg. Index", "Diversity", "% Black", "% Asian", "% Latino", "Median Income (1000s)", "% Local Gov. Worker", "% Renters", "% 65+", "% College Grads", "Pop (logged)"),
-  Estimate = round(imp_over_baqir_1_sum_table$estimate, 3),
-  `Std. Error` = round(imp_over_baqir_1_sum_table$std.error,3),
-  `P-Value` = round(imp_over_baqir_1_sum_table$p.value, 3)
-)
-
-kable(imp_over_baqir_1_sum_table_vars, "latex",
-      caption = "\\textbf{Effect of Segregation on Overall per Capita Direct General City Expenditures: Imputed Data for Cities with Populations of 25,000+}",
-      booktabs = T) %>%
-    row_spec(0, bold = TRUE) %>%
-  footnote(general = c("This table shows the results of Trounstine's third model for the effect of segregation on political polarization",
-  "(racial vote divide) using the two-group Theil's H segregation Index and including controls for ideology",
-  "using the new, multiply imputed datasets. Compared to Trounstine's original results, the main coefficient on",
-  "segregation index has decreased in magnitude although, it remains statistically significant. The other",
-  "coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian and",
-  "Black have switched signs. Standard errors have also reduced slightly in these specifications compared to",
-  "the original analysis in Trounstine (2016)."),
-           general_title = "Table 6:") %>%
-  kable_styling(full_width = TRUE)
-
-```
-
-As a summary of all of the model results for the two main coefficients of interest, segregation index and diversity, a coefficient plot is presented in Figure XXX, with the models ordered by increasing median log population size of the sample on the x-axis.
-Looking first at the coefficients for diversity, the two models with low median city populaiton size have significant, positive coefficients, while the models with the larger median city populations have insignificant coefficients.
-This suggestst that diversity is an important estimator of public goods spending for small, but not necessarily for large, cities.
-Next, looking at the plot for the segregation index, we see the oppposite effect.
-For the models where the median city population sizes were small, the coefficient on segregaiton is insignificant.
-However, for the two models with larger median city populations, the coefficients were significant and negative.
-This suggests that for small cities, segregation is not a very good estimator of public goods spending, but when cities are larger, increases in a city's segregation index are associated with decreases in public goods spending.
-
-```{r coef_plot_originals_over_under, echo = FALSE}
-
-model_summaries %>%
-  ggplot(aes(x = median, y = estimate)) +
-  geom_point()+
-  geom_errorbar(aes(ymin = estimate - 2 * std_error, ymax = estimate + 2 * std_error, width = .2)) +
-  geom_hline(yintercept = 0, color = "red") +
-  facet_wrap(~variable, labeller = labeller(variable = coef.labels)) +
-  ggtitle("Coefficient Plots for Diversity and White/Non-White Segregation Indices Across\nthe Models")+
-  xlab("Models Ordered by Increasing Median Population Size of the Sample") +
-  ylab("Estimate and 95% Confidence Interval") +
-  labs(caption = "This plot demonstrates how the significance of diversity and segregation in predicting public\ngoods spending varies with city size.
-As city populaiton size increases, diversity tends to have\nless explanatory power for public goods spending while segregation has more.
-The opposite\nis true when considering city population size decreasing: segregation becomes less important\nas diversity becomes increasingly important.") +
-  theme_bw()+
-  theme(plot.caption = element_text(hjust = 0))
-
-```
-
-# Conclusion
-
-Why cities differ in their amount of spending on public goods is an interesting questions that is frequently debated in the literature.
-@trounstine_segregation_2016 posits that segregation may be an important underlying cause of the underprovsion of public goods.
-Finding evidence that residential segregation by race increases political partisanship, @trounstine_segregation_2016 argues that residential segregation can increase division and make cooperation amongst competing groups difficult, which results in decreased spending on public goods.
-The findings of @trounstine_segregation_2016 are particularly important because they suggest that segregation, as defined by many homogeneous neighborhoods within a larger diverse geographical area, is the key factor in disinvestment in public goods.
-This contradicts previous research which has suggested that levels of diversity were instead most important (see for example @baqir_public_1999 or @hopkins_diversity_2009).
-While @trounstine_segregation_2016 still represents relatively new reasearch as of 2020, it has yet to be fully vetted by additional research.
-Furthermore, some research that has been published on the topic since its publication suggests that other factors such as larger inequities in the political system favoring socially powerful groups [@lee_ethnic_2018] or the interaction of income and racial inequality [@an_its_2018] may be more important in explaining public goods provisions.
-
-I first worked to provide a check on the analysis presented in @trounstine_segregation_2016 by attempting to replicate the work in R.
-I was able to successfully replicate all of the main results from @trounstine_segregation_2016, with the exception of a few of a few marginal analyses of the complex, multi-level models which, to my knowledge, are currently not supported by available R packages.
-I was, however, able to successfully replicate these results in Stata.
-
-As an additional robustness check I also tested the models in @trounstine_segregation_2016 by re-running them with additional data that I imputed from missing values in the original datasets.
-The large number of missing values in both of the datasets used in @trounstine_segregation_2016's main analysis created a concern for potential bias in the original results and a lack of representativeness due to the large amount of data excluded from the regression analysis due to missing values.
-Thus, I used the mice package in R to create multiply imputed datasets, upon which I re-ran the models and pooled the results to generate the final model coefficients and parameters.
-
-The results of the data imputation exercise differed between the two datasets.
-For the analyses using the smaller, racial polarization dataset, the results from the imputed data resulted in a smaller magnitude of the coefficient on the main independent variable, and also made it statistically insignificant in the main model specification.
-This suggests that the segregation index may not have as strong of a positive association with political polarization as @trounstine_segregation_2016 suggests.
-Nevertheless, the imputation exercise generally supports the main ideas in this part of Trounstine's analysis.
-
-On the other hand, for the analyses using the much larger financial segregation dataset, the results of the models using the multiply imputed data sharply contrasted the results of @trounstine_segregation_2016, suggesting that diversity, and not segregation, was the best explanatory variable for public goods spending across cities.
-While these results originally seemed quite contradictory, I was able reconcile this finding by discovering that the results of @trounstine_segregation_2016 seem to be only really representative of larger cities.
-By dropping all observations in the original data with missing values for key variables, it seems that @trounstine_segregation_2016 inadvertently restricted their sample to almost entirely larger cities (above 25,000 residents) whereas the full sample consisted of cities that had smaller populaitons.
-To test the hypothesis that diversity is more important for predicting public goods spending for small cities while segregation is more important for predicting public goods spending for larger cities, I divided the original dataset into two subsets based on the city classificaiton criteria used in @baqir_public_1999 that cities must have a population of at least 25,000 people.
-I then multiply imputed the missing values for each data subset and re-ran the models.
-I found that the results presented initial evidence in support of my hypothesis.
-for the cities below the 25,000 person populaiton cutoff, the coefficient for diversity was positive and significant while the coefficient for the segregation index was insignificant.
-For cities above the 25,000 person cutoff, the results were very similar to the results found in @trounstine_segregation_2016: the coefficient for diversity was insignificant, but the coefficient for the segregation index was significant and negative.
-
-The replication exercise and the robustness check of @trounstine_segregation_2016's model using multiply imputed data provide additional evidence that residential racial segregation is associated with political polarization.
-Furthermore, I find evidence that supports the finding of @trounstine_segregation_2016 that increases in segregation are associated with decreases in public goods spending; however, I find that this is only the case for larger cities.
-In contrast to the argument made by @trounstine_segregation_2016, I find that, for small cities, diversity, not segregation, seems to be the most important explanatory variable for public goods spending.
-One potential explanation for this result could be that when cities become too small, the sort of segregation by neighborhood described in @trounstine_segregation_2016 as a diverse city broken down into homogenous, segregated neighborhoods becomes hard to maintain.
-When populaiton sizes are small, segregation may become difficult and inter-racial interactions may become more common, leading diversity to be more indicative of a degree of integration.
-This provides a possible explanation as to why the coefficient on diversity was positive for very small cities, as these "cities" may function more closely as neighborhoods (many of them with populaitons ranging from X-X thousand); as discussed in the literature review, diversity at the neighborhood level is associated with lower levels of political polarization (Oliver 2010) and thus we would expect these areas to have higher levels of public goods spending according to the ideas of @trounstine_segregation_2016.
-As cities become larger and larger, however, comprehensive segregation becomes more attainable.
-Thus, segregation, not diversity, becomes a better indicator of inter-racial harmony and cooperation and thus the best explanatory variable for public goods spending.
-
-It is possible that other mechanisms may be more important in explaining differences in spending across cities on public goods.
-For example, it could be that there is an important interaction effect between income and segregation, as others have previously suggested, or there could be some other intervening mechanism or a confounding variable that is leading to the negative association between segregation and lower spending on public goods.
-@trounstine_segregation_2016 has identified an important relationship between segregation and the provision of public goods.
-However, my analysis suggests that further research is needed to assess for which cities this relationship holds.
-At what city size or population density does segregaiton become more relevant than diversity?
-And what implications does this have for how public policy should be designed and implemented to address these issues?
-These are important questions that merit further investigation, because by improving our ability to identify, understand, and address its root causes, we may be able to better address the underprovision of public goods, which may inhibit social mobility and unfairly disadvantage certain groups.
-
-\newpage
-
-# Appendix
-
-```{r  include = FALSE}
-
-## regression 1 Table 1
-
-# perform a multi-level mixed-effects linear regression of biggest split on the multi-group H index with controls for Herfindahl Diversity Index, % Asian interpolated, % Black interpolated, % Latino interpolated, median household income interpolated, % renters interpolated, percent college grads interpolated, a dummy indicating if there were biracial candidates in the election, a dummy  indicating if the election was nonpartisan, an indicator if the election was a primary, and the log population.
-The regression also includes fixed effects for year and region and random effects for cities (geo_id2).
-Diversity is  included because of the claim that more diverse populations will have more heterogeneous political preferences.
-The other fixed effect control variables are included because they are known to be potentially correlated with segregation.
-winner == 1 requires that there was a winner in the election.
-
-# regression specification. Apply REML = FALSE. The default for lmer() in R is
-# to optimize the restricted (residual) maximum likelihood (REML) whereas in
-# xtmixed in Stata the default is to optimize the log likelihood (which you can
-# do in lmer() in R by setting REML = FALSE), so this will match the STATA code
-
-m1 <- lmer(biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-## regression 2 Table 1
-
-# Perform the same regression as for Column 1 above but this time regress on the two-group calculation of Theil's H interpolated.
-It is unclear where the "diversity" variable is coming from, as the only variable related to diversity in the specificed dataset is diversityinterp.
-This is a problem that will need to be resolved.
-Essentially, this regression just tests an alternate specification to the first in which the segregation index in defined in terms of two-groups rather than multiple.
-
-m2 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-# perform the same regression as for column 2, but now add in a measure of
-# average white political ideology. The point of this is to control for ideology
-# so that the author can separate any effects of segregation from any potential
-# effects of white political ideology. This is important because it is possible
-# that segregation is just a proxy for white conservatism and thus failure to
-# include this variable could lead to ommitted variable bias.
-
-m3 <- lmer(biggestsplit ~ H_citytract_NHW_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + whiteideology_fill2 + year.f + south + midwest + west + (1 | geo_id2), data = rp_1, REML=FALSE)
-
-```
-
-```{r results="asis", echo = FALSE}
-
-# create a stargazer table of the results
-
-t1 <- stargazer(m1, m2, m3, omit = c("year", "south", "midwest", "west"),
-                header = FALSE,
-                style = "apsr",
-                title = "\\textbf{Racial Polarization in Segregated Cities}",
-                single.row = FALSE,
-                no.space = F,
-                covariate.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Diversity", "Percent Asian", "Percent Black", "Percent Latino", "Medain HH Income (1000s)", "Percent Renters", "Percent College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology", "Constant"),
-                dep.var.labels = c("\\textbf{\\underline{Racial Divide with:    }}"),
-                column.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Ideology Controls"),
-                notes = c("Table A1: This table displays the results of the replication effort of the analyses conducted in Trounstine (2016)", 
-                          "using the racial polarization dataset. The replication code can be found on my personal Github repository, which is",
-                          " linked in the introduction. The original table is displayed for comparison as Figure 3."),
-                table.placement = "H",
-                notes.align = "l",
-                font.size = "small")
-
-```
-
-![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016.
-My replication of these results can be found in Table A1 in this paper.](table_1.png)
-
-```{r felm, include = FALSE}
-
+```{r run_first_T_mode_for_coeff_plot, include = F}
 # Main Analysis 2
@@
 felm1 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
+```
+
+```{r calc_coeff_sds_original_fs_impute, include = FALSE}
+
+model_coeff <- tibble(
+  variable = c("White/Non-White Seg. Index", "Diversity", 
+               "White/Non-White Seg. Index", "Diversity",
+               "White/Non-White Seg. Index", "Diversity", 
+               "White/Non-White Seg. Index", "Diversity"),
+  estimate = c(imp_under_baqir_1_sum[1,2], imp_under_baqir_1_sum[2,2],
+               imp_felm1_sum[1,2], imp_felm1_sum[2,2],
+               coef(felm1)[1], coef(felm1)[2],
+               imp_over_baqir_1_sum[1,2], imp_over_baqir_1_sum[2,2]),
+  std_error = c(imp_under_baqir_1_sum[1,3], imp_under_baqir_1_sum[2,3],
+                imp_felm1_sum[1,3], imp_felm1_sum[2,3],
+                summary(felm1)$coeff[1,2], summary(felm1)$coeff[2,2],
+                imp_over_baqir_1_sum[1,3], imp_over_baqir_1_sum[2,3]),
+  model = c( "fin_imp_pop_under_baqir", "fin_imp_pop_under_baqir",
+             "fin_imp", "fin_imp",
+            "fin_dge", "fin_dge",
+            "fin_imp_pop_over_baqir", "fin_imp_pop_over_baqir")
+)
+
+model_coeff <- model_coeff %>%
+  mutate(variable = as.factor(variable))
+
+```
+
+```{r dataset_rows_in_analysis, include = FALSE}
+
+complete_fs <- complete(imp_fs,1) %>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+complete_over_baqir <- complete(imp_fs_pop_overbaqir, 1)%>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+complete_under_baqir <- complete(imp_fs_pop_under_baqir, 1)%>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+```
+
+```{r dataset_medians, include = FALSE}
+
+data_info <- tibble(
+  dataset = c("fin_imp", "fin_imp_pop_over_baqir", "fin_imp_pop_under_baqir",
+               "fin_dge"),
+  median = c(median(fin_imp$logpop), median(fin_imp_pop_over_baqir$logpop),
+              median(fin_imp_pop_under_baqir$logpop), median(fin_dge$logpop)),
+  rows = c(nrow(complete_fs), nrow(complete_over_baqir), nrow(complete_under_baqir),
+          nrow(fin_dge))
+)
+
+model_summaries <- left_join(model_coeff, data_info, by = c("model" = "dataset"))
+
+```
+
+```{r histograms_city_pop_in_specifications_prep, include = FALSE}
+
+pop_data_over_baqir <- tibble(
+  log_pop = complete_over_baqir$logpop,
+  Analysis = "Imputed, pop. > 25k"
+)
+
+pop_data_under_baqir <- tibble(
+  log_pop = complete_under_baqir$logpop,
+  Analysis = "Imputed, pop. < 25k"
+)
+
+pop_data_imp_fs <- tibble(
+  log_pop = complete_fs$logpop,
+  Analysis = "Imputed, Whole Sample"
+)
+
+pop_data_fin_dge <- tibble(
+  log_pop = fin_dge$logpop,
+  Analysis = "Trounstine (2016)"
+)
+
+pop_data_fin_seg <- tibble(
+  log_pop = fin_seg$logpop,
+  Analysis = "Original Sample"
+)
+
+pop_hist_data <- rbind(pop_data_over_baqir, pop_data_imp_fs)
+pop_hist_data <- rbind(pop_hist_data, pop_data_under_baqir)
+pop_hist_data <- rbind(pop_hist_data, pop_data_fin_dge)
+pop_hist_data <- rbind(pop_hist_data, pop_data_fin_seg)
+
+median_pops <- tibble(
+  Analysis = c("Imputed, pop. > 25k", "Imputed, pop. < 25k", "Imputed, Whole Sample", "Trounstine (2016)", "Original Sample"),
+  median_log_pop = c(median(complete(imp_fs_pop_overbaqir,1)$logpop),
+                     median(complete(imp_fs_pop_under_baqir, 1)$logpop),
+                     median(complete(imp_fs, 1)$logpop),
+                     median(fin_dge$logpop),
+                     median(fin_seg$logpop, na.rm = T))
+)
+
+pop_hist_data <- left_join(pop_hist_data, median_pops)
+
+```
+
+```{r city_pops_histogram, echo = FALSE, warning = FALSE}
+
+pop_hist_data %>%
+  ggplot() +
+  geom_histogram(aes(x = log_pop, fill = Analysis)) +
+  geom_vline(aes(xintercept = median_log_pop), color = "red") +
+  facet_wrap(~Analysis) +
+  coord_cartesian(xlim = c(0,15)) +
+  ggtitle("Histograms of Log Population of City Observations Included in the\nVarious Regression Analyses") +
+  labs(caption = "This figure makes clear the differences in city size (in terms of population) among the different analyses.\n It is clear that the listwise deletion of observations with missing values resulted in a sample that almost entirely\nconsisted of larger cities in Trounstine (2016).
+The distribution of city population in Trounstine (2016)\nmore closely resembles the distribution of the original sample with a greater than 25,000 population\ncutoff imposed than the original sample.
+The red lines indicate the median log population in each sample.") +
+  ylab("Count") +
+  xlab("Log Population") +
+  theme_bw() +
+  theme(plot.caption = element_text(hjust = 0),
+        strip.text.x = element_text(size = 8))
+
+```
+
+The results of the models run with the multiply imputed datasets above and below the cutoff are presented in the following two tables.
+
+```{r over_baqir_t1, echo = FALSE}
+
+# print results of 1st regression
+
+imp_over_baqir_1_sum_table <- as.data.frame(imp_over_baqir_1_sum %>% 
+  select(term, estimate, std.error, p.value))
+
+imp_over_baqir_1_sum_table_vars <- tibble(
+  Variable = c("White/Nonwhite Seg. Index", "Diversity", "% Black", "% Asian", "% Latino", "Median Income (1000s)", "% Local Gov. Worker", "% Renters", "% 65+", "% College Grads", "Pop (logged)"),
+  Estimate = round(imp_over_baqir_1_sum_table$estimate, 3),
+  `Std. Error` = round(imp_over_baqir_1_sum_table$std.error,3),
+  `P-Value` = round(imp_over_baqir_1_sum_table$p.value, 3)
+)
+
+kable(imp_over_baqir_1_sum_table_vars, "latex",
+      caption = "\\textbf{Effect of Segregation on Overall per Capita Direct General City Expenditures: Imputed Data for Cities with Populations of 25,000+}",
+      booktabs = T) %>%
+    row_spec(0, bold = TRUE) %>%
+  footnote(general = c("This table shows the results of Trounstine's third model for the effect of segregation on political polarization",
+  "(racial vote divide) using the two-group Theil's H segregation Index and including controls for ideology",
+  "using the new, multiply imputed datasets. Compared to Trounstine's original results, the main coefficient on",
+  "segregation index has decreased in magnitude although, it remains statistically significant. The other",
+  "coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian and",
+  "Black have switched signs. Standard errors have also reduced slightly in these specifications compared to",
+  "the original analysis in Trounstine (2016)."),
+           general_title = "Table 6:") %>%
+  kable_styling(full_width = TRUE)
+
+```
+
+As a summary of all of the model results for the two main coefficients of interest, segregation index and diversity, a coefficient plot is presented in Figure XXX, with the models ordered by increasing median log population size of the sample on the x-axis.
+Looking first at the coefficients for diversity, the two models with low median city populaiton size have significant, positive coefficients, while the models with the larger median city populations have insignificant coefficients.
+This suggestst that diversity is an important estimator of public goods spending for small, but not necessarily for large, cities.
+Next, looking at the plot for the segregation index, we see the oppposite effect.
+For the models where the median city population sizes were small, the coefficient on segregaiton is insignificant.
+However, for the two models with larger median city populations, the coefficients were significant and negative.
+This suggests that for small cities, segregation is not a very good estimator of public goods spending, but when cities are larger, increases in a city's segregation index are associated with decreases in public goods spending.
+
+```{r coef_plot_originals_over_under, echo = FALSE}
+
+model_summaries %>%
+  ggplot(aes(x = median, y = estimate)) +
+  geom_point()+
+  geom_errorbar(aes(ymin = estimate - 2 * std_error, ymax = estimate + 2 * std_error, width = .2)) +
+  geom_hline(yintercept = 0, color = "red") +
+  facet_wrap(~variable) +
+  ggtitle("Coefficient Plots for Diversity and White/Non-White Segregation Indices Across\nthe Models")+
+  xlab("Models Ordered by Increasing Median Population Size of the Sample") +
+  ylab("Estimate and 95% Confidence Interval") +
+  labs(caption = "This plot demonstrates how the significance of diversity and segregation in predicting public goods spending varies\n with city size.
+As city populaiton size increases, diversity tends to have less explanatory power\nfor public goods spending while segregation has more.
+The opposite is true when considering\ncity population size decreasing: segregation becomes less important as diversity becomes\nincreasingly important.") +
+  theme_bw()+
+  theme(plot.caption = element_text(hjust = 0))
+
+```
+
+# Conclusion
+
+Why cities differ in their amount of spending on public goods is an interesting question that is frequently debated in the literature.
+@trounstine_segregation_2016 posits that segregation may be an important underlying cause of the underprovsion of public goods.
+Finding evidence that residential segregation by race increases political partisanship, @trounstine_segregation_2016 argues that residential segregation can increase division and make cooperation amongst competing groups difficult, which results in decreased spending on public goods.
+The findings of @trounstine_segregation_2016 are particularly important because they suggest that segregation, as defined by many homogeneous neighborhoods within a larger diverse geographical area, is the key factor in disinvestment in public goods.
+This contradicts previous research which has suggested that levels of diversity were instead most important (see for example @baqir_public_1999 or @hopkins_diversity_2009).
+While @trounstine_segregation_2016 still represents relatively new reasearch as of 2020, it has yet to be fully vetted by additional research.
+Furthermore, some research that has been published on the topic since its publication suggests that other factors such as larger inequities in the political system favoring socially powerful groups [@lee_ethnic_2018] or the interaction of income and racial inequality [@an_its_2018] may be more important in explaining public goods provisions.
+
+I first worked to provide a check on the analysis presented in @trounstine_segregation_2016 by attempting to replicate the work in R.
+I was able to successfully replicate all of the main results from @trounstine_segregation_2016, with the exception of a few of a few marginal analyses of the complex, multi-level models which, to my knowledge, are currently not supported by available R packages.
+I was, however, able to successfully replicate these results in Stata.
+
+As an additional robustness check I also tested the models in @trounstine_segregation_2016 by re-running them with additional data that I imputed from missing values in the original datasets.
+The large number of missing values in both of the datasets used in @trounstine_segregation_2016's main analysis created a concern for potential bias in the original results and a lack of representativeness due to the large amount of data excluded from the regression analysis due to missing values.
+Thus, I used the mice package in R to create multiply imputed datasets, upon which I re-ran the models and pooled the results to generate the final model coefficients and parameters.
+
+The results of the data imputation exercise differed between the two datasets.
+For the analyses using the smaller, racial polarization dataset, the results from the imputed data resulted in a smaller magnitude of the coefficient on the main independent variable, and also made it statistically insignificant in the main model specification.
+This suggests that the segregation index may not have as strong of a positive association with political polarization as @trounstine_segregation_2016 suggests.
+Nevertheless, the imputation exercise generally supports the main ideas in this part of Trounstine's analysis.
+
+On the other hand, for the analyses using the much larger financial segregation dataset, the results of the models using the multiply imputed data sharply contrasted the results of @trounstine_segregation_2016, suggesting that diversity, and not segregation, was the best explanatory variable for public goods spending across cities.
+While these results originally seemed quite contradictory, I was able reconcile this finding by discovering that the results of @trounstine_segregation_2016 seem to be only really representative of larger cities.
+By dropping all observations in the original data with missing values for key variables, it seems that @trounstine_segregation_2016 inadvertently restricted their sample to almost entirely larger cities (above 25,000 residents) whereas the full sample consisted of cities that had smaller populaitons.
+To test the hypothesis that diversity is more important for predicting public goods spending for small cities while segregation is more important for predicting public goods spending for larger cities, I divided the original dataset into two subsets based on the city classificaiton criteria used in @baqir_public_1999 that cities must have a population of at least 25,000 people.
+I then multiply imputed the missing values for each data subset and re-ran the models.
+I found that the results presented initial evidence in support of my hypothesis.
+for the cities below the 25,000 person populaiton cutoff, the coefficient for diversity was positive and significant while the coefficient for the segregation index was insignificant.
+For cities above the 25,000 person cutoff, the results were very similar to the results found in @trounstine_segregation_2016: the coefficient for diversity was insignificant, but the coefficient for the segregation index was significant and negative.
+
+The replication exercise and the robustness check of @trounstine_segregation_2016's model using multiply imputed data provide additional evidence that residential racial segregation is associated with political polarization.
+Furthermore, I find evidence that supports the finding of @trounstine_segregation_2016 that increases in segregation are associated with decreases in public goods spending; however, I find that this is only the case for larger cities.
+In contrast to the argument made by @trounstine_segregation_2016, I find that, for small cities, diversity, not segregation, seems to be the most important explanatory variable for public goods spending.
+One potential explanation for this result could be that when cities become too small, the sort of segregation by neighborhood described in @trounstine_segregation_2016 as a diverse city broken down into homogenous, segregated neighborhoods becomes hard to maintain.
+When populaiton sizes are small, segregation may become difficult and inter-racial interactions may become more common, leading diversity to be more indicative of a degree of integration.
+This provides a possible explanation as to why the coefficient on diversity was positive for very small cities, as these "cities" may function more closely as neighborhoods (many of them with populaitons ranging from X-X thousand); as discussed in the literature review, diversity at the neighborhood level is associated with lower levels of political polarization (Oliver 2010) and thus we would expect these areas to have higher levels of public goods spending according to the ideas of @trounstine_segregation_2016.
+As cities become larger and larger, however, comprehensive segregation becomes more attainable.
+Thus, segregation, not diversity, becomes a better indicator of inter-racial harmony and cooperation and thus the best explanatory variable for public goods spending.
+
+It is possible that other mechanisms may be more important in explaining differences in spending across cities on public goods.
+For example, it could be that there is an important interaction effect between income and segregation, as others have previously suggested, or there could be some other intervening mechanism or a confounding variable that is leading to the negative association between segregation and lower spending on public goods.
+@trounstine_segregation_2016 has identified an important relationship between segregation and the provision of public goods.
+However, my analysis suggests that further research is needed to assess for which cities this relationship holds.
+At what city size or population density does segregaiton become more relevant than diversity?
+And what implications does this have for how public policy should be designed and implemented to address these issues?
+These are important questions that merit further investigation, because by improving our ability to identify, understand, and address its root causes, we may be able to better address the underprovision of public goods, which may inhibit social mobility and unfairly disadvantage certain groups.
+
+\newpage
+
+# Appendix
+
+```{r results="asis", echo = FALSE}
+
+# create a stargazer table of the results
+
+t1 <- stargazer(m1, m2, m3, omit = c("year", "south", "midwest", "west"),
+                header = FALSE,
+                style = "apsr",
+                title = "\\textbf{Racial Polarization in Segregated Cities}",
+                single.row = FALSE,
+                no.space = F,
+                covariate.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Diversity", "Percent Asian", "Percent Black", "Percent Latino", "Medain HH Income (1000s)", "Percent Renters", "Percent College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology", "Constant"),
+                dep.var.labels = c("\\textbf{\\underline{Racial Divide with:    }}"),
+                column.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Ideology Controls"),
+                notes = c("Table A1: This table displays the results of the replication effort of the analyses conducted in Trounstine (2016)", 
+                          "using the racial polarization dataset. The replication code can be found on my personal Github repository, which is",
+                          " linked in the introduction. The original table is displayed for comparison as Figure 3."),
+                table.placement = "H",
+                notes.align = "l",
+                font.size = "small")
+
+```
+
+![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016.
+My replication of these results can be found in Table A1 in this paper.](table_1.png)
+
+```{r felm, include = FALSE, eval = FALSE}
+
+# Main Analysis 2
+
+## regression 1 Table 2
+
+# The following is a fixed effects model regression with clustering around
+# geo_id2. It mandates that total census tracts in the city is greater than 1,
+# which we want because our measure of evenness of racial spread is constant for
+# cities with only one tract by our definition (which requires comparing tracts
+# within cities). It also mandates that Direct General Expenditures (DGE) per
+# capita, CPI adjusted is not equal to 0, which would be problematic and
+# indicate a potential data error. This regression regresses the DGE per capita
+# on the the two-group calculation of  Theil's H interpolated. Controls are
+# included for diversity and the % populations of Blacks, Asians, and Latinos to
+# help identify whether it is actually diversity that drives down spending.These
+# demographic controls also help to account for the fact that whites and
+# minorities tend to perfer different levels of government spending in general.
+# This will help isolate the effects of segregation v. other forms of diversity
+# on public spending. Other controls for Median household income, CPI adjusted,
+# percent over 65, percent college grads, percent local government workers, log
+# population help control for additional factors related to segregation and
+# expenditure. Controls for percent renters interpolated and Median household
+# income also help to control for the general wealth of cities, which could be a
+# potential driver of public spending. Fixed effects for cities are also
+# included  so that the author can examine the effect of segregation in the same
+# city over  time, which also helps control for many other factors not otherwise
+# taken into account (such as city age)
+
+# apply the conditions in Stata regression
+
+fin_seg_sub <- fin_seg %>%
+  filter(totaltractsf > 1 | is.na(totaltractsf), dgepercap_cpi != 0) %>%
+  mutate(medinc_cpi = medinc_cpi/1000)
+
+# felm(y~x | factor(fe1) + factor(fe2) | 0 | clustervar)
+
+felm1 <- felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2, data = fin_seg_sub)
 
@@
 
-```{r main_fp_tables, results = "asis", echo = FALSE}
+```{r main_fp_tables, results = "asis", echo = FALSE, eval = FALSE, include = FALSE}
 
@@
 
+```{r fs_densityplot, echo = FALSE, eval = FALSE, include = FALSE}
+
+my.settings <- list(
+  par.main.text = list(font = 1, cex = 1)
+)
+
+#densityplot(imp_fs)
+densityplot(x = imp_fs, 
+            data = ~ H_citytract_NHW_i + chng5pctblk + chng5pctlatino + chng5pctasian + ideology_fill,
+            main = "Density Plots of Imputed and Original Data by Variable\nin the Financial Segregation Dataset",
+            par.settings = my.settings,
+            par.strip.text = list(cex = 1))
+
+```
+
 \newpage

### 2020-05-07 Burzillo_Trounstine_Replication.Rmd
edits to introduction

--- 2020-05-07 Final_Draft.Rmd
@@
 output: 
-  pdf_document:
+  bookdown::pdf_document2: 
     fig_caption: true
 bibliography: final_proj_bib.bib
-#biblio-style: "apalike"
 link_citations: true
@@
   \usepackage{multirow}
+  \usepackage{setspace}\doublespacing
+toc: false
 
@@
 In this analysis, I was able to successfully replicate @trounstine_segregation_2016’s main results.
-I then attempted to better deal with the large amounts of missing data in the datasets used in the original analysis by multiply imputing missing values using the mice() package and then by re-running the original models using the multiply imputed datasets.
+I then attempted to better deal with the large amounts of missing data in the datasets used in the original analysis by multiply imputing missing values and re-running the original models using the multiply imputed datasets.
 My results suggest that segregation is associated with increased racial political polarization, although maybe not as strongly as Trounstine (2016) originally suggested.
@@
 As a result, many scholars have worked to determine what factors may lead to the underprovision of public goods spending.
-Research in the past has associated racial diversity or changes in levels of diversity with the under-provision of public goods [@baqir_public_1999; @hopkins_diversity_2009].However, @trounstine_segregation_2016 argues that it is racial segregation, not diversity in and of itself, that results in the under-provision of public goods.
+Research in the past has associated racial diversity or changes in levels of diversity with the under-provision of public goods [@baqir_public_1999; @hopkins_diversity_2009].
+However, @trounstine_segregation_2016 argues that it is racial segregation, not diversity in and of itself, that results in the under-provision of public goods.
 Trounstine’s analysis consists of two main parts.
-First, she uses election and demographic data from 25 of America’s largest cities between 1990 and 2010 to run a multilevel mixed-effects linear regression with fixed effects for region and year and with random effects for cities in order to show that polarization increases with segregation.
+First, she uses election and demographic data from 25 of America’s largest cities between 1990 and 2010 to run a multilevel mixed-effects linear regression with fixed effects for region and year and with random effects for cities in order to show that political polarization increases with segregation.
 Trounstine measures segregation with Theil's H index, which measures the degree to which the diversity of a neighborhood differs from the diversity of the entire city.
@@
 One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data, which substantially constrains the sample size used in the regression analysis.
-For example, the regression analysis in the main specification using the the original racial polarization dataset exludes %`r round((obs_rp - 91)/obs_rp, 2)` of the observations, and the regression analysis in the main specification using the original financial segregation data excludes %`r round((obs_fin_seg - 13742)/ obs_fin_seg, 2)` of observations from the original dataset.
+For example, the regression analysis in the main specification using the the original racial polarization dataset exludes %`r round((obs_rp - 91)/obs_rp * 100, 2)` of the observations, and the regression analysis in the main specification using the original financial segregation data excludes %`r round((obs_fin_seg - 13742)/ obs_fin_seg * 100, 2)` of observations from the original dataset.
 As an extension of @trounstine_segregation_2016, I impute missing values in the original data using the mice package in R, which generates multivariate imputations using chained equations [@mice].
@@
 
-Comparing the results of the original regressions and those done with the imputed data yields similar big picture results in terms of the direction of the signs on the coefficients on the segregation indices.
-Like in @trounstine_segregation_2016, I find that segregation is positively associated with political polarization and negatively associated with spending on public goods.
-However, the magnitude of the effects in most specifications has diminished and most results become statistically insignificant.
-While these findings do not necessarily challenge the results of @trounstine_segregation_2016, they do call into question the relative importance of segregation in determining public goods spending and political polarization and suggest that the results of @trounstine_segregation_2016 may not be quite as robust as once thought.
+Comparing the results of the original regressions and those done with the imputed data yields similar big picture results for the analyses concerning the relationship between political polarization and segregation.
+Like in @trounstine_segregation_2016, I find that segregation is positively associated with political polarization; however, the magnitude and significance of the effect has diminsihed slightly.
+For the second set of analyses conducted with the financial segregation data, my initial results for running the models with the imputed data differ significantly from @trounstine_segregation_2016, suggesting that diversity, not segregation, is the more robust explanatory factor in patterns of public goods spending across cities.
+Nevertheless, this is likely because the data imputation exercise led to the inclusion of a much larger percentage of small cities in the sample, which were perhaps inadvertently largely excluded in @trounstine_segregation_2016 due to the list-wise deletion of observations with missing values, which were more frequently found in small cities.
+To explore whether or not city size impacted the results, I divided the original sample into two groups, large and small cities, based on the 25,000 population cutoff used to define cities in @baqir_public_1999.
+Performing the data imputation exercise and re-running the models on these subsets revealed that for large cities, segregation was the most powerful explanatory variable for public goods spending, while for small cities, diversity remained the most powerful explanatory variable.
 
@@
 
-```{r results_printing_rp_impute_regressions_2, results = "asis", include = FALSE, eval = FALSE}
-
-# print results of 2nd regression
-
-imp_2_rp_sum_table <- as.data.frame(imp_2_rp_sum) %>% 
-  select(term, estimate, std.error, p.value) %>%
-  head(13)
-
-imp_2_rp_sum_table_vars <- tibble(
-  Variable = c("Intercept", "White/Nonwhite Seg. Index", "Diversity", "% Asian", "% Black", "% Latino",
-               "Median Income (1000s)", "% Renters", "% College Grads", "Biracial Elec.", "Nonpartisan Elec.", "Primary Elec.", "Pop (logged)"),
-  Estimate = round(imp_2_rp_sum_table$estimate, 3),
-  `Std. Error` = round(imp_2_rp_sum_table$std.error,3),
-  `P-Value` = round(imp_2_rp_sum_table$p.value, 3)
-  )
-
-kable(imp_2_rp_sum_table_vars, "latex", caption = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Two-Group Segregation Index}", booktabs = T) %>%
-  row_spec(0, bold = TRUE) %>%
-  footnote(general = c("This table shows the results of Trounstine's second model for the effect of segregation on political polarization",
-  "(racial vote divide) using the two-group Theil's H segregation Index using the new, multiply imputed datasets.", 
-  "Compared to Trounstine's original results, the main coefficient on segregation index has decreased in magnitude",
-  "although, it remains statistically significant. The other coefficients except for the biracial indicator are",
-  "insignificant, and the coefficients on percent Black, percent Latino, and Median Income have switched signs.",
-  "Standard errors have also reduced slightly in these specifications compared to the original analysis in",
-  "Trounstine (2016)."),
-           general_title = "Table 2:") %>%
-  kable_styling(full_width = TRUE)
-
-```
-
 In the third regression, like in the second, the main coefficient on segregation index has decreased in magnitude but remains significant.
@@
 In all three of the specifications, standard errors reduced slightly using the larger, multiply imputed datasets compared to the original analysis with the original data in @trounstine_segregation_2016.
-
-```{r results_printing_rp_impute_regressions_3, results = "asis", include = FALSE, eval = FALSE}
-
-# print results of 3rd regression
-
-imp_3_rp_sum_table <- as.data.frame(imp_3_rp_sum) %>% 
-  select(term, estimate, std.error, p.value) %>%
-  head(14)
-
-imp_3_rp_sum_table_vars <- tibble(
-  Variable = c("Intercept", "White/Nonwhite Seg. Index", "Diversity", "% Asian", "% Black", "% Latino",
-               "Median Income (1000s)", "% Renters", "% College Grads", "Biracial Elec.", "Nonpartisan Elec.", "Primary Elec.", "Pop (logged)", "White Ideology"),
-  Estimate = round(imp_3_rp_sum_table$estimate, 3),
-  `Std. Error` = round(imp_3_rp_sum_table$std.error,3),
-  `P-Value` = round(imp_3_rp_sum_table$p.value, 3)
-  )
-
-kable(imp_3_rp_sum_table_vars, "latex", caption = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Ideology Control}", booktabs = T) %>%
-  row_spec(0, bold = TRUE) %>%
-  footnote(general = c("This table shows the results of Trounstine's third model for the effect of segregation on political polarization",
-  "(racial vote divide) using the two-group Theil's H segregation Index and including controls for ideology",
-  "using the new, multiply imputed datasets. Compared to Trounstine's original results, the main coefficient on",
-  "segregation index has decreased in magnitude although, it remains statistically significant. The other",
-  "coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian and",
-  "Black have switched signs. Standard errors have also reduced slightly in these specifications compared to",
-  "the original analysis in Trounstine (2016)."),
-           general_title = "Table 3:") %>%
-  kable_styling(full_width = TRUE)
-
-```
 
@@
 
-```{r coef_plot_originals_over_under, echo = FALSE}
+```{r coef_plot_rp, echo = FALSE}
 
@@
 
-```{r fs_imputed_pooled_regressions, include = FALSE, eval = FALSE}
-
-## regression 2 Table 2
-
-# fit multiple imputed datasets
-
-fit_imp_felm2 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm2 <- pool(fit_imp_felm2)
-imp_felm2_sum <- summary(pool_imp_felm2)
-
-## Regression 3 Table 2
-
-fit_imp_felm3 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm3 <- pool(fit_imp_felm3)
-imp_felm3_sum <- summary(pool_imp_felm3)
-
-print(imp_felm1_sum)
-
-```
-
 ```{r results_printing_fs_impute_regressions_1, results = "asis", echo=FALSE}
@@
 
-```{r results_printing_fs_impute_regressions_2, results = "asis", echo=FALSE, eval = FALSE, include = FALSE}
-
-# print results of 2nd regression
-
-imp_felm2_sum_table <- as.data.frame(imp_felm2_sum %>% 
-  select(term, estimate, std.error, p.value))
-
-imp_felm2_sum_table_vars <- tibble(
-  Variable = c("White/Nonwhite Seg.
-Index", "% Black", "% Asian", "% Latino", "5Y Change % Black", "5Y Change % Latino", "5Y Change % Asian", "Median Income (1000s)", "% Local Gov.
-Worker", "% Renters", "% 65+", "% College Grads", "Pop (logged)"),
-  Estimate = round(imp_felm2_sum_table$estimate, 3),
-  `Std. Error` = round(imp_felm2_sum_table$std.error,3),
-  `P-Value` = round(imp_felm2_sum_table$p.value, 3)
-)
-
-kable(imp_felm2_sum_table_vars, "latex",
-      caption = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Changing Demographics}",
-      booktabs = T) %>%
-    row_spec(0, bold = TRUE) %>%
-  footnote(general = c("This table shows the results of Trounstine's second model for the effect of segregation on per capita",
-  "direct public expenditure using the two-group Theil's H Segregation Index using the new, multiply imputed datasets.",
-  "Again, in contrast to Trounstine's original results, the main coefficient on segregation index has decreased to",
-  "essentially zero and has become statistically insignificant with a very large P-Value."),
-           general_title = "Table 5:") %>%
-  kable_styling(full_width = TRUE)
-
-```
-
-```{r results_printing_fs_impute_regressions_3, results = "asis", echo = FALSE, eval = FALSE, include = FALSE}
-
-# print results of 3rd regression
-
-imp_felm3_sum_table <- as.data.frame(imp_felm3_sum %>% 
-  select(term, estimate, std.error, p.value))
-
-imp_felm3_sum_table_vars <- tibble(
-  Variable = c("White/Nonwhite Seg.
-Index", "Diversity", "% Black", "% Asian", "% Latino", "Median Income (1000s)", "% Local Gov.
-Worker", "% Renters", "% 65+", "% College Grads", "Pop (logged)", "Ideology"),
-  Estimate = round(imp_felm3_sum_table$estimate, 3),
-  `Std. Error` = round(imp_felm3_sum_table$std.error,3),
-  `P-Value` = round(imp_felm3_sum_table$p.value, 3)
-)
-
-kable(imp_felm3_sum_table_vars, "latex",
-      caption = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Ideology Control}",
-      booktabs = T) %>%
-    row_spec(0, bold = TRUE) %>%
-  footnote(general = c("This table shows the results of Trounstine's third model for the effect of segregation on political polarization",
-  "(racial vote divide) using the two-group Theil's H segregation Index and including controls for ideology",
-  "using the new, multiply imputed datasets. Compared to Trounstine's original results, the main coefficient on",
-  "segregation index has decreased in magnitude although, it remains statistically significant. The other",
-  "coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian and",
-  "Black have switched signs. Standard errors have also reduced slightly in these specifications compared to",
-  "the original analysis in Trounstine (2016)."),
-           general_title = "Table 6:") %>%
-  kable_styling(full_width = TRUE)
-
-```
-
 Because these results differed to such a degree from @trounstine_segregation_2016's original findings, I performed some checks on the data included in each analysis.
@@
 
-```{r run_first_T_mode_for_coeff_plot, include = F}
+```{r run_first_T_model_for_coeff_plot, include = F}
 # Main Analysis 2
@@
 
+```{r under_baqir_t1, echo = FALSE}
+
+# print results of 1st regression
+
+imp_under_baqir_1_sum_table <- as.data.frame(imp_under_baqir_1_sum %>% 
+  select(term, estimate, std.error, p.value))
+
+imp_under_baqir_1_sum_table_vars <- tibble(
+  Variable = c("White/Nonwhite Seg. Index", "Diversity", "% Black", "% Asian", "% Latino", "Median Income (1000s)", "% Local Gov. Worker", "% Renters", "% 65+", "% College Grads", "Pop (logged)"),
+  Estimate = round(imp_under_baqir_1_sum_table$estimate, 3),
+  `Std. Error` = round(imp_under_baqir_1_sum_table$std.error,3),
+  `P-Value` = round(imp_under_baqir_1_sum_table$p.value, 3)
+)
+
+kable(imp_under_baqir_1_sum_table_vars, "latex",
+      caption = "\\textbf{Effect of Segregation on Overall per Capita Direct General City Expenditures: Imputed Data for Cities with Populations of 25,000+}",
+      booktabs = T) %>%
+    row_spec(0, bold = TRUE) %>%
+  footnote(general = c("This table shows the results of Trounstine's third model for the effect of segregation on political polarization",
+  "(racial vote divide) using the two-group Theil's H segregation Index and including controls for ideology",
+  "using the new, multiply imputed datasets. Compared to Trounstine's original results, the main coefficient on",
+  "segregation index has decreased in magnitude although, it remains statistically significant. The other",
+  "coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian and",
+  "Black have switched signs. Standard errors have also reduced slightly in these specifications compared to",
+  "the original analysis in Trounstine (2016)."),
+           general_title = "Table 6:") %>%
+  kable_styling(full_width = TRUE)
+
+```
+
 As a summary of all of the model results for the two main coefficients of interest, segregation index and diversity, a coefficient plot is presented in Figure XXX, with the models ordered by increasing median log population size of the sample on the x-axis.
@@
 
-```{r main_fp_tables, results = "asis", echo = FALSE, eval = FALSE, include = FALSE}
-
-# create main table for table 3
-
-table2 <- stargazer(felm1, felm2, felm3, omit = c("year", "south", "midwest", "west"), 
-                    header = FALSE,
-                    style = "apsr",
-                    title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures}",
-                    covariate.labels = c("White/Nonwhite H Index", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Change Percent Black", "Change Percent Latino", "Change Percent Asian", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Population (logged)", "White Ideology", "Constant"),
-                    dep.var.labels = c("\\textbf{\\underline{Direct General Expenditure Per Capita}}"),
-                    column.labels = c("Main Specification", "Changing Demographics", "Ideology Controls"),
-                    notes = c("Table A2: This table displays the results of the replication effort of the analyses conducted in Trounstine (2016)", "
-                              assessing the effect of segregation in direct per capita public expenditures using the financial segregation",
-                              "dataset. The replication code can be found on my personal Github repository, which islinked in the introduction."),
-                    table.placement = "H",
-                    notes.align = "l",
-                    font.size = "small")
-
-```
-
-```{r, include = FALSE}
+```{r, include = FALSE, eval = FALSE}
 
@@
 
-```{r iv_regs, include = FALSE}
+```{r iv_regs, include = FALSE, eval = FALSE}
 
@@
 
+```{r fs_imputed_pooled_regressions_specifications_2_and_3, include = FALSE, eval = FALSE}
+
+## regression 2 Table 2
+
+# fit multiple imputed datasets
+
+fit_imp_felm2 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_imp_felm2 <- pool(fit_imp_felm2)
+imp_felm2_sum <- summary(pool_imp_felm2)
+
+## Regression 3 Table 2
+
+fit_imp_felm3 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))
+
+# pool the analyses
+
+pool_imp_felm3 <- pool(fit_imp_felm3)
+imp_felm3_sum <- summary(pool_imp_felm3)
+
+print(imp_felm1_sum)
+
+```
+
 \newpage

### 2020-05-07 Burzillo_Trounstine_Replication.Rmd
edits to lit review and extension write up

@@
 Neighborhoods are often important actors within local politics because local governments provide many functions that are allocational in nature and concern geographical space [@trounstine_segregation_2016].
-Thus, when neighborhoods are divided on racial lines as well as spacial lines, it is natural to expect higher degrees of racial polarization as a result.
+Thus, when local areas are composed of neighborhoods that are divided on racial lines as well as spacial lines, it is natural to expect higher degrees of racial polarization as a result.
 
@@
 Thus, while people of different races co-exist within a highly segregated city, they live separately within their own neighborhoods, which creates an environment ripe for racial tension [@trounstine_segregation_2016].
-It is thus not simply the level of diversity or integration that matters for racial harmony and cooperation, but their patterns within a larger geographic framework [@trounstine_segregation_2016; @oliver_paradoxes_2010; @bharathi_public_2018].
+It is thus not simply the levels of diversity or integration that matter for racial harmony and cooperation, but their patterns within a larger geographic framework [@trounstine_segregation_2016; @oliver_paradoxes_2010; @bharathi_public_2018].
 
@@
 For example, @lee_ethnic_2018 finds evidence that larger inequalities within the political system favoring socially powerful groups, not local diversity patterns leading to decreased cooperation, may be a better explanation of failures in public goods provision in diverse areas.
-Others suggest that additional factors, such as income segregation, may be important confounding factors in public goods provision.
-@an_its_2018, for example, suggests that the more closely related income inequality is to racial inequality, the less investment is made in public goods, and that this interaction was a better predictor of public goods spending patterns than measures of diversity.
-There is, in fact, a variety of evidence suggesting that it is meaningful to consider the effects of income inequaltiy and diversity and segregation jointly [@an_its_2018; @massey_american_1993].
-Given the active debate in the literature over the relaitonships between diversity, segregation, public spending, and other factors, it is increasingly important to re-examine previously reported findings as a means of robustness checks.
+Others suggest that additional factors, such as income segregation, may be important confounding factors in public goods provision [@an_its_2018; @massey_american_1993].
+@an_its_2018, for example, suggests that the more closely related income inequality is to racial inequality, the less investment is made in public goods, and that this interaction may be a better predictor of public goods spending patterns than measures of diversity.
+Given the active debate in the literature over the relaitonships between diversity, segregation, public goods spending, and other factors, it is increasingly important to re-examine previously reported findings as a means of robustness checks.
 
@@
 
-I was able to successfully replicate all of the main results from Trounstine (2016).
+In this analysis, I was able to successfully replicate all of the main results from Trounstine (2016).
 All regressions and tables were fully replicated in R.
-As an example, in table X, I replicate Table 1 from page 713 of @trounstine_segregation_2016, which is also included as Figure 1 for comparison.
+As an example, in table XXX in the Appendix, I replicate Table 1 from page 713 of @trounstine_segregation_2016, which is also included as Figure XXX for comparison.
 However, I was unable to successfully replicate Trounstine (2016)’s marginal effects analyses and margins plots using R.
@@
 There was one interesting outcome from my attempt to replicate the original Stata code in R.
-Due to the differences in R and Stata in dealing with missing values, the results of my first replication of analyses using the financial segregation dataset were slightly different than the results in Stata from the original paper.
+Due to the differences in R and Stata in dealing with missing values, the results of my first replication of the analyses using the financial segregation dataset were slightly different from the results in Stata presented the original paper.
+Ultimately, I discovered that this discrepancy was due to differences in R and Stata in dealing with missing values during conditioning.
 In order to exclude cities from her analysis with only one census tract, Trounstine conditions her regressions in Stata such that the value for the number of census tracts is greater than one.
 In Stata, this does not remove missing values, whereas in R, it does.
-Since this variable is used only as a conditional filter and not as a regression variable (and thus, the observations with missing values for number of census tracts are not dropped), Trounstine’s analysis includes 14 cities and 58 observations with missing values for census tracts in addition to cities with two or more census tracts.
+Since this variable is used only as a conditional filter and not as a regression variable (and thus, the observations with missing values for number of census tracts are not dropped when running the regressions), Trounstine’s analysis includes 14 cities and 58 observations with missing values for census tracts in addition to cities with two or more census tracts.
 This is a potential oversight on the part of the author, and I would suggest also dropping observations with missing census tract data, or else imputing them given that the aim of her condition was to exclude cities without a sufficient number of census tracts.
@@
 
-One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data values in her original datasets.
-Because both R and Stata drop any observations with missing values for any of the variables used in a regression, this can exlcude a large portion of the data from the analysis and potentially bias the results if the data is not missing completely at random.
+One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data values in the original datasets.
+Because both R and Stata by default drop any observations with missing values for any of the variables used in a regression, this can exlcude a large portion of the data from the analysis and potentially bias the results if the data is not missing completely at random.
 A large amount of data is missing in both of the main datasets used in the analyses of @trounstine_segregation_2016.
 The main model specification using the racial polarization dataset exludes `r (obs_rp - 91)` of the original  `r obs_rp` observations, or  %`r round(100*(obs_rp - 91)/obs_rp,2)` of the data.
-Additionally, the main model specification using the financial segregation data set excludes `r round(obs_fin_seg - 13742,2)` of the original `r obs_fin_seg` observations, or %`r round(100*(obs_fin_seg - 13742)/ obs_fin_seg,2)` of observations from the original dataset.
+Additionally, the main model specification using the financial segregation data set excludes `r format(obs_fin_seg - 13742, big.mark = ",")` of the original `r format(obs_fin_seg, big.mark = ",")` observations, or %`r round(100*(obs_fin_seg - 13742)/ obs_fin_seg,2)` of observations from the original dataset.
 
@@
 Before performing the multiple imputations on the datasets, I first examined the missing data for patterns.
-To better understand any potential patterns in missing data, I plotted the pattern of missingness and created a histogram showing the frequency of missing values for those variables with missing values in figure X1 for the racial polarization data and figure X2 for the financial segregation data.
-Looking at figure X1, the histogram shows that the variables for the largest vote split along racial lines and the variable indicating whether or not the election had candidates of more than one race had by far the largest percentages of missing data, missing %`r round(sum(is.na(rp_impute$biggestsplit))/nrow(rp_impute)*100,2)` and  %`r round(sum(is.na(rp_impute$biracial))/nrow(rp_impute)*100,2)`, respectively.
+To better understand any potential patterns in missing data, I plotted the pattern of missingness and created a histogram showing the frequency of missing values for those variables with missing values in Figure 1 for the racial polarization data and in Figure 2 for the financial segregation data.
+Looking at Figure 1, the histogram shows that the variables for the largest vote split along racial lines and the variable indicating whether or not the election had candidates of more than one race had by far the largest percentages of missing data, missing %`r round(sum(is.na(rp_impute$biggestsplit))/nrow(rp_impute)*100,2)` and  %`r round(sum(is.na(rp_impute$biracial))/nrow(rp_impute)*100,2)` of observations, respectively.
 It is important to note that the variable for the largest vote split along racial lines is the dependent variable in the regresison analysis, and thus, we are missing a large percentage of this key variable.
-From the plot on the right, we can see that approximately 42% of observations are complete (have no missing values).
-There seem to be a correspondence between missing a value for the largest vote split and missing a value for the biracial election indicator.
+From the plot on the right in Figure 1, we can see that approximately 42% of observations are complete (have no missing values).
+There seems to be a correspondence between missing a value for the largest vote split and missing a value for the biracial election indicator.
 There also seem to be about 2% of values for wich most of the variables are missing.
@@
 ```{r rp_aggr_plot, echo = FALSE, fig.cap = "This plot examines the pattern of missing data in the the original racial polarization dataset from Trounstine (2016).
-The plot on the left shows the percentage of missing data for each variable with missing data and reveals that the variables that are missing by far the most data are the largest vote split along racial lines (biggestsplit) and the variable indicating whether or not the election had candidates of more than one race (biracial).
+The plot on the left shows the percentage of missing data for each variable with missing data and reveals that the variables for the largest vote split along racial lines (biggestsplit) and the indicator for whether or not the election had candidates of more than one race (biracial) were missing most frequently.
 The plot on the right shows the pattern of missingness among the variables.
@@
 
-In figure X2, we can similarly observe the trends for the financial segregation dataset.
+In Figure 2, we can similarly observe the trends for the financial segregation dataset.
 In this dataset, there is a very high proportion of missing variables for a number of variables.
-For example, there are `r sum(is.na(fin_imp$H_citytract_NHW_i))` missing values for the segregation index, which is the main independent variable, or %`r round(sum(is.na(fin_imp$H_citytract_NHW_i))/nrow(fin_imp)*100,2)` of the data.
+For example, there are `r format(sum(is.na(fin_imp$H_citytract_NHW_i)), big.mark = ",")` missing values for the segregation index, which is the main independent variable, or %`r round(sum(is.na(fin_imp$H_citytract_NHW_i))/nrow(fin_imp)*100,2)` of the data.
 In this dataset, there are also many more observations for which values are missing for multiple variables in comparison to the racial polarization dataset.
@@
 The plot on the right shows the pattern of missingness among the variables.
-We can see that only .58\\% of observations are complete (have no missing values), and a large majority of the observations are missing data for many variables.", fig.width= 7, fig.height = 5, fig.pos="H"}
+Only .58\\% of observations are complete (have no missing values), and a large majority of the observations are missing data for many variables.", fig.width= 7, fig.height = 5, fig.pos="H"}
 
@@
 
-Because neither dataset seems to exhibit any clear patterns in the missing, data, it makes sense to proceed with the imputation.
-For the racial polarization dataset, I performed multiple imputations with 20 iterations using mice, while for the financial segregation dataset, I performed only 5 iterations due to the large size of the dataset and computing limitaitons.
+Finding no clear patterns in the missingness of the data, I next proceed with the multiple imputations.
+For the racial polarization dataset, I performed multiple imputations with 20 iterations using mice(), while for the financial segregation dataset, I performed only 5 iterations due to the large size of the dataset and computing limitaitons.
 A non-stochastic imputation method, Classification and Regression Trees (CART), was used instead of the default for the imputation for both datasets because of an error with matrix inversion caused by the data that prevented the use of the default method, predictive mean matching.
 For the racial polarization dataset, I included all of the variables used in the analysis associated with the dataset and was able to impute all missing values.
-For the financial segregation dataset, however, I only imputed values for the main independent variable, the segregation index, and a few other variables, although all variables used in the analysis were included in the data subset input into the mice function.
+For the financial segregation dataset, however, I only imputed values for the main independent variable, the segregation index, and a few other variables, although all variables used in the analysis were included in the data subset input into the mice() function to inform the predictions.
 More of the data could not be imputed from the financial segregation dataset due to computing and time constraints for this project given the dataset's large size and high proportion of missing values.

### 2020-05-08 Burzillo_Trounstine_Replication.Rmd
edits to writing

@@
 output: 
-  bookdown::pdf_document2: 
+  pdf_document: 
     fig_caption: true
@@
 
-## make sure to talk about the fact that still a large number of values missing for the imputed variables here
-
 Before examining the results of Trounstine's model using the multiply imputed data, I first ran some diagnostic tests on the imputation results to make sure that everything ran as expected.
@@
 The only cases in which there was some cause for concern were for some of the variables with very few missing values in the racial polarization dataset (such as the indicators for region).
-However, this is more or less to be expected given the small number of imputations performed in these cases.
-Thus, and especially because there are so few of these values missing in the actual datasets, this was not a major concern.
-See figures X and X1 to see the density plots of the imputed values overlayed on the density plots of the original variables.
-The code to generate the rest of the plots and results of the diagnostic tests discussed here are presented in the Appendix.
-
-```{r rp_densityplot, echo = FALSE}
+However, since there are so few of these values missing in the actual datasets, this was not a major concern.
+Figure 3 presents the density plots of the imputed values in red overlaid on the density plots of the original variables in blue.
+The code to generate the rest of the plots and results of the diagnostic tests discussed here are included in the Appendix on GitHub.
+
+```{r rp_densityplot, echo = FALSE, fig.cap = "Figure 3 presents the density plots of the imputed data (red) overlaid on the density plot for the pre-existing data (blue) for all of those variables with missing values in the racial polarization dataset.
+For the most part, the imputed data seem to fit the pre-existing data relatively well.
+The only cases in which there is some cause for concern were for some of the variables with very few missing values in the racial polarization dataset (such as the indicators for region).
+However, since there are so few of these values missing in the actual datasets, this was not a major concern.", fig.pos="H"}
 
@@
       par.settings = my.settings,
-      par.strip.text = list(cex = .7))
+      par.strip.text = list(cex = .6))
 
@@
 Since the results of the diagnostic checks were promising, I next proceeded to re-estimate the original model using the multiply imputed datasets, pooling the results to produce final pooled regression coefficients and parameters.
-The results for the analyses using the racial polarization dataset are presented in tables X1-X3.
+The results of the analysis of the racial polarization dataset using  @trounstine_segregation_2016's first model specification are presented in Tables 1.
 
@@
 ```
-
-The results of the model with the new dataset are slightly different in comparison to the original results from Trounstine (2016).
-With the imputed data, we now have a total of `r nrow(complete(rp_impute))` observations in our model as compared to the original model, which had only 91 observations.
-Interestingly, while the sign of the coefficient on the main variable of interest, the Theil's H segregation index, is the same and the standard error has decreased slightly, the result has become statisically insignificant and the 95% confidence interval contains zero.
-Thus while these results still suggest that segregation may be associated with increased political polarization, they confer a lesser degree of certainty than Trounstine's original analysis.
-The coefficients for % Black population, % Latino population, and median household income have also switched signs, and all coefficients except the indicator for a biracial election are also statistically insignificant, as was the case in the original analysis.
-The coefficient on the indicator for a primary election, has also changed from being significant in the original analysis to insignificant here.
-In general, the standard errors on the coefficients have decreased slightly.
 
@@
   footnote(general = c("This table shows the results of Trounstine's first model for the effect of segregation on political polarization",
-  "(racial vote divide) using the multi-group Theil's H segregation Index using the new, multiply imputed",
+  "(racial vote divide) using the multi-group Theil's H Segregation Index using the new, multiply imputed",
   "datasets. The sign of the coefficient on the main variable of interest, the segregation index, is the same, but",
@@
 
-In the second regression, the results are similar.
-The main coefficient on segregation index has decreased in magnitude, it remains statistically significant.
+The results of the model with the new dataset are slightly different in comparison to the original results from Trounstine (2016).
+With the imputed data, we now have a total of `r nrow(complete(rp_impute))` observations in our model as compared to the original model, which had only 91 observations.
+Interestingly, while the sign of the coefficient on the main variable of interest, the Theil's H segregation index, is the same and the standard error has decreased slightly, the result has become statisically insignificant and the 95% confidence interval contains zero.
+Thus while these results still suggest that segregation may be associated with increased political polarization, they confer a lesser degree of certainty than Trounstine's original analysis.
+The coefficients for % Black population, % Latino population, and median household income have also switched signs, and all coefficients except the indicator for a biracial election are also statistically insignificant, as was the case in the original analysis.
+The coefficient on the indicator for a primary election, has also changed from being significant in the original analysis to insignificant here.
+In general, the standard errors on the coefficients have decreased slightly.
+
+In the second and third model specifications, which use the two-group Theil's H Segregation Index, the results were similar.
+The main coefficient on segregation index decreased in magnitude, although it remained statistically significant.
 The other coefficients except for the biracial indicator are insignificant, and the coefficients on percent Black, percent Latino, and median household income have all switched signs.
-
-In the third regression, like in the second, the main coefficient on segregation index has decreased in magnitude but remains significant.
-The other coefficients except for the biracial indicator are insignificant, and the coefficients on percent Black, percent Asian, median income, and logged population have switched signs.
-In all three of the specifications, standard errors reduced slightly using the larger, multiply imputed datasets compared to the original analysis with the original data in @trounstine_segregation_2016.
+The other coefficients except for the biracial indicator are insignificant, and standard errors have reduced slightly in these specifications compared to the original analysis in Trounstine (2016).
+As a visual comparison of the model coefficients, I include coefficient plots for the diversity and segregation index variables as Figure 4.
+From this plot, it is clear that across all of the models, the coefficient on diversity is positive and insignificant, while the coefficient on the segregaiton index is positive and, in most cases, significant.
 
@@
                 imp_2_rp_sum[2,3], imp_2_rp_sum[3,3],
-                imp_3_rp_sum[2,2], imp_3_rp_sum[3,2],
+                imp_3_rp_sum[2,3], imp_3_rp_sum[3,3],
                 m1_se_seg, m1_se_d,
@@
 
-```{r coef_plot_rp, echo = FALSE}
+```{r coef_plot_rp, echo = FALSE, fig.pos="H"}
 
@@
   geom_errorbar(aes(ymin = estimate - 2 * std_error, ymax = estimate + 2 * std_error, width = .2)) +
-  geom_hline(yintercept = 0, color = "red") +
+  geom_hline(yintercept = 0, color = "black") +
   facet_wrap(~variable) +
-  ggtitle("Coefficient Plots for Diversity and Segregation Indices Across\nthe Racial Polarization Models")+
+  ggtitle("Coefficient Plots for Diversity and Segregation Indices Across the Racial\nPolarization Models")+
   xlab("Model Specifications") +
   ylab("Estimate and 95% Confidence Interval") +
-  labs(caption = "This plot demonstrates how the significance of diversity and segregation in predicting public goods spending varies\n with city size.
-As city populaiton size increases, diversity tends to have less explanatory power for public goods\nspending while segregation has more.
-The opposite is true when considering city population size decreasing:\nsegregation becomes less important as diversity becomes increasingly important.") +
+  labs(caption = "Figure 4: This plot demonstrates how the magnitude and significance of the coefficients on diversity and the segregation\nindex vary among the models.
+Across all of the models, the coefficient on diversity is positive and insignificant.
+The\ncoefficient on the segregation index is also consistently positive across the models.
+In all 3 of the model specifications\nfrom Trounstine (2016) and in 2 of the 3 specifications using the multiply imputed data, the coefficient on the segregation\nindex is significant.") +
   theme_bw()+
@@
   labs(color = "Model Category", shape = "Specification") +
-  scale_color_manual(values= c("orange", "blue"))
-
-```
-
-For the financial segregation dataset, we similarly fit each of our 5 imputed datasets to the original models from @trounstine_segregation_2016 using this data and then pool the results for each.
-The pooled results are presented in tables 4-6.
+  scale_color_manual(values= c("red", "blue"))
+
+```
+
+For the financial segregation dataset, I similarly fit each of our 5 imputed datasets to the original models from @trounstine_segregation_2016 using this data and then pool the results for each.
+As a result of the imputation process, I was able to include an additional `r 73119 - 13742` observations in the analysis, increasing the sample size by %`r round((73119 - 13742)/ 13742*100,0)`.
+While this is an improvement, I was unable to impute all of the missing values because of the large percentage of missing values in the original dataset, which limited the performance of the algorithm, and due to time and computing constraints for this project.
 
@@
 
-As a result of the imputation process, I was able to include an additional XXXXXX observations in the analysis.
-
-The results of the first regression present a stark difference to the results of @trounstine_segregation_2016.
-Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant.
+The results of the first specification of model using the multiply imputed financial segregation data present a stark difference from the results of @trounstine_segregation_2016.
+Crucially, the effect size of the segregation index on public spending has essentially gone to zero and become statistically insignificant.
 Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
 The results of the second and third specifications were similar, with the coefficient on segregation going almost to zero and becoming insignificant on both.
-For brevity, these results are not presented.
+For brevity, the results of the second and third specifications are not presented, but they are available in the Appendix on GitHub.
 
@@
 Referring back to @baqir_public_1999, I decided to divide the orginal sample based upon the populaiton cutoff for cities used in that paper, which determined that the populaiton must be above 25,000 people for an area to be considered a city.
-Splitting the financial segregation dataset into two datasets, one above and one below the 25,000 population cutoff, I then imputed missing values and used the multiply imputed datasets in Trounstine's original models.
-
-Figure XXX displays the populaiton distributions used in each of these analyses.
-The figure makes it clear that the observations included in @trounstine_segregation_2016's original analysis were not representative of the original datasample with the missing values, as most of the cities with lower populations were excluded as a result of the list-wise data deletion.
+Splitting the financial segregation dataset in two, one dataset above and one below the 25,000 population cutoff, I then again imputed missing values for each and used the multiply imputed datasets in Trounstine's original models.
+
+Figure 5 displays the population distributions used in each of these analyses.
+The figure makes it clear that the observations included in @trounstine_segregation_2016's original analysis were not representative of the original data sample with the missing values, as most of the cities with lower populations were excluded as a result of the list-wise data deletion.
 While the dataset generated from the data imputation on the whole sample also has a different distribution for city populaiton, the range of the data seems to be much more representative of the overall data range in comparison to the @trounstine_segregation_2016 sample.
@@
             "fin_dge", "fin_dge",
-            "fin_imp_pop_over_baqir", "fin_imp_pop_over_baqir")
+            "fin_imp_pop_over_baqir", "fin_imp_pop_over_baqir"),
+  color = c("Imputations", "Imputations",
+            "Imputations", "Imputations",
+            "Trounstine (2016)", "Trounstine (2016)",
+            "Imputations", "Imputations")
 )
@@
   ggtitle("Histograms of Log Population of City Observations Included in the\nVarious Regression Analyses") +
-  labs(caption = "This figure makes clear the differences in city size (in terms of population) among the different analyses.\n It is clear that the listwise deletion of observations with missing values resulted in a sample that almost entirely\nconsisted of larger cities in Trounstine (2016).
+  labs(caption = "Figure 5: This figure makes clear the differences in city size (in terms of population) among the different analyses.\n It is clear that the listwise deletion of observations with missing values resulted in a sample that almost entirely\nconsisted of larger cities in Trounstine (2016).
 The distribution of city population in Trounstine (2016)\nmore closely resembles the distribution of the original sample with a greater than 25,000 population\ncutoff imposed than the original sample.
@@
 The results of the models run with the multiply imputed datasets above and below the cutoff are presented in the following two tables.
+In Table 3, the results for cities above the 25,000 person population cutoff are displayed.
+As in @trounstine_segregation_2016, the coefficient on the segregation index is negative and highly significant while the coefficient on diversity is insignificant and the magnitude of the coefficient is close to zero.
+In Table 4, the results for cities below the 25,000 person populaiton cutoff are displayed.
+Here, the coefficient on diversity is positive and significant while the coefficient on the segregation index is much smaller and insignificant.
 
@@
     row_spec(0, bold = TRUE) %>%
-  footnote(general = c("This table shows the results of Trounstine's third model for the effect of segregation on political polarization",
-  "(racial vote divide) using the two-group Theil's H segregation Index and including controls for ideology",
-  "using the new, multiply imputed datasets. Compared to Trounstine's original results, the main coefficient on",
-  "segregation index has decreased in magnitude although, it remains statistically significant. The other",
-  "coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian and",
-  "Black have switched signs. Standard errors have also reduced slightly in these specifications compared to",
-  "the original analysis in Trounstine (2016)."),
-           general_title = "Table 6:") %>%
+  footnote(general = c("Table 3: This table shows the results of Trounstine's model examining the effect of segregation on overall",
+  "per capita direct general expenditure using the multiply imputed dataset for cities with populations above",
+  "25,000 people. As in Trounstine (2016), the effect of segregation on public goods spending is large, negative,",
+  "and significant while the effect of diversity is small in magnitude and insignificant."),
+           general_title = "Table 3:") %>%
   kable_styling(full_width = TRUE)
@@
 kable(imp_under_baqir_1_sum_table_vars, "latex",
-      caption = "\\textbf{Effect of Segregation on Overall per Capita Direct General City Expenditures: Imputed Data for Cities with Populations of 25,000+}",
+      caption = "\\textbf{Effect of Segregation on Overall per Capita Direct General City Expenditures: Imputed Data for Cities with Populations of Less Than 25,000}",
       booktabs = T) %>%
     row_spec(0, bold = TRUE) %>%
-  footnote(general = c("This table shows the results of Trounstine's third model for the effect of segregation on political polarization",
-  "(racial vote divide) using the two-group Theil's H segregation Index and including controls for ideology",
-  "using the new, multiply imputed datasets. Compared to Trounstine's original results, the main coefficient on",
-  "segregation index has decreased in magnitude although, it remains statistically significant. The other",
-  "coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian and",
-  "Black have switched signs. Standard errors have also reduced slightly in these specifications compared to",
-  "the original analysis in Trounstine (2016)."),
-           general_title = "Table 6:") %>%
+  footnote(general = c("Table 4: This table shows the results of Trounstine's model examining the effect of segregation on overal",
+  "per capita direct general expenditure using the multiply imputed dataset for cities with populations below",
+  "25,000 people. As in Trounstine (2016), the effect of segregation on public goods spending is large, negative,",
+  "and significant while the effect of diversity is small in magnitude and insignificant."),
+           general_title = "Table 4:") %>%
   kable_styling(full_width = TRUE)
@@
 
-As a summary of all of the model results for the two main coefficients of interest, segregation index and diversity, a coefficient plot is presented in Figure XXX, with the models ordered by increasing median log population size of the sample on the x-axis.
+As a summary of all of the model results for the two main coefficients of interest, segregation index and diversity, a coefficient plot is presented as Figure XXX, with the models ordered by increasing median log population size of the sample on the x-axis.
 Looking first at the coefficients for diversity, the two models with low median city populaiton size have significant, positive coefficients, while the models with the larger median city populations have insignificant coefficients.
@@
 
+model_summaries <- model_summaries %>%
+  mutate(Model = c("Imputed, < 25k", "Imputed, < 25k", 
+                   "Imputed, Whole Sample", "Imputed, Whole Sample",
+                   "Trounstine (2016)", "Trounstine (2016)",
+                   "Imputed, > 25k", "Imputed, > 25k"))
+
 model_summaries %>%
-  ggplot(aes(x = median, y = estimate)) +
+  ggplot(aes(x = median, y = estimate, color = Model)) +
   geom_point()+
   geom_errorbar(aes(ymin = estimate - 2 * std_error, ymax = estimate + 2 * std_error, width = .2)) +
-  geom_hline(yintercept = 0, color = "red") +
+  geom_hline(yintercept = 0, color = "black") +
   facet_wrap(~variable) +
-  ggtitle("Coefficient Plots for Diversity and White/Non-White Segregation Indices Across\nthe Models")+
+  ggtitle("Coefficient Plots for Diversity and White/Non-White Segregation Indices\nAcross the Models")+
   xlab("Models Ordered by Increasing Median Population Size of the Sample") +
   ylab("Estimate and 95% Confidence Interval") +
-  labs(caption = "This plot demonstrates how the significance of diversity and segregation in predicting public goods spending varies\n with city size.
-As city populaiton size increases, diversity tends to have less explanatory power\nfor public goods spending while segregation has more.
-The opposite is true when considering\ncity population size decreasing: segregation becomes less important as diversity becomes\nincreasingly important.") +
+  labs(caption = "This plot demonstrates how the significance of diversity and segregation in predicting public goods spending varies\nwith city size.
+As city populaiton size increases, diversity tends to have less explanatory power for public goods\nspending while segregation has more.
+The opposite is true when considering city population size decreasing:\nsegregation becomes less important as diversity becomes increasingly important.") +
   theme_bw()+
-  theme(plot.caption = element_text(hjust = 0))
+  theme(plot.caption = element_text(hjust = 0)) +
+  labs(color = "Model Category")
 
@@
 This contradicts previous research which has suggested that levels of diversity were instead most important (see for example @baqir_public_1999 or @hopkins_diversity_2009).
-While @trounstine_segregation_2016 still represents relatively new reasearch as of 2020, it has yet to be fully vetted by additional research.
-Furthermore, some research that has been published on the topic since its publication suggests that other factors such as larger inequities in the political system favoring socially powerful groups [@lee_ethnic_2018] or the interaction of income and racial inequality [@an_its_2018] may be more important in explaining public goods provisions.
-
-I first worked to provide a check on the analysis presented in @trounstine_segregation_2016 by attempting to replicate the work in R.
-I was able to successfully replicate all of the main results from @trounstine_segregation_2016, with the exception of a few of a few marginal analyses of the complex, multi-level models which, to my knowledge, are currently not supported by available R packages.
+
+In this paper, I first worked to provide a check on the analysis presented in @trounstine_segregation_2016 by attempting to replicate the work in R.
+I was able to successfully replicate all of the main results, with the exception of a few of a few marginal analyses of the complex, multi-level models which, to my knowledge, are currently not supported by available R packages.
 I was, however, able to successfully replicate these results in Stata.
 
-As an additional robustness check I also tested the models in @trounstine_segregation_2016 by re-running them with additional data that I imputed from missing values in the original datasets.
-The large number of missing values in both of the datasets used in @trounstine_segregation_2016's main analysis created a concern for potential bias in the original results and a lack of representativeness due to the large amount of data excluded from the regression analysis due to missing values.
-Thus, I used the mice package in R to create multiply imputed datasets, upon which I re-ran the models and pooled the results to generate the final model coefficients and parameters.
+I then tested the models in @trounstine_segregation_2016 by re-running them with additional data that I imputed from missing values in the original datasets.
+The large number of missing values in both of the datasets used in @trounstine_segregation_2016's main analysis created a concern for potential bias in the original results and for a lack of representativeness due to the large proportion of observations excluded from the regression analysis because of missing data.
+Using the mice package in R, I created multiply imputed datasets, upon which I re-ran the models and pooled the results to generate the final model coefficients and parameters.
 
 The results of the data imputation exercise differed between the two datasets.
-For the analyses using the smaller, racial polarization dataset, the results from the imputed data resulted in a smaller magnitude of the coefficient on the main independent variable, and also made it statistically insignificant in the main model specification.
-This suggests that the segregation index may not have as strong of a positive association with political polarization as @trounstine_segregation_2016 suggests.
-Nevertheless, the imputation exercise generally supports the main ideas in this part of Trounstine's analysis.
-
-On the other hand, for the analyses using the much larger financial segregation dataset, the results of the models using the multiply imputed data sharply contrasted the results of @trounstine_segregation_2016, suggesting that diversity, and not segregation, was the best explanatory variable for public goods spending across cities.
+For the analyses using the smaller, racial polarization dataset, re-running the models with the imputed data resulted in a smaller magnitude of the coefficient on the segregation index, and also made it statistically insignificant in the main model specification.
+This suggests that the segregation index may not have as strong of a positive association with political polarization as @trounstine_segregation_2016 suggests, but in general, the imputation exercise supportted the main conclusions of Trounstine's analysis.
+
+On the other hand, for the analyses using the much larger financial segregation dataset, the results of the models using the multiply imputed data sharply contrasted the results of @trounstine_segregation_2016, suggesting that diversity, and not segregation, was the best explanatory variable for public goods spending across all cities.
 While these results originally seemed quite contradictory, I was able reconcile this finding by discovering that the results of @trounstine_segregation_2016 seem to be only really representative of larger cities.
-By dropping all observations in the original data with missing values for key variables, it seems that @trounstine_segregation_2016 inadvertently restricted their sample to almost entirely larger cities (above 25,000 residents) whereas the full sample consisted of cities that had smaller populaitons.
+By dropping all observations in the original data with missing values for variables included in the regressions, it seems that @trounstine_segregation_2016 inadvertently restricted their sample to almost entirely larger cities (above 25,000 residents) whereas the full sample consisted of cities that had smaller populaitons on average.
 To test the hypothesis that diversity is more important for predicting public goods spending for small cities while segregation is more important for predicting public goods spending for larger cities, I divided the original dataset into two subsets based on the city classificaiton criteria used in @baqir_public_1999 that cities must have a population of at least 25,000 people.
@@
 I found that the results presented initial evidence in support of my hypothesis.
-for the cities below the 25,000 person populaiton cutoff, the coefficient for diversity was positive and significant while the coefficient for the segregation index was insignificant.
+For the cities below the 25,000 person population cutoff, the coefficient for diversity was positive and significant while the coefficient for the segregation index was insignificant.
 For cities above the 25,000 person cutoff, the results were very similar to the results found in @trounstine_segregation_2016: the coefficient for diversity was insignificant, but the coefficient for the segregation index was significant and negative.
+
+```{r}
+
+range(fin_seg$population)
+
+quantile(fin_seg$population, c(.25, .5, .75, .80, .90, 1))
+
+median_fin_seg_pop <- median(fin_seg$population)
+
+range(fin_dge$population)
+
+quantile(fin_dge$population, c(.25, .5, .75, .80, .90, 1))
+
+median(fin_dge$population)
+
+```
 
@@
 One potential explanation for this result could be that when cities become too small, the sort of segregation by neighborhood described in @trounstine_segregation_2016 as a diverse city broken down into homogenous, segregated neighborhoods becomes hard to maintain.
-When populaiton sizes are small, segregation may become difficult and inter-racial interactions may become more common, leading diversity to be more indicative of a degree of integration.
-This provides a possible explanation as to why the coefficient on diversity was positive for very small cities, as these "cities" may function more closely as neighborhoods (many of them with populaitons ranging from X-X thousand); as discussed in the literature review, diversity at the neighborhood level is associated with lower levels of political polarization (Oliver 2010) and thus we would expect these areas to have higher levels of public goods spending according to the ideas of @trounstine_segregation_2016.
+When populaiton sizes are small, segregation may become difficult and inter-racial interactions may become more common, leading diversity to be more likely associated with integration and increased inter-racial contact.
+This provides a possible explanation as to why the coefficient on diversity was positive for very small cities, as these "cities" may function more closely as neighborhoods.
+This is plausible given that many of the "cities" in the original financial segregation dataset in @trounstine_segregation_2016 were extremely small, with the overall median city population being `r median_fin_seg_pop`.
+As discussed in the literature review, diversity at the neighborhood level is associated with lower levels of political polarization (Oliver 2010) and thus we would expect these areas to have higher levels of public goods spending according to the logic of @trounstine_segregation_2016.
 As cities become larger and larger, however, comprehensive segregation becomes more attainable.
@@
 
-It is possible that other mechanisms may be more important in explaining differences in spending across cities on public goods.
-For example, it could be that there is an important interaction effect between income and segregation, as others have previously suggested, or there could be some other intervening mechanism or a confounding variable that is leading to the negative association between segregation and lower spending on public goods.
-@trounstine_segregation_2016 has identified an important relationship between segregation and the provision of public goods.
-However, my analysis suggests that further research is needed to assess for which cities this relationship holds.
-At what city size or population density does segregaiton become more relevant than diversity?
+The underprovision of public goods may inhibit social mobility and unfairly disadvantage certain groups.
+@trounstine_segregation_2016 has identified an important relationship between segregation and the provision of public goods, which I suggest holds for larger cities, but not necessarily for smaller ones.
+Given the evidence presented here that the importance of segregation and diversity as predictors of the underprovision of public goods may differ based on city size, further research is needed to assess the nuance of these relationships.
+For example, at what city size or population does segregation become more relevant than diversity?
 And what implications does this have for how public policy should be designed and implemented to address these issues?
-These are important questions that merit further investigation, because by improving our ability to identify, understand, and address its root causes, we may be able to better address the underprovision of public goods, which may inhibit social mobility and unfairly disadvantage certain groups.
+In answering some of these questions, we may be able to improve our ability to identify, understand, and address the root causes of the underprovision of public goods.
 

### 2020-05-08 Burzillo_Trounstine_Replication.Rmd
edits to text

@@
 
-@trounstine_segregation_2016 suggests that high levels of residential segregation are associated with increased political polarization and decreased public spending.
+@trounstine_segregation_2016 suggests that high levels of residential segregation are associated with increased political polarization and decreased public goods spending.
 In this analysis, I was able to successfully replicate @trounstine_segregation_2016’s main results.
@@
 First, she uses election and demographic data from 25 of America’s largest cities between 1990 and 2010 to run a multilevel mixed-effects linear regression with fixed effects for region and year and with random effects for cities in order to show that political polarization increases with segregation.
-Trounstine measures segregation with Theil's H index, which measures the degree to which the diversity of a neighborhood differs from the diversity of the entire city.
-The second main part of Trounstine’s analysis looks at the ability of the Theil’s H segregation index to explain a variety of types of public expenditures by city using a sample of 2,637 cities with 13,742 city-year observations.
+Trounstine measures segregation with Theil's H Index, which measures the degree to which the diversity of a neighborhood differs from the diversity of the entire city.
+The second main part of Trounstine’s analysis looks at the ability of the Theil’s H Segregation Index to explain a variety of types of public expenditures by city using a sample of 2,637 cities with 13,742 city-year observations.
 Using linear regressions with fixed effects for cities and robust standard errors clustered by city, Trounstine finds a significant, negative correlation between segregation and public goods spending that is robust to the inclusion of a variety of relevant controls and an alternative specification in which the number of waterways is used as an instrument for segregation.
@@
 
-One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data, which substantially constrains the sample size used in the regression analysis.
-For example, the regression analysis in the main specification using the the original racial polarization dataset exludes %`r round((obs_rp - 91)/obs_rp * 100, 2)` of the observations, and the regression analysis in the main specification using the original financial segregation data excludes %`r round((obs_fin_seg - 13742)/ obs_fin_seg * 100, 2)` of observations from the original dataset.
+One concern with the original analysis in @trounstine_segregation_2016 is the exclusion of large amounts of missing data, which substantially constrains the sample size in the regression analysis.
+For example, the regression analysis in the main specification using the the original racial polarization dataset exludes %`r round((obs_rp - 91)/obs_rp * 100, 0)` of the observations, and the regression analysis in the main specification using the original financial segregation data excludes %`r round((obs_fin_seg - 13742)/ obs_fin_seg * 100, 0)` of observations.
 As an extension of @trounstine_segregation_2016, I impute missing values in the original data using the mice package in R, which generates multivariate imputations using chained equations [@mice].
@@
 To explore whether or not city size impacted the results, I divided the original sample into two groups, large and small cities, based on the 25,000 population cutoff used to define cities in @baqir_public_1999.
-Performing the data imputation exercise and re-running the models on these subsets revealed that for large cities, segregation was the most powerful explanatory variable for public goods spending, while for small cities, diversity remained the most powerful explanatory variable.
+Performing the data imputation exercise and re-running the models on these subsets revealed that for large cities, segregation was the most powerful explanatory variable for public goods spending and was associated with decreases in public spending, while for small cities, diversity remained the most powerful explanatory variable and was associated with increases in public spending.
 
@@
 Despite some progress made towards racial equity in the U.S.
-on other fronts, residential racial segregation continues to be prevasive and deeply entrenched in society [@fischer_distinguishing_2004; @oliver_paradoxes_2010; @massey_american_1993].
+on other fronts, residential racial segregation continues to be deeply entrenched in American society [@fischer_distinguishing_2004; @oliver_paradoxes_2010; @massey_american_1993].
 Research suggests that this kind of segregation has political consequences, as political cleavages in segregated cities tend to have racial as well as spatial dimensions [@massey_american_1993].
@@
 Studying residential segregation is difficult because its effects tend to differ by geographic level.
-On the neighborhood level, the kind of geographic racial isolation brought on by residential segregation has been associated with racial intolerance, resentment, and competition between racial groups [@oliver_paradoxes_2010].
+On the neighborhood level, the kind of geographic racial isolation brought on by residential segregation and a lack of intra-neighborhood racial diversity has been associated with racial intolerance, resentment, and competition between racial groups [@oliver_paradoxes_2010].
 Living within segregated neighborhoods has also been associated with holding negative stereotypes and perceptions about out groups [@eric_oliver_intergroup_2003].
-As a result, homogeneous neighborhoods have been associated with increased racial tension and political polarization in comparison to integrated, diverse neighborhoods.
-However, at the city or metropolitan level, the opposite seems to be true: when considering larger geographic areas, diversity and integration are correlated with racial tension, competition, prejudice, lower levels of cooperation, and lower spending on public goods [@oliver_paradoxes_2010; @baqir_public_1999; @hopkins_diversity_2009].
-While these differences in the expected effect of segregation on the geographic level may seem confusing at first, they make sense as they suggest that the most severely segregated areas are those that are diverse overall, but have many homogeneous neighborhoods.
+As a result, non-diverese, homogeneous neighborhoods have been associated with increased racial tension and political polarization in comparison to integrated, diverse neighborhoods.
+However, at the city or metropolitan level, the opposite seems to be true: when considering larger geographic areas, diversity is correlated with racial tension, competition, prejudice, lower levels of cooperation, and lower spending on public goods [@oliver_paradoxes_2010; @baqir_public_1999; @hopkins_diversity_2009].
+While these differences in the expected effect of diversity and segregation on the geographic level may seem confusing at first, they make sense as they suggest that the most severely segregated areas are those that are diverse overall, but have many homogeneous neighborhoods.
 Thus, while people of different races co-exist within a highly segregated city, they live separately within their own neighborhoods, which creates an environment ripe for racial tension [@trounstine_segregation_2016].
@@
 
-Political polarization along racial lines may lead to decreased public spending and goods provision because groups may have different preferences, which can make compromise hard, and because groups may preceive a disutility in out-groups receiving public goods expenditure [@baqir_public_1999].
+Political polarization along racial lines may lead to decreased public spending and goods provision because groups may have different preferences, which can make compromise hard, and because groups may preceive a disutility in out-groups' receiving public goods expenditure [@baqir_public_1999].
 @einstein_divided_2012 found evidence that racial segregation predicts large political divisions at the metropolitan level and that these divisions can create a lack of willingness to compromise and collaborate on local policy problems.
 @trounstine_segregation_2016 finds similar results at the city level: that residential racial segregation is associated with both increased political division and decreased public spending.
-Thus, these authors suggest that it is the combination of homogenous neighborhoods within a much larger, diverse geographic area that leads to increased political polarization and reduced public goods spending in local governments.
+Thus, these authors suggest that it is the combination of homogenous neighborhoods within a much larger, diverse geographic area that can lead to increased political polarization and reduced public goods spending in local governments.
 
@@
 @an_its_2018, for example, suggests that the more closely related income inequality is to racial inequality, the less investment is made in public goods, and that this interaction may be a better predictor of public goods spending patterns than measures of diversity.
-Given the active debate in the literature over the relaitonships between diversity, segregation, public goods spending, and other factors, it is increasingly important to re-examine previously reported findings as a means of robustness checks.
+Given the active debate in the literature over the relationships between diversity, segregation, public goods spending, and other factors, it is increasingly important to re-examine previously reported findings as a means of robustness checks.
 
@@
 In this analysis, I was able to successfully replicate all of the main results from Trounstine (2016).
-All regressions and tables were fully replicated in R.
-As an example, in table XXX in the Appendix, I replicate Table 1 from page 713 of @trounstine_segregation_2016, which is also included as Figure XXX for comparison.
-However, I was unable to successfully replicate Trounstine (2016)’s marginal effects analyses and margins plots using R.
-There does not yet appear to be a built-in R function to calculate marginal or predicted effects or to generate margins plots from the complicated multi-level models employed in the original paper, and creating such a function was outside of the scope of this analysis.
+All of the regressions and their results were fully replicated in R.
+As an example, in Table 5, which is presented in the Appendix, I replicate Table 1 from page 713 of @trounstine_segregation_2016, which is also included as Figure 7 for comparison.
+I was unable to successfully replicate Trounstine (2016)’s marginal effects analyses and margins plots using R.
+There does not yet appear to be a built-in R function to calculate marginal or predicted effects or to generate margins plots from the complicated multi-level models employed in the original paper, and creating such functions was outside of the scope of this project.
 Nevertheless, these results were successfully replicated in Stata.
@@
 There was one interesting outcome from my attempt to replicate the original Stata code in R.
-Due to the differences in R and Stata in dealing with missing values, the results of my first replication of the analyses using the financial segregation dataset were slightly different from the results in Stata presented the original paper.
+Due to the differences in R and Stata in dealing with missing values, the results of my first replication of the analyses using the financial segregation dataset were slightly different from the results in Stata presented in the original paper.
 Ultimately, I discovered that this discrepancy was due to differences in R and Stata in dealing with missing values during conditioning.
@@
 In Stata, this does not remove missing values, whereas in R, it does.
-Since this variable is used only as a conditional filter and not as a regression variable (and thus, the observations with missing values for number of census tracts are not dropped when running the regressions), Trounstine’s analysis includes 14 cities and 58 observations with missing values for census tracts in addition to cities with two or more census tracts.
+Since this variable is used only as a conditional filter and not as a regression variable (and thus, the observations with missing values for the number of census tracts are not dropped when running the regressions), Trounstine’s analysis includes 14 cities and 58 observations with missing values for census tracts in addition to cities with two or more census tracts.
 This is a potential oversight on the part of the author, and I would suggest also dropping observations with missing census tract data, or else imputing them given that the aim of her condition was to exclude cities without a sufficient number of census tracts.
-Nevertheless, dropping these values did not have much of an effect on the subsequent results, likely because they represent a small proportion of the overall sample.
+Nevertheless, dropping these values did not have much of an effect on the subsequent results, likely because they represent a very small proportion of the overall sample.
 
@@
 A large amount of data is missing in both of the main datasets used in the analyses of @trounstine_segregation_2016.
-The main model specification using the racial polarization dataset exludes `r (obs_rp - 91)` of the original  `r obs_rp` observations, or  %`r round(100*(obs_rp - 91)/obs_rp,2)` of the data.
-Additionally, the main model specification using the financial segregation data set excludes `r format(obs_fin_seg - 13742, big.mark = ",")` of the original `r format(obs_fin_seg, big.mark = ",")` observations, or %`r round(100*(obs_fin_seg - 13742)/ obs_fin_seg,2)` of observations from the original dataset.
+The main model specification using the racial polarization dataset exludes `r (obs_rp - 91)` of the original  `r obs_rp` observations, or  %`r round(100*(obs_rp - 91)/obs_rp,0)` of the data.
+Additionally, the main model specification using the financial segregation data set excludes `r format(obs_fin_seg - 13742, big.mark = ",")` of the original `r format(obs_fin_seg, big.mark = ",")` observations, or %`r round(100*(obs_fin_seg - 13742)/ obs_fin_seg,0)` of observations from the original dataset.
 
@@
 As a result, multiple imputation helps to account for the uncertainty inherent in the imputation process and allows for the calculation of standard errors around estimators.
-Thus, multiple imputation allows the researcher to more accurately assess the of uncertainty in the analysis in general.
+Thus, multiple imputation allows the researcher to more accurately assess the uncertainty of the analysis in general.
 
 Before performing the multiple imputations on the datasets, I first examined the missing data for patterns.
-To better understand any potential patterns in missing data, I plotted the pattern of missingness and created a histogram showing the frequency of missing values for those variables with missing values in Figure 1 for the racial polarization data and in Figure 2 for the financial segregation data.
-Looking at Figure 1, the histogram shows that the variables for the largest vote split along racial lines and the variable indicating whether or not the election had candidates of more than one race had by far the largest percentages of missing data, missing %`r round(sum(is.na(rp_impute$biggestsplit))/nrow(rp_impute)*100,2)` and  %`r round(sum(is.na(rp_impute$biracial))/nrow(rp_impute)*100,2)` of observations, respectively.
+To better understand any potential patterns in the missing data, I plotted the pattern of missingness and created a histogram showing the frequency of missing values for those variables with missing values in Figure 1 for the racial polarization data and in Figure 2 for the financial segregation data.
+Looking at Figure 1, the histogram shows that the dependent variable in the analysis, which denotes the largest vote split along racial lines, and the variable indicating whether or not the election had candidates of more than one race had by far the largest percentages of missing data, missing %`r round(sum(is.na(rp_impute$biggestsplit))/nrow(rp_impute)*100,0)` and  %`r round(sum(is.na(rp_impute$biracial))/nrow(rp_impute)*100,0)` of observations, respectively.
 It is important to note that the variable for the largest vote split along racial lines is the dependent variable in the regresison analysis, and thus, we are missing a large percentage of this key variable.
@@
 ```{r rp_aggr_plot, echo = FALSE, fig.cap = "This plot examines the pattern of missing data in the the original racial polarization dataset from Trounstine (2016).
-The plot on the left shows the percentage of missing data for each variable with missing data and reveals that the variables for the largest vote split along racial lines (biggestsplit) and the indicator for whether or not the election had candidates of more than one race (biracial) were missing most frequently.
+The plot on the left shows the percentage of missing data for each variable with missing data and reveals that the dependent variable, which denotes the largest vote split along racial lines, and the indicator for whether or not the election had candidates of more than one race were missing most frequently.
 The plot on the right shows the pattern of missingness among the variables.
 We can see that approximately 42\\% of observations are complete (have no missing values).
-There seems to be a correspondence between missing a value for biggest split and missing biracial.
+There seems to be a correspondence between missing a value for biggest split and missing a value for biracial.
 There also seem to be about 2\\% of values for which most of the variables are missing.
@@
 In Figure 2, we can similarly observe the trends for the financial segregation dataset.
-In this dataset, there is a very high proportion of missing variables for a number of variables.
-For example, there are `r format(sum(is.na(fin_imp$H_citytract_NHW_i)), big.mark = ",")` missing values for the segregation index, which is the main independent variable, or %`r round(sum(is.na(fin_imp$H_citytract_NHW_i))/nrow(fin_imp)*100,2)` of the data.
-In this dataset, there are also many more observations for which values are missing for multiple variables in comparison to the racial polarization dataset.
-In total, a mere %`r .0058*100` of observations are complete for all variables included in the main specification for the financial segregaion dataset.
+In this dataset, there is a very high proportion of missing values for most of the variables.
+For example, there are `r format(sum(is.na(fin_imp$H_citytract_NHW_i)), big.mark = ",")` missing values for the segregation index, which is the main independent variable, or %`r round(sum(is.na(fin_imp$H_citytract_NHW_i))/nrow(fin_imp)*100,0)` of the data.
+In this dataset, there are also many more observations for which values are missing for multiple variables in comparison to the racial polarization dataset, as can be seen in the figure on the right in Figure 2.
+In total, a mere %`r .0058*100` of observations are complete for all variables included in the main specification for the financial segregation dataset.
 
@@
 
-Finding no clear patterns in the missingness of the data, I next proceed with the multiple imputations.
-For the racial polarization dataset, I performed multiple imputations with 20 iterations using mice(), while for the financial segregation dataset, I performed only 5 iterations due to the large size of the dataset and computing limitaitons.
-A non-stochastic imputation method, Classification and Regression Trees (CART), was used instead of the default for the imputation for both datasets because of an error with matrix inversion caused by the data that prevented the use of the default method, predictive mean matching.
+Finding no clear patterns in the missingness of the data initially, I proceed with the multiple imputations.
+For the racial polarization dataset, I performed multiple imputations with 20 iterations using mice(), while for the financial segregation dataset, I performed 5 iterations due to the large size of the dataset and computing limitations.
+A non-stochastic imputation method, Classification and Regression Trees (CART), was used instead of the default for the imputation for both datasets because of an error with matrix inversion caused by the data that prevented the use of the default method, Predictive Mean Matching.
 For the racial polarization dataset, I included all of the variables used in the analysis associated with the dataset and was able to impute all missing values.
 For the financial segregation dataset, however, I only imputed values for the main independent variable, the segregation index, and a few other variables, although all variables used in the analysis were included in the data subset input into the mice() function to inform the predictions.
-More of the data could not be imputed from the financial segregation dataset due to computing and time constraints for this project given the dataset's large size and high proportion of missing values.
+For those variables from the financial segregation dataset that I did impute data for, I was not able to impute all of the missing values.
+More of the data could not be imputed because of the very high proportion of missing values, the large size of the dataset in general, and computing and time constraints for this project.
 
@@
 However, since there are so few of these values missing in the actual datasets, this was not a major concern.
-Figure 3 presents the density plots of the imputed values in red overlaid on the density plots of the original variables in blue.
+Figure 3 presents the density plots of the imputed values in red overlaid on the density plots of the original variables in blue for the racial polarization data.
 The code to generate the rest of the plots and results of the diagnostic tests discussed here are included in the Appendix on GitHub.
@@
 Since the results of the diagnostic checks were promising, I next proceeded to re-estimate the original model using the multiply imputed datasets, pooling the results to produce final pooled regression coefficients and parameters.
-The results of the analysis of the racial polarization dataset using  @trounstine_segregation_2016's first model specification are presented in Tables 1.
+The results of the analysis of the racial polarization dataset using  @trounstine_segregation_2016's first model specification are presented in Table 1.
 
@@
 
-```{r results_printing_rp_impute_regressions_1, results = "asis", echo=FALSE}
+```{r results_printing_rp_impute_regressions_1, results = "asis", echo=FALSE, fig.pos="H"}
 
@@
 
-The results of the model with the new dataset are slightly different in comparison to the original results from Trounstine (2016).
-With the imputed data, we now have a total of `r nrow(complete(rp_impute))` observations in our model as compared to the original model, which had only 91 observations.
-Interestingly, while the sign of the coefficient on the main variable of interest, the Theil's H segregation index, is the same and the standard error has decreased slightly, the result has become statisically insignificant and the 95% confidence interval contains zero.
+The results of the model with the new dataset are slightly different compared to the original results from Trounstine (2016).
+With the imputed data, we now have a total of `r nrow(complete(rp_impute))` observations in our model compared to the original model, which had only 91 observations.
+Interestingly, while the sign of the coefficient on the main variable of interest, the Theil's H Segregation Index, is the same and the standard error has decreased slightly, the result has become statisically insignificant and the 95% confidence interval contains zero.
 Thus while these results still suggest that segregation may be associated with increased political polarization, they confer a lesser degree of certainty than Trounstine's original analysis.
-The coefficients for % Black population, % Latino population, and median household income have also switched signs, and all coefficients except the indicator for a biracial election are also statistically insignificant, as was the case in the original analysis.
-The coefficient on the indicator for a primary election, has also changed from being significant in the original analysis to insignificant here.
+All coefficients are statistically insignificant except for the indicator for a biracial election, which remains significant, and  the indicator for a primary election, which has changed from being significant in the original analysis to being insignificant here.
 In general, the standard errors on the coefficients have decreased slightly.

### 2020-05-08 Burzillo_Trounstine_Replication.Rmd
changes to num imputations
edits to formatting, etc.

@@
 link_citations: true
+linestretch: 1.5
 header_includes: 
@@
   \usepackage{multirow}
-  \usepackage{setspace}\doublespacing
-toc: false
 
@@
 In this analysis, I was able to successfully replicate @trounstine_segregation_2016’s main results.
-I then attempted to better deal with the large amounts of missing data in the datasets used in the original analysis by multiply imputing missing values and re-running the original models using the multiply imputed datasets.
+I then attempted to better deal with the large amounts of missing data in the datasets used in the original analysis by multiply imputing missing values and re-running the original models using the resulting multiply imputed datasets.
 My results suggest that segregation is associated with increased racial political polarization, although maybe not as strongly as Trounstine (2016) originally suggested.
@@
 ```
-
+\setlength\parindent{24pt}
 # Introduction
 
-There is a large degree of variation in public goods spending across local governments.
-As a result, many scholars have worked to determine what factors may lead to the underprovision of public goods spending.
+|          There is a large degree of variation in public goods spending across local governments.
+As a result, many scholars have worked to determine what factors may lead to the underprovision of public goods.
 Research in the past has associated racial diversity or changes in levels of diversity with the under-provision of public goods [@baqir_public_1999; @hopkins_diversity_2009].
@@
 
-In this analysis, I first work to replicate the main results of @trounstine_segregation_2016 using R statistical software [@r].
+|          In this analysis, I first work to replicate the main results of @trounstine_segregation_2016 using R statistical software [@r].
 The original data and Stata code made publically available by the author were downloaded via the Harvard Dataverse [@DVN/4LZXTY_2015].
@@
 
-One concern with the original analysis in @trounstine_segregation_2016 is the exclusion of large amounts of missing data, which substantially constrains the sample size in the regression analysis.
-For example, the regression analysis in the main specification using the the original racial polarization dataset exludes %`r round((obs_rp - 91)/obs_rp * 100, 0)` of the observations, and the regression analysis in the main specification using the original financial segregation data excludes %`r round((obs_fin_seg - 13742)/ obs_fin_seg * 100, 0)` of observations.
+|          One concern with the original analysis in @trounstine_segregation_2016 is the exclusion of large amounts of missing data, which substantially constrains the sample size in the regression analysis.
+For example, the regression analysis in the main specification using the the original racial polarization dataset exludes %`r round((obs_rp - 91)/obs_rp * 100, 0)` of the observations, and the regression analysis in the main specification using the original financial segregation dataset excludes %`r round((obs_fin_seg - 13742)/ obs_fin_seg * 100, 0)` of observations.
 As an extension of @trounstine_segregation_2016, I impute missing values in the original data using the mice package in R, which generates multivariate imputations using chained equations [@mice].
@@
 
-Comparing the results of the original regressions and those done with the imputed data yields similar big picture results for the analyses concerning the relationship between political polarization and segregation.
+|          Comparing the results of the original regressions and those done with the imputed data yields similar big picture results for the analyses concerning the relationship between political polarization and segregation.
 Like in @trounstine_segregation_2016, I find that segregation is positively associated with political polarization; however, the magnitude and significance of the effect has diminsihed slightly.
 For the second set of analyses conducted with the financial segregation data, my initial results for running the models with the imputed data differ significantly from @trounstine_segregation_2016, suggesting that diversity, not segregation, is the more robust explanatory factor in patterns of public goods spending across cities.
-Nevertheless, this is likely because the data imputation exercise led to the inclusion of a much larger percentage of small cities in the sample, which were perhaps inadvertently largely excluded in @trounstine_segregation_2016 due to the list-wise deletion of observations with missing values, which were more frequently found in small cities.
+Nevertheless, this is likely because the data imputation exercise led to the inclusion of a much larger percentage of small cities in the sample, which were perhaps inadvertently largely excluded in @trounstine_segregation_2016 due to the list-wise deletion of observations with missing values, which were more frequently found in the observations of small cities.
 To explore whether or not city size impacted the results, I divided the original sample into two groups, large and small cities, based on the 25,000 population cutoff used to define cities in @baqir_public_1999.
@@
 
-Despite some progress made towards racial equity in the U.S.
+|          Despite some progress made towards racial equity in the U.S.
 on other fronts, residential racial segregation continues to be deeply entrenched in American society [@fischer_distinguishing_2004; @oliver_paradoxes_2010; @massey_american_1993].
@@
 Neighborhoods are often important actors within local politics because local governments provide many functions that are allocational in nature and concern geographical space [@trounstine_segregation_2016].
-Thus, when local areas are composed of neighborhoods that are divided on racial lines as well as spacial lines, it is natural to expect higher degrees of racial polarization as a result.
-
-Studying residential segregation is difficult because its effects tend to differ by geographic level.
-On the neighborhood level, the kind of geographic racial isolation brought on by residential segregation and a lack of intra-neighborhood racial diversity has been associated with racial intolerance, resentment, and competition between racial groups [@oliver_paradoxes_2010].
-Living within segregated neighborhoods has also been associated with holding negative stereotypes and perceptions about out groups [@eric_oliver_intergroup_2003].
+Thus, when local areas are composed of competing neighborhoods that are divided on racial lines as well as spacial lines, it is natural to expect higher degrees of racial polarization as a result.
+
+|          In order to understand what segregation is and why it is important as a political concept, it is critical to understand the literature on the effects of diversity at various geographic levels.
+Studying diversity can be somewhat difficult and confusing because its effects tend to differ by geographic level.
+On the neighborhood level, a lack of intra-neighborhood racial diversity has been associated with racial intolerance, resentment, and competition between racial groups [@oliver_paradoxes_2010].
+Living within non-diverse or segregated neighborhoods has also been associated with holding negative stereotypes and perceptions about out groups [@eric_oliver_intergroup_2003].
 As a result, non-diverese, homogeneous neighborhoods have been associated with increased racial tension and political polarization in comparison to integrated, diverse neighborhoods.
-However, at the city or metropolitan level, the opposite seems to be true: when considering larger geographic areas, diversity is correlated with racial tension, competition, prejudice, lower levels of cooperation, and lower spending on public goods [@oliver_paradoxes_2010; @baqir_public_1999; @hopkins_diversity_2009].
-While these differences in the expected effect of diversity and segregation on the geographic level may seem confusing at first, they make sense as they suggest that the most severely segregated areas are those that are diverse overall, but have many homogeneous neighborhoods.
-Thus, while people of different races co-exist within a highly segregated city, they live separately within their own neighborhoods, which creates an environment ripe for racial tension [@trounstine_segregation_2016].
-It is thus not simply the levels of diversity or integration that matter for racial harmony and cooperation, but their patterns within a larger geographic framework [@trounstine_segregation_2016; @oliver_paradoxes_2010; @bharathi_public_2018].
-
-Political polarization along racial lines may lead to decreased public spending and goods provision because groups may have different preferences, which can make compromise hard, and because groups may preceive a disutility in out-groups' receiving public goods expenditure [@baqir_public_1999].
+However, at the city or metropolitan level, the opposite seems to be true: when considering larger geographic areas, diversity, not homogeneity, is correlated with racial tension, competition, prejudice, lower levels of cooperation, and lower spending on public goods [@oliver_paradoxes_2010; @baqir_public_1999; @hopkins_diversity_2009].
+As a result, these theories predict that geographic areas most ripe for racial tension and competition will be those that are diverse overall, but have many homogeneous, non-diverse neighborhoods, meaning that while people of different races co-exist within a larger metropolitan area, they live separately within their own neighborhoods.
+This situation corresponds to @trounstine_segregation_2016's definition of a severely segregated city.
+The differing effects of diversity at the neighborhood versus the larger geographic level provide an argument for considering segregation as opposed to simply diversity in local politics because measures of segregation (such as the Theils's H Index used by @trounstine_segregation_2016) take into account the patterns of racial mixing at both the neighborhood and larger geographic level that, alltogether, are important in predicting whether a locality will be characterized by interracial cooperation or political polarization [@trounstine_segregation_2016; @oliver_paradoxes_2010; @bharathi_public_2018].
+
+|          Political polarization along racial lines may lead to decreased public spending and goods provision because groups may have different preferences, which can make compromise hard, and because groups may preceive a disutility in out-groups' receiving public goods expenditure [@baqir_public_1999].
 @einstein_divided_2012 found evidence that racial segregation predicts large political divisions at the metropolitan level and that these divisions can create a lack of willingness to compromise and collaborate on local policy problems.
@@
 
-More recently, some scholars have called this hypothesis and its importance into question.
+|          More recently, some scholars have called this hypothesis and its importance into question.
 For example, @lee_ethnic_2018 finds evidence that larger inequalities within the political system favoring socially powerful groups, not local diversity patterns leading to decreased cooperation, may be a better explanation of failures in public goods provision in diverse areas.
@@
 
-In this analysis, I was able to successfully replicate all of the main results from Trounstine (2016).
-All of the regressions and their results were fully replicated in R.
+|          In this analysis, I was able to successfully replicate all of the main results from Trounstine (2016).
+The regression analysis was fully replicated in R.
 As an example, in Table 5, which is presented in the Appendix, I replicate Table 1 from page 713 of @trounstine_segregation_2016, which is also included as Figure 7 for comparison.
 I was unable to successfully replicate Trounstine (2016)’s marginal effects analyses and margins plots using R.
-There does not yet appear to be a built-in R function to calculate marginal or predicted effects or to generate margins plots from the complicated multi-level models employed in the original paper, and creating such functions was outside of the scope of this project.
+There does not yet appear to be a publically available R package or function to calculate marginal or predicted effects or to generate margins plots from the complicated multi-level models employed in the original paper, and creating such functions was outside of the scope of this project.
 Nevertheless, these results were successfully replicated in Stata.
 
-There was one interesting outcome from my attempt to replicate the original Stata code in R.
+|          There was one interesting outcome from my attempt to replicate the original Stata code in R.
 Due to the differences in R and Stata in dealing with missing values, the results of my first replication of the analyses using the financial segregation dataset were slightly different from the results in Stata presented in the original paper.
@@
 This is a potential oversight on the part of the author, and I would suggest also dropping observations with missing census tract data, or else imputing them given that the aim of her condition was to exclude cities without a sufficient number of census tracts.
-Nevertheless, dropping these values did not have much of an effect on the subsequent results, likely because they represent a very small proportion of the overall sample.
+Nevertheless, when I tried dropping these values from the analysis as a robustness check, I found that the change in the sample led to negligible differences in the results, likely because these observations represent a very small proportion of the overall sample.
 
@@
 
-One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data values in the original datasets.
-Because both R and Stata by default drop any observations with missing values for any of the variables used in a regression, this can exlcude a large portion of the data from the analysis and potentially bias the results if the data is not missing completely at random.
+|          One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data values in the original datasets.
+In general, because both R and Stata by default drop any observations with missing values for any of the variables used in a regression, the existence of missing values can lead to the exlcusion of a large portion of the data from the analysis and potentially bias the results if the data is not missing completely at random.
 A large amount of data is missing in both of the main datasets used in the analyses of @trounstine_segregation_2016.
 The main model specification using the racial polarization dataset exludes `r (obs_rp - 91)` of the original  `r obs_rp` observations, or  %`r round(100*(obs_rp - 91)/obs_rp,0)` of the data.
-Additionally, the main model specification using the financial segregation data set excludes `r format(obs_fin_seg - 13742, big.mark = ",")` of the original `r format(obs_fin_seg, big.mark = ",")` observations, or %`r round(100*(obs_fin_seg - 13742)/ obs_fin_seg,0)` of observations from the original dataset.
-
-In an attempt to better deal with the problem of missing data in @trounstine_segregation_2016, I impute missing values in the original data using the mice package in R, which generates multivariate imputations using chained equations [@mice].
+Additionally, the main model specification using the financial segregation dataset excludes `r format(obs_fin_seg - 13742, big.mark = ",")` of the original `r format(obs_fin_seg, big.mark = ",")` observations, or %`r round(100*(obs_fin_seg - 13742)/ obs_fin_seg,0)` of observations from the original dataset.
+
+|          In an attempt to better deal with the problem of missing data in @trounstine_segregation_2016, I impute missing values in the original data using the mice package in R, which generates multivariate imputations using chained equations [@mice].
 While there are a variety of different imputation methods that could have been employed, multiple imputation (such as the multiple multivariate imputations generated by mice) is desirable because instead of inputting a single value such as the mean for missing values, it instead uses the distribution of the available data to estimate multiple potential values for the missing data.
@@
 
-Before performing the multiple imputations on the datasets, I first examined the missing data for patterns.
+|          Before performing the multiple imputations on the datasets, I first examined the missing data for patterns.
 To better understand any potential patterns in the missing data, I plotted the pattern of missingness and created a histogram showing the frequency of missing values for those variables with missing values in Figure 1 for the racial polarization data and in Figure 2 for the financial segregation data.
 Looking at Figure 1, the histogram shows that the dependent variable in the analysis, which denotes the largest vote split along racial lines, and the variable indicating whether or not the election had candidates of more than one race had by far the largest percentages of missing data, missing %`r round(sum(is.na(rp_impute$biggestsplit))/nrow(rp_impute)*100,0)` and  %`r round(sum(is.na(rp_impute$biracial))/nrow(rp_impute)*100,0)` of observations, respectively.
-It is important to note that the variable for the largest vote split along racial lines is the dependent variable in the regresison analysis, and thus, we are missing a large percentage of this key variable.
-From the plot on the right in Figure 1, we can see that approximately 42% of observations are complete (have no missing values).
+From the plot on the right in Figure 1, we can see that approximately 42% of observations are complete, meaning they have no missing values.
 There seems to be a correspondence between missing a value for the largest vote split and missing a value for the biracial election indicator.
-There also seem to be about 2% of values for wich most of the variables are missing.
+There also seem to be about 2% of values for which most of the variables are missing.
 However, most observations are not missing more than 2-3 values.
@@
 
-In Figure 2, we can similarly observe the trends for the financial segregation dataset.
+|          In Figure 2, we can similarly observe the trends for the financial segregation dataset.
 In this dataset, there is a very high proportion of missing values for most of the variables.
@@
 
-Finding no clear patterns in the missingness of the data initially, I proceed with the multiple imputations.
+|          Finding no clear patterns in the missingness of the data initially, I proceeded with the multiple imputations.
 For the racial polarization dataset, I performed multiple imputations with 20 iterations using mice(), while for the financial segregation dataset, I performed 5 iterations due to the large size of the dataset and computing limitations.
@@
 For the racial polarization dataset, I included all of the variables used in the analysis associated with the dataset and was able to impute all missing values.
-For the financial segregation dataset, however, I only imputed values for the main independent variable, the segregation index, and a few other variables, although all variables used in the analysis were included in the data subset input into the mice() function to inform the predictions.
-For those variables from the financial segregation dataset that I did impute data for, I was not able to impute all of the missing values.
+For the financial segregation dataset, however, I only imputed values for the main independent variable, the segregation index, and a few other variables, although all variables used in the regression analysis were included in the data subset input into the mice() function to inform the predictions.
+For those variables from the financial segregation dataset for which I did impute data, I was not able to impute all of the missing values.
 More of the data could not be imputed because of the very high proportion of missing values, the large size of the dataset in general, and computing and time constraints for this project.
@@
 
-imp_1_rp <- mice(rp_impute, method = "cart", maxit = 20)
+imp_1_rp <- mice(rp_impute, method = "cart", maxit = 5)
 
@@
 
-Before examining the results of Trounstine's model using the multiply imputed data, I first ran some diagnostic tests on the imputation results to make sure that everything ran as expected.
+|          Before examining the results of Trounstine's model using the multiply imputed data, I first ran some diagnostic tests on the imputation results to make sure that everything ran as expected.
 First, I checked the convergence of the algorithm used within mice() by plotting the trace lines as a function of the number of iterations for each of the variables.
@@
 All of these checks suggested that the imputed values were within a plausible range of the data and that their distribution fit the underlying distribution of the data relatively well.
-The only cases in which there was some cause for concern were for some of the variables with very few missing values in the racial polarization dataset (such as the indicators for region).
-However, since there are so few of these values missing in the actual datasets, this was not a major concern.
+The only cases in which there was some cause for concern were for some of the variables with very few missing values in the racial polarization dataset, such as the indicators for region.
+However, since there are so few of these values missing in the actual dataset, this was not a major concern.
 Figure 3 presents the density plots of the imputed values in red overlaid on the density plots of the original variables in blue for the racial polarization data.
@@
 
-```{r rp_densityplot, echo = FALSE, fig.cap = "Figure 3 presents the density plots of the imputed data (red) overlaid on the density plot for the pre-existing data (blue) for all of those variables with missing values in the racial polarization dataset.
+```{r rp_densityplot, echo = FALSE, fig.cap = "Figure 3 presents the density plots of the imputed data (red) overlaid on the density plot for the pre-existing data (blue) for all those variables with missing values in the racial polarization dataset.
 For the most part, the imputed data seem to fit the pre-existing data relatively well.
@@
       par.settings = my.settings,
-      par.strip.text = list(cex = .6))
-
-```
-
-Since the results of the diagnostic checks were promising, I next proceeded to re-estimate the original model using the multiply imputed datasets, pooling the results to produce final pooled regression coefficients and parameters.
+      par.strip.text = list(cex = .5))
+
+```
+
+|          Since the results of the diagnostic checks were promising, I next proceeded to re-estimate the original model using the multiply imputed datasets, pooling the results to produce final pooled regression coefficients and parameters.
 The results of the analysis of the racial polarization dataset using  @trounstine_segregation_2016's first model specification are presented in Table 1.
+The results of the model with the new dataset are slightly different compared to the original results from Trounstine (2016).
+With the imputed data, we now have a total of `r nrow(complete(rp_impute))` observations in our model compared to the original model, which had only 91 observations.
+Interestingly, while the sign of the coefficient on the main variable of interest, the Theil's H Segregation Index, is the same and the standard error has decreased slightly, the result has become statisically insignificant and the 95% confidence interval contains zero.
+Thus while these results still suggest that segregation may be associated with increased political polarization, they confer a lesser degree of certainty than Trounstine's original analysis.
+All coefficients are statistically insignificant except for the indicator for a biracial election, which remains significant, and  the indicator for a primary election, which has changed from being significant in the original analysis to being insignificant here.
+In general, the standard errors on the coefficients have decreased slightly.
 
@@
 
-kable(imp_1_rp_sum_table_vars, "latex", caption = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Multigroup Segregation Index}", booktabs = T) %>%
+kable(imp_1_rp_sum_table_vars, 
+      "latex", 
+      caption = "\\textbf{Racial Polarization in Segregated Cities using the Multiply Imputed Data: Racial Divide with Multigroup Segregation Index}",
+      align = c("l","c","c","c"),
+      booktabs = T) %>%
   row_spec(0, bold = TRUE) %>%
-  footnote(general = c("This table shows the results of Trounstine's first model for the effect of segregation on political polarization",
-  "(racial vote divide) using the multi-group Theil's H Segregation Index using the new, multiply imputed",
-  "datasets. The sign of the coefficient on the main variable of interest, the segregation index, is the same, but",
-  "the result has become statisically insignificant with the 95% confidence interval containing zero. Thus",
-  "while these results still suggest that segregation may be associated with increased political polarization,",
-  "they confer a lesser degree of certainty than Trounstine's original analysis. The coefficients for % Black",
-  "population, % Latino population, and median household income have also switched signs. The coefficient",
-  "on the indicator for a primary election, has also changed from being significant in the original analysis",
-  "to insignificant here. In general, the standard errors on the coefficients have decreased slightly."),
-           general_title = "Table 1:")%>%
-  kable_styling(full_width = TRUE)
-
-```
-
-The results of the model with the new dataset are slightly different compared to the original results from Trounstine (2016).
-With the imputed data, we now have a total of `r nrow(complete(rp_impute))` observations in our model compared to the original model, which had only 91 observations.
-Interestingly, while the sign of the coefficient on the main variable of interest, the Theil's H Segregation Index, is the same and the standard error has decreased slightly, the result has become statisically insignificant and the 95% confidence interval contains zero.
-Thus while these results still suggest that segregation may be associated with increased political polarization, they confer a lesser degree of certainty than Trounstine's original analysis.
-All coefficients are statistically insignificant except for the indicator for a biracial election, which remains significant, and  the indicator for a primary election, which has changed from being significant in the original analysis to being insignificant here.
-In general, the standard errors on the coefficients have decreased slightly.
-
-In the second and third model specifications, which use the two-group Theil's H Segregation Index, the results were similar.
+  footnote(symbol = c("N = 203"),
+    general = c("This table shows the results of Trounstine's first model for the effect of segregation on political polarization",
+  "using the multi-group Theil's H Segregation Index using the new, multiply imputed datasets. The",
+  "sign of the coefficient on the main variable of interest, the segregation index, is positive as in",
+  "Trounstine (2016), but the result has become statisically insignificant with the 95% confidence",
+  "interval containing zero. Thus while these results still suggest that segregation may be",
+  "associated with increased political polarization, they confer a lesser degree of certainty than",
+  "Trounstine's original analysis. In general, the standard errors on the coefficients have",
+  "decreased slightly."),
+           general_title = "Table 1:",
+  footnote_order = c("symbol", "general"))%>%
+  kable_styling(full_width = TRUE, latex_options = "hold_position")
+
+```
+
+|          In the second and third model specifications, which use the two-group Theil's H Segregation Index, the results were similar.
 The main coefficient on segregation index decreased in magnitude, although it remained statistically significant.
-The other coefficients except for the biracial indicator are insignificant, and the coefficients on percent Black, percent Latino, and median household income have all switched signs.
 The other coefficients except for the biracial indicator are insignificant, and standard errors have reduced slightly in these specifications compared to the original analysis in Trounstine (2016).
@@
   ylab("Estimate and 95% Confidence Interval") +
-  labs(caption = "Figure 4: This plot demonstrates how the magnitude and significance of the coefficients on diversity and the segregation\nindex vary among the models.
-Across all of the models, the coefficient on diversity is positive and insignificant.
-The\ncoefficient on the segregation index is also consistently positive across the models.
-In all 3 of the model specifications\nfrom Trounstine (2016) and in 2 of the 3 specifications using the multiply imputed data, the coefficient on the segregation\nindex is significant.") +
+  labs(caption = "Figure 4: This plot demonstrates how the magnitude and significance of the coefficients on diversity and\nthe segregation index vary among the models.
+Across all of the models, the coefficient on diversity is\npositive and insignificant.
+The coefficient on the segregation index is also consistently positive.
+In all 3\nof the model specifications from Trounstine (2016) and in 2 of the 3 specifications using the multiply\nimputed data, the coefficient on the segregation index is significant.") +
   theme_bw()+
@@
 
-For the financial segregation dataset, I similarly fit each of our 5 imputed datasets to the original models from @trounstine_segregation_2016 using this data and then pool the results for each.
-As a result of the imputation process, I was able to include an additional `r 73119 - 13742` observations in the analysis, increasing the sample size by %`r round((73119 - 13742)/ 13742*100,0)`.
+|          For the financial segregation dataset, I similarly fit each of our 5 imputed datasets to the original models from @trounstine_segregation_2016 using this data and then pooled the results for each.
+As a result of the imputation process, I was able to include an additional `r format(73119 - 13742, big.mark = ",")` observations in the analysis, increasing the sample size by %`r round((73119 - 13742)/ 13742*100,0)`.
 While this is an improvement, I was unable to impute all of the missing values because of the large percentage of missing values in the original dataset, which limited the performance of the algorithm, and due to time and computing constraints for this project.
@@
 
-```
-
-The results of the first specification of model using the multiply imputed financial segregation data present a stark difference from the results of @trounstine_segregation_2016.
+# calculate number of observations used in the main specification
+complete_fs <- complete(imp_fs,1) %>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+rows_complete_fs <- nrow(complete_fs)
+```
+
+|          The results of the first specification of model using the multiply imputed financial segregation data present a stark difference from the results of @trounstine_segregation_2016.
 Crucially, the effect size of the segregation index on public spending has essentially gone to zero and become statistically insignificant.
-Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
+Interestingly, the coefficient on the diversity variable has increased substantially from .106 to `r round(imp_felm1_sum[2,2], 3)` and has become statistically significant.
 The results of the second and third specifications were similar, with the coefficient on segregation going almost to zero and becoming insignificant on both.
@@
 
-kable(imp_felm1_sum_table_vars, "latex",
+kable(imp_felm1_sum_table_vars, 
+      "latex",
       caption = "\\textbf{Effect of Segregation on Overall per Capita Direct General City Expenditures: Imputed Data for all Cities}",
+      align = c("l","c","c","c"),
       booktabs = T) %>%
     row_spec(0, bold = TRUE) %>%
-  footnote(general = c("This table shows the results of Trounstine's first model for the effect of segregation on per capita direct",
+  footnote(symbol = c("N = 73,119"),
+    general = c("This table shows the results of Trounstine's first model for the effect of segregation on per capita direct",
   "public expenditure using the two-group Theil's H Segregation Index using the new, multiply imputed datasets.",
   "The results present a stark contrast to Trounstine's original results: the main coefficient on segregation index",
-  "has decreased to essentially zero and has become statistically insignificant. The very large P-Value may indicate",
-  "there is a larger difference between the two models. The coefficient on diversity has increased in magnitude and",
-  "become statistically significant."),
+  "has decreased to essentially zero and has become statistically insignificant.  The coefficient on diversity has",
+  "increased in magnitude and become statistically significant."),
+  footnote_order = c("symbol", "general"),
            general_title = "Table 4:") %>%
-  kable_styling(full_width = TRUE)
-
-```
-
-Because these results differed to such a degree from @trounstine_segregation_2016's original findings, I performed some checks on the data included in each analysis.
+  kable_styling(full_width = TRUE, latex_options = "hold_position")
+
+```
+
+|          Because these results differed to such a degree from @trounstine_segregation_2016's original findings, I performed some checks on the data included in each analysis.
 I discovered that @trounstine_segregation_2016 excluded most cities below a certain population size because of the nature of the paper's listwise deletion.
@@
 
-Figure 5 displays the population distributions used in each of these analyses.
+|          Figure 5 displays the population distributions used in each of these analyses.
 The figure makes it clear that the observations included in @trounstine_segregation_2016's original analysis were not representative of the original data sample with the missing values, as most of the cities with lower populations were excluded as a result of the list-wise data deletion.
@@
 
-imp_fs_pop_overbaqir <- mice(fin_imp_pop_over_baqir, method = meth, maxit = 5)
+imp_fs_pop_overbaqir <- mice(fin_imp_pop_over_baqir, method = meth, maxit = 1)
 
@@
 imp_over_baqir_1_sum <- summary(pool_fit_over_baqir_1)
+
+# calculate the number of observations used in the regression
+
+complete_over_baqir <- complete(imp_fs_pop_overbaqir, 1)%>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+n_complete_over_baqir <- nrow(complete_over_baqir)
 
@@
 imp_under_baqir_1_sum <- summary(pool_fit_under_baqir_1)
+
+# calculate number of observations in regression
+
+complete_under_baqir <- complete(imp_fs_pop_under_baqir, 1)%>%
+  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
+         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
+         !(is.na(pctlatinopopinterp)),
+         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
+         !(is.na(pctrentersinterp)),
+         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
+         !(is.na(logpop)), dgepercap_cpi != 0)
+
+n_complete_under_baqir <- nrow(complete_under_baqir)
 
@@
 
-```{r dataset_rows_in_analysis, include = FALSE}
-
-complete_fs <- complete(imp_fs,1) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
-         !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
-         !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
-         !(is.na(logpop)), dgepercap_cpi != 0)
-
-complete_over_baqir <- complete(imp_fs_pop_overbaqir, 1)%>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
-         !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
-         !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
-         !(is.na(logpop)), dgepercap_cpi != 0)
-
-complete_under_baqir <- complete(imp_fs_pop_under_baqir, 1)%>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
-         !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
-         !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
-         !(is.na(logpop)), dgepercap_cpi != 0)
-
-```
-
 ```{r dataset_medians, include = FALSE}
@@
   ggplot() +
-  geom_histogram(aes(x = log_pop, fill = Analysis)) +
+  geom_histogram(aes(x = log_pop, fill = Analysis), binwidth = .5) +
   geom_vline(aes(xintercept = median_log_pop), color = "red") +
@@
   ggtitle("Histograms of Log Population of City Observations Included in the\nVarious Regression Analyses") +
-  labs(caption = "Figure 5: This figure makes clear the differences in city size (in terms of population) among the different analyses.\n It is clear that the listwise deletion of observations with missing values resulted in a sample that almost entirely\nconsisted of larger cities in Trounstine (2016).
-The distribution of city population in Trounstine (2016)\nmore closely resembles the distribution of the original sample with a greater than 25,000 population\ncutoff imposed than the original sample.
-The red lines indicate the median log population in each sample.") +
+  labs(caption = "Figure 5: This figure makes clear the differences in city size (in terms of population) among the different\nanalyses.
+It is clear that the listwise deletion of observations with missing values resulted in a sample\nthat almost entirely consisted of larger cities in Trounstine (2016).
+The distribution of city population\nin Trounstine (2016) more closely resembles the distribution of the original sample with a greater than\n25,000 population cutoff imposed than the original sample.
+The red lines indicate the median log\npopulation in each sample.") +
   ylab("Count") +
@@
   theme(plot.caption = element_text(hjust = 0),
-        strip.text.x = element_text(size = 8))
-
-```
-
-The results of the models run with the multiply imputed datasets above and below the cutoff are presented in the following two tables.
+        strip.text.x = element_text(size = 7))
+
+```
+
+|          The results of the models run with the multiply imputed datasets above and below the cutoff are presented in the following two tables.
 In Table 3, the results for cities above the 25,000 person population cutoff are displayed.
@@
 
-kable(imp_over_baqir_1_sum_table_vars, "latex",
+kable(imp_over_baqir_1_sum_table_vars,
+      "latex",
       caption = "\\textbf{Effect of Segregation on Overall per Capita Direct General City Expenditures: Imputed Data for Cities with Populations of 25,000+}",
+      align = c("l","c","c","c"),
       booktabs = T) %>%
     row_spec(0, bold = TRUE) %>%
-  footnote(general = c("Table 3: This table shows the results of Trounstine's model examining the effect of segregation on overall",
+  footnote(symbol = c("N = 6716"),
+    general = c("This table shows the results of Trounstine's model examining the effect of segregation on overall",
   "per capita direct general expenditure using the multiply imputed dataset for cities with populations above",
@@
   "and significant while the effect of diversity is small in magnitude and insignificant."),
+  footnote_order = c("symbol", "general"), 
            general_title = "Table 3:") %>%
-  kable_styling(full_width = TRUE)
+  kable_styling(full_width = TRUE, latex_options = "hold_position")
 
@@
 
-kable(imp_under_baqir_1_sum_table_vars, "latex",
+kable(imp_under_baqir_1_sum_table_vars, 
+      "latex",
       caption = "\\textbf{Effect of Segregation on Overall per Capita Direct General City Expenditures: Imputed Data for Cities with Populations of Less Than 25,000}",
+      align = c("l","c","c","c"),
       booktabs = T) %>%
     row_spec(0, bold = TRUE) %>%
-  footnote(general = c("Table 4: This table shows the results of Trounstine's model examining the effect of segregation on overal",
+  footnote(symbol = c("N = 66,403"),
+    general = c("This table shows the results of Trounstine's model examining the effect of segregation on overal",
   "per capita direct general expenditure using the multiply imputed dataset for cities with populations below",
-  "25,000 people. As in Trounstine (2016), the effect of segregation on public goods spending is large, negative,",
-  "and significant while the effect of diversity is small in magnitude and insignificant."),
+  "25,000 people. In contrast to Trounstine (2016) and the results of our analysis with the imputed datasets for",
+  "cities over 25,000 people, the effect of segregation on public goods spending is negligible and insignificant,",
+  "while the effect of diversity is large, positive, and significant."),
+  footnote_order = c("symbol", "general"),
            general_title = "Table 4:") %>%
-  kable_styling(full_width = TRUE)
-
-```
-
-As a summary of all of the model results for the two main coefficients of interest, segregation index and diversity, a coefficient plot is presented as Figure XXX, with the models ordered by increasing median log population size of the sample on the x-axis.
+  kable_styling(full_width = TRUE, latex_options = "hold_position")
+
+```
+
+|          As a summary of all of the model results for the two main coefficients of interest, segregation index and diversity, a coefficient plot is presented as Figure XXX, with the models ordered by increasing median log population size of the sample on the x-axis.
 Looking first at the coefficients for diversity, the two models with low median city populaiton size have significant, positive coefficients, while the models with the larger median city populations have insignificant coefficients.
@@
   ylab("Estimate and 95% Confidence Interval") +
-  labs(caption = "This plot demonstrates how the significance of diversity and segregation in predicting public goods spending varies\nwith city size.
-As city populaiton size increases, diversity tends to have less explanatory power for public goods\nspending while segregation has more.
-The opposite is true when considering city population size decreasing:\nsegregation becomes less important as diversity becomes increasingly important.") +
+  labs(caption = "This plot demonstrates how the significance of diversity and segregation in predicting public goods spending\nvaries with city size.
+As city populaiton size increases, diversity tends to have less explanatory power for\npublic goods spending while segregation has more.
+The opposite is true when considering city population\nsize decreasing: segregation becomes less important as diversity becomes increasingly important.") +
   theme_bw()+
@@
 
-Why cities differ in their amount of spending on public goods is an interesting question that is frequently debated in the literature.
+|          Why cities differ in their amount of spending on public goods is an interesting question that is frequently debated in the literature.
 @trounstine_segregation_2016 posits that segregation may be an important underlying cause of the underprovsion of public goods.
@@
 
-In this paper, I first worked to provide a check on the analysis presented in @trounstine_segregation_2016 by attempting to replicate the work in R.
+|          In this paper, I first worked to provide a check on the analysis presented in @trounstine_segregation_2016 by attempting to replicate the work in R.
 I was able to successfully replicate all of the main results, with the exception of a few of a few marginal analyses of the complex, multi-level models which, to my knowledge, are currently not supported by available R packages.
@@
 
-I then tested the models in @trounstine_segregation_2016 by re-running them with additional data that I imputed from missing values in the original datasets.
+|          I then tested the models in @trounstine_segregation_2016 by re-running them with additional data that I imputed from missing values in the original datasets.
 The large number of missing values in both of the datasets used in @trounstine_segregation_2016's main analysis created a concern for potential bias in the original results and for a lack of representativeness due to the large proportion of observations excluded from the regression analysis because of missing data.
@@
 
-The results of the data imputation exercise differed between the two datasets.
+|          The results of the data imputation exercise differed between the two datasets.
 For the analyses using the smaller, racial polarization dataset, re-running the models with the imputed data resulted in a smaller magnitude of the coefficient on the segregation index, and also made it statistically insignificant in the main model specification.
@@
 
-On the other hand, for the analyses using the much larger financial segregation dataset, the results of the models using the multiply imputed data sharply contrasted the results of @trounstine_segregation_2016, suggesting that diversity, and not segregation, was the best explanatory variable for public goods spending across all cities.
+|          On the other hand, for the analyses using the much larger financial segregation dataset, the results of the models using the multiply imputed data sharply contrasted the results of @trounstine_segregation_2016, suggesting that diversity, and not segregation, was the best explanatory variable for public goods spending across all cities.
 While these results originally seemed quite contradictory, I was able reconcile this finding by discovering that the results of @trounstine_segregation_2016 seem to be only really representative of larger cities.
@@
 
-```{r}
-
-range(fin_seg$population)
-
-quantile(fin_seg$population, c(.25, .5, .75, .80, .90, 1))
-
-median_fin_seg_pop <- median(fin_seg$population)
-
-range(fin_dge$population)
-
-quantile(fin_dge$population, c(.25, .5, .75, .80, .90, 1))
-
-median(fin_dge$population)
-
-```
-
-The replication exercise and the robustness check of @trounstine_segregation_2016's model using multiply imputed data provide additional evidence that residential racial segregation is associated with political polarization.
+|          The replication exercise and the robustness check of @trounstine_segregation_2016's model using multiply imputed data provide additional evidence that residential racial segregation is associated with political polarization.
 Furthermore, I find evidence that supports the finding of @trounstine_segregation_2016 that increases in segregation are associated with decreases in public goods spending; however, I find that this is only the case for larger cities.
@@
 This provides a possible explanation as to why the coefficient on diversity was positive for very small cities, as these "cities" may function more closely as neighborhoods.
-This is plausible given that many of the "cities" in the original financial segregation dataset in @trounstine_segregation_2016 were extremely small, with the overall median city population being `r median_fin_seg_pop`.
+This is plausible given that many of the "cities" in the original financial segregation dataset in @trounstine_segregation_2016 were extremely small, with the overall median city population being `r median(fin_seg$population)`.
 As discussed in the literature review, diversity at the neighborhood level is associated with lower levels of political polarization (Oliver 2010) and thus we would expect these areas to have higher levels of public goods spending according to the logic of @trounstine_segregation_2016.
@@
 
-The underprovision of public goods may inhibit social mobility and unfairly disadvantage certain groups.
+|          The underprovision of public goods may inhibit social mobility and unfairly disadvantage certain groups.
 @trounstine_segregation_2016 has identified an important relationship between segregation and the provision of public goods, which I suggest holds for larger cities, but not necessarily for smaller ones.
@@
                 column.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Ideology Controls"),
-                notes = c("Table A1: This table displays the results of the replication effort of the analyses conducted in Trounstine (2016)", 
+                notes = c("Table 5: This table displays the results of the replication effort of the analyses conducted in Trounstine (2016)", 
                           "using the racial polarization dataset. The replication code can be found on my personal Github repository, which is",
-                          " linked in the introduction. The original table is displayed for comparison as Figure 3."),
+                          " linked in the introduction. The original table is displayed for comparison as Figure 7."),
                 table.placement = "H",
@@
 
-![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016.
-My replication of these results can be found in Table A1 in this paper.](table_1.png)
+![Figure 7: This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016.
+My replication of these results can be found in Table 5 in the Appendix of this paper.](table_1.png)
 

### 2020-05-08 test_extension.Rmd
edits to formatting, etc.

@@
 bibliography: final_proj_bib.bib
-#biblio-style: "apalike"
 link_citations: true
+linestretch: 1.5
 header_includes: 
-  \usepackage{float}
-  \usepackage{multirow}
+  - \usepackage{float}
+  - \usepackage{multirow}
 
@@
 
-There is a large degree of variation in public goods spending across local governments.
+|          There is a large degree of variation in public goods spending across local governments.
 As a result, many scholars have worked to determine what factors may lead to the underprovision of public goods spending.
@@
 
-One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data, which substantially constrains the sample size used in the regression analysis.
+|          One concern with the original analysis in @trounstine_segregation_2016 is the large amount of missing data, which substantially constrains the sample size used in the regression analysis.
 For example, the regression analysis in the main specification using the the original racial polarization dataset exludes %`r round((obs_rp - 91)/obs_rp, 2)` of the observations, and the regression analysis in the main specification using the original financial segregation data excludes %`r round((obs_fin_seg - 13742)/ obs_fin_seg, 2)` of observations from the original dataset.
@@
 
-Comparing the results of the original regressions and those done with the imputed data yields similar big picture results in terms of the direction of the signs on the coefficients on the segregation indices.
+|          Comparing the results of the original regressions and those done with the imputed data yields similar big picture results in terms of the direction of the signs on the coefficients on the segregation indices.
 Like in @trounstine_segregation_2016, I find that segregation is positively associated with political polarization and negatively associated with spending on public goods.
@@
 
-Despite some progress made towards racial equity in the U.S.
+|          Despite some progress made towards racial equity in the U.S.
 on other fronts, residential racial segregation continues to be prevasive and deeply entrenched in society [@fischer_distinguishing_2004; @oliver_paradoxes_2010; @massey_american_1993].
@@
 
-```{r fin_aggr_plot, echo = FALSE, fig.cap = "This plot examines the pattern of missing data in the the original financial segregation dataset from Trounstine (2016).
-The plot on the left shows the percentage of missing data for each variable with missing data and reveals that a large number of variables are missing the vast majority of data.
-The plot on the right shows the pattern of missingness among the variables.
-We can see that only .58\\% of observations are complete (have no missing values), and a large majority of the observations are missing data for many variables.", fig.width= 7, fig.height = 5, fig.pos="H"}
-
-# select all variables with missing values for the aggr plot
-
-fin_imp_aggr <- fin_imp %>%
-  select(ideology_fill, H_citytract_NHW_i, chng5pctblk, chng5pctlatino, 
-         chng5pctasian, diversityinterp, pctblkpopinterp, pctasianpopinterp,
-         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp,
-         pctover65, pctcollegegradinterp) %>%
-    rename("White Ideology" = ideology_fill, "White/Non-White H Index" = H_citytract_NHW_i,
-           "5Y Change % Black" = chng5pctblk, "5Y Change % Latino" = chng5pctlatino, 
-           "5Y Change % Asian" = chng5pctasian, "Diversity" = diversityinterp, 
-           "% Asian" = pctasianpopinterp, "% Black" = pctblkpopinterp, 
-           "% Latino" = pctlatinopopinterp, "Median HH Income" = medinc_cpi,
-           "% Local Gov. Worker" = pctlocalgovworker_100, "% Renters" = pctrentersinterp, 
-           "% College Grads" = pctcollegegradinterp, "% 65+" = pctover65)
-
-new_try <- head(fin_imp_aggr, 20)
-
-# create the aggr plot
-
-aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.4, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
-title(main = "Patterns of Missingness in the Financial Segregation Data",
-      sub = "", font.main = 1, font.axis = 1, cex.main = 1, line = 3,  oma = c(1,3,5,1), font.main = 1, font.axis = 1)
-# this plot tells us that only .58% of the data are complete (not missing anything)
-
-```
-
 Because neither dataset seems to exhibit any clear patterns in the missing, data, it makes sense to proceed with the imputation.
@@
 
-```{r fp_imputations_original, include = FALSE}
+```{r rp_imputations, include = FALSE}
 
-# perform multiple imputations.
-We have the same issue here with the default method as with the previous dataset so we use CART.
-Additionally, because of the extremely large size of this dataset, we choose to only impute the variable H_citytract_NHW_i, as it is the most frequently missing variable and also out main independent variable.
-Just imputing this allows us to include way more observations in the regression than the original data despite the still large number of NAs overall.
-One concern here would be that if there was some reason that this variable was missing rather than other variables that only imputing this variable could lead to some bias in the results.
+# Now that we have imputed the missing data, we can re-run the analyses from the
+# original paper to see how and if this changes the analysis. We can use the
+# with() function from the mice package to fit each of the imputed datasets to
+# the model and then pool the results afterwards.
 
-# generate a blank run to get the method matrix
+# regression 1: fit multiple imputed datasets
 
-ini <- mice(fin_imp, maxit = 0, print = FALSE)
+fit_imp_1_rp <- with(imp_1_rp, lmer(formula = biggestsplit ~ H_citytract_multi_i + diversityinterp + pctasianpopinterp + pctblkpopinterp + pctlatinopopinterp + medincinterp + pctrentersinterp +  pctcollegegradinterp + biracial + nonpartisan + primary + logpop + year.f + south + midwest + west + (1 | geo_id2), REML=FALSE))
 
-# view the current method settings
+# pool and summarize the analyses
 
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs <- mice(fin_imp, method = meth, maxit = 1)
+pool_imp_1_rp <- pool(fit_imp_1_rp)
+imp_1_rp_sum <- summary(pool_imp_1_rp)
 
@@
 
-## make sure to talk about the fact that still a large number of values missing for the imputed variables here
+```{r results_printing_rp_impute_regressions_1, results = "asis", echo=FALSE, fig.pos="H"}
 
-Before examining the results of Trounstine's model using the multiply imputed data, I first ran some diagnostic tests on the imputation results to make sure that everything ran as expected.
-First, I checked the convergence of the algorithm used within mice() by plotting the trace lines as a function of the number of iterations for each of the variables.
-Then, I visually inspected the distributions of the imputed data in comparison to the original data with density and strip plots.
-All of these checks suggested that the imputed values were within a plausible range of the data and that their distribution fit the underlying distribution of the data relatively well.
-The only cases in which there was some cause for concern were for some of the variables with very few missing values in the racial polarization dataset (such as the indicators for region).
-However, this is more or less to be expected given the small number of imputations performed in these cases.
-Thus, and especially because there are so few of these values missing in the actual datasets, this was not a major concern.
-See figures X and X1 to see the density plots of the imputed values overlayed on the density plots of the original variables.
-The code to generate the rest of the plots and results of the diagnostic tests discussed here are presented in the Appendix.
+# print results of 1st regression
 
-```{r fs_densityplot, echo = FALSE}
+imp_1_rp_sum_table <- as.data.frame(imp_1_rp_sum) %>% 
+  select(term, estimate, std.error, p.value) %>%
+  head(13) %>%
+  mutate()
 
-my.settings <- list(
-  par.main.text = list(font = 1, cex = 1)
+imp_1_rp_sum_table_vars <- tibble(
+  Variable = c("Intercept", "Multigroup Seg. Index", "Diversity", "% Asian", "% Black", "% Latino",
+               "Median Income (1000s)", "% Renters", "% College Grads", "Biracial Elec.", "Nonpartisan Elec.", "Primary Elec.", "Pop (logged)", "N"),
+  Estimate = c(round(imp_1_rp_sum_table$estimate, 3), 203),
+  `Std. Error` = c(round(imp_1_rp_sum_table$std.error,3), ""),
+  `P-Value` = c(round(imp_1_rp_sum_table$p.value, 3), "")
   )
 
-#densityplot(imp_fs)
-densityplot(x = imp_fs, 
-            data = ~ H_citytract_NHW_i + chng5pctblk + chng5pctlatino + chng5pctasian + ideology_fill,
-            main = "Density Plots of Imputed and Original Data by Variable\nin the Financial Segregation Dataset",
-            par.settings = my.settings,
-            par.strip.text = list(cex = 1))
+kable(imp_1_rp_sum_table_vars, 
+      "latex", 
+      caption = "\\textbf{Racial Polarization in Segregated Cities: Racial Divide with Multigroup Segregation Index}", 
+      booktabs = T,
+      align = c("l","c","c","c")) %>%
+  row_spec(0, bold = TRUE) %>%
+  footnote(symbol = c("N = klefnwkjenfjw"),
+    general = c("This table shows the results of Trounstine's first model for the effect of segregation on political polarization",
+  "(racial vote divide) using the multi-group Theil's H Segregation Index using the new, multiply imputed",
+  "datasets. The sign of the coefficient on the main variable of interest, the segregation index, is the same, but",
+  "the result has become statisically insignificant with the 95% confidence interval containing zero. Thus",
+  "while these results still suggest that segregation may be associated with increased political polarization,",
+  "they confer a lesser degree of certainty than Trounstine's original analysis. The coefficients for % Black",
+  "population, % Latino population, and median household income have also switched signs. The coefficient",
+  "on the indicator for a primary election, has also changed from being significant in the original analysis",
+  "to insignificant here. In general, the standard errors on the coefficients have decreased slightly."),
+           general_title = "Table 1:",
+    footnote_order = c("symbol", "general")) %>%
+  kable_styling(full_width = TRUE, latex_options = "hold_position" )
 
 ```
-
-Given the promising results of the diagnostic checks, I next proceeded to re-estimate the original model using the multiply imputed datasets, pooling the results to produce final pooled regression coefficients and parameters.
-The results for the analyses using the racial polarization dataset are presented in tables X1-X3.
 
@@
 In all three of the specifications, tandard errors reduced slightly using the larger, multiply imputed datasets compared to the original analysis with the original data in @trounstine_segregation_2016.
-
-For the financial segregation dataset, we similarly fit each of our 5 imputed datasets to the original models from @trounstine_segregation_2016 using this data and then pool the results for each.
-The pooled results are presented in tables 4-6.
-
-```{r fs_imputed_main_1st_specification, include = FALSE}
-
-# Main Analysis 2: Imputations
-
-## regression 1 Table 2
-
-# fit multiple imputed datasets
-
-fit_imp_felm1 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm1 <- pool(fit_imp_felm1)
-imp_felm1_sum <- summary(pool_imp_felm1)
-
-```
-
-The results of the first regression present a stark difference to the results of @trounstine_segregation_2016.
-Crucially, the effect size of the segregation index on public spending has essentially gone to zero and has become statistically insignificant.
-Interestingly, the coefficient on the diversity variable has increased substantially from .106 to .759 and has become statistically significant.
-The sign of the coefficient on percent Asian popultion has switched signs from negative to positive; however, it remains statistically insignificant.
-
-The results of the first regression indicate that Trounstine's results are robust to the inclusion of the imputed data, which led to the inclusion of an additional 59,377 observations in the analysis.
-The coefficients, standard errors, and significance levels are essentially unchanged.
-The same is largely true for the second and third specifications, but the magnitude of the coefficient on the segregation decreases slightly.
-
-```{r fs_imputed_pooled_regressions, include = FALSE, eval = FALSE}
-
-## regression 2 Table 2
-
-# fit multiple imputed datasets
-
-fit_imp_felm2 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + chng5pctblk + chng5pctlatino + chng5pctasian+ medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm2 <- pool(fit_imp_felm2)
-imp_felm2_sum <- summary(pool_imp_felm2)
-
-## Regression 3 Table 2
-
-fit_imp_felm3 <- with(imp_fs, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop + ideology_fill | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_imp_felm3 <- pool(fit_imp_felm3)
-imp_felm3_sum <- summary(pool_imp_felm3)
-
-print(imp_felm1_sum)
-
-```
-
-```{r results_printing_fs_impute_regressions_1, results = "asis", echo=FALSE}
-
-# print results of 1st regression
-
-imp_felm1_sum_table <- as.data.frame(imp_felm1_sum %>% 
-  select(term, estimate, std.error, p.value))
-
-imp_felm1_sum_table_vars <- tibble(
-  Variable = c("White/Nonwhite Seg. Index", "Diversity", "% Black", "% Asian", "% Latino", "Median Income (1000s)", "% Local Gov. Worker", "% Renters", "% 65+", "% College Grads", "Pop (logged)"),
-  Estimate = round(imp_felm1_sum_table$estimate, 3),
-  `Std. Error` = round(imp_felm1_sum_table$std.error,3),
-  `P-Value` = round(imp_felm1_sum_table$p.value, 3)
-)
-
-kable(imp_felm1_sum_table_vars, "latex",
-      caption = "\\textbf{Effect of Segregation on Overall per Capita Direct General City Expenditures: Imputed Data for all Cities}",
-      booktabs = T) %>%
-    row_spec(0, bold = TRUE) %>%
-  footnote(general = c("This table shows the results of Trounstine's first model for the effect of segregation on per capita direct",
-  "public expenditure using the two-group Theil's H Segregation Index using the new, multiply imputed datasets.",
-  "The results present a stark contrast to Trounstine's original results: the main coefficient on segregation index",
-  "has decreased to essentially zero and has become statistically insignificant. The very large P-Value may indicate",
-  "there is a larger difference between the two models. The coefficient on diversity has increased in magnitude and",
-  "become statistically significant."),
-           general_title = "Table 4:") %>%
-  kable_styling(full_width = TRUE)
-
-```
-
-```{r results_printing_fs_impute_regressions_2, results = "asis", echo=FALSE, eval = FALSE, invlude = FALSE}
-
-# print results of 2nd regression
-
-imp_felm2_sum_table <- as.data.frame(imp_felm2_sum %>% 
-  select(term, estimate, std.error, p.value))
-
-imp_felm2_sum_table_vars <- tibble(
-  Variable = c("White/Nonwhite Seg.
-Index", "% Black", "% Asian", "% Latino", "5Y Change % Black", "5Y Change % Latino", "5Y Change % Asian", "Median Income (1000s)", "% Local Gov.
-Worker", "% Renters", "% 65+", "% College Grads", "Pop (logged)"),
-  Estimate = round(imp_felm2_sum_table$estimate, 3),
-  `Std. Error` = round(imp_felm2_sum_table$std.error,3),
-  `P-Value` = round(imp_felm2_sum_table$p.value, 3)
-)
-
-kable(imp_felm2_sum_table_vars, "latex",
-      caption = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Changing Demographics}",
-      booktabs = T) %>%
-    row_spec(0, bold = TRUE) %>%
-  footnote(general = c("This table shows the results of Trounstine's second model for the effect of segregation on per capita",
-  "direct public expenditure using the two-group Theil's H Segregation Index using the new, multiply imputed datasets.",
-  "Again, in contrast to Trounstine's original results, the main coefficient on segregation index has decreased to",
-  "essentially zero and has become statistically insignificant with a very large P-Value."),
-           general_title = "Table 5:") %>%
-  kable_styling(full_width = TRUE)
-
-```
-
-```{r results_printing_fs_impute_regressions_3, results = "asis", echo=FALSE, eval = FALSE, include = FALSE}
-
-# print results of 3rd regression
-
-imp_felm3_sum_table <- as.data.frame(imp_felm3_sum %>% 
-  select(term, estimate, std.error, p.value))
-
-imp_felm3_sum_table_vars <- tibble(
-  Variable = c("White/Nonwhite Seg.
-Index", "Diversity", "% Black", "% Asian", "% Latino", "Median Income (1000s)", "% Local Gov.
-Worker", "% Renters", "% 65+", "% College Grads", "Pop (logged)", "Ideology"),
-  Estimate = round(imp_felm3_sum_table$estimate, 3),
-  `Std. Error` = round(imp_felm3_sum_table$std.error,3),
-  `P-Value` = round(imp_felm3_sum_table$p.value, 3)
-)
-
-kable(imp_felm3_sum_table_vars, "latex",
-      caption = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures: Direct General Exp. with Ideology Control}",
-      booktabs = T) %>%
-    row_spec(0, bold = TRUE) %>%
-  footnote(general = c("This table shows the results of Trounstine's third model for the effect of segregation on political polarization",
-  "(racial vote divide) using the two-group Theil's H segregation Index and including controls for ideology",
-  "using the new, multiply imputed datasets. Compared to Trounstine's original results, the main coefficient on",
-  "segregation index has decreased in magnitude although, it remains statistically significant. The other",
-  "coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian and",
-  "Black have switched signs. Standard errors have also reduced slightly in these specifications compared to",
-  "the original analysis in Trounstine (2016)."),
-           general_title = "Table 6:") %>%
-  kable_styling(full_width = TRUE)
-
-```
-
-```{r population_over_Baqir, include = FALSE}
-
-# Baqir et al uses city as population above 25,000
-
-baqir <- log(25000)
-
-fin_imp_pop_over_baqir <- fin_imp %>%
-  filter(logpop > baqir )
-
-nrow(fin_imp_pop_over_baqir)
-median(fin_imp_pop_over_baqir$logpop)
-
-gg_miss_var(fin_imp_pop_over_baqir, show_pct = T)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_over_baqir, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_overbaqir <- mice(fin_imp_pop_over_baqir, method = meth, maxit = 5)
-
-```
-
-```{r over_baqir_1st_specification, include = FALSE}
-
-# fit multiple imputed datasets
-
-fit_over_baqir_1 <- with(imp_fs_pop_overbaqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_fit_over_baqir_1 <- pool(fit_over_baqir_1)
-imp_over_baqir_1_sum <- summary(pool_fit_over_baqir_1)
-
-```
-
-```{r over_baqir_t1, echo = FALSE}
-
-# print results of 1st regression
-
-imp_over_baqir_1_sum_table <- as.data.frame(imp_over_baqir_1_sum %>% 
-  select(term, estimate, std.error, p.value))
-
-imp_over_baqir_1_sum_table_vars <- tibble(
-  Variable = c("White/Nonwhite Seg. Index", "Diversity", "% Black", "% Asian", "% Latino", "Median Income (1000s)", "% Local Gov. Worker", "% Renters", "% 65+", "% College Grads"),
-  Estimate = round(imp_over_baqir_1_sum_table$estimate, 3),
-  `Std. Error` = round(imp_over_baqir_1_sum_table$std.error,3),
-  `P-Value` = round(imp_over_baqir_1_sum_table$p.value, 3)
-)
-
-kable(imp_over_baqir_1_sum_table_vars, "latex",
-      caption = "\\textbf{Effect of Segregation on Overall per Capita Direct General City Expenditures: Imputed Data for Cities with Populations of 25,000+}",
-      booktabs = T) %>%
-    row_spec(0, bold = TRUE) %>%
-  footnote(general = c("This table shows the results of Trounstine's third model for the effect of segregation on political polarization",
-  "(racial vote divide) using the two-group Theil's H segregation Index and including controls for ideology",
-  "using the new, multiply imputed datasets. Compared to Trounstine's original results, the main coefficient on",
-  "segregation index has decreased in magnitude although, it remains statistically significant. The other",
-  "coefficients except for the biracial indicator are insignificant, and the coefficients on percent Asian and",
-  "Black have switched signs. Standard errors have also reduced slightly in these specifications compared to",
-  "the original analysis in Trounstine (2016)."),
-           general_title = "Table 6:") %>%
-  kable_styling(full_width = TRUE)
-
-```
-
-```{r population_under_Baqir, include = FALSE}
-
-# Baqir et al uses city as population above 25,000
-
-baqir <- log(25000)
-
-fin_imp_pop_under_baqir <- fin_imp %>%
-  filter(logpop < baqir )
-
-nrow(fin_imp_pop_under_baqir)
-median(fin_imp_pop_under_baqir$logpop)
-
-gg_miss_var(fin_imp_pop_under_baqir, show_pct = T)
-
-# generate a blank run to get the method matrix
-
-ini <- mice(fin_imp_pop_under_baqir, maxit = 0, print = FALSE)
-
-# view the current method settings
-
-meth <- ini$method
-
-# change the method variables for all variables except H_citytract_NHW_i to ""
-# so that their missing values aren't imputed
-
-meth[c("dgepercap_cpi", "diversityinterp", "pctblkpopinterp", "pctasianpopinterp",
-         "pctlatinopopinterp", "medinc_cpi", "pctlocalgovworker_100", "pctrentersinterp",
-         "pctover65", "pctcollegegradinterp", "logpop", "geo_id2")]=""
-
-# change the default method to "cart" so that we don't get the error
-
-meth[c("H_citytract_NHW_i", "chng5pctblk", 
-       "chng5pctlatino", "chng5pctasian", "ideology_fill")] = "cart"
-
-# perform the multiple imputations with 5 iterations
-
-imp_fs_pop_under_baqir <- mice(fin_imp_pop_under_baqir, method = meth, maxit = 1)
-
-```
-
-```{r population_under_Baqir_1st_specification, include = FALSE}
-
-# fit multiple imputed datasets
-
-fit_under_baqir_1 <- with(imp_fs_pop_under_baqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))
-
-# pool the analyses
-
-pool_fit_under_baqir_1 <- pool(fit_under_baqir_1)
-imp_under_baqir_1_sum <- summary(pool_fit_under_baqir_1)
-
-```
-
-```{r calc_coeff_sds_original_fs_impute, include = FALSE}
-
-model_coeff <- tibble(
-  variable = c("White/Non-White Seg. Index", "Diversity", 
-               "White/Non-White Seg. Index", "Diversity",
-               "White/Non-White Seg. Index", "Diversity", 
-               "White/Non-White Seg. Index", "Diversity"),
-  estimate = c(imp_under_baqir_1_sum[1,2], imp_under_baqir_1_sum[2,2],
-               imp_felm1_sum[1,2], imp_felm1_sum[2,2],
-               coef(felm1)[1], coef(felm1)[2],
-               imp_over_baqir_1_sum[1,2], imp_over_baqir_1_sum[2,2]),
-  std_error = c(imp_under_baqir_1_sum[1,3], imp_under_baqir_1_sum[2,3],
-                imp_felm1_sum[1,3], imp_felm1_sum[2,3],
-                summary(felm1)$coeff[1,2], summary(felm1)$coeff[2,2],
-                imp_over_baqir_1_sum[1,3], imp_over_baqir_1_sum[2,3]),
-  model = c( "fin_imp_pop_under_baqir", "fin_imp_pop_under_baqir",
-             "fin_imp", "fin_imp",
-            "fin_dge", "fin_dge",
-            "fin_imp_pop_over_baqir", "fin_imp_pop_over_baqir")
-)
-
-model_coeff <- model_coeff %>%
-  mutate(variable = as.factor(variable))
-
-```
-
-```{r dataset_rows_in_analysis}
-
-complete_fs <- complete(imp_fs,1) %>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
-         !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
-         !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
-         !(is.na(logpop)), dgepercap_cpi != 0)
-
-complete_over_baqir <- complete(imp_fs_pop_overbaqir, 1)%>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
-         !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
-         !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
-         !(is.na(logpop)), dgepercap_cpi != 0)
-
-complete_under_baqir <- complete(imp_fs_pop_under_baqir, 1)%>%
-  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
-         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
-         !(is.na(pctlatinopopinterp)),
-         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
-         !(is.na(pctrentersinterp)),
-         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
-         !(is.na(logpop)), dgepercap_cpi != 0)
-
-```
-
-```{r dataset_medians}
-
-data_info <- tibble(
-  dataset = c("fin_imp", "fin_imp_pop_over_baqir", "fin_imp_pop_under_baqir",
-               "fin_dge"),
-  median = c(median(fin_imp$logpop), median(fin_imp_pop_over_baqir$logpop),
-              median(fin_imp_pop_under_baqir$logpop), median(fin_dge$logpop)),
-  rows = c(nrow(complete_fs), nrow(complete_over_baqir), nrow(complete_under_baqir),
-          nrow(fin_dge))
-)
-
-model_summaries <- left_join(model_coeff, data_info, by = c("model" = "dataset"))
-
-```
-
-```{r coef_plot_originals_over_under, echo = FALSE}
-
-model_summaries %>%
-  ggplot(aes(x = median, y = estimate)) +
-  geom_point()+
-  geom_errorbar(aes(ymin = estimate - 2 * std_error, ymax = estimate + 2 * std_error, width = .2)) +
-  geom_hline(yintercept = 0, color = "red") +
-  facet_wrap(~variable, labeller = labeller(variable = coef.labels)) +
-  ggtitle("Coefficient Plots for Diversity and White/Non-White Segregation Indices Across\nthe Models")+
-  xlab("Models Ordered by Increasing Median Population Size of the Sample") +
-  ylab("Estimate and 95% Confidence Interval") +
-  labs(caption = "This plot demonstrates how the significance of diversity and segregation in predicting public\ngoods spending varies with city size.
-As city populaiton size increases, diversity tends to have\nless explanatory power for public goods spending while segregation has more.
-The opposite\nis true when considering city population size decreasing: segregation becomes less important\nas diversity becomes increasingly important.") +
-  theme_bw()+
-  theme(plot.caption = element_text(hjust = 0))
-
-```
-
-```{r histograms_city_pop_in_specifications_prep, include = FALSE}
-
-pop_data_over_baqir <- tibble(
-  log_pop = complete_over_baqir$logpop,
-  Analysis = "Imputed, pop. > 25k"
-)
-
-pop_data_under_baqir <- tibble(
-  log_pop = complete_under_baqir$logpop,
-  Analysis = "Imputed, pop. < 25k"
-)
-
-pop_data_imp_fs <- tibble(
-  log_pop = complete_fs$logpop,
-  Analysis = "Imputed, Whole Sample"
-)
-
-pop_data_fin_dge <- tibble(
-  log_pop = fin_dge$logpop,
-  Analysis = "Trounstine (2016)"
-)
-
-pop_data_fin_seg <- tibble(
-  log_pop = fin_seg$logpop,
-  Analysis = "Original Sample"
-)
-
-pop_hist_data <- rbind(pop_data_over_baqir, pop_data_imp_fs)
-pop_hist_data <- rbind(pop_hist_data, pop_data_under_baqir)
-pop_hist_data <- rbind(pop_hist_data, pop_data_fin_dge)
-pop_hist_data <- rbind(pop_hist_data, pop_data_fin_seg)
-
-median_pops <- tibble(
-  Analysis = c("Imputed, pop. > 25k", "Imputed, pop. < 25k", "Imputed, Whole Sample", "Trounstine (2016)", "Original Sample"),
-  median_log_pop = c(median(complete(imp_fs_pop_overbaqir,1)$logpop),
-                     median(complete(imp_fs_pop_under_baqir, 1)$logpop),
-                     median(complete(imp_fs, 1)$logpop),
-                     median(fin_dge$logpop),
-                     median(fin_seg$logpop, na.rm = T))
-)
-
-pop_hist_data <- left_join(pop_hist_data, median_pops)
-
-```
-
-```{r city_pops_histogram, echo = FALSE, warning = FALSE}
-
-pop_hist_data %>%
-  ggplot() +
-  geom_histogram(aes(x = log_pop, fill = Analysis)) +
-  geom_vline(aes(xintercept = median_log_pop), color = "red") +
-  facet_wrap(~Analysis) +
-  coord_cartesian(xlim = c(0,15)) +
-  ggtitle("Histograms of Log Population of City Observations Included in the\nVarious Regression Analyses") +
-  labs(caption = "This figure makes clear the differences in city size (in terms of population) among the different analyses.\n It is clear that the listwise deletion of observations with missing values resulted in a sample that almost entirely\nconsisted of larger cities in Trounstine (2016).
-The distribution of city population in Trounstine (2016)\nmore closely resembles the distribution of the original sample with a greater than 25,000 population\ncutoff imposed than the original sample.
-The red lines indicate the median log population in each sample.") +
-  ylab("Count") +
-  xlab("Log Population") +
-  theme_bw() +
-  theme(plot.caption = element_text(hjust = 0),
-        strip.text.x = element_text(size = 8))
-
-```
-
-# Conclusion
-
-Why cities differ in their amount of spending on public goods is an interesting questions that is frequently debated in the literature.
-@trounstine_segregation_2016 posits that segregation may be an important underlying cause of the underprovsion of public goods.
-Finding evidence that residential segregation by race increases political partisanship, @trounstine_segregation_2016 argues that residential segregation can increase division and make cooperation amongst competing groups difficult, which results in decreased spending on public goods.
-The findings of @trounstine_segregation_2016 are particularly important because they suggest that segregation, as defined by many homogeneous neighborhoods within a larger diverse geographical area, is the key factor in disinvestment in public goods.
-This contradicts previous research which has suggested that levels of diversity were instead most important (see for example @baqir_public_1999 or @hopkins_diversity_2009).
-While @trounstine_segregation_2016 still represents relatively new reasearch as of 2020, it has yet to be fully vetted by additional research.
-Furthermore, some research that has been published on the topic since its publication suggests that other factors such as larger inequities in the political system favoring socially powerful groups [@lee_ethnic_2018] or the interaction of income and racial inequality [@an_its_2018] may be more important in explaining public goods provisions.
-
-I first worked to provide a check on the analysis presented in @trounstine_segregation_2016 by attempting to replicate the work in R.
-I was able to successfully replicate all of the main results from @trounstine_segregation_2016, with the exception of a few of a few marginal analyses of the complex, multi-level models which, to my knowledge, are currently not supported by available R packages.
-I was, however, able to successfully replicate these results in Stata.
-
-As an additional robustness check I also tested the models in @trounstine_segregation_2016 by re-running them with additional data that I imputed from missing values in the original datasets.
-The large number of missing values in both of the datasets used in @trounstine_segregation_2016's main analysis created a concern for potential bias in the original results and a lack of representativeness due to the large amount of data excluded from the regression analysis due to missing values.
-Thus, I used the mice package in R to create multiply imputed datasets, upon which I re-ran the models and pooled the results to generate the final model coefficients and parameters.
-
-The results of the data imputation exercise differed between the two datasets.
-For the analyses using the smaller, racial polarization dataset, the results from the imputed data resulted in a smaller magnitude of the coefficient on the main independent variable, and also made it statistically insignificant in the main model specification.
-This suggests that the segregation index may not have as strong of a positive association with political polarization as @trounstine_segregation_2016 suggests.
-However, for the analyses using the much larger financial segregation dataset, the results of the models using the multiply imputed data largely mirrored the results of @trounstine_segregation_2016, and the coefficients and significance levels were essentially the same between the two, with the standard errors on the model estimates being generally slightly lower for the analyses using the imputed data.
-This provides strong support for @trounstine_segregation_2016's finding that residential racial segregation is associated with diminshed spending on public goods.
-
-The replication exercise and robustness check using multiply imputed data here provide strong evidence that residential segregation along racial lines does in fact correlate negatively with spending on a variety of public goods.
-What my analysis calls more into question, is by what mechanism this happens.
-Using the multiply imputed data, I still found some evidence that segregation may be associated with increased political polarization which @trounstine_segregation_2016 suggests may lead to diminished public goods spending; however, the effect size is much smaller than that found in @trounstine_segregation_2016, and some of the results have become insignificant.
-It is possible that other mechanisms may be more important in explaining why segregation might be associated with decreased spending on public goods.
-For example, it could be that there is an important interaction effect between income and segregation, as others have previously suggested, or there could be some other intervening mechanism or a confounding variable that is leading to the negative association between segregation and lower spending on public goods.
-@trounstine_segregation_2016 has identified an important relationship between segregation and the provision of public goods.
-However, my analysis suggests that further research is needed to assess the potential mechanisms by which residential segregation by race or even a confounding variable may result in dimished spending.
-If this mechanism can be better understood, than it will be possible to more effectively understand and address the underprovision of public goods, which may inhibit social mobility and unfairly disadvantage certain groups.
-
-\newpage
-# Bibliography

### 2020-05-08 Burzillo_Trounstine_Replication.Rmd
final edits

@@
 ```
-\setlength\parindent{24pt}
+
 # Introduction
@@
 As a result, many scholars have worked to determine what factors may lead to the underprovision of public goods.
-Research in the past has associated racial diversity or changes in levels of diversity with the under-provision of public goods [@baqir_public_1999; @hopkins_diversity_2009].
-However, @trounstine_segregation_2016 argues that it is racial segregation, not diversity in and of itself, that results in the under-provision of public goods.
+Research in the past has associated racial diversity or changes in levels of diversity with the underprovision of public goods [@baqir_public_1999; @hopkins_diversity_2009].
+However, @trounstine_segregation_2016 argues that it is racial segregation, not diversity in and of itself, that results in the underprovision of public goods.
 Trounstine’s analysis consists of two main parts.
 First, she uses election and demographic data from 25 of America’s largest cities between 1990 and 2010 to run a multilevel mixed-effects linear regression with fixed effects for region and year and with random effects for cities in order to show that political polarization increases with segregation.
-Trounstine measures segregation with Theil's H Index, which measures the degree to which the diversity of a neighborhood differs from the diversity of the entire city.
+Trounstine measures segregation with Theil's H Index, which measures the degree to which the diversity of a neighborhood differs from the diversity of an entire city.
 The second main part of Trounstine’s analysis looks at the ability of the Theil’s H Segregation Index to explain a variety of types of public expenditures by city using a sample of 2,637 cities with 13,742 city-year observations.
-Using linear regressions with fixed effects for cities and robust standard errors clustered by city, Trounstine finds a significant, negative correlation between segregation and public goods spending that is robust to the inclusion of a variety of relevant controls and an alternative specification in which the number of waterways is used as an instrument for segregation.
+Using linear regressions with fixed effects for cities and robust standard errors clustered by city, Trounstine finds a significant, negative relationship between segregation and public goods spending that is robust to the inclusion of a variety of relevant controls and an alternative specification in which the number of waterways is used as an instrument for segregation.
 
@@
 
-|          One concern with the original analysis in @trounstine_segregation_2016 is the exclusion of large amounts of missing data, which substantially constrains the sample size in the regression analysis.
+|        One concern with @trounstine_segregation_2016 is the exclusion of a large proportion of observations from the regression analysis due to missing data for some values, which substantially constrains the sample size.
 For example, the regression analysis in the main specification using the the original racial polarization dataset exludes %`r round((obs_rp - 91)/obs_rp * 100, 0)` of the observations, and the regression analysis in the main specification using the original financial segregation dataset excludes %`r round((obs_fin_seg - 13742)/ obs_fin_seg * 100, 0)` of observations.
@@
 Studying diversity can be somewhat difficult and confusing because its effects tend to differ by geographic level.
-On the neighborhood level, a lack of intra-neighborhood racial diversity has been associated with racial intolerance, resentment, and competition between racial groups [@oliver_paradoxes_2010].
+On the neighborhood level, a lack of racial diversity has been associated with racial intolerance, resentment, and competition between racial groups [@oliver_paradoxes_2010].
 Living within non-diverse or segregated neighborhoods has also been associated with holding negative stereotypes and perceptions about out groups [@eric_oliver_intergroup_2003].
@@
 However, at the city or metropolitan level, the opposite seems to be true: when considering larger geographic areas, diversity, not homogeneity, is correlated with racial tension, competition, prejudice, lower levels of cooperation, and lower spending on public goods [@oliver_paradoxes_2010; @baqir_public_1999; @hopkins_diversity_2009].
-As a result, these theories predict that geographic areas most ripe for racial tension and competition will be those that are diverse overall, but have many homogeneous, non-diverse neighborhoods, meaning that while people of different races co-exist within a larger metropolitan area, they live separately within their own neighborhoods.
+Considering these theories jointly would predict that the geographic areas most ripe for racial tension and competition will be those that are diverse overall, but have many homogeneous, non-diverse neighborhoods, meaning that while people of different races co-exist within a larger metropolitan area, they live separately within their own neighborhoods.
 This situation corresponds to @trounstine_segregation_2016's definition of a severely segregated city.
@@
 |        In an attempt to better deal with the problem of missing data in @trounstine_segregation_2016, I impute missing values in the original data using the mice package in R, which generates multivariate imputations using chained equations [@mice].
-While there are a variety of different imputation methods that could have been employed, multiple imputation (such as the multiple multivariate imputations generated by mice) is desirable because instead of inputting a single value such as the mean for missing values, it instead uses the distribution of the available data to estimate multiple potential values for the missing data.
+While there are a variety of different imputation methods that could have been employed, multiple imputation (such as the multiple multivariate imputations generated by mice) is desirable because instead of inputting a single value such as the mean for missing values, it instead uses the distribution of the available data to estimate multiple potential values for the missing values.
 As a result, multiple imputation helps to account for the uncertainty inherent in the imputation process and allows for the calculation of standard errors around estimators.
-Thus, multiple imputation allows the researcher to more accurately assess the uncertainty of the analysis in general.
+This allows the researcher to more accurately assess the uncertainty of the analysis in general.
 
@@
 For example, there are `r format(sum(is.na(fin_imp$H_citytract_NHW_i)), big.mark = ",")` missing values for the segregation index, which is the main independent variable, or %`r round(sum(is.na(fin_imp$H_citytract_NHW_i))/nrow(fin_imp)*100,0)` of the data.
-In this dataset, there are also many more observations for which values are missing for multiple variables in comparison to the racial polarization dataset, as can be seen in the figure on the right in Figure 2.
+In this dataset, there are also many more observations for which values are missing for multiple variables in comparison to the racial polarization dataset, as can be seen in the plot on the right in Figure 2.
 In total, a mere %`r .0058*100` of observations are complete for all variables included in the main specification for the financial segregation dataset.
@@
 
-imp_1_rp <- mice(rp_impute, method = "cart", maxit = 5)
+imp_1_rp <- mice(rp_impute, method = "cart", maxit = 20)
 
@@
 
-imp_fs <- mice(fin_imp, method = meth, maxit = 1)
+imp_fs <- mice(fin_imp, method = meth, maxit = 5)
 
@@
 
-```{r rp_densityplot, echo = FALSE, fig.cap = "Figure 3 presents the density plots of the imputed data (red) overlaid on the density plot for the pre-existing data (blue) for all those variables with missing values in the racial polarization dataset.
+```{r rp_densityplot, echo = FALSE, fig.cap = "This figure presents the density plots of the imputed data (red) overlaid on the density plot for the pre-existing data (blue) for all those variables with missing values in the racial polarization dataset.
 For the most part, the imputed data seem to fit the pre-existing data relatively well.
@@
     general = c("This table shows the results of Trounstine's first model for the effect of segregation on political polarization",
-  "using the multi-group Theil's H Segregation Index using the new, multiply imputed datasets. The",
-  "sign of the coefficient on the main variable of interest, the segregation index, is positive as in",
-  "Trounstine (2016), but the result has become statisically insignificant with the 95% confidence",
-  "interval containing zero. Thus while these results still suggest that segregation may be",
-  "associated with increased political polarization, they confer a lesser degree of certainty than",
-  "Trounstine's original analysis. In general, the standard errors on the coefficients have",
-  "decreased slightly."),
+  "using the multi-group Theil's H Segregation Index and the new, multiply imputed datasets. The sign",
+  "of the coefficient on the main variable of interest, the segregation index, is positive as in Trounstine",
+  "(2016), but the result has become statisically insignificant with the 95% confidence interval containing",
+  "zero. Thus while these results still suggest that segregation may be associated with increased",
+  "political polarization, they confer a lesser degree of certainty than Trounstine's original analysis.",
+  "In general, the standard errors on the coefficients have decreased slightly."),
            general_title = "Table 1:",
@@
 
-|          In the second and third model specifications, which use the two-group Theil's H Segregation Index, the results were similar.
-The main coefficient on segregation index decreased in magnitude, although it remained statistically significant.
+|        For the second and third model specifications, which use the two-group Theil's H Segregation Index, the results were similar.
+The main coefficient on the segregation index decreased in magnitude, although it remained statistically significant.
 The other coefficients except for the biracial indicator are insignificant, and standard errors have reduced slightly in these specifications compared to the original analysis in Trounstine (2016).
@@
 
-|          For the financial segregation dataset, I similarly fit each of our 5 imputed datasets to the original models from @trounstine_segregation_2016 using this data and then pooled the results for each.
+|        For the financial segregation dataset, I similarly fit each of our 5 imputed datasets to the original models from @trounstine_segregation_2016 and then pooled the results for each.
 As a result of the imputation process, I was able to include an additional `r format(73119 - 13742, big.mark = ",")` observations in the analysis, increasing the sample size by %`r round((73119 - 13742)/ 13742*100,0)`.
@@
     general = c("This table shows the results of Trounstine's first model for the effect of segregation on per capita direct",
-  "public expenditure using the two-group Theil's H Segregation Index using the new, multiply imputed datasets.",
+  "public expenditure using the two-group Theil's H Segregation Index and the new, multiply imputed datasets.",
   "The results present a stark contrast to Trounstine's original results: the main coefficient on segregation index",
@@
 |        Because these results differed to such a degree from @trounstine_segregation_2016's original findings, I performed some checks on the data included in each analysis.
-I discovered that @trounstine_segregation_2016 excluded most cities below a certain population size because of the nature of the paper's listwise deletion.
-It may be that small cities are more likely to be missing data, and thus they were more likely to be dropped in @trounstine_segregation_2016's analysis.
-Referring back to @baqir_public_1999, I decided to divide the orginal sample based upon the populaiton cutoff for cities used in that paper, which determined that the populaiton must be above 25,000 people for an area to be considered a city.
-Splitting the financial segregation dataset in two, one dataset above and one below the 25,000 population cutoff, I then again imputed missing values for each and used the multiply imputed datasets in Trounstine's original models.
-
-|          Figure 5 displays the population distributions used in each of these analyses.
+I discovered that @trounstine_segregation_2016 excluded most cities below a certain population size because of the nature of the paper's list-wise deletion of observations containing missing values: as small cities were more likely to be missing data, it seems that they were inadvertently and disproportionately dropped from @trounstine_segregation_2016's regression analysis.
+Given this development, I decided to test whether or not city population size affected the results.
+Making use of the population cutoff of at least 25,000 people used to define cities in @baqir_public_1999, I divided the orginal sample into cities having populations above and below 25,000 people.
+I then again imputed missing values for each and used the multiply imputed datasets in re-runs of Trounstine's original models.
+
+|        Before discussing the results of these two additional analyses, I first illustrate the differences in the city population sizes for the observations used in the various analyses in Figure 5, which displays the population distributions of the samples used in each.
 The figure makes it clear that the observations included in @trounstine_segregation_2016's original analysis were not representative of the original data sample with the missing values, as most of the cities with lower populations were excluded as a result of the list-wise data deletion.
 While the dataset generated from the data imputation on the whole sample also has a different distribution for city populaiton, the range of the data seems to be much more representative of the overall data range in comparison to the @trounstine_segregation_2016 sample.
-For comparison, I also include the distributions of the multiply imputed datasets above and below the 25,000 populaiton cutoff.
+In the plot, I also include the distributions of city population size of the multiply imputed datasets above and below the 25,000 population cutoff.
 For cities above the cutoff, the city population distribution is similar to the distribution in @trounstine_segregation_2016.
@@
 
-imp_fs_pop_overbaqir <- mice(fin_imp_pop_over_baqir, method = meth, maxit = 1)
+imp_fs_pop_overbaqir <- mice(fin_imp_pop_over_baqir, method = meth, maxit = 5)
 
@@
 
-imp_fs_pop_under_baqir <- mice(fin_imp_pop_under_baqir, method = meth, maxit = 1)
+imp_fs_pop_under_baqir <- mice(fin_imp_pop_under_baqir, method = meth, maxit = 5)
 
@@
   labs(caption = "Figure 5: This figure makes clear the differences in city size (in terms of population) among the different\nanalyses.
-It is clear that the listwise deletion of observations with missing values resulted in a sample\nthat almost entirely consisted of larger cities in Trounstine (2016).
-The distribution of city population\nin Trounstine (2016) more closely resembles the distribution of the original sample with a greater than\n25,000 population cutoff imposed than the original sample.
-The red lines indicate the median log\npopulation in each sample.") +
+It demonstrates how the list-wise deletion of observations with missing values resulted in a\nsample that almost entirely consisted of larger cities in Trounstine (2016).
+The distribution of city\npopulation in Trounstine (2016) more closely resembles the distribution of the original sample with a\ngreater than 25,000 population cutoff imposed than the distribution of the original sample.
+The red lines\nindicate the median log population in each sample.") +
   ylab("Count") +
@@
 
-```{r over_baqir_t1, echo = FALSE}
+```{r over_baqir_t1, echo = FALSE, fig.pos="H"}
 
@@
     row_spec(0, bold = TRUE) %>%
-  footnote(symbol = c("N = 6716"),
-    general = c("This table shows the results of Trounstine's model examining the effect of segregation on overall",
-  "per capita direct general expenditure using the multiply imputed dataset for cities with populations above",
+  footnote(symbol = c("N = 6,716"),
+    general = c("This table shows the results of Trounstine's model examining the effect of segregation on overall per",
+  "capita direct general expenditure using the multiply imputed dataset for cities with populations above",
   "25,000 people. As in Trounstine (2016), the effect of segregation on public goods spending is large, negative,",
@@
 
-```{r under_baqir_t1, echo = FALSE}
+```{r under_baqir_t1, echo = FALSE, fig.pos="H"}
 
@@
   footnote(symbol = c("N = 66,403"),
-    general = c("This table shows the results of Trounstine's model examining the effect of segregation on overal",
-  "per capita direct general expenditure using the multiply imputed dataset for cities with populations below",
-  "25,000 people. In contrast to Trounstine (2016) and the results of our analysis with the imputed datasets for",
-  "cities over 25,000 people, the effect of segregation on public goods spending is negligible and insignificant,",
-  "while the effect of diversity is large, positive, and significant."),
+    general = c("This table shows the results of Trounstine's model examining the effect of segregation on overal per",
+  "capita direct general expenditure using the multiply imputed dataset for cities with populations below",
+  "25,000 people. In contrast to Trounstine (2016) and the results of our analysis with the imputed datasets",
+  "for cities over 25,000 people, the effect of segregation on public goods spending is negligible and",
+  "insignificant, while the effect of diversity is large, positive, and significant."),
   footnote_order = c("symbol", "general"),
@@
 
-|          As a summary of all of the model results for the two main coefficients of interest, segregation index and diversity, a coefficient plot is presented as Figure XXX, with the models ordered by increasing median log population size of the sample on the x-axis.
-Looking first at the coefficients for diversity, the two models with low median city populaiton size have significant, positive coefficients, while the models with the larger median city populations have insignificant coefficients.
+|        As a summary of all of the model results for the two main coefficients of interest, segregation index and diversity, a coefficient plot is presented as Figure 6, with the models ordered by increasing median log population size of the sample on the x-axis.
+Looking first at the coefficients for diversity, the two models with low median city population size have significant, positive coefficients, while the models with the larger median city populations have insignificant coefficients.
 This suggestst that diversity is an important estimator of public goods spending for small, but not necessarily for large, cities.
 Next, looking at the plot for the segregation index, we see the oppposite effect.
-For the models where the median city population sizes were small, the coefficient on segregaiton is insignificant.
-However, for the two models with larger median city populations, the coefficients were significant and negative.
+For the models where the median city population sizes were small, the coefficient on segregation is insignificant.
+However, for the two models with larger median city populations, the coefficients are significant and negative.
 This suggests that for small cities, segregation is not a very good estimator of public goods spending, but when cities are larger, increases in a city's segregation index are associated with decreases in public goods spending.
@@
   labs(caption = "This plot demonstrates how the significance of diversity and segregation in predicting public goods spending\nvaries with city size.
-As city populaiton size increases, diversity tends to have less explanatory power for\npublic goods spending while segregation has more.
-The opposite is true when considering city population\nsize decreasing: segregation becomes less important as diversity becomes increasingly important.") +
+As city population size increases, diversity tends to have less explanatory power for\npublic goods spending while segregation has more.
+The opposite is true when moving in the opposite\ndirection: as city population size decreases, segregation becomes less important as diversity becomes\nincreasingly important in explaining public goods spending.") +
   theme_bw()+
@@
 Finding evidence that residential segregation by race increases political partisanship, @trounstine_segregation_2016 argues that residential segregation can increase division and make cooperation amongst competing groups difficult, which results in decreased spending on public goods.
-The findings of @trounstine_segregation_2016 are particularly important because they suggest that segregation, as defined by many homogeneous neighborhoods within a larger diverse geographical area, is the key factor in disinvestment in public goods.
+The findings of @trounstine_segregation_2016 are particularly important because they suggest that segregation, as defined by many homogeneous neighborhoods within a larger, diverse geographical area, is the key factor in disinvestment in public goods.
 This contradicts previous research which has suggested that levels of diversity were instead most important (see for example @baqir_public_1999 or @hopkins_diversity_2009).
@@
 |        In this paper, I first worked to provide a check on the analysis presented in @trounstine_segregation_2016 by attempting to replicate the work in R.
-I was able to successfully replicate all of the main results, with the exception of a few of a few marginal analyses of the complex, multi-level models which, to my knowledge, are currently not supported by available R packages.
+I was able to successfully replicate all of the main results, with the exception of the marginal analyses of the complex, multi-level models which, to my knowledge, are currently not supported by available R packages or functions.
 I was, however, able to successfully replicate these results in Stata.
@@
 |        I then tested the models in @trounstine_segregation_2016 by re-running them with additional data that I imputed from missing values in the original datasets.
-The large number of missing values in both of the datasets used in @trounstine_segregation_2016's main analysis created a concern for potential bias in the original results and for a lack of representativeness due to the large proportion of observations excluded from the regression analysis because of missing data.
+The large number of missing values in both of the datasets used in @trounstine_segregation_2016's main analysis created a concern for potential bias in the original results because observations with missing values were automatically excluded from the regression analysis.
 Using the mice package in R, I created multiply imputed datasets, upon which I re-ran the models and pooled the results to generate the final model coefficients and parameters.
@@
 For the analyses using the smaller, racial polarization dataset, re-running the models with the imputed data resulted in a smaller magnitude of the coefficient on the segregation index, and also made it statistically insignificant in the main model specification.
-This suggests that the segregation index may not have as strong of a positive association with political polarization as @trounstine_segregation_2016 suggests, but in general, the imputation exercise supportted the main conclusions of Trounstine's analysis.
+This suggests that segregation is still positively associated with political polarization, but maybe not quite as strongly as @trounstine_segregation_2016 suggests.
 
 |        On the other hand, for the analyses using the much larger financial segregation dataset, the results of the models using the multiply imputed data sharply contrasted the results of @trounstine_segregation_2016, suggesting that diversity, and not segregation, was the best explanatory variable for public goods spending across all cities.
-While these results originally seemed quite contradictory, I was able reconcile this finding by discovering that the results of @trounstine_segregation_2016 seem to be only really representative of larger cities.
-By dropping all observations in the original data with missing values for variables included in the regressions, it seems that @trounstine_segregation_2016 inadvertently restricted their sample to almost entirely larger cities (above 25,000 residents) whereas the full sample consisted of cities that had smaller populaitons on average.
-To test the hypothesis that diversity is more important for predicting public goods spending for small cities while segregation is more important for predicting public goods spending for larger cities, I divided the original dataset into two subsets based on the city classificaiton criteria used in @baqir_public_1999 that cities must have a population of at least 25,000 people.
+While these results originally seemed quite contradictory to @trounstine_segregation_2016, I was able reconcile this finding by discovering that the results of @trounstine_segregation_2016 seem to be representative only of larger cities.
+By dropping all observations in the original data with missing values for variables included in the regressions, it seems that @trounstine_segregation_2016 inadvertently restricted their sample to almost entirely larger cities (above 25,000 residents) whereas the full sample consisted of cities that had smaller populations on average.
+To test the hypothesis that diversity is more important for predicting public goods spending for small cities while segregation is more important for predicting public goods spending for larger cities, I divided the original dataset into two subsets of cities with populations above and below 25,000 people.
 I then multiply imputed the missing values for each data subset and re-ran the models.
@@
 
-|          The replication exercise and the robustness check of @trounstine_segregation_2016's model using multiply imputed data provide additional evidence that residential racial segregation is associated with political polarization.
+|        The replication exercise and the robustness check of @trounstine_segregation_2016's models using multiply imputed data provide evidence that residential racial segregation is associated with political polarization.
 Furthermore, I find evidence that supports the finding of @trounstine_segregation_2016 that increases in segregation are associated with decreases in public goods spending; however, I find that this is only the case for larger cities.
-In contrast to the argument made by @trounstine_segregation_2016, I find that, for small cities, diversity, not segregation, seems to be the most important explanatory variable for public goods spending.
-One potential explanation for this result could be that when cities become too small, the sort of segregation by neighborhood described in @trounstine_segregation_2016 as a diverse city broken down into homogenous, segregated neighborhoods becomes hard to maintain.
-When populaiton sizes are small, segregation may become difficult and inter-racial interactions may become more common, leading diversity to be more likely associated with integration and increased inter-racial contact.
-This provides a possible explanation as to why the coefficient on diversity was positive for very small cities, as these "cities" may function more closely as neighborhoods.
-This is plausible given that many of the "cities" in the original financial segregation dataset in @trounstine_segregation_2016 were extremely small, with the overall median city population being `r median(fin_seg$population)`.
-As discussed in the literature review, diversity at the neighborhood level is associated with lower levels of political polarization (Oliver 2010) and thus we would expect these areas to have higher levels of public goods spending according to the logic of @trounstine_segregation_2016.
-As cities become larger and larger, however, comprehensive segregation becomes more attainable.
-Thus, segregation, not diversity, becomes a better indicator of inter-racial harmony and cooperation and thus the best explanatory variable for public goods spending.
+For small cities, I find that diversity, not segregation, seems to be the most important explanatory variable for public goods spending.
+One potential explanation for why segregation does not seem to meaningfully explain public expenditures for small cities is that, when cities become too small, segregation becomes difficult to maintain.
+The sort of segregation by neighborhood described in @trounstine_segregation_2016 as a diverse city broken down into homogenous, segregated neighborhoods requires that multiple neighborhoods exist and have the space to be separated geographically.
+When city population sizes are small, this may not be feasible, and interracial interactions may become more common.
+As a result, an increase in diversity may be associated with a larger degree of integration and increased interracial contact within a small city, just as the literature expects would happen on the neighborhood level (Oliver 2010).
+This explanation makes sense in the context of the fact that the coefficient on diversity was positive for small cities in my model, indicating that an increase in diversity in small cities was associated with an increase in public spending, perhaps due to this absence of racial polarization.
+Given the very small size of most "cities" in the original datasets in @trounstine_segregation_2016, I might even argue that these political entities would be more productively considered as "towns" or "neighborhoods," given that the overall median city population in the financial segregation dataset was a mere `r median(fin_seg$population)`.
 
@@
                 title = "\\textbf{Racial Polarization in Segregated Cities}",
-                single.row = FALSE,
-                no.space = F,
+                single.row = TRUE,
+                no.space = T,
                 covariate.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Diversity", "Percent Asian", "Percent Black", "Percent Latino", "Medain HH Income (1000s)", "Percent Renters", "Percent College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology", "Constant"),
@@
 
-![Figure 7: This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016.
+![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016.
 My replication of these results can be found in Table 5 in the Appendix of this paper.](table_1.png)

### 2020-05-09 Burzillo_Trounstine_Replication.Rmd
final draft commit

@@
   footnote_order = c("symbol", "general"),
-           general_title = "Table 4:") %>%
+           general_title = "Table 2:") %>%
   kable_styling(full_width = TRUE, latex_options = "hold_position")
@@
 
+### Figure 7
 ![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016.

### 2020-05-09 Burzillo_Trounstine_Replication.Rmd
changes to repo organization
changes to readme

@@
 
-rp <- read_dta("racial_polarization_winners.dta")
-fin_seg<- read_dta("fin_seg.dta")
+rp <- read_dta("Trounstine_files/racial_polarization_winners.dta")
+fin_seg<- read_dta("Trounstine_files/fin_seg.dta")
 
@@
 ![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016.
-My replication of these results can be found in Table 5 in the Appendix of this paper.](table_1.png)
+My replication of these results can be found in Table 5 in the Appendix of this paper.](Trounstine_files/table_1.png)
 
